### 2020-01-17 CalNotes.tex
Initial commit

\documentclass[10pt]{article}

\input{ex_shared}

\begin{document}
\maketitle

\textbf{Abstract.} \corr{Copy-paste of SIAM UQ abstract, modify.} We present a novel technique for estimating the drift function of a diffusion process possessing two separated time scales. Our aim is fitting a homogenized diffusion model to a continuous sample path coming from the full multiscale process, thus dealing with an issue of model misspecification. We consider a Bayesian framework and study the asymptotic limit of posterior distributions over the drift function. In this setting, we show on the one hand that if the continuous multiscale data are not pre-processed, then the posterior distribution concentrates asymptotically on the wrong value of the drift function. On the other hand, we show that data can be treated ahead of the inference procedure in order to obtain the desired posterior. In particular, we prove that there exists a family of transformations which are linear on the space of continuous sample paths and which, when applied to multiscale data, allow the posterior distribution to be asymptotically correct. We present a series of numerical examples on test cases which corroborate our theoretical findings.

\textbf{AMS subject classifications.}

\textbf{Keywords.}

\section{Introduction}

\corr{Add motivating introduction.}
In \cite{PaS07} (\corr{is there other literature?}), the authors prove that inference of the parameters of a homogenized model has to be performed carefully. In this work, the analysis contained in \cite{PaS07} is widened with respect to the following aspects:
\begin{enumerate}[label=\arabic*)]
	\item a more general form of the drift function is considered, thus allowing a more flexible framework for applications and hinting possible extensions to the infinite-dimensional case,
	\item the inference procedure is reinterpreted from a Bayesian perspective, which guarantees more complete uncertainty quantification on the inference result. Moreover, given the nature of the problem, posterior distributions follow a Gaussian law which can be analytically determined, thus guaranteeing computationally fast inference,
	\item we extend the sub-sampling technique introduced in \cite{PaS07}, which can be applied to discrete sequences, by introducing theoretical tools which allow the treatment of continuous streams of data.
\end{enumerate}

Let $\epl > 0$ and let us consider the one-dimensional multiscale stochastic differential equation (SDE)
\begin{equation}\label{eq:SDE_MS}
	\d X_t^\epl = -V'(X_t^\epl) \dd t - \frac1\epl p'\left(\frac{X_t^\epl}\epl\right) + \sqrt{2\sigma} \dd W_t,
\end{equation}
where $\sigma > 0$ and $W_t$ is a standard one-dimensional Brownian motion. The functions $V, p\colon \R \to \R$ are slow and fast potentials driving the dynamics of the solution $X_t^\epl$. Given $N \in \N_{>0}$, we assume the slow potential to be of the form
\begin{equation}
	V(x) = \sum_{i=1}^N \alpha_i V_i(x),
\end{equation}
for coefficients $\alpha_i \in \R$, $i = 1, \ldots, N$, and smooth functions $V_i\colon \R \to \R$. Moreover, we assume $p$ to be smooth and periodic of period $L$. Theory of homogenization \cite{BLP78} guarantees the existence of an SDE of the form
\begin{equation}\label{eq:SDE_HOM}
	\d X_t^0 = - K V'(X) \dd t + \sqrt{2K\sigma} \dd W_t,
\end{equation}
where $W_t$ is the same Brownian motion and where the fast dynamics have been eliminated, such that $X_t^\epl \to X_t^0$ for $\epl\to 0$ in law as random variables in $\mathcal C^0((0, T), \R)$. In the following, we will denote $A_i \defeq K\alpha_i$. The coefficient $K$ is given by the formula
\begin{equation}\label{eq:K_HOM}
	K = \int_0^L (1 + \Phi'(y))^2 \, \mu(\d y),
\end{equation}
with 
\begin{equation}
	\mu(\d y) = Z^{-1} e^{-p(y)/\sigma} \dd y, \quad\text{where}\quad Z = \int_0^L e^{-p(y)/\sigma} \dd y,
\end{equation}
and where the function $\Phi$ is the solution of the elliptic partial differential equation
\begin{equation}
	-p'(y)\Phi'(y) + \sigma \Phi''(y) = p'(y), \quad 0 \leq y \leq L,
\end{equation}
endowed with periodic boundary conditions.

\section{Posterior formal computations}

Let us denote by $A \in \R^N$ the vector of the coefficients $A_i \defeq K \alpha_i$ appearing in the drift term of the homogenized SDE \eqref{eq:SDE_HOM}. In a Bayesian setting, our goal is to determine the posterior distribution $\mu(A \mid X_{0:T})$ given a continuous trajectory $X_{0:T} \defeq (X_t, 0 \leq t \leq T)$. Choosing a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$ on $A$, where $A_0 \in \R^N$ and $C_0 \in \R^{N\times N}$ is symmetric positive definite, the posterior distribution admits a density $p(A \mid X_{0:T})$ with respect to the Lebesgue measure which satisfies
\begin{equation}
	p(A \mid X_{0:T}) = \frac1Z \, p(X_{0:T} \mid A) \, p_0(A),
\end{equation}
where $Z$ is the normalization constant, $p_0$ is the density of $\mu_0$, and where Girsanov's formula allows to write the likelihood as
\begin{equation}
	p(X_{0:T} \mid A) = \exp\left\{-\int_0^T \langle A, \mathbf V'(X_t)\rangle \dd X_t - \frac12 \int_0^T \langle A, \mathbf V'(X_t) \rangle^2 \dd t \right\}.
\end{equation}
In the formula above, we denote by $\mathbf V \colon \R \to \R^N$ the vector-valued function whose $i$-th component is $\mathbf V_i = V_i$, and by $\mathbf V'$ the vector of its derivatives, i.e., the Jacobian matrix. Moreover, we denote by $\langle \cdot, \cdot \rangle$ the Euclidean scalar product in $\R^N$ and by $\norm{\cdot}_2$ the corresponding norm. The log-posterior density is then given by
\begin{equation}
\begin{aligned}
	\log p(A \mid X_{0:T}) = &-\log Z -\int_0^T \langle A, \mathbf V'(X_t)\rangle \dd X_t - \frac12 \int_0^T \langle A, \mathbf V'(X_t) \rangle^2 \dd t \\
	&- \frac12 \norm{C_0^{-1/2}(A - A_0)}_2^2.
\end{aligned}
\end{equation}
Since the log-posterior density is quadratic in $A$, the posterior is Gaussian, and it is therefore sufficient to determine its mean and covariance to fully characterize it. We denote by $m_T$ and $C_T$ the mean and covariance matrix, respectively. Let us consider the matrix-valued function $M \colon \R \to \R^{N\times N}$ whose entries are given by
\begin{equation}
	M_{ij} = \frac1T \int_0^T V_i'(X_t) \, V_j'(X_t) \dd t, \quad i, j = 1, \ldots, N,
\end{equation}
and the vector-valued function $h \colon \R \to \R^N$ defined by
\begin{equation}
	h_i = \frac1T \int_0^T V_i'(X_t) \dd X_t, \quad i = 1, \ldots, N.
\end{equation}
If we employ this notation, we can rewrite the log-posterior density as
\begin{equation}
\begin{aligned}
	\log p(A \mid X_{0:T}) = &-\log Z - T\langle A, h\rangle - \frac{T}{2} \langle A, M A\rangle - \frac12 \langle A - A_0, C_0^{-1}(A-A_0) \rangle.
\end{aligned}
\end{equation}
Completing the squares in the log-posterior density, it is possible to show that the posterior is a Gaussian $\mu(A \mid X_{0:T}) = \mathcal N(\bar A_T, C_T)$, whose precision matrix and mean are formally given by
\begin{equation}
\begin{aligned}
	C_T^{-1} &= C_0^{-1} + T M, \\
	C_T^{-1}\bar A_T &= C_0^{-1}A_0 - T h. 
\end{aligned}
\end{equation}
We are now interested in the limit of the posterior distribution for $T \to \infty$. Let us first define the maximum likelihood estimator (MLE) $\widehat A(X_{0:T})$ of $A$, which is obtained by maximizing the log-likelihood function $\log p(X_{0:T} \mid A)$, and which is hence formally given by
\begin{equation}
	\widehat A(X_{0:T}) = -M^{-1}h.
\end{equation}
We now introduce regularity assumptions on the SDE.
\begin{assumption}\label{as:regularity} The potentials $p$ and $V$ are such that 
	\begin{enumerate}
		\item for all $T > 0$, the symmetric matrix $M$ is positive definite and its minimum eigenvalue satisfies $\lambda_{\min}(M) \geq \bar \lambda > 0$,
		\item 	\corr{other assumptions to be added}
	\end{enumerate}
\end{assumption}

We can now state the main result for asymptotic convergence of the posterior distribution.
\begin{proposition}\label{prop:equiv} Given a continuous stochastic process $X_t$ which is ergodic with invariant measure $\mu^{\infty}$ such that $\E^{\mu^\infty}(V_i'(\cdot)) \leq C$ for some constant $C > 0$ and for all $i = 1, \ldots, N$, the posterior $\mu(A \mid X_{0:T})$ contracts to the limit of $\widehat A(X_{0:T})$ for $T \to \infty$.
%	 for $T$ arbitrarily large and under Assumption \ref{as:regularity}, the posterior mean and covariance satisfy
%	\begin{equation}
%	\begin{aligned}
%		&\lim_{T \to \infty} \norm{m_T - \widehat A(X_{0:T})}_2 = 0, \\
%		&\lim_{T \to \infty} \norm{C_T}_F = 0,
%	\end{aligned}
%	\end{equation}
%	i.e., the posterior tends in distribution to the Dirac delta centred in the limit of the MLE.
\end{proposition}
\begin{proof} Let us first consider the covariance matrix. Hua's identity yields
	\begin{equation}
		C_T = T^{-1} \left(M^{-1} - Q^{-1}\right),
	\end{equation}
	where 
	\begin{equation}
		Q = M + T M C_0 M.
	\end{equation}
	The eigenvalues of $Q$ satisfy for all $i = 1, \ldots, N$
	\begin{equation}
		\lambda_i(Q) = \lambda_i(M) + T \lambda_i(M C_0 M) \geq \bar \lambda + T \lambda_{\min}(C_0),
	\end{equation}
	and therefore we obtain
	\begin{equation}\label{eq:boundQinv}
		\lambda_{\max}(Q^{-1}) \leq \frac{1}{\bar \lambda + T \lambda_{\min}(C_0)}.
	\end{equation}
	Similarly, we have a bound for the maximum eigenvalue of $M^{-1}$ given by
	\begin{equation}\label{eq:boundMinv}
		\lambda_{\max}(M^{-1}) \leq \frac1{\bar{\lambda}},
	\end{equation}
	which implies that
	\begin{equation}
		\trace{C_T} \leq \frac{N}{T} \left(\frac1{\bar{\lambda}} + \frac{1}{\bar \lambda + T \lambda_{\min}(C_0)}\right),
	\end{equation}
	and which therefore allows us to conclude that
	\begin{equation}
		\lim_{T\to\infty} \norm{C_T}_F = 0.
	\end{equation}
	We now consider the mean. Replacing the expression of the maximum likelihood estimator, we obtain
	\begin{equation}
		\norm{m_T - \widehat A(X_{0:T})}_2 = T^{-1}\norm{M^{-1}C_0^{-1}A_0 - Q^{-1}\left(C_0^{-1}A_0 -h \right)}_2.
	\end{equation}
	Let us remark that \eqref{eq:boundQinv} implies $\norm{Q^{-1}}_F \to 0$ for $T \to \infty$ and \eqref{eq:boundMinv} implies $\norm{M^{-1}}_F \leq C$ for some $C > 0$ independently of $T$. Moreover, the ergodic theorem guarantees that $\norm{h}_2 \leq C$ for $T$ sufficiently big, and therefore the Cauchy--Schwarz and the triangle inequalities imply 
	\begin{equation}
		\lim_{T\to\infty} \norm{m_T - \widehat A(X_{0:T})}_2 = 0,
	\end{equation}
	which proves the desired result.
\end{proof}

\begin{remark} Proposition \ref{prop:equiv} guarantees that in the asymptotic limit of $T \to \infty$, it is equivalent to consider the Bayesian approach and the maximum likelihood approach, and can therefore be interpreted as a consistency result for both approaches. Nonetheless, in this Gaussian framework the Bayesian approach provides richer information on the inference result with a negligible additional cost.
\end{remark}

\section{The one-dimensional case}

Let us consider $N = 1$ and write $A_1 = A$ and $V_1 = V$, respectively. The posterior distribution of $A$ given a trajectory $(X_t, 0 \leq t \leq T)$ is in this case a Gaussian $\mathcal N(\bar A_T, \sigma^2_T)$ where
\begin{equation}
\begin{aligned}
	\bar A_T &= \frac{A_0}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t} - \frac{\sigma_0^2\int_0^T  V'(X_t) \dd X_t}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t}, \\
	\sigma^{-2}_T &= \sigma_0^{-2} + \int_0^T V'(X_t)^2 \dd t.
\end{aligned}
\end{equation}
We will in the following sections analyse the convergence of the posterior, both in case data from the multiscale process is not treated and in case they are pre-processed.

\subsection{Failure without pre-processing}

Let us consider a trajectory $X_{0:T}^\epl \defeq (X_t^\epl, 0 \leq t \leq T)$ coming from the multiscale equation \eqref{eq:SDE_MS}, and the corresponding posterior distribution over the parameter $A$, which we denote by $\mu^\epl(A \mid X_{0:T}^\epl)$. The following result holds.
\begin{theorem} Under assumption \ref{as:regularity} and if $T = \epl^{-\gamma}$ for $\gamma > 0$, then the posterior distribution $\mu^\epl(A \mid X_{0:T}^\epl) = \mathcal N(\bar A^\epl_T,  \sigma^2_T)$ satisfies
	\begin{equation}
	\begin{aligned}
		&\lim_{\epl \to 0} \bar A^\epl_T = \alpha, \\
		&\lim_{\epl \to 0} \sigma^2_T = 0.
	\end{aligned}
	\end{equation}
\end{theorem}
\begin{proof} Proposition \ref{prop:equiv} guarantees that 
	\begin{equation}
		\lim_{\epl \to 0} \abs{\bar A_T - \hat A(X^\epl_{0:T})} = 0,
	\end{equation}
	and that $\sigma^2_T \to 0$ for $\epl \to 0$. Moreover, \cite[Theorem 3.4]{PaS07} yields
	\begin{equation}
		\lim_{\epl \to 0} \hat A(X^\epl_{0:T}) = \alpha,
	\end{equation}
	which completes the proof.
\end{proof}

The result above implies that the posterior distribution over the drift coefficient concentrates asymptotically on an undesired value.

\subsection{A filtering approach}

In the previous section, we have shown that posterior distributions over the drift coefficient of the homogenized equation are asymptotically incorrect if multiscale data are replaced into the expression of the likelihood. Hence, the need of pre-processing the data is highlighted. In particular, we consider a filtering approach. Let $k \colon \R^+ \times \R^+ \to \R$ be a kernel function and consider the process $Z^\epl \defeq (Z^{\epl,k}_t, 0 \leq t \leq T)$ defined by the weighted average
\begin{equation}\label{eq:ZDef}
	Z^{\epl,k}_t \defeq \int_0^t k^\epl(t, s)X^\epl_s \dd s.
\end{equation}
Let $\beta, \delta > 0$ and let us consider a family of exponential kernel functions defined as
\begin{equation}
	k^\epl(t, s) = C_\beta \delta^{-1/\beta} e^{-(t-s)^\beta/\delta},
\end{equation}
where $C_{\beta}$ is a normalizing constant given by
\begin{equation}
	C_\beta = \beta \, \Gamma(1/\beta)^{-1},
\end{equation}
and where $\Gamma(\cdot)$ is the gamma function. In the following, only in case $\beta = 1$ a rigorous analysis is carried on. Nonetheless, numerical experiments show that for higher values of $\beta$ the performances of estimators computed employing the filter are more robust and qualitatively better.

\corr{Implementation}

\subsection{Ergodic properties of the filter}\label{sec:ergodic}

In the following, we consider the filter with $\beta = 1$, i.e.,
\begin{equation}
	k(t,s) = \frac{1}{\delta} e^{-\frac{t-s}{\delta}},
\end{equation}
since in this case it holds
\begin{equation}
	\d Z^\epl_t = k(t,t) X^\epl_t \dd t + \int_0^t \partial_t k(t,s) X^\epl_s \dd s \dd t = \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
\end{equation}
Considering the processes $X^\epl$ and $Z^\epl$ together, we obtain a system of stochastic differential equations
\begin{equation}
\label{systemSDE}
\begin{aligned}
\d X^\epl_t &= \left ( - \alpha V'(X^\epl_t) - \frac{1}\epl p' \left ( \frac{X^\epl_t}\epl \right ) \right ) \dd t + \sqrt{2\sigma} \dd W_t, \\
\d Z^\epl_t &= \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
\end{aligned}
\end{equation}
Let $\rho^\epl = \rho^\epl(x,z)$ be the stationary distribution of the joint process $(X^\epl, Z^\epl)^\top$. Then $\rho^\epl$ is the solution of the two-dimensional stationary Fokker--Planck equation
\begin{equation}
\begin{aligned}
	\label{eq:FPsystem}
	\sigma \partial^2_{xx} \rho^\epl(x,z) & + \left ( \alpha V''(x) + \frac{1}{\epl^2} p'' \left ( \frac{x}\epl \right ) + \frac{1}{\delta} \right ) \rho^\epl(x,z) \\
	& + \left ( \alpha V'(x) + \frac{1}\epl p' \left ( \frac{x}\epl \right ) \right ) \partial_x \rho^\epl(x,z) + \frac{1}{\delta}(z - x) \partial_z \rho^\epl(x,z) = 0.
\end{aligned}
\end{equation}

\begin{example}\label{ex:OrnUhl} A closed form solution of \eqref{eq:FPsystem} can be obtained in a simple homogenized case. Let $p(y) = 0$ and the parameters $\alpha$, $\sigma$ be replaced respectively by $A$ and $\Sigma$. Then, if $V(x) = x^2/2$, equation \eqref{eq:FPsystem} has the analytical solution 
\begin{equation}
\rho^0(x,z) = \frac{1}{A_{\rho^0}} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right),
\end{equation}
where
\begin{equation}
A_{\rho^0} = \int_{\R} \int_{\R} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right) \dd x \dd z.
\end{equation}
This is the density of a multivariate normal distribution $\mathcal N(0, \Gamma)$, where the covariance matrix is given by
\begin{equation}
\Gamma = \frac{\Sigma}{A (1 + A\delta)} \begin{pmatrix} 1+A\delta & 1 \\ 1 & 1 \end{pmatrix}.
\end{equation}
Let us remark that this distribution can be obtained from direct computations involving Gaussian processes. In particular, it is known that $X_t \sim \mathcal{GP}(\mu_t, \mathcal C(t, s))$, where 
\begin{equation}
	\mu_t = X_0 e^{-At}, \quad \mathcal C(t, s) = \frac{\Sigma}{A} \left( e^{-A|t-s|} - e^{-A(t+s)} \right).
\end{equation}
The basic properties of Gaussian processes imply that $Z_t$ is a Gaussian process, and that the couple $(X_t, Z_t)^\top$ is a Gaussian process, too, whose mean and covariance are computable explicitly.
\end{example}

In a general case, it is not possible to find an explicit solution to \eqref{eq:FPsystem}. Nevertheless, it is possible to show some relevant properties of the solution itself, which are summarized in the following Lemma.

\begin{lemma}\label{lem:FPMarginal} Let $\rho^\epl$ be the \corr{unique solution} of \eqref{eq:FPsystem} and let us write 
\begin{equation}\label{eq:densityDecomposition}
	\rho^\epl(x, z) = \phi^\epl(z)\psi^\epl(z)R^\epl(x,z),
\end{equation}
where $\phi^\epl$ and $\psi^\epl$ are the marginal densities, i.e., 
\begin{equation}
	\phi^\epl(x) = \int_{\R} \rho^\epl(x,z) \dd z, \quad  \psi^\epl(z) = \int_{\R} \rho^\epl(x,z) \dd x.
\end{equation}
Then, it holds
\begin{equation}\label{eq:marginalX}
	\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(- \frac{\alpha}{\sigma} V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
\end{equation}
where
\begin{equation}
	C_{\phi^\epl} = \int_{\R} \exp\left(- \frac{\alpha}{\sigma} V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right) \dd x.
\end{equation}
Moreover, it holds
\begin{equation}
	\sigma \delta \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)].
\end{equation}
\end{lemma}

\begin{proof} Integrating equation \eqref{eq:FPsystem} with respect to $z$ we obtain the stationary Fokker--Planck equation for the process $X^\epl$, i.e.
\begin{equation}
\label{FPx}
\sigma (\phi^\epl)''(x) + \left ( \alpha V''(x) + \frac{1}{\epl^2} p'' \left ( \frac{x}\epl \right ) \right ) \phi^\epl(x) + \left ( \alpha V'(x) + \frac{1}\epl p' \left ( \frac{x}\epl \right ) \right ) (\phi^\epl)'(x) = 0,
\end{equation}
whose solution is given by
\begin{equation}
\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(- \frac{\alpha}{\sigma} V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
\end{equation}
and which proves \eqref{eq:marginalX}. By integrating equation \eqref{eq:FPsystem} with respect to $x$ and integrating by parts we obtain
\begin{equation}
\psi^\epl(z) + z (\psi^\epl)'(z) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x,
\end{equation}
which can be written as
\begin{equation}
	\frac{\d}{\d z} (z \psi^\epl(z)) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x.
\end{equation}
Now, since $\psi^\epl$ is the density of a probability distribution, this implies that 
\begin{equation}\label{FPz}
z \psi^\epl(z) = \int_{\R} x \rho^\epl(x,z) \dd x,
\end{equation}
which, replacing the decomposition \eqref{eq:densityDecomposition}, yields
\begin{equation} \label{eq:z_condition}
z = \int_{\R} x \phi^\epl(x) R^\epl(x,z) \dd x.
\end{equation}
Replacing the decomposition \eqref{eq:densityDecomposition} in equation \eqref{eq:FPsystem} and using equation \eqref{FPx} we obtain the following equality
\begin{equation}\label{eq:psiEqualityPDE}
\sigma \phi^\epl \psi^\epl \partial^2_{xx} R^\epl + \frac{1}{\delta} \phi^\epl \psi^\epl R^\epl + \sigma (\phi^\epl)' \psi^\epl \partial_x R^\epl + \frac{1}{\delta} (z-x) \phi^\epl ((\psi^\epl)' R + \psi^\epl \partial_z R^\epl) = 0.
\end{equation}
We now multiply the equation above by $x$ and integrate with respect to $x$. Let us consider some simplifications explicitly. First, an integration by parts yields
\begin{equation}\label{eq:psiEqualityPDE_1}
\begin{aligned}
	\sigma \psi^\epl \int_{\R}  x \phi^\epl \partial^2_{xx} R^\epl \dd x+ \sigma \psi^\epl \int_{\R} x (\phi^\epl)' \partial_x R^\epl \dd x &= -\sigma \psi^\epl \int_{\R} \phi^\epl \partial_x R^\epl \dd x.
\end{aligned}
\end{equation}
Then, applying \eqref{eq:z_condition}, we have
\begin{equation}\label{eq:psiEqualityPDE_2}
	\frac1\delta \psi^\epl \int_{\R} x \phi^\epl  R^\epl \dd x = \frac1\delta z \psi^\epl.
\end{equation}
Moreover, again applying \eqref{eq:z_condition}, we can compute
\begin{equation}\label{eq:psiEqualityPDE_3}
\begin{aligned}
	\frac1\delta (\psi^\epl)' \int_\R (z-x)x \phi^\epl  R \dd x = \frac1\delta (\psi^\epl)' \left(z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x\right).
\end{aligned}
\end{equation}
Finally, we compute the last term always applying \eqref{eq:z_condition} obtaining
\begin{equation}\label{eq:psiEqualityPDE_4}
	\frac1\delta \psi^\epl \int_\R (z-x)x \phi^\epl \partial_z R \dd x = \frac1\delta \psi^\epl\left(z - \int_{\R} x^2 \phi^\epl \partial_z R^\epl \dd x\right).
\end{equation}
Replacing the equalities \eqref{eq:psiEqualityPDE_1}, \eqref{eq:psiEqualityPDE_2}, \eqref{eq:psiEqualityPDE_3} and \eqref{eq:psiEqualityPDE_4} into \eqref{eq:psiEqualityPDE} we obtain
\begin{equation}
(\psi^\epl)' \left ( z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x \right ) + \psi^\epl \left ( 2z - \int_{\R} x^2 \phi^\epl \partial_z R^\epl \dd x - \delta \sigma \int_{\R} \phi^\epl \partial_x R^\epl \dd x \right ) = 0.
\end{equation}
We rewrite the equality above as
\begin{equation} \label{eq:psiEquality}
\delta \sigma \psi^\epl(z) \int_{\R} \phi^\epl(x) \partial_x R^\epl(x, z) \dd x = 
\begin{aligned}[t] &(\psi^\epl)'(z) z^2 - (\psi^\epl)'(z) \int_{\R} x^2 \phi^\epl(x) R^\epl(x, z) \dd x \\
& + 2 \psi^\epl(x) z - \psi^\epl \int_{\R} x^2 \phi^\epl(x) \partial_z R^\epl(x, z) \dd x.
\end{aligned}
\end{equation}
Multiplying by $V'(z)$, integrating with respect to $z$ and integrating by parts, we obtain
\begin{equation}
\begin{aligned}
\sigma \delta \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z &=  \int_{\R} \int_{\R} (x^2 - z^2) V''(z) \rho_\epl(x,z) \dd x \dd z \\
&= \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)],
\end{aligned}
\end{equation}
which is the desired result.
\end{proof}

\begin{remark} It could be possible to find a closed-form solution to \eqref{eq:FPsystem} in a more general framework than Example \ref{ex:OrnUhl}. Nonetheless, an explicit solution is not necessary for our argument.
\end{remark}

\subsubsection{Convergence of the invariant measure}\label{sec:convMeasure}

It is known that the invariant distribution of the process $X^\epl$ converges weakly to the invariant distribution of the process $X^0$ solution to \eqref{eq:SDE_HOM}. We now consider the random variable $(X^\epl, Z^\epl)^\top$ and present an analogous convergence result for the couple.

\begin{lemma}\label{lem:convMeasure} Let $\mu^\epl$ be the invariant measure of the couple $(X^\epl, Z^\epl)^\top$. Then, the measure $\mu^\epl$ converges weakly to the measure $\mu^0(\d x, \d z) = \rho^0(x, z) \dd x \dd z$, whose density $\rho^0$ is the unique solution of the Fokker--Planck equation
\begin{equation} \label{eq:FPsystem_homogenized}
	\Sigma \partial^2_{xx} \rho^0(x,z) + \left ( A V''(x) + \frac{1}{\delta} \right ) \rho^0(x,z) + A V'(x) \partial_x \rho^0(x,z) + \frac{1}{\delta}(z - x) \partial_z \rho^0(x,z) = 0,
\end{equation}
where $A$ and $\Sigma$ are the coefficients of the homogenized equation \eqref{eq:SDE_HOM}.
\end{lemma}
\begin{proof} 
\end{proof}

We now present an analogous result to Lemma \ref{lem:FPMarginal} for the limit distribution.

\begin{corollary}\label{lem:FPMarginal_Hom} Let $\rho^0$ be the \corr{unique solution} of \eqref{eq:FPsystem_homogenized} and let us write 
	\begin{equation}
		\rho^0(x, z) = \phi^0(z)\psi^0(z)R^0(x,z),
	\end{equation}
	where $\phi^0$ and $\psi^0$ are the marginal densities, i.e., 
	\begin{equation}
		\phi^0(x) = \int_{\R} \rho^0(x,z) \dd z, \quad \psi^0(z) = \int_{\R} \rho^0(x,z) \dd x.
	\end{equation}
	Then, if $A$ and $\Sigma$ are the coefficients of the homogenized equation \eqref{eq:SDE_HOM}, it holds
	\begin{equation}
		\phi^0(x) = \frac{1}{C_{\phi^0}} \exp\left(- \frac{A}{\Sigma} V(x)\right), \quad \text{where } \quad C_{\phi^0} = \int_{\R} \exp\left(- \frac{A}{\Sigma} V(x) \right) \dd x.
	\end{equation}
	Moreover, it holds
	\begin{equation}
		\Sigma \delta \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z = \E^{\rho^0}[((X^0)^2 - (Z^0)^2)V''(Z^0)].
	\end{equation}
\end{corollary}
\begin{proof} The proof is directly obtained from Lemma \ref{lem:FPMarginal} replacing $p(y)=0$ and $\alpha, \sigma$ by $A, \Sigma$ respectively. 
\end{proof}

\subsection{The estimator}

The estimator of the homogenized drift coefficient $A$ we analyse is given by the formula
\begin{equation}\label{eq:AHatMixed}
\widehat A^\epl(T) = - \frac{\int_0^T V'(Z^\epl_t) \dd X^\epl_t}{\int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t}.
\end{equation}

\begin{theorem}\label{thm:mainTheorem} Let $\widehat A^\epl(T)$ be defined in \eqref{eq:AHatMixed}. Then, if \corr{Assumptions}, 
	\begin{equation}\label{eq:theoremFirst}
	\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A^\epl(T) = A, \quad \text{a.s.},
	\end{equation}
	where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}. Moreover, the following central limit theorem holds
	\begin{equation}\label{eq:theoremSecond}
	\lim_{\epl \to 0} \lim_{T \to \infty} \sqrt{T} \left(A - \widehat A^\epl(T) \right) = \Lambda, \quad \text{in law}, 
	\end{equation}
	where $\Lambda \sim \mathcal N(0, \gamma^2)$ and where 
	\begin{equation}
	\gamma = \sqrt{2\sigma} \frac{\sqrt{\E^{\rho^0}[V'(Z)^2]}}{\E^{\rho^0}[V'(Z)V'(X)]}.
	\end{equation}
\end{theorem}

\begin{proof} Replacing the expression of $\d X^\epl_t$ into \eqref{eq:AHatMixed}, we get
\begin{equation}\label{Ahat_decomposition}
\begin{aligned} \nonumber
\widehat A^\epl(T) &= \frac{\alpha \int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t + \int_0^T V'(Z^\epl_t) \frac1\epl  p' \left ( \frac{X^\epl_t}\epl \right )\dd t - \sqrt{2\sigma} \int_0^T V'(Z^\epl_t) \dd W_t}{\int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t} \\ 
&= \alpha + \frac{\int_0^T V'(Z^\epl_t) \frac1\epl  p' \left ( \frac{X^\epl_t}\epl \right )\dd t}{\int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t} - \sqrt{2\sigma} \frac{\int_0^T V'(Z^\epl_t) \dd W_t}{\int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t}\\
&\eqdef \alpha + I_1^\epl(T) - I_2^\epl(T).
\end{aligned}
\end{equation}
We study the terms $I_1^\epl$ and $I_2^\epl$ separately. The ergodic theorem applied to $I_1^\epl$ yields
\begin{equation}\label{limit_estimator}
\lim_{T \to \infty} I_1^\epl(T) = \frac{\E^{\rho^\epl} \left [ \frac{1}\epl V'(Z^\epl) p' \left ( \frac{X^\epl}\epl \right ) \right ]}{\E^{\rho^\epl} [ V'(Z^\epl) V'(X^\epl) ]}, \quad \text{a.s.}
\end{equation}
Let us consider the numerator of the expression above. Due to Lemma \ref{lem:FPMarginal} and integrating by parts, we have
\begin{equation}
\begin{aligned}
	\E^{\rho^\epl} \left [ V'(Z^\epl) \frac1\epl p' \left ( \frac{X^\epl}\epl \right ) \right ] &= \int_{\R} \int_{\R} V'(z) \, \frac1\epl p' \left ( \frac{x}\epl \right ) \frac{1}{C_{\phi^\epl}} e^{- \frac{\alpha}{\sigma} V(x)} e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \psi^\epl(z) R^\epl(x,z) \dd x \dd z \\
	&= -\sigma \int_{\R} \int_{\R} \frac{\d}{\d x}\left( e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \right) \frac{1}{C_{\phi^\epl}} e^{- \frac{\alpha}{\sigma} V(x)} V'(z) \psi^\epl(z) R^\epl(x,z) \dd x \dd z \\
	&= \sigma \int_{\R} \int_{\R} \frac{1}{C_{\phi^\epl}} e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \partial_x \left ( e^{- \frac{\alpha}{\sigma} V(x)} R^\epl(x,z) \right ) V'(z) \psi^\epl(z) \dd x \dd z,
\end{aligned}
\end{equation}
which implies
\begin{align}
	\E^{\rho^\epl} \left [ \frac{1}\epl V'(Z^\epl) p' \left ( \frac{X^\epl}\epl \right ) \right ] &= 
	\begin{aligned}[t]
		&-\alpha \int_{\R} \int_{\R} V'(x) V'(z) \rho^\epl(x, z) \dd x \dd z \\
		&+\sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z 
	\end{aligned}
	\\
	&= - \alpha \E^{\rho^\epl} [ V'(Z^\epl) V'(X^\epl) ] + \sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z.
\end{align}
Replacing the equality above into \eqref{limit_estimator}, we obtain
\begin{equation}
\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac{\sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z}{\E^{\rho^\epl} [ V'(Z^\epl) V'(X^\epl) ]}, \quad \text{a.s.}
\end{equation}
Due to Lemma \ref{lem:FPMarginal}, we therefore have
\begin{equation}
	\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac{\E^{\rho^\epl}[(X^2 - Z^2)V''(Z)]}{\delta \E^{\rho^\epl}[V'(Z) V'(X)]}, \quad \text{a.s.}	
\end{equation}
We now pass to the limit as $\epl$ goes to zero and
\begin{equation} \label{limit_estimator_2}
	\lim_{\epl \to 0} \lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac{\E^{\rho^0}[(X^2 - Z^2)V''(Z)]}{\delta \E^{\rho^0}[V'(Z) V'(X)]}, \quad \text{a.s.},
\end{equation}
where the function $\rho^0$ is the density of the limit invariant distribution for $\epl \to 0$, as in Lemma \ref{lem:convMeasure}. Due to Lemma \ref{lem:FPMarginal_Hom}, we have
\begin{equation}\label{eq:final_result}
\frac{1}{\delta} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] = \Sigma \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z,
\end{equation}
and finally, an integration by parts yields
\begin{align}
	\E^{\rho^0}[V'(Z) V'(X)] &= \int_{\R} \int_{\R} V'(x) V'(z) \frac{1}{C_{\phi^0}} e^{-\frac{A}{\Sigma} V(x)} \psi^0(z) R^0(x,z) \dd x \dd z \\
	&= - \frac{\Sigma}{A} \int_{\R} \int_{\R} V'(z) \left ( \frac{1}{C_{\phi^0}} e^{-\frac{A}{\Sigma} V(x)} \right )' \psi^0(z) R^0(x,z) \dd x \dd z \\
	&= \frac{\Sigma}{A} \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z.
\end{align}
We can therefore conclude that
\begin{equation}\label{eq:Proof_I1}
\lim_{\epl \to 0} \lim_{T \to \infty} I_1(T) = -\alpha + A, \quad \text{a.s.}
\end{equation}
We now consider the second term $I_2$, and rewrite it as 
\begin{equation}
	I^\epl_2(T) = - \sqrt{2\sigma} \frac{\frac1T\int_0^T V'(Z^\epl_t)^2 \dd t}{\frac1T\int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t} \frac{\int_0^T V'(Z^\epl_t) \dd W_t}{\int_0^T V'(Z^\epl_t)^2 \dd t} \eqdef -\sqrt{2\sigma} I_{2,1}^\epl(T)  I_{2,2}^\epl(T).
\end{equation}
The ergodic theorem yields
\begin{equation}
	\lim_{T \to \infty} I_{2,1}^\epl(T) = \frac{\E^{\rho^\epl}[V'(Z^\epl)^2]}{\E^{\rho^\epl}[V'(Z^\epl)V'(X^\epl)]} \eqdef M^\epl,
\end{equation}
where $M^\epl$ is bounded uniformly in $\epl$. Moreover, \corr{the strong law of large numbers for martingales implies}
\begin{equation}
	\lim_{T \to \infty} I_{2,2}^\epl(T) = 0, \quad \text{a.s.},
\end{equation}
independently of $\epl$. Therefore
\begin{equation}
	\lim_{\epl \to 0}\lim_{T \to \infty} I_2^\epl(T) = 0, \quad \text{a.s.},
\end{equation}
which, together with \eqref{eq:Proof_I1}, proves \eqref{eq:theoremFirst}. 
\end{proof}

\section{Numerical experiments}

\bibliographystyle{siam}
\bibliography{../../anmc}
\end{document}

### 2020-01-20 CalNotes.tex
Culo
multidim

@@
 \begin{equation}\label{eq:ZDef}
-	Z^{\epl,k}_t \defeq \int_0^t k^\epl(t, s)X^\epl_s \dd s.
+	Z^{\epl,k}_t \defeq \int_0^t k^\epl(t-s)X^\epl_s \dd s.
 \end{equation}
@@
 \begin{equation}
-	k^\epl(t, s) = C_\beta \delta^{-1/\beta} e^{-(t-s)^\beta/\delta},
+	k^\epl(t-s) = C_\beta \delta^{-1/\beta} e^{-(t-s)^\beta/\delta},
 \end{equation}
@@
 
-\corr{Implementation}
+Given a trajectory $X^\epl \defeq (X^\epl_t, 0\leq t \leq T)$, it is relatively inexpensive to compute $Z^\epl$ from a computational standpoint.
+In particular, the process $Z^\epl$ is the convolution of the kernel with the process $X^\epl$.
+Hence, computational tools based on the Fast Fourier Transform (FFT) exist and allow to compute $Z^\epl$ fast.
 
@@
 \begin{equation}
-	\d Z^\epl_t = k(t,t) X^\epl_t \dd t + \int_0^t \partial_t k(t,s) X^\epl_s \dd s \dd t = \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
+	\d Z^\epl_t = k(0) X^\epl_t \dd t + \int_0^t \partial_t k(t-s) X^\epl_s \dd s \dd t = \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
 \end{equation}
@@
 \begin{aligned}
-\d X^\epl_t &= \left ( - \alpha V'(X^\epl_t) - \frac{1}\epl p' \left ( \frac{X^\epl_t}\epl \right ) \right ) \dd t + \sqrt{2\sigma} \dd W_t, \\
+\d X^\epl_t &= -\left( \alpha \nabla_x V(X^\epl_t) - \frac{1}\epl \nabla_x p \left ( \frac{X^\epl_t}\epl \right ) \right ) \dd t + \sqrt{2\sigma} \dd W_t, \\
 \d Z^\epl_t &= \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
@@
 \end{equation}
-Let $\rho^\epl = \rho^\epl(x,z)$ be the stationary distribution of the joint process $(X^\epl, Z^\epl)^\top$. Then $\rho^\epl$ is the solution of the two-dimensional stationary Fokker--Planck equation
+Let $\rho^\epl = \rho^\epl(x,z)$ be the stationary distribution of the joint process $(X^\epl, Z^\epl)^\top$.
+Then $\rho^\epl$ is the solution of the $2d$-dimensional stationary Fokker--Planck equation
 \begin{equation}
@@
 	\label{eq:FPsystem}
-	\sigma \partial^2_{xx} \rho^\epl(x,z) & + \left ( \alpha V''(x) + \frac{1}{\epl^2} p'' \left ( \frac{x}\epl \right ) + \frac{1}{\delta} \right ) \rho^\epl(x,z) \\
-	& + \left ( \alpha V'(x) + \frac{1}\epl p' \left ( \frac{x}\epl \right ) \right ) \partial_x \rho^\epl(x,z) + \frac{1}{\delta}(z - x) \partial_z \rho^\epl(x,z) = 0.
+	\sigma \Delta_x \rho^\epl(x,z) & + \left ( \alpha  \Delta_x V(x) + \frac{1}{\epl^2} \Delta_x p \left( \frac{x}\epl \right) + \frac1\delta \right) \rho^\epl(x,z) \\
+	& + \left ( \alpha \nabla_x V(x) + \frac{1}\epl \nabla_x p \left ( \frac{x}\epl \right ) \right ) \cdot \nabla_x \rho^\epl(x,z) + \frac{1}{\delta}(z - x) \cdot \nabla_z \rho^\epl(x,z) = 0.
 \end{aligned}
@@
 	\E^{\rho^0}[V'(Z) V'(X)] &= \int_{\R} \int_{\R} V'(x) V'(z) \frac{1}{C_{\phi^0}} e^{-\frac{A}{\Sigma} V(x)} \psi^0(z) R^0(x,z) \dd x \dd z \\
-	&= - \frac{\Sigma}{A} \int_{\R} \int_{\R} V'(z) \left ( \frac{1}{C_{\phi^0}} e^{-\frac{A}{\Sigma} V(x)} \right )' \psi^0(z) R^0(x,z) \dd x \dd z \\
+	&= - \frac{\Sigma}{A} \int_{\R} \int_{\R} V'(z) \frac{\d}{\d x} \left(\frac{1}{C_{\phi^0}} e^{-\frac{A}{\Sigma} V(x)} \right ) \psi^0(z) R^0(x,z) \dd x \dd z \\
 	&= \frac{\Sigma}{A} \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z.

### 2020-01-23 CalNotes.tex
multidim - partial

@@
 endowed with periodic boundary conditions.
+
+\corr{Failure without pre-processing: explain.}
+
+Let us consider a trajectory $X_{0:T}^\epl \defeq (X_t^\epl, 0 \leq t \leq T)$ coming from the multiscale equation \eqref{eq:SDE_MS}, and the corresponding posterior distribution over the parameter $A$, which we denote by $\mu^\epl(A \mid X_{0:T}^\epl)$.
+The following result holds.
+\begin{theorem} Under assumption \ref{as:regularity} and if $T = \epl^{-\gamma}$ for $\gamma > 0$, then the posterior distribution $\mu^\epl(A \mid X_{0:T}^\epl) = \mathcal N(\bar A^\epl_T,  \sigma^2_T)$ satisfies
+	\begin{equation}
+	\begin{aligned}
+	&\lim_{\epl \to 0} \bar A^\epl_T = \alpha, \\
+	&\lim_{\epl \to 0} \sigma^2_T = 0.
+	\end{aligned}
+	\end{equation}
+\end{theorem}
+\begin{proof} Proposition \ref{prop:equiv} guarantees that 
+	\begin{equation}
+	\lim_{\epl \to 0} \abs{\bar A_T - \hat A(X^\epl_{0:T})} = 0,
+	\end{equation}
+	and that $\sigma^2_T \to 0$ for $\epl \to 0$. Moreover, \cite[Theorem 3.4]{PaS07} yields
+	\begin{equation}
+	\lim_{\epl \to 0} \hat A(X^\epl_{0:T}) = \alpha,
+	\end{equation}
+	which completes the proof.
+\end{proof}
+
+The result above implies that the posterior distribution over the drift coefficient concentrates asymptotically on an undesired value.
 
@@
 
-\section{The one-dimensional case}
-
-Let us consider $N = 1$ and write $A_1 = A$ and $V_1 = V$, respectively.
-The posterior distribution of $A$ given a trajectory $(X_t, 0 \leq t \leq T)$ is in this case a Gaussian $\mathcal N(\bar A_T, \sigma^2_T)$ where
-\begin{equation}
-\begin{aligned}
-	\bar A_T &= \frac{A_0}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t} - \frac{\sigma_0^2\int_0^T  V'(X_t) \dd X_t}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t}, \\
-	\sigma^{-2}_T &= \sigma_0^{-2} + \int_0^T V'(X_t)^2 \dd t.
-\end{aligned}
-\end{equation}
-We will in the following sections analyse the convergence of the posterior, both in case data from the multiscale process is not treated and in case they are pre-processed.
-
-\subsection{Failure without pre-processing}
-
-Let us consider a trajectory $X_{0:T}^\epl \defeq (X_t^\epl, 0 \leq t \leq T)$ coming from the multiscale equation \eqref{eq:SDE_MS}, and the corresponding posterior distribution over the parameter $A$, which we denote by $\mu^\epl(A \mid X_{0:T}^\epl)$.
-The following result holds.
-\begin{theorem} Under assumption \ref{as:regularity} and if $T = \epl^{-\gamma}$ for $\gamma > 0$, then the posterior distribution $\mu^\epl(A \mid X_{0:T}^\epl) = \mathcal N(\bar A^\epl_T,  \sigma^2_T)$ satisfies
-	\begin{equation}
-	\begin{aligned}
-		&\lim_{\epl \to 0} \bar A^\epl_T = \alpha, \\
-		&\lim_{\epl \to 0} \sigma^2_T = 0.
-	\end{aligned}
-	\end{equation}
-\end{theorem}
-\begin{proof} Proposition \ref{prop:equiv} guarantees that 
-	\begin{equation}
-		\lim_{\epl \to 0} \abs{\bar A_T - \hat A(X^\epl_{0:T})} = 0,
-	\end{equation}
-	and that $\sigma^2_T \to 0$ for $\epl \to 0$. Moreover, \cite[Theorem 3.4]{PaS07} yields
-	\begin{equation}
-		\lim_{\epl \to 0} \hat A(X^\epl_{0:T}) = \alpha,
-	\end{equation}
-	which completes the proof.
-\end{proof}
-
-The result above implies that the posterior distribution over the drift coefficient concentrates asymptotically on an undesired value.
-
-\subsection{A filtering approach}
+\section{A filtering approach}
 
@@
 \begin{equation}\label{eq:ZDef}
-	Z^{\epl,k}_t \defeq \int_0^t k^\epl(t-s)X^\epl_s \dd s.
+	Z^{\epl,k}_t \defeq \int_0^t k^\epl(t-s)X^\epl_s \dd s,
 \end{equation}
-Let $\beta, \delta > 0$ and let us consider a family of exponential kernel functions defined as
+where the equality is component-wise in $\R^d$. Let $\beta, \delta > 0$ and let us consider a family of exponential kernel functions defined as
 \begin{equation}
@@
 In particular, the process $Z^\epl$ is the convolution of the kernel with the process $X^\epl$.
-Hence, computational tools based on the Fast Fourier Transform (FFT) exist and allow to compute $Z^\epl$ fast.
+Hence, computational tools based on the Fast Fourier Transform (FFT) exist and allow to compute $Z^\epl$ fast component-wise.
 
@@
 \end{equation}
+
+We will treat analytically two different cases. First, the case where the state $X_t^\epl$ is a vector of $\R^d$ and we wish to find the
+
 Considering the processes $X^\epl$ and $Z^\epl$ together, we obtain a system of stochastic differential equations
@@
 \begin{equation}
-	\sigma \delta \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)].
+	\sigma \delta \int_{\R} \int_{\R} \phi^\epl(x) \psi^\epl(z) \nabla_z V(z) \cdot \nabla_x R^\epl(x,z) \dd x \dd z = \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)].
 \end{equation}
@@
 \label{FPx}
-\sigma (\phi^\epl)''(x) + \left ( \alpha V''(x) + \frac{1}{\epl^2} p'' \left ( \frac{x}\epl \right ) \right ) \phi^\epl(x) + \left ( \alpha V'(x) + \frac{1}\epl p' \left ( \frac{x}\epl \right ) \right ) (\phi^\epl)'(x) = 0,
+\sigma \Delta_x \phi^\epl(x) + \left ( \alpha \Delta_x V(x) + \frac1{\epl^2} \Delta_x p \left( \frac{x}\epl \right) \right) \phi^\epl(x) + \left ( \alpha \nabla_xV(x) + \frac{1}\epl \nabla_xp \left ( \frac{x}\epl \right ) \right ) \cdot \nabla_x\phi^\epl(x) = 0,
 \end{equation}
@@
 \begin{equation}
-\psi^\epl(z) + z (\psi^\epl)'(z) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x,
+\psi^\epl(z) + z \cdot \nabla_z \psi^\epl(z) = \nabla_z \cdot \int_{\R^d} x \rho^\epl(x,z) \dd x,
 \end{equation}
@@
 \begin{equation}
-	\frac{\d}{\d z} (z \psi^\epl(z)) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x.
+	\nabla_z \cdot (z \psi^\epl(z)) = \nabla_z \cdot \int_{\R^d} x \rho^\epl(x,z) \dd x.
 \end{equation}
@@
 \begin{equation}\label{FPz}
-z \psi^\epl(z) = \int_{\R} x \rho^\epl(x,z) \dd x,
+z \psi^\epl(z) = \int_{\R^d} x \rho^\epl(x,z) \dd x,
 \end{equation}
@@
 \begin{equation} \label{eq:z_condition}
-z = \int_{\R} x \phi^\epl(x) R^\epl(x,z) \dd x.
+z = \int_{\R^d} x \phi^\epl(x) R^\epl(x,z) \dd x.
 \end{equation}
@@
 \begin{equation}\label{eq:psiEqualityPDE}
-\sigma \phi^\epl \psi^\epl \partial^2_{xx} R^\epl + \frac{1}{\delta} \phi^\epl \psi^\epl R^\epl + \sigma (\phi^\epl)' \psi^\epl \partial_x R^\epl + \frac{1}{\delta} (z-x) \phi^\epl ((\psi^\epl)' R + \psi^\epl \partial_z R^\epl) = 0.
+\sigma \phi^\epl \psi^\epl \Delta_x R^\epl + \frac{1}{\delta} \phi^\epl \psi^\epl R^\epl + \sigma \psi^\epl \nabla_x\phi^\epl \cdot \nabla_x R^\epl + \frac{1}{\delta} \phi^\epl  (z-x) \cdot (R^\epl \nabla_z\psi^\epl  + \psi^\epl \nabla_z R^\epl) = 0.
 \end{equation}
@@
 \begin{aligned}
-	\frac1\delta (\psi^\epl)' \int_\R (z-x)x \phi^\epl  R \dd x = \frac1\delta (\psi^\epl)' \left(z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x\right).
+	\frac1\delta (\psi^\epl)' \int_\R (z-x)x \phi^\epl  R^\epl \dd x = \frac1\delta (\psi^\epl)' \left(z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x\right).
 \end{aligned}
@@
 which is the desired result.
+
+\textbf{Multi-dimensional:} First
+\begin{equation}
+	\iint \left(\sigma \phi^\epl \psi^\epl \Delta_x R^\epl + \sigma \psi^\epl \nabla_x\phi^\epl \cdot \nabla_x R^\epl\right)(x \cdot \nabla_z V(z)) \dd x \dd z = -\sigma \iint \phi\psi \nabla_z V(z) \cdot \nabla_x R \dd x \dd z.
+\end{equation}
+Second
 \end{proof}

### 2020-01-23 CalNotes.tex
high dimensional parameter

--- 2020-01-17 CalNotes.tex
@@
 \begin{equation}\label{eq:SDE_HOM}
-	\d X_t^0 = - K V'(X) \dd t + \sqrt{2K\sigma} \dd W_t,
+	\d X_t^0 = - K V'(X_t^0) \dd t + \sqrt{2K\sigma} \dd W_t,
 \end{equation}
@@
 	\end{equation}
-	where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}. Moreover, the following central limit theorem holds
-	\begin{equation}\label{eq:theoremSecond}
-	\lim_{\epl \to 0} \lim_{T \to \infty} \sqrt{T} \left(A - \widehat A^\epl(T) \right) = \Lambda, \quad \text{in law}, 
-	\end{equation}
-	where $\Lambda \sim \mathcal N(0, \gamma^2)$ and where 
-	\begin{equation}
-	\gamma = \sqrt{2\sigma} \frac{\sqrt{\E^{\rho^0}[V'(Z)^2]}}{\E^{\rho^0}[V'(Z)V'(X)]}.
-	\end{equation}
+	where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.
+%   Moreover, the following central limit theorem holds
+%	\begin{equation}\label{eq:theoremSecond}
+%	\lim_{\epl \to 0} \lim_{T \to \infty} \sqrt{T} \left(A - \widehat A^\epl(T) \right) = \Lambda, \quad \text{in law}, 
+%	\end{equation}
+%	where $\Lambda \sim \mathcal N(0, \gamma^2)$ and where 
+%	\begin{equation}
+%	\gamma = \sqrt{2\sigma} \frac{\sqrt{\E^{\rho^0}[V'(Z)^2]}}{\E^{\rho^0}[V'(Z)V'(X)]}.
+%	\end{equation}
 \end{theorem}
@@
 
+\subsection{Notes on the high-dimensional parameter}
+
+Let us consider the following stochastic differential equation
+\begin{equation}
+\label{multiscale_equation_N}
+\d X^\varepsilon_t = \left ( - \alpha \cdot V'(X^\varepsilon_t) - \frac{1}{\varepsilon} p' \left ( \frac{X^\varepsilon_t}{\varepsilon} \right ) \right ) \d t + \sqrt{2\sigma} \d W_t, 
+\end{equation}
+where $\alpha \in \R^N$ and $V \colon \R \to \R^N$, $V(x) = \begin{pmatrix} V_1(x) \dots V_N(x) \end{pmatrix}^\top$ is a vector of potentials. Its homogenized equation is
+\begin{equation}
+\d X_t = - A \cdot V'(X_t) \d t + \sqrt{2\Sigma} \d W_t, 
+\end{equation}
+where $A = K\alpha$ and $\Sigma = K \sigma$. We consider the following estimator for the homogenized drift coefficient $A$
+\begin{equation}
+\hat{A} = - M^{-1} h,
+\end{equation}
+where
+\begin{equation}
+\label{estimators_N}
+M = \frac{1}{T} \int_0^T V'(Z^\varepsilon_t) \otimes V'(X^\varepsilon_t) \dd t \qquad \text{and} \qquad h = \frac{1}{T} \int_0^T V'(Z^\varepsilon_t) \dd X^\varepsilon_t.
+\end{equation}
+Note that repeating the same argument as in the case $N = 1$ we have
+\begin{equation}
+\label{formula_e}
+\delta \sigma \int_{\R} \int_{\R} V'(z) \phi^\varepsilon(x) \psi^\varepsilon(z) \partial_x R^\varepsilon(x,z) \dd x \dd z = \E^{\rho^\varepsilon} [ ((X^\varepsilon)^2 - (Z^\varepsilon)^2) V''(Z^\varepsilon) ],
+\end{equation}
+and
+\begin{equation}
+\label{formula_0}
+\delta \Sigma \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z = \E^{\rho^0} [ (X^2 - Z^2) V''(Z) ].
+\end{equation}
+Inserting equation \eqref{multiscale_equation_N} into \eqref{estimators_N} we have
+\begin{equation}
+\begin{aligned}
+h = & - \frac{1}{T} \int_0^T V'(Z^\varepsilon_t) (\alpha \cdot V'(X^\varepsilon_t)) \dd t - \frac{1}{T} \int_0^T \frac{1}{\varepsilon} p' \left ( \frac{X^\varepsilon_t}{\varepsilon} \right ) V'(Z^\varepsilon_t) \dd t + \frac{\sqrt{2\sigma}}{T} \int_0^T V'(Z^\varepsilon_t) \dd W_t \\
+= & - \left ( \frac{1}{T} \int_0^T V'(Z^\varepsilon_t) \otimes V'(X^\varepsilon_t) \dd t \right ) \alpha - \frac{1}{T} \int_0^T \frac{1}{\varepsilon} p' \left ( \frac{X^\varepsilon_t}{\varepsilon} \right ) V'(Z^\varepsilon_t) \dd t + \frac{\sqrt{2\sigma}}{T} \int_0^T V'(Z^\varepsilon_t) \dd W_t,
+\end{aligned}
+\end{equation}
+which implies
+\begin{equation}
+\begin{aligned}
+\hat{A} = \alpha & + \left ( \frac{1}{T} \int_0^T V'(Z^\varepsilon_t) \otimes V'(X^\varepsilon_t) \dd t \right )^{-1} \left ( \frac{1}{T} \int_0^T \frac{1}{\varepsilon} p' \left ( \frac{X^\varepsilon_t}{\varepsilon} \right ) V'(Z^\varepsilon_t) \dd t \right ) \\
+& - \sqrt{2\sigma} \left ( \frac{1}{T} \int_0^T V'(Z^\varepsilon_t) \otimes V'(X^\varepsilon_t) \dd t \right )^{-1} \left ( \frac{1}{T} \int_0^T V'(Z^\varepsilon_t) \dd W_t \right ).
+\end{aligned}
+\end{equation}
+Passing to the limit as $T$ goes to infinity and applying the ergodic theorem and the strong law of large numbers for martingale we have
+\begin{equation}
+\lim_{T \to \infty} - \sqrt{2\sigma} \left ( \frac{1}{T} \int_0^T V'(Z^\varepsilon_t) \otimes V'(X^\varepsilon_t) \dd t \right )^{-1} \left ( \frac{1}{T} \int_0^T V'(Z^\varepsilon_t) \dd W_t \right ) = 0,
+\end{equation}
+and
+\begin{equation}
+\begin{aligned}
+\lim_{T \to \infty} \left ( \frac{1}{T} \int_0^T V'(Z^\varepsilon_t) \otimes V'(X^\varepsilon_t) \dd t \right )^{-1} & \left ( \frac{1}{T} \int_0^T \frac{1}{\varepsilon} p' \left ( \frac{X^\varepsilon_t}{\varepsilon} \right ) V'(Z^\varepsilon_t) \dd t \right ) \\
+& = \E^{\rho^\varepsilon} [V'(Z^\varepsilon) \otimes V'(X^\varepsilon)]^{-1} \E^{\rho^\varepsilon} \left [ \frac{1}{\varepsilon} p' \left ( \frac{X^\varepsilon}{\varepsilon} \right ) V'(Z^\varepsilon) \right ],
+\end{aligned}
+\end{equation}
+which implies
+\begin{equation}
+\lim_{T \to \infty} \hat{A} = \alpha + \E^{\rho^\varepsilon} [V'(Z^\varepsilon) \otimes V'(X^\varepsilon)]^{-1} \E^{\rho^\varepsilon} \left [ \frac{1}{\varepsilon} p' \left ( \frac{X^\varepsilon}{\varepsilon} \right ) V'(Z^\varepsilon) \right ].
+\end{equation}
+An integration by parts yields
+\begin{equation}
+\begin{aligned}
+\E^{\rho^\varepsilon} \left [ \frac{1}{\varepsilon} p' \left ( \frac{X^\varepsilon}{\varepsilon} \right ) V'(Z^\varepsilon) \right ] = & - \E^{\rho^\varepsilon} [V'(Z^\varepsilon) \otimes V'(X^\varepsilon)] \alpha \\
+& + \sigma \int_{\R} \int_{\R} V'(z) \phi^\varepsilon(x) \psi^\varepsilon(z) \partial_x R^\varepsilon(x,z) \dd x \dd z,
+\end{aligned}
+\end{equation}
+and applying formula \eqref{formula_e} we have
+\begin{equation}
+\lim_{T \to \infty} \hat{A} = \frac{1}{\delta} \E^{\rho^\varepsilon} [V'(Z^\varepsilon) \otimes V'(X^\varepsilon)]^{-1} \E^{\rho^\varepsilon} [ ((X^\varepsilon)^2 - (Z^\varepsilon)^2) V''(Z^\varepsilon) ].
+\end{equation}
+Passing to the limit as $\varepsilon$ goes to zero we obtain
+\begin{equation}
+\lim_{\varepsilon \to 0} \lim_{T \to \infty} \hat{A} = \frac{1}{\delta} \E^{\rho^0} [V'(Z) \otimes V'(X)]^{-1} \E^{\rho^0} [ (X^2 - Z^2) V''(Z) ].
+\end{equation}
+Using formula \eqref{formula_0} and integrating by parts we have
+\begin{equation}
+\begin{aligned}
+\frac{1}{\delta} \E^{\rho^0} [ (X^2 - Z^2) V''(Z) ] & = \Sigma \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z \\
+& = \E^{\rho^0} [V'(Z) \otimes V'(X)] A,
+\end{aligned}
+\end{equation}
+which implies
+\begin{equation}
+\lim_{\varepsilon \to 0} \lim_{T \to \infty} \hat{A} = A.
+\end{equation}
+
 \section{Numerical experiments}
@@
 \bibliographystyle{siam}
-\bibliography{../../anmc}
+\bibliography{anmc}
 \end{document}

### 2020-01-23 CalNotes.tex
Partial

@@
 endowed with periodic boundary conditions.
+
+\subsection{Failure without pre-processing}
+
+Let us consider a trajectory $X_{0:T}^\epl \defeq (X_t^\epl, 0 \leq t \leq T)$ coming from the multiscale equation \eqref{eq:SDE_MS}, and the corresponding posterior distribution over the parameter $A$, which we denote by $\mu^\epl(A \mid X_{0:T}^\epl)$.
+The following result holds.
+\begin{theorem} Under assumption \ref{as:regularity} and if $T = \epl^{-\gamma}$ for $\gamma > 0$, then the posterior distribution $\mu^\epl(A \mid X_{0:T}^\epl) = \mathcal N(\bar A^\epl_T,  \sigma^2_T)$ satisfies
+	\begin{equation}
+	\begin{aligned}
+	&\lim_{\epl \to 0} \bar A^\epl_T = \alpha, \\
+	&\lim_{\epl \to 0} \sigma^2_T = 0.
+	\end{aligned}
+	\end{equation}
+\end{theorem}
+\begin{proof} Proposition \ref{prop:equiv} guarantees that 
+	\begin{equation}
+	\lim_{\epl \to 0} \abs{\bar A_T - \hat A(X^\epl_{0:T})} = 0,
+	\end{equation}
+	and that $\sigma^2_T \to 0$ for $\epl \to 0$. Moreover, \cite[Theorem 3.4]{PaS07} yields
+	\begin{equation}
+	\lim_{\epl \to 0} \hat A(X^\epl_{0:T}) = \alpha,
+	\end{equation}
+	which completes the proof.
+\end{proof}
+
+The result above implies that the posterior distribution over the drift coefficient concentrates asymptotically on an undesired value.
 
@@
 
-\section{The one-dimensional case}
+\section{A filtering approach}
 
-Let us consider $N = 1$ and write $A_1 = A$ and $V_1 = V$, respectively.
+%Let us consider $N = 1$ and write $A_1 = A$ and $V_1 = V$, respectively.
 The posterior distribution of $A$ given a trajectory $(X_t, 0 \leq t \leq T)$ is in this case a Gaussian $\mathcal N(\bar A_T, \sigma^2_T)$ where
-\begin{equation}
-\begin{aligned}
-	\bar A_T &= \frac{A_0}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t} - \frac{\sigma_0^2\int_0^T  V'(X_t) \dd X_t}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t}, \\
-	\sigma^{-2}_T &= \sigma_0^{-2} + \int_0^T V'(X_t)^2 \dd t.
-\end{aligned}
-\end{equation}
-We will in the following sections analyse the convergence of the posterior, both in case data from the multiscale process is not treated and in case they are pre-processed.
-
-\subsection{Failure without pre-processing}
-
-Let us consider a trajectory $X_{0:T}^\epl \defeq (X_t^\epl, 0 \leq t \leq T)$ coming from the multiscale equation \eqref{eq:SDE_MS}, and the corresponding posterior distribution over the parameter $A$, which we denote by $\mu^\epl(A \mid X_{0:T}^\epl)$.
-The following result holds.
-\begin{theorem} Under assumption \ref{as:regularity} and if $T = \epl^{-\gamma}$ for $\gamma > 0$, then the posterior distribution $\mu^\epl(A \mid X_{0:T}^\epl) = \mathcal N(\bar A^\epl_T,  \sigma^2_T)$ satisfies
-	\begin{equation}
-	\begin{aligned}
-		&\lim_{\epl \to 0} \bar A^\epl_T = \alpha, \\
-		&\lim_{\epl \to 0} \sigma^2_T = 0.
-	\end{aligned}
-	\end{equation}
-\end{theorem}
-\begin{proof} Proposition \ref{prop:equiv} guarantees that 
-	\begin{equation}
-		\lim_{\epl \to 0} \abs{\bar A_T - \hat A(X^\epl_{0:T})} = 0,
-	\end{equation}
-	and that $\sigma^2_T \to 0$ for $\epl \to 0$. Moreover, \cite[Theorem 3.4]{PaS07} yields
-	\begin{equation}
-		\lim_{\epl \to 0} \hat A(X^\epl_{0:T}) = \alpha,
-	\end{equation}
-	which completes the proof.
-\end{proof}
-
-The result above implies that the posterior distribution over the drift coefficient concentrates asymptotically on an undesired value.
-
-\subsection{A filtering approach}
+%\begin{equation}
+%\begin{aligned}
+%	\bar A_T &= \frac{A_0}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t} - \frac{\sigma_0^2\int_0^T  V'(X_t) \dd X_t}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t}, \\
+%	\sigma^{-2}_T &= \sigma_0^{-2} + \int_0^T V'(X_t)^2 \dd t.
+%\end{aligned}
+%\end{equation}
+%We will in the following sections analyse the convergence of the posterior, both in case data from the multiscale process is not treated and in case they are pre-processed.
 

### 2020-01-23 CalNotes.tex
Corrections N-dimensional meeting AA

--- 2020-01-23 CalNotes.tex
@@
 \begin{equation}\label{eq:SDE_MS}
-	\d X_t^\epl = -V'(X_t^\epl) \dd t - \frac1\epl p'\left(\frac{X_t^\epl}\epl\right) + \sqrt{2\sigma} \dd W_t,
+	\d X_t^\epl = -\alpha \cdot V'(X_t^\epl) \dd t - \frac1\epl p'\left(\frac{X_t^\epl}\epl\right) + \sqrt{2\sigma} \dd W_t,
 \end{equation}
-where $\sigma > 0$ and $W_t$ is a standard one-dimensional Brownian motion.
-The functions $V, p\colon \R \to \R$ are slow and fast potentials driving the dynamics of the solution $X_t^\epl$.
+where $\alpha_i \in \R$, $i = 1, \ldots, N$ and $\sigma > 0$ are the drift and diffusion coefficients respectively and $W_t$ is a standard one-dimensional Brownian motion.
+The functions $V\colon \R \to \R^N$ and $p\colon \R \to \R$ are slow and fast potentials driving the dynamics of the solution $X_t^\epl$.
 Given $N \in \N_{>0}$, we assume the slow potential to be of the form
 \begin{equation}
-	V(x) = \sum_{i=1}^N \alpha_i V_i(x),
+	V(x) = \begin{pmatrix} V_1(x) & V_2(x) & \cdots & V_N(x) \end{pmatrix}^\top,
 \end{equation}
-for coefficients $\alpha_i \in \R$, $i = 1, \ldots, N$, and smooth functions $V_i\colon \R \to \R$.
+for smooth functions $V_i\colon \R \to \R$, $i = 1, \ldots, N$.
 Moreover, we assume $p$ to be smooth and periodic of period $L$.
@@
 \begin{equation}\label{eq:SDE_HOM}
-	\d X_t^0 = - K V'(X) \dd t + \sqrt{2K\sigma} \dd W_t,
+	\d X_t^0 = - A \cdot V'(X_t^0) \dd t + \sqrt{2\Sigma} \dd W_t,
 \end{equation}
 where $W_t$ is the same Brownian motion and where the fast dynamics have been eliminated, such that $X_t^\epl \to X_t^0$ for $\epl\to 0$ in law as random variables in $\mathcal C^0((0, T), \R)$.
-In the following, we will denote $A_i \defeq K\alpha_i$.
-The coefficient $K$ is given by the formula
+In particular, we have $A_i = K\alpha_i$ and $\Sigma = K \sigma$, where the coefficient $K$ is given by the formula
 \begin{equation}\label{eq:K_HOM}
@@
 
-\corr{Failure without pre-processing: explain.}
+\subsection{Failure without pre-processing \corr{rewrite}}
 
-Let us consider a trajectory $X_{0:T}^\epl \defeq (X_t^\epl, 0 \leq t \leq T)$ coming from the multiscale equation \eqref{eq:SDE_MS}, and the corresponding posterior distribution over the parameter $A$, which we denote by $\mu^\epl(A \mid X_{0:T}^\epl)$.
+Let us consider a trajectory $X^\epl \defeq (X_t^\epl, 0 \leq t \leq T)$ coming from the multiscale equation \eqref{eq:SDE_MS}, and the corresponding posterior distribution over the parameter $A$, which we denote by $\mu^\epl(A \mid X^\epl)$.
 The following result holds.
-\begin{theorem} Under assumption \ref{as:regularity} and if $T = \epl^{-\gamma}$ for $\gamma > 0$, then the posterior distribution $\mu^\epl(A \mid X_{0:T}^\epl) = \mathcal N(\bar A^\epl_T,  \sigma^2_T)$ satisfies
+\begin{theorem} Under assumption \ref{as:regularity} and if $T = \epl^{-\gamma}$ for $\gamma > 0$, then the posterior distribution $\mu^\epl(A \mid X^\epl) = \mathcal N(\bar A^\epl_T,  \sigma^2_T)$ satisfies
 	\begin{equation}
@@
 
-Let us denote by $A \in \R^N$ the vector of the coefficients $A_i \defeq K \alpha_i$ appearing in the drift term of the homogenized SDE \eqref{eq:SDE_HOM}.
-In a Bayesian setting, our goal is to determine the posterior distribution $\mu(A \mid X_{0:T})$ given a continuous trajectory $X_{0:T} \defeq (X_t, 0 \leq t \leq T)$.
-Choosing a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$ on $A$, where $A_0 \in \R^N$ and $C_0 \in \R^{N\times N}$ is symmetric positive definite, the posterior distribution admits a density $p(A \mid X_{0:T})$ with respect to the Lebesgue measure which satisfies
+In a Bayesian setting, our goal is to determine the posterior distribution $\mu(A \mid X)$ given a continuous trajectory $X \defeq (X_t, 0 \leq t \leq T)$.
+Choosing a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$ on $A$, where $A_0 \in \R^N$ and $C_0 \in \R^{N\times N}$ is symmetric positive definite, the posterior distribution admits a density $p(A \mid X)$ with respect to the Lebesgue measure which satisfies
 \begin{equation}
-	p(A \mid X_{0:T}) = \frac1Z \, p(X_{0:T} \mid A) \, p_0(A),
+	p(A \mid X) = \frac1Z \, p(X \mid A) \, p_0(A),
 \end{equation}
@@
 \begin{equation}
-	p(X_{0:T} \mid A) = \exp\left\{-\int_0^T \langle A, \mathbf V'(X_t)\rangle \dd X_t - \frac12 \int_0^T \langle A, \mathbf V'(X_t) \rangle^2 \dd t \right\}.
+	p(X \mid A) = \exp\left(-\frac{I(X\mid A)}{2\Sigma} \right), 
 \end{equation}
-In the formula above, we denote by $\mathbf V \colon \R \to \R^N$ the vector-valued function whose $i$-th component is $\mathbf V_i = V_i$, and by $\mathbf V'$ the vector of its derivatives, i.e., the Jacobian matrix.
-Moreover, we denote by $\langle \cdot, \cdot \rangle$ the Euclidean scalar product in $\R^N$ and by $\norm{\cdot}_2$ the corresponding norm.
+and where
+\begin{equation}
+	I(X\mid A) = \int_0^T A \cdot V'(X_t) \dd X_t + \frac12 \int_0^T \left( A \cdot V'(X_t) \right)^2 \dd t.
+\end{equation}
+
 The log-posterior density is then given by
@@
 \begin{aligned}
-	\log p(A \mid X_{0:T}) = &-\log Z -\int_0^T \langle A, \mathbf V'(X_t)\rangle \dd X_t - \frac12 \int_0^T \langle A, \mathbf V'(X_t) \rangle^2 \dd t \\
+	\log p(A \mid X) = &-\log Z -\frac1{2\Sigma}\int_0^T A \cdot V'(X_t) \dd X_t - \frac1{4\Sigma} \int_0^T \left(A \cdot V'(X_t) \right)^2 \dd t \\
 	&- \frac12 \norm{C_0^{-1/2}(A - A_0)}_2^2.
@@
 \begin{equation}
-	M_{ij} = \frac1T \int_0^T V_i'(X_t) \, V_j'(X_t) \dd t, \quad i, j = 1, \ldots, N,
+	M_{ij} = \frac1{2\Sigma T} \int_0^T V_i'(X_t) \, V_j'(X_t) \dd t, \quad i, j = 1, \ldots, N,
 \end{equation}
@@
 \begin{equation}
-	h_i = \frac1T \int_0^T V_i'(X_t) \dd X_t, \quad i = 1, \ldots, N.
+	h_i = \frac1{2\Sigma T} \int_0^T V_i'(X_t) \dd X_t, \quad i = 1, \ldots, N.
 \end{equation}
-If we employ this notation, we can rewrite the log-posterior density as
+Let us remark that we can rewrite $M$ and $h$ in vector notation as
+\begin{equation}
+		M = \frac1{2\Sigma T} \int_0^T V'(X_t) \otimes V'(X_t) \dd t, \quad h = \frac1{2\Sigma T} \int_0^T V'(X_t) \dd X_t,
+\end{equation}
+where $\otimes$ denotes the tensor product in $\R^N$. Therefore, we can rewrite the log-posterior density as
 \begin{equation}
 \begin{aligned}
-	\log p(A \mid X_{0:T}) = &-\log Z - T\langle A, h\rangle - \frac{T}{2} \langle A, M A\rangle - \frac12 \langle A - A_0, C_0^{-1}(A-A_0) \rangle.
+	\log p(A \mid X) = &-\log Z - T A \cdot h - \frac{T}{2} A \cdot M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
 \end{aligned}
 \end{equation}
-Completing the squares in the log-posterior density, it is possible to show that the posterior is a Gaussian $\mu(A \mid X_{0:T}) = \mathcal N(\bar A_T, C_T)$, whose precision matrix and mean are formally given by
+Completing the squares in the log-posterior density, it is possible to show that the posterior is a Gaussian $\mu(A \mid X) = \mathcal N(m_T, C_T)$, whose precision matrix and mean are formally given by
 \begin{equation}
@@
 	C_T^{-1} &= C_0^{-1} + T M, \\
-	C_T^{-1}\bar A_T &= C_0^{-1}A_0 - T h. 
+	C_T^{-1}m_T &= C_0^{-1}A_0 - T h. 
 \end{aligned}
@@
 We are now interested in the limit of the posterior distribution for $T \to \infty$.
-Let us first define the maximum likelihood estimator (MLE) $\widehat A(X_{0:T})$ of $A$, which is obtained by maximizing the log-likelihood function $\log p(X_{0:T} \mid A)$, and which is hence formally given by
+Let us first define the maximum likelihood estimator (MLE) $\widehat A(X)$ of $A$, which is obtained by maximizing the log-likelihood function $\log p(X \mid A)$, and which is hence formally given by
 \begin{equation}
-	\widehat A(X_{0:T}) = -M^{-1}h.
+	\widehat A(X) = -M^{-1}h.
 \end{equation}
@@
 We can now state the main result for asymptotic convergence of the posterior distribution.
-\begin{proposition}\label{prop:equiv} Given a continuous stochastic process $X_t$ which is ergodic with invariant measure $\mu^{\infty}$ such that $\E^{\mu^\infty}(V_i'(\cdot)) \leq C$ for some constant $C > 0$ and for all $i = 1, \ldots, N$, the posterior $\mu(A \mid X_{0:T})$ contracts to the limit of $\widehat A(X_{0:T})$ for $T \to \infty$.
+\begin{proposition}\label{prop:equiv} Given a continuous stochastic process $X \defeq (X_t, 0 \leq t, \leq T)$ which is ergodic with invariant measure $\mu^{\infty}$ such that $\E^{\mu^\infty}(V_i'(\cdot)) \leq C$ for some constant $C > 0$ and for all $i = 1, \ldots, N$, the posterior $\mu(A \mid X)$ contracts to the limit of $\widehat A(X)$ for $T \to \infty$.
 %	 for $T$ arbitrarily large and under Assumption \ref{as:regularity}, the posterior mean and covariance satisfy
@@
 %	\begin{aligned}
-%		&\lim_{T \to \infty} \norm{m_T - \widehat A(X_{0:T})}_2 = 0, \\
+%		&\lim_{T \to \infty} \norm{m_T - \widehat A(X)}_2 = 0, \\
 %		&\lim_{T \to \infty} \norm{C_T}_F = 0,
@@
 	\begin{equation}
-		\norm{m_T - \widehat A(X_{0:T})}_2 = T^{-1}\norm{M^{-1}C_0^{-1}A_0 - Q^{-1}\left(C_0^{-1}A_0 -h \right)}_2.
+		\norm{m_T - \widehat A(X)}_2 = T^{-1}\norm{M^{-1}C_0^{-1}A_0 - Q^{-1}\left(C_0^{-1}A_0 - Th \right)}_2.
 	\end{equation}
@@
 	\begin{equation}
-		\lim_{T\to\infty} \norm{m_T - \widehat A(X_{0:T})}_2 = 0,
+		\lim_{T\to\infty} \norm{m_T - \widehat A(X)}_2 = 0,
 	\end{equation}
@@
 
+%Let us consider $N = 1$ and write $A_1 = A$ and $V_1 = V$, respectively.
+The posterior distribution of $A$ given a trajectory $(X_t, 0 \leq t \leq T)$ is in this case a Gaussian $\mathcal N(\bar A_T, \sigma^2_T)$ where
+%\begin{equation}
+%\begin{aligned}
+%	\bar A_T &= \frac{A_0}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t} - \frac{\sigma_0^2\int_0^T  V'(X_t) \dd X_t}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t}, \\
+%	\sigma^{-2}_T &= \sigma_0^{-2} + \int_0^T V'(X_t)^2 \dd t.
+%\end{aligned}
+%\end{equation}
+%We will in the following sections analyse the convergence of the posterior, both in case data from the multiscale process is not treated and in case they are pre-processed.
+
 In the previous section, we have shown that posterior distributions over the drift coefficient of the homogenized equation are asymptotically incorrect if multiscale data are replaced into the expression of the likelihood.
@@
 \begin{equation}\label{eq:ZDef}
-	Z^{\epl,k}_t \defeq \int_0^t k^\epl(t-s)X^\epl_s \dd s,
+	Z^{\epl,k}_t \defeq \int_0^t k^\epl(t, s)X^\epl_s \dd s.
 \end{equation}
-where the equality is component-wise in $\R^d$. Let $\beta, \delta > 0$ and let us consider a family of exponential kernel functions defined as
+Let $\beta, \delta > 0$ and let us consider a family of exponential kernel functions defined as
 \begin{equation}
-	k^\epl(t-s) = C_\beta \delta^{-1/\beta} e^{-(t-s)^\beta/\delta},
+	k^\epl(t, s) = C_\beta \delta^{-1/\beta} e^{-(t-s)^\beta/\delta},
 \end{equation}
@@
 \begin{equation}
-	\d Z^\epl_t = k(0) X^\epl_t \dd t + \int_0^t \partial_t k(t-s) X^\epl_s \dd s \dd t = \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
+	\d Z^\epl_t = k(t,t) X^\epl_t \dd t + \int_0^t \partial_t k(t,s) X^\epl_s \dd s \dd t = \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
 \end{equation}
-
-We will treat analytically two different cases. First, the case where the state $X_t^\epl$ is a vector of $\R^d$ and we wish to find the
-
 Considering the processes $X^\epl$ and $Z^\epl$ together, we obtain a system of stochastic differential equations
@@
 \begin{aligned}
-\d X^\epl_t &= -\left( \alpha \nabla_x V(X^\epl_t) - \frac{1}\epl \nabla_x p \left ( \frac{X^\epl_t}\epl \right ) \right ) \dd t + \sqrt{2\sigma} \dd W_t, \\
+\d X_t^\epl &= -\alpha \cdot V'(X_t^\epl) \dd t - \frac1\epl p'\left(\frac{X_t^\epl}\epl\right) + \sqrt{2\sigma} \dd W_t, \\
 \d Z^\epl_t &= \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
@@
 Let $\rho^\epl = \rho^\epl(x,z)$ be the stationary distribution of the joint process $(X^\epl, Z^\epl)^\top$.
-Then $\rho^\epl$ is the solution of the $2d$-dimensional stationary Fokker--Planck equation
+\corr{How do we show that the couple $(X^\epl, Z^\epl)^\top$ is ergodic.} Then $\rho^\epl$ is the solution of the two-dimensional stationary Fokker--Planck equation
 \begin{equation}
@@
 	\label{eq:FPsystem}
-	\sigma \Delta_x \rho^\epl(x,z) & + \left ( \alpha  \Delta_x V(x) + \frac{1}{\epl^2} \Delta_x p \left( \frac{x}\epl \right) + \frac1\delta \right) \rho^\epl(x,z) \\
-	& + \left ( \alpha \nabla_x V(x) + \frac{1}\epl \nabla_x p \left ( \frac{x}\epl \right ) \right ) \cdot \nabla_x \rho^\epl(x,z) + \frac{1}{\delta}(z - x) \cdot \nabla_z \rho^\epl(x,z) = 0.
+	\sigma \partial^2_{xx} \rho^\epl(x,z) & + \left ( \alpha \cdot V''(x) + \frac{1}{\epl^2} p'' \left ( \frac{x}\epl \right ) + \frac{1}{\delta} \right ) \rho^\epl(x,z) \\
+	& + \left ( \alpha \cdot V'(x) + \frac{1}\epl p' \left ( \frac{x}\epl \right ) \right ) \partial_x \rho^\epl(x,z) + \frac{1}{\delta}(z - x) \partial_z \rho^\epl(x,z) = 0.
 \end{aligned}
@@
 
-\begin{example}\label{ex:OrnUhl} A closed form solution of \eqref{eq:FPsystem} can be obtained in a simple homogenized case.
+\begin{example}\label{ex:OrnUhl} A closed form solution of \eqref{eq:FPsystem} can be obtained in a simple homogenized case with the dimension of the parameter $N=1$.
 Let $p(y) = 0$ and the parameters $\alpha$, $\sigma$ be replaced respectively by $A$ and $\Sigma$.
@@
 \begin{equation}
-\rho^0(x,z) = \frac{1}{A_{\rho^0}} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right),
+\rho^0(x,z) = \frac{1}{C_{\rho^0}} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right),
 \end{equation}
@@
 \begin{equation}
-A_{\rho^0} = \int_{\R} \int_{\R} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right) \dd x \dd z.
+C_{\rho^0} = \int_{\R} \int_{\R} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right) \dd x \dd z.
 \end{equation}
@@
 \begin{equation}\label{eq:marginalX}
-	\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(- \frac{\alpha}{\sigma} V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
+	\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(-\frac{1}{\sigma} \alpha \cdot V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
 \end{equation}
@@
 \begin{equation}
-	C_{\phi^\epl} = \int_{\R} \exp\left(- \frac{\alpha}{\sigma} V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right) \dd x.
+	C_{\phi^\epl} = \int_{\R} \exp\left(-\frac{1}{\sigma} \alpha \cdot V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right) \dd x.
 \end{equation}
@@
 \begin{equation}
-	\sigma \delta \int_{\R} \int_{\R} \phi^\epl(x) \psi^\epl(z) \nabla_z V(z) \cdot \nabla_x R^\epl(x,z) \dd x \dd z = \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)].
+	\sigma \delta \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)].
 \end{equation}
@@
 \label{FPx}
-\sigma \Delta_x \phi^\epl(x) + \left ( \alpha \Delta_x V(x) + \frac1{\epl^2} \Delta_x p \left( \frac{x}\epl \right) \right) \phi^\epl(x) + \left ( \alpha \nabla_xV(x) + \frac{1}\epl \nabla_xp \left ( \frac{x}\epl \right ) \right ) \cdot \nabla_x\phi^\epl(x) = 0,
+\sigma (\phi^\epl)''(x) + \left ( \alpha \cdot V''(x) + \frac{1}{\epl^2} p'' \left ( \frac{x}\epl \right ) \right ) \phi^\epl(x) + \left ( \alpha \cdot V'(x) + \frac{1}\epl p' \left ( \frac{x}\epl \right ) \right ) (\phi^\epl)'(x) = 0,
 \end{equation}
@@
 \begin{equation}
-\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(- \frac{\alpha}{\sigma} V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
+\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(- \frac{1}{\sigma} \alpha \cdot V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
 \end{equation}
@@
 \begin{equation}
-\psi^\epl(z) + z \cdot \nabla_z \psi^\epl(z) = \nabla_z \cdot \int_{\R^d} x \rho^\epl(x,z) \dd x,
+\psi^\epl(z) + z (\psi^\epl)'(z) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x,
 \end{equation}
@@
 \begin{equation}
-	\nabla_z \cdot (z \psi^\epl(z)) = \nabla_z \cdot \int_{\R^d} x \rho^\epl(x,z) \dd x.
+	\frac{\d}{\d z} (z \psi^\epl(z)) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x.
 \end{equation}
@@
 \begin{equation}\label{FPz}
-z \psi^\epl(z) = \int_{\R^d} x \rho^\epl(x,z) \dd x,
+z \psi^\epl(z) = \int_{\R} x \rho^\epl(x,z) \dd x,
 \end{equation}
@@
 \begin{equation} \label{eq:z_condition}
-z = \int_{\R^d} x \phi^\epl(x) R^\epl(x,z) \dd x.
+z = \int_{\R} x \phi^\epl(x) R^\epl(x,z) \dd x.
 \end{equation}
@@
 \begin{equation}\label{eq:psiEqualityPDE}
-\sigma \phi^\epl \psi^\epl \Delta_x R^\epl + \frac{1}{\delta} \phi^\epl \psi^\epl R^\epl + \sigma \psi^\epl \nabla_x\phi^\epl \cdot \nabla_x R^\epl + \frac{1}{\delta} \phi^\epl  (z-x) \cdot (R^\epl \nabla_z\psi^\epl  + \psi^\epl \nabla_z R^\epl) = 0.
+\sigma \phi^\epl \psi^\epl \partial^2_{xx} R^\epl + \frac{1}{\delta} \phi^\epl \psi^\epl R^\epl + \sigma (\phi^\epl)' \psi^\epl \partial_x R^\epl + \frac{1}{\delta} (z-x) \phi^\epl ((\psi^\epl)' R + \psi^\epl \partial_z R^\epl) = 0.
 \end{equation}
@@
 \begin{aligned}
-	\frac1\delta (\psi^\epl)' \int_\R (z-x)x \phi^\epl  R^\epl \dd x = \frac1\delta (\psi^\epl)' \left(z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x\right).
+	\frac1\delta (\psi^\epl)' \int_\R (z-x)x \phi^\epl  R \dd x = \frac1\delta (\psi^\epl)' \left(z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x\right).
 \end{aligned}
@@
 \end{equation}
-Multiplying by $V'(z)$, integrating with respect to $z$ and integrating by parts, we obtain
+Multiplying by $V'(z)$, integrating with respect to $z$ and integrating by parts, we obtain the following identity in $\R^N$
 \begin{equation}
@@
 which is the desired result.
-
-\textbf{Multi-dimensional:} First
-\begin{equation}
-	\iint \left(\sigma \phi^\epl \psi^\epl \Delta_x R^\epl + \sigma \psi^\epl \nabla_x\phi^\epl \cdot \nabla_x R^\epl\right)(x \cdot \nabla_z V(z)) \dd x \dd z = -\sigma \iint \phi\psi \nabla_z V(z) \cdot \nabla_x R \dd x \dd z.
-\end{equation}
-Second
 \end{proof}
@@
 \begin{equation} \label{eq:FPsystem_homogenized}
-	\Sigma \partial^2_{xx} \rho^0(x,z) + \left ( A V''(x) + \frac{1}{\delta} \right ) \rho^0(x,z) + A V'(x) \partial_x \rho^0(x,z) + \frac{1}{\delta}(z - x) \partial_z \rho^0(x,z) = 0,
+	\Sigma \partial^2_{xx} \rho^0(x,z) + \left ( A \cdot V''(x) + \frac{1}{\delta} \right ) \rho^0(x,z) + A \cdot V'(x) \partial_x \rho^0(x,z) + \frac{1}{\delta}(z - x) \partial_z \rho^0(x,z) = 0,
 \end{equation}
@@
 \end{lemma}
-\begin{proof} 
+\begin{proof} \todo
 \end{proof}
@@
 	\begin{equation}
-		\phi^0(x) = \frac{1}{C_{\phi^0}} \exp\left(- \frac{A}{\Sigma} V(x)\right), \quad \text{where } \quad C_{\phi^0} = \int_{\R} \exp\left(- \frac{A}{\Sigma} V(x) \right) \dd x.
+		\phi^0(x) = \frac{1}{C_{\phi^0}} \exp\left(- \frac1{\Sigma} A\cdot V(x)\right), \quad \text{where } \quad C_{\phi^0} = \int_{\R} \exp\left(- \frac1{\Sigma} A\cdot V(x) \right) \dd x.
 	\end{equation}
@@
 \begin{equation}\label{eq:AHatMixed}
+	\widehat A^\epl(T) = - \widetilde M^{-1} \widetilde h,
+\end{equation}
+where
+\begin{equation}
+	\widetilde M = \frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t \qquad \text{and} \qquad \widetilde h = \frac{1}{T} \int_0^T V'(Z^\epl_t) \dd X^\epl_t.
+\end{equation}
+In practice, one evaluation of $V'(\cdot)$ is computed with the filter, while the differential and the second evaluation of $V'(\cdot)$ are maintained with the original process $X^\epl$.
+
+\begin{remark} Let us remark that in the one-dimensional case $N = 1$, the estimator reduces to
+\begin{equation}
 \widehat A^\epl(T) = - \frac{\int_0^T V'(Z^\epl_t) \dd X^\epl_t}{\int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t}.
 \end{equation}
+\end{remark}
 
@@
 	\end{equation}
-	where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}. Moreover, the following central limit theorem holds
-	\begin{equation}\label{eq:theoremSecond}
-	\lim_{\epl \to 0} \lim_{T \to \infty} \sqrt{T} \left(A - \widehat A^\epl(T) \right) = \Lambda, \quad \text{in law}, 
-	\end{equation}
-	where $\Lambda \sim \mathcal N(0, \gamma^2)$ and where 
-	\begin{equation}
-	\gamma = \sqrt{2\sigma} \frac{\sqrt{\E^{\rho^0}[V'(Z)^2]}}{\E^{\rho^0}[V'(Z)V'(X)]}.
-	\end{equation}
+	where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.
+%   Moreover, the following central limit theorem holds
+%	\begin{equation}\label{eq:theoremSecond}
+%	\lim_{\epl \to 0} \lim_{T \to \infty} \sqrt{T} \left(A - \widehat A^\epl(T) \right) = \Lambda, \quad \text{in law}, 
+%	\end{equation}
+%	where $\Lambda \sim \mathcal N(0, \gamma^2)$ and where 
+%	\begin{equation}
+%	\gamma = \sqrt{2\sigma} \frac{\sqrt{\E^{\rho^0}[V'(Z)^2]}}{\E^{\rho^0}[V'(Z)V'(X)]}.
+%	\end{equation}
 \end{theorem}
 
-\begin{proof} Replacing the expression of $\d X^\epl_t$ into \eqref{eq:AHatMixed}, we get
+\begin{proof} Replacing the expression of $\d X^\epl_t$ into \eqref{eq:AHatMixed}, we get for $\widetilde h$
 \begin{equation}\label{Ahat_decomposition}
-\begin{aligned} \nonumber
-\widehat A^\epl(T) &= \frac{\alpha \int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t + \int_0^T V'(Z^\epl_t) \frac1\epl  p' \left ( \frac{X^\epl_t}\epl \right )\dd t - \sqrt{2\sigma} \int_0^T V'(Z^\epl_t) \dd W_t}{\int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t} \\
-&= \alpha + \frac{\int_0^T V'(Z^\epl_t) \frac1\epl  p' \left ( \frac{X^\epl_t}\epl \right )\dd t}{\int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t} - \sqrt{2\sigma} \frac{\int_0^T V'(Z^\epl_t) \dd W_t}{\int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t}\\
+\widetilde h = -\widetilde M \alpha - \frac{1}{T} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t + \frac{\sqrt{2\sigma}}{T} \int_0^T V'(Z^\epl_t) \dd W_t.
+\end{equation}
+Therefore, we have
+\begin{equation}
+\begin{aligned}
+	\widehat A^\epl(T) &= \alpha + \frac{1}{T} \widetilde M^{-1} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t - \frac{\sqrt{2\sigma}}{T}  \widetilde M^{-1} \int_0^T V'(Z^\epl_t) \dd W_t\\
 	&\eqdef \alpha + I_1^\epl(T) - I_2^\epl(T).
@@
 \begin{equation}\label{limit_estimator}
-\lim_{T \to \infty} I_1^\epl(T) = \frac{\E^{\rho^\epl} \left [ \frac{1}\epl V'(Z^\epl) p' \left ( \frac{X^\epl}\epl \right ) \right ]}{\E^{\rho^\epl} [ V'(Z^\epl) V'(X^\epl) ]}, \quad \text{a.s.}
+\lim_{T \to \infty} I_1^\epl(T) = \E^{\rho^\epl} [V'(Z^\epl) \otimes V'(X^\epl)]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ], \quad \text{a.s.}
 \end{equation}
-Let us consider the numerator of the expression above. Due to Lemma \ref{lem:FPMarginal} and integrating by parts, we have
+Due to Lemma \ref{lem:FPMarginal} and integrating by parts, we have
 \begin{equation}
 \begin{aligned}
-	\E^{\rho^\epl} \left [ V'(Z^\epl) \frac1\epl p' \left ( \frac{X^\epl}\epl \right ) \right ] &= \int_{\R} \int_{\R} V'(z) \, \frac1\epl p' \left ( \frac{x}\epl \right ) \frac{1}{C_{\phi^\epl}} e^{- \frac{\alpha}{\sigma} V(x)} e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \psi^\epl(z) R^\epl(x,z) \dd x \dd z \\
-	&= -\sigma \int_{\R} \int_{\R} \frac{\d}{\d x}\left( e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \right) \frac{1}{C_{\phi^\epl}} e^{- \frac{\alpha}{\sigma} V(x)} V'(z) \psi^\epl(z) R^\epl(x,z) \dd x \dd z \\
-	&= \sigma \int_{\R} \int_{\R} \frac{1}{C_{\phi^\epl}} e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \partial_x \left ( e^{- \frac{\alpha}{\sigma} V(x)} R^\epl(x,z) \right ) V'(z) \psi^\epl(z) \dd x \dd z,
+	\E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] &= \int_{\R} \int_{\R} V'(z) \, \frac1\epl p' \left ( \frac{x}\epl \right ) \frac{1}{C_{\phi^\epl}} e^{- \frac{1}{\sigma} \alpha \cdot V(x)} e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \psi^\epl(z) R^\epl(x,z) \dd x \dd z \\
+	&= -\sigma \int_{\R} \int_{\R} \frac{\d}{\d x}\left( e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \right) \frac{1}{C_{\phi^\epl}} e^{- \frac{1}{\sigma} \alpha \cdot V(x)} V'(z) \psi^\epl(z) R^\epl(x,z) \dd x \dd z \\
+	&= \sigma \int_{\R} \int_{\R} \frac{1}{C_{\phi^\epl}} e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \partial_x \left ( e^{- \frac{1}{\sigma} \alpha \cdot V(x)} R^\epl(x,z) \right ) V'(z) \psi^\epl(z) \dd x \dd z,
 \end{aligned}
@@
 \begin{align}
-	\E^{\rho^\epl} \left [ \frac{1}\epl V'(Z^\epl) p' \left ( \frac{X^\epl}\epl \right ) \right ] &= 
+	\E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] &= 
 	\begin{aligned}[t]
-		&-\alpha \int_{\R} \int_{\R} V'(x) V'(z) \rho^\epl(x, z) \dd x \dd z \\
+		&- \left(\int_{\R} \int_{\R} V'(Z^\varepsilon_t) \otimes V'(X^\varepsilon_t) \rho^\epl(x, z) \dd x \dd z\right) \alpha \\
 		&+\sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z 
@@
 	\\
-	&= - \alpha \E^{\rho^\epl} [ V'(Z^\epl) V'(X^\epl) ] + \sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z.
+	&= -  \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]\alpha + \sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z.
 \end{align}
@@
 \begin{equation}
-\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac{\sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z}{\E^{\rho^\epl} [ V'(Z^\epl) V'(X^\epl) ]}, \quad \text{a.s.}
+\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z, \quad \text{a.s.}
 \end{equation}
@@
 \begin{equation}
-	\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac{\E^{\rho^\epl}[(X^2 - Z^2)V''(Z)]}{\delta \E^{\rho^\epl}[V'(Z) V'(X)]}, \quad \text{a.s.}	
+	\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)], \quad \text{a.s.}	
 \end{equation}
@@
 \begin{equation} \label{limit_estimator_2}
-	\lim_{\epl \to 0} \lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac{\E^{\rho^0}[(X^2 - Z^2)V''(Z)]}{\delta \E^{\rho^0}[V'(Z) V'(X)]}, \quad \text{a.s.},
+	\lim_{\epl \to 0} \lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)], \quad \text{a.s.},
 \end{equation}
@@
 \end{equation}
-and finally, an integration by parts yields
-\begin{align}
-	\E^{\rho^0}[V'(Z) V'(X)] &= \int_{\R} \int_{\R} V'(x) V'(z) \frac{1}{C_{\phi^0}} e^{-\frac{A}{\Sigma} V(x)} \psi^0(z) R^0(x,z) \dd x \dd z \\
-	&= - \frac{\Sigma}{A} \int_{\R} \int_{\R} V'(z) \frac{\d}{\d x} \left(\frac{1}{C_{\phi^0}} e^{-\frac{A}{\Sigma} V(x)} \right ) \psi^0(z) R^0(x,z) \dd x \dd z \\
-	&= \frac{\Sigma}{A} \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z.
-\end{align}
+and moreover, an integration by parts yields
+\begin{equation}
+\begin{aligned}
+	\frac{1}{\delta} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] &= -\Sigma \int_{\R} \int_{\R} V'(z) (\phi^0)'(x) \psi^0(z) R^0(x,z) \dd x \dd z\\
+	&= -\int_{\R} \int_{\R} V'(z) \left ( \frac{1}{C_{\phi^0}} e^{-\frac{1}{\Sigma} A\cdot V(x)} \right )' \psi^0(z) R^0(x,z) \dd x \dd z \\
+	&= \left(\int_{\R} \int_{\R} V'(z) \otimes V'(x) \rho^0(x,z) \dd x \dd z\right)A\\
+	&=  \E^{\rho^0} [ V'(Z) \otimes V'(X) ]A
+\end{aligned}
+\end{equation}
 We can therefore conclude that
@@
 \end{equation}
-We now consider the second term $I_2$, and rewrite it as 
+We now consider the second term $I_2$, and rewrite it as (\corr{Still one-dimensional, correct to $N$-dimensional parameter})
 \begin{equation}

### 2020-01-28 CalNotes.tex
Numerical experiments added

@@
 Given $N \in \N_{>0}$, we assume the slow potential to be of the form
-\begin{equation}
+\begin{equation}\label{eq:Potential}
 	V(x) = \begin{pmatrix} V_1(x) & V_2(x) & \cdots & V_N(x) \end{pmatrix}^\top,
@@
 
+\subsection{The subsampling approach for point estimates}
+
+\subsection{Outline}
+
 \section{Posterior formal computations}
 
-In a Bayesian setting, our goal is to determine the posterior distribution $\mu(A \mid X)$ given a continuous trajectory $X \defeq (X_t, 0 \leq t \leq T)$.
+In a Bayesian setting, the goal is to determine the posterior distribution $\mu(A \mid X)$ given a continuous trajectory $X \defeq (X_t, 0 \leq t \leq T)$.
 Choosing a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$ on $A$, where $A_0 \in \R^N$ and $C_0 \in \R^{N\times N}$ is symmetric positive definite, the posterior distribution admits a density $p(A \mid X)$ with respect to the Lebesgue measure which satisfies
@@
 \end{equation}
-and where
+with
 \begin{equation}
@@
 \begin{equation}\label{eq:ZDef}
-	Z^{\epl,k}_t \defeq \int_0^t k^\epl(t, s)X^\epl_s \dd s.
+	Z^{\epl}_t \defeq \int_0^t k(t, s)X^\epl_s \dd s.
 \end{equation}
 Let $\beta, \delta > 0$ and let us consider a family of exponential kernel functions defined as
-\begin{equation}
-	k^\epl(t, s) = C_\beta \delta^{-1/\beta} e^{-(t-s)^\beta/\delta},
+\begin{equation}\label{eq:filter}
+	k(t, s) = C_\beta \delta^{-1/\beta} e^{-(t-s)^\beta/\delta},
 \end{equation}
@@
 	\frac{1}{\delta} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] &= -\Sigma \int_{\R} \int_{\R} V'(z) (\phi^0)'(x) \psi^0(z) R^0(x,z) \dd x \dd z\\
-	&= -\int_{\R} \int_{\R} V'(z) \left ( \frac{1}{C_{\phi^0}} e^{-\frac{1}{\Sigma} A\cdot V(x)} \right )' \psi^0(z) R^0(x,z) \dd x \dd z \\
+	&= -\Sigma \int_{\R} \int_{\R} V'(z) \left ( \frac{1}{C_{\phi^0}} e^{-\frac{1}{\Sigma} A\cdot V(x)} \right )' \psi^0(z) R^0(x,z) \dd x \dd z \\
 	&= \left(\int_{\R} \int_{\R} V'(z) \otimes V'(x) \rho^0(x,z) \dd x \dd z\right)A\\
@@
 
+\subsection{The Bayesian setting}
+
 \section{Numerical experiments}
+
+In this section we show numerical experiments confirming our theoretical findings and showing the potentiality of the filtering approach.
+
+\subsection{Parameters of the filter}
+\begin{figure}[t]
+	\centering
+	\begin{tabular}{ccc}
+		\includegraphics[]{Figures/OUSubs_s5} & \includegraphics[]{Figures/OUFilt_s5_b1}  & \includegraphics[]{Figures/OUFilt_s5_b5} \\ % & \includegraphics[]{Figures/OUFilt_s5_b10} \\
+		\includegraphics[]{Figures/OUSubs_s7} & \includegraphics[]{Figures/OUFilt_s7_b1}  & \includegraphics[]{Figures/OUFilt_s7_b5} \\ % & \includegraphics[]{Figures/OUFilt_s7_b10} \\
+		\includegraphics[]{Figures/OUSubs_s10} & \includegraphics[]{Figures/OUFilt_s10_b1}  & \includegraphics[]{Figures/OUFilt_s10_b5} % & \includegraphics[]{Figures/OUFilt_s10_b10}
+	\end{tabular}
+	\caption{Results for the Ornstein--Uhlenbeck process.
+The axis of abscissae $\zeta$ represents the value of $\delta = \epl^\zeta$ for both subsampling and the filter.
+The three rows correspond to $\sigma = 0.5, 0.7, 1.0$ from top to bottom.}
+	\label{fig:OU}
+\end{figure}
+We consider $N = 1$ and the quadratic potential $V(x) = x^2/2$.
+In this case, the solution of the homogenized equation is an Ornstein--Uhlenbeck process.
+Moreover, we set the multiscale equation \eqref{eq:SDE_MS} with $\epl = 0.1$ and the fast potential $p(y) = \cos(y)$.
+We generate data $X^\epl$ for $0 \leq t \leq T$ and $T = 10^3$ employing the Euler--Maruyama method with time step $\Delta_t = \epl^3$.
+
+As a first experiment, we consider the effect of setting different values of the parameter $\delta$ of the filter \eqref{eq:filter} on the estimator.
+As a comparison and for similarity with the subsampling approach, we consider $\delta = \epl^{\zeta}$ and vary $\zeta \in [0, 1]$.
+We employ the same values of $\delta$ for the subsampling, too, as the theoretical results guarantee convergence only for these values.
+Moreover, we repeat the experiments fixing $\beta = 1, 5$ and for three different values of the diffusion, i.e., we choose $\sigma = 0.5, 0.7, 1$.
+We report in Figure \ref{fig:OU} the experimental results.
+Let us remark that
+\begin{enumerate}
+	\item for $\sigma = 0.5$ the results given by subsampling and by the filter with $\beta = 1$ are similar, while for higher values of $\sigma$ the filtering approach seems better than subsampling, 
+	\item in general, choosing a higher value of $\beta$ seems beneficial for the quality of the estimator,
+	\item the dependence on $\delta$ of numerical results given by the filter seems relevant only in case $\beta = 1$ and for small values of $\sigma$.
+For $\beta = 1$ and higher values of $\sigma$, the estimator is stable with respect to this parameter, as predicted in Theorem \ref{thm:mainTheorem}.
+This can be observed for a higher value of $\beta$ but we have no theoretical guarantee in this case.
+\end{enumerate}
+
+As a second experiment, we therefore test the variability of the estimator with respect to $\beta$ in \eqref{eq:filter}.
+We repeat the numerical experiment in Figure \ref{fig:OU} and we choose to consider $\delta = \epl$, which corresponds to $\zeta = 1$ and seems to be the worst-case scenario for the filter, at least for $\beta = 1$.
+We consider again $\sigma = 0.5, 0.7, 1$ and vary $\beta = 1, 2, \ldots, 10$.
+Results, given in Figure \ref{fig:OUBeta}, show empirically that the estimator is fast stable with respect to $\beta$.
+
+\begin{figure}[t]
+	\centering
+	\begin{tabular}{ccc}
+		\includegraphics[]{Figures/OUBeta_s5} & \includegraphics[]{Figures/OUBeta_s7}  & \includegraphics[]{Figures/OUBeta_s10} \\
+	\end{tabular}
+	\caption{Dependence of the estimator given by the filter for the Ornstein--Uhlenbeck process on the parameter $\beta$ in \eqref{eq:filter}.
+From left to right we consider different values of $\sigma$.}
+	\label{fig:OUBeta}
+\end{figure}
+
+\subsection{The Bayesian approach: bistable potential}
+\begin{figure}[t]
+	\centering
+	\begin{tabular}{ccc}
+		\includegraphics[]{Figures/Bayes_T200} & \includegraphics[]{Figures/Bayes_T400}  & \includegraphics[]{Figures/Bayes_T800} \\
+	\end{tabular}
+	\caption{Posterior distributions over the parameter $A = (A_1, A_2)^\top$ for the bistable potential obtained with the filtering approach.
+The figures refer to time $t = 200, 400, 800$ from left to right, respectively.
+The MLE $\widehat A$ is represented with a circle, while the true value $A$ of the drift coefficient of the homogenized equation is represented with a cross.}
+	\label{fig:Bayes}
+\end{figure}
+
+In this numerical experiment we consider $N = 2$ and the bistable potential, i.e., the function $V$ defined as
+\begin{equation}
+	V(x) = \begin{pmatrix} \dfrac{x^4}{4} & \dfrac{x^2}{2} \end{pmatrix}^\top,
+\end{equation}
+with coefficients $\alpha_1 = 1$ and $\alpha_2 = -2$.
+We then consider the multiscale equation with $\sigma = 0.8$, the fast potential $p(y) = \cos(y)$ and $\epl = 0.05$, thus simulating a trajectory $X^\epl$ for time $0 \leq t \leq T$, with $T = 800$.
+We adopt here a Bayesian approach and compute the posterior distribution $\mu(A \mid X^\epl)$ obtained with the filtering approach.
+The filter's parameters are set to $\beta = 1$ and $\delta = \epl^{1/2}$ in \eqref{eq:filter}.
+Let us remark that in order to compute the posterior covariance the diffusion coefficient $\Sigma$ of the homogenized equation has to be known.
+In this case, we pre-compute the value of $\Sigma$ via the coefficient $K$ and the theory of homogenization, but let us remark that $\Sigma$ could be estimated employing the subsampling technique of \cite{PaS07}.
+We stop computations at times $t = 200, 400, 800$ in order to observe the shrinkage of the Gaussian posterior towards the MLE with respect to time.
+In Figure \ref{fig:Bayes}, we observe that the posterior does indeed shrink towards the MLE, which in turn gets progressively closer to the true value of the drift coefficient $A$ of the homogenized equation.
+
+\subsection{Multi-dimensional parameter}
+
+\begin{figure}[t]
+	\centering
+	\begin{tabular}{ccc}
+		\includegraphics[]{Figures/KLNothing} & \includegraphics[]{Figures/KLFilt}  & \includegraphics[]{Figures/KLSubs}
+	\end{tabular}
+	\caption{Results for the four-dimensional parameters. From left to right the potential function estimated with (i) the data itself, (ii) the filter, (iii) subsampled data.}
+	\label{fig:KLStyle}
+\end{figure}
+
+We consider $N = 4$ and the potential function $V(x)$ as in \eqref{eq:Potential} with
+\begin{equation}
+	V_i(x) = \frac{x^{2i}}{2i}, \quad i =1, \ldots, 4,
+\end{equation}
+so that $\alpha \cdot V'(x) = \alpha_1 x + \alpha_2 x^3 + \alpha_3 x^5 + \alpha_4 x^7$, with $\alpha = (-2, -1, 1, 1/2)$.
+We consider $\epl = 0.05$, the fast potential $p(y) = \cos(y)$ and simulate a trajectory of $X^\epl$ for $0 \leq t \leq T$ with $T = 10^3$ employing the Euler--Maruyama method with time step $\Delta_t = \epl^3$.
+We compute the MLE of the drift coefficient $A \in \R^4$ of the homogenized equation \eqref{eq:SDE_HOM} employing
+\begin{enumerate}
+	\item the data $X^\epl$ itself,
+	\item subsampled data with subsampling parameter $\delta = \epl^{2/3}$,
+	\item filtered data $Z^\epl$ computed with $\beta = 1$ and $\delta = 0.2$.
+\end{enumerate}
+In particular, we pick this specific value of $\delta$ for the subsampling following the optimality criterion given in \cite{PaS07}.
+Results, given in Figure \ref{fig:KLStyle}, show that the filter-based estimation captures well the homogenized potential.
 

### 2020-01-28 CalNotes.tex

@@
 \begin{equation}
-	\d Z^\epl_t = k(t,t) X^\epl_t \dd t + \int_0^t \partial_t k(t,s) X^\epl_s \dd s \dd t = \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
+	\d Z^\epl_t = k(0) X^\epl_t \dd t + \int_0^t \partial_t k(t-s) X^\epl_s \dd s \dd t = \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
 \end{equation}
+
+We will treat analytically two different cases. First, the case where the state $X_t^\epl$ is a vector of $\R^d$ and we wish to find the
+
 Considering the processes $X^\epl$ and $Z^\epl$ together, we obtain a system of stochastic differential equations

### 2020-01-29 CalNotes.tex
Bayesian

--- 2020-01-28 CalNotes.tex
@@
 \begin{equation}\label{eq:SDE_MS}
-	\d X_t^\epl = -\alpha \cdot V'(X_t^\epl) \dd t - \frac1\epl p'\left(\frac{X_t^\epl}\epl\right) + \sqrt{2\sigma} \dd W_t,
+	\d X_t^\epl = -\alpha \cdot V'(X_t^\epl) \dd t - \frac1\epl p'\left(\frac{X_t^\epl}\epl\right) \dd t + \sqrt{2\sigma} \dd W_t,
 \end{equation}
@@
 
-\subsection{Failure without pre-processing \corr{rewrite}}
-
-Let us consider a trajectory $X^\epl \defeq (X_t^\epl, 0 \leq t \leq T)$ coming from the multiscale equation \eqref{eq:SDE_MS}, and the corresponding posterior distribution over the parameter $A$, which we denote by $\mu^\epl(A \mid X^\epl)$.
-The following result holds.
-\begin{theorem} Under assumption \ref{as:regularity} and if $T = \epl^{-\gamma}$ for $\gamma > 0$, then the posterior distribution $\mu^\epl(A \mid X^\epl) = \mathcal N(\bar A^\epl_T,  \sigma^2_T)$ satisfies
-	\begin{equation}
-	\begin{aligned}
-	&\lim_{\epl \to 0} \bar A^\epl_T = \alpha, \\
-	&\lim_{\epl \to 0} \sigma^2_T = 0.
-	\end{aligned}
-	\end{equation}
-\end{theorem}
-\begin{proof} Proposition \ref{prop:equiv} guarantees that 
-	\begin{equation}
-	\lim_{\epl \to 0} \abs{\bar A_T - \hat A(X^\epl_{0:T})} = 0,
-	\end{equation}
-	and that $\sigma^2_T \to 0$ for $\epl \to 0$. Moreover, \cite[Theorem 3.4]{PaS07} yields
-	\begin{equation}
-	\lim_{\epl \to 0} \hat A(X^\epl_{0:T}) = \alpha,
-	\end{equation}
-	which completes the proof.
-\end{proof}
-
-The result above implies that the posterior distribution over the drift coefficient concentrates asymptotically on an undesired value.
-
-\subsection{The subsampling approach for point estimates}
-
-\subsection{Outline}
-
-\section{Posterior formal computations}
+\section{The Bayesian setting}\label{sec:Bayesian}
 
@@
 \begin{equation}
-\begin{aligned}
-	\log p(A \mid X) = &-\log Z - T A \cdot h - \frac{T}{2} A \cdot M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
-\end{aligned}
+	\log p(A \mid X) = -\log Z - T A \cdot h - \frac{T}{2} A \cdot M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
 \end{equation}
@@
 
+\section{Failure without pre-processing}
+
+Let us consider a trajectory $X^\epl \defeq (X_t^\epl, 0 \leq t \leq T)$ coming from the multiscale equation \eqref{eq:SDE_MS}, and the corresponding posterior distribution over the parameter $A$, which we denote by $\mu^\epl(A \mid X^\epl)$.
+The following result holds.
+\begin{theorem} Under assumption \ref{as:regularity} and if $T = \epl^{-\gamma}$ for $\gamma > 0$, then the posterior distribution $\mu^\epl(A \mid X^\epl) = \mathcal N(\bar A^\epl_T,  \sigma^2_T)$ satisfies
+	\begin{equation}
+	\begin{aligned}
+	&\lim_{\epl \to 0} \bar A^\epl_T = \alpha, \\
+	&\lim_{\epl \to 0} \sigma^2_T = 0.
+	\end{aligned}
+	\end{equation}
+\end{theorem}
+\begin{proof} Proposition \ref{prop:equiv} guarantees that 
+	\begin{equation}
+	\lim_{\epl \to 0} \abs{\bar A_T - \hat A(X^\epl_{0:T})} = 0,
+	\end{equation}
+	and that $\sigma^2_T \to 0$ for $\epl \to 0$. Moreover, \cite[Theorem 3.4]{PaS07} yields
+	\begin{equation}
+	\lim_{\epl \to 0} \hat A(X^\epl_{0:T}) = \alpha,
+	\end{equation}
+	which completes the proof.
+\end{proof}
+
+The result above implies that the posterior distribution over the drift coefficient concentrates asymptotically on an undesired value.
+
+\subsection{The subsampling approach for point estimates}
+
 \section{A filtering approach}
-
-%Let us consider $N = 1$ and write $A_1 = A$ and $V_1 = V$, respectively.
-The posterior distribution of $A$ given a trajectory $(X_t, 0 \leq t \leq T)$ is in this case a Gaussian $\mathcal N(\bar A_T, \sigma^2_T)$ where
-%\begin{equation}
-%\begin{aligned}
-%	\bar A_T &= \frac{A_0}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t} - \frac{\sigma_0^2\int_0^T  V'(X_t) \dd X_t}{1+\sigma_0^2\int_0^T V'(X_t)^2 \dd t}, \\
-%	\sigma^{-2}_T &= \sigma_0^{-2} + \int_0^T V'(X_t)^2 \dd t.
-%\end{aligned}
-%\end{equation}
-%We will in the following sections analyse the convergence of the posterior, both in case data from the multiscale process is not treated and in case they are pre-processed.
 
@@
 where
-\begin{equation}
+\begin{equation}\label{eq:MandHTilde}
 	\widetilde M = \frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t \qquad \text{and} \qquad \widetilde h = \frac{1}{T} \int_0^T V'(Z^\epl_t) \dd X^\epl_t.
@@
 
-\begin{remark} Let us remark that in the one-dimensional case $N = 1$, the estimator reduces to
+\begin{remark} Let us remark that in the one-dimensional case $N = 1$, the estimator can be written as
 \begin{equation}
@@
 
-\begin{theorem}\label{thm:mainTheorem} Let $\widehat A^\epl(T)$ be defined in \eqref{eq:AHatMixed}. Then, if \corr{Assumptions}, 
+In the one-dimensional case, it is clear that the maximum likelihood estimator based on $X^\epl$ alone, i.e., the quantity
+\begin{equation}
+	\widehat A^\epl(T) = - \frac{\int_0^T V'(X^\epl_t) \dd X^\epl_t}{\int_0^T V'(X^\epl_t)^2 \dd t}.
+\end{equation}
+is well defined for $V(x) \neq 0$. Equivalently, for a $N$-dimensional parameter, a sufficient assumption for the well-posedness of the estimator is to require the symmetric matrix $M$ defined as
+\begin{equation}
+	M = \frac{1}{T} \int_0^T V'(X^\epl_t) \otimes V'(X^\epl_t) \dd t,
+\end{equation}
+to be positive definite. In the following lemma, we
+
+\begin{lemma} The matrix $\widetilde M$ defined in \eqref{eq:MandHTilde} is invertible almost surely. \end{lemma}
+\begin{proof}
+
+\end{proof}
+
+\begin{theorem}\label{thm:mainTheorem} Let $\widehat A^\epl(T)$ be defined in \eqref{eq:AHatMixed}. Then
 	\begin{equation}\label{eq:theoremFirst}
@@
 \subsection{The Bayesian setting}
+
+In this section we show how the filtering approach can be employed in a Bayesian framework.
+As in Section \ref{sec:Bayesian} let us consider a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$.
+Then, the density $p^\epl(A \mid X)$ of the posterior distribution $\mu^\epl(A \mid X^\epl)$ given by multiscale data satisfies
+\begin{equation}
+	p^\epl(A \mid X) = \frac1{Z^\epl} \, p^\epl(X \mid A) \, p_0(A),
+\end{equation}
+where $Z^\epl$ is the normalization term and where the likelihood function is given by
+\begin{equation}
+	p^\epl(X \mid A) = \exp\left(-\frac{I^\epl(X\mid A)}{2\Sigma} \right), 
+\end{equation}
+with
+\begin{equation}
+	I^\epl(X\mid A) = \int_0^T A \cdot V'(X_t^\epl) \dd X_t^\epl + \frac12 \int_0^T \left( A \cdot V'(X_t^\epl) \right)^2 \dd t.
+\end{equation}
+Let us consider the likelihood function $\widetilde p^\epl(X \mid A)$ modified to include the filtered data $Z^\epl$ given by
+\begin{equation}
+	\widetilde p^\epl(X \mid A) = \exp\left(-\frac{\widetilde I^\epl(X\mid A)}{2\Sigma} \right), 
+\end{equation}
+with
+\begin{equation}
+	\widetilde I^\epl(X\mid A) = \int_0^T A \cdot V'(Z_t^\epl) \dd X_t^\epl + \frac12 \int_0^T \left( A \cdot V'(X_t^\epl) \right) \left( A \cdot V'(Z_t^\epl) \right) \dd t.
+\end{equation}
+Moreover, let us consider the modified posterior distribution $\widetilde \mu^\epl(A \mid X)$ with density
+\begin{equation}
+	\widetilde p^\epl(A \mid X) = \frac1{\widetilde Z^\epl} \, \widetilde p^\epl(X \mid A) \, p_0(A),
+\end{equation}
+Let us remark that employing \eqref{eq:MandHTilde} we can write 
+\begin{equation}
+	\log \widetilde p^\epl(A \mid X) = -\log \widetilde Z^\epl - T A \cdot \widetilde h - \frac{T}{2} A \cdot \widetilde M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
+\end{equation}
+With respect to Section \ref{sec:Bayesian}, the matrix $\widetilde M$ is not symmetric. Nonetheless, we remark that
+\begin{equation}
+	A \cdot \widetilde M A = A \cdot \widetilde M_S A,
+\end{equation}
+where $\widetilde M_S$ is the symmetric part of $\widetilde M$, i.e.,
+\begin{equation}
+	\widetilde M_S = \frac12 \left(\widetilde M + \widetilde M^\top\right).
+\end{equation}
+Hence, we can rewrite 
+\begin{equation}	
+	\log \widetilde p^\epl(A \mid X) = -\log \widetilde Z^\epl - T A \cdot \widetilde h - \frac{T}{2} A \cdot \widetilde M_S A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
+\end{equation}
+This shows that the posterior $\widetilde \mu^\epl$ is a Gaussian $\mathcal N(\widetilde m_T, \widetilde C_T)$ where the covariance and mean can be obtained as 
+\begin{equation}
+\begin{aligned}
+	\widetilde C_T^{-1} &= C_0^{-1} + T \widetilde M, \\
+	\widetilde C_T^{-1} \widetilde m_T &= C_0^{-1}A_0 - T \widetilde h. 
+\end{aligned}
+\end{equation}
+
+In the following theorem we show that the posterior we obtain 
+\begin{theorem} Under
+\end{theorem}
 

### 2020-02-10 CalNotes.tex
Update after visit to ICL

@@
 
-\corr{Add motivating introduction.}
-In \cite{PaS07} (\corr{is there other literature?}), the authors prove that inference of the parameters of a homogenized model has to be performed carefully.
-In this work, the analysis contained in \cite{PaS07} is widened with respect to the following aspects:
-\begin{enumerate}[label=\arabic*)]
-	\item a more general form of the drift function is considered, thus allowing a more flexible framework for applications and hinting possible extensions to the infinite-dimensional case,
-	\item the inference procedure is reinterpreted from a Bayesian perspective, which guarantees more complete uncertainty quantification on the inference result.
-Moreover, given the nature of the problem, posterior distributions follow a Gaussian law which can be analytically determined, thus guaranteeing computationally fast inference,
-	\item we extend the sub-sampling technique introduced in \cite{PaS07}, which can be applied to discrete sequences, by introducing theoretical tools which allow the treatment of continuous streams of data.
+Data-driven approaches to the derivation of effective stochastic coarse-grained dynamics has become a standard tool in different areas such as molecular dynamics (CITE) or atmosphere and ocean science \cite{KKP15,CoP09,YMV19}.
+When fitting data to a low dimensional coarse-grained model, one is faced with the problem of model misspecification; indeed, the data, coming from the full dynamics, is compatible with the coarse-grained model only at the time scales at which the effective dynamics is valid.
+This is related to the issue of high frequency data that is arises in econometrics \cite{AiJ14,AMZ05,ZMA05,OSP10}.
+
+The issue of model misspecification in inverse problems with a multiscale structure has been treated in the context of partial differential equations (PDE).
+In particular, it has been shown that it is possible to infer a coarse-grained equation from data coming from the full model and to retrieve asymptotically the correct result \cite{NPS12}.
+A series of papers \cite{AbD18, AbD19, AGZ19} focuses on retrieving the full model when the multiscale coefficient is endowed with a specific parametrized structure.
+Being these problems ill-posed, the latter is achieved via Tikhonov regularization \cite{AbD19,NPS12}, adopting a Bayesian approach \cite{AbD18, NPS12} or exploiting techniques of Kalman filtering \cite{AGZ19}.
+In \cite{AbD18,AGZ19}, the authors highlight the need of accounting explicitly for the modelling error due to homogenisation and apply statistical techniques taken from \cite{CDS18,CES14}.
+
+For simple models in molecular dynamics, the effect of model misspecification was studied in a series of papers \cite{PaS07,PPS09,PPS12,GaS17,GaS18} under the assumption of scale separation.
+In particular, for Brownian particles moving in two-scale potentials it was shown that, when fitting data from the full dynamics to the homogenised equation, the maximum likelihood estimator (MLE) is asymptotically biased \cite[Theorem 3.4]{PaS07}.
+To be more precise, in the large sample size limit the MLE converges to the coefficients of the unhomogenised equation, rather than to those of the homogenised one.
+The bias of the MLE estimator can be eliminated by subsampling at an appropriate rate, which lies between the two characteristic time scales of the problem \cite[Theorems 3.5 and 3.6]{PaS07}.
+This is similar to the estimation of the integrated stochastic volatility in the presence of market micro-structure noise, where the data has to be subsampled at an appropriate rate \cite{AMZ05,ZMA05}.
+The correct subsampling rate can be in some instances rather extreme with respect to the frequency of the data and lead to get rid of more than $99\%$ of the data.
+As the intuition suggests, this increases significantly the bias of the estimator, which is usually taken care of with additional bias corrections and variance reduction procedures.
+
+The necessity to subsample the data can be alleviated by using appropriate martingale estimators, as was done in \cite{KPK13,KKP15}.
+This class of estimators can be applied to the case where the noise is multiplicative and also given by a deterministic chaotic system, as opposed to white noise.
+Estimators of this family have been applied to time series from paleoclimatic data and marine biology and augmented with appropriate model selection methodologies \cite{KPP15}.
+
+In this paper, we bypass the issue of subsampling by implementing an appropriate filtering methodology.
+In particular, we show that smoothing the data coming from the multiscale model with an appropriate linear time-invariant filter of the exponential family allows to retrieve the drift coefficient of the homogenized equation.
+The methodology we present is not involved computationally, easy to implement in practice and presents two main advantages:
+\begin{enumerate}
+	\item the filter's kernel depends on two parameters which can be tuned to obtain more robust results and which can be interpreted as analogous to the subsampling rate.
+Nevertheless, while the MLE is extremely sensitive with respect to the latter, changing the filter parameters does not have a strong influence on the result, therefore allowing our technique to be applied as a black-box tool for parameter estimation,
+	\item the entire stream of data is employed, which, in practice, enhances the quality of the filter-based MLE in terms of bias.
+Moreover, avoiding subsampling and thus discretising the data allows us to employ continuous-time theoretical tools.
 \end{enumerate}
+
+It is natural to reinterpret the problem of inferring the drift parameter of multiscale diffusion processes under a Bayesian perspective \cite{PSV09,PSZ13}.
+In particular, the form of the likelihood function guarantees, under a Gaussian prior hypothesis, that the posterior distribution is itself a Gaussian.
+Therefore, one can simply compute the mean and covariance of the posterior distribution to obtain a full quantification of the inference process.
+The Bayesian approach has been adopted in several works concerning single and multiscale PDEs, too, and has proved itself to be versatile and efficient in this framework (see, e.g., \cite{AbD18, AGZ19}).
+Moreover, infinite-dimensional inverse problems are intrinsically ill-posed, and interpreting them in a Bayesian manner is an efficient tool for regularizing them and guaranteeing their well-posedness \cite{Stu10, DaS16}.
+The regularization property of a Bayesian approach has been recently demonstrated for inverse problems involving multiscale PDE \cite{AbD18}.
+In this work, we investigate the effects of inserting our filtering methodology in a Bayesian framework.
+In particular, we analyse the effects of modifying the likelihood function inserting the filtered trajectory, showing how this corrects the faulty asymptotic behaviour which would be present in case no pre-processing would be applied.
+
+\subsection{Outline}
+
+The rest of the paper is organised as follows.
+In Section \ref{sec:Setting} we introduce the problem and lay the basis of our analysis setting the main assumptions and notation.
+In Section \ref{sec:Filter} we present our filtering methodology, with a particular focus on ergodic properties, on multiscale convergence and, naturally, to the properties of our estimator.
+In Section \ref{sec:Bayesian} we introduce the Bayesian framework and show how it can be enhanced with filtering techniques.
+Finally, in Section \ref{sec:NumExp} we demonstrate the effectiveness of our methodology via a series of numerical experiments.
+
+\section{Problem setting}\label{sec:Setting}
 
@@
 
-\section{The Bayesian setting}\label{sec:Bayesian}
-
-In a Bayesian setting, the goal is to determine the posterior distribution $\mu(A \mid X)$ given a continuous trajectory $X \defeq (X_t, 0 \leq t \leq T)$.
-Choosing a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$ on $A$, where $A_0 \in \R^N$ and $C_0 \in \R^{N\times N}$ is symmetric positive definite, the posterior distribution admits a density $p(A \mid X)$ with respect to the Lebesgue measure which satisfies
+Let $T > 0$ and let $X^\epl \defeq (X^\epl_t, 0\leq t, \leq T)$ be a realization of the solution of \eqref{eq:SDE_MS} up to final time.
+In order to estimate the drift coefficient $A$ of the homogenized equation we maximize the likelihood function
 \begin{equation}
-	p(A \mid X) = \frac1Z \, p(X \mid A) \, p_0(A),
+p(X^\epl \mid A) = \exp\left(-\frac{I(X^\epl\mid A)}{2\Sigma} \right), 
 \end{equation}
-where $Z$ is the normalization constant, $p_0$ is the density of $\mu_0$, and where Girsanov's formula allows to write the likelihood as
+where Girsanov formula allows to write explicitly the log-likelihood as
 \begin{equation}
-	p(X \mid A) = \exp\left(-\frac{I(X\mid A)}{2\Sigma} \right), 
+I(X^\epl \mid A) = \int_0^T A \cdot V'(X^\epl_t) \dd X^\epl_t + \frac12 \int_0^T \left( A \cdot V'(X^\epl_t) \right)^2 \dd t.
 \end{equation}
-with
+Therefore, the maximum likelihood estimator can be formally computed in closed form as
 \begin{equation}
-	I(X\mid A) = \int_0^T A \cdot V'(X_t) \dd X_t + \frac12 \int_0^T \left( A \cdot V'(X_t) \right)^2 \dd t.
+	\widehat A^\epl(T) \defeq \arg \min_{A \in \R^N} I(X^\epl \mid A) = M^{-1}h,
 \end{equation}
-
-The log-posterior density is then given by
-\begin{equation}
-\begin{aligned}
-	\log p(A \mid X) = &-\log Z -\frac1{2\Sigma}\int_0^T A \cdot V'(X_t) \dd X_t - \frac1{4\Sigma} \int_0^T \left(A \cdot V'(X_t) \right)^2 \dd t \\
-	&- \frac12 \norm{C_0^{-1/2}(A - A_0)}_2^2.
-\end{aligned}
-\end{equation}
-Since the log-posterior density is quadratic in $A$, the posterior is Gaussian, and it is therefore sufficient to determine its mean and covariance to fully characterize it.
-We denote by $m_T$ and $C_T$ the mean and covariance matrix, respectively.
-Let us consider the matrix-valued function $M \colon \R \to \R^{N\times N}$ whose entries are given by
-\begin{equation}
-	M_{ij} = \frac1{2\Sigma T} \int_0^T V_i'(X_t) \, V_j'(X_t) \dd t, \quad i, j = 1, \ldots, N,
-\end{equation}
-and the vector-valued function $h \colon \R \to \R^N$ defined by
-\begin{equation}
-	h_i = \frac1{2\Sigma T} \int_0^T V_i'(X_t) \dd X_t, \quad i = 1, \ldots, N.
-\end{equation}
-Let us remark that we can rewrite $M$ and $h$ in vector notation as
+where $M\in\R^{N\times N}$ and $h\in\R^N$ are defined as
 \begin{equation}
@@
 \end{equation}
-where $\otimes$ denotes the tensor product in $\R^N$. Therefore, we can rewrite the log-posterior density as
+and where $\otimes$ denotes the tensor product in $\R^N$.
+Let us now state the assumptions which will be employed throughout the rest of our work. In particular, we consider the dissipative setting of \cite{PaS07}.
+\begin{assumption}\label{as:regularity} The potentials $p$ and $V$ satisfy
+	\begin{enumerate}
+		\item $p \in \mathcal C^\infty(\R, \R) \cap L^\infty(\R, \R)$,
+		\item\label{as:regularity_diss} the potential $V \in \mathcal C^\infty(\R, \R)$ and there exist $a,b > 0$ such that
 		\begin{equation}
-	\log p(A \mid X) = -\log Z - T A \cdot h - \frac{T}{2} A \cdot M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
+		-V'(x)x \leq a - bx^2.
 		\end{equation} 
-Completing the squares in the log-posterior density, it is possible to show that the posterior is a Gaussian $\mu(A \mid X) = \mathcal N(m_T, C_T)$, whose precision matrix and mean are formally given by
-\begin{equation}
-\begin{aligned}
-	C_T^{-1} &= C_0^{-1} + T M, \\
-	C_T^{-1}m_T &= C_0^{-1}A_0 - T h. 
-\end{aligned}
-\end{equation}
-We are now interested in the limit of the posterior distribution for $T \to \infty$.
-Let us first define the maximum likelihood estimator (MLE) $\widehat A(X)$ of $A$, which is obtained by maximizing the log-likelihood function $\log p(X \mid A)$, and which is hence formally given by
-\begin{equation}
-	\widehat A(X) = -M^{-1}h.
-\end{equation}
-We now introduce regularity assumptions on the SDE.
-\begin{assumption}\label{as:regularity} The potentials $p$ and $V$ are such that 
-	\begin{enumerate}
-		\item for all $T > 0$, the symmetric matrix $M$ is positive definite and its minimum eigenvalue satisfies $\lambda_{\min}(M) \geq \bar \lambda > 0$,
-		\item 	\corr{other assumptions to be added}
+		Moreover, for all $T > 0$, the symmetric matrix $M$ is positive definite and its minimum eigenvalue satisfies $\lambda_{\min}(M) \geq \bar \lambda > 0$.
 	\end{enumerate}
 \end{assumption}
+Under these assumptions, the estimator $\widehat A^\epl(T)$ is indeed well-posed. Moreover, these assumptions guarantee that the process $X^\epl$ is geometrically ergodic, and
 
-We can now state the main result for asymptotic convergence of the posterior distribution.
-\begin{proposition}\label{prop:equiv} Given a continuous stochastic process $X \defeq (X_t, 0 \leq t, \leq T)$ which is ergodic with invariant measure $\mu^{\infty}$ such that $\E^{\mu^\infty}(V_i'(\cdot)) \leq C$ for some constant $C > 0$ and for all $i = 1, \ldots, N$, the posterior $\mu(A \mid X)$ contracts to the limit of $\widehat A(X)$ for $T \to \infty$.
-%	 for $T$ arbitrarily large and under Assumption \ref{as:regularity}, the posterior mean and covariance satisfy
-%	\begin{equation}
-%	\begin{aligned}
-%		&\lim_{T \to \infty} \norm{m_T - \widehat A(X)}_2 = 0, \\
-%		&\lim_{T \to \infty} \norm{C_T}_F = 0,
-%	\end{aligned}
-%	\end{equation}
-%	i.e., the posterior tends in distribution to the Dirac delta centred in the limit of the MLE.
-\end{proposition}
-\begin{proof} Let us first consider the covariance matrix. Hua's identity yields
-	\begin{equation}
-		C_T = T^{-1} \left(M^{-1} - Q^{-1}\right),
-	\end{equation}
-	where 
-	\begin{equation}
-		Q = M + T M C_0 M.
-	\end{equation}
-	The eigenvalues of $Q$ satisfy for all $i = 1, \ldots, N$
-	\begin{equation}
-		\lambda_i(Q) = \lambda_i(M) + T \lambda_i(M C_0 M) \geq \bar \lambda + T \lambda_{\min}(C_0),
-	\end{equation}
-	and therefore we obtain
-	\begin{equation}\label{eq:boundQinv}
-		\lambda_{\max}(Q^{-1}) \leq \frac{1}{\bar \lambda + T \lambda_{\min}(C_0)}.
-	\end{equation}
-	Similarly, we have a bound for the maximum eigenvalue of $M^{-1}$ given by
-	\begin{equation}\label{eq:boundMinv}
-		\lambda_{\max}(M^{-1}) \leq \frac1{\bar{\lambda}},
-	\end{equation}
-	which implies that
-	\begin{equation}
-		\trace{C_T} \leq \frac{N}{T} \left(\frac1{\bar{\lambda}} + \frac{1}{\bar \lambda + T \lambda_{\min}(C_0)}\right),
-	\end{equation}
-	and which therefore allows us to conclude that
-	\begin{equation}
-		\lim_{T\to\infty} \norm{C_T}_F = 0.
-	\end{equation}
-	We now consider the mean. Replacing the expression of the maximum likelihood estimator, we obtain
-	\begin{equation}
-		\norm{m_T - \widehat A(X)}_2 = T^{-1}\norm{M^{-1}C_0^{-1}A_0 - Q^{-1}\left(C_0^{-1}A_0 - Th \right)}_2.
-	\end{equation}
-	Let us remark that \eqref{eq:boundQinv} implies $\norm{Q^{-1}}_F \to 0$ for $T \to \infty$ and \eqref{eq:boundMinv} implies $\norm{M^{-1}}_F \leq C$ for some $C > 0$ independently of $T$.
-Moreover, the ergodic theorem guarantees that $\norm{h}_2 \leq C$ for $T$ sufficiently big, and therefore the Cauchy--Schwarz and the triangle inequalities imply
-	\begin{equation}
-		\lim_{T\to\infty} \norm{m_T - \widehat A(X)}_2 = 0,
-	\end{equation}
-	which proves the desired result.
-\end{proof}
-
-\begin{remark} Proposition \ref{prop:equiv} guarantees that in the asymptotic limit of $T \to \infty$, it is equivalent to consider the Bayesian approach and the maximum likelihood approach, and can therefore be interpreted as a consistency result for both approaches.
-Nonetheless, in this Gaussian framework the Bayesian approach provides richer information on the inference result with a negligible additional cost.
-\end{remark}
-
-\section{Failure without pre-processing}
-
-Let us consider a trajectory $X^\epl \defeq (X_t^\epl, 0 \leq t \leq T)$ coming from the multiscale equation \eqref{eq:SDE_MS}, and the corresponding posterior distribution over the parameter $A$, which we denote by $\mu^\epl(A \mid X^\epl)$.
-The following result holds.
-\begin{theorem} Under assumption \ref{as:regularity} and if $T = \epl^{-\gamma}$ for $\gamma > 0$, then the posterior distribution $\mu^\epl(A \mid X^\epl) = \mathcal N(\bar A^\epl_T,  \sigma^2_T)$ satisfies
-	\begin{equation}
-	\begin{aligned}
-	&\lim_{\epl \to 0} \bar A^\epl_T = \alpha, \\
-	&\lim_{\epl \to 0} \sigma^2_T = 0.
-	\end{aligned}
-	\end{equation}
-\end{theorem}
-\begin{proof} Proposition \ref{prop:equiv} guarantees that 
-	\begin{equation}
-	\lim_{\epl \to 0} \abs{\bar A_T - \hat A(X^\epl_{0:T})} = 0,
-	\end{equation}
-	and that $\sigma^2_T \to 0$ for $\epl \to 0$. Moreover, \cite[Theorem 3.4]{PaS07} yields
-	\begin{equation}
-	\lim_{\epl \to 0} \hat A(X^\epl_{0:T}) = \alpha,
-	\end{equation}
-	which completes the proof.
-\end{proof}
-
-The result above implies that the posterior distribution over the drift coefficient concentrates asymptotically on an undesired value.
-
-\subsection{The subsampling approach for point estimates}
-
-\section{A filtering approach}
+\section{The filtering approach}\label{sec:Filter}
 
@@
 In the following, we consider the filter with $\beta = 1$, i.e.,
-\begin{equation}
+\begin{equation}\label{eq:filter_beta1}
 	k(t,s) = \frac{1}{\delta} e^{-\frac{t-s}{\delta}},
@@
 \begin{equation}
-\label{systemSDE}
+\label{eq:systemSDE}
 \begin{aligned}
@@
 \end{equation}
-Let $\rho^\epl = \rho^\epl(x,z)$ be the stationary distribution of the joint process $(X^\epl, Z^\epl)^\top$.
-\corr{How do we show that the couple $(X^\epl, Z^\epl)^\top$ is ergodic.} Then $\rho^\epl$ is the solution of the two-dimensional stationary Fokker--Planck equation
+The following result guarantees that the measure induced by the joint process $(X_t^\epl, Z_t^\epl)^\top$ admits a smooth density.
+
+\begin{lemma}\label{lem:density} Let $(X_t^\epl, Z_t^\epl)^\top$ be the solution of \eqref{eq:systemSDE}.
+Then the measure $\mu^\epl$ of the process admits a smooth density $\rho^\epl$ with respect to the Lebesgue measure.
+%	 satisfying
+%	\begin{equation}
+%	\begin{aligned}
+%	\partial_t\rho^\epl(t,x,z) -\sigma \partial^2_{xx} \rho^\epl(t,x,z) &- \partial_x \left(\left ( \alpha \cdot V'(x) + \frac{1}\epl p' \left ( \frac{x}\epl \right ) \right )\rho^\epl(t,x,z)\right) \\
+%	&- \frac{1}{\delta}\partial_z\left((z - x) \rho^\epl(t,x,z)\right) = 0.
+%	\end{aligned}
+%	\end{equation} 
+\end{lemma}
+
+\begin{proof} We have to show that the joint process solution to \eqref{eq:systemSDE} is hypo-elliptic. Let us define the function $f\colon \R \to \R$ as 
+	\begin{equation}
+		f(x) = -\alpha \cdot V'(x) - \frac1\epl p'\left(\frac{x}\epl\right).
+	\end{equation}
+	Then, the generator of the process $(X_t^\epl, Z_t^\epl)^\top$ is given by
+	\begin{equation}
+		\mathcal L = f \partial_x + \sigma \partial_{xx}^2 + \frac1\delta (x - z)\partial_z \eqdef \mathcal X_0 + \sigma \mathcal X_1^2, 
+	\end{equation}
+	where 
+	\begin{equation}
+		\mathcal X_0 = f \partial_x + \frac1\delta (x - z)\partial_z, \quad \mathcal X_1 = \partial_x.
+	\end{equation}
+	The commutator $[\mathcal X_0, \mathcal X_1]$ applied to a test function $v$ then gives
 	\begin{equation}
 	\begin{aligned}
-	\label{eq:FPsystem}
-	\sigma \partial^2_{xx} \rho^\epl(x,z) & + \left ( \alpha \cdot V''(x) + \frac{1}{\epl^2} p'' \left ( \frac{x}\epl \right ) + \frac{1}{\delta} \right ) \rho^\epl(x,z) \\
-	& + \left ( \alpha \cdot V'(x) + \frac{1}\epl p' \left ( \frac{x}\epl \right ) \right ) \partial_x \rho^\epl(x,z) + \frac{1}{\delta}(z - x) \partial_z \rho^\epl(x,z) = 0.
+		[\mathcal X_0, \mathcal X_1]v &= f \partial_x^2 v + \frac1\delta (x - z) \partial_x \partial_z v  - \partial_x\left(f\partial_x v + \frac1\delta (x - z)\partial_z v\right)\\
+		&= -\partial_x f \partial_x v - \frac1\delta \partial_z v.
 	\end{aligned}
 	\end{equation}
+	Consequently, 
+	\begin{equation}
+		\mathrm{Lie}\left(\mathcal X_1, [\mathcal X_0, \mathcal X_1]\right) = \mathrm{Lie} \left(\partial_x, -\partial_x f \partial_x - \frac1\delta\partial_z\right),
+	\end{equation}
+	which spans $T_x\R^2$. The desired result then follows from Hörmander's theorem (see e.g. \cite[Chapter 6]{Pav14}).
+\end{proof}
+
+Having established that the law of the joint process admits a smooth density with respect to the Lebesgue measure, we now show in the following Lemma a property of ergodicity.
+
+\begin{lemma}\label{lem:ergodicity} Let Assumption \ref{as:regularity} hold and let $b > 0$ be given in Assumption \ref{as:regularity}\ref{as:regularity_diss}.
+Then, if $\delta > 1/(4b)$, the process $(X_t^\epl, Z_t^\epl)^\top$ solution of \eqref{eq:systemSDE} is geometrically ergodic, i.e., there exists $C, \lambda > 0$ such that for all measurable $f$ such that for some integer $p > 0$
+	\begin{equation}
+		f(x) \leq 1 + \abs{x}^p,
+	\end{equation}
+	it holds
+	\begin{equation}
+		\abs{\E f(X^\epl_t, Z^\epl_t) - \int_\R\int_\R f(x, z) \rho^\epl(x, z) \dd x \dd z} \leq C\left(1 + \norm{\begin{pmatrix} X^\epl_0 \\ Z^\epl_0 \end{pmatrix}}^p \right)e^{-\lambda t},
+	\end{equation}
+	where $\rho^\epl$ is the solution to the stationary Fokker--Planck equation
+	\begin{equation}
+	\label{eq:FPsystem}
+	\sigma \partial^2_{xx} \rho^\epl(x,z) +  \partial_x \left( \left( \alpha \cdot V'(x) + \frac{1}{\epl} p' \left ( \frac{x}\epl \right ) \right ) \rho^\epl(x,z) \right) + \frac{1}{\delta} \partial_z \left((z - x) \rho^\epl(x,z)\right) = 0.
+	\end{equation}
+\end{lemma}
+
+\begin{proof} Lemma \ref{lem:density} guarantees that the Fokker--Planck equation can be written directly from the system \eqref{eq:systemSDE}. For geometric ergodicity, let 
+\begin{equation}
+	 \mathcal S(x,z) \defeq \begin{pmatrix} -V'(x) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} = -V'(x)x+\frac1\delta(xz-z^2)
+\end{equation}
+Due to Assumption \ref{as:regularity}\ref{as:regularity_diss} and Young's inequality, we then have for all $\gamma > 0$
+\begin{equation}
+	\mathcal S(x,z) \leq a + \left(\frac{1}{2\gamma\delta} - b\right)x^2 + \frac1\delta\left(\frac{\gamma}{2} - 1\right)z^2.
+\end{equation}
+We choose $\gamma = \gamma^* \defeq 1 - b\delta + \sqrt{2-2b\delta+b^2\delta^2} > 0$ so that
+\begin{equation}
+	C(\gamma^*) \defeq -\frac{1}{2\gamma^*\delta} + b = -\frac1\delta\left(\frac{\gamma^*}{2} - 1\right),
+\end{equation}
+and we notice that $C(\gamma^*) > 0$ if $\delta > 1/(4b)$. In this case, we have
+\begin{equation}
+	\mathcal S(x, z) \leq a - C(\gamma^*) \norm{\begin{pmatrix} x \\ z \end{pmatrix}}^2,
+\end{equation}
+and problem \eqref{eq:systemSDE} is dissipative. The result then follows from \cite[Theorem 4.4]{MSH02}.
+\end{proof}
+
+\begin{remark} Let us remark that for the multiscale equation \eqref{eq:SDE_MS} one should check the condition above for the drift function $V(x) + \epl^{-1}p(x/\epl)$.
+Nevertheless, being $p$ bounded, the result holds trivially.
+\end{remark}
 
@@
 
-\begin{lemma}\label{lem:FPMarginal} Let $\rho^\epl$ be the \corr{unique solution} of \eqref{eq:FPsystem} and let us write 
+\begin{lemma}\label{lem:FPMarginal} Let $\rho^\epl$ be the solution of \eqref{eq:FPsystem} and let us write 
 \begin{equation}\label{eq:densityDecomposition}
@@
 
-\subsubsection{Convergence of the invariant measure}\label{sec:convMeasure}
+\subsection{Multiscale convergence}\label{sec:convMS}
+
+We now investigate the convergence of the couple $(X_t^\epl, Z_t^\epl)^\top$ with respect to the multiscale parameter $\epl \to 0$.
+\corr{Rewrite the following two lemmas with considerations from discussion with Greg: maybe one lemma is enough and clearer.}
+
+\begin{lemma}\label{lem:convMS} Let $T > 0$.
+Then, the couple $(X^\epl, Z^\epl)^\top \defeq \left((X_t^\epl, Z_t^\epl)^\top, 0\leq t \leq T\right)$ converges in law for $\epl \to 0$ in $\mathcal C^0((0, T), \R^2)$ to the couple $ (X, Z)^\top \defeq \left((X_t, Z_t)^\top, 0\leq t \leq T\right)$ solution to
+	\begin{equation}
+	\label{eq:systemSDEHom}
+	\begin{aligned}
+		\d X_t &= -A \cdot V'(X_t) \dd t + \sqrt{2\Sigma} \dd W_t, \\
+		\d Z_t &= \frac{1}{\delta} \left ( X_t - Z_t \right ) \dd t,
+	\end{aligned}
+	\end{equation}
+	where $A\in \R^N$ and $\Sigma > 0$ are the coefficients of \eqref{eq:SDE_HOM}.
+\end{lemma}
+\begin{proof} Standard homogenization theory (see e.g. \cite[Chapter 3]{BLP78}) can be employed, and therefore the proof is omitted here.
+\end{proof}
 
 It is known that the invariant distribution of the process $X^\epl$ converges weakly to the invariant distribution of the process $X^0$ solution to \eqref{eq:SDE_HOM}.
-We now consider the random variable $(X^\epl, Z^\epl)^\top$ and present an analogous convergence result for the couple.
+We now consider the random variable $(X^\epl, Z^\epl)^\top$ and present an analogous convergence result for the joint process.
 
-\begin{lemma}\label{lem:convMeasure} Let $\mu^\epl$ be the invariant measure of the couple $(X^\epl, Z^\epl)^\top$.
+\begin{lemma}\label{lem:convMeasure} Let $\mu^\epl$ be the invariant measure of the couple $(X^\epl, Z^\epl)^\top$ and let $(X_0^\epl, Z_0^\epl)^\top \sim \mu^\epl$.
 Then, the measure $\mu^\epl$ converges weakly to the measure $\mu^0(\d x, \d z) = \rho^0(x, z) \dd x \dd z$, whose density $\rho^0$ is the unique solution of the Fokker--Planck equation
@@
 \end{lemma}
-\begin{proof} \todo
+\begin{proof} Lemma \ref{lem:convMS}, together with the assumption that the joint process has an initial condition distributed as the invariant measures, guarantees via the Portmanteau theorem the weak convergence of $\mu^\epl$ to $\mu^0$.
 \end{proof}
 
-We now present an analogous result to Lemma \ref{lem:FPMarginal} for the limit distribution.
+We conclude this section presenting an analogous result to Lemma \ref{lem:FPMarginal} for the limit distribution.
 
-\begin{corollary}\label{lem:FPMarginal_Hom} Let $\rho^0$ be the \corr{unique solution} of \eqref{eq:FPsystem_homogenized} and let us write 
+\begin{corollary}\label{lem:FPMarginal_Hom} Let $\rho^0$ be the solution of \eqref{eq:FPsystem_homogenized} and let us write 
 	\begin{equation}
@@
 
-\subsection{The estimator}
+\subsection{The modified estimator}
 
@@
 \end{equation}
-to be positive definite. In the following lemma, we
+to be positive definite. In the following lemma, we ensure that the estimator based on the filtering method is well-defined.
 
-\begin{lemma} The matrix $\widetilde M$ defined in \eqref{eq:MandHTilde} is invertible almost surely. \end{lemma}
+\begin{lemma} The matrix $\widetilde M$ defined in \eqref{eq:MandHTilde} is invertible almost surely. 
+\end{lemma}
 \begin{proof} 
-
+\todo
 \end{proof}
@@
 \begin{equation}\label{eq:Proof_I1}
-\lim_{\epl \to 0} \lim_{T \to \infty} I_1(T) = -\alpha + A, \quad \text{a.s.}
+\lim_{\epl \to 0} \lim_{T \to \infty} I_1^\epl(T) = -\alpha + A, \quad \text{a.s.}
 \end{equation}
-We now consider the second term $I_2$, and rewrite it as (\corr{Still one-dimensional, correct to $N$-dimensional parameter})
+We now consider the second term $I_2^\epl$, and rewrite it as
 \begin{equation}
-	I^\epl_2(T) = - \sqrt{2\sigma} \frac{\frac1T\int_0^T V'(Z^\epl_t)^2 \dd t}{\frac1T\int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t} \frac{\int_0^T V'(Z^\epl_t) \dd W_t}{\int_0^T V'(Z^\epl_t)^2 \dd t} \eqdef -\sqrt{2\sigma} I_{2,1}^\epl(T)  I_{2,2}^\epl(T).
+	I^\epl_2(T) = -\sqrt{2\sigma} I_{2,1}^\epl(T)  I_{2,2}^\epl(T),
+\end{equation}
+where
+\begin{equation}
+\begin{aligned}
+	I_{2,1}^\epl(T) &\defeq \left(\frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\left(\frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t\right),\\
+	I_{2,2}^\epl(T) &\defeq \left(\frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t\right)^{-1}\int_0^T V'(Z^\epl_t) \dd W_t.
+\end{aligned}
 \end{equation}
@@
 \begin{equation}
-	\lim_{T \to \infty} I_{2,1}^\epl(T) = \frac{\E^{\rho^\epl}[V'(Z^\epl)^2]}{\E^{\rho^\epl}[V'(Z^\epl)V'(X^\epl)]} \eqdef M^\epl,
+	\lim_{T \to \infty} I_{2,1}^\epl(T) = \E^{\rho^\epl}\left[V'(Z^\epl) \otimes V'(X^\epl)\right]^{-1}\E^{\rho^\epl}\left[V'(Z^\epl) \otimes V'(Z^\epl)\right] \eqdef M^\epl,
 \end{equation}
-where $M^\epl$ is bounded uniformly in $\epl$. Moreover, \corr{the strong law of large numbers for martingales implies}
+where $M^\epl$ is bounded uniformly in $\epl$. Moreover, the strong law of large numbers for martingales implies
 \begin{equation}
@@
 
-\subsection{The Bayesian setting}
+\section{The Bayesian setting}\label{sec:Bayesian}
 
+In a Bayesian setting, the goal is to determine the posterior distribution $\mu(A \mid X)$ given a continuous trajectory $X \defeq (X_t, 0 \leq t \leq T)$.
+Choosing a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$ on $A$, where $A_0 \in \R^N$ and $C_0 \in \R^{N\times N}$ is symmetric positive definite, the posterior distribution admits a density $p(A \mid X)$ with respect to the Lebesgue measure which satisfies
+\begin{equation}
+p(A \mid X) = \frac1Z \, p(X \mid A) \, p_0(A),
+\end{equation}
+where $Z$ is the normalization constant, $p_0$ is the density of $\mu_0$, and where Girsanov's formula allows to write the likelihood as
+\begin{equation}
+p(X \mid A) = \exp\left(-\frac{I(X\mid A)}{2\Sigma} \right), 
+\end{equation}
+with
+\begin{equation}
+I(X\mid A) = \int_0^T A \cdot V'(X_t) \dd X_t + \frac12 \int_0^T \left( A \cdot V'(X_t) \right)^2 \dd t.
+\end{equation}
+
+The log-posterior density is then given by
+\begin{equation}
+\begin{aligned}
+\log p(A \mid X) = &-\log Z -\frac1{2\Sigma}\int_0^T A \cdot V'(X_t) \dd X_t - \frac1{4\Sigma} \int_0^T \left(A \cdot V'(X_t) \right)^2 \dd t \\
+&- \frac12 \norm{C_0^{-1/2}(A - A_0)}_2^2.
+\end{aligned}
+\end{equation}
+Since the log-posterior density is quadratic in $A$, the posterior is Gaussian, and it is therefore sufficient to determine its mean and covariance to fully characterize it.
+We denote by $m_T$ and $C_T$ the mean and covariance matrix, respectively.
+Let us consider the matrix-valued function $M \colon \R \to \R^{N\times N}$ whose entries are given by
+\begin{equation}
+M_{ij} = \frac1{2\Sigma T} \int_0^T V_i'(X_t) \, V_j'(X_t) \dd t, \quad i, j = 1, \ldots, N,
+\end{equation}
+and the vector-valued function $h \colon \R \to \R^N$ defined by
+\begin{equation}
+h_i = \frac1{2\Sigma T} \int_0^T V_i'(X_t) \dd X_t, \quad i = 1, \ldots, N.
+\end{equation}
+Let us remark that we can rewrite $M$ and $h$ in vector notation as
+\begin{equation}
+M = \frac1{2\Sigma T} \int_0^T V'(X_t) \otimes V'(X_t) \dd t, \quad h = \frac1{2\Sigma T} \int_0^T V'(X_t) \dd X_t,
+\end{equation}
+where $\otimes$ denotes the tensor product in $\R^N$. Therefore, we can rewrite the log-posterior density as
+\begin{equation}
+\log p(A \mid X) = -\log Z - T A \cdot h - \frac{T}{2} A \cdot M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
+\end{equation}
+Completing the squares in the log-posterior density, it is possible to show that the posterior is a Gaussian $\mu(A \mid X) = \mathcal N(m_T, C_T)$, whose precision matrix and mean are formally given by
+\begin{equation}
+\begin{aligned}
+C_T^{-1} &= C_0^{-1} + T M, \\
+C_T^{-1}m_T &= C_0^{-1}A_0 - T h. 
+\end{aligned}
+\end{equation}
+We are now interested in the limit of the posterior distribution for $T \to \infty$.
+Let us first define the maximum likelihood estimator (MLE) $\widehat A(X)$ of $A$, which is obtained by maximizing the log-likelihood function $\log p(X \mid A)$, and which is hence formally given by
+\begin{equation}
+\widehat A(X) = -M^{-1}h.
+\end{equation}
+We now introduce regularity assumptions on the SDE.
+
+We can now state the main result for asymptotic convergence of the posterior distribution.
+\begin{proposition}\label{prop:equiv} Given a continuous stochastic process $X \defeq (X_t, 0 \leq t, \leq T)$ which is ergodic with invariant measure $\mu^{\infty}$ such that $\E^{\mu^\infty}(V_i'(\cdot)) \leq C$ for some constant $C > 0$ and for all $i = 1, \ldots, N$, the posterior $\mu(A \mid X)$ contracts to the limit of $\widehat A(X)$ for $T \to \infty$.
+	%	 for $T$ arbitrarily large and under Assumption \ref{as:regularity}, the posterior mean and covariance satisfy
+	%	\begin{equation}
+	%	\begin{aligned}
+	%		&\lim_{T \to \infty} \norm{m_T - \widehat A(X)}_2 = 0, \\
+	%		&\lim_{T \to \infty} \norm{C_T}_F = 0,
+	%	\end{aligned}
+	%	\end{equation}
+	%	i.e., the posterior tends in distribution to the Dirac delta centred in the limit of the MLE.
+\end{proposition}
+\begin{proof} Let us first consider the covariance matrix. Hua's identity yields
+	\begin{equation}
+	C_T = T^{-1} \left(M^{-1} - Q^{-1}\right),
+	\end{equation}
+	where 
+	\begin{equation}
+	Q = M + T M C_0 M.
+	\end{equation}
+	The eigenvalues of $Q$ satisfy for all $i = 1, \ldots, N$
+	\begin{equation}
+	\lambda_i(Q) = \lambda_i(M) + T \lambda_i(M C_0 M) \geq \bar \lambda + T \lambda_{\min}(C_0),
+	\end{equation}
+	and therefore we obtain
+	\begin{equation}\label{eq:boundQinv}
+	\lambda_{\max}(Q^{-1}) \leq \frac{1}{\bar \lambda + T \lambda_{\min}(C_0)}.
+	\end{equation}
+	Similarly, we have a bound for the maximum eigenvalue of $M^{-1}$ given by
+	\begin{equation}\label{eq:boundMinv}
+	\lambda_{\max}(M^{-1}) \leq \frac1{\bar{\lambda}},
+	\end{equation}
+	which implies that
+	\begin{equation}
+	\trace{C_T} \leq \frac{N}{T} \left(\frac1{\bar{\lambda}} + \frac{1}{\bar \lambda + T \lambda_{\min}(C_0)}\right),
+	\end{equation}
+	and which therefore allows us to conclude that
+	\begin{equation}
+	\lim_{T\to\infty} \norm{C_T}_F = 0.
+	\end{equation}
+	We now consider the mean. Replacing the expression of the maximum likelihood estimator, we obtain
+	\begin{equation}
+	\norm{m_T - \widehat A(X)}_2 = T^{-1}\norm{M^{-1}C_0^{-1}A_0 - Q^{-1}\left(C_0^{-1}A_0 - Th \right)}_2.
+	\end{equation}
+	Let us remark that \eqref{eq:boundQinv} implies $\norm{Q^{-1}}_F \to 0$ for $T \to \infty$ and \eqref{eq:boundMinv} implies $\norm{M^{-1}}_F \leq C$ for some $C > 0$ independently of $T$.
+Moreover, the ergodic theorem guarantees that $\norm{h}_2 \leq C$ for $T$ sufficiently big, and therefore the Cauchy--Schwarz and the triangle inequalities imply
+	\begin{equation}
+	\lim_{T\to\infty} \norm{m_T - \widehat A(X)}_2 = 0,
+	\end{equation}
+	which proves the desired result.
+\end{proof}
+
+\begin{remark} Proposition \ref{prop:equiv} guarantees that in the asymptotic limit of $T \to \infty$, it is equivalent to consider the Bayesian approach and the maximum likelihood approach, and can therefore be interpreted as a consistency result for both approaches.
+Nonetheless, in this Gaussian framework the Bayesian approach provides richer information on the inference result with a negligible additional cost.
+\end{remark}
+
+\subsection{The filtering approach}
 In this section we show how the filtering approach can be employed in a Bayesian framework.
@@
 
-\section{Numerical experiments}
+\section{Numerical experiments}\label{sec:NumExp}
 
@@
 \bibliographystyle{siam}
-\bibliography{anmc}
+\bibliography{../anmc}
 \end{document}

### 2020-02-13 CalNotes.tex
Update after second estimator and Bayesian

@@
 \documentclass[10pt]{article}
+%\documentclass{siamart1116}
 
@@
 
-Data-driven approaches to the derivation of effective stochastic coarse-grained dynamics has become a standard tool in different areas such as molecular dynamics (CITE) or atmosphere and ocean science \cite{KKP15,CoP09,YMV19}.
+Data-driven approaches to the derivation of effective stochastic coarse-grained dynamics has become a standard tool in different areas such as molecular dynamics or atmosphere and ocean science \cite{KKP15,CoP09,YMV19}.
 When fitting data to a low dimensional coarse-grained model, one is faced with the problem of model misspecification; indeed, the data, coming from the full dynamics, is compatible with the coarse-grained model only at the time scales at which the effective dynamics is valid.
-This is related to the issue of high frequency data that is arises in econometrics \cite{AiJ14,AMZ05,ZMA05,OSP10}.
+This is related to the issue of high-frequency data that arises in econometrics \cite{AiJ14,AMZ05,ZMA05,OSP10}.
 
@@
 To be more precise, in the large sample size limit the MLE converges to the coefficients of the unhomogenised equation, rather than to those of the homogenised one.
-The bias of the MLE estimator can be eliminated by subsampling at an appropriate rate, which lies between the two characteristic time scales of the problem \cite[Theorems 3.5 and 3.6]{PaS07}.
+The bias of the MLE can be eliminated by subsampling at an appropriate rate, which lies between the two characteristic time scales of the problem \cite[Theorems 3.5 and 3.6]{PaS07}.
 This is similar to the estimation of the integrated stochastic volatility in the presence of market micro-structure noise, where the data has to be subsampled at an appropriate rate \cite{AMZ05,ZMA05}.
@@
 In particular, the form of the likelihood function guarantees, under a Gaussian prior hypothesis, that the posterior distribution is itself a Gaussian.
-Therefore, one can simply compute the mean and covariance of the posterior distribution to obtain a full quantification of the inference process.
+Therefore, one can simply compute the mean and covariance of the posterior distribution to obtain a full uncertainty quantification of the inference process.
 The Bayesian approach has been adopted in several works concerning single and multiscale PDEs, too, and has proved itself to be versatile and efficient in this framework (see, e.g., \cite{AbD18, AGZ19}).
 Moreover, infinite-dimensional inverse problems are intrinsically ill-posed, and interpreting them in a Bayesian manner is an efficient tool for regularizing them and guaranteeing their well-posedness \cite{Stu10, DaS16}.
-The regularization property of a Bayesian approach has been recently demonstrated for inverse problems involving multiscale PDE \cite{AbD18}.
+The regularization property of a Bayesian approach has been recently demonstrated for inverse problems involving multiscale PDEs \cite{AbD18}.
 In this work, we investigate the effects of inserting our filtering methodology in a Bayesian framework.
 In particular, we analyse the effects of modifying the likelihood function inserting the filtered trajectory, showing how this corrects the faulty asymptotic behaviour which would be present in case no pre-processing would be applied.
-
-\subsection{Outline}
 
@@
 
+In this section, we introduce the class of diffusion processes which we treat in this paper and the classical methodology employed for the estimation of the drift.
 Let $\epl > 0$ and let us consider the one-dimensional multiscale stochastic differential equation (SDE)
@@
 \end{equation}
-where $\alpha_i \in \R$, $i = 1, \ldots, N$ and $\sigma > 0$ are the drift and diffusion coefficients respectively and $W_t$ is a standard one-dimensional Brownian motion.
-The functions $V\colon \R \to \R^N$ and $p\colon \R \to \R$ are slow and fast potentials driving the dynamics of the solution $X_t^\epl$.
-Given $N \in \N_{>0}$, we assume the slow potential to be of the form
+where, given a positive integer $N$, we have that $\alpha \in \R^N$ and $\sigma > 0$ are the drift and diffusion coefficients respectively and $W_t$ is a standard one-dimensional Brownian motion.
+The functions $V\colon \R \to \R^N$ and $p\colon \R \to \R$ correspond to the fast-scale and the slow-scale confining potentials.
+In particular, we assume
 \begin{equation}\label{eq:Potential}
@@
 Moreover, we assume $p$ to be smooth and periodic of period $L$.
-Theory of homogenization \cite{BLP78} guarantees the existence of an SDE of the form
+Theory of homogenization \cite[Chapter 3]{BLP78} guarantees the existence of an SDE of the form
 \begin{equation}\label{eq:SDE_HOM}
-	\d X_t^0 = - A \cdot V'(X_t^0) \dd t + \sqrt{2\Sigma} \dd W_t,
+	\d X_t = - A \cdot V'(X_t) \dd t + \sqrt{2\Sigma} \dd W_t,
 \end{equation}
-where $W_t$ is the same Brownian motion and where the fast dynamics have been eliminated, such that $X_t^\epl \to X_t^0$ for $\epl\to 0$ in law as random variables in $\mathcal C^0((0, T), \R)$.
+where $W_t$ is the same Brownian motion as in \eqref{eq:SDE_MS}, such that $X_t^\epl \to X_t$ for $\epl\to 0$ in law as random variables in $\mathcal C^0((0, T); \R)$.
 In particular, we have $A_i = K\alpha_i$ and $\Sigma = K \sigma$, where the coefficient $K$ is given by the formula
@@
 \begin{equation}
-	\mu(\d y) = Z^{-1} e^{-p(y)/\sigma} \dd y, \quad\text{where}\quad Z = \int_0^L e^{-p(y)/\sigma} \dd y,
+	\mu(\d y) = \frac1Z e^{-p(y)/\sigma} \dd y, \quad\text{where}\quad Z = \int_0^L e^{-p(y)/\sigma} \dd y,
 \end{equation}
@@
 
+We now briefly present the classical methodology for estimating the drift coefficient.
 Let $T > 0$ and let $X^\epl \defeq (X^\epl_t, 0\leq t, \leq T)$ be a realization of the solution of \eqref{eq:SDE_MS} up to final time.
-In order to estimate the drift coefficient $A$ of the homogenized equation we maximize the likelihood function
-\begin{equation}
+Girsanov's change of measure formula applied to \eqref{eq:SDE_HOM} allows to write the likelihood of $X^\epl$ given a drift coefficient $A$ of \eqref{eq:SDE_HOM} as
+\begin{equation}\label{eq:Likelihood}
 p(X^\epl \mid A) = \exp\left(-\frac{I(X^\epl\mid A)}{2\Sigma} \right), 
 \end{equation}
-where Girsanov formula allows to write explicitly the log-likelihood as
+where 
 \begin{equation}
@@
 \end{equation}
-Therefore, the maximum likelihood estimator can be formally computed in closed form as
-\begin{equation}
+Minimizing the functional $I(X^\epl \mid A)$ with respect to $A$ therefore gives the maximum likelihood estimator (MLE) of $A$, which can be formally computed in closed form as
+\begin{equation}\label{eq:MLE}
 	\widehat A^\epl(T) \defeq \arg \min_{A \in \R^N} I(X^\epl \mid A) = M^{-1}h,
@@
 where $M\in\R^{N\times N}$ and $h\in\R^N$ are defined as
-\begin{equation}
-M = \frac1{2\Sigma T} \int_0^T V'(X_t) \otimes V'(X_t) \dd t, \quad h = \frac1{2\Sigma T} \int_0^T V'(X_t) \dd X_t,
+\begin{equation}\label{eq:MandH}
+M = \frac1{2\Sigma T} \int_0^T V'(X^\epl_t) \otimes V'(X^\epl_t) \dd t, \quad h = \frac1{2\Sigma T} \int_0^T V'(X^\epl_t) \dd X^\epl_t,
 \end{equation}
 and where $\otimes$ denotes the tensor product in $\R^N$.
-Let us now state the assumptions which will be employed throughout the rest of our work. In particular, we consider the dissipative setting of \cite{PaS07}.
+Let us now state the assumptions which will be employed throughout the rest of our work. In particular, we consider the same dissipative setting as \cite[Assumption 3.1]{PaS07}.
 \begin{assumption}\label{as:regularity} The potentials $p$ and $V$ satisfy
 	\begin{enumerate}
-		\item $p \in \mathcal C^\infty(\R, \R) \cap L^\infty(\R, \R)$,
-		\item\label{as:regularity_diss} the potential $V \in \mathcal C^\infty(\R, \R)$ and there exist $a,b > 0$ such that
+		\item $p \in \mathcal C^\infty(\R) \cap L^\infty(\R)$ and is $L$-periodic for some $L > 0$,
+		\item\label{as:regularity_diss} $V_i \in \mathcal C^\infty(\R)$ for all $i=1, \ldots, N$ is polynomially bounded from above and bounded from below, and there exist $a,b > 0$ such that
 		\begin{equation}
-		-V'(x)x \leq a - bx^2.
+		-\sum_{i=1}^N V_i'(x)x \leq a - bx^2.
 		\end{equation} 
-		Moreover, for all $T > 0$, the symmetric matrix $M$ is positive definite and its minimum eigenvalue satisfies $\lambda_{\min}(M) \geq \bar \lambda > 0$.
+		\item for all $T > 0$, the symmetric matrix $M$ is positive definite and there exists $\bar \lambda > 0$ such that $\lambda_{\min}(M) \geq \bar \lambda$.
 	\end{enumerate}
 \end{assumption}
-Under these assumptions, the estimator $\widehat A^\epl(T)$ is indeed well-posed. Moreover, these assumptions guarantee that the process $X^\epl$ is geometrically ergodic, and
+
+Under these assumptions, the MLE given in \eqref{eq:MLE} is indeed the unique minimizer of the likelihood function, as shown in \cite[Theorem 2.4]{PSV09}.
+
+Given the convergence of $X^\epl_t \to X_t$ in the space of continuous stochastic processes, one would expect that the MLE \eqref{eq:MLE} would be asymptotically unbiased for the drift coefficient $A$ of the homogenized equation \eqref{eq:SDE_HOM}.
+Instead, it is possible to prove that in the asymptotic limit for $T \to \infty$ and $\epl \to 0$, the MLE tends to the drift coefficient $\alpha$ of the unhomogenized equation \eqref{eq:SDE_MS}.
+We report here this result, whose proof can be found for the case $N = 1$ in \cite[Theorem 3.4]{PaS07}.
+Let us remark that the proof for $N > 1$ follows directly from the one-dimensional case.
+
+\begin{theorem}\label{thm:Bias} Let Assumption \ref{as:regularity} hold and let $X^\epl_0$ be distributed according to the invariant measure of the process $X_t^\epl$ solution of \eqref{eq:SDE_MS}.
+Then
+	\begin{equation}
+		\lim_{\epl \to 0}\lim_{T \to \infty} \widehat A^\epl(T) = \alpha, \quad \text{a.s.},
+	\end{equation}
+	where $\alpha$ is the drift coefficient of equation \eqref{eq:SDE_MS}.
+\end{theorem}
+
+As anticipated in the introduction, the main tool for obtaining unbiased estimators in the literature is subsampling the data.
+In particular, let the dimension of the parameter $N = 1$, let $\delta > 0$ and let $T = n\delta$ with $n$ a positive integer.
+Then, a subsampled estimator for $A$ is given by
+\begin{equation}
+	\widehat A^\epl_\delta(T) = - \frac{\sum_{j=0}^{n-1} V'(X^\epl_{j\delta})\left(X^\epl_{(j+1)\delta} - X^\epl_{j\delta}\right)}{\delta \sum_{j=0}^{n-1} V'(X^\epl_{j\delta})^2},
+\end{equation}
+which is a discretized version of $\widehat A^\epl(T)$.
+It is possible to show \cite[Theorem 3.5]{PaS07} that choosing $\delta = \epl^\zeta$ with $\zeta \in (0, 1)$ and if $T$ is sufficiently big, then $\widehat A^\epl_\delta(T)$ is an asymptotically unbiased estimator of $A$ with respect to $T \to \infty$ and $\epl \to 0$, in probability.
+Despite being widely employed in practice, estimators based on subsampling present some drawbacks, as discussed in the introduction.
+In the following, we will introduce and analyse a novel approach for the drift estimation.
+
+\begin{remark} Let us remark that for enhancing the clarity of the exposition, in this article we chose to focus on the case of a multi-dimensional parameter in the setting of one-dimensional diffusion processes.
+In fact, all the theory we present in the following could be generalized to the case of $d$-dimensional SDEs equivalent to \eqref{eq:SDE_MS}, which can be written as
+	\begin{equation}
+		\d X_t^\epl = - \sum_{i=1}^N \alpha_i \nabla V_i(X_t^\epl) \dd t - \frac1\epl \nabla p\left(\frac{X_t^\epl}{\epl}\right) \dd t + \sqrt{2\sigma} \dd W_t,
+	\end{equation}
+	where $W_t$ is a standard $d$-dimensional Brownian motion. The proof of all results below should be slightly modified, but we verified that all arguments still hold true in the $d$-dimensional case. 
+\end{remark}
 
@@
 
-In the previous section, we have shown that posterior distributions over the drift coefficient of the homogenized equation are asymptotically incorrect if multiscale data are replaced into the expression of the likelihood.
-Hence, the need of pre-processing the data is highlighted.
-In particular, we consider a filtering approach.
-Let $k \colon \R^+ \times \R^+ \to \R$ be a kernel function and consider the process $Z^\epl \defeq (Z^{\epl,k}_t, 0 \leq t \leq T)$ defined by the weighted average
-\begin{equation}\label{eq:ZDef}
-	Z^{\epl}_t \defeq \int_0^t k(t, s)X^\epl_s \dd s.
-\end{equation}
-Let $\beta, \delta > 0$ and let us consider a family of exponential kernel functions defined as
+In this section, we introduce and analyse a novel filtering approach to solve the biasedness issue highlighted by Theorem \ref{thm:Bias}.
+Let $\beta, \delta > 0$ and let us consider a family of exponential kernel functions $k \colon \R^+ \to \R$ defined as
 \begin{equation}\label{eq:filter}
-	k(t, s) = C_\beta \delta^{-1/\beta} e^{-(t-s)^\beta/\delta},
+k(r) = C_\beta \delta^{-1/\beta} e^{-r^\beta/\delta},
 \end{equation}
@@
 \end{equation}
-and where $\Gamma(\cdot)$ is the gamma function.
+and where $\Gamma(\cdot)$ is the gamma function. We consider the process $Z^\epl \defeq (Z^\epl_t, 0 \leq t \leq T)$ defined by the weighted average
+\begin{equation}\label{eq:ZDef}
+	Z^{\epl}_t \defeq \int_0^t k(t - s)X^\epl_s \dd s.
+\end{equation}
+The process $Z^\epl$ can be interpreted as a smoothed version of the original trajectory $X^\epl$.
+In fact, in the field of signal processing the kernel \eqref{eq:filter} belongs to the class of low-pass linear time-invariant filters, which cut the high frequencies in a signal to highlight its slowest components.
 In the following, only in case $\beta = 1$ a rigorous analysis is carried on.
@@
 
-Given a trajectory $X^\epl \defeq (X^\epl_t, 0\leq t \leq T)$, it is relatively inexpensive to compute $Z^\epl$ from a computational standpoint.
-In particular, the process $Z^\epl$ is the convolution of the kernel with the process $X^\epl$.
+\begin{remark} Given a trajectory $X^\epl \defeq (X^\epl_t, 0\leq t \leq T)$, it is relatively inexpensive to compute $Z^\epl$ from a computational standpoint.
+In particular, the process $Z^\epl$ is the truncated convolution of the kernel with the process $X^\epl$.
 Hence, computational tools based on the Fast Fourier Transform (FFT) exist and allow to compute $Z^\epl$ fast component-wise.
+Moreover, the process $Z_t^\epl$ can be computed, in case $\beta = 1$, in a recursive manner and therefore ``online''.
+\end{remark}
+
+In the rest of this section we will focus on the properties of the process $Z^\epl$ when it is considered together with the original process $X^\epl$.
+In particular, we focus on ergodic properties and multiscale convergence.
+Finally, we present and analyse an unbiased estimator obtained with the filtering process.
 
@@
 
-In the following, we consider the filter with $\beta = 1$, i.e.,
+Let us consider the filtering kernel \eqref{eq:filter} with $\beta = 1$, i.e.,
 \begin{equation}\label{eq:filter_beta1}
-	k(t,s) = \frac{1}{\delta} e^{-\frac{t-s}{\delta}},
+	k(r) = \frac{1}{\delta} e^{-r/\delta}.
 \end{equation}
-since in this case it holds
+In this case, Leibniz integral rule yields the equality
 \begin{equation}
-	\d Z^\epl_t = k(t,t) X^\epl_t \dd t + \int_0^t \partial_t k(t,s) X^\epl_s \dd s \dd t = \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
+	\d Z^\epl_t = k(0) X^\epl_t \dd t + \int_0^t k'(t-s) X^\epl_s \dd s \dd t = \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t,
 \end{equation}
-Considering the processes $X^\epl$ and $Z^\epl$ together, we obtain a system of stochastic differential equations
+which can be interpreted as an ordinary differential equation for $Z_t^\epl$ driven by the stochastic signal $X^\epl$.
+Considering the processes $X^\epl$ and $Z^\epl$ together, we obtain the system of two one-dimensional SDEs
 \begin{equation}
@@
 \end{equation}
-The following result guarantees that the measure induced by the joint process $(X_t^\epl, Z_t^\epl)^\top$ admits a smooth density.
+The first ingredient for verifying the ergodic properties of the two-dimensional process $(X^\epl, Z^\epl)^\top \defeq ((X^\epl_t, Z^\epl_t)^\top, 0 \leq t \leq T)$ is verifying that the measure induced by the stochastic process admits a smooth density with respect to the Lebesgue measure.
+Since noise is present only on the first component, this is a consequence of the theory of hypo-ellipticity, as summarized in the following Lemma.
 
-\begin{lemma}\label{lem:density} Let $(X_t^\epl, Z_t^\epl)^\top$ be the solution of \eqref{eq:systemSDE}.
-Then the measure $\mu^\epl$ of the process admits a smooth density $\rho^\epl$ with respect to the Lebesgue measure.
-%	 satisfying
-%	\begin{equation}
-%	\begin{aligned}
-%	\partial_t\rho^\epl(t,x,z) -\sigma \partial^2_{xx} \rho^\epl(t,x,z) &- \partial_x \left(\left ( \alpha \cdot V'(x) + \frac{1}\epl p' \left ( \frac{x}\epl \right ) \right )\rho^\epl(t,x,z)\right) \\
-%	&- \frac{1}{\delta}\partial_z\left((z - x) \rho^\epl(t,x,z)\right) = 0.
-%	\end{aligned}
-%	\end{equation} 
+\begin{lemma}\label{lem:density} Let $(X^\epl, Z^\epl)^\top$ be the solution of \eqref{eq:systemSDE} and let $\mu^\epl_t$ be the measure induced by the couple at time $t$.
+Then, the measure $\mu^\epl_t$ admits a smooth density $\rho^\epl_t$ with respect to the Lebesgue measure.
 \end{lemma}
 
-\begin{proof} We have to show that the joint process solution to \eqref{eq:systemSDE} is hypo-elliptic. Let us define the function $f\colon \R \to \R$ as 
+\begin{proof} We have to show that the joint process solution to \eqref{eq:systemSDE} is hypo-elliptic. Denoting as $f\colon \R \to \R$ the function 
 	\begin{equation}
-		f(x) = -\alpha \cdot V'(x) - \frac1\epl p'\left(\frac{x}\epl\right).
+		f(x) = -\alpha \cdot V'(x) - \frac1\epl p'\left(\frac{x}\epl\right),
 	\end{equation}
-	Then, the generator of the process $(X_t^\epl, Z_t^\epl)^\top$ is given by
+	the generator of the process $(X^\epl, Z^\epl)^\top$ is given by
 	\begin{equation}
@@
 
-Having established that the law of the joint process admits a smooth density with respect to the Lebesgue measure, we now show in the following Lemma a property of ergodicity.
+Once it is established that the law of the process admits a smooth density for all times $t>0$, which satisfies a time-dependent Fokker--Planck equation, we are interested in the limiting properties of this law.
+In particular, we know that the process $X^\epl$ alone is geometrically ergodic \cite[Theorem 4.4]{MSH02}, and we wish the couple $(X^\epl, Z^\epl)^\top$ to be endowed with the same property.
+The following Lemma guarantees that the couple is indeed geometrically ergodic exploiting an argument of dissipativity.
 
 \begin{lemma}\label{lem:ergodicity} Let Assumption \ref{as:regularity} hold and let $b > 0$ be given in Assumption \ref{as:regularity}\ref{as:regularity_diss}.
-Then, if $\delta > 1/(4b)$, the process $(X_t^\epl, Z_t^\epl)^\top$ solution of \eqref{eq:systemSDE} is geometrically ergodic, i.e., there exists $C, \lambda > 0$ such that for all measurable $f$ such that for some integer $p > 0$
+Then, if $\delta > 1/(4b)$, the process $(X^\epl, Z^\epl)^\top$ solution of \eqref{eq:systemSDE} is geometrically ergodic, i.e., there exists $C, \lambda > 0$ such that for all measurable $f$ such that for some integer $q > 0$
 	\begin{equation}
-		f(x) \leq 1 + \abs{x}^p,
+		f(x) \leq 1 + \abs{x}^q,
 	\end{equation}
@@
 	\begin{equation}
-		\abs{\E f(X^\epl_t, Z^\epl_t) - \int_\R\int_\R f(x, z) \rho^\epl(x, z) \dd x \dd z} \leq C\left(1 + \norm{\begin{pmatrix} X^\epl_0 \\ Z^\epl_0 \end{pmatrix}}^p \right)e^{-\lambda t},
+		\abs{\E f(X^\epl_t, Z^\epl_t) - \int_\R\int_\R f(x, z) \rho^\epl(x, z) \dd x \dd z} \leq C\left(1 + \norm{\begin{pmatrix} X^\epl_0 & Z^\epl_0 \end{pmatrix}^\top}^q \right)e^{-\lambda t},
 	\end{equation}
-	where $\rho^\epl$ is the solution to the stationary Fokker--Planck equation
+	where $\E$ denotes expectation with respect to the Wiener measure and $\rho^\epl$ is the solution to the stationary Fokker--Planck equation
 	\begin{equation}
@@
 \begin{equation}
-	 \mathcal S(x,z) \defeq \begin{pmatrix} -V'(x) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} = -V'(x)x+\frac1\delta(xz-z^2)
+	 \mathcal S(x,z) \defeq \begin{pmatrix} -\sum_{i=1}^N V_i'(x) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} = -\sum_{i=1}^N V_i'(x)x+\frac1\delta(xz-z^2)
 \end{equation}
@@
 \begin{equation}
-	\mathcal S(x, z) \leq a - C(\gamma^*) \norm{\begin{pmatrix} x \\ z \end{pmatrix}}^2,
+	\mathcal S(x, z) \leq a - C(\gamma^*) \norm{\begin{pmatrix} x & z \end{pmatrix}^\top}^2,
 \end{equation}
@@
 Nevertheless, being $p$ bounded, the result holds trivially.
+\end{remark}
+
+\begin{remark} The condition $\delta > 1 / (4b)$ is not very restrictive.
+Let the parameter dimension $N = 1$ and let $V(x) \propto x^{2p}$ for an integer $p > 1$.
+Then, Assumption \ref{as:regularity}\ref{as:regularity_diss} holds for an arbitrarily large $b > 0$.
+Therefore, the filter's parameter $\delta$ can be chosen along the entire positive real axis.
+A similar argument can be employed for higher dimensions $N > 1$.
 \end{remark}
@@
 \end{equation}
-Let us remark that this distribution can be obtained from direct computations involving Gaussian processes. In particular, it is known that $X_t \sim \mathcal{GP}(\mu_t, \mathcal C(t, s))$, where 
+Let us remark that this distribution can be obtained from direct computations involving Gaussian processes.
+In particular, it is known that $X_t \sim \mathcal{GP}(\mu_t, \mathcal C(t, s))$, where at stationarity $\mu_t = 0$ and
 \begin{equation}
-	\mu_t = X_0 e^{-At}, \quad \mathcal C(t, s) = \frac{\Sigma}{A} \left( e^{-A|t-s|} - e^{-A(t+s)} \right).
+	\mathcal C(t, s) = \frac{\Sigma}{A} e^{-A|t-s|}.
 \end{equation}
@@
 
-\begin{lemma}\label{lem:FPMarginal} Let $\rho^\epl$ be the solution of \eqref{eq:FPsystem} and let us write 
+\begin{lemma}\label{lem:FPMarginal} Under the assumptions of Lemma \ref{lem:ergodicity}, let $\rho^\epl$ be the solution of \eqref{eq:FPsystem} and let us write 
 \begin{equation}\label{eq:densityDecomposition}
-	\rho^\epl(x, z) = \phi^\epl(z)\psi^\epl(z)R^\epl(x,z),
+	\rho^\epl(x, z) = \phi^\epl(x)\psi^\epl(z)R^\epl(x,z),
 \end{equation}
-where $\phi^\epl$ and $\psi^\epl$ are the marginal densities, i.e., 
+where $\phi^\epl$ and $\psi^\epl$ are the marginal densities of $X^\epl$ and $Z^\epl$ respectively, i.e., 
 \begin{equation}
@@
 
-\begin{remark} It could be possible to find a closed-form solution to \eqref{eq:FPsystem} in a more general framework than Example \ref{ex:OrnUhl}.
-Nonetheless, an explicit solution is not necessary for our argument.
-\end{remark}
-
 \subsection{Multiscale convergence}\label{sec:convMS}
 
-We now investigate the convergence of the couple $(X_t^\epl, Z_t^\epl)^\top$ with respect to the multiscale parameter $\epl \to 0$.
-\corr{Rewrite the following two lemmas with considerations from discussion with Greg: maybe one lemma is enough and clearer.}
+We now investigate the convergence of the couple $(X^\epl, Z^\epl)^\top$ with respect to the multiscale parameter $\epl \to 0$.
+In particular, it is known that the invariant measure of $X^\epl$ converges weakly to the invariant measure of $X$ solution of the homogenized equation \eqref{eq:SDE_HOM}.
+The following result guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.
 
-\begin{lemma}\label{lem:convMS} Let $T > 0$.
-Then, the couple $(X^\epl, Z^\epl)^\top \defeq \left((X_t^\epl, Z_t^\epl)^\top, 0\leq t \leq T\right)$ converges in law for $\epl \to 0$ in $\mathcal C^0((0, T), \R^2)$ to the couple $ (X, Z)^\top \defeq \left((X_t, Z_t)^\top, 0\leq t \leq T\right)$ solution to
+\begin{lemma}\label{lem:convMeasure} Under Assumption \ref{as:regularity}, let $\mu^\epl$ be the invariant measure of the couple $(X^\epl, Z^\epl)^\top$ and let $(X_0^\epl, Z_0^\epl)^\top \sim \mu^\epl$.
+Then, the measure $\mu^\epl$ converges weakly to the measure $\mu^0(\d x, \d z) = \rho^0(x, z) \dd x \dd z$, whose density $\rho^0$ is the unique solution of the Fokker--Planck equation
+\begin{equation} \label{eq:FPsystem_homogenized}
+	\Sigma \partial^2_{xx} \rho^0(x,z) + \partial_x\left( A \cdot V'(x) \rho^0(x,z) \right) + \frac{1}{\delta}\partial_z\left((z - x) \rho^0(x,z) \right) = 0,
+\end{equation}
+where $A$ and $\Sigma$ are the coefficients of the homogenized equation \eqref{eq:SDE_HOM}.
+\end{lemma}
+\begin{proof} Let $(X, Z)^\top \defeq \left((X_t, Z_t)^\top, 0\leq t \leq T\right)$ be the solution of
 	\begin{equation}
@@
 	\end{equation} 
-	where $A\in \R^N$ and $\Sigma > 0$ are the coefficients of \eqref{eq:SDE_HOM}.
-\end{lemma}
-\begin{proof} Standard homogenization theory (see e.g. \cite[Chapter 3]{BLP78}) can be employed, and therefore the proof is omitted here.
-\end{proof}
-
-It is known that the invariant distribution of the process $X^\epl$ converges weakly to the invariant distribution of the process $X^0$ solution to \eqref{eq:SDE_HOM}.
-We now consider the random variable $(X^\epl, Z^\epl)^\top$ and present an analogous convergence result for the joint process.
-
-\begin{lemma}\label{lem:convMeasure} Let $\mu^\epl$ be the invariant measure of the couple $(X^\epl, Z^\epl)^\top$ and let $(X_0^\epl, Z_0^\epl)^\top \sim \mu^\epl$.
-Then, the measure $\mu^\epl$ converges weakly to the measure $\mu^0(\d x, \d z) = \rho^0(x, z) \dd x \dd z$, whose density $\rho^0$ is the unique solution of the Fokker--Planck equation
-\begin{equation} \label{eq:FPsystem_homogenized}
-	\Sigma \partial^2_{xx} \rho^0(x,z) + \left ( A \cdot V''(x) + \frac{1}{\delta} \right ) \rho^0(x,z) + A \cdot V'(x) \partial_x \rho^0(x,z) + \frac{1}{\delta}(z - x) \partial_z \rho^0(x,z) = 0,
-\end{equation}
-where $A$ and $\Sigma$ are the coefficients of the homogenized equation \eqref{eq:SDE_HOM}.
-\end{lemma}
-\begin{proof} Lemma \ref{lem:convMS}, together with the assumption that the joint process has an initial condition distributed as the invariant measures, guarantees via the Portmanteau theorem the weak convergence of $\mu^\epl$ to $\mu^0$.
+	with $(X_0, Z_0)^\top \sim \mu^0$.
+The arguments of Section \ref{sec:ergodic} can be repeated to conclude that the invariant measure of $(X, Z)^\top$ admits a smooth density $\rho^0$ which satisfies \eqref{eq:FPsystem_homogenized}.
+Moreover, standard homogenization theory (see e.g.
+\cite[Chapter 3]{BLP78}) guarantees that$(X^\epl,Z^\epl)^\top \to (X,Z)^\top$ for $\epl \to 0$ in law as random variables with values in $\mathcal C^0((0, T); \R^2)$.
+The Portmanteau theorem can be employed to conclude that the measure $\mu^\epl$ converges weakly to $\mu^0$ for $\epl \to 0$.
 \end{proof}
@@
 	\begin{equation}
-		\rho^0(x, z) = \phi^0(z)\psi^0(z)R^0(x,z),
+		\rho^0(x, z) = \phi^0(x)\psi^0(z)R^0(x,z),
 	\end{equation}
@@
 	\begin{equation}
-		\Sigma \delta \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z = \E^{\rho^0}[((X^0)^2 - (Z^0)^2)V''(Z^0)].
+		\Sigma \delta \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z = \E^{\rho^0}[(X^2 - Z^2)V''(Z)].
 	\end{equation}
@@
 
-\subsection{The modified estimator}
+\subsection{The filtering-based estimator}\label{sec:FilterMLE}
 
-The estimator of the homogenized drift coefficient $A$ we analyse is given by the formula
+We now consider the inference problem and propose our filtering-based estimator of the drift, which is formally given by the formula
 \begin{equation}\label{eq:AHatMixed}
-	\widehat A^\epl(T) = - \widetilde M^{-1} \widetilde h,
+	\widehat A^\epl_k(T) = - \widetilde M^{-1} \widetilde h,
 \end{equation}
-where
+where we employ the subscript $k$ for reference to the filter's kernel in \eqref{eq:filter}, and where
 \begin{equation}\label{eq:MandHTilde}
-	\widetilde M = \frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t \qquad \text{and} \qquad \widetilde h = \frac{1}{T} \int_0^T V'(Z^\epl_t) \dd X^\epl_t.
+	\widetilde M = \frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t, \qquad \text{and} \qquad \widetilde h = \frac{1}{T} \int_0^T V'(Z^\epl_t) \dd X^\epl_t.
 \end{equation}
-In practice, one evaluation of $V'(\cdot)$ is computed with the filter, while the differential and the second evaluation of $V'(\cdot)$ are maintained with the original process $X^\epl$.
+Let us remark that the formula above is obtained from \eqref{eq:MLE} by replacing only one instance of $X_t^\epl$ with $Z_t^\epl$ in both $M$ and $h$.
+In particular, it is fundamental for proving unbiasedness to keep in the definition of $h$ the differential of the original process $\d X^\epl_t$.
+Let us furthermore remark that $\widehat A^\epl_k(T)$ need not be the minimizer of some filtering-based likelihood function.
+In fact, if one were to replace $Z_t^\epl$ directly in \eqref{eq:Likelihood}, the non-symmetric matrix $\widetilde M$ would appear and $\widehat A^\epl_k(T)$ would not be guaranteed of being the minimizer.
+Moreover, let us remark that even though
+\begin{equation}
+	\widetilde M = M + \Delta, \quad \Delta \defeq \widetilde M - M,
+\end{equation}
+where $\Delta$ is a matrix which is supposedly small due to the closeness of $X_t^\epl$ and its filtered version $Z_t^\epl$, this does not suffice to directly conclude that $\widetilde M$ is positive definite when $M$ is.
+Therefore, the estimator $\widehat A^\epl_k(T)$ has to be thought of as a perturbation of $\widehat A^\epl(T)$, directly at the level of estimators and after the maximization procedure.
+The only theoretical guarantee which is still needed for the well-posedness of $\widehat A^\epl_k(T)$ is for $\widetilde M$ to be invertible, which is given by the following Lemma.
 
-\begin{remark} Let us remark that in the one-dimensional case $N = 1$, the estimator can be written as
-\begin{equation}
-\widehat A^\epl(T) = - \frac{\int_0^T V'(Z^\epl_t) \dd X^\epl_t}{\int_0^T V'(Z^\epl_t) V'(X^\epl_t) \dd t}.
-\end{equation}
-\end{remark}
-
-In the one-dimensional case, it is clear that the maximum likelihood estimator based on $X^\epl$ alone, i.e., the quantity
-\begin{equation}
-	\widehat A^\epl(T) = - \frac{\int_0^T V'(X^\epl_t) \dd X^\epl_t}{\int_0^T V'(X^\epl_t)^2 \dd t}.
-\end{equation}
-is well defined for $V(x) \neq 0$. Equivalently, for a $N$-dimensional parameter, a sufficient assumption for the well-posedness of the estimator is to require the symmetric matrix $M$ defined as
-\begin{equation}
-	M = \frac{1}{T} \int_0^T V'(X^\epl_t) \otimes V'(X^\epl_t) \dd t,
-\end{equation}
-to be positive definite. In the following lemma, we ensure that the estimator based on the filtering method is well-defined.
-
-\begin{lemma} The matrix $\widetilde M$ defined in \eqref{eq:MandHTilde} is invertible almost surely. 
+\begin{lemma}\label{lem:AHatWellPosed} The matrix $\widetilde M$ defined in \eqref{eq:MandHTilde} is invertible almost surely. 
 \end{lemma}
 \begin{proof} 
-\todo
+\todo: \corr{Idea.
+We don't need $\widetilde M$ to be symmetric positive definite (it is not) due to the comment just above the lemma.
+Nevertheless, if the functions $V_i'(x)$ are not such that the rows of $\widetilde M$ are identical for any $(X_t, Z_t)$, then the randomness in the entries should guarantee that $\det \widetilde M \neq 0$ with probability one.
+Still missing the (probably trivial) argument why this is true.}
 \end{proof}
 
-\begin{theorem}\label{thm:mainTheorem} Let $\widehat A^\epl(T)$ be defined in \eqref{eq:AHatMixed}. Then
-	\begin{equation}\label{eq:theoremFirst}
-	\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A^\epl(T) = A, \quad \text{a.s.},
+We are now able to present the main result of unbiasedness of the filtering-based estimator.
+\begin{theorem}\label{thm:mainTheorem} Under the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure}, let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed}. Then
+	\begin{equation}
+	\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A_k^\epl(T) = A, \quad \text{a.s.},
 	\end{equation}
 	where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.
-%   Moreover, the following central limit theorem holds
-%	\begin{equation}\label{eq:theoremSecond}
-%	\lim_{\epl \to 0} \lim_{T \to \infty} \sqrt{T} \left(A - \widehat A^\epl(T) \right) = \Lambda, \quad \text{in law}, 
-%	\end{equation}
-%	where $\Lambda \sim \mathcal N(0, \gamma^2)$ and where 
-%	\begin{equation}
-%	\gamma = \sqrt{2\sigma} \frac{\sqrt{\E^{\rho^0}[V'(Z)^2]}}{\E^{\rho^0}[V'(Z)V'(X)]}.
-%	\end{equation}
 \end{theorem}
@@
 \begin{aligned}
-	\widehat A^\epl(T) &= \alpha + \frac{1}{T} \widetilde M^{-1} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t - \frac{\sqrt{2\sigma}}{T}  \widetilde M^{-1} \int_0^T V'(Z^\epl_t) \dd W_t\\
+	\widehat A^\epl_k(T) &= \alpha + \frac{1}{T} \widetilde M^{-1} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t - \frac{\sqrt{2\sigma}}{T}  \widetilde M^{-1} \int_0^T V'(Z^\epl_t) \dd W_t\\
 	&\eqdef \alpha + I_1^\epl(T) - I_2^\epl(T).
@@
 \end{equation}
-which, together with \eqref{eq:Proof_I1}, proves \eqref{eq:theoremFirst}. 
+which, together with \eqref{eq:Proof_I1}, proves the desired result.
+\end{proof}
+
+\subsection{A second filtering-based estimator}\label{sec:FilterMLE_2}
+
+In this section we consider a modification to the estimator \eqref{eq:AHatMixed}, which is defined as
+\begin{equation}\label{eq:AHatMixedTilde}
+	\widetilde A^\epl_k(T) = -M^{-1}\widetilde h,
+\end{equation}
+where the matrix $M$ is taken from \eqref{eq:MandH} and the vector $\widetilde{h}$ is taken from \eqref{eq:MandHTilde}.
+For this estimator, which has the advantage of being well-posed due to Assumption \ref{as:regularity}, we will be able to prove a result of unbiasedness under a condition on the filtering parameter $\delta$.
+Let us start with an estimate concerning the distance between $X^\epl$ and $Z^\epl$.
+
+\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$. Then
+	\begin{equation}
+		\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
+	\end{equation}
+	for a constant $C > 0$ independent of $\epl$ and $\delta$.
+\end{lemma}
+\begin{proof} Let us first remark that the filtering kernel satisfies
+	\begin{equation}\label{eq:filterIntegral}
+		\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta},
+	\end{equation}
+	which implies that the measure $\kappa_t(\d s)$ on $(0, t)$ defined as
+	\begin{equation}
+		\kappa_t(\d s) \defeq \frac{k(t-s)}{1 - e^{-t/\delta}} \dd s,
+	\end{equation}
+	is a probability measure.
+Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$.
+Let $Z_t^\epl$ be the corresponding filtered process.
+By definition of $Z^\epl_t$ and due \eqref{eq:filterIntegral} we now have
+	\begin{equation}
+	\begin{aligned}
+		X_t^\epl - Z_t^\epl &= X_t^\epl - \int_0^t k(t-s) X_s^\epl \dd s\\
+		&= \int_0^t k(t - s) \left(X_t^\epl - X_s^\epl\right) \dd s + e^{-t/\delta} X^\epl_t\\
+		&= (1 - e^{-t/\delta})\int_0^t \left(X_t^\epl - X_s^\epl\right) \kappa_t(\d s) + e^{-t/\delta} X^\epl_t.
+	\end{aligned}
+	\end{equation}
+	Therefore, Jensen's inequalities yields for a constant depending only on $p$
+	\begin{equation}
+	\begin{aligned}
+		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} &\leq C (1 - e^{-t/\delta})^{2p} \int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} \kappa_t (\d s) + C e^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p}\\
+		&\leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} k(t-s) \dd s + Ce^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p}
+	\end{aligned}
+	\end{equation}
+	where we replaced the definition of $\kappa(\d s)$ and exploited the fact that $1 - e^{-t/\delta}\leq 1$ for all $t \geq 0$.
+Due to \cite[Corollary 5.4]{PaS07}, we know that $X^\epl_t$ has bounded moments of all orders with respect to its invariant measure.
+Moreover, the estimate
+	\begin{equation}
+		\E^{\phi^\epl}\abs{X_t^\epl - X_s^\epl}^{2p} \leq C\left(\epl^{2p} + (t-s)^{2p} + (t-s)^p\right),
+	\end{equation}
+	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}. Finally, it is possible to verify by induction on $r$ that for all integers $r$ it holds
+	\begin{equation}
+		\int_0^t k(t-s) (t - s)^r \dd s \leq r! \, \delta^r, 
+	\end{equation}
+	which implies that there exists a constant $C > 0$ and depending only on $p$ such that
+	\begin{equation}
+		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p + e^{-2pt/\delta}\right).
+	\end{equation}
+	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
+In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$
+	\begin{equation}
+		\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} + Ce^{-\lambda t},
+	\end{equation}
+	which, for $t$ sufficiently big, yields
+	\begin{equation}
+		\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
+	\end{equation}
+	which is the desired result.
+\end{proof}
+
+Let us consider a couple $(X^\epl, Z^\epl)^\top$. In the following, we will adopt the notation
+\begin{equation}\label{eq:CalM}
+	\mathcal M = \E^{\rho^\epl}[V'(X^\epl) \otimes V'(X^\epl)] \quad \text{and} \quad \widetilde{\mathcal M} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)],
+\end{equation}
+which due to the ergodic theorem satisfy
+\begin{equation}
+	\lim_{T \to \infty} M = \mathcal M, \quad \text{and} \quad \lim_{T \to \infty} \widetilde M = \mathcal{\widetilde M},
+\end{equation}
+almost surely. In the following Lemma, we consider the difference between the two matrices $\mathcal M$ and $\widetilde{\mathcal M}$.
+
+\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Lemma \ref{lem:distanceZandX} hold. Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}$ defined in \eqref{eq:CalM} satisfy
+	\begin{equation}
+		\norm{\mathcal M - \widetilde{\mathcal M}}_2 \leq C\left(\epl + \delta^{1/2}\right),
+	\end{equation}
+	for a constant $C > 0$ independent of $\epl$ and $\delta$.
+\end{lemma}
+\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
+	\begin{equation}
+	\begin{aligned}
+		\norm{\mathcal M - \widetilde{\mathcal M}}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
+		&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
+	\end{aligned}
+	\end{equation}
+	The Lipschitz condition on $V$ together with the boundedness of the moments of $X^\epl$ and Lemma \ref{lem:distanceZandX} yields for a constant $C > 0$
+	\begin{equation}
+	\begin{aligned}
+		\norm{\mathcal M - \widetilde{\mathcal M}}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
+	\end{aligned}
+	\end{equation}
+	which is the desired result.
+\end{proof}
+
+We finally can prove the unbiasedness of the estimator $\widetilde A^\epl_k(T)$.
+
+\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold.
+Then, if $\delta$ in \eqref{eq:filter} satisfies $\delta = \delta(\epl)$ with $\delta(\epl) \to 0$ for $\epl \to 0$, it holds
+	\begin{equation}
+		\lim_{\epl \to 0} \lim_{T \to \infty} \widetilde A^\epl_k(T) = A, \quad \text{a.s.},
+	\end{equation} 
+	for $\widetilde A^\epl_k(T)$ defined in \eqref{eq:AHatMixedTilde}.
+\end{theorem}
+\begin{proof} We first consider the difference between the two estimators $\widetilde A^\epl_k(T)$ and $\widehat A^\epl_k(T)$. In particular, the ergodic theorem and an algebraic equality imply
+	\begin{equation}
+	\begin{aligned}
+		\lim_{T \to \infty} \left(\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)\right) &= \left(\mathcal M^{-1} - \widetilde{\mathcal M}^{-1}\right) \lim_{T \to \infty}\widetilde h \\
+		&= \mathcal M^{-1}\left(\mathcal M - \widetilde{\mathcal M}\right)  \widetilde{\mathcal M}^{-1} \lim_{T \to \infty} \widetilde h\\
+		&= \mathcal M^{-1}\left(\mathcal M - \widetilde{\mathcal M}\right)\lim_{T \to \infty} \widehat A^\epl_k(T),
+	\end{aligned}
+	\end{equation}
+	almost surely. Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
+	\begin{equation}\label{eq:DistATildeAHat}
+		\lim_{T \to \infty} \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 \leq C \left(\epl + \delta^{1/2} \right).
+	\end{equation}
+	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem}. Now, the triangle inequality yields
+	\begin{equation}
+		\norm{\widetilde A^\epl_k(T) - A}_2 \leq \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 + \norm{\widehat A^\epl_k(T) - A}_2.
+	\end{equation}
+	Therefore, due to Theorem \ref{thm:mainTheorem}, the inequality \eqref{eq:DistATildeAHat} and since $\delta \to 0$ for $\epl \to 0$, the desired result holds almost surely.
 \end{proof}
@@
 
-In a Bayesian setting, the goal is to determine the posterior distribution $\mu(A \mid X)$ given a continuous trajectory $X \defeq (X_t, 0 \leq t \leq T)$.
-Choosing a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$ on $A$, where $A_0 \in \R^N$ and $C_0 \in \R^{N\times N}$ is symmetric positive definite, the posterior distribution admits a density $p(A \mid X)$ with respect to the Lebesgue measure which satisfies
+In this section we present a Bayesian reinterpretation of the inference procedure, which, given the structure of the problem, allows to get at a full uncertainty quantification with a low computational effort.
+
+Let us fix a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$ on $A$, where $A_0 \in \R^N$ and $C_0 \in \R^{N\times N}$ is symmetric positive definite.
+Then, given a final time $T > 0$, the posterior distribution $\mu_T$ admits a density $p(A \mid X^\epl)$ with respect to the Lebesgue measure which satisfies
 \begin{equation}
-p(A \mid X) = \frac1Z \, p(X \mid A) \, p_0(A),
+p(A \mid X^\epl) = \frac1{Z^\epl} \, p(X^\epl \mid A) \, p_0(A),
 \end{equation}
-where $Z$ is the normalization constant, $p_0$ is the density of $\mu_0$, and where Girsanov's formula allows to write the likelihood as
-\begin{equation}
-p(X \mid A) = \exp\left(-\frac{I(X\mid A)}{2\Sigma} \right), 
+where $Z^\epl$ is the normalization constant, $p_0$ is the density of $\mu_0$, and where the likelihood $p(X^\epl \mid A)$ is given in \eqref{eq:Likelihood}.
+The log-posterior density is therefore given by
+\begin{equation}\label{eq:Posterior}
+\log p(A \mid X^\epl) = -\log Z^\epl - T A \cdot h - \frac{T}{2} A \cdot M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0),
 \end{equation}
-with
-\begin{equation}
-I(X\mid A) = \int_0^T A \cdot V'(X_t) \dd X_t + \frac12 \int_0^T \left( A \cdot V'(X_t) \right)^2 \dd t.
-\end{equation}
-
-The log-posterior density is then given by
+where $M$ and $h$ are defined in \eqref{eq:MandH}.
+Since the log-posterior density is quadratic in $A$, the posterior is Gaussian, and it is therefore sufficient to determine its mean and covariance to fully characterize it.
+We denote by $m_{T,\epl}$ and $C_{T,\epl}$ the mean and covariance matrix, respectively.
+Completing the squares in the log-posterior density, we formally obtain
 \begin{equation}
 \begin{aligned}
-\log p(A \mid X) = &-\log Z -\frac1{2\Sigma}\int_0^T A \cdot V'(X_t) \dd X_t - \frac1{4\Sigma} \int_0^T \left(A \cdot V'(X_t) \right)^2 \dd t \\
-&- \frac12 \norm{C_0^{-1/2}(A - A_0)}_2^2.
+C_{T,\epl}^{-1} &= C_0^{-1} + T M, \\
+C_{T,\epl}^{-1}m_{T,\epl} &= C_0^{-1}A_0 - T h. 
 \end{aligned}
 \end{equation}
-Since the log-posterior density is quadratic in $A$, the posterior is Gaussian, and it is therefore sufficient to determine its mean and covariance to fully characterize it.
-We denote by $m_T$ and $C_T$ the mean and covariance matrix, respectively.
-Let us consider the matrix-valued function $M \colon \R \to \R^{N\times N}$ whose entries are given by
-\begin{equation}
-M_{ij} = \frac1{2\Sigma T} \int_0^T V_i'(X_t) \, V_j'(X_t) \dd t, \quad i, j = 1, \ldots, N,
-\end{equation}
-and the vector-valued function $h \colon \R \to \R^N$ defined by
-\begin{equation}
-h_i = \frac1{2\Sigma T} \int_0^T V_i'(X_t) \dd X_t, \quad i = 1, \ldots, N.
-\end{equation}
-Let us remark that we can rewrite $M$ and $h$ in vector notation as
-\begin{equation}
-M = \frac1{2\Sigma T} \int_0^T V'(X_t) \otimes V'(X_t) \dd t, \quad h = \frac1{2\Sigma T} \int_0^T V'(X_t) \dd X_t,
-\end{equation}
-where $\otimes$ denotes the tensor product in $\R^N$. Therefore, we can rewrite the log-posterior density as
-\begin{equation}
-\log p(A \mid X) = -\log Z - T A \cdot h - \frac{T}{2} A \cdot M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
-\end{equation}
-Completing the squares in the log-posterior density, it is possible to show that the posterior is a Gaussian $\mu(A \mid X) = \mathcal N(m_T, C_T)$, whose precision matrix and mean are formally given by
-\begin{equation}
-\begin{aligned}
-C_T^{-1} &= C_0^{-1} + T M, \\
-C_T^{-1}m_T &= C_0^{-1}A_0 - T h. 
-\end{aligned}
-\end{equation}
-We are now interested in the limit of the posterior distribution for $T \to \infty$.
-Let us first define the maximum likelihood estimator (MLE) $\widehat A(X)$ of $A$, which is obtained by maximizing the log-likelihood function $\log p(X \mid A)$, and which is hence formally given by
-\begin{equation}
-\widehat A(X) = -M^{-1}h.
-\end{equation}
-We now introduce regularity assumptions on the SDE.
+Under Assumption \ref{as:regularity}, one can show that the posterior at time $T > 0$ is indeed given by $\mu_{T,\epl} = \mathcal N(m_{T,\epl}, C_{T,\epl})$.
+We are now interested in the asymptotic limit of the posterior distribution for $T \to \infty$ and for $\epl \to 0$.
 
 We can now state the main result for asymptotic convergence of the posterior distribution.
-\begin{proposition}\label{prop:equiv} Given a continuous stochastic process $X \defeq (X_t, 0 \leq t, \leq T)$ which is ergodic with invariant measure $\mu^{\infty}$ such that $\E^{\mu^\infty}(V_i'(\cdot)) \leq C$ for some constant $C > 0$ and for all $i = 1, \ldots, N$, the posterior $\mu(A \mid X)$ contracts to the limit of $\widehat A(X)$ for $T \to \infty$.
-	%	 for $T$ arbitrarily large and under Assumption \ref{as:regularity}, the posterior mean and covariance satisfy
-	%	\begin{equation}
-	%	\begin{aligned}
-	%		&\lim_{T \to \infty} \norm{m_T - \widehat A(X)}_2 = 0, \\
-	%		&\lim_{T \to \infty} \norm{C_T}_F = 0,
-	%	\end{aligned}
-	%	\end{equation}
-	%	i.e., the posterior tends in distribution to the Dirac delta centred in the limit of the MLE.
-\end{proposition}
+\begin{theorem}\label{thm:BayesianBias} Under Assumption \ref{as:regularity}, the posterior measure $\mu_{T,\epl} = \mathcal N(m_{T,\epl}, C_{T,\epl})$ satisfies
+	\begin{equation}
+		\lim_{\epl \to 0}\lim_{T \to \infty} \mu_{T,\epl}(\cdot) = \delta(\cdot - \alpha), \quad \text{a.s.},
+	\end{equation}
+	weakly in the space of probability measures on $\R^N$, where $\delta$ is the Dirac measure on $\R^N$.
+\end{theorem}
 \begin{proof} Let us first consider the covariance matrix. Hua's identity yields
 	\begin{equation}
-	C_T = T^{-1} \left(M^{-1} - Q^{-1}\right),
+	C_{T,\epl} = T^{-1} \left(M^{-1} - Q^{-1}\right),
 	\end{equation}
@@
 	\end{equation}
-	The eigenvalues of $Q$ satisfy for all $i = 1, \ldots, N$
+	Let us first remark that due to the hypothesis on $M$ and the ergodic theorem it holds for all $T > 0$
 	\begin{equation}
-	\lambda_i(Q) = \lambda_i(M) + T \lambda_i(M C_0 M) \geq \bar \lambda + T \lambda_{\min}(C_0),
+		\norm{M^{-1}}_2 \leq \frac1{\bar \lambda}
 	\end{equation}
-	and therefore we obtain
-	\begin{equation}\label{eq:boundQinv}
-	\lambda_{\max}(Q^{-1}) \leq \frac{1}{\bar \lambda + T \lambda_{\min}(C_0)}.
+	We now have that for generic symmetric positive definite matrices $R$ and $S$ it holds
+	\begin{equation}
+		\norm{(R+S)^{-1}}_2 \leq \norm{S^{-1}}_2.
 	\end{equation}
-	Similarly, we have a bound for the maximum eigenvalue of $M^{-1}$ given by
-	\begin{equation}\label{eq:boundMinv}
-	\lambda_{\max}(M^{-1}) \leq \frac1{\bar{\lambda}},
+	Applying this inequality to $Q^{-1}$, we obtain
+	\begin{equation}
+		\norm{Q^{-1}}_2 \leq \frac1T \norm{(MC_0M)^{-1}}_2 \leq \frac1T \norm{M^{-1}}_2^2 \norm{C_0^{-1}}_2 = \frac1{T\bar \lambda^2} \norm{C_0^{-1}}_2,
 	\end{equation}
-	which implies that
+	which implies
 	\begin{equation}
-	\trace{C_T} \leq \frac{N}{T} \left(\frac1{\bar{\lambda}} + \frac{1}{\bar \lambda + T \lambda_{\min}(C_0)}\right),
+		\lim_{T \to \infty}\norm{Q^{-1}}_2 = 0,
 	\end{equation}
-	and which therefore allows us to conclude that
+	and due to the triangle inequality
+	\begin{equation}\label{eq:CovarianceShrink}
+		\lim_{T \to \infty}\norm{C_{T,\epl}}_2 = 0.
+	\end{equation}
+	We proved that in the limit for $T \to \infty$ the covariance shrinks to zero independently of $\epl$. We now consider the mean. First, we remark that the triangle inequality yields
 	\begin{equation}
-	\lim_{T\to\infty} \norm{C_T}_F = 0.
+		\norm{m_{T,\epl} - \alpha}_2 \leq \norm{m_{T,\epl} - \widehat A^\epl(T)}_2 + \norm{\widehat A^\epl(T) - \alpha}_2.
 	\end{equation}
-	We now consider the mean. Replacing the expression of the maximum likelihood estimator, we obtain
+	For the second term, Theorem \ref{thm:Bias} implies 
 	\begin{equation}
-	\norm{m_T - \widehat A(X)}_2 = T^{-1}\norm{M^{-1}C_0^{-1}A_0 - Q^{-1}\left(C_0^{-1}A_0 - Th \right)}_2.
+		\lim_{\epl \to 0} \lim_{T \to \infty}\norm{\widehat A^\epl(T) - \alpha}_2 = 0, \quad \text{a.s.}
 	\end{equation}
-	Let us remark that \eqref{eq:boundQinv} implies $\norm{Q^{-1}}_F \to 0$ for $T \to \infty$ and \eqref{eq:boundMinv} implies $\norm{M^{-1}}_F \leq C$ for some $C > 0$ independently of $T$.
-Moreover, the ergodic theorem guarantees that $\norm{h}_2 \leq C$ for $T$ sufficiently big, and therefore the Cauchy--Schwarz and the triangle inequalities imply
+	Let us now consider the first term.	Replacing the expression of the maximum likelihood estimator and due to the Cauchy--Schwarz and triangle inequalities, we obtain
 	\begin{equation}
-	\lim_{T\to\infty} \norm{m_T - \widehat A(X)}_2 = 0,
+	\begin{aligned}
+		\norm{m_{T,\epl} - \widehat A^\epl(T)}_2 &= \frac1T\norm{M^{-1}C_0^{-1}A_0 - Q^{-1}\left(C_0^{-1}A_0 - Th \right)}_2\\
+		&\leq \frac1{T\bar \lambda} \norm{C_0^{-1}}_2 \left(\norm{A_0}_2 + \frac1{\bar \lambda}\norm{h}_2 + \frac1{T\bar \lambda} \norm{C_0^{-1}}_2\norm{A_0}_2\right).
+	\end{aligned}
 	\end{equation}
-	which proves the desired result.
+	Moreover, the ergodic theorem and the strong law of large numbers for martingales guarantee that $\norm{h}_2$ is bounded a.s. for $T \to \infty$. Therefore
+	\begin{equation}
+	\lim_{T\to\infty} \norm{m_{T,\epl} - \widehat A^\epl(T)}_2 = 0, \quad \text{a.s.},
+	\end{equation}
+	independently of $\epl$. Finally, 
+	\begin{equation}
+		\lim_{\epl \to 0} \lim_{T \to \infty}\norm{m_{T,\epl} - \alpha}_2 = 0, \quad \text{a.s.},
+	\end{equation}
+	which, together with \eqref{eq:CovarianceShrink}, implies the desired result. 
 \end{proof}
 
-\begin{remark} Proposition \ref{prop:equiv} guarantees that in the asymptotic limit of $T \to \infty$, it is equivalent to consider the Bayesian approach and the maximum likelihood approach, and can therefore be interpreted as a consistency result for both approaches.
-Nonetheless, in this Gaussian framework the Bayesian approach provides richer information on the inference result with a negligible additional cost.
+\begin{remark} The result above has the same consequences in the Bayesian setting as Theorem \ref{thm:Bias} has for the MLE.
+In particular, it shows that the posterior distribution obtained when data is not pre-processed concentrates asymptotically on the drift coefficient of the unhomogenized equation \eqref{eq:SDE_MS}.
+Moreover, a partial result which can be deduced from the proof is that in the limit for $T \to \infty$ and for a positive value $\epl > 0$ the Bayesian and the MLE approaches are equivalent.
+In particular, we have for all $\epl > 0$
+	\begin{equation}
+	\begin{aligned}
+		&\lim_{T\to\infty} \norm{C_{T,\epl}}_2 = 0,\\
+		&\lim_{T \to\infty}\norm{m_{T,\epl} - \widehat A^\epl(T)}_2 =0,
+	\end{aligned}	
+	\end{equation} 
+	i.e., the weak limit of the posterior $\mu_{T,\epl}$ for $T\to \infty$ is the Dirac delta concentrated on the limit of $\widehat A^\epl(T)$ for $T\to \infty$. 
 \end{remark}
@@
 \subsection{The filtering approach}
-In this section we show how the filtering approach can be employed in a Bayesian framework.
+
+In this section, we present how to correct the faulty behaviour highlighted by Theorem \ref{thm:BayesianBias} with filtering techniques.
+In particular, we employ the same strategy that led to the estimator $\widetilde A^\epl_k(T)$ presented in Section \ref{sec:FilterMLE_2}.
+Therefore, we modify the likelihood function as
+\begin{equation}
+	\widetilde p(X^\epl \mid A) = \exp\left(-\frac{\widetilde I(X^\epl\mid A)}{2\Sigma} \right), 
+\end{equation}
+where 
+\begin{equation}
+	\widetilde I(X^\epl \mid A) =\int_0^T A \cdot V'(Z^\epl_t) \dd X^\epl_t + \int_0^T \left(A \cdot V'(X^\epl_t)\right)^2 \dd t,
+\end{equation}
+so that the estimator $\widetilde A^\epl_k(T)$ introduced in \eqref{eq:AHatMixedTilde} is the MLE based on the new likelihood $\widetilde p(X^\epl \mid A)$.
+With this likelihood function, we obtain the modified posterior $\widetilde \mu_{T,\epl} = \mathcal N(\widetilde m_{T, \epl}, C_{T, \epl})$, whose parameters are given by
+\begin{equation}
+\begin{aligned}
+	C_{T, \epl}^{-1} &= C_0^{-1} + T M, \\
+	C_{T,\epl}^{-1}\widetilde m_{T,\epl} &= C_0^{-1}A_0 - T \widetilde h. 
+\end{aligned}	
+\end{equation}
+Let us remark that the posterior $\widetilde \mu_{T,\epl}$ has the same covariance as $\mu_{T,\epl}$. The following result now holds.
+\begin{theorem} Let the Assumptions of Theorem \ref{thm:mainTheoremTilde} hold. Then, the modified posterior measure $\widetilde\mu_{T,\epl} = \mathcal N(\widetilde m_{T,\epl}, C_{T,\epl})$ satisfies
+	\begin{equation}
+	\lim_{\epl \to 0}\lim_{T \to \infty} \widetilde \mu_{T,\epl}(\cdot) = \delta(\cdot - A), \quad \text{a.s.},
+	\end{equation}
+	weakly in the space of probability measures on $\R$, where $\delta$ is the Dirac measure on $\R$.
+\end{theorem}
+\begin{proof} The proof follows from the proof of Theorem \ref{thm:BayesianBias} and from Theorem \ref{thm:mainTheoremTilde}.
+\end{proof}
+
+%In this section we show how the filtering approach can be employed in a Bayesian framework.
 As in Section \ref{sec:Bayesian} let us consider a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$.
 Then, the density $p^\epl(A \mid X)$ of the posterior distribution $\mu^\epl(A \mid X^\epl)$ given by multiscale data satisfies
-\begin{equation}
-	p^\epl(A \mid X) = \frac1{Z^\epl} \, p^\epl(X \mid A) \, p_0(A),
-\end{equation}
-where $Z^\epl$ is the normalization term and where the likelihood function is given by
-\begin{equation}
-	p^\epl(X \mid A) = \exp\left(-\frac{I^\epl(X\mid A)}{2\Sigma} \right), 
-\end{equation}
-with
-\begin{equation}
-	I^\epl(X\mid A) = \int_0^T A \cdot V'(X_t^\epl) \dd X_t^\epl + \frac12 \int_0^T \left( A \cdot V'(X_t^\epl) \right)^2 \dd t.
-\end{equation}
-Let us consider the likelihood function $\widetilde p^\epl(X \mid A)$ modified to include the filtered data $Z^\epl$ given by
-\begin{equation}
-	\widetilde p^\epl(X \mid A) = \exp\left(-\frac{\widetilde I^\epl(X\mid A)}{2\Sigma} \right), 
-\end{equation}
-with
-\begin{equation}
-	\widetilde I^\epl(X\mid A) = \int_0^T A \cdot V'(Z_t^\epl) \dd X_t^\epl + \frac12 \int_0^T \left( A \cdot V'(X_t^\epl) \right) \left( A \cdot V'(Z_t^\epl) \right) \dd t.
-\end{equation}
-Moreover, let us consider the modified posterior distribution $\widetilde \mu^\epl(A \mid X)$ with density
-\begin{equation}
-	\widetilde p^\epl(A \mid X) = \frac1{\widetilde Z^\epl} \, \widetilde p^\epl(X \mid A) \, p_0(A),
-\end{equation}
-Let us remark that employing \eqref{eq:MandHTilde} we can write 
-\begin{equation}
-	\log \widetilde p^\epl(A \mid X) = -\log \widetilde Z^\epl - T A \cdot \widetilde h - \frac{T}{2} A \cdot \widetilde M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
-\end{equation}
-With respect to Section \ref{sec:Bayesian}, the matrix $\widetilde M$ is not symmetric. Nonetheless, we remark that
-\begin{equation}
-	A \cdot \widetilde M A = A \cdot \widetilde M_S A,
-\end{equation}
-where $\widetilde M_S$ is the symmetric part of $\widetilde M$, i.e.,
-\begin{equation}
-	\widetilde M_S = \frac12 \left(\widetilde M + \widetilde M^\top\right).
-\end{equation}
-Hence, we can rewrite 
-\begin{equation}	
-	\log \widetilde p^\epl(A \mid X) = -\log \widetilde Z^\epl - T A \cdot \widetilde h - \frac{T}{2} A \cdot \widetilde M_S A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
-\end{equation}
-This shows that the posterior $\widetilde \mu^\epl$ is a Gaussian $\mathcal N(\widetilde m_T, \widetilde C_T)$ where the covariance and mean can be obtained as 
-\begin{equation}
-\begin{aligned}
-	\widetilde C_T^{-1} &= C_0^{-1} + T \widetilde M, \\
-	\widetilde C_T^{-1} \widetilde m_T &= C_0^{-1}A_0 - T \widetilde h. 
-\end{aligned}
-\end{equation}
-
-In the following theorem we show that the posterior we obtain 
-\begin{theorem} Under
-\end{theorem}
+%\begin{equation}
+%	p^\epl(A \mid X) = \frac1{Z^\epl} \, p^\epl(X \mid A) \, p_0(A),
+%\end{equation}
+%where $Z^\epl$ is the normalization term and where the likelihood function is given by
+%\begin{equation}
+%	p^\epl(X \mid A) = \exp\left(-\frac{I^\epl(X\mid A)}{2\Sigma} \right), 
+%\end{equation}
+%with
+%\begin{equation}
+%	I^\epl(X\mid A) = \int_0^T A \cdot V'(X_t^\epl) \dd X_t^\epl + \frac12 \int_0^T \left( A \cdot V'(X_t^\epl) \right)^2 \dd t.
+%\end{equation}
+%Let us consider the likelihood function $\widetilde p^\epl(X \mid A)$ modified to include the filtered data $Z^\epl$ given by
+%\begin{equation}
+%	\widetilde p^\epl(X \mid A) = \exp\left(-\frac{\widetilde I^\epl(X\mid A)}{2\Sigma} \right), 
+%\end{equation}
+%with
+%\begin{equation}
+%	\widetilde I^\epl(X\mid A) = \int_0^T A \cdot V'(Z_t^\epl) \dd X_t^\epl + \frac12 \int_0^T \left( A \cdot V'(X_t^\epl) \right) \left( A \cdot V'(Z_t^\epl) \right) \dd t.
+%\end{equation}
+%Moreover, let us consider the modified posterior distribution $\widetilde \mu^\epl(A \mid X)$ with density
+%\begin{equation}
+%	\widetilde p^\epl(A \mid X) = \frac1{\widetilde Z^\epl} \, \widetilde p^\epl(X \mid A) \, p_0(A),
+%\end{equation}
+%Let us remark that employing \eqref{eq:MandHTilde} we can write 
+%\begin{equation}
+%	\log \widetilde p^\epl(A \mid X) = -\log \widetilde Z^\epl - T A \cdot \widetilde h - \frac{T}{2} A \cdot \widetilde M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
+%\end{equation}
+%With respect to Section \ref{sec:Bayesian}, the matrix $\widetilde M$ is not symmetric. Nonetheless, we remark that
+%\begin{equation}
+%	A \cdot \widetilde M A = A \cdot \widetilde M_S A,
+%\end{equation}
+%where $\widetilde M_S$ is the symmetric part of $\widetilde M$, i.e.,
+%\begin{equation}
+%	\widetilde M_S = \frac12 \left(\widetilde M + \widetilde M^\top\right).
+%\end{equation}
+%Hence, we can rewrite 
+%\begin{equation}	
+%	\log \widetilde p^\epl(A \mid X) = -\log \widetilde Z^\epl - T A \cdot \widetilde h - \frac{T}{2} A \cdot \widetilde M_S A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
+%\end{equation}
+%This shows that the posterior $\widetilde \mu^\epl$ is a Gaussian $\mathcal N(\widetilde m_T, \widetilde C_T)$ where the covariance and mean can be obtained as 
+%\begin{equation}
+%\begin{aligned}
+%	\widetilde C_T^{-1} &= C_0^{-1} + T \widetilde M, \\
+%	\widetilde C_T^{-1} \widetilde m_T &= C_0^{-1}A_0 - T \widetilde h. 
+%\end{aligned}
+%\end{equation}
+%
+%In the following theorem we show that the posterior we obtain 
+%\begin{theorem} Under
+%\end{theorem}
 
@@
 	\end{tabular}
-	\caption{Results for the four-dimensional parameters. From left to right the potential function estimated with (i) the data itself, (ii) the filter, (iii) subsampled data.}
+	\caption{Results for the four-dimensional parameters. From left to right the potential function estimated with the data itself, the filter, subsampled data.}
 	\label{fig:KLStyle}
@@
 
+\section{Conclusion}
+
+In this work we considered a novel methodology based on filtering for the estimation of the drift of multiscale diffusion processes.
+We proved results of ergodicity, convergence and, most importantly, unbiasedness of estimators drawn from our methodology.
+Moreover, we combined a Bayesian approach and our new technique to guarantee a robust uncertainty quantification of the inference procedure.
+Numerical experiments demonstrate how the filtering-based estimator requires less knowledge of the characteristic time-scales of the multiscale equation and how it can be employed as a black-box tool for parameter estimation on a range of academic examples.
+We believe this work gives way to several further developments.
+In particular, we believe it would be relevant to
+\begin{enumerate}
+	\item analyse the filtering methodology for $\beta > 1$ in \eqref{eq:filter}, which seems to give more robust results in practice,
+	\item extend the analysis to the non-parametric framework most likely by means of Bayesian regularization techniques,
+	\item consider multiscale models for which the homogenized equation presents multiplicative noise,
+	\item test the filtering methodology against real-world data,
+	\item apply similar filtering methodologies to correct faulty behaviour of non likelihood-based estimators.
+\end{enumerate}
+
 \bibliographystyle{siam}
-\bibliography{../anmc}
+\bibliography{anmc}
 \end{document}

### 2020-02-13 CalNotes.tex
First draft completed

@@
 
-\textbf{Abstract.} \corr{Copy-paste of SIAM UQ abstract, modify.} We present a novel technique for estimating the drift function of a diffusion process possessing two separated time scales.
-Our aim is fitting a homogenized diffusion model to a continuous sample path coming from the full multiscale process, thus dealing with an issue of model misspecification.
-We consider a Bayesian framework and study the asymptotic limit of posterior distributions over the drift function.
-In this setting, we show on the one hand that if the continuous multiscale data are not pre-processed, then the posterior distribution concentrates asymptotically on the wrong value of the drift function.
-On the other hand, we show that data can be treated ahead of the inference procedure in order to obtain the desired posterior.
-In particular, we prove that there exists a family of transformations which are linear on the space of continuous sample paths and which, when applied to multiscale data, allow the posterior distribution to be asymptotically correct.
-We present a series of numerical examples on test cases which corroborate our theoretical findings.
-
-\textbf{AMS subject classifications.}
-
-\textbf{Keywords.}
+\textbf{Abstract.} We study the problem of drift estimation for two-scale continuous time series.
+We set ourselves in the framework of overdamped Langevin equations, for which the existence of a single-scale surrogate homogenized equation exists.
+In this setting, estimating the drift coefficient of the homogenized equation requires pre-processing of the data, often in the form of subsampling.
+We avoid subsampling by filtering the data with an appropriate kernel function and computing maximum likelihood estimators based on the filtered process.
+We show that the estimators we propose are asymptotically unbiased and demonstrate numerically the advantages of our method with respect to subsampling.
+Finally, we show how our filtering methodology can be combined with Bayesian techniques and provide a full uncertainty quantification of the inference procedure.
+
+\textbf{AMS subject classifications.} 62F15, 65C30, 62M05, 74Q10.
+
+\textbf{Keywords.} Parameter inference, diffusion process, data-driven homogenization, filtering, Bayesian inference, Langevin equation.
 
@@
 In Section \ref{sec:Setting} we introduce the problem and lay the basis of our analysis setting the main assumptions and notation.
-In Section \ref{sec:Filter} we present our filtering methodology, with a particular focus on ergodic properties, on multiscale convergence and, naturally, to the properties of our estimator.
+In Section \ref{sec:Filter} we present our filtering methodology, with a particular focus on ergodic properties, on multiscale convergence and, naturally, to the properties of our estimators.
 In Section \ref{sec:Bayesian} we introduce the Bayesian framework and show how it can be enhanced with filtering techniques.
@@
 		\end{equation} 
+		\item $V'$ is Lipschitz continuous on $\R$: there exists a constant $C > 0$ such that
+		\begin{equation}
+			\norm{V'(x) - V'(y)} \leq C\abs{x - y},
+		\end{equation} 
 		\item for all $T > 0$, the symmetric matrix $M$ is positive definite and there exists $\bar \lambda > 0$ such that $\lambda_{\min}(M) \geq \bar \lambda$.
@@
 Let us furthermore remark that $\widehat A^\epl_k(T)$ need not be the minimizer of some filtering-based likelihood function.
-In fact, if one were to replace $Z_t^\epl$ directly in \eqref{eq:Likelihood}, the non-symmetric matrix $\widetilde M$ would appear and $\widehat A^\epl_k(T)$ would not be guaranteed of being the minimizer.
-Moreover, let us remark that even though
-\begin{equation}
-	\widetilde M = M + \Delta, \quad \Delta \defeq \widetilde M - M,
-\end{equation}
-where $\Delta$ is a matrix which is supposedly small due to the closeness of $X_t^\epl$ and its filtered version $Z_t^\epl$, this does not suffice to directly conclude that $\widetilde M$ is positive definite when $M$ is.
+In fact, if one were to replace $Z_t^\epl$ directly in \eqref{eq:Likelihood}, the symmetric part of the matrix $\widetilde M$ would appear and $\widehat A^\epl_k(T)$ would not be the minimizer.
 Therefore, the estimator $\widehat A^\epl_k(T)$ has to be thought of as a perturbation of $\widehat A^\epl(T)$, directly at the level of estimators and after the maximization procedure.
-The only theoretical guarantee which is still needed for the well-posedness of $\widehat A^\epl_k(T)$ is for $\widetilde M$ to be invertible, which is given by the following Lemma.
-
-\begin{lemma}\label{lem:AHatWellPosed} The matrix $\widetilde M$ defined in \eqref{eq:MandHTilde} is invertible almost surely. 
-\end{lemma}
-\begin{proof} 
-\todo: \corr{Idea.
+The only theoretical guarantee which is still needed for the well-posedness of $\widehat A^\epl_k(T)$ is for $\widetilde M$ to be invertible, which we assume to be true and which we observed to hold in practice.
+
+%\begin{lemma}\label{lem:AHatWellPosed} Under Assumption \ref{as:regularity}, the matrix $\widetilde M$ defined in \eqref{eq:MandHTilde} is invertible a.s. 
+%\end{lemma}
+%\begin{proof} 
+%\todo: \corr{Idea.
 We don't need $\widetilde M$ to be symmetric positive definite (it is not) due to the comment just above the lemma.
@@
 Still missing the (probably trivial) argument why this is true.}
-\end{proof}
+%\end{proof}
 
 We are now able to present the main result of unbiasedness of the filtering-based estimator.
-\begin{theorem}\label{thm:mainTheorem} Under the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure}, let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed}. Then
+\begin{theorem}\label{thm:mainTheorem} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, and let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed}.
+If $\widetilde M$ is invertible, then
 	\begin{equation}
@@
 
-\subsection{The filtering approach}
+\subsection{The filtering approach}\label{sec:BayesianFilter}
 
@@
 	\begin{tabular}{ccc}
-		\includegraphics[]{Figures/Bayes_T200} & \includegraphics[]{Figures/Bayes_T400}  & \includegraphics[]{Figures/Bayes_T800} \\
+		\includegraphics[]{Figures/Bayes_T100} & \includegraphics[]{Figures/Bayes_T200}  & \includegraphics[]{Figures/Bayes_T400} \\
 	\end{tabular}
 	\caption{Posterior distributions over the parameter $A = (A_1, A_2)^\top$ for the bistable potential obtained with the filtering approach.
-The figures refer to time $t = 200, 400, 800$ from left to right, respectively.
-The MLE $\widehat A$ is represented with a circle, while the true value $A$ of the drift coefficient of the homogenized equation is represented with a cross.}
+The figures refer to final time $T = 200, 400, 800$ from left to right, respectively.
+The MLE $\widetilde A^\epl_k(t)$ is represented with a circle, while the true value $A$ of the drift coefficient of the homogenized equation is represented with a cross.}
 	\label{fig:Bayes}
@@
 with coefficients $\alpha_1 = 1$ and $\alpha_2 = -2$.
-We then consider the multiscale equation with $\sigma = 0.8$, the fast potential $p(y) = \cos(y)$ and $\epl = 0.05$, thus simulating a trajectory $X^\epl$ for time $0 \leq t \leq T$, with $T = 800$.
-We adopt here a Bayesian approach and compute the posterior distribution $\mu(A \mid X^\epl)$ obtained with the filtering approach.
-The filter's parameters are set to $\beta = 1$ and $\delta = \epl^{1/2}$ in \eqref{eq:filter}.
+We then consider the multiscale equation with $\sigma = 0.7$, the fast potential $p(y) = \cos(y)$ and $\epl = 0.05$, thus simulating a trajectory $X^\epl$.
+We adopt here a Bayesian approach and compute the posterior distribution $\widetilde \mu_{\epl, T}$ obtained with the filtering approach introduced in Section \ref{sec:BayesianFilter}.
+The filter's parameters are set to $\beta = 1$ and $\delta = \epl$ in \eqref{eq:filter}.
 Let us remark that in order to compute the posterior covariance the diffusion coefficient $\Sigma$ of the homogenized equation has to be known.
 In this case, we pre-compute the value of $\Sigma$ via the coefficient $K$ and the theory of homogenization, but let us remark that $\Sigma$ could be estimated employing the subsampling technique of \cite{PaS07}.
-We stop computations at times $t = 200, 400, 800$ in order to observe the shrinkage of the Gaussian posterior towards the MLE with respect to time.
+We stop computations at times $T = 100, 200, 400$ in order to observe the shrinkage of the Gaussian posterior towards the MLE $\widetilde A^\epl_k(T)$ with respect to time.
 In Figure \ref{fig:Bayes}, we observe that the posterior does indeed shrink towards the MLE, which in turn gets progressively closer to the true value of the drift coefficient $A$ of the homogenized equation.

### 2020-02-14 CalNotes.tex
Proofreading

@@
 \textbf{Abstract.} We study the problem of drift estimation for two-scale continuous time series.
-We set ourselves in the framework of overdamped Langevin equations, for which the existence of a single-scale surrogate homogenized equation exists.
+We set ourselves in the framework of overdamped Langevin equations, for which a single-scale surrogate homogenized equation exists.
 In this setting, estimating the drift coefficient of the homogenized equation requires pre-processing of the data, often in the form of subsampling.
-We avoid subsampling by filtering the data with an appropriate kernel function and computing maximum likelihood estimators based on the filtered process.
+We avoid subsampling by filtering the data with an appropriate kernel function and compute maximum likelihood estimators based on the filtered process.
 We show that the estimators we propose are asymptotically unbiased and demonstrate numerically the advantages of our method with respect to subsampling.
@@
 
-Data-driven approaches to the derivation of effective stochastic coarse-grained dynamics has become a standard tool in different areas such as molecular dynamics or atmosphere and ocean science \cite{KKP15,CoP09,YMV19}.
+Data-driven approaches to the derivation of effective stochastic coarse-grained dynamics have become a standard tool in different areas such as molecular dynamics or atmosphere and ocean science \cite{KKP15,CoP09,YMV19}.
 When fitting data to a low dimensional coarse-grained model, one is faced with the problem of model misspecification; indeed, the data, coming from the full dynamics, is compatible with the coarse-grained model only at the time scales at which the effective dynamics is valid.
@@
 Being these problems ill-posed, the latter is achieved via Tikhonov regularization \cite{AbD19,NPS12}, adopting a Bayesian approach \cite{AbD18, NPS12} or exploiting techniques of Kalman filtering \cite{AGZ19}.
-In \cite{AbD18,AGZ19}, the authors highlight the need of accounting explicitly for the modelling error due to homogenisation and apply statistical techniques taken from \cite{CDS18,CES14}.
+In \cite{AbD18,AGZ19}, the authors highlight the need of accounting explicitly for the modelling error due to homogenization and apply statistical techniques taken from \cite{CDS18,CES14}.
 
 For simple models in molecular dynamics, the effect of model misspecification was studied in a series of papers \cite{PaS07,PPS09,PPS12,GaS17,GaS18} under the assumption of scale separation.
-In particular, for Brownian particles moving in two-scale potentials it was shown that, when fitting data from the full dynamics to the homogenised equation, the maximum likelihood estimator (MLE) is asymptotically biased \cite[Theorem 3.4]{PaS07}.
-To be more precise, in the large sample size limit the MLE converges to the coefficients of the unhomogenised equation, rather than to those of the homogenised one.
+In particular, for Brownian particles moving in two-scale potentials it was shown that, when fitting data from the full dynamics to the homogenized equation, the maximum likelihood estimator (MLE) is asymptotically biased \cite[Theorem 3.4]{PaS07}.
+To be more precise, in the large sample size limit the MLE converges to the coefficients of the unhomogenized equation, rather than to those of the homogenized one.
 The bias of the MLE can be eliminated by subsampling at an appropriate rate, which lies between the two characteristic time scales of the problem \cite[Theorems 3.5 and 3.6]{PaS07}.
@@
 In Section \ref{sec:Setting} we introduce the problem and lay the basis of our analysis setting the main assumptions and notation.
-In Section \ref{sec:Filter} we present our filtering methodology, with a particular focus on ergodic properties, on multiscale convergence and, naturally, to the properties of our estimators.
+In Section \ref{sec:Filter} we present our filtering methodology, with a particular focus on ergodic properties, on multiscale convergence and, naturally, on the properties of our estimators.
 In Section \ref{sec:Bayesian} we introduce the Bayesian framework and show how it can be enhanced with filtering techniques.
@@
 where, given a positive integer $N$, we have that $\alpha \in \R^N$ and $\sigma > 0$ are the drift and diffusion coefficients respectively and $W_t$ is a standard one-dimensional Brownian motion.
-The functions $V\colon \R \to \R^N$ and $p\colon \R \to \R$ correspond to the fast-scale and the slow-scale confining potentials.
+The functions $V\colon \R \to \R^N$ and $p\colon \R \to \R$ correspond to the slow-scale and the fast-scale confining potentials.
 In particular, we assume
@@
 \end{equation}
-where $W_t$ is the same Brownian motion as in \eqref{eq:SDE_MS}, such that $X_t^\epl \to X_t$ for $\epl\to 0$ in law as random variables in $\mathcal C^0((0, T); \R)$.
-In particular, we have $A_i = K\alpha_i$ and $\Sigma = K \sigma$, where the coefficient $K$ is given by the formula
+where $W_t$ is the same Brownian motion as in \eqref{eq:SDE_MS}, such that $X_t^\epl \to X_t$ for $\epl\to 0$ in law as random variables in $\mathcal C^0([0, T]; \R)$.
+In particular, we have $A = K\alpha$ and $\Sigma = K \sigma$, where the coefficient $K$ is given by the formula
 \begin{equation}\label{eq:K_HOM}
@@
 \end{equation}
-and where the function $\Phi$ is the solution of the elliptic partial differential equation
+and where the function $\Phi$ is the unique solution with zero-mean with respect to the measure $\mu$ of the elliptic partial differential equation
 \begin{equation}
@@
 We now briefly present the classical methodology for estimating the drift coefficient.
-Let $T > 0$ and let $X^\epl \defeq (X^\epl_t, 0\leq t, \leq T)$ be a realization of the solution of \eqref{eq:SDE_MS} up to final time.
-Girsanov's change of measure formula applied to \eqref{eq:SDE_HOM} allows to write the likelihood of $X^\epl$ given a drift coefficient $A$ of \eqref{eq:SDE_HOM} as
+Let $T > 0$ and let $X^\epl \defeq (X^\epl_t, 0\leq t \leq T)$ be a realization of the solution of \eqref{eq:SDE_MS} up to final time.
+Girsanov's change of measure formula applied to \eqref{eq:SDE_HOM} allows to write the likelihood of $X^\epl$ given a drift coefficient $A$ as
 \begin{equation}\label{eq:Likelihood}
@@
 \end{equation}
-and where $\otimes$ denotes the tensor product in $\R^N$.
-Let us now state the assumptions which will be employed throughout the rest of our work. In particular, we consider the same dissipative setting as \cite[Assumption 3.1]{PaS07}.
+and where $\otimes$ denotes the outer product in $\R^N$.
+Let us now state the assumptions which will be employed throughout the rest of our work.
+In particular, we consider the same dissipative setting as \cite[Assumption 3.1]{PaS07}.
 \begin{assumption}\label{as:regularity} The potentials $p$ and $V$ satisfy
@@
 		\begin{equation}
-			\norm{V'(x) - V'(y)} \leq C\abs{x - y},
+			\norm{V'(x) - V'(y)}_2 \leq C\abs{x - y},
 		\end{equation} 
@@
 
-\begin{remark} Given a trajectory $X^\epl \defeq (X^\epl_t, 0\leq t \leq T)$, it is relatively inexpensive to compute $Z^\epl$ from a computational standpoint.
+\begin{remark} Given a trajectory $X^\epl$, it is relatively inexpensive to compute $Z^\epl$ from a computational standpoint.
 In particular, the process $Z^\epl$ is the truncated convolution of the kernel with the process $X^\epl$.
 Hence, computational tools based on the Fast Fourier Transform (FFT) exist and allow to compute $Z^\epl$ fast component-wise.
-Moreover, the process $Z_t^\epl$ can be computed, in case $\beta = 1$, in a recursive manner and therefore ``online''.
+Moreover, the process $Z^\epl$ can be computed, in case $\beta = 1$, in a recursive manner and therefore ``online''.
 \end{remark}
@@
 In particular, we focus on ergodic properties and multiscale convergence.
-Finally, we present and analyse an unbiased estimator obtained with the filtering process.
+Finally, we present and analyse unbiased estimators obtained with the filtering process.
 
@@
 \begin{lemma}\label{lem:ergodicity} Let Assumption \ref{as:regularity} hold and let $b > 0$ be given in Assumption \ref{as:regularity}\ref{as:regularity_diss}.
-Then, if $\delta > 1/(4b)$, the process $(X^\epl, Z^\epl)^\top$ solution of \eqref{eq:systemSDE} is geometrically ergodic, i.e., there exists $C, \lambda > 0$ such that for all measurable $f$ such that for some integer $q > 0$
-	\begin{equation}
-		f(x) \leq 1 + \abs{x}^q,
+Then, if $\delta > 1/(4b)$, the process $(X^\epl, Z^\epl)^\top$ solution of \eqref{eq:systemSDE} is geometrically ergodic, i.e., there exists $C, \lambda > 0$ such that for all measurable $f\colon \R^2\to \R$ such that for some integer $q > 0$
+	\begin{equation}
+		f(x, z) \leq 1 + \norm{\begin{pmatrix} x & z \end{pmatrix}^\top}_2^q,
 	\end{equation}
@@
 	\begin{equation}
-		\abs{\E f(X^\epl_t, Z^\epl_t) - \int_\R\int_\R f(x, z) \rho^\epl(x, z) \dd x \dd z} \leq C\left(1 + \norm{\begin{pmatrix} X^\epl_0 & Z^\epl_0 \end{pmatrix}^\top}^q \right)e^{-\lambda t},
+		\abs{\E f(X^\epl_t, Z^\epl_t) - \int_\R\int_\R f(x, z) \rho^\epl(x, z) \dd x \dd z} \leq C\left(1 + \norm{\begin{pmatrix} X^\epl_0 & Z^\epl_0 \end{pmatrix}^\top}_2^q \right)e^{-\lambda t},
 	\end{equation}
@@
 \begin{equation}
-	 \mathcal S(x,z) \defeq \begin{pmatrix} -\sum_{i=1}^N V_i'(x) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} = -\sum_{i=1}^N V_i'(x)x+\frac1\delta(xz-z^2)
+	 \mathcal S(x,z) \defeq \begin{pmatrix} -\sum_{i=1}^N V_i'(x) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} = -\sum_{i=1}^N V_i'(x)x+\frac1\delta(xz-z^2).
 \end{equation}
@@
 \end{equation}
-We choose $\gamma = \gamma^* \defeq 1 - b\delta + \sqrt{2-2b\delta+b^2\delta^2} > 0$ so that
+We choose $\gamma = \gamma^* \defeq 1 - b\delta + \sqrt{1 + (1 - b\delta)^2} > 0$ so that
 \begin{equation}
@@
 
-\begin{remark} Let us remark that for the multiscale equation \eqref{eq:SDE_MS} one should check the condition above for the drift function $V(x) + \epl^{-1}p(x/\epl)$.
-Nevertheless, being $p$ bounded, the result holds trivially.
+\begin{remark} Let us remark that for the multiscale equation \eqref{eq:SDE_MS} one should check the condition above for the potential $V(x) + p(x/\epl)$.
+Nevertheless, for functions $p$ satisfying Assumption \ref{as:regularity}, the result holds trivially.
 \end{remark}
@@
 Then, Assumption \ref{as:regularity}\ref{as:regularity_diss} holds for an arbitrarily large $b > 0$.
-Therefore, the filter's parameter $\delta$ can be chosen along the entire positive real axis.
+Therefore, the parameter of the filter $\delta$ can be chosen along the entire positive real axis.
 A similar argument can be employed for higher dimensions $N > 1$.
@@
 Let us remark that this distribution can be obtained from direct computations involving Gaussian processes.
-In particular, it is known that $X_t \sim \mathcal{GP}(\mu_t, \mathcal C(t, s))$, where at stationarity $\mu_t = 0$ and
+In particular, it is known that $X \sim \mathcal{GP}(\mu_t, \mathcal C(t, s))$, where at stationarity $\mu_t = 0$ and
 \begin{equation}
@@
 \label{FPx}
-\sigma (\phi^\epl)''(x) + \left ( \alpha \cdot V''(x) + \frac{1}{\epl^2} p'' \left ( \frac{x}\epl \right ) \right ) \phi^\epl(x) + \left ( \alpha \cdot V'(x) + \frac{1}\epl p' \left ( \frac{x}\epl \right ) \right ) (\phi^\epl)'(x) = 0,
+\sigma (\phi^\epl)''(x) + \frac{\d}{\d x} \left( \left ( \alpha \cdot V'(x) + \frac{1}{\epl} p' \left ( \frac{x}\epl \right ) \right ) \phi^\epl(x)\right) = 0,
 \end{equation}
@@
 \end{equation}
-Replacing the decomposition \eqref{eq:densityDecomposition} in equation \eqref{eq:FPsystem} and using equation \eqref{FPx} we obtain the following equality
+In view of \eqref{eq:densityDecomposition} and \eqref{FPx}, equation \eqref{eq:FPsystem} can be rewritten as
 \begin{equation}\label{eq:psiEqualityPDE}
@@
 Moreover, standard homogenization theory (see e.g.
-\cite[Chapter 3]{BLP78}) guarantees that$(X^\epl,Z^\epl)^\top \to (X,Z)^\top$ for $\epl \to 0$ in law as random variables with values in $\mathcal C^0((0, T); \R^2)$.
+\cite[Chapter 3]{BLP78}) guarantees that $(X^\epl,Z^\epl)^\top \to (X,Z)^\top$ for $\epl \to 0$ in law as random variables with values in $\mathcal C^0([0, T]; \R^2)$.
 The Portmanteau theorem can be employed to conclude that the measure $\mu^\epl$ converges weakly to $\mu^0$ for $\epl \to 0$.
@@
 
-\begin{proof} Replacing the expression of $\d X^\epl_t$ into \eqref{eq:AHatMixed}, we get for $\widetilde h$
+\begin{proof} Replacing the expression of $\d X^\epl_t$ into \eqref{eq:MandHTilde}, we get for $\widetilde h$
 \begin{equation}\label{Ahat_decomposition}
@@
 Therefore, we have
-\begin{equation}
+\begin{equation}\label{eq:alphaDecomposition}
 \begin{aligned}
@@
 \end{equation}
-We study the terms $I_1^\epl$ and $I_2^\epl$ separately. The ergodic theorem applied to $I_1^\epl$ yields
+We study the terms $I_1^\epl(T)$ and $I_2^\epl(T)$ separately. The ergodic theorem applied to $I_1^\epl(T)$ yields
 \begin{equation}\label{limit_estimator}
@@
 	\begin{aligned}[t]
-		&- \left(\int_{\R} \int_{\R} V'(Z^\varepsilon_t) \otimes V'(X^\varepsilon_t) \rho^\epl(x, z) \dd x \dd z\right) \alpha \\
+		&- \left(\int_{\R} \int_{\R} V'(z) \otimes V'(x) \rho^\epl(x, z) \dd x \dd z\right) \alpha \\
 		&+\sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z 
@@
 \end{equation}
-where the function $\rho^0$ is the density of the limit invariant distribution for $\epl \to 0$, as in Lemma \ref{lem:convMeasure}. Due to Lemma \ref{lem:FPMarginal_Hom}, we have
+where the function $\rho^0$ is the density of the limit invariant distribution for $\epl \to 0$, as in Lemma \ref{lem:convMeasure}. Due to Corollary \ref{lem:FPMarginal_Hom}, we have
 \begin{equation}\label{eq:final_result}
@@
 	\frac{1}{\delta} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] &= -\Sigma \int_{\R} \int_{\R} V'(z) (\phi^0)'(x) \psi^0(z) R^0(x,z) \dd x \dd z\\
-	&= -\Sigma \int_{\R} \int_{\R} V'(z) \left ( \frac{1}{C_{\phi^0}} e^{-\frac{1}{\Sigma} A\cdot V(x)} \right )' \psi^0(z) R^0(x,z) \dd x \dd z \\
+	&= -\Sigma \int_{\R} \int_{\R} V'(z) \frac{\d}{\d x} \left ( \frac{1}{C_{\phi^0}} e^{-\frac{1}{\Sigma} A\cdot V(x)} \right ) \psi^0(z) R^0(x,z) \dd x \dd z \\
 	&= \left(\int_{\R} \int_{\R} V'(z) \otimes V'(x) \rho^0(x,z) \dd x \dd z\right)A\\
-	&=  \E^{\rho^0} [ V'(Z) \otimes V'(X) ]A
+	&=  \E^{\rho^0} [ V'(Z) \otimes V'(X) ]A.
 \end{aligned}
@@
 \end{equation}
-We now consider the second term $I_2^\epl$, and rewrite it as
-\begin{equation}
-	I^\epl_2(T) = -\sqrt{2\sigma} I_{2,1}^\epl(T)  I_{2,2}^\epl(T),
+We now consider the second term $I_2^\epl(T)$, and rewrite it as
+\begin{equation}
+	I^\epl_2(T) = \sqrt{2\sigma} I_{2,1}^\epl(T)  I_{2,2}^\epl(T),
 \end{equation}
@@
 	I_{2,1}^\epl(T) &\defeq \left(\frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\left(\frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t\right),\\
-	I_{2,2}^\epl(T) &\defeq \left(\frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t\right)^{-1}\int_0^T V'(Z^\epl_t) \dd W_t.
+	I_{2,2}^\epl(T) &\defeq \left(\frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t\right)^{-1} \left(\frac1T \int_0^T V'(Z^\epl_t) \dd W_t\right).
 \end{aligned}
@@
 \begin{equation}
-	\lim_{T \to \infty} I_{2,1}^\epl(T) = \E^{\rho^\epl}\left[V'(Z^\epl) \otimes V'(X^\epl)\right]^{-1}\E^{\rho^\epl}\left[V'(Z^\epl) \otimes V'(Z^\epl)\right] \eqdef M^\epl,
-\end{equation}
-where $M^\epl$ is bounded uniformly in $\epl$. Moreover, the strong law of large numbers for martingales implies
+	\lim_{T \to \infty} I_{2,1}^\epl(T) = \E^{\rho^\epl}\left[V'(Z^\epl) \otimes V'(X^\epl)\right]^{-1}\E^{\rho^\epl}\left[V'(Z^\epl) \otimes V'(Z^\epl)\right] \eqdef R^\epl,
+\end{equation}
+where $R^\epl$ is bounded uniformly in $\epl$. Moreover, the strong law of large numbers for martingales implies
 \begin{equation}
@@
 \end{equation}
-which, together with \eqref{eq:Proof_I1}, proves the desired result.
+which, together with \eqref{eq:Proof_I1} and \eqref{eq:alphaDecomposition}, proves the desired result.
 \end{proof}
@@
 where the matrix $M$ is taken from \eqref{eq:MandH} and the vector $\widetilde{h}$ is taken from \eqref{eq:MandHTilde}.
-For this estimator, which has the advantage of being well-posed due to Assumption \ref{as:regularity}, we will be able to prove a result of unbiasedness under a condition on the filtering parameter $\delta$.
+For this estimator we will be able to prove a result of unbiasedness under a condition on the filtering parameter $\delta$.
+Let us remark that for $\widehat A^\epl_k(T)$ we do not need any condition on this parameter.
+Nevertheless, this second estimator is the minimizer of a likelihood function unlike the first, and will therefore be used in the Bayesian framework.
 Let us start with an estimate concerning the distance between $X^\epl$ and $Z^\epl$.
 
-\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$. Then
+\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
+Then, if $\delta \leq 1$, it holds for any integer $p \geq 1$
 	\begin{equation}
@@
 	\end{equation}
-	Therefore, Jensen's inequalities yields for a constant depending only on $p$
+	Therefore, Jensen's inequalities yields for a constant $C > 0$ depending only on $p$
 	\begin{equation}
@@
 		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} &\leq C (1 - e^{-t/\delta})^{2p} \int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} \kappa_t (\d s) + C e^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p}\\
-		&\leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} k(t-s) \dd s + Ce^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p}
+		&\leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} k(t-s) \dd s + Ce^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p},
 	\end{aligned}
@@
 	\end{equation}
-	which implies that there exists a constant $C > 0$ and depending only on $p$ such that
+	which implies that there exists a constant $C > 0$ depending only on $p$ such that
 	\begin{equation}
@@
 	\end{equation}
-	The Lipschitz condition on $V$ together with the boundedness of the moments of $X^\epl$ and Lemma \ref{lem:distanceZandX} yields for a constant $C > 0$
+	The Lipschitz condition on $V$ together with the boundedness of the moments of $X^\epl$ and Lemma \ref{lem:distanceZandX} yield for a constant $C > 0$
 	\begin{equation}
@@
 
-We finally can prove the unbiasedness of the estimator $\widetilde A^\epl_k(T)$.
+We can finally prove the unbiasedness of the estimator $\widetilde A^\epl_k(T)$.
 
@@
 	\end{equation}
-	Therefore, due to Theorem \ref{thm:mainTheorem}, the inequality \eqref{eq:DistATildeAHat} and since $\delta \to 0$ for $\epl \to 0$, the desired result holds almost surely.
+	Therefore, due to Theorem \ref{thm:mainTheorem}, the inequality \eqref{eq:DistATildeAHat} and since $\delta \to 0$ for $\epl \to 0$, the desired result holds.
 \end{proof}
@@
 Let us fix a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$ on $A$, where $A_0 \in \R^N$ and $C_0 \in \R^{N\times N}$ is symmetric positive definite.
-Then, given a final time $T > 0$, the posterior distribution $\mu_T$ admits a density $p(A \mid X^\epl)$ with respect to the Lebesgue measure which satisfies
+Then, given a final time $T > 0$, the posterior distribution $\mu_{T,\epl}$ admits a density $p(A \mid X^\epl)$ with respect to the Lebesgue measure which satisfies
 \begin{equation}
@@
 	\begin{equation}
-		\norm{M^{-1}}_2 \leq \frac1{\bar \lambda}
+		\norm{M^{-1}}_2 \leq \frac1{\bar \lambda}.
 	\end{equation}
@@
 	\end{equation}
-	Let us now consider the first term.	Replacing the expression of the maximum likelihood estimator and due to the Cauchy--Schwarz and triangle inequalities, we obtain
+	Let us now consider the first term.	Replacing the expression of the maximum likelihood estimator \eqref{eq:MLE} and due to the Cauchy--Schwarz and triangle inequalities, we obtain
 	\begin{equation}
@@
 	\caption{Posterior distributions over the parameter $A = (A_1, A_2)^\top$ for the bistable potential obtained with the filtering approach.
-The figures refer to final time $T = 200, 400, 800$ from left to right, respectively.
+The figures refer to final time $T = 100, 200, 400$ from left to right, respectively.
 The MLE $\widetilde A^\epl_k(t)$ is represented with a circle, while the true value $A$ of the drift coefficient of the homogenized equation is represented with a cross.}
@@
 \begin{equation}
-	V(x) = \begin{pmatrix} \dfrac{x^4}{4} & \dfrac{x^2}{2} \end{pmatrix}^\top,
-\end{equation}
-with coefficients $\alpha_1 = 1$ and $\alpha_2 = -2$.
+	V(x) = \begin{pmatrix} \dfrac{x^4}{4} & -\dfrac{x^2}{2} \end{pmatrix}^\top,
+\end{equation}
+with coefficients $\alpha_1 = 1$ and $\alpha_2 = 2$.
 We then consider the multiscale equation with $\sigma = 0.7$, the fast potential $p(y) = \cos(y)$ and $\epl = 0.05$, thus simulating a trajectory $X^\epl$.
-We adopt here a Bayesian approach and compute the posterior distribution $\widetilde \mu_{\epl, T}$ obtained with the filtering approach introduced in Section \ref{sec:BayesianFilter}.
-The filter's parameters are set to $\beta = 1$ and $\delta = \epl$ in \eqref{eq:filter}.
+We adopt here a Bayesian approach and compute the posterior distribution $\widetilde \mu_{T, \epl}$ obtained with the filtering approach introduced in Section \ref{sec:BayesianFilter}.
+The parameters of the filter are set to $\beta = 1$ and $\delta = \epl$ in \eqref{eq:filter}.
 Let us remark that in order to compute the posterior covariance the diffusion coefficient $\Sigma$ of the homogenized equation has to be known.

### 2020-02-14 CalNotes.tex
Chebyshev

@@
 	\end{equation}
-	weakly in the space of probability measures on $\R$, where $\delta$ is the Dirac measure on $\R$.
+	weakly in the space of probability measures on $\R^N$, where $\delta$ is the Dirac measure on $\R^N$.
 \end{theorem}
@@
 	\end{tabular}
-	\caption{Results for the four-dimensional parameters. From left to right the potential function estimated with the data itself, the filter, subsampled data.}
+	\caption{Results for the four-dimensional parameter. From left to right the potential function estimated with the data itself, the filter, subsampled data.}
 	\label{fig:KLStyle}
@@
 
-We consider $N = 4$ and the potential function $V(x)$ as in \eqref{eq:Potential} with
-\begin{equation}
-	V_i(x) = \frac{x^{2i}}{2i}, \quad i =1, \ldots, 4,
-\end{equation}
-so that $\alpha \cdot V'(x) = \alpha_1 x + \alpha_2 x^3 + \alpha_3 x^5 + \alpha_4 x^7$, with $\alpha = (-2, -1, 1, 1/2)$.
-We consider $\epl = 0.05$, the fast potential $p(y) = \cos(y)$ and simulate a trajectory of $X^\epl$ for $0 \leq t \leq T$ with $T = 10^3$ employing the Euler--Maruyama method with time step $\Delta_t = \epl^3$.
-We compute the MLE of the drift coefficient $A \in \R^4$ of the homogenized equation \eqref{eq:SDE_HOM} employing
+\begin{table}[t]
+	\centering
+	\begin{tabular}{ccccc}
+		\toprule
+		Coefficient & Truth & No preprocessing & Filtering & Subsampling  \\ 
+		\midrule
+		$A_1$ & -0.62 & -0.92 & -0.70 & -0.59\\
+		$A_2$ & -0.31 & -0.70 & -0.27 & 0.05 \\
+		$A_3$ & 0.31  & 0.55  & 0.31  & 0.14 \\
+		$A_4$ & 0.62  & 1.22  & 0.57  & 0.13 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Numerical results for the four-dimensional parameter rounded to the second significant figure.}
+	\label{tab:KLStyle}
+\end{table}
+
+Let us consider the Chebyshev polynomials of the first kind, i.e., the polynomials $T_i\colon \R \to \R$, $i=0, 1, \ldots$, defined by the recurrence relation
+\begin{equation}
+	T_0(x) = 1, \quad T_1(x) = x, \quad T_{i+1}(x) = 2xT_i(x) - T_{i-1}(x).
+\end{equation}
+We consider the potential function $V(x)$ as in \eqref{eq:Potential} with
+\begin{equation}
+	V_i(x) = T_i(x), \quad i =1, \ldots, 4.
+\end{equation}
+This potential function satisfies Assumption \ref{as:regularity} whenever $N$ is even and if the leading coefficient $\alpha_N$ is positive.
+We set $N = 4$ and the drift coefficient $\alpha = (-1, -1/2, 1/2, 1)$.
+With this drift coefficient, the potential function is of the bistable kind.
+Moreover, we set $\epl = 0.05$, the diffusion coefficient $\sigma = 1$, the fast potential $p(y) = \cos(y)$ and simulate a trajectory of $X^\epl$ for $0 \leq t \leq T$ with $T = 10^3$ employing the Euler--Maruyama method with time step $\Delta_t = \epl^3$.
+We estimate the drift coefficient $A \in \R^4$ with the estimators
 \begin{enumerate}
-	\item the data $X^\epl$ itself,
-	\item subsampled data with subsampling parameter $\delta = \epl^{2/3}$,
-	\item filtered data $Z^\epl$ computed with $\beta = 1$ and $\delta = 0.2$.
+	\item $\widehat A^\epl(T)$ based on the data $X^\epl$ itself,
+	\item $\widehat A^\epl_\delta(T)$ based on subsampled data with subsampling parameter $\delta = \epl^{2/3}$,
+	\item $\widehat A^\epl_k(T)$ based on filtered data $Z^\epl$ computed with $\beta = 1$ and $\delta = 1$.
 \end{enumerate}
 In particular, we pick this specific value of $\delta$ for the subsampling following the optimality criterion given in \cite{PaS07}.
-Results, given in Figure \ref{fig:KLStyle}, show that the filter-based estimation captures well the homogenized potential.
+Results, given in Figure \ref{fig:KLStyle} and Table \ref{tab:KLStyle}, show that the filter-based estimation captures well the homogenized potential as well as the coefficient $A$.
+Moreover, it is possible to remark the negative result given by Theorem \ref{thm:Bias} holds in practice, i.e., with no pre-processing the estimator $\widehat A^\epl(T)$ tends to the drift coefficient $\alpha$ of the unhomogenized equation.
 

### 2020-02-14 CalNotes.tex
some correction

@@
 Data-driven approaches to the derivation of effective stochastic coarse-grained dynamics have become a standard tool in different areas such as molecular dynamics or atmosphere and ocean science \cite{KKP15,CoP09,YMV19}.
-When fitting data to a low dimensional coarse-grained model, one is faced with the problem of model misspecification; indeed, the data, coming from the full dynamics, is compatible with the coarse-grained model only at the time scales at which the effective dynamics is valid.
+When fitting data to a low dimensional coarse-grained model, one is faced with the problem of model misspecification; indeed, the data, coming from the full dynamics, are compatible with the coarse-grained model only at the time scales at which the effective dynamics is valid.
 This is related to the issue of high-frequency data that arises in econometrics \cite{AiJ14,AMZ05,ZMA05,OSP10}.
@@
 The bias of the MLE can be eliminated by subsampling at an appropriate rate, which lies between the two characteristic time scales of the problem \cite[Theorems 3.5 and 3.6]{PaS07}.
-This is similar to the estimation of the integrated stochastic volatility in the presence of market micro-structure noise, where the data has to be subsampled at an appropriate rate \cite{AMZ05,ZMA05}.
+This is similar to the estimation of the integrated stochastic volatility in the presence of market micro-structure noise, where the data have to be subsampled at an appropriate rate \cite{AMZ05,ZMA05}.
 The correct subsampling rate can be in some instances rather extreme with respect to the frequency of the data and lead to get rid of more than $99\%$ of the data.
@@
 \begin{equation}\label{eq:MandH}
-M = \frac1{2\Sigma T} \int_0^T V'(X^\epl_t) \otimes V'(X^\epl_t) \dd t, \quad h = \frac1{2\Sigma T} \int_0^T V'(X^\epl_t) \dd X^\epl_t,
+M = \frac1T \int_0^T V'(X^\epl_t) \otimes V'(X^\epl_t) \dd t, \quad h = \frac1T \int_0^T V'(X^\epl_t) \dd X^\epl_t,
 \end{equation}
@@
 		\end{equation} 
-		\item $V'$ is Lipschitz continuous on $\R$: there exists a constant $C > 0$ such that
+		\item $V'$ is Lipschitz continuous, i.e. there exists a constant $C > 0$ such that
 		\begin{equation}
@@
 
-\begin{theorem}\label{thm:Bias} Let Assumption \ref{as:regularity} hold and let $X^\epl_0$ be distributed according to the invariant measure of the process $X_t^\epl$ solution of \eqref{eq:SDE_MS}.
-Then
+\begin{theorem}\label{thm:Bias} Let Assumption \ref{as:regularity} hold and let $X^\epl_0$ be distributed according to the invariant measure of the process $X^\epl$ solution of \eqref{eq:SDE_MS}. Then
 	\begin{equation}
@@
 \end{equation}
-The basic properties of Gaussian processes imply that $Z_t$ is a Gaussian process, and that the couple $(X_t, Z_t)^\top$ is a Gaussian process, too, whose mean and covariance are computable explicitly.
+The basic properties of Gaussian processes imply that $Z$ is a Gaussian process, and that the couple $(X, Z)^\top$ is a Gaussian process, too, whose mean and covariance are computable explicitly.
 \end{example}
@@
 \begin{equation}\label{eq:Posterior}
-\log p(A \mid X^\epl) = -\log Z^\epl - T A \cdot h - \frac{T}{2} A \cdot M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0),
+\log p(A \mid X^\epl) = -\log Z^\epl - \frac{T}{2\Sigma} A \cdot h - \frac{T}{4\Sigma} A \cdot M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0),
 \end{equation}
@@
 \begin{aligned}
-C_{T,\epl}^{-1} &= C_0^{-1} + T M, \\
-C_{T,\epl}^{-1}m_{T,\epl} &= C_0^{-1}A_0 - T h. 
+C_{T,\epl}^{-1} &= C_0^{-1} + \frac{T}{2\Sigma} M, \\
+C_{T,\epl}^{-1}m_{T,\epl} &= C_0^{-1}A_0 - \frac{T}{2\Sigma} h. 
 \end{aligned}
@@
 	\begin{equation}
-	C_{T,\epl} = T^{-1} \left(M^{-1} - Q^{-1}\right),
+	C_{T,\epl} = \frac{2\Sigma}{T} \left(M^{-1} - Q^{-1}\right),
 	\end{equation}
@@
 	\begin{equation}
-	Q = M + T M C_0 M.
+	Q = M + \frac{T}{2\Sigma} M C_0 M.
 	\end{equation}
@@
 	\begin{equation}
-		\norm{Q^{-1}}_2 \leq \frac1T \norm{(MC_0M)^{-1}}_2 \leq \frac1T \norm{M^{-1}}_2^2 \norm{C_0^{-1}}_2 = \frac1{T\bar \lambda^2} \norm{C_0^{-1}}_2,
+		\norm{Q^{-1}}_2 \leq \frac{2\Sigma}T \norm{(MC_0M)^{-1}}_2 \leq \frac{2\Sigma}T \norm{M^{-1}}_2^2 \norm{C_0^{-1}}_2 = \frac{2\Sigma}{T\bar \lambda^2} \norm{C_0^{-1}}_2,
 	\end{equation}
@@
 	\begin{aligned}
-		\norm{m_{T,\epl} - \widehat A^\epl(T)}_2 &= \frac1T\norm{M^{-1}C_0^{-1}A_0 - Q^{-1}\left(C_0^{-1}A_0 - Th \right)}_2\\
-		&\leq \frac1{T\bar \lambda} \norm{C_0^{-1}}_2 \left(\norm{A_0}_2 + \frac1{\bar \lambda}\norm{h}_2 + \frac1{T\bar \lambda} \norm{C_0^{-1}}_2\norm{A_0}_2\right).
+		\norm{m_{T,\epl} - \widehat A^\epl(T)}_2 &= \frac{2\Sigma}T\norm{M^{-1}C_0^{-1}A_0 - Q^{-1}\left(C_0^{-1}A_0 - \frac{T}{2\Sigma} h \right)}_2\\
+		&\leq \frac{2\Sigma}{T\bar \lambda} \norm{C_0^{-1}}_2 \left(\norm{A_0}_2 + \frac1{\bar \lambda}\norm{h}_2 + \frac{2\Sigma}{T\bar \lambda} \norm{C_0^{-1}}_2\norm{A_0}_2\right).
 	\end{aligned}
@@
 \begin{aligned}
-	C_{T, \epl}^{-1} &= C_0^{-1} + T M, \\
-	C_{T,\epl}^{-1}\widetilde m_{T,\epl} &= C_0^{-1}A_0 - T \widetilde h. 
+	C_{T, \epl}^{-1} &= C_0^{-1} + \frac{T}{2\Sigma} M, \\
+	C_{T,\epl}^{-1}\widetilde m_{T,\epl} &= C_0^{-1}A_0 - \frac{T}{2\Sigma} \widetilde h. 
 \end{aligned}	

### 2020-02-25 CalNotes.tex
Figures fix
Modifications after discussion with Assyr

@@
 \documentclass[10pt]{article}
-%\documentclass{siamart1116}
 
@@
 \begin{aligned}
-\d X_t^\epl &= -\alpha \cdot V'(X_t^\epl) \dd t - \frac1\epl p'\left(\frac{X_t^\epl}\epl\right) + \sqrt{2\sigma} \dd W_t, \\
+\d X_t^\epl &= -\alpha \cdot V'(X_t^\epl) \dd t - \frac1\epl p'\left(\frac{X_t^\epl}\epl\right) \dd t+ \sqrt{2\sigma} \dd W_t, \\
 \d Z^\epl_t &= \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
@@
 
-\subsection{A second filtering-based estimator}\label{sec:FilterMLE_2}
-
-In this section we consider a modification to the estimator \eqref{eq:AHatMixed}, which is defined as
-\begin{equation}\label{eq:AHatMixedTilde}
-	\widetilde A^\epl_k(T) = -M^{-1}\widetilde h,
-\end{equation}
-where the matrix $M$ is taken from \eqref{eq:MandH} and the vector $\widetilde{h}$ is taken from \eqref{eq:MandHTilde}.
-For this estimator we will be able to prove a result of unbiasedness under a condition on the filtering parameter $\delta$.
-Let us remark that for $\widehat A^\epl_k(T)$ we do not need any condition on this parameter.
-Nevertheless, this second estimator is the minimizer of a likelihood function unlike the first, and will therefore be used in the Bayesian framework.
-Let us start with an estimate concerning the distance between $X^\epl$ and $Z^\epl$.
-
-\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
-Then, if $\delta \leq 1$, it holds for any integer $p \geq 1$
-	\begin{equation}
-		\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
-	\end{equation}
-	for a constant $C > 0$ independent of $\epl$ and $\delta$.
-\end{lemma}
-\begin{proof} Let us first remark that the filtering kernel satisfies
-	\begin{equation}\label{eq:filterIntegral}
-		\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta},
-	\end{equation}
-	which implies that the measure $\kappa_t(\d s)$ on $(0, t)$ defined as
-	\begin{equation}
-		\kappa_t(\d s) \defeq \frac{k(t-s)}{1 - e^{-t/\delta}} \dd s,
-	\end{equation}
-	is a probability measure.
-Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$.
-Let $Z_t^\epl$ be the corresponding filtered process.
-By definition of $Z^\epl_t$ and due \eqref{eq:filterIntegral} we now have
-	\begin{equation}
-	\begin{aligned}
-		X_t^\epl - Z_t^\epl &= X_t^\epl - \int_0^t k(t-s) X_s^\epl \dd s\\
-		&= \int_0^t k(t - s) \left(X_t^\epl - X_s^\epl\right) \dd s + e^{-t/\delta} X^\epl_t\\
-		&= (1 - e^{-t/\delta})\int_0^t \left(X_t^\epl - X_s^\epl\right) \kappa_t(\d s) + e^{-t/\delta} X^\epl_t.
-	\end{aligned}
-	\end{equation}
-	Therefore, Jensen's inequalities yields for a constant $C > 0$ depending only on $p$
-	\begin{equation}
-	\begin{aligned}
-		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} &\leq C (1 - e^{-t/\delta})^{2p} \int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} \kappa_t (\d s) + C e^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p}\\
-		&\leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} k(t-s) \dd s + Ce^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p},
-	\end{aligned}
-	\end{equation}
-	where we replaced the definition of $\kappa(\d s)$ and exploited the fact that $1 - e^{-t/\delta}\leq 1$ for all $t \geq 0$.
-Due to \cite[Corollary 5.4]{PaS07}, we know that $X^\epl_t$ has bounded moments of all orders with respect to its invariant measure.
-Moreover, the estimate
-	\begin{equation}
-		\E^{\phi^\epl}\abs{X_t^\epl - X_s^\epl}^{2p} \leq C\left(\epl^{2p} + (t-s)^{2p} + (t-s)^p\right),
-	\end{equation}
-	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}. Finally, it is possible to verify by induction on $r$ that for all integers $r$ it holds
-	\begin{equation}
-		\int_0^t k(t-s) (t - s)^r \dd s \leq r! \, \delta^r, 
-	\end{equation}
-	which implies that there exists a constant $C > 0$ depending only on $p$ such that
-	\begin{equation}
-		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p + e^{-2pt/\delta}\right).
-	\end{equation}
-	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
-In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$
-	\begin{equation}
-		\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} + Ce^{-\lambda t},
-	\end{equation}
-	which, for $t$ sufficiently big, yields
-	\begin{equation}
-		\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
-	\end{equation}
-	which is the desired result.
-\end{proof}
-
-Let us consider a couple $(X^\epl, Z^\epl)^\top$. In the following, we will adopt the notation
-\begin{equation}\label{eq:CalM}
-	\mathcal M = \E^{\rho^\epl}[V'(X^\epl) \otimes V'(X^\epl)] \quad \text{and} \quad \widetilde{\mathcal M} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)],
-\end{equation}
-which due to the ergodic theorem satisfy
-\begin{equation}
-	\lim_{T \to \infty} M = \mathcal M, \quad \text{and} \quad \lim_{T \to \infty} \widetilde M = \mathcal{\widetilde M},
-\end{equation}
-almost surely. In the following Lemma, we consider the difference between the two matrices $\mathcal M$ and $\widetilde{\mathcal M}$.
-
-\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Lemma \ref{lem:distanceZandX} hold. Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}$ defined in \eqref{eq:CalM} satisfy
-	\begin{equation}
-		\norm{\mathcal M - \widetilde{\mathcal M}}_2 \leq C\left(\epl + \delta^{1/2}\right),
-	\end{equation}
-	for a constant $C > 0$ independent of $\epl$ and $\delta$.
-\end{lemma}
-\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
-	\begin{equation}
-	\begin{aligned}
-		\norm{\mathcal M - \widetilde{\mathcal M}}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
-		&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
-	\end{aligned}
-	\end{equation}
-	The Lipschitz condition on $V$ together with the boundedness of the moments of $X^\epl$ and Lemma \ref{lem:distanceZandX} yield for a constant $C > 0$
-	\begin{equation}
-	\begin{aligned}
-		\norm{\mathcal M - \widetilde{\mathcal M}}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
-	\end{aligned}
-	\end{equation}
-	which is the desired result.
-\end{proof}
-
-We can finally prove the unbiasedness of the estimator $\widetilde A^\epl_k(T)$.
-
-\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold.
-Then, if $\delta$ in \eqref{eq:filter} satisfies $\delta = \delta(\epl)$ with $\delta(\epl) \to 0$ for $\epl \to 0$, it holds
-	\begin{equation}
-		\lim_{\epl \to 0} \lim_{T \to \infty} \widetilde A^\epl_k(T) = A, \quad \text{a.s.},
-	\end{equation} 
-	for $\widetilde A^\epl_k(T)$ defined in \eqref{eq:AHatMixedTilde}.
-\end{theorem}
-\begin{proof} We first consider the difference between the two estimators $\widetilde A^\epl_k(T)$ and $\widehat A^\epl_k(T)$. In particular, the ergodic theorem and an algebraic equality imply
-	\begin{equation}
-	\begin{aligned}
-		\lim_{T \to \infty} \left(\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)\right) &= \left(\mathcal M^{-1} - \widetilde{\mathcal M}^{-1}\right) \lim_{T \to \infty}\widetilde h \\
-		&= \mathcal M^{-1}\left(\mathcal M - \widetilde{\mathcal M}\right)  \widetilde{\mathcal M}^{-1} \lim_{T \to \infty} \widetilde h\\
-		&= \mathcal M^{-1}\left(\mathcal M - \widetilde{\mathcal M}\right)\lim_{T \to \infty} \widehat A^\epl_k(T),
-	\end{aligned}
-	\end{equation}
-	almost surely. Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
-	\begin{equation}\label{eq:DistATildeAHat}
-		\lim_{T \to \infty} \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 \leq C \left(\epl + \delta^{1/2} \right).
-	\end{equation}
-	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem}. Now, the triangle inequality yields
-	\begin{equation}
-		\norm{\widetilde A^\epl_k(T) - A}_2 \leq \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 + \norm{\widehat A^\epl_k(T) - A}_2.
-	\end{equation}
-	Therefore, due to Theorem \ref{thm:mainTheorem}, the inequality \eqref{eq:DistATildeAHat} and since $\delta \to 0$ for $\epl \to 0$, the desired result holds.
-\end{proof}
-
 \section{The Bayesian setting}\label{sec:Bayesian}
@@
 In this section, we present how to correct the faulty behaviour highlighted by Theorem \ref{thm:BayesianBias} with filtering techniques.
-In particular, we employ the same strategy that led to the estimator $\widetilde A^\epl_k(T)$ presented in Section \ref{sec:FilterMLE_2}.
-Therefore, we modify the likelihood function as
+Employing the filter in the same way as for the MLE, we can modify the likelihood function and obtain
+\begin{equation}
+	\widehat p(X^\epl \mid A) = \exp\left(-\frac{\widehat I(X^\epl\mid A)}{2\Sigma} \right), 
+\end{equation}
+where 
+\begin{equation}
+\begin{aligned}
+	\widehat I(X^\epl \mid A) & = \int_0^T A \cdot V'(Z^\epl_t) \dd X^\epl_t + \frac12 \int_0^T \left(A \cdot V'(X^\epl_t)\right)\left(A \cdot V'(Z^\epl_t)\right) \dd t \\
+	&= \widetilde h \cdot A + \frac12 A \cdot \widetilde M A.
+\end{aligned}
+\end{equation}
+Let us remark that $\widetilde M$ is not symmetric. Nevertheless, we have that
+\begin{equation}
+	A \cdot \widetilde M A = A \cdot \widetilde M_S A,
+\end{equation}
+where $\widetilde M_S$ is the symmetric part of $\widetilde M$.
+Repeating the same reasoning as above, one would therefore obtain a modified posterior $\widehat \mu_{T, \epl} = \mathcal N(\widehat m_{T, \epl}, \widehat C_{T, \epl})$, whose covariance matrix and mean would be given by
+\begin{equation}
+\begin{aligned}
+	\widehat C_{T, \epl}^{-1} &= C_0^{-1} + \frac{T}{2\Sigma} \widetilde M_S, \\
+	\widehat C_{T,\epl}^{-1}\widehat m_{T,\epl} &= C_0^{-1}A_0 - \frac{T}{2\Sigma} \widetilde h. 
+\end{aligned}	
+\end{equation}
+There is no guarantee under Assumption \ref{as:regularity} that $\widehat C_{T, \epl}$ is positive define and therefore a covariance matrix.
+Hence, in this Bayesian setting, we consider a different modification of the likelihood where we perturb only the vector $h$, i.e.,
 \begin{equation}
@@
 \begin{equation}
-	\widetilde I(X^\epl \mid A) =\int_0^T A \cdot V'(Z^\epl_t) \dd X^\epl_t + \int_0^T \left(A \cdot V'(X^\epl_t)\right)^2 \dd t,
-\end{equation}
-so that the estimator $\widetilde A^\epl_k(T)$ introduced in \eqref{eq:AHatMixedTilde} is the MLE based on the new likelihood $\widetilde p(X^\epl \mid A)$.
-With this likelihood function, we obtain the modified posterior $\widetilde \mu_{T,\epl} = \mathcal N(\widetilde m_{T, \epl}, C_{T, \epl})$, whose parameters are given by
+\begin{aligned}
+	\widetilde I(X^\epl \mid A) & = \int_0^T A \cdot V'(Z^\epl_t) \dd X^\epl_t + \frac12 \int_0^T \left(A \cdot V'(X^\epl_t)\right)^2 \dd t \\
+	&= \widetilde h \cdot A + \frac12 A \cdot M A.
+\end{aligned}
+\end{equation}
+so that we obtain the modified posterior $\widetilde \mu_{T,\epl} = \mathcal N(\widetilde m_{T, \epl}, C_{T, \epl})$, whose parameters are given by
 \begin{equation}
@@
 \end{equation}
-Let us remark that the posterior $\widetilde \mu_{T,\epl}$ has the same covariance as $\mu_{T,\epl}$. The following result now holds.
+Let us remark that the posterior $\widetilde \mu_{T,\epl}$ has the same covariance as $\mu_{T,\epl}$ and that therefore it is indeed a valid Gaussian posterior distribution.
+Nevertheless, in order to employ the tool of convergence introduced in Theorem \ref{thm:BayesianBias}, we need to study the properties of the MLE based on the likelihood $\widetilde p(X^\epl \mid A)$, i.e., the quantity
+\begin{equation}\label{eq:AHatMixedTilde}
+	\widetilde A^\epl_k(T) = - M^{-1} \widetilde h.
+\end{equation}
+The following theorem guarantees the unbiasedness of this estimator under a condition on the parameter $\delta$ of the filter, and we refer to the Appendix for its proof.
+\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold.
+Then, if $\delta$ in \eqref{eq:filter} satisfies $\delta = \delta(\epl)$ with $\delta(\epl) \to 0$ for $\epl \to 0$, it holds
+	\begin{equation}
+	\lim_{\epl \to 0} \lim_{T \to \infty} \widetilde A^\epl_k(T) = A, \quad \text{a.s.},
+	\end{equation} 
+	for $\widetilde A^\epl_k(T)$ defined in \eqref{eq:AHatMixedTilde}.
+\end{theorem}
+
+The following result gives the convergence of the modified posterior distribution $\widetilde \mu_{T, \epl}$ to the drift coefficient of the homogenized equation.
 \begin{theorem} Let the Assumptions of Theorem \ref{thm:mainTheoremTilde} hold. Then, the modified posterior measure $\widetilde\mu_{T,\epl} = \mathcal N(\widetilde m_{T,\epl}, C_{T,\epl})$ satisfies
@@
 \end{proof}
-
-%In this section we show how the filtering approach can be employed in a Bayesian framework.
-As in Section \ref{sec:Bayesian} let us consider a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$.
-Then, the density $p^\epl(A \mid X)$ of the posterior distribution $\mu^\epl(A \mid X^\epl)$ given by multiscale data satisfies
-%\begin{equation}
-%	p^\epl(A \mid X) = \frac1{Z^\epl} \, p^\epl(X \mid A) \, p_0(A),
-%\end{equation}
-%where $Z^\epl$ is the normalization term and where the likelihood function is given by
-%\begin{equation}
-%	p^\epl(X \mid A) = \exp\left(-\frac{I^\epl(X\mid A)}{2\Sigma} \right), 
-%\end{equation}
-%with
-%\begin{equation}
-%	I^\epl(X\mid A) = \int_0^T A \cdot V'(X_t^\epl) \dd X_t^\epl + \frac12 \int_0^T \left( A \cdot V'(X_t^\epl) \right)^2 \dd t.
-%\end{equation}
-%Let us consider the likelihood function $\widetilde p^\epl(X \mid A)$ modified to include the filtered data $Z^\epl$ given by
-%\begin{equation}
-%	\widetilde p^\epl(X \mid A) = \exp\left(-\frac{\widetilde I^\epl(X\mid A)}{2\Sigma} \right), 
-%\end{equation}
-%with
-%\begin{equation}
-%	\widetilde I^\epl(X\mid A) = \int_0^T A \cdot V'(Z_t^\epl) \dd X_t^\epl + \frac12 \int_0^T \left( A \cdot V'(X_t^\epl) \right) \left( A \cdot V'(Z_t^\epl) \right) \dd t.
-%\end{equation}
-%Moreover, let us consider the modified posterior distribution $\widetilde \mu^\epl(A \mid X)$ with density
-%\begin{equation}
-%	\widetilde p^\epl(A \mid X) = \frac1{\widetilde Z^\epl} \, \widetilde p^\epl(X \mid A) \, p_0(A),
-%\end{equation}
-%Let us remark that employing \eqref{eq:MandHTilde} we can write 
-%\begin{equation}
-%	\log \widetilde p^\epl(A \mid X) = -\log \widetilde Z^\epl - T A \cdot \widetilde h - \frac{T}{2} A \cdot \widetilde M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
-%\end{equation}
-%With respect to Section \ref{sec:Bayesian}, the matrix $\widetilde M$ is not symmetric. Nonetheless, we remark that
-%\begin{equation}
-%	A \cdot \widetilde M A = A \cdot \widetilde M_S A,
-%\end{equation}
-%where $\widetilde M_S$ is the symmetric part of $\widetilde M$, i.e.,
-%\begin{equation}
-%	\widetilde M_S = \frac12 \left(\widetilde M + \widetilde M^\top\right).
-%\end{equation}
-%Hence, we can rewrite 
-%\begin{equation}	
-%	\log \widetilde p^\epl(A \mid X) = -\log \widetilde Z^\epl - T A \cdot \widetilde h - \frac{T}{2} A \cdot \widetilde M_S A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0).
-%\end{equation}
-%This shows that the posterior $\widetilde \mu^\epl$ is a Gaussian $\mathcal N(\widetilde m_T, \widetilde C_T)$ where the covariance and mean can be obtained as 
-%\begin{equation}
-%\begin{aligned}
-%	\widetilde C_T^{-1} &= C_0^{-1} + T \widetilde M, \\
-%	\widetilde C_T^{-1} \widetilde m_T &= C_0^{-1}A_0 - T \widetilde h. 
-%\end{aligned}
-%\end{equation}
-%
-%In the following theorem we show that the posterior we obtain 
-%\begin{theorem} Under
-%\end{theorem}
 
@@
 
-\subsection{The Bayesian approach: bistable potential}
-\begin{figure}[t]
-	\centering
-	\begin{tabular}{ccc}
-		\includegraphics[]{Figures/Bayes_T100} & \includegraphics[]{Figures/Bayes_T200}  & \includegraphics[]{Figures/Bayes_T400} \\
-	\end{tabular}
-	\caption{Posterior distributions over the parameter $A = (A_1, A_2)^\top$ for the bistable potential obtained with the filtering approach.
-The figures refer to final time $T = 100, 200, 400$ from left to right, respectively.
-The MLE $\widetilde A^\epl_k(t)$ is represented with a circle, while the true value $A$ of the drift coefficient of the homogenized equation is represented with a cross.}
-	\label{fig:Bayes}
-\end{figure}
-
-In this numerical experiment we consider $N = 2$ and the bistable potential, i.e., the function $V$ defined as
-\begin{equation}
-	V(x) = \begin{pmatrix} \dfrac{x^4}{4} & -\dfrac{x^2}{2} \end{pmatrix}^\top,
-\end{equation}
-with coefficients $\alpha_1 = 1$ and $\alpha_2 = 2$.
-We then consider the multiscale equation with $\sigma = 0.7$, the fast potential $p(y) = \cos(y)$ and $\epl = 0.05$, thus simulating a trajectory $X^\epl$.
-We adopt here a Bayesian approach and compute the posterior distribution $\widetilde \mu_{T, \epl}$ obtained with the filtering approach introduced in Section \ref{sec:BayesianFilter}.
-The parameters of the filter are set to $\beta = 1$ and $\delta = \epl$ in \eqref{eq:filter}.
-Let us remark that in order to compute the posterior covariance the diffusion coefficient $\Sigma$ of the homogenized equation has to be known.
-In this case, we pre-compute the value of $\Sigma$ via the coefficient $K$ and the theory of homogenization, but let us remark that $\Sigma$ could be estimated employing the subsampling technique of \cite{PaS07}.
-We stop computations at times $T = 100, 200, 400$ in order to observe the shrinkage of the Gaussian posterior towards the MLE $\widetilde A^\epl_k(T)$ with respect to time.
-In Figure \ref{fig:Bayes}, we observe that the posterior does indeed shrink towards the MLE, which in turn gets progressively closer to the true value of the drift coefficient $A$ of the homogenized equation.
-
-\subsection{Multi-dimensional parameter}
+\subsection{Multi-dimensional drift coefficient}
 
@@
 
-\begin{table}[t]
+\begin{table}[ht!]
 	\centering
-	\begin{tabular}{ccccc}
+	\begin{tabular}{cccccc}
 		\toprule
-		Coefficient & Truth & No preprocessing & Filtering & Subsampling  \\ 
+		Coefficient & Multiscale & Homogenized & No preprocessing  & Filtering  		  & Subsampling  			 \\ 
+		& $\alpha$ & $A$   & $\widehat A^\epl$ & $\widehat A^\epl_k$ & $\widehat A^\epl_\delta$ \\
 		\midrule
-		$A_1$ & -0.62 & -0.92 & -0.70 & -0.59\\
-		$A_2$ & -0.31 & -0.70 & -0.27 & 0.05 \\
-		$A_3$ & 0.31  & 0.55  & 0.31  & 0.14 \\
-		$A_4$ & 0.62  & 1.22  & 0.57  & 0.13 \\
+		$1$ &-1   & -0.62 & -0.92 & -0.70 & -0.59\\
+		$2$ &-0.5 & -0.31 & -0.70 & -0.27 & 0.05 \\
+		$3$ & 0.5 & 0.31  & 0.55  & 0.31  & 0.14 \\
+		$4$ & 1   & 0.62  & 1.22  & 0.57  & 0.13 \\
 		\bottomrule
 	\end{tabular}
-	\caption{Numerical results for the four-dimensional parameter rounded to the second significant figure.}
+	\caption{Numerical results for the four-dimensional parameter rounded to the second significant digit.}
 	\label{tab:KLStyle}
@@
 
+\subsection{The Bayesian approach: bistable potential}
+\begin{figure}[t]
+	\centering
+	\begin{tabular}{ccc}
+		\includegraphics[]{Figures/Bayes_T100} & \includegraphics[]{Figures/Bayes_T200}  & \includegraphics[]{Figures/Bayes_T400} \\
+	\end{tabular}
+	\caption{Posterior distributions over the parameter $A = (A_1, A_2)^\top$ for the bistable potential obtained with the filtering approach.
+The figures refer to final time $T = 100, 200, 400$ from left to right, respectively.
+The MLE $\widetilde A^\epl_k(t)$ is represented with a circle, while the true value $A$ of the drift coefficient of the homogenized equation is represented with a cross.}
+	\label{fig:Bayes}
+\end{figure}
+
+In this numerical experiment we consider $N = 2$ and the bistable potential, i.e., the function $V$ defined as
+\begin{equation}
+	V(x) = \begin{pmatrix} \dfrac{x^4}{4} & -\dfrac{x^2}{2} \end{pmatrix}^\top,
+\end{equation}
+with coefficients $\alpha_1 = 1$ and $\alpha_2 = 2$.
+We then consider the multiscale equation with $\sigma = 0.7$, the fast potential $p(y) = \cos(y)$ and $\epl = 0.05$, thus simulating a trajectory $X^\epl$.
+We adopt here a Bayesian approach and compute the posterior distribution $\widetilde \mu_{T, \epl}$ obtained with the filtering approach introduced in Section \ref{sec:BayesianFilter}.
+The parameters of the filter are set to $\beta = 1$ and $\delta = \epl$ in \eqref{eq:filter}.
+Let us remark that in order to compute the posterior covariance the diffusion coefficient $\Sigma$ of the homogenized equation has to be known.
+In this case, we pre-compute the value of $\Sigma$ via the coefficient $K$ and the theory of homogenization, but let us remark that $\Sigma$ could be estimated employing the subsampling technique of \cite{PaS07}.
+We stop computations at times $T = 100, 200, 400$ in order to observe the shrinkage of the Gaussian posterior towards the MLE $\widetilde A^\epl_k(T)$ with respect to time.
+In Figure \ref{fig:Bayes}, we observe that the posterior does indeed shrink towards the MLE, which in turn gets progressively closer to the true value of the drift coefficient $A$ of the homogenized equation.
+
 \section{Conclusion}
@@
 
+\begin{appendices}
+
+\section{}
+Let us consider the estimator defined in \eqref{eq:AHatMixedTilde}, that is
+\begin{equation}
+	\widetilde A^\epl_k(T) = -M^{-1}\widetilde h,
+\end{equation}
+where the matrix $M$ is taken from \eqref{eq:MandH} and the vector $\widetilde{h}$ is taken from \eqref{eq:MandHTilde}.
+We prove here Theorem \ref{thm:mainTheoremTilde}, i.e., the unbiasedness of this estimator, for which it is necessary to prove two technical lemmas.
+Let us start with an estimate concerning the distance between $X^\epl$ and $Z^\epl$.
+
+\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
+Then, if $\delta \leq 1$, it holds for any integer $p \geq 1$
+	\begin{equation}
+	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
+	\end{equation}
+	for a constant $C > 0$ independent of $\epl$ and $\delta$.
+\end{lemma}
+\begin{proof} Let us first remark that the filtering kernel satisfies
+	\begin{equation}\label{eq:filterIntegral}
+	\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta},
+	\end{equation}
+	which implies that the measure $\kappa_t(\d s)$ on $(0, t)$ defined as
+	\begin{equation}
+	\kappa_t(\d s) \defeq \frac{k(t-s)}{1 - e^{-t/\delta}} \dd s,
+	\end{equation}
+	is a probability measure.
+Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$.
+Let $Z_t^\epl$ be the corresponding filtered process.
+By definition of $Z^\epl_t$ and due \eqref{eq:filterIntegral} we now have
+	\begin{equation}
+	\begin{aligned}
+	X_t^\epl - Z_t^\epl &= X_t^\epl - \int_0^t k(t-s) X_s^\epl \dd s\\
+	&= \int_0^t k(t - s) \left(X_t^\epl - X_s^\epl\right) \dd s + e^{-t/\delta} X^\epl_t\\
+	&= (1 - e^{-t/\delta})\int_0^t \left(X_t^\epl - X_s^\epl\right) \kappa_t(\d s) + e^{-t/\delta} X^\epl_t.
+	\end{aligned}
+	\end{equation}
+	Therefore, Jensen's inequalities yields for a constant $C > 0$ depending only on $p$
+	\begin{equation}
+	\begin{aligned}
+	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} &\leq C (1 - e^{-t/\delta})^{2p} \int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} \kappa_t (\d s) + C e^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p}\\
+	&\leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} k(t-s) \dd s + Ce^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p},
+	\end{aligned}
+	\end{equation}
+	where we replaced the definition of $\kappa(\d s)$ and exploited the fact that $1 - e^{-t/\delta}\leq 1$ for all $t \geq 0$.
+Due to \cite[Corollary 5.4]{PaS07}, we know that $X^\epl_t$ has bounded moments of all orders with respect to its invariant measure.
+Moreover, the estimate
+	\begin{equation}
+	\E^{\phi^\epl}\abs{X_t^\epl - X_s^\epl}^{2p} \leq C\left(\epl^{2p} + (t-s)^{2p} + (t-s)^p\right),
+	\end{equation}
+	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}. Finally, it is possible to verify by induction on $r$ that for all integers $r$ it holds
+	\begin{equation}
+	\int_0^t k(t-s) (t - s)^r \dd s \leq r! \, \delta^r, 
+	\end{equation}
+	which implies that there exists a constant $C > 0$ depending only on $p$ such that
+	\begin{equation}
+	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p + e^{-2pt/\delta}\right).
+	\end{equation}
+	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
+In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$
+	\begin{equation}
+	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} + Ce^{-\lambda t},
+	\end{equation}
+	which, for $t$ sufficiently big, yields
+	\begin{equation}
+	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
+	\end{equation}
+	which is the desired result.
+\end{proof}
+
+Let us consider a couple $(X^\epl, Z^\epl)^\top$. In the following, we will adopt the notation
+\begin{equation}\label{eq:CalM}
+\mathcal M = \E^{\rho^\epl}[V'(X^\epl) \otimes V'(X^\epl)] \quad \text{and} \quad \widetilde{\mathcal M} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)],
+\end{equation}
+which due to the ergodic theorem satisfy
+\begin{equation}
+\lim_{T \to \infty} M = \mathcal M, \quad \text{and} \quad \lim_{T \to \infty} \widetilde M = \mathcal{\widetilde M},
+\end{equation}
+almost surely. In the following Lemma, we consider the difference between the two matrices $\mathcal M$ and $\widetilde{\mathcal M}$.
+
+\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Lemma \ref{lem:distanceZandX} hold. Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}$ defined in \eqref{eq:CalM} satisfy
+	\begin{equation}
+	\norm{\mathcal M - \widetilde{\mathcal M}}_2 \leq C\left(\epl + \delta^{1/2}\right),
+	\end{equation}
+	for a constant $C > 0$ independent of $\epl$ and $\delta$.
+\end{lemma}
+\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
+	\begin{equation}
+	\begin{aligned}
+	\norm{\mathcal M - \widetilde{\mathcal M}}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
+	&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
+	\end{aligned}
+	\end{equation}
+	The Lipschitz condition on $V$ together with the boundedness of the moments of $X^\epl$ and Lemma \ref{lem:distanceZandX} yield for a constant $C > 0$
+	\begin{equation}
+	\begin{aligned}
+	\norm{\mathcal M - \widetilde{\mathcal M}}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
+	\end{aligned}
+	\end{equation}
+	which is the desired result.
+\end{proof}
+
+We can finally prove the unbiasedness of the estimator $\widetilde A^\epl_k(T)$.
+
+\begin{proof}[Proof of Theorem \ref{thm:mainTheoremTilde}] We first consider the difference between the two estimators $\widetilde A^\epl_k(T)$ and $\widehat A^\epl_k(T)$.
+In particular, the ergodic theorem and an algebraic equality imply
+	\begin{equation}
+	\begin{aligned}
+	\lim_{T \to \infty} \left(\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)\right) &= \left(\mathcal M^{-1} - \widetilde{\mathcal M}^{-1}\right) \lim_{T \to \infty}\widetilde h \\
+	&= \mathcal M^{-1}\left(\mathcal M - \widetilde{\mathcal M}\right)  \widetilde{\mathcal M}^{-1} \lim_{T \to \infty} \widetilde h\\
+	&= \mathcal M^{-1}\left(\mathcal M - \widetilde{\mathcal M}\right)\lim_{T \to \infty} \widehat A^\epl_k(T),
+	\end{aligned}
+	\end{equation}
+	almost surely. Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
+	\begin{equation}\label{eq:DistATildeAHat}
+	\lim_{T \to \infty} \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 \leq C \left(\epl + \delta^{1/2} \right).
+	\end{equation}
+	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem}. Now, the triangle inequality yields
+	\begin{equation}
+	\norm{\widetilde A^\epl_k(T) - A}_2 \leq \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 + \norm{\widehat A^\epl_k(T) - A}_2.
+	\end{equation}
+	Therefore, due to Theorem \ref{thm:mainTheorem}, the inequality \eqref{eq:DistATildeAHat} and since $\delta \to 0$ for $\epl \to 0$, the desired result holds.
+\end{proof}
+\end{appendices}
+
 \bibliographystyle{siam}

### 2020-02-26 CalNotes.tex
Update after Andrew's comments

@@
 
-Data-driven approaches to the derivation of effective stochastic coarse-grained dynamics have become a standard tool in different areas such as molecular dynamics or atmosphere and ocean science \cite{KKP15,CoP09,YMV19}.
-When fitting data to a low dimensional coarse-grained model, one is faced with the problem of model misspecification; indeed, the data, coming from the full dynamics, are compatible with the coarse-grained model only at the time scales at which the effective dynamics is valid.
-This is related to the issue of high-frequency data that arises in econometrics \cite{AiJ14,AMZ05,ZMA05,OSP10}.
-
-The issue of model misspecification in inverse problems with a multiscale structure has been treated in the context of partial differential equations (PDE).
+Efficient parameter estimation for stochastic models is essential in a wide range of applications in natural and social sciences.
+In several areas, the data originates from phenomena which vary continuously in time and which are endowed with a multiscale structure.
+This is the case, for example, in molecular dynamics, oceanography and atmosphere science or in econometrics.
+Frequently, it is desirable in this areas to infer from data a simpler model which captures effectively large-scale structures, or slow variations, disregarding small-scale fluctuations or treating them as a source of noise.
+The mismatch between the data and their desired slow-scale representation is a typical instance of a problem of model misspecification, which, if ignored or mistreated, can lead to wrong solutions.
+Indeed, the data, coming from the full dynamics, are compatible with the coarse-grained model only at the time scales at which the effective dynamics is valid.
+
+In this paper we consider a simple multiscale setting arising from models of molecular dynamics, with a complete separation between a fast and a slow scale.
+In particular, we consider diffusion processes for which the confining potential has slow variations, and whose motion is perturbed by a fast-scale potential with rapid periodic and bounded oscillations.
+Given this simple class of model problems, we are interested in determining the drift coefficient of an equation of the overdamped Langevin type in which the fast-scale potential is eliminated.
+The theory of homogenization guarantees that such a single-scale equation can be uniquely determined, and our goal is therefore to obtain effective coarse-grained dynamics from data consistently with respect to the homogenization result.
+
+Several methods to take into account model misspecification in multiscale frameworks as above exist.
+For diffusion processes, the proposed approaches rely in different measures to subsampling, which has proved itself to some extent effective in many applications, but which requires nevertheless precise knowledge of how separated the two characteristic time scales are.
+Robustness of this methodology is dubious, too, as inference results tend to be extremely sensitive to the subsampling rate.
+
+In the rest of the introduction, we first give a brief overview of the existing literature on the topic of deterministic and stochastic multiscale inference problems, then introduce our novel methodology and its favourable properties and conclude with an outline of this paper.
+
+\subsection{Literature Review}
+
+For simple models in molecular dynamics, the effect of model misspecification was studied in a series of papers \cite{PaS07,PPS09,PPS12,GaS17,GaS18} under the assumption of scale separation.
+In particular, for Brownian particles moving in two-scale potentials it was shown that, when fitting data from the full dynamics to the homogenized equation, the maximum likelihood estimator (MLE) is asymptotically biased \cite[Theorem 3.4]{PaS07}.
+To be more precise, in the large sample size limit the MLE converges to the coefficients of the unhomogenized equation, rather than to those of the homogenized one.
+The bias of the MLE can be eliminated by subsampling at an appropriate rate, which lies between the two characteristic time scales of the problem \cite[Theorems 3.5 and 3.6]{PaS07}.
+
+Similar techniques can be employed in econometrics, in particular for the estimation of the integrated stochastic volatility in the presence of market micro-structure noise.
+In this case, too, the data have to be subsampled at an appropriate rate \cite{AMZ05,OSP10}.
+The correct subsampling rate can be in some instances rather extreme with respect to the frequency of the data and lead to get rid of more than $99\%$ of the data.
+As the intuition suggests, this increases significantly the bias of the estimator, which is usually taken care of with additional bias corrections and variance reduction procedures.
+The need of such methodology is accentuated by data being obtained at high-frequency \cite{AiJ14,ZMA05}.
+
+The problem of extracting large-scale variations from multiscale data is studied in atmosphere and ocean science.
+In this field, too, subsampling the data is necessary to obtain an accurate coarse-grained model \cite{CoP09,YMV19}.
+
+The necessity to subsample the data can be alleviated by using appropriate martingale estimators, as was done in \cite{KPK13,KKP15}.
+This class of estimators can be applied to the case where the noise is multiplicative and also given by a deterministic chaotic system, as opposed to white noise.
+Estimators of this family have been applied to time series from paleoclimatic data and marine biology and augmented with appropriate model selection methodologies \cite{KPP15}.
+
+Inference of diffusion processes can be naturally performed under a Bayesian perspective.
+If one focuses on the drift coefficient, the form of the likelihood function guarantees, under a Gaussian prior hypothesis, that the posterior distribution is itself a Gaussian.
+The versatility of the Bayesian approach in the infinite-dimensional case \cite{Stu10, DaS16} gives the possibility to extend the problem of inferring the drift of a diffusion process to the non-parametric case \cite{PSV09, PSZ13}.
+
+The issue of model misspecification in inverse problems with a multiscale structure has been treated in the context of partial differential equations, too.
 In particular, it has been shown that it is possible to infer a coarse-grained equation from data coming from the full model and to retrieve asymptotically the correct result \cite{NPS12}.
@@
 
-For simple models in molecular dynamics, the effect of model misspecification was studied in a series of papers \cite{PaS07,PPS09,PPS12,GaS17,GaS18} under the assumption of scale separation.
-In particular, for Brownian particles moving in two-scale potentials it was shown that, when fitting data from the full dynamics to the homogenized equation, the maximum likelihood estimator (MLE) is asymptotically biased \cite[Theorem 3.4]{PaS07}.
-To be more precise, in the large sample size limit the MLE converges to the coefficients of the unhomogenized equation, rather than to those of the homogenized one.
-The bias of the MLE can be eliminated by subsampling at an appropriate rate, which lies between the two characteristic time scales of the problem \cite[Theorems 3.5 and 3.6]{PaS07}.
-This is similar to the estimation of the integrated stochastic volatility in the presence of market micro-structure noise, where the data have to be subsampled at an appropriate rate \cite{AMZ05,ZMA05}.
-The correct subsampling rate can be in some instances rather extreme with respect to the frequency of the data and lead to get rid of more than $99\%$ of the data.
-As the intuition suggests, this increases significantly the bias of the estimator, which is usually taken care of with additional bias corrections and variance reduction procedures.
-
-The necessity to subsample the data can be alleviated by using appropriate martingale estimators, as was done in \cite{KPK13,KKP15}.
-This class of estimators can be applied to the case where the noise is multiplicative and also given by a deterministic chaotic system, as opposed to white noise.
-Estimators of this family have been applied to time series from paleoclimatic data and marine biology and augmented with appropriate model selection methodologies \cite{KPP15}.
-
+\subsection{Our contributions}
 In this paper, we bypass the issue of subsampling by implementing an appropriate filtering methodology.
@@
 	\item the filter's kernel depends on two parameters which can be tuned to obtain more robust results and which can be interpreted as analogous to the subsampling rate.
-Nevertheless, while the MLE is extremely sensitive with respect to the latter, changing the filter parameters does not have a strong influence on the result, therefore allowing our technique to be applied as a black-box tool for parameter estimation,
+Nevertheless, while the MLE is extremely sensitive with respect to the latter, our filtering methodology is robust with respect to its parameters, and can therefore be applied as a black-box tool for parameter estimation,
 	\item the entire stream of data is employed, which, in practice, enhances the quality of the filter-based MLE in terms of bias.
@@
 \end{enumerate}
-
-It is natural to reinterpret the problem of inferring the drift parameter of multiscale diffusion processes under a Bayesian perspective \cite{PSV09,PSZ13}.
-In particular, the form of the likelihood function guarantees, under a Gaussian prior hypothesis, that the posterior distribution is itself a Gaussian.
-Therefore, one can simply compute the mean and covariance of the posterior distribution to obtain a full uncertainty quantification of the inference process.
-The Bayesian approach has been adopted in several works concerning single and multiscale PDEs, too, and has proved itself to be versatile and efficient in this framework (see, e.g., \cite{AbD18, AGZ19}).
-Moreover, infinite-dimensional inverse problems are intrinsically ill-posed, and interpreting them in a Bayesian manner is an efficient tool for regularizing them and guaranteeing their well-posedness \cite{Stu10, DaS16}.
-The regularization property of a Bayesian approach has been recently demonstrated for inverse problems involving multiscale PDEs \cite{AbD18}.
-In this work, we investigate the effects of inserting our filtering methodology in a Bayesian framework.
-In particular, we analyse the effects of modifying the likelihood function inserting the filtered trajectory, showing how this corrects the faulty asymptotic behaviour which would be present in case no pre-processing would be applied.
-
+After having deduced unbiased estimators, we focus on how to insert the filtering methodology into a Bayesian approach.
+In particular, we analyse the effects of modifying the likelihood function if the smoothed trajectory is inserted in an appropriate manner.
+Under mild hypotheses on the filter parameters, we are able to show that the posterior distributions obtained with our methodology are asymptotically consistent with respect to the drift parameter of the homogenized equation.
+To our knowledge, this is the first instance of a successful Bayesian approach applied to multiscale diffusion processes.
+
+\subsection{Outline}
 The rest of the paper is organised as follows.
@@
 where $W_t$ is the same Brownian motion as in \eqref{eq:SDE_MS}, such that $X_t^\epl \to X_t$ for $\epl\to 0$ in law as random variables in $\mathcal C^0([0, T]; \R)$.
-In particular, we have $A = K\alpha$ and $\Sigma = K \sigma$, where the coefficient $K$ is given by the formula
+In particular, we have $A = K\alpha$ and $\Sigma = K \sigma$, where the coefficient \corr{$0<K<1$} is given by the formula
 \begin{equation}\label{eq:K_HOM}
@@
 \end{equation}
-endowed with periodic boundary conditions.
-
+endowed with periodic boundary conditions. \corr{Let us remark that in this one-dimensional setting it is possible to determine $\Phi$ explicitly, and the homogenization coefficient $K$ is given by
+\begin{equation}
+	K = \frac{L^2}{Z\widehat Z},
+\end{equation}
+where
+\begin{equation}
+	Z = \int_0^L e^{-p(y)/\sigma} \dd y, \quad \widehat Z = \int_0^L e^{p(y)/\sigma} \dd y.
+\end{equation}}
 We now briefly present the classical methodology for estimating the drift coefficient.
@@
 The first ingredient for verifying the ergodic properties of the two-dimensional process $(X^\epl, Z^\epl)^\top \defeq ((X^\epl_t, Z^\epl_t)^\top, 0 \leq t \leq T)$ is verifying that the measure induced by the stochastic process admits a smooth density with respect to the Lebesgue measure.
-Since noise is present only on the first component, this is a consequence of the theory of hypo-ellipticity, as summarized in the following Lemma.
+Since noise is present only on the first component, this is a consequence of the theory of hypo-ellipticity, as summarized in the following Lemma, \corr{whose proof is given in Appendix \ref{ap:Proofs}.}
 
@@
 
-\begin{proof} We have to show that the joint process solution to \eqref{eq:systemSDE} is hypo-elliptic. Denoting as $f\colon \R \to \R$ the function 
-	\begin{equation}
-		f(x) = -\alpha \cdot V'(x) - \frac1\epl p'\left(\frac{x}\epl\right),
-	\end{equation}
-	the generator of the process $(X^\epl, Z^\epl)^\top$ is given by
-	\begin{equation}
-		\mathcal L = f \partial_x + \sigma \partial_{xx}^2 + \frac1\delta (x - z)\partial_z \eqdef \mathcal X_0 + \sigma \mathcal X_1^2, 
-	\end{equation}
-	where 
-	\begin{equation}
-		\mathcal X_0 = f \partial_x + \frac1\delta (x - z)\partial_z, \quad \mathcal X_1 = \partial_x.
-	\end{equation}
-	The commutator $[\mathcal X_0, \mathcal X_1]$ applied to a test function $v$ then gives
-	\begin{equation}
-	\begin{aligned}
-		[\mathcal X_0, \mathcal X_1]v &= f \partial_x^2 v + \frac1\delta (x - z) \partial_x \partial_z v  - \partial_x\left(f\partial_x v + \frac1\delta (x - z)\partial_z v\right)\\
-		&= -\partial_x f \partial_x v - \frac1\delta \partial_z v.
-	\end{aligned}
-	\end{equation}
-	Consequently, 
-	\begin{equation}
-		\mathrm{Lie}\left(\mathcal X_1, [\mathcal X_0, \mathcal X_1]\right) = \mathrm{Lie} \left(\partial_x, -\partial_x f \partial_x - \frac1\delta\partial_z\right),
-	\end{equation}
-	which spans $T_x\R^2$. The desired result then follows from Hörmander's theorem (see e.g. \cite[Chapter 6]{Pav14}).
-\end{proof}
-
 Once it is established that the law of the process admits a smooth density for all times $t>0$, which satisfies a time-dependent Fokker--Planck equation, we are interested in the limiting properties of this law.
 In particular, we know that the process $X^\epl$ alone is geometrically ergodic \cite[Theorem 4.4]{MSH02}, and we wish the couple $(X^\epl, Z^\epl)^\top$ to be endowed with the same property.
-The following Lemma guarantees that the couple is indeed geometrically ergodic exploiting an argument of dissipativity.
+The following Lemma guarantees that the couple is indeed geometrically ergodic, \corr{and its proof is given in Appendix \ref{ap:Proofs}.}
 
@@
 \end{lemma}
-
-\begin{proof} Lemma \ref{lem:density} guarantees that the Fokker--Planck equation can be written directly from the system \eqref{eq:systemSDE}. For geometric ergodicity, let 
-\begin{equation}
-	 \mathcal S(x,z) \defeq \begin{pmatrix} -\sum_{i=1}^N V_i'(x) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} = -\sum_{i=1}^N V_i'(x)x+\frac1\delta(xz-z^2).
-\end{equation}
-Due to Assumption \ref{as:regularity}\ref{as:regularity_diss} and Young's inequality, we then have for all $\gamma > 0$
-\begin{equation}
-	\mathcal S(x,z) \leq a + \left(\frac{1}{2\gamma\delta} - b\right)x^2 + \frac1\delta\left(\frac{\gamma}{2} - 1\right)z^2.
-\end{equation}
-We choose $\gamma = \gamma^* \defeq 1 - b\delta + \sqrt{1 + (1 - b\delta)^2} > 0$ so that
-\begin{equation}
-	C(\gamma^*) \defeq -\frac{1}{2\gamma^*\delta} + b = -\frac1\delta\left(\frac{\gamma^*}{2} - 1\right),
-\end{equation}
-and we notice that $C(\gamma^*) > 0$ if $\delta > 1/(4b)$. In this case, we have
-\begin{equation}
-	\mathcal S(x, z) \leq a - C(\gamma^*) \norm{\begin{pmatrix} x & z \end{pmatrix}^\top}^2,
-\end{equation}
-and problem \eqref{eq:systemSDE} is dissipative. The result then follows from \cite[Theorem 4.4]{MSH02}.
-\end{proof}
 
@@
 In a general case, it is not possible to find an explicit solution to \eqref{eq:FPsystem}.
-Nevertheless, it is possible to show some relevant properties of the solution itself, which are summarized in the following Lemma.
+Nevertheless, it is possible to show some relevant properties of the solution itself, which are summarized in the following Lemma, \corr{whose proof is given in Appendix \ref{ap:Proofs}.}
 
@@
 
-\begin{proof} Integrating equation \eqref{eq:FPsystem} with respect to $z$ we obtain the stationary Fokker--Planck equation for the process $X^\epl$, i.e.
-\begin{equation}
-\label{FPx}
-\sigma (\phi^\epl)''(x) + \frac{\d}{\d x} \left( \left ( \alpha \cdot V'(x) + \frac{1}{\epl} p' \left ( \frac{x}\epl \right ) \right ) \phi^\epl(x)\right) = 0,
-\end{equation}
-whose solution is given by
-\begin{equation}
-\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(- \frac{1}{\sigma} \alpha \cdot V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
-\end{equation}
-and which proves \eqref{eq:marginalX}. By integrating equation \eqref{eq:FPsystem} with respect to $x$ and integrating by parts we obtain
-\begin{equation}
-\psi^\epl(z) + z (\psi^\epl)'(z) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x,
-\end{equation}
-which can be written as
-\begin{equation}
-	\frac{\d}{\d z} (z \psi^\epl(z)) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x.
-\end{equation}
-Now, since $\psi^\epl$ is the density of a probability distribution, this implies that 
-\begin{equation}\label{FPz}
-z \psi^\epl(z) = \int_{\R} x \rho^\epl(x,z) \dd x,
-\end{equation}
-which, replacing the decomposition \eqref{eq:densityDecomposition}, yields
-\begin{equation} \label{eq:z_condition}
-z = \int_{\R} x \phi^\epl(x) R^\epl(x,z) \dd x.
-\end{equation}
-In view of \eqref{eq:densityDecomposition} and \eqref{FPx}, equation \eqref{eq:FPsystem} can be rewritten as
-\begin{equation}\label{eq:psiEqualityPDE}
-\sigma \phi^\epl \psi^\epl \partial^2_{xx} R^\epl + \frac{1}{\delta} \phi^\epl \psi^\epl R^\epl + \sigma (\phi^\epl)' \psi^\epl \partial_x R^\epl + \frac{1}{\delta} (z-x) \phi^\epl ((\psi^\epl)' R + \psi^\epl \partial_z R^\epl) = 0.
-\end{equation}
-We now multiply the equation above by $x$ and integrate with respect to $x$. Let us consider some simplifications explicitly. First, an integration by parts yields
-\begin{equation}\label{eq:psiEqualityPDE_1}
-\begin{aligned}
-	\sigma \psi^\epl \int_{\R}  x \phi^\epl \partial^2_{xx} R^\epl \dd x+ \sigma \psi^\epl \int_{\R} x (\phi^\epl)' \partial_x R^\epl \dd x &= -\sigma \psi^\epl \int_{\R} \phi^\epl \partial_x R^\epl \dd x.
-\end{aligned}
-\end{equation}
-Then, applying \eqref{eq:z_condition}, we have
-\begin{equation}\label{eq:psiEqualityPDE_2}
-	\frac1\delta \psi^\epl \int_{\R} x \phi^\epl  R^\epl \dd x = \frac1\delta z \psi^\epl.
-\end{equation}
-Moreover, again applying \eqref{eq:z_condition}, we can compute
-\begin{equation}\label{eq:psiEqualityPDE_3}
-\begin{aligned}
-	\frac1\delta (\psi^\epl)' \int_\R (z-x)x \phi^\epl  R \dd x = \frac1\delta (\psi^\epl)' \left(z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x\right).
-\end{aligned}
-\end{equation}
-Finally, we compute the last term always applying \eqref{eq:z_condition} obtaining
-\begin{equation}\label{eq:psiEqualityPDE_4}
-	\frac1\delta \psi^\epl \int_\R (z-x)x \phi^\epl \partial_z R \dd x = \frac1\delta \psi^\epl\left(z - \int_{\R} x^2 \phi^\epl \partial_z R^\epl \dd x\right).
-\end{equation}
-Replacing the equalities \eqref{eq:psiEqualityPDE_1}, \eqref{eq:psiEqualityPDE_2}, \eqref{eq:psiEqualityPDE_3} and \eqref{eq:psiEqualityPDE_4} into \eqref{eq:psiEqualityPDE} we obtain
-\begin{equation}
-(\psi^\epl)' \left ( z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x \right ) + \psi^\epl \left ( 2z - \int_{\R} x^2 \phi^\epl \partial_z R^\epl \dd x - \delta \sigma \int_{\R} \phi^\epl \partial_x R^\epl \dd x \right ) = 0.
-\end{equation}
-We rewrite the equality above as
-\begin{equation} \label{eq:psiEquality}
-\delta \sigma \psi^\epl(z) \int_{\R} \phi^\epl(x) \partial_x R^\epl(x, z) \dd x = 
-\begin{aligned}[t] &(\psi^\epl)'(z) z^2 - (\psi^\epl)'(z) \int_{\R} x^2 \phi^\epl(x) R^\epl(x, z) \dd x \\
-& + 2 \psi^\epl(x) z - \psi^\epl \int_{\R} x^2 \phi^\epl(x) \partial_z R^\epl(x, z) \dd x.
-\end{aligned}
-\end{equation}
-Multiplying by $V'(z)$, integrating with respect to $z$ and integrating by parts, we obtain the following identity in $\R^N$
-\begin{equation}
-\begin{aligned}
-\sigma \delta \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z &=  \int_{\R} \int_{\R} (x^2 - z^2) V''(z) \rho_\epl(x,z) \dd x \dd z \\
-&= \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)],
-\end{aligned}
-\end{equation}
-which is the desired result.
-\end{proof}
-
 \subsection{Multiscale convergence}\label{sec:convMS}
@@
 In particular, it is known that the invariant measure of $X^\epl$ converges weakly to the invariant measure of $X$ solution of the homogenized equation \eqref{eq:SDE_HOM}.
-The following result guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.
+The following result, \corr{whose proof is given in Appendix \ref{ap:Proofs},} guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.
 
@@
 \end{lemma}
-\begin{proof} Let $(X, Z)^\top \defeq \left((X_t, Z_t)^\top, 0\leq t \leq T\right)$ be the solution of
-	\begin{equation}
-	\label{eq:systemSDEHom}
-	\begin{aligned}
-		\d X_t &= -A \cdot V'(X_t) \dd t + \sqrt{2\Sigma} \dd W_t, \\
-		\d Z_t &= \frac{1}{\delta} \left ( X_t - Z_t \right ) \dd t,
-	\end{aligned}
-	\end{equation} 
-	with $(X_0, Z_0)^\top \sim \mu^0$.
-The arguments of Section \ref{sec:ergodic} can be repeated to conclude that the invariant measure of $(X, Z)^\top$ admits a smooth density $\rho^0$ which satisfies \eqref{eq:FPsystem_homogenized}.
-Moreover, standard homogenization theory (see e.g.
-\cite[Chapter 3]{BLP78}) guarantees that $(X^\epl,Z^\epl)^\top \to (X,Z)^\top$ for $\epl \to 0$ in law as random variables with values in $\mathcal C^0([0, T]; \R^2)$.
-The Portmanteau theorem can be employed to conclude that the measure $\mu^\epl$ converges weakly to $\mu^0$ for $\epl \to 0$.
-\end{proof}
 
@@
 \end{equation}
-The following theorem guarantees the unbiasedness of this estimator under a condition on the parameter $\delta$ of the filter, and we refer to the Appendix for its proof.
+The following theorem guarantees the unbiasedness of this estimator under a condition on the parameter $\delta$ of the filter, and we refer to Appendix \ref{ap:EstimatorTilde} for its proof.
 \begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold.
@@
 
-\begin{table}[ht!]
+\begin{table}[t]
 	\centering
@@
 	\end{tabular}
-	\caption{Numerical results for the four-dimensional parameter rounded to the second significant digit.}
+	\caption{Numerical results for the four-dimensional parameter.}
 	\label{tab:KLStyle}
@@
 
-\section{}
+\section{Proof of Lemmas}\label{ap:Proofs}
+
+\begin{proof}[Proof of Lemma \ref{lem:density}] We have to show that the joint process solution to \eqref{eq:systemSDE} is hypo-elliptic. Denoting as $f\colon \R \to \R$ the function 
+	\begin{equation}
+	f(x) = -\alpha \cdot V'(x) - \frac1\epl p'\left(\frac{x}\epl\right),
+	\end{equation}
+	the generator of the process $(X^\epl, Z^\epl)^\top$ is given by
+	\begin{equation}
+	\mathcal L = f \partial_x + \sigma \partial_{xx}^2 + \frac1\delta (x - z)\partial_z \eqdef \mathcal X_0 + \sigma \mathcal X_1^2, 
+	\end{equation}
+	where 
+	\begin{equation}
+	\mathcal X_0 = f \partial_x + \frac1\delta (x - z)\partial_z, \quad \mathcal X_1 = \partial_x.
+	\end{equation}
+	The commutator $[\mathcal X_0, \mathcal X_1]$ applied to a test function $v$ then gives
+	\begin{equation}
+	\begin{aligned}
+	[\mathcal X_0, \mathcal X_1]v &= f \partial_x^2 v + \frac1\delta (x - z) \partial_x \partial_z v  - \partial_x\left(f\partial_x v + \frac1\delta (x - z)\partial_z v\right)\\
+	&= -\partial_x f \partial_x v - \frac1\delta \partial_z v.
+	\end{aligned}
+	\end{equation}
+	Consequently, 
+	\begin{equation}
+	\mathrm{Lie}\left(\mathcal X_1, [\mathcal X_0, \mathcal X_1]\right) = \mathrm{Lie} \left(\partial_x, -\partial_x f \partial_x - \frac1\delta\partial_z\right),
+	\end{equation}
+	which spans $T_x\R^2$. The desired result then follows from Hörmander's theorem (see e.g. \cite[Chapter 6]{Pav14}).
+\end{proof}
+
+\begin{proof}[Proof of Lemma \ref{lem:ergodicity}] Lemma \ref{lem:density} guarantees that the Fokker--Planck equation can be written directly from the system \eqref{eq:systemSDE}.
+For geometric ergodicity, let
+	\begin{equation}
+	\mathcal S(x,z) \defeq \begin{pmatrix} -\sum_{i=1}^N V_i'(x) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} = -\sum_{i=1}^N V_i'(x)x+\frac1\delta(xz-z^2).
+	\end{equation}
+	Due to Assumption \ref{as:regularity}\ref{as:regularity_diss} and Young's inequality, we then have for all $\gamma > 0$
+	\begin{equation}
+	\mathcal S(x,z) \leq a + \left(\frac{1}{2\gamma\delta} - b\right)x^2 + \frac1\delta\left(\frac{\gamma}{2} - 1\right)z^2.
+	\end{equation}
+	We choose $\gamma = \gamma^* \defeq 1 - b\delta + \sqrt{1 + (1 - b\delta)^2} > 0$ so that
+	\begin{equation}
+	C(\gamma^*) \defeq -\frac{1}{2\gamma^*\delta} + b = -\frac1\delta\left(\frac{\gamma^*}{2} - 1\right),
+	\end{equation}
+	and we notice that $C(\gamma^*) > 0$ if $\delta > 1/(4b)$. In this case, we have
+	\begin{equation}
+	\mathcal S(x, z) \leq a - C(\gamma^*) \norm{\begin{pmatrix} x & z \end{pmatrix}^\top}^2,
+	\end{equation}
+	and problem \eqref{eq:systemSDE} is dissipative. The result then follows from \cite[Theorem 4.4]{MSH02}.
+\end{proof}
+
+\begin{proof}[Proof of Lemma \ref{lem:FPMarginal}] Integrating equation \eqref{eq:FPsystem} with respect to $z$ we obtain the stationary Fokker--Planck equation for the process $X^\epl$, i.e.
+	\begin{equation}
+	\label{FPx}
+	\sigma (\phi^\epl)''(x) + \frac{\d}{\d x} \left( \left ( \alpha \cdot V'(x) + \frac{1}{\epl} p' \left ( \frac{x}\epl \right ) \right ) \phi^\epl(x)\right) = 0,
+	\end{equation}
+	whose solution is given by
+	\begin{equation}
+	\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(- \frac{1}{\sigma} \alpha \cdot V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
+	\end{equation}
+	and which proves \eqref{eq:marginalX}. By integrating equation \eqref{eq:FPsystem} with respect to $x$ and integrating by parts we obtain
+	\begin{equation}
+	\psi^\epl(z) + z (\psi^\epl)'(z) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x,
+	\end{equation}
+	which can be written as
+	\begin{equation}
+	\frac{\d}{\d z} (z \psi^\epl(z)) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x.
+	\end{equation}
+	Now, since $\psi^\epl$ is the density of a probability distribution, this implies that 
+	\begin{equation}\label{FPz}
+	z \psi^\epl(z) = \int_{\R} x \rho^\epl(x,z) \dd x,
+	\end{equation}
+	which, replacing the decomposition \eqref{eq:densityDecomposition}, yields
+	\begin{equation} \label{eq:z_condition}
+	z = \int_{\R} x \phi^\epl(x) R^\epl(x,z) \dd x.
+	\end{equation}
+	In view of \eqref{eq:densityDecomposition} and \eqref{FPx}, equation \eqref{eq:FPsystem} can be rewritten as
+	\begin{equation}\label{eq:psiEqualityPDE}
+	\sigma \phi^\epl \psi^\epl \partial^2_{xx} R^\epl + \frac{1}{\delta} \phi^\epl \psi^\epl R^\epl + \sigma (\phi^\epl)' \psi^\epl \partial_x R^\epl + \frac{1}{\delta} (z-x) \phi^\epl ((\psi^\epl)' R + \psi^\epl \partial_z R^\epl) = 0.
+	\end{equation}
+	We now multiply the equation above by $x$ and integrate with respect to $x$. Let us consider some simplifications explicitly. First, an integration by parts yields
+	\begin{equation}\label{eq:psiEqualityPDE_1}
+	\begin{aligned}
+	\sigma \psi^\epl \int_{\R}  x \phi^\epl \partial^2_{xx} R^\epl \dd x+ \sigma \psi^\epl \int_{\R} x (\phi^\epl)' \partial_x R^\epl \dd x &= -\sigma \psi^\epl \int_{\R} \phi^\epl \partial_x R^\epl \dd x.
+	\end{aligned}
+	\end{equation}
+	Then, applying \eqref{eq:z_condition}, we have
+	\begin{equation}\label{eq:psiEqualityPDE_2}
+	\frac1\delta \psi^\epl \int_{\R} x \phi^\epl  R^\epl \dd x = \frac1\delta z \psi^\epl.
+	\end{equation}
+	Moreover, again applying \eqref{eq:z_condition}, we can compute
+	\begin{equation}\label{eq:psiEqualityPDE_3}
+	\begin{aligned}
+	\frac1\delta (\psi^\epl)' \int_\R (z-x)x \phi^\epl  R \dd x = \frac1\delta (\psi^\epl)' \left(z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x\right).
+	\end{aligned}
+	\end{equation}
+	Finally, we compute the last term always applying \eqref{eq:z_condition} obtaining
+	\begin{equation}\label{eq:psiEqualityPDE_4}
+	\frac1\delta \psi^\epl \int_\R (z-x)x \phi^\epl \partial_z R \dd x = \frac1\delta \psi^\epl\left(z - \int_{\R} x^2 \phi^\epl \partial_z R^\epl \dd x\right).
+	\end{equation}
+	Replacing the equalities \eqref{eq:psiEqualityPDE_1}, \eqref{eq:psiEqualityPDE_2}, \eqref{eq:psiEqualityPDE_3} and \eqref{eq:psiEqualityPDE_4} into \eqref{eq:psiEqualityPDE} we obtain
+	\begin{equation}
+	(\psi^\epl)' \left ( z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x \right ) + \psi^\epl \left ( 2z - \int_{\R} x^2 \phi^\epl \partial_z R^\epl \dd x - \delta \sigma \int_{\R} \phi^\epl \partial_x R^\epl \dd x \right ) = 0.
+	\end{equation}
+	We rewrite the equality above as
+	\begin{equation} \label{eq:psiEquality}
+	\delta \sigma \psi^\epl(z) \int_{\R} \phi^\epl(x) \partial_x R^\epl(x, z) \dd x = 
+	\begin{aligned}[t] &(\psi^\epl)'(z) z^2 - (\psi^\epl)'(z) \int_{\R} x^2 \phi^\epl(x) R^\epl(x, z) \dd x \\
+	& + 2 \psi^\epl(x) z - \psi^\epl \int_{\R} x^2 \phi^\epl(x) \partial_z R^\epl(x, z) \dd x.
+	\end{aligned}
+	\end{equation}
+	Multiplying by $V'(z)$, integrating with respect to $z$ and integrating by parts, we obtain the following identity in $\R^N$
+	\begin{equation}
+	\begin{aligned}
+	\sigma \delta \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z &=  \int_{\R} \int_{\R} (x^2 - z^2) V''(z) \rho_\epl(x,z) \dd x \dd z \\
+	&= \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)],
+	\end{aligned}
+	\end{equation}
+	which is the desired result.
+\end{proof}
+
+\begin{proof}[Proof of Lemma \ref{lem:convMeasure}] Let $(X, Z)^\top \defeq \left((X_t, Z_t)^\top, 0\leq t \leq T\right)$ be the solution of
+	\begin{equation}
+	\label{eq:systemSDEHom}
+	\begin{aligned}
+	\d X_t &= -A \cdot V'(X_t) \dd t + \sqrt{2\Sigma} \dd W_t, \\
+	\d Z_t &= \frac{1}{\delta} \left ( X_t - Z_t \right ) \dd t,
+	\end{aligned}
+	\end{equation} 
+	with $(X_0, Z_0)^\top \sim \mu^0$.
+The arguments of Section \ref{sec:ergodic} can be repeated to conclude that the invariant measure of $(X, Z)^\top$ admits a smooth density $\rho^0$ which satisfies \eqref{eq:FPsystem_homogenized}.
+Moreover, standard homogenization theory (see e.g.
+\cite[Chapter 3]{BLP78}) guarantees that $(X^\epl,Z^\epl)^\top \to (X,Z)^\top$ for $\epl \to 0$ in law as random variables with values in $\mathcal C^0([0, T]; \R^2)$.
+The Portmanteau theorem can be employed to conclude that the measure $\mu^\epl$ converges weakly to $\mu^0$ for $\epl \to 0$.
+\end{proof}
+
+\section{Proof of Theorem \ref{thm:mainTheoremTilde}}\label{ap:EstimatorTilde}
 Let us consider the estimator defined in \eqref{eq:AHatMixedTilde}, that is

### 2020-02-27 CalNotes.tex
CLT - Start

@@
 which, together with \eqref{eq:Proof_I1} and \eqref{eq:alphaDecomposition}, proves the desired result.
+\end{proof}
+
+Central limit theorem text.
+\begin{theorem} Central limit theorem statement.
+\end{theorem}
+
+\begin{proof} Let us remark that $Z_t^\epl$ is adapted with respect to the natural filtration $\mathcal F_t$ of the Wiener process $W \defeq \left(W_t, t \geq 0\right)$. Therefore, denoting
+	\begin{equation}
+		Q^\epl_t \defeq \int_0^t V'(Z^\epl_t) \dd W_t,
+	\end{equation}
+	we have that $Q^\epl_t$ is a martingale and its quadratic variation is given by
+	\begin{equation}
+		\langle Q^\epl \rangle_t = \int_0^t V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t. 
+	\end{equation}
+	The ergodic theorem yields \corr{we need this in $L^1$}
+	\begin{equation}
+		\frac{\langle Q^\epl \rangle_t}{t} \to \E^{\rho^\epl}[V'(Z) \otimes V'(Z)], \quad \text{a.s.},
+	\end{equation}
+	and therefore the martingale central limit theorem gives 
+	\begin{equation}
+		\frac{1}{\sqrt{T}} Q^\epl_T \to \xi \sim \mathcal N(0, \E^{\rho^\epl}[V'(Z) \otimes V'(Z)]), \quad \text{in law}.
+	\end{equation}
+	Now, let us remark that
+	\begin{equation}
+		\sqrt{T} I_2^\epl(T) = \frac{1}{\sqrt{T}} \widetilde M^{-1} Q^\epl_T,
+	\end{equation}
+	and that by the ergodic theorem 
+	\begin{equation}
+		\lim_{T \to \infty} \widetilde M^{-1} = \E^{\rho^\epl}[V'(Z) \otimes V'(X)]^{-1}.
+	\end{equation}
+	Therefore, we have by Slutsky's theorem that
+	\begin{equation}
+		\lim_{T \to \infty} \sqrt{T} I_2^\epl(T) \to \Xi \sim \mathcal N\left(0, \Gamma \right), \quad \text{in law}.
+	\end{equation}
+	where the covariance matrix $\Gamma$ is given by
+	\begin{equation}
+		\Gamma = \E^{\rho^\epl}[V'(Z) \otimes V'(X)]^{-1}\E^{\rho^\epl}[V'(Z) \otimes V'(Z)]\E^{\rho^\epl}[V'(X) \otimes V'(Z)]^{-1}.
+	\end{equation}
 \end{proof}

### 2020-02-28 CalNotes.tex
CLT - Update

--- 2020-02-26 CalNotes.tex
@@
 which, together with \eqref{eq:Proof_I1} and \eqref{eq:alphaDecomposition}, proves the desired result.
+\end{proof}
+
+Central limit theorem text.
+\begin{theorem}\label{thm:CLT} Central limit theorem statement:
+	\begin{equation}
+		\lim_{\epl \to 0}\lim_{T \to \infty} \sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \Lambda, \quad \text{in law,}
+	\end{equation}
+	where $\Lambda \sim \mathcal N(0, \Gamma)$ and 
+	\begin{equation}
+		\Gamma = 2\sigma \E^{\rho^0}[V'(Z) \otimes V'(X)]^{-1}\E^{\rho^0}[V'(Z) \otimes V'(Z)]\E^{\rho^0}[V'(X) \otimes V'(Z)]^{-1}.
+	\end{equation}
+\end{theorem}
+
+\begin{proof} Let us consider the decomposition \eqref{eq:alphaDecomposition}, which yields
+	\begin{equation}
+		\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) - \sqrt{T} I_2^\epl(T).
+	\end{equation}
+	\corr{Second term is OK:} We rewrite the term involving $I_2^\epl(T)$ as
+	\begin{equation}
+	\sqrt{T} I_2^\epl(T) = \frac{\sqrt{2\sigma}}{\sqrt{T}} \widetilde M^{-1} Q^\epl_T,
+	\end{equation}
+	where, since $Z_t^\epl$ is adapted with respect to the natural filtration $\mathcal F_t$ of the Wiener process $W \defeq \left(W_t, t \geq 0\right)$, the quantity
+	\begin{equation}
+	Q^\epl_T \defeq \int_0^T V'(Z^\epl_t) \dd W_t,
+	\end{equation}
+	is a martingale whose quadratic variation is given by
+	\begin{equation}
+	\langle Q^\epl \rangle_T = \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t. 
+	\end{equation}
+	Since the ergodic theorem guarantees that 
+	\begin{equation}
+	\lim_{T\to\infty}\frac{\langle Q^\epl \rangle_T}{T} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)], \quad \text{in } L^1(\mu^\epl),
+	\end{equation}
+	the martingale central limit theorem gives 
+	\begin{equation}
+	\lim_{T\to\infty}\frac{1}{\sqrt{T}} Q^\epl_T = \Xi^\epl, \quad \text{in law},
+	\end{equation}
+	where $\Xi^\epl \sim \mathcal N(0, \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)])$.
+	Now, by the ergodic theorem 
+	\begin{equation}
+	\lim_{T \to \infty} \widetilde M^{-1} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}, \quad \text{a.s.}
+	\end{equation}
+	Therefore, we have by Slutsky's theorem that
+	\begin{equation}
+	\lim_{T \to \infty} \sqrt{T} I_2^\epl(T) = \Lambda^\epl \sim \mathcal N\left(0, \Gamma^\epl\right), \quad \text{in law}.
+	\end{equation}
+	where the covariance matrix $\Gamma^\epl$ is given by
+	\begin{equation}
+		\Gamma^\epl = 2\sigma \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}\E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)]\E^{\rho^\epl}[V'(X^\epl) \otimes V'(Z^\epl)]^{-1}.
+	\end{equation}
+	Finally, we denote by $\Lambda$ the limit for $\epl \to 0$ of the sequence of Gaussian random variables $\Lambda^\epl$.
+
+	\corr{Idea for the first term:} Let $\mathcal L^\epl$ be the generator of the joint process $(X^\epl, Z^\epl)$, i.e.,
+	\begin{equation}
+		\mathcal L^\epl = \begin{pmatrix} -V'(x) - \frac1\epl p'\left(\frac{x}{\epl}\right) \\ \frac1\delta (x - z)	\end{pmatrix} \cdot \nabla_{x, z} + \sigma \partial^2_{xx}.
+	\end{equation}
+	Then, let $\Phi^\epl$ the solution of the Poisson equation
+	\begin{equation}
+		\mathcal L^\epl \Phi^\epl(x, z) = V'(z)\frac1\epl p'\left(\frac{x}{\epl}\right) - \E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right].
+	\end{equation}	
+	An application of Itô formula \cite[Remark 6.17]{PaS08} yields
+	\begin{equation}
+		\frac{1}{T} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t = \E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right] + \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T},
+	\end{equation}
+	where the remainder $R_T^\epl$ is given by
+	\begin{equation}
+		R_T^\epl \defeq \Phi^\epl(X^\epl_T, Z^\epl_T) - \Phi^\epl(X^\epl_0, Z^\epl_0),
+	\end{equation}
+	and $S^\epl_T$ is the martingale defined as
+	\begin{equation}
+		S^\epl_T \defeq \int_0^T \partial_x \Phi^\epl(X_t^\epl, Z_t^\epl) \dd t.
+	\end{equation}
+	Therefore, we have
+	\begin{equation}
+	\begin{aligned}
+		\sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) = & \sqrt{T}\left(\alpha - A + \widetilde M^{-1}\E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right]\right)\\
+		& + \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} - \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}}.
+	\end{aligned}
+	\end{equation}
+	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get by the ergodic theorem that
+	\begin{equation}
+		\lim_{T \to \infty} \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
+	\end{equation}
+	Repeating the same reasoning as for $Q_T^\epl$, we get 
+	\begin{equation}
+		\lim_{T \to \infty} \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
+	\end{equation}
+	where the covariance is given by
+	\begin{equation}
+		\Gamma_1^\epl = 2\sigma \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}\E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)]\E^{\rho^\epl}[V'(X^\epl) \otimes V'(Z^\epl)]^{-1}.
+	\end{equation}
+
 \end{proof}
@@
 
+\subsection{Central limit theorem}
+\begin{figure}[t]
+	\centering
+	\includegraphics[]{Figures/CLT}
+	\caption{Central limit theorem result.
+The histogram represents numerical results, the solid curve a Gaussian fit to the latter and the dashed curve $\rho_a$ represents the theoretical estimate given in Theorem \ref{thm:CLT}.}
+	\label{fig:CLT}
+\end{figure}
+
 \subsection{The Bayesian approach: bistable potential}

### 2020-02-28 CalNotes.tex
TCL

@@
 	\begin{equation}
-		\Gamma = 2\sigma \E^{\rho^0}[V'(Z) \otimes V'(X)]^{-1}\E^{\rho^0}[V'(Z) \otimes V'(Z)]\E^{\rho^0}[V'(X) \otimes V'(Z)]^{-1}.
+		\Gamma = 2\sigma \E^{\rho^0}[V'(Z) \otimes V'(X)]^{-1}\E^{\rho^0}[V'(Z) \otimes V'(Z)]\E^{\rho^0}[V'(X) \otimes V'(Z)]^{-1} \corr{+ \dots}.
 	\end{equation}
@@
 
-\begin{proof} Let us consider the decomposition \eqref{eq:alphaDecomposition}, which yields
-	\begin{equation}
-		\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) - \sqrt{T} I_2^\epl(T).
-	\end{equation}
-	\corr{Second term is OK:} We rewrite the term involving $I_2^\epl(T)$ as
+\begin{proof} Let us remark that in the proof of Theorem \ref{thm:mainTheorem} we showed that
+	\begin{equation}
+	A = \frac1\delta \E^{\rho^0}[V'(Z) \otimes V'(X)]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)],
+	\end{equation}
+	and
+	\begin{equation}
+	\E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] = - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ] \alpha + \frac1\delta \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)].
+	\end{equation}
+	Hence, the decomposition \eqref{eq:alphaDecomposition} yields
+	\begin{equation}
+	\begin{aligned}
+	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = & \sqrt{T}\left( I_1^\epl(T) - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right) \\
+	&+ \sqrt{T} \frac1\delta \left( \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \right. \\
+	&\qquad \qquad \left. - \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
+	&- \sqrt{T} I_2^\epl(T).
+	\end{aligned}
+	\end{equation}
+	\corr{Third term is OK:} We rewrite the term involving $I_2^\epl(T)$ as
 	\begin{equation}
@@
 
-	\corr{Idea for the first term:} Let $\mathcal L^\epl$ be the generator of the joint process $(X^\epl, Z^\epl)$, i.e.,
+	\corr{Idea for the first term:} The first term can be decomposed in
+	\begin{equation} \label{eq:decomposition_first_term}
+	\begin{aligned}
+	\sqrt{T}&\left( I_1^\epl(T) - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right) \\
+	&\hspace{2cm}= \sqrt{T} \left( I_1^\epl(T) - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \frac1T \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t \right) \\
+	&\hspace{2cm} \quad + \sqrt{T} \left(\E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \frac1T \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t \right. \\
+	&\hspace{4cm} \left. - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right),
+	\end{aligned}
+	\end{equation}
+	and now we focus on its second part. Let $\mathcal L^\epl$ be the generator of the joint process $(X^\epl, Z^\epl)$, i.e.,
 	\begin{equation}
@@
 	\end{equation}
-	Then, let $\Phi^\epl$ the solution of the Poisson equation
-	\begin{equation}
-		\mathcal L^\epl \Phi^\epl(x, z) = V'(z)\frac1\epl p'\left(\frac{x}{\epl}\right) - \E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right].
+	Then, let $\Phi_1^\epl$ the solution of the Poisson equation
+	\begin{equation}
+		\mathcal L^\epl \Phi_1^\epl(x, z) = V'(z)\frac1\epl p'\left(\frac{x}{\epl}\right) - \E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right].
 	\end{equation}	
@@
 	\begin{equation}
-		R_T^\epl \defeq \Phi^\epl(X^\epl_T, Z^\epl_T) - \Phi^\epl(X^\epl_0, Z^\epl_0),
+		R_T^\epl \defeq \Phi_1^\epl(X^\epl_T, Z^\epl_T) - \Phi_1^\epl(X^\epl_0, Z^\epl_0),
 	\end{equation}
@@
 	\begin{equation}
-		S^\epl_T \defeq \int_0^T \partial_x \Phi^\epl(X_t^\epl, Z_t^\epl) \dd t.
+		S^\epl_T \defeq \int_0^T \partial_x \Phi_1^\epl(X_t^\epl, Z_t^\epl) \dd t.
 	\end{equation}
 	Therefore, we have
-	\begin{equation}
-	\begin{aligned}
-		\sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) = & \sqrt{T}\left(\alpha - A + \widetilde M^{-1}\E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right]\right)\\
-		& + \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} - \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}}.
+%	\begin{equation}
+%	\begin{aligned}
+%		\sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) = & \sqrt{T}\left(\alpha - A + \widetilde M^{-1}\E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right]\right)\\
+%		& + \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} - \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}}.
+%	\end{aligned}
+%	\end{equation}
+	\begin{equation}
+	\begin{aligned}
+		\sqrt{T} \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} & \left( \frac1T \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t - \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right) \\
+		&= \sqrt{T} \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \left( \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T} \right)
 	\end{aligned}
@@
 	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get by the ergodic theorem that
-	\begin{equation}
-		\lim_{T \to \infty} \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
+%	\begin{equation}
+%		\lim_{T \to \infty} \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
+%	\end{equation}
+	\begin{equation}
+		\lim_{T \to \infty} \frac{\E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
 	\end{equation}
 	Repeating the same reasoning as for $Q_T^\epl$, we get 
-	\begin{equation}
-		\lim_{T \to \infty} \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
+%	\begin{equation}
+%		\lim_{T \to \infty} \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
+%	\end{equation}
+	\begin{equation}
+	\lim_{T \to \infty} \sqrt{2\sigma} \frac{\E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
 	\end{equation}
@@
 	\begin{equation}
-		\Gamma_1^\epl = 2\sigma \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}\E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)]\E^{\rho^\epl}[V'(X^\epl) \otimes V'(Z^\epl)]^{-1}.
-	\end{equation}
-
+		\Gamma_1^\epl = 2\sigma \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}\E^{\rho^\epl}[\partial_x \Phi_1^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_1^\epl(X^\epl, Z^\epl)]\E^{\rho^\epl}[V'(X^\epl) \otimes V'(Z^\epl)]^{-1}.
+	\end{equation}
+	\corr{For the second part of \eqref{eq:decomposition_first_term} we follow a similar procedure defining a different Poisson equation.
+The argument has to be slightly modified because we have to work with random matrix rather than random vector, but finally we obtain a second Gaussian term $\mathcal N(0, \Gamma_2^\epl)$.
+Therefore, we have to study the limit as $\epl$ goes to zero of the covariance matrices $\Gamma_1^\epl$ and $\Gamma_2^\epl$, which depend on the solutions $\Phi_1^\epl$ and $\Phi_2^\epl$ of the Poisson problems.} \\
+
+	\corr{Idea for the second term:} The second term can be decomposed in 
+	\begin{equation}
+	\begin{aligned}
+	\sqrt{T} \frac1\delta & \left( \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \right. \\
+	&\hspace{3cm} \left. - \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
+	&= \sqrt{T} \frac1\delta \left( \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \right. \\
+	&\hspace{3cm} \left. - \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \right) \\
+	&\quad + \sqrt{T} \frac1\delta \left( \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \right. \\
+	&\hspace{3cm} \left. - \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right), \\
+	\end{aligned}
+	\end{equation}
+	\corr{and we need the rate of convergence of the measure $\rho^\epl$ to $\rho^0$.}
 \end{proof}

### 2020-03-03 CalNotes.tex
Update CTL

@@
 Efficient parameter estimation for stochastic models is essential in a wide range of applications in natural and social sciences.
-In several areas, the data originates from phenomena which vary continuously in time and which are endowed with a multiscale structure.
+In several areas, the data originate from phenomena which vary continuously in time and which are endowed with a multiscale structure.
 This is the case, for example, in molecular dynamics, oceanography and atmosphere science or in econometrics.
@@
 		\begin{equation}
-		-\sum_{i=1}^N V_i'(x)x \leq a - bx^2.
+		-\alpha \cdot V'(x) x \leq a - bx^2.
 		\end{equation} 
@@
 \end{assumption}
+
+\corr{
+\begin{remark}\label{rem:regularity_diss} In the following, in particular in the proof of Lemma \ref{lem:ergodicity}, we will employ Assumption \ref{as:regularity}\ref{as:regularity_diss} for the whole drift of the SDE \eqref{eq:SDE_MS}, i.e., the function
+	\begin{equation}
+		V^\epl(x) \defeq \alpha \cdot V(x) - p\left(\frac{x}{\epl}\right).
+	\end{equation}
+	Since $p \in L^\infty$, the assumption above is sufficient for $V^\epl$ to satisfy Assumption \ref{as:regularity}\ref{as:regularity_diss} with different values for $a$ and $b$.
+In particular, if the condition holds for $\alpha \cdot V$ for a given $b > 0$, then one can choose a new value for the same coefficient which is arbitrarily close to the original one for $V^\epl$.
+\end{remark}
+}
 
@@
 \end{lemma}
-
-\begin{remark} Let us remark that for the multiscale equation \eqref{eq:SDE_MS} one should check the condition above for the potential $V(x) + p(x/\epl)$.
-Nevertheless, for functions $p$ satisfying Assumption \ref{as:regularity}, the result holds trivially.
-\end{remark}
 
@@
 
-\begin{proof} Let us remark that in the proof of Theorem \ref{thm:mainTheorem} we showed that
-	\begin{equation}
-	A = \frac1\delta \E^{\rho^0}[V'(Z) \otimes V'(X)]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)],
+\begin{proof} Let us introduce the notation
+	\begin{equation}
+		\mathcal M_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ], \quad \mathcal M_0 \defeq \E^{\rho^0} [ V'(Z) \otimes V'(X) ],
+	\end{equation}
+	and the notation
+	\begin{equation}
+		\mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ]\
+	\end{equation}
+	and let us remark that from the proof of Theorem \ref{thm:mainTheorem} one can deduce the equalities
+	\begin{equation}\label{eq:CTL_A}
+		A = \frac1\delta \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)],
 	\end{equation}
 	and
-	\begin{equation}
-	\E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] = - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ] \alpha + \frac1\delta \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)].
-	\end{equation}
-	Hence, the decomposition \eqref{eq:alphaDecomposition} yields
-	\begin{equation}
-	\begin{aligned}
-	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = & \sqrt{T}\left( I_1^\epl(T) - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right) \\
-	&+ \sqrt{T} \frac1\delta \left( \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \right. \\
-	&\qquad \qquad \left. - \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
+	\begin{equation}\label{eq:CTL_alpha}
+		\alpha = \mathcal M_\epl^{-1} \left(\frac1\delta \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathfrak p_\epl \right).
+	\end{equation}
+	Let us furthermore remark that the decomposition \eqref{eq:alphaDecomposition} yields
+	\begin{equation}
+		\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \sqrt{T} \left(\alpha - A + I_1^\epl - I_2^\epl\right).
+	\end{equation}
+	Replacing the expression for $A$ and $\alpha$ given in \eqref{eq:CTL_A} and \eqref{eq:CTL_alpha}, we get
+	\begin{equation}
+	\begin{aligned}
+	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) &= \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \\
+	&+  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
 	&- \sqrt{T} I_2^\epl(T).
@@
 	\begin{equation}
-	\lim_{T \to \infty} \widetilde M^{-1} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}, \quad \text{a.s.}
+	\lim_{T \to \infty} \widetilde M^{-1} = \mathcal M_\epl^{-1}, \quad \text{a.s.}
 	\end{equation}
@@
 	\begin{equation}
-		\Gamma^\epl = 2\sigma \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}\E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)]\E^{\rho^\epl}[V'(X^\epl) \otimes V'(Z^\epl)]^{-1}.
+		\Gamma^\epl = 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)]\mathcal M_\epl^{-\top}.
 	\end{equation}
@@
 
-	\corr{Idea for the first term:} The first term can be decomposed in
+	\corr{Idea for the first term:} Let us introduce the notation
+	\begin{equation}
+		J_1^\epl(T) \defeq \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl\right),
+	\end{equation}
+	and let us remark that we can rewrite
 	\begin{equation} \label{eq:decomposition_first_term}
 	\begin{aligned}
-	\sqrt{T}&\left( I_1^\epl(T) - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right) \\
-	&\hspace{2cm}= \sqrt{T} \left( I_1^\epl(T) - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \frac1T \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t \right) \\
-	&\hspace{2cm} \quad + \sqrt{T} \left(\E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \frac1T \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t \right. \\
-	&\hspace{4cm} \left. - \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right),
-	\end{aligned}
-	\end{equation}
-	and now we focus on its second part. Let $\mathcal L^\epl$ be the generator of the joint process $(X^\epl, Z^\epl)$, i.e.,
-	\begin{equation}
-		\mathcal L^\epl = \begin{pmatrix} -V'(x) - \frac1\epl p'\left(\frac{x}{\epl}\right) \\ \frac1\delta (x - z)	\end{pmatrix} \cdot \nabla_{x, z} + \sigma \partial^2_{xx}.
-	\end{equation}
-	Then, let $\Phi_1^\epl$ the solution of the Poisson equation
-	\begin{equation}
-		\mathcal L^\epl \Phi_1^\epl(x, z) = V'(z)\frac1\epl p'\left(\frac{x}{\epl}\right) - \E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right].
-	\end{equation}	
-	An application of Itô formula \cite[Remark 6.17]{PaS08} yields
-	\begin{equation}
-		\frac{1}{T} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t = \E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right] + \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T},
-	\end{equation}
-	where the remainder $R_T^\epl$ is given by
-	\begin{equation}
-		R_T^\epl \defeq \Phi_1^\epl(X^\epl_T, Z^\epl_T) - \Phi_1^\epl(X^\epl_0, Z^\epl_0),
-	\end{equation}
-	and $S^\epl_T$ is the martingale defined as
-	\begin{equation}
-		S^\epl_T \defeq \int_0^T \partial_x \Phi_1^\epl(X_t^\epl, Z_t^\epl) \dd t.
-	\end{equation}
+	J_1^\epl(T) &= \sqrt{T} \left( I_1^\epl(T) - \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\mathfrak p_\epl \right) \\
+	& \quad + \sqrt{T} \left(\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} - \mathcal M_\epl^{-1}\right) \mathfrak p_\epl\\
+	&\eqdef J_{1,1}^\epl(T) + J_{1,2}^\epl(T).
+	\end{aligned}
+	\end{equation}
+	In order to treat the terms $J_{1,1}^\epl(T)$ and $J_{1,2}^\epl(T)$, we will employ a technique presented in \cite[Remark 6.17]{PaS08}.
+Denoting by $\mathcal L^\epl$ be the generator of the joint process $(X^\epl, Z^\epl)$, i.e.,
+	\begin{equation}
+		\mathcal L^\epl = -\left(V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)\partial_x + \frac1\delta (x - z) \partial_z  + \sigma \partial^2_{xx},
+	\end{equation}
+	let $\Phi^\epl$ the solution of the Poisson equation
+	\begin{equation}\label{eq:CLT_Poisson}
+		\mathcal L^\epl \Phi^\epl(x, z) = \chi(x, z) - \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)].
+	\end{equation}	
+	where $\chi$ is a sufficiently smooth function. Then, an application of Itô formula  yields
+	\begin{equation}
+	\frac{1}{T} \int_0^T  \chi(X_t^\epl, Z_t^\epl) \dd t = \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)] + \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T},
+	\end{equation}
+	where
+	\begin{equation}
+		R_T^\epl \defeq \Phi^\epl(X^\epl_T, Z^\epl_T) - \Phi^\epl(X^\epl_0, Z^\epl_0), \quad S^\epl_T \defeq \int_0^T \partial_x \Phi^\epl(X_t^\epl, Z_t^\epl) \dd W_t.
+	\end{equation}
+	Let us consider $J_{1,1}^\epl(T)$ and denote by $\Phi_1^\epl$ the solution of \eqref{eq:CLT_Poisson} with 
+	\begin{equation}
+		\chi(x, z) = 
+	\end{equation}
+
+	Let us first focus on $J_{1,2}^\epl(T)$. Denoting by
+
 	Therefore, we have
@@
 	\begin{equation}
-	\begin{aligned}
-		\sqrt{T} \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} & \left( \frac1T \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t - \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] \right) \\
-		&= \sqrt{T} \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \left( \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T} \right)
-	\end{aligned}
-	\end{equation}
-	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get by the ergodic theorem that
+		J_{1,1}^\epl(T)= \sqrt{T} \mathcal M_\epl^{-1} \left( \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T} \right)
+	\end{equation}
+	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get
 %	\begin{equation}
@@
 	\begin{equation}
-		\lim_{T \to \infty} \frac{\E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
+		\lim_{T \to \infty} \frac{\mathcal M_\epl^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
 	\end{equation}
@@
 	\begin{equation}
-	\lim_{T \to \infty} \sqrt{2\sigma} \frac{\E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
+	\lim_{T \to \infty} \sqrt{2\sigma} \frac{\mathcal M_\epl^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
 	\end{equation}
@@
 	\begin{equation}
-		\Gamma_1^\epl = 2\sigma \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)]^{-1}\E^{\rho^\epl}[\partial_x \Phi_1^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_1^\epl(X^\epl, Z^\epl)]\E^{\rho^\epl}[V'(X^\epl) \otimes V'(Z^\epl)]^{-1}.
+		\Gamma_1^\epl = 2\sigma \mathcal M^{-1}\E^{\rho^\epl}[\partial_x \Phi_1^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_1^\epl(X^\epl, Z^\epl)]\mathcal M^{-\top}.
 	\end{equation}
@@
 	\begin{equation}
-	\mathcal S(x,z) \defeq \begin{pmatrix} -\sum_{i=1}^N V_i'(x) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} = -\sum_{i=1}^N V_i'(x)x+\frac1\delta(xz-z^2).
-	\end{equation}
-	Due to Assumption \ref{as:regularity}\ref{as:regularity_diss} and Young's inequality, we then have for all $\gamma > 0$
+	\mathcal S(x,z) \defeq \begin{pmatrix} -\alpha \cdot V'(x) - \frac1\epl p'(\frac{x}{\epl}) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} =  -\left(\alpha \cdot V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)x + \frac1\delta(xz-z^2).
+	\end{equation}
+	Due to Assumption \ref{as:regularity}\ref{as:regularity_diss}, Remark \ref{rem:regularity_diss} and Young's inequality, we then have for all $\gamma > 0$
 	\begin{equation}

### 2020-03-03 CalNotes.tex
CLT 2

@@
 	\end{equation}
-	Let us consider $J_{1,1}^\epl(T)$ and denote by $\Phi_1^\epl$ the solution of \eqref{eq:CLT_Poisson} with 
-	\begin{equation}
-		\chi(x, z) = 
+	Let us consider $J_{1,1}^\epl(T)$, which can be written
+	\begin{equation}
+	J_{1,1}^\epl(T) = \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( \frac{1}{T} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t - \mathfrak p_\epl \right),
+	\end{equation}
+	and denote by $\Phi_1^\epl$ the solution of \eqref{eq:CLT_Poisson} with 
+	\begin{equation}
+		\chi(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z).
 	\end{equation}
@@
 	\begin{equation}
-		J_{1,1}^\epl(T)= \sqrt{T} \mathcal M_\epl^{-1} \left( \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T} \right)
-	\end{equation}
-	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get
+		J_{1,1}^\epl(T)= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T} \right)
+	\end{equation}
+	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get by the ergodic theorem
 %	\begin{equation}
@@
 	\begin{equation}
-		\lim_{T \to \infty} \frac{\mathcal M_\epl^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
-	\end{equation}
-	Repeating the same reasoning as for $Q_T^\epl$, we get 
+		\lim_{T \to \infty} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
+	\end{equation}
+	Repeating the same reasoning as for $Q_T^\epl$ and employing the ergodic theorem, we get 
 %	\begin{equation}
@@
 	\begin{equation}
-	\lim_{T \to \infty} \sqrt{2\sigma} \frac{\mathcal M_\epl^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
+	\lim_{T \to \infty} \sqrt{2\sigma} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
 	\end{equation}

### 2020-03-05 CalNotes.tex
Partial proof CLT

--- 2020-03-03 CalNotes.tex
@@
 
-For simple models in molecular dynamics, the effect of model misspecification was studied in a series of papers \cite{PaS07,PPS09,PPS12,GaS17,GaS18} under the assumption of scale separation.
+For simple models in molecular dynamics, the effect of model misspecification was studied in a series of papers \cite{ABT10,ABJ13,PaS07,PPS09,PPS12,GaS17,GaS18} under the assumption of scale separation.
 In particular, for Brownian particles moving in two-scale potentials it was shown that, when fitting data from the full dynamics to the homogenized equation, the maximum likelihood estimator (MLE) is asymptotically biased \cite[Theorem 3.4]{PaS07}.
@@
 
-Central limit theorem text.
+\subsection{Central limit theorem}
+
+\corr{Text to be added with motivation, proof in Appendix \ref{ap:CLT}.
 \begin{theorem}\label{thm:CLT} Central limit theorem statement:
@@
 	\begin{equation}
-		\Gamma = 2\sigma \E^{\rho^0}[V'(Z) \otimes V'(X)]^{-1}\E^{\rho^0}[V'(Z) \otimes V'(Z)]\E^{\rho^0}[V'(X) \otimes V'(Z)]^{-1} \corr{+ \dots}.
-	\end{equation}
+		\Gamma = 2\sigma \E^{\rho^0}[V'(Z) \otimes V'(X)]^{-1}\E^{\rho^0}[V'(Z) \otimes V'(Z)]\E^{\rho^0}[V'(X) \otimes V'(Z)]^{-1}.
+	\end{equation}
+	This covariance may not be correct (see proof in the Appendix) but it is just the limit of the ``third term'' 
 \end{theorem}
-
-\begin{proof} Let us introduce the notation
-	\begin{equation}
-		\mathcal M_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ], \quad \mathcal M_0 \defeq \E^{\rho^0} [ V'(Z) \otimes V'(X) ],
-	\end{equation}
-	and the notation
-	\begin{equation}
-		\mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ]\
-	\end{equation}
-	and let us remark that from the proof of Theorem \ref{thm:mainTheorem} one can deduce the equalities
-	\begin{equation}\label{eq:CTL_A}
-		A = \frac1\delta \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)],
-	\end{equation}
-	and
-	\begin{equation}\label{eq:CTL_alpha}
-		\alpha = \mathcal M_\epl^{-1} \left(\frac1\delta \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathfrak p_\epl \right).
-	\end{equation}
-	Let us furthermore remark that the decomposition \eqref{eq:alphaDecomposition} yields
-	\begin{equation}
-		\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \sqrt{T} \left(\alpha - A + I_1^\epl - I_2^\epl\right).
-	\end{equation}
-	Replacing the expression for $A$ and $\alpha$ given in \eqref{eq:CTL_A} and \eqref{eq:CTL_alpha}, we get
-	\begin{equation}
-	\begin{aligned}
-	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) &= \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \\
-	&+  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
-	&- \sqrt{T} I_2^\epl(T).
-	\end{aligned}
-	\end{equation}
-	\corr{Third term is OK:} We rewrite the term involving $I_2^\epl(T)$ as
-	\begin{equation}
-	\sqrt{T} I_2^\epl(T) = \frac{\sqrt{2\sigma}}{\sqrt{T}} \widetilde M^{-1} Q^\epl_T,
-	\end{equation}
-	where, since $Z_t^\epl$ is adapted with respect to the natural filtration $\mathcal F_t$ of the Wiener process $W \defeq \left(W_t, t \geq 0\right)$, the quantity
-	\begin{equation}
-	Q^\epl_T \defeq \int_0^T V'(Z^\epl_t) \dd W_t,
-	\end{equation}
-	is a martingale whose quadratic variation is given by
-	\begin{equation}
-	\langle Q^\epl \rangle_T = \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t. 
-	\end{equation}
-	Since the ergodic theorem guarantees that 
-	\begin{equation}
-	\lim_{T\to\infty}\frac{\langle Q^\epl \rangle_T}{T} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)], \quad \text{in } L^1(\mu^\epl),
-	\end{equation}
-	the martingale central limit theorem gives 
-	\begin{equation}
-	\lim_{T\to\infty}\frac{1}{\sqrt{T}} Q^\epl_T = \Xi^\epl, \quad \text{in law},
-	\end{equation}
-	where $\Xi^\epl \sim \mathcal N(0, \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)])$.
-	Now, by the ergodic theorem 
-	\begin{equation}
-	\lim_{T \to \infty} \widetilde M^{-1} = \mathcal M_\epl^{-1}, \quad \text{a.s.}
-	\end{equation}
-	Therefore, we have by Slutsky's theorem that
-	\begin{equation}
-	\lim_{T \to \infty} \sqrt{T} I_2^\epl(T) = \Lambda^\epl \sim \mathcal N\left(0, \Gamma^\epl\right), \quad \text{in law}.
-	\end{equation}
-	where the covariance matrix $\Gamma^\epl$ is given by
-	\begin{equation}
-		\Gamma^\epl = 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)]\mathcal M_\epl^{-\top}.
-	\end{equation}
-	Finally, we denote by $\Lambda$ the limit for $\epl \to 0$ of the sequence of Gaussian random variables $\Lambda^\epl$.
-
-	\corr{Idea for the first term:} Let us introduce the notation
-	\begin{equation}
-		J_1^\epl(T) \defeq \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl\right),
-	\end{equation}
-	and let us remark that we can rewrite
-	\begin{equation} \label{eq:decomposition_first_term}
-	\begin{aligned}
-	J_1^\epl(T) &= \sqrt{T} \left( I_1^\epl(T) - \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\mathfrak p_\epl \right) \\
-	& \quad + \sqrt{T} \left(\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} - \mathcal M_\epl^{-1}\right) \mathfrak p_\epl\\
-	&\eqdef J_{1,1}^\epl(T) + J_{1,2}^\epl(T).
-	\end{aligned}
-	\end{equation}
-	In order to treat the terms $J_{1,1}^\epl(T)$ and $J_{1,2}^\epl(T)$, we will employ a technique presented in \cite[Remark 6.17]{PaS08}.
-Denoting by $\mathcal L^\epl$ be the generator of the joint process $(X^\epl, Z^\epl)$, i.e.,
-	\begin{equation}
-		\mathcal L^\epl = -\left(V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)\partial_x + \frac1\delta (x - z) \partial_z  + \sigma \partial^2_{xx},
-	\end{equation}
-	let $\Phi^\epl$ the solution of the Poisson equation
-	\begin{equation}\label{eq:CLT_Poisson}
-		\mathcal L^\epl \Phi^\epl(x, z) = \chi(x, z) - \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)].
-	\end{equation}	
-	where $\chi$ is a sufficiently smooth function. Then, an application of Itô formula  yields
-	\begin{equation}
-	\frac{1}{T} \int_0^T  \chi(X_t^\epl, Z_t^\epl) \dd t = \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)] + \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T},
-	\end{equation}
-	where
-	\begin{equation}
-		R_T^\epl \defeq \Phi^\epl(X^\epl_T, Z^\epl_T) - \Phi^\epl(X^\epl_0, Z^\epl_0), \quad S^\epl_T \defeq \int_0^T \partial_x \Phi^\epl(X_t^\epl, Z_t^\epl) \dd W_t.
-	\end{equation}
-	Let us consider $J_{1,1}^\epl(T)$ and denote by $\Phi_1^\epl$ the solution of \eqref{eq:CLT_Poisson} with 
-	\begin{equation}
-		\chi(x, z) = 
-	\end{equation}
-
-	Let us first focus on $J_{1,2}^\epl(T)$. Denoting by
-
-	Therefore, we have
-%	\begin{equation}
-%	\begin{aligned}
-%		\sqrt{T}\left(\alpha - A + I_1^\epl(T)\right) = & \sqrt{T}\left(\alpha - A + \widetilde M^{-1}\E^{\rho^\epl}\left[V'(Z^\epl)\frac1\epl p'\left(\frac{X^\epl}{\epl}\right)\right]\right)\\
-%		& + \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} - \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}}.
-%	\end{aligned}
-%	\end{equation}
-	\begin{equation}
-		J_{1,1}^\epl(T)= \sqrt{T} \mathcal M_\epl^{-1} \left( \frac{R_T^\epl}{T} - \sqrt{2\sigma}\frac{S^\epl_T}{T} \right)
-	\end{equation}
-	Since \corr{$R^\epl_T$ is bounded independently of $\epl$}, we first get
-%	\begin{equation}
-%		\lim_{T \to \infty} \frac{\widetilde M^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
-%	\end{equation}
-	\begin{equation}
-		\lim_{T \to \infty} \frac{\mathcal M_\epl^{-1} R_T^\epl}{\sqrt{T}} = 0, \quad \text{a.s.}
-	\end{equation}
-	Repeating the same reasoning as for $Q_T^\epl$, we get 
-%	\begin{equation}
-%		\lim_{T \to \infty} \sqrt{2\sigma} \frac{\widetilde M^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
-%	\end{equation}
-	\begin{equation}
-	\lim_{T \to \infty} \sqrt{2\sigma} \frac{\mathcal M_\epl^{-1} S_T^\epl}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
-	\end{equation}
-	where the covariance is given by
-	\begin{equation}
-		\Gamma_1^\epl = 2\sigma \mathcal M^{-1}\E^{\rho^\epl}[\partial_x \Phi_1^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_1^\epl(X^\epl, Z^\epl)]\mathcal M^{-\top}.
-	\end{equation}
-	\corr{For the second part of \eqref{eq:decomposition_first_term} we follow a similar procedure defining a different Poisson equation.
-The argument has to be slightly modified because we have to work with random matrix rather than random vector, but finally we obtain a second Gaussian term $\mathcal N(0, \Gamma_2^\epl)$.
-Therefore, we have to study the limit as $\epl$ goes to zero of the covariance matrices $\Gamma_1^\epl$ and $\Gamma_2^\epl$, which depend on the solutions $\Phi_1^\epl$ and $\Phi_2^\epl$ of the Poisson problems.} \\
-
-	\corr{Idea for the second term:} The second term can be decomposed in 
-	\begin{equation}
-	\begin{aligned}
-	\sqrt{T} \frac1\delta & \left( \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \right. \\
-	&\hspace{3cm} \left. - \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
-	&= \sqrt{T} \frac1\delta \left( \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \right. \\
-	&\hspace{3cm} \left. - \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \right) \\
-	&\quad + \sqrt{T} \frac1\delta \left( \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \right. \\
-	&\hspace{3cm} \left. - \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right), \\
-	\end{aligned}
-	\end{equation}
-	\corr{and we need the rate of convergence of the measure $\rho^\epl$ to $\rho^0$.}
-\end{proof}
-
+}
 \section{The Bayesian setting}\label{sec:Bayesian}
@@
 
-\subsection{Parameters of the filter}
+\subsection{Parameters of the filter}\label{sec:Num_Param}
 \begin{figure}[t]
@@
 
+\subsection{Central limit theorem}
+\begin{figure}[t]
+	\centering
+	\includegraphics[]{Figures/CLT}
+	\caption{Central limit theorem result.
+The histogram represents numerical results, the solid curve a Gaussian fit to the latter and the dashed curve the theoretical estimate given in Theorem \ref{thm:CLT}.}
+	\label{fig:CLT}
+\end{figure}
+
+In this experiment we wish to confirm the validity of Theorem \ref{thm:CLT}.
+We consider the same test equation as for Section \ref{sec:Num_Param}, i.e., the quadratic potential $V(x) = x^2/2$ with fluctuating potential $p(y) = \sin(y)$, multiscale parameter $\epl = 0.05$ and diffusion coefficient $\sigma = 1$.
+The parameters of the filter are set to $\beta = 1$ and $\delta = 1$.
+We compute the estimator $\widehat A^\epl_k(T)$ with final time $T = 10^3$ on $2000$ realizations of the solution and estimate the quantity
+\begin{equation}	
+	\Delta_A^\epl(T) \defeq \sqrt{T}\left(\widehat A^\epl_k(T) - A\right),	
+\end{equation}
+where $A$ is the drift coefficient of the homogenized equation.
+Results, depicted in Figure \ref{fig:CLT}, show that the distribution of $\Delta_A^\epl(T)$ indeed follows a zero-mean Gaussian law, \corr{whose covariance agrees with the theoretical results (?)}.
+
 \subsection{Multi-dimensional drift coefficient}
@@
 
-\subsection{Central limit theorem}
-\begin{figure}[t]
-	\centering
-	\includegraphics[]{Figures/CLT}
-	\caption{Central limit theorem result.
-The histogram represents numerical results, the solid curve a Gaussian fit to the latter and the dashed curve $\rho_a$ represents the theoretical estimate given in Theorem \ref{thm:CLT}.}
-	\label{fig:CLT}
-\end{figure}
-
 \subsection{The Bayesian approach: bistable potential}
@@
 	\end{equation}
-	which spans $T_x\R^2$. The desired result then follows from Hörmander's theorem (see e.g. \cite[Chapter 6]{Pav14}).
+	which spans the tangent space of $\R^2$ at $(x, z)$, denoted $T_{x, z}\R^2$. The desired result then follows from Hörmander's theorem (see e.g. \cite[Chapter 6]{Pav14}).
 \end{proof}
@@
 
+\section{Proof of Theorem \ref{thm:CLT}}\label{ap:CLT}
+
+Let us first introduce a technical Lemma.
+\begin{lemma}\label{lem:CLT} Let $\mathcal L_\epl$ be the generator of the couple $(X^\epl, Z^\epl)^\top$, i.e.,
+	\begin{equation}
+		\mathcal L_\epl = -\left(\alpha \cdot V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)\partial_x + \frac1\delta (x - z) \partial_z  + \sigma \partial^2_{xx}.
+	\end{equation} 
+	Moreover, let $\rho^\epl$ be the invariant measure of $(X^\epl, Z^\epl)^\top$ and $\Phi^\epl\colon \R^2 \to \R^N$ be the solution of 
+	\begin{equation}\label{eq:CLT_Poisson}
+		-\mathcal L_\epl \Phi^\epl = \chi -  \E^{\rho^\epl}[\chi],
+	\end{equation}
+	for $\chi \colon \R^2 \to \R^N$ satisfying $\E^{\rho^\epl}[\Phi^\epl] = 0$. Then, it holds
+	\begin{equation}\label{eq:CLT_PoissonIto}
+		\frac{1}{T} \int_0^T  \chi(X_t^\epl, Z_t^\epl) \dd t = \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)] - \frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T},
+	\end{equation}
+	where
+	\begin{equation}\label{eq:CLT_PoissonRemainders}
+		R^\epl(T) \defeq \Phi^\epl(X^\epl_T, Z^\epl_T) - \Phi^\epl(X^\epl_0, Z^\epl_0), \quad S^\epl(T) \defeq \int_0^T \partial_x \Phi^\epl(X_t^\epl, Z_t^\epl) \dd W_t.
+	\end{equation}
+	Moreover, it holds
+	\begin{equation}\label{eq:CLT_Equiv}
+		2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl \otimes \partial_x \Phi^\epl] = \E^{\rho^\epl}[\chi \otimes \Phi^\epl + \Phi^\epl \otimes \chi].
+	\end{equation}	
+\end{lemma}
+\begin{proof} The proof of \eqref{eq:CLT_PoissonIto} and \eqref{eq:CLT_PoissonRemainders} is an application of the Itô formula (see e.g.
+\cite[Remark 6.17]{PaS08}).
+For \eqref{eq:CLT_Equiv}, it is possible to show that since $\mathcal L_\epl^*\rho^\epl = 0$ it holds
+	\begin{equation}
+		\mathcal L_\epl^* (\Phi^\epl \rho) = 2 \sigma \rho^\epl \partial_{xx}^2 \Phi^\epl - \rho^\epl \mathcal L_\epl\Phi^\epl + 2 \sigma \partial_x \Phi^\epl \partial_x \rho^\epl.
+	\end{equation}
+	Therefore, an integration by parts yields 
+	\begin{equation}
+	\begin{aligned}
+		\E^{\rho^\epl}[\mathcal L_\epl \Phi^\epl \otimes \Phi^\epl] &= 	\int_{\R}\int_{\R} \Phi^\epl \otimes \mathcal L_\epl^*\left(\Phi^\epl \rho^\epl\right) \dd x \dd z \\
+		&= -\int_{\R}\int_{\R}\Phi^\epl \otimes \mathcal L_\epl \Phi^\epl \rho^\epl \dd x \dd z- 2\sigma \int_{\R}\int_{\R} \partial_x \Phi^\epl \otimes \partial_x \Phi^\epl \rho^\epl \dd x \dd z\\
+		&= -\E^{\rho^\epl}[\Phi^\epl \otimes \mathcal L_\epl \Phi^\epl] - 2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl \otimes \partial_x \Phi^\epl]. 
+	\end{aligned}
+	\end{equation}
+	Finally, since $\E^{\rho^\epl}[\Phi] = 0$ 
+	\begin{equation}
+	\begin{aligned}
+		2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl \otimes \partial_x \Phi^\epl] &= -\E^{\rho^\epl}[\mathcal L_\epl \Phi^\epl \otimes \Phi^\epl + \Phi^\epl \otimes \mathcal L_\epl \Phi^\epl]\\
+		&= \E^{\rho^\epl}[\chi \otimes \Phi^\epl + \Phi^\epl \otimes \chi],
+	\end{aligned}
+	\end{equation}
+	which is the desired result.
+\end{proof}
+
+We can now proceed with the main proof.
+\begin{proof}[Proof of Theorem \ref{thm:CLT}] Let us introduce the notation
+	\begin{equation}\label{eq:CLT_DefMEps}
+	\mathcal M_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ], \quad \mathcal M_0 \defeq \E^{\rho^0} [ V'(Z) \otimes V'(X) ],
+	\end{equation}
+	and the notation
+	\begin{equation}
+	\mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ]\
+	\end{equation}
+	and let us remark that from the proof of Theorem \ref{thm:mainTheorem} one can deduce the equalities
+	\begin{equation}\label{eq:CTL_A}
+	A = \frac1\delta \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)],
+	\end{equation}
+	and
+	\begin{equation}\label{eq:CTL_alpha}
+	\alpha = \mathcal M_\epl^{-1} \left(\frac1\delta \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathfrak p_\epl \right).
+	\end{equation}
+	Let us furthermore remark that the decomposition \eqref{eq:alphaDecomposition} yields
+	\begin{equation}
+	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \sqrt{T} \left(\alpha - A + I_1^\epl - I_2^\epl\right).
+	\end{equation}
+	Replacing the expression for $A$ and $\alpha$ given in \eqref{eq:CTL_A} and \eqref{eq:CTL_alpha}, we get
+	\begin{equation}
+	\begin{aligned}
+	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) &= \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \\
+	&+  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
+	&- \sqrt{T} I_2^\epl(T).
+	\end{aligned}
+	\end{equation}
+	\corr{Third term is OK:} We rewrite the term involving $I_2^\epl(T)$ as
+	\begin{equation}
+	\sqrt{T} I_2^\epl(T) = \frac{\sqrt{2\sigma}}{\sqrt{T}} \widetilde M^{-1} Q^\epl(T),
+	\end{equation}
+	where, since $Z_t^\epl$ is adapted with respect to the natural filtration $\mathcal F_t$ of the Wiener process $W \defeq \left(W_t, t \geq 0\right)$, the quantity
+	\begin{equation}
+	Q^\epl(T) \defeq \int_0^T V'(Z^\epl_t) \dd W_t,
+	\end{equation}
+	is a martingale whose quadratic variation is given by
+	\begin{equation}
+	\langle Q^\epl \rangle_T = \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t. 
+	\end{equation}
+	Since the ergodic theorem guarantees that 
+	\begin{equation}
+	\lim_{T\to\infty}\frac{\langle Q^\epl \rangle_T}{T} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)], \quad \text{in } L^1(\mu^\epl),
+	\end{equation}
+	the martingale central limit theorem gives 
+	\begin{equation}
+	\lim_{T\to\infty}\frac{1}{\sqrt{T}} Q^\epl(T) = \Xi^\epl, \quad \text{in law},
+	\end{equation}
+	where $\Xi^\epl \sim \mathcal N(0, \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)])$.
+	Now, by the ergodic theorem 
+	\begin{equation}
+	\lim_{T \to \infty} \widetilde M^{-1} = \mathcal M_\epl^{-1}, \quad \text{a.s.}
+	\end{equation}
+	Therefore, we have by Slutsky's theorem that
+	\begin{equation}
+	\lim_{T \to \infty} \sqrt{T} I_2^\epl(T) = \Lambda^\epl \sim \mathcal N\left(0, \Gamma^\epl\right), \quad \text{in law}.
+	\end{equation}
+	where the covariance matrix $\Gamma^\epl$ is given by
+	\begin{equation}
+	\Gamma^\epl = 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)]\mathcal M_\epl^{-\top}.
+	\end{equation}
+	Finally, we denote by $\Lambda$ the limit for $\epl \to 0$ of the sequence of Gaussian random variables $\Lambda^\epl$.
+
+	\corr{Idea for the first term:} Let us introduce the notation
+	\begin{equation}
+	J_1^\epl(T) \defeq \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl\right),
+	\end{equation}
+	and let us remark that we can rewrite
+	\begin{equation} \label{eq:decomposition_first_term}
+	\begin{aligned}
+	J_1^\epl(T) &= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\left(\frac1T \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t - \mathfrak p_\epl \right) \\
+	& \quad + \sqrt{T} \left(\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} - \mathcal M_\epl^{-1}\right) \mathfrak p_\epl\\
+	&\eqdef J_{1,1}^\epl(T) + J_{1,2}^\epl(T).
+	\end{aligned}
+	\end{equation}
+	Let us denote by $\Phi_1^\epl$ the solution of \eqref{eq:CLT_Poisson} in Lemma \ref{lem:CLT} with right hand side
+	\begin{equation}
+	\chi_1(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z).
+	\end{equation}
+	Then, denoting as $R_1^\epl(T)$ and $S_1^\epl(T)$ the quantities introduced in \eqref{eq:CLT_PoissonRemainders} with $\Phi_1^\epl$ in place of $\Phi^\epl$, we have
+	\begin{equation}
+	J_{1,1}^\epl(T)= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( -\frac{R_1^\epl(T)}{T} + \sqrt{2\sigma}\frac{S_1^\epl(T)}{T} \right).
+	\end{equation}
+	Since \corr{$R_1^\epl(T)$ is bounded independently of $\epl$ (is it clear?)}, we first get by the ergodic theorem
+	\begin{equation}
+	\lim_{T \to \infty} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{R_1^\epl(T)}{\sqrt{T}} = 0, \quad \text{a.s.}
+	\end{equation}
+	Repeating the same reasoning as for $Q^\epl(T)$ and employing the ergodic theorem, we get 
+	\begin{equation}
+	\lim_{T \to \infty} J_{1,1}^\epl(T) = \lim_{T \to \infty} \sqrt{2\sigma} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{S^\epl_1(T)}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
+	\end{equation}
+	where the covariance is given by due to \eqref{eq:CLT_Equiv}
+	\begin{equation}
+	\begin{aligned}
+	\Gamma_1^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x \Phi_1^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_1^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
+	&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[\Phi_1^\epl(X^\epl, Z^\epl) \otimes \chi_1(X^\epl, Z^\epl) + \chi_1(X^\epl, Z^\epl) \otimes \Phi_1^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
+	\end{aligned}
+	\end{equation}
+	Let us now consider the term $J_{1,2}^\epl(T)$ and rewrite it as
+	\begin{equation}
+	J_{1,2}^\epl(T) =  \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\left(\mathfrak p_\epl - \frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \mathcal M_\epl^{-1} \mathfrak p_\epl  \dd t\right).
+	\end{equation}	
+	Let now us denote by $\Phi_2^\epl$ the solution of \eqref{eq:CLT_Poisson} in Lemma \ref{lem:CLT} with right hand side
+	\begin{equation}
+	\chi_2(x, z) = V'(z) \otimes V'(x) \mathcal M_\epl^{-1} \mathfrak p_\epl.
+	\end{equation}
+	Applying \eqref{eq:CLT_PoissonIto} and by the definition \eqref{eq:CLT_DefMEps} of $\mathcal M_\epl$, we get
+	\begin{equation}
+	\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \mathcal M_\epl^{-1} \mathfrak p_\epl \dd t =  \mathfrak p_\epl - \frac{R_2^\epl(T)}{T} + \sqrt{2\sigma}\frac{S_2^\epl(T)}{T},
+	\end{equation}
+	where $R_2^\epl(T)$ and $S_2^\epl(T)$ are the quantities introduced in \eqref{eq:CLT_PoissonRemainders} with $\Phi_2^\epl$ in place of $\Phi^\epl$. Therefore, 
+	\begin{equation}
+	J_{1,2}^\epl(T) =  \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\left(\frac{R_2^\epl(T)}{T} - \sqrt{2\sigma}\frac{S_2^\epl(T)}{T}\right).
+	\end{equation}
+	Repeating the same reasoning as for $R_1^\epl(T)$ and $S_1^\epl(T)$ and applying the ergodic theorem, we get
+	\begin{equation}
+	\lim_{T \to \infty} J_{1,2}^\epl(T) = \Lambda_2^\epl \sim \mathcal N(0, \Gamma_2^\epl),
+	\end{equation}
+	where the covariance is given by due to \eqref{eq:CLT_Equiv}
+	\begin{equation}
+	\begin{aligned}
+		\Gamma_2^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x \Phi_2^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_2^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
+		&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[\Phi_2^\epl(X^\epl, Z^\epl) \otimes \chi_2(X^\epl, Z^\epl) + \chi_2(X^\epl, Z^\epl) \otimes \Phi_2^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
+	\end{aligned}
+	\end{equation}
+	\corr{For the covariances $\Gamma_1^\epl$ and $\Gamma_2^\epl$ we don't know how they behave in the limit $\epl \to 0$.
+It would be nice if they were vanishing, but they involve the solutions $\Phi_1^\epl$ and $\Phi_2^\epl$, which have r.h.s.
+depending of $\epl$ (especially $\Phi_1$).}
+
+	\corr{Idea for the second term:} Let us now introduce the notation
+	\begin{equation}
+		J_2^\epl(T) = \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right).
+	\end{equation}
+	We have the decomposition
+	\begin{equation}
+	\begin{aligned}
+	J^\epl_{2}(T) &=  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1}  - \mathcal M_0^{-1} \right)\E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \\
+	&\quad + \frac{\sqrt{T}}\delta \mathcal M_0^{-1}\left(\E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
+	&\eqdef J_{2,1}^\epl(T) + J_{2,2}^\epl(T).
+	\end{aligned}
+	\end{equation}
+	\corr{In order to send the terms above to zero, we need the convergence rate of $\mu^\epl$ to $\mu^0$ w.r.t.
+$\epl$ (by fixing $T = \epl^{-\gamma}$ with an appropriate $\gamma$).
+Some arguments in this sense seem to appear in [\textit{Periodic Homogenization for Hypoelliptic Diffusions} -- M.
+Hairer and G.A.
+Pavliotis 2004] but it is not clear to us whether it applies to this case too.}
+\end{proof}
+
 \section{Proof of Theorem \ref{thm:mainTheoremTilde}}\label{ap:EstimatorTilde}
@@
 \end{proof}
+
 \end{appendices}

### 2020-03-09 CalNotes.tex
Typo missing X,Z
update CLT with only one Poisson problem

@@
 	\begin{equation}\label{eq:CLT_Poisson}
-		-\mathcal L_\epl \Phi^\epl = \chi -  \E^{\rho^\epl}[\chi],
-	\end{equation}
-	for $\chi \colon \R^2 \to \R^N$ satisfying $\E^{\rho^\epl}[\Phi^\epl] = 0$. Then, it holds
+		-\mathcal L_\epl \Phi^\epl = \chi^\epl -  \E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)],
+	\end{equation}
+	for $\chi^\epl \colon \R^2 \to \R^N$ satisfying $\E^{\rho^\epl}[\Phi^\epl(X^\epl, Z^\epl)] = 0$. Then, it holds
 	\begin{equation}\label{eq:CLT_PoissonIto}
-		\frac{1}{T} \int_0^T  \chi(X_t^\epl, Z_t^\epl) \dd t = \E^{\rho^\epl}[\chi(X^\epl, Z^\epl)] - \frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T},
+		\frac{1}{T} \int_0^T  \chi^\epl(X_t^\epl, Z_t^\epl) \dd t = \E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)] - \frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T},
 	\end{equation}
@@
 	\begin{equation}\label{eq:CLT_Equiv}
-		2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl \otimes \partial_x \Phi^\epl] = \E^{\rho^\epl}[\chi \otimes \Phi^\epl + \Phi^\epl \otimes \chi].
+		2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)] = \E^{\rho^\epl}
+		\begin{aligned}[t]
+		[&\chi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl) \\
+		&+ \Phi^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)].
+		\end{aligned}
 	\end{equation}	
@@
 	\begin{equation}
-		\mathcal L_\epl^* (\Phi^\epl \rho) = 2 \sigma \rho^\epl \partial_{xx}^2 \Phi^\epl - \rho^\epl \mathcal L_\epl\Phi^\epl + 2 \sigma \partial_x \Phi^\epl \partial_x \rho^\epl.
+		\mathcal L_\epl^* (\Phi^\epl \rho^\epl) = 2 \sigma \rho^\epl \partial_{xx}^2 \Phi^\epl - \rho^\epl \mathcal L_\epl\Phi^\epl + 2 \sigma \partial_x \Phi^\epl \partial_x \rho^\epl.
 	\end{equation}
@@
 	\begin{aligned}
-		\E^{\rho^\epl}[\mathcal L_\epl \Phi^\epl \otimes \Phi^\epl] &= 	\int_{\R}\int_{\R} \Phi^\epl \otimes \mathcal L_\epl^*\left(\Phi^\epl \rho^\epl\right) \dd x \dd z \\
+		\E^{\rho^\epl}[\mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl)] &= 	\int_{\R}\int_{\R} \Phi^\epl \otimes \mathcal L_\epl^*\left(\Phi^\epl \rho^\epl\right) \dd x \dd z \\
 		&= -\int_{\R}\int_{\R}\Phi^\epl \otimes \mathcal L_\epl \Phi^\epl \rho^\epl \dd x \dd z- 2\sigma \int_{\R}\int_{\R} \partial_x \Phi^\epl \otimes \partial_x \Phi^\epl \rho^\epl \dd x \dd z\\
-		&= -\E^{\rho^\epl}[\Phi^\epl \otimes \mathcal L_\epl \Phi^\epl] - 2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl \otimes \partial_x \Phi^\epl]. 
-	\end{aligned}
-	\end{equation}
-	Finally, since $\E^{\rho^\epl}[\Phi] = 0$ 
-	\begin{equation}
-	\begin{aligned}
-		2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl \otimes \partial_x \Phi^\epl] &= -\E^{\rho^\epl}[\mathcal L_\epl \Phi^\epl \otimes \Phi^\epl + \Phi^\epl \otimes \mathcal L_\epl \Phi^\epl]\\
-		&= \E^{\rho^\epl}[\chi \otimes \Phi^\epl + \Phi^\epl \otimes \chi],
+		&= 
+		\begin{aligned}[t]
+		&-\E^{\rho^\epl}[\Phi^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl)] \\
+		&- 2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)].
+		\end{aligned}
+	\end{aligned}
+	\end{equation}
+	Finally, since $\E^{\rho^\epl}[\Phi(X^\epl, Z^\epl)] = 0$ 
+	\begin{equation}
+	\begin{aligned}
+		2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)] &= -\E^{\rho^\epl}
+		\begin{aligned}[t]
+		[&\mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl) \\
+		& + \Phi^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl)]
+		\end{aligned}
+		\\
+		&= \E^{\rho^\epl}
+		\begin{aligned}[t]
+		[&\chi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl) \\
+		&+ \Phi^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)],
+		\end{aligned}
 	\end{aligned}
@@
 	\begin{aligned}
-	J_1^\epl(T) &= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\left(\frac1T \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t - \mathfrak p_\epl \right) \\
-	& \quad + \sqrt{T} \left(\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} - \mathcal M_\epl^{-1}\right) \mathfrak p_\epl\\
-	&\eqdef J_{1,1}^\epl(T) + J_{1,2}^\epl(T).
-	\end{aligned}
-	\end{equation}
-	Let us denote by $\Phi_1^\epl$ the solution of \eqref{eq:CLT_Poisson} in Lemma \ref{lem:CLT} with right hand side
-	\begin{equation}
-	\chi_1(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z).
-	\end{equation}
-	Then, denoting as $R_1^\epl(T)$ and $S_1^\epl(T)$ the quantities introduced in \eqref{eq:CLT_PoissonRemainders} with $\Phi_1^\epl$ in place of $\Phi^\epl$, we have
-	\begin{equation}
-	J_{1,1}^\epl(T)= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( -\frac{R_1^\epl(T)}{T} + \sqrt{2\sigma}\frac{S_1^\epl(T)}{T} \right).
-	\end{equation}
-	Since \corr{$R_1^\epl(T)$ is bounded independently of $\epl$ (is it clear?)}, we first get by the ergodic theorem
-	\begin{equation}
-	\lim_{T \to \infty} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{R_1^\epl(T)}{\sqrt{T}} = 0, \quad \text{a.s.}
-	\end{equation}
-	Repeating the same reasoning as for $Q^\epl(T)$ and employing the ergodic theorem, we get 
-	\begin{equation}
-	\lim_{T \to \infty} J_{1,1}^\epl(T) = \lim_{T \to \infty} \sqrt{2\sigma} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{S^\epl_1(T)}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
+	J_1^\epl(T) = \sqrt{T} &\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\\
+		&\quad \times \left(\frac1T \int_0^T \left( \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t)	- V'(Z^\epl_t) \otimes V'(X^\epl_t) \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \dd t	 \right).
+	\end{aligned}
+	\end{equation}
+	Let us denote by $\Phi^\epl$ the solution of \eqref{eq:CLT_Poisson} in Lemma \ref{lem:CLT} with right hand side
+	\begin{equation}
+	\chi^\epl(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z) - V'(z) \otimes V'(x) \mathcal M_\epl^{-1} \mathfrak p_\epl,
+	\end{equation}
+	and note that $\E^{\rho^\epl}[\chi^\epl(X^\epl,Z^\epl)] = 0$. Then we have
+	\begin{equation}
+	J_1^\epl(T)= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( -\frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T} \right),
+	\end{equation}
+	where $R^\epl(T)$ and $S^\epl(T)$ are defined in \eqref{eq:CLT_PoissonRemainders}. Since \corr{$R^\epl(T)$ is bounded independently of $\epl$ (is it clear?)}, we first get by the ergodic theorem
+	\begin{equation}
+	\lim_{T \to \infty} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{R^\epl(T)}{\sqrt{T}} = 0, \quad \text{a.s.}
+	\end{equation}
+	Repeating the same reasoning as for $Q^\epl(T)$ and employing the ergodic theorem and the Slutsky's theorem, we get 
+	\begin{equation}
+	\lim_{T \to \infty} J_1^\epl(T) = \lim_{T \to \infty} \sqrt{2\sigma} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{S^\epl(T)}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
 	\end{equation}
@@
 	\begin{aligned}
-	\Gamma_1^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x \Phi_1^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_1^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
-	&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[\Phi_1^\epl(X^\epl, Z^\epl) \otimes \chi_1(X^\epl, Z^\epl) + \chi_1(X^\epl, Z^\epl) \otimes \Phi_1^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
-	\end{aligned}
-	\end{equation}
-	Let us now consider the term $J_{1,2}^\epl(T)$ and rewrite it as
-	\begin{equation}
-	J_{1,2}^\epl(T) =  \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\left(\mathfrak p_\epl - \frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \mathcal M_\epl^{-1} \mathfrak p_\epl  \dd t\right).
-	\end{equation}	
-	Let now us denote by $\Phi_2^\epl$ the solution of \eqref{eq:CLT_Poisson} in Lemma \ref{lem:CLT} with right hand side
-	\begin{equation}
-	\chi_2(x, z) = V'(z) \otimes V'(x) \mathcal M_\epl^{-1} \mathfrak p_\epl.
-	\end{equation}
-	Applying \eqref{eq:CLT_PoissonIto} and by the definition \eqref{eq:CLT_DefMEps} of $\mathcal M_\epl$, we get
-	\begin{equation}
-	\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \mathcal M_\epl^{-1} \mathfrak p_\epl \dd t =  \mathfrak p_\epl - \frac{R_2^\epl(T)}{T} + \sqrt{2\sigma}\frac{S_2^\epl(T)}{T},
-	\end{equation}
-	where $R_2^\epl(T)$ and $S_2^\epl(T)$ are the quantities introduced in \eqref{eq:CLT_PoissonRemainders} with $\Phi_2^\epl$ in place of $\Phi^\epl$. Therefore, 
-	\begin{equation}
-	J_{1,2}^\epl(T) =  \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\left(\frac{R_2^\epl(T)}{T} - \sqrt{2\sigma}\frac{S_2^\epl(T)}{T}\right).
-	\end{equation}
-	Repeating the same reasoning as for $R_1^\epl(T)$ and $S_1^\epl(T)$ and applying the ergodic theorem, we get
-	\begin{equation}
-	\lim_{T \to \infty} J_{1,2}^\epl(T) = \Lambda_2^\epl \sim \mathcal N(0, \Gamma_2^\epl),
-	\end{equation}
-	where the covariance is given by due to \eqref{eq:CLT_Equiv}
-	\begin{equation}
-	\begin{aligned}
-		\Gamma_2^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x \Phi_2^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi_2^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
-		&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[\Phi_2^\epl(X^\epl, Z^\epl) \otimes \chi_2(X^\epl, Z^\epl) + \chi_2(X^\epl, Z^\epl) \otimes \Phi_2^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
-	\end{aligned}
-	\end{equation}
-	\corr{For the covariances $\Gamma_1^\epl$ and $\Gamma_2^\epl$ we don't know how they behave in the limit $\epl \to 0$.
-It would be nice if they were vanishing, but they involve the solutions $\Phi_1^\epl$ and $\Phi_2^\epl$, which have r.h.s.
-depending of $\epl$ (especially $\Phi_1$).}
+	\Gamma_1^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
+	&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[\Phi^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl) + \chi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
+	\end{aligned}
+	\end{equation}
+	\corr{For the covariance $\Gamma_1^\epl$ we don't know how it behaves in the limit $\epl \to 0$.
+It would be nice if it was vanishing, but it involves the solution $\Phi^\epl$, which has r.h.s.
+depending of $\epl$.
+We noticed that the homogenized problem of
+	\begin{equation}
+		-\mathcal L_\epl \Phi^\epl = \chi^\epl,
+	\end{equation}
+	is given by
+	\begin{equation}
+		-\mathcal L_0 \Phi^0 = 0,
+	\end{equation}
+	whose zero-mean solution is $\Phi^0 = 0$.}
 

### 2020-03-10 CalNotes.tex
CLT Poisson Homogenization2

@@
 and where the function $\Phi$ is the unique solution with zero-mean with respect to the measure $\mu$ of the elliptic partial differential equation
-\begin{equation}
+\begin{equation}\label{eq:CellProblem}
 	-p'(y)\Phi'(y) + \sigma \Phi''(y) = p'(y), \quad 0 \leq y \leq L,
@@
 	\end{equation} 
-	Moreover, let $\rho^\epl$ be the invariant measure of $(X^\epl, Z^\epl)^\top$ and $\Phi^\epl\colon \R^2 \to \R^N$ be the solution of 
+	Moreover, let $\rho^\epl$ be the density of the invariant measure of $(X^\epl, Z^\epl)^\top$ and $u^\epl\colon \R^2 \to \R^N$ be the solution of 
 	\begin{equation}\label{eq:CLT_Poisson}
-		-\mathcal L_\epl \Phi^\epl = \chi^\epl -  \E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)],
-	\end{equation}
-	for $\chi^\epl \colon \R^2 \to \R^N$ satisfying $\E^{\rho^\epl}[\Phi^\epl(X^\epl, Z^\epl)] = 0$. Then, it holds
+		-\mathcal L_\epl u^\epl = \chi^\epl -  \E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)],
+	\end{equation}
+	satisfying $\E^{\rho^\epl}[u^\epl(X^\epl, Z^\epl)] = 0$ for $\chi^\epl \colon \R^2 \to \R^N$. Then, it holds
 	\begin{equation}\label{eq:CLT_PoissonIto}
@@
 	\begin{equation}\label{eq:CLT_PoissonRemainders}
-		R^\epl(T) \defeq \Phi^\epl(X^\epl_T, Z^\epl_T) - \Phi^\epl(X^\epl_0, Z^\epl_0), \quad S^\epl(T) \defeq \int_0^T \partial_x \Phi^\epl(X_t^\epl, Z_t^\epl) \dd W_t.
+		R^\epl(T) \defeq u^\epl(X^\epl_T, Z^\epl_T) - u^\epl(X^\epl_0, Z^\epl_0), \quad S^\epl(T) \defeq \int_0^T \partial_x u^\epl(X_t^\epl, Z_t^\epl) \dd W_t.
 	\end{equation}
@@
 	\begin{equation}\label{eq:CLT_Equiv}
-		2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)] = \E^{\rho^\epl}
+		2\sigma \E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)] = \E^{\rho^\epl}
 		\begin{aligned}[t]
-		[&\chi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl) \\
-		&+ \Phi^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)].
+		[&\chi^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl) \\
+		&+ u^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)].
 		\end{aligned}
@@
 	\begin{equation}
-		\mathcal L_\epl^* (\Phi^\epl \rho^\epl) = 2 \sigma \rho^\epl \partial_{xx}^2 \Phi^\epl - \rho^\epl \mathcal L_\epl\Phi^\epl + 2 \sigma \partial_x \Phi^\epl \partial_x \rho^\epl.
+		\mathcal L_\epl^* (u^\epl \rho^\epl) = 2 \sigma \rho^\epl \partial_{xx}^2 u^\epl - \rho^\epl \mathcal L_\epl u^\epl + 2 \sigma \partial_x u^\epl \partial_x \rho^\epl.
 	\end{equation}
@@
 	\begin{aligned}
-		\E^{\rho^\epl}[\mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl)] &= 	\int_{\R}\int_{\R} \Phi^\epl \otimes \mathcal L_\epl^*\left(\Phi^\epl \rho^\epl\right) \dd x \dd z \\
-		&= -\int_{\R}\int_{\R}\Phi^\epl \otimes \mathcal L_\epl \Phi^\epl \rho^\epl \dd x \dd z- 2\sigma \int_{\R}\int_{\R} \partial_x \Phi^\epl \otimes \partial_x \Phi^\epl \rho^\epl \dd x \dd z\\
+		\E^{\rho^\epl}[\mathcal L_\epl u^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl)] &= 	\int_{\R}\int_{\R} u^\epl \otimes \mathcal L_\epl^*\left(u^\epl \rho^\epl\right) \dd x \dd z \\
+		&= -\int_{\R}\int_{\R}u^\epl \otimes \mathcal L_\epl u^\epl \rho^\epl \dd x \dd z- 2\sigma \int_{\R}\int_{\R} \partial_x u^\epl \otimes \partial_x u^\epl \rho^\epl \dd x \dd z\\
 		&= 
 		\begin{aligned}[t]
-		&-\E^{\rho^\epl}[\Phi^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl)] \\
-		&- 2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)].
-		\end{aligned}
-	\end{aligned}
-	\end{equation}
-	Finally, since $\E^{\rho^\epl}[\Phi(X^\epl, Z^\epl)] = 0$ 
-	\begin{equation}
-	\begin{aligned}
-		2\sigma \E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)] &= -\E^{\rho^\epl}
+		&-\E^{\rho^\epl}[u^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl u^\epl(X^\epl, Z^\epl)] \\
+		&- 2\sigma \E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)].
+		\end{aligned}
+	\end{aligned}
+	\end{equation}
+	Finally, since $\E^{\rho^\epl}[u(X^\epl, Z^\epl)] = 0$ 
+	\begin{equation}
+	\begin{aligned}
+		2\sigma \E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)] &= -\E^{\rho^\epl}
 		\begin{aligned}[t]
-		[&\mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl) \\
-		& + \Phi^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl \Phi^\epl(X^\epl, Z^\epl)]
+		[&\mathcal L_\epl u^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl) \\
+		& + u^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl u^\epl(X^\epl, Z^\epl)]
 		\end{aligned}
@@
 		\begin{aligned}[t]
-		[&\chi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl) \\
-		&+ \Phi^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)],
+		[&\chi^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl) \\
+		&+ u^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)],
 		\end{aligned}
@@
 	which is the desired result.
+\end{proof}
+
+\begin{lemma} Let $u^\epl$ be the solution of \eqref{eq:CLT_Poisson} with 
+	\begin{equation}
+		\chi^\epl(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z) - V'(z) \otimes V'(x) \mathcal M_\epl^{-1} \mathfrak p_\epl,
+	\end{equation}
+	where
+	\begin{equation}
+		\mathcal M_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ], \quad \mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ].
+	\end{equation}
+	Then, $u^\epl \to 0$ \corr{in which sense?} for $\epl \to 0$.
+\end{lemma}
+\begin{proof} We here present a formal proof based on asymptotic expansion with respect to $\epl$. Let us first remark that by definition
+	\begin{equation}
+		\E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)] = 0,
+	\end{equation}
+	and therefore problem \eqref{eq:CLT_Poisson} reads
+	\begin{equation}
+		-\mathcal L^\epl u^\epl = \chi^\epl.
+	\end{equation}
+	Let us now denote $y = x/\epl$ and write
+	\begin{equation}
+		u^\epl(x, z) = u_0(x, y, z) + \epl u_1(x, y, z) + \epl^2 u_2(x, y, z) + \ldots,
+	\end{equation}
+	which implies that
+	\begin{equation}
+	\begin{aligned}
+		\partial_x u^\epl &= \partial_x(u_0(x, y, z) + \epl u_1(x, y, z) + \epl^2 u_2(x, y, z) + \ldots) \\
+		&\quad+ \frac1\epl\partial_y(u_0(x, y, z) + \epl u_1(x, y, z) + \epl^2 u_2(x, y, z) + \ldots).
+	\end{aligned}
+	\end{equation}
+	Let us first remark that from the proof of Theorem \ref{thm:mainTheorem} we have that
+	\begin{equation}
+		\lim_{\epl \to 0} \mathcal M_\epl^{-1}\mathfrak p_\epl = A - \alpha.
+	\end{equation} 	
+	Replacing $u^\epl$ in \eqref{eq:CLT_Poisson} and grouping the terms of order $\epl^0$, $\epl^{-1}$ and $\epl^{-2}$ we get the system
+	\begin{align}
+		L_0 u_0 &= 0, \label{eq:CLT_AsExp1}\\
+		L_1 u_0 + L_0 u_1 &= - p'(y) V'(z), \label{eq:CLT_AsExp2}\\
+		L_0 u_2 + L_1 u_1 + L_2 u_0 &= \left(V'(z) \otimes V'(x)\right) (A - \alpha),\label{eq:CLT_AsExp3}
+	\end{align}
+	where 
+	\begin{equation}
+	\begin{aligned}
+		L_0 &= -p'(y) \partial_y + \sigma \partial^2_{yy},\\
+		L_1 &= -p'(y) \partial_x - \alpha \cdot V'(x) \partial_y + 2 \sigma \partial^2_{xy}, \\
+		L_2 &= 	-\alpha \cdot V'(x) \partial_x - \frac1{\delta}(z - x)	\partial_z + \sigma \partial^2_{xx}.
+	\end{aligned}
+	\end{equation}
+	Let us first remark that equation \eqref{eq:CLT_AsExp1} is satisfied for $u_0 = u_0(x, z)$ independent of $y$.
+In particular, the kernel of $L_0$ is made of constants and the kernel of $L_0^*$ is one-dimensional and $\mathrm{Ker}(L_0^*) = \mathrm{Span}\{\rho\}$ where
+	\begin{equation}\label{eq:CLT_Invariant}
+		\rho(y) = \frac1Z e^{-p(y)/\sigma}, \quad\text{where}\quad Z = \int_0^L e^{-p(y)/\sigma} \dd y,
+	\end{equation} 
+	where $L$ is the period of $p$. Since $u_0$ is independent of $y$ equation \eqref{eq:CLT_AsExp2} reduces to 
+	\begin{equation}
+		L_0 u_1 = p'(y)\left(\partial_x u_0 -V'(z)\right).
+	\end{equation}
+	Let us remark that the general solution $u_1$ can be written as
+	\begin{equation}
+		u_1(x,y,z) = \Phi(y)\left(\partial_x u_0(x, z) - V'(z)\right),
+	\end{equation}
+	where $\Phi \colon \R \to \R$ satisfies
+	\begin{equation}
+		-L_0 \Phi = -p'(y).
+	\end{equation} 
+	Let us remark that this cell problem is the same as \eqref{eq:CellProblem}. We consider now equation \eqref{eq:CLT_AsExp3} and remark that we can rewrite it as
+	\begin{equation}
+	\begin{aligned}
+		L_0 u_2 &= (V'(z) \otimes V'(x))(A - \alpha) - \left(2\Phi'(y) - \frac1\sigma p'(y) \Phi(y) + 1\right) \sigma \partial^2_{xx}u_0 \\
+		&\quad +\left(\Phi'(y) + 1\right) \left( \alpha \cdot V'(x) \right) \partial_x u_0 - \left(V'(z) \otimes V'(x) \right)\alpha \Phi'(y) + \frac1\delta(z-x) \partial_z u_0.
+	\end{aligned}
+	\end{equation}
+	By the Fredholm alternative, in order for \eqref{eq:CLT_AsExp3} to have a solution we need the right hand side to have zero-mean with respect to $\rho$ in \eqref{eq:CLT_Invariant}.
+Therefore, recalling that the homogenization coefficient $K$ in \eqref{eq:K_HOM} is given by
+	\begin{equation}
+		K = \int_0^L (1 + \Phi'(y))^2 \rho(y) \dd y
+	\end{equation}
+	and remarking that integrations by part allow to rewrite $K$ as
+	\begin{equation}
+		K = \int_0^L (1 + \Phi'(y)) \rho(y) \dd y, \quad  K = \int_0^L \left(2\Phi'(y) - \frac1\sigma p'(y) \Phi(y) + 1\right) \rho(y) \dd y,
+	\end{equation}
+	we get
+	\begin{equation}
+		0 = (V'(z) \otimes V'(x))(A - \alpha - (K - 1)\alpha) - K \sigma \partial^2_{xx}u_0 + \left(K \alpha \cdot V'(x)\right) \partial_x u_0  + \frac1\delta(z-x) \partial_z u_0,
+	\end{equation}
+	which, since $A = K\alpha$ and $\Sigma = K\sigma$, implies
+	\begin{equation}
+		0 = -\Sigma \partial^2_{xx}u_0 + \left(A \cdot V'(x)\right) \partial_x u_0  + \frac1\delta(z-x) \partial_z u_0,
+	\end{equation}
 \end{proof}
@@
 	\begin{equation}
-	\mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ]\
+	\mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ]
 	\end{equation}
@@
 	\end{equation}
-	Let us denote by $\Phi^\epl$ the solution of \eqref{eq:CLT_Poisson} in Lemma \ref{lem:CLT} with right hand side
+	Let us denote by $\Phi^\epl$ the solution of \eqref{eq:CLT_Poisson} with right hand side
 	\begin{equation}
@@
 	\end{equation}
-	and note that $\E^{\rho^\epl}[\chi^\epl(X^\epl,Z^\epl)] = 0$. Then we have
+	and note that $\E^{\rho^\epl}[\chi^\epl(X^\epl,Z^\epl)] = 0$. Then, by Lemma \ref{lem:CLT}, we have
 	\begin{equation}

### 2020-03-10 CalNotes.tex
update CLT second lemma

@@
 
-\begin{lemma} Let $u^\epl$ be the solution of \eqref{eq:CLT_Poisson} with 
+\begin{lemma} \label{lem:CLT_hom}
+	Let $u^\epl$ be the solution of \eqref{eq:CLT_Poisson} with 
 	\begin{equation}
@@
 	\begin{equation}
-		0 = (V'(z) \otimes V'(x))(A - \alpha - (K - 1)\alpha) - K \sigma \partial^2_{xx}u_0 + \left(K \alpha \cdot V'(x)\right) \partial_x u_0  + \frac1\delta(z-x) \partial_z u_0,
-	\end{equation}
-	which, since $A = K\alpha$ and $\Sigma = K\sigma$, implies
+		0 = (V'(z) \otimes V'(x))(A - \alpha - (K - 1)\alpha) - K \sigma \partial^2_{xx}u_0 + \left(K \alpha \cdot V'(x)\right) \partial_x u_0  + \frac1\delta(z-x) \partial_z u_0.
+	\end{equation}
+	Moreover, since $A = K\alpha$ and $\Sigma = K\sigma$, it implies
 	\begin{equation}
 		0 = -\Sigma \partial^2_{xx}u_0 + \left(A \cdot V'(x)\right) \partial_x u_0  + \frac1\delta(z-x) \partial_z u_0,
+	\end{equation}
+	which can be written as
+	\begin{equation}\label{eq:CLT_Poisson_hom}
+		- \mathcal L_0 u_0 = 0,
+	\end{equation}
+	where $\mathcal L_0$ is the generator of the couple $(X^0,Z^0)^\top$. Finally, the unique solution of \eqref{eq:CLT_Poisson_hom} satisfying
+	\begin{equation}
+		\E^{\rho^0}[u_0(X,Z)] = 0,
+	\end{equation}
+	is given by
+	\begin{equation}
+		u_0(x,z) = 0.
 	\end{equation}
@@
 	\end{equation}
-	Let us denote by $\Phi^\epl$ the solution of \eqref{eq:CLT_Poisson} with right hand side
+	Let us denote by $u^\epl$ the solution of \eqref{eq:CLT_Poisson} with right hand side
 	\begin{equation}
@@
 	\begin{aligned}
-	\Gamma_1^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x \Phi^\epl(X^\epl, Z^\epl) \otimes \partial_x \Phi^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
-	&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[\Phi^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl) + \chi^\epl(X^\epl, Z^\epl) \otimes \Phi^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
+	\Gamma_1^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
+	&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[u^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl) + \chi^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
 	\end{aligned}
@@
 	\corr{For the covariance $\Gamma_1^\epl$ we don't know how it behaves in the limit $\epl \to 0$.
-It would be nice if it was vanishing, but it involves the solution $\Phi^\epl$, which has r.h.s.
-depending of $\epl$.
-We noticed that the homogenized problem of
-	\begin{equation}
-		-\mathcal L_\epl \Phi^\epl = \chi^\epl,
-	\end{equation}
-	is given by
-	\begin{equation}
-		-\mathcal L_0 \Phi^0 = 0,
-	\end{equation}
-	whose zero-mean solution is $\Phi^0 = 0$.}
+It would be nice if it was vanishing since it involves the solution $u^\epl$, which goes to zero (in some sense) due to Lemma \ref{lem:CLT_hom}.}
 

### 2020-03-12 CalNotes.tex
Work on delta=eps power

@@
 	\begin{aligned}[t] &(\psi^\epl)'(z) z^2 - (\psi^\epl)'(z) \int_{\R} x^2 \phi^\epl(x) R^\epl(x, z) \dd x \\
-	& + 2 \psi^\epl(x) z - \psi^\epl \int_{\R} x^2 \phi^\epl(x) \partial_z R^\epl(x, z) \dd x.
+	& + 2 \psi^\epl(z) z - \psi^\epl \int_{\R} x^2 \phi^\epl(x) \partial_z R^\epl(x, z) \dd x.
 	\end{aligned}
@@
 	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}. Finally, it is possible to verify by induction on $r$ that for all integers $r$ it holds
-	\begin{equation}
+	\begin{equation}\label{eq:FilterTminusS}
 	\int_0^t k(t-s) (t - s)^r \dd s \leq r! \, \delta^r, 
@@
 
+\section{Some calculations}
+
+\begin{lemma}
+	\begin{equation}
+		Z_t^\epl - X_t^\epl = \delta (A \cdot V'(X_t^\epl)) + \ldots
+	\end{equation}
+\end{lemma}
+\begin{proof} Let $t > s$, $\Phi$ solution of \eqref{eq:CellProblem} and $Y_t^\epl = X_t^\epl / \epl$. Then, an application of the Itô formula yields \cite[Formula 5.8]{PaS07}
+	\begin{equation}\label{eq:App_DiffXtXs}
+	\begin{aligned}
+		X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
+		&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r + \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)).
+	\end{aligned}
+	\end{equation}
+	Recall that we have
+	\begin{equation}
+		X_t^\epl - Z_t^\epl = \int_0^t k(t-s) (X_t - X_s) \dd s + e^{-t/\delta}X_t.
+	\end{equation}
+	Plugging \eqref{eq:App_DiffXtXs} into the equation above, we obtain
+	\begin{equation}
+		X_t^\epl - Z_t^\epl = I_1^\epl(t) + I_2^\epl(t) + I_3^\epl(t) + I_4^\epl(t),
+	\end{equation}
+	where
+	\begin{equation}
+	\begin{aligned}
+		I_1^\epl(t) &\defeq -\int_0^t k(t-s)\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r \dd s,\\
+		I_2^\epl(t) &\defeq \sqrt{2\sigma}\int_0^t k(t-s) \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r \dd s, \\
+		I_3^\epl(t) &\defeq \epl \int_0^t k(t-s)(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)) \dd s,\\
+		I_4^\epl(t) &= e^{-t / \delta}X_t.
+	\end{aligned}
+	\end{equation}
+	Let us analyze the terms above singularly. For $I_1^\epl(t)$, one can show \cite[Proposition 5.8]{PaS07}
+	\begin{equation}
+		 \int_s^t (\alpha \cdot V'(X_r^\epl)) (1 + \Phi'(Y^\epl_r)) \dd r = (t - s)(A \cdot V'(X_t^\epl)) + R_1^\epl(t-s),
+	\end{equation}
+	in law, where
+	\begin{equation}\label{eq:FirstTermPavStu}
+		\left(\E^{\phi^\epl}\abs{R_1^\epl(t-s)}^p\right)^{1/p} \leq C(\epl^2 + \epl(t-s)^{1/2}+(t-s)^{3/2}).
+	\end{equation}
+	Therefore, 
+	\begin{equation}\label{eq:Diff_I1}
+	\begin{aligned}
+		I_1^\epl(t) &= -(A \cdot V'(X_t^\epl)) \int_0^t k(t-s) (t-s)\dd s + \int_0^t k(t-s)R^\epl(t-s) \dd s\\
+		&= -\delta (A \cdot  V'(X_t^\epl)) + e^{-t/\delta}(t + \delta)(A \cdot V'(X_t^\epl)) + \widetilde R_1^\epl(t),
+	\end{aligned}
+	\end{equation}
+	where we exploited the equality
+	\begin{equation}
+		\int_0^t k(t-s) (t-s) \dd s = \delta - e^{-t/\delta}(t + \delta),
+	\end{equation}
+	and where
+	\begin{equation}
+		\widetilde R_1^\epl(t) \defeq \int_0^t k(t-s)R_1^\epl(t-s) \dd s.
+	\end{equation}
+	Now, Jensen's inequality with $\kappa(\d s)$ and the inequalities \eqref{eq:FirstTermPavStu} and \eqref{eq:FilterTminusS} yield for all integers $p \geq 1$ and a constant $C$ depending only on $p$
+	\begin{equation}
+	\begin{aligned}
+		\E\abs{\widetilde R_1^\epl(t)}^{2p} &= (1-e^{-t/\delta})^{2p}\E\abs{\int_0^t R_1^\epl(t-s) \kappa(\d s)}^{2p}\\
+		&\leq (1-e^{-t/\delta})^{2p} \int_0^t \E \abs{R_1^\epl(t-s)}^{2p} \kappa(\d s)\\
+		&\leq C (1-e^{-t/\delta})^{2p-1} \int_0^t k(t-s)(\epl^{4p} + \epl(t-s)^p+(t-s)^{3p}) \dd s\\
+		&\leq C \left( \epl^{4p} + \epl \delta^p + \delta^{3p} \right).
+	\end{aligned}
+	\end{equation}
+	We now consider the second term. Let us remark that it holds \cite[Proposition 5.7, Section 6.2]{PaS07}
+	\begin{equation}
+		\sqrt{2\sigma} \int_s^t \left(1+\Phi'(Y_s^\epl)\right) \dd W_r = \sqrt{2\Sigma}\left(\widehat W_t - \widehat W_s\right) + R_2^\epl(t-s),
+	\end{equation}
+	in law, where $\Sigma$ is the diffusion coefficient of the homogenized equation \eqref{eq:SDE_HOM}, $\widehat W_t$ is a standard Brownian motion and 
+	\begin{equation}
+		\left(\E\abs{R_2^\epl(t-s)}^p\right)^{1/p} \leq C\epl^\iota,
+	\end{equation}
+	for all $\iota \in (0, 1/2)$. Therefore, it holds in law
+	\begin{equation}
+		I_2^\epl(t) = \int_0^t k(t-s) \left(\widehat W_t - \widehat W_s\right) \dd s + \widetilde R_2^\epl(t),
+	\end{equation}
+	where
+	\begin{equation}
+		\widetilde R_2^\epl(t) \defeq \int_0^t k(t-s) R_2^\epl(t-s) \dd s.
+	\end{equation}
+	Let us now remark that applying Jensen's inequality with $\kappa(\d s)$, due to the moments of the Gaussian distribution and applying \eqref{eq:FilterTminusS}, we have for a constant $C > 0$ depending only on $p$
+	\begin{equation}
+	\begin{aligned}
+		\E\abs{\int_0^t k(t-s) \left(\widehat W_t - \widehat W_s\right) \dd s}^p &\leq (1-e^{-t/\delta})^{p-1} \int_0^t (2\Sigma)^{p/2}k(t-s)\E\abs{\widehat W_t - \widehat W_s}^p \dd s\\
+		&\leq C \int_0^t k(t - s) (t-s)^p \dd s \\
+		&\leq C \delta^p.
+	\end{aligned}
+	\end{equation}
+	Moreover, always applying Jensen's inequality with $\kappa(\d s)$ we simply obtain
+	\begin{equation}
+		\E\abs{\widetilde R_2^\epl(t)}^p \leq C \epl^{p\iota}.
+	\end{equation}
+	Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
+	\begin{equation}
+		\abs{I_3^\epl(t)} \leq C \epl, 
+	\end{equation}
+	almost surely. Finally, due to \cite[Corollary 5.4]{PaS07}, we know that $X_t^\epl$ has bounded moments of all orders and therefore
+	\begin{equation}
+		\E\abs{I_4^\epl(t)}^p \leq C e^{-pt/\delta},
+	\end{equation}
+	which concludes the proof.
+\end{proof}
+
 \end{appendices}

### 2020-03-16 CalNotes.tex
proof case delta eps_zeta

@@
 \begin{equation}
-	\sigma \delta \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)].
+	\sigma \delta \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)].
 \end{equation}
@@
 	\begin{equation}
-		\Sigma \delta \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z = \E^{\rho^0}[(X^2 - Z^2)V''(Z)].
+		\Sigma \delta \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z = \E^{\rho^0}[(X - Z)^2 V''(Z)].
 	\end{equation}
@@
 Due to Lemma \ref{lem:FPMarginal}, we therefore have
-\begin{equation}
-	\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)], \quad \text{a.s.}	
+\begin{equation} \label{eq:for_zeta}
+	\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)], \quad \text{a.s.}	
 \end{equation}
@@
 \begin{equation} \label{limit_estimator_2}
-	\lim_{\epl \to 0} \lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)], \quad \text{a.s.},
+	\lim_{\epl \to 0} \lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X - Z)^2 V''(Z)], \quad \text{a.s.},
 \end{equation}
@@
 \begin{equation}\label{eq:final_result}
-	\frac{1}{\delta} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] = \Sigma \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z,
+	\frac{1}{\delta} \E^{\rho^0}[(X - Z)^2 V''(Z)] = \Sigma \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z,
 \end{equation}
@@
 \begin{aligned}
-	\frac{1}{\delta} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] &= -\Sigma \int_{\R} \int_{\R} V'(z) (\phi^0)'(x) \psi^0(z) R^0(x,z) \dd x \dd z\\
+	\frac{1}{\delta} \E^{\rho^0}[(X - Z)^2 V''(Z)] &= -\Sigma \int_{\R} \int_{\R} V'(z) (\phi^0)'(x) \psi^0(z) R^0(x,z) \dd x \dd z\\
 	&= -\Sigma \int_{\R} \int_{\R} V'(z) \frac{\d}{\d x} \left ( \frac{1}{C_{\phi^0}} e^{-\frac{1}{\Sigma} A\cdot V(x)} \right ) \psi^0(z) R^0(x,z) \dd x \dd z \\
@@
 
+\corr{ CASE $\delta = \epl^\zeta$ (PROOF IN APPENDIX \ref{ap:zeta}).
+\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and let $\delta = \epl^\zeta$ with $\zeta \in (0,1)$.
+If $\widetilde M$ is invertible, then
+		\begin{equation}
+		\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A_k^\epl(T) = A, \quad \text{in law},
+		\end{equation}
+		where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.
+\end{theorem}}
+
 \subsection{Central limit theorem}
@@
 }
+
 \section{The Bayesian setting}\label{sec:Bayesian}
@@
 	\begin{equation}
-	\lim_{\epl \to 0} \lim_{T \to \infty} \widetilde A^\epl_k(T) = A, \quad \text{a.s.},
+	\lim_{\epl \to 0} \lim_{T \to \infty} \widetilde A^\epl_k(T) = A, \quad \corr{\text{in law}},
 	\end{equation} 
@@
 	\begin{equation}
-	\lim_{\epl \to 0}\lim_{T \to \infty} \widetilde \mu_{T,\epl}(\cdot) = \delta(\cdot - A), \quad \text{a.s.},
+	\lim_{\epl \to 0}\lim_{T \to \infty} \widetilde \mu_{T,\epl}(\cdot) = \delta(\cdot - A), \quad \corr{\text{in law}},
 	\end{equation}
@@
 	\end{equation}
-	and which proves \eqref{eq:marginalX}. By integrating equation \eqref{eq:FPsystem} with respect to $x$ and integrating by parts we obtain
-	\begin{equation}
-	\psi^\epl(z) + z (\psi^\epl)'(z) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x,
-	\end{equation}
-	which can be written as
-	\begin{equation}
-	\frac{\d}{\d z} (z \psi^\epl(z)) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x.
-	\end{equation}
-	Now, since $\psi^\epl$ is the density of a probability distribution, this implies that 
-	\begin{equation}\label{FPz}
-	z \psi^\epl(z) = \int_{\R} x \rho^\epl(x,z) \dd x,
-	\end{equation}
-	which, replacing the decomposition \eqref{eq:densityDecomposition}, yields
-	\begin{equation} \label{eq:z_condition}
-	z = \int_{\R} x \phi^\epl(x) R^\epl(x,z) \dd x.
-	\end{equation}
-	In view of \eqref{eq:densityDecomposition} and \eqref{FPx}, equation \eqref{eq:FPsystem} can be rewritten as
+	and which proves \eqref{eq:marginalX}. \corr{In view of \eqref{eq:densityDecomposition} and \eqref{FPx}, equation \eqref{eq:FPsystem} can be rewritten as
 	\begin{equation}\label{eq:psiEqualityPDE}
-	\sigma \phi^\epl \psi^\epl \partial^2_{xx} R^\epl + \frac{1}{\delta} \phi^\epl \psi^\epl R^\epl + \sigma (\phi^\epl)' \psi^\epl \partial_x R^\epl + \frac{1}{\delta} (z-x) \phi^\epl ((\psi^\epl)' R + \psi^\epl \partial_z R^\epl) = 0.
-	\end{equation}
-	We now multiply the equation above by $x$ and integrate with respect to $x$. Let us consider some simplifications explicitly. First, an integration by parts yields
-	\begin{equation}\label{eq:psiEqualityPDE_1}
-	\begin{aligned}
-	\sigma \psi^\epl \int_{\R}  x \phi^\epl \partial^2_{xx} R^\epl \dd x+ \sigma \psi^\epl \int_{\R} x (\phi^\epl)' \partial_x R^\epl \dd x &= -\sigma \psi^\epl \int_{\R} \phi^\epl \partial_x R^\epl \dd x.
-	\end{aligned}
-	\end{equation}
-	Then, applying \eqref{eq:z_condition}, we have
-	\begin{equation}\label{eq:psiEqualityPDE_2}
-	\frac1\delta \psi^\epl \int_{\R} x \phi^\epl  R^\epl \dd x = \frac1\delta z \psi^\epl.
-	\end{equation}
-	Moreover, again applying \eqref{eq:z_condition}, we can compute
-	\begin{equation}\label{eq:psiEqualityPDE_3}
-	\begin{aligned}
-	\frac1\delta (\psi^\epl)' \int_\R (z-x)x \phi^\epl  R \dd x = \frac1\delta (\psi^\epl)' \left(z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x\right).
-	\end{aligned}
-	\end{equation}
-	Finally, we compute the last term always applying \eqref{eq:z_condition} obtaining
-	\begin{equation}\label{eq:psiEqualityPDE_4}
-	\frac1\delta \psi^\epl \int_\R (z-x)x \phi^\epl \partial_z R \dd x = \frac1\delta \psi^\epl\left(z - \int_{\R} x^2 \phi^\epl \partial_z R^\epl \dd x\right).
-	\end{equation}
-	Replacing the equalities \eqref{eq:psiEqualityPDE_1}, \eqref{eq:psiEqualityPDE_2}, \eqref{eq:psiEqualityPDE_3} and \eqref{eq:psiEqualityPDE_4} into \eqref{eq:psiEqualityPDE} we obtain
-	\begin{equation}
-	(\psi^\epl)' \left ( z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x \right ) + \psi^\epl \left ( 2z - \int_{\R} x^2 \phi^\epl \partial_z R^\epl \dd x - \delta \sigma \int_{\R} \phi^\epl \partial_x R^\epl \dd x \right ) = 0.
-	\end{equation}
-	We rewrite the equality above as
-	\begin{equation} \label{eq:psiEquality}
-	\delta \sigma \psi^\epl(z) \int_{\R} \phi^\epl(x) \partial_x R^\epl(x, z) \dd x = 
-	\begin{aligned}[t] &(\psi^\epl)'(z) z^2 - (\psi^\epl)'(z) \int_{\R} x^2 \phi^\epl(x) R^\epl(x, z) \dd x \\
-	& + 2 \psi^\epl(z) z - \psi^\epl \int_{\R} x^2 \phi^\epl(x) \partial_z R^\epl(x, z) \dd x.
-	\end{aligned}
-	\end{equation}
-	Multiplying by $V'(z)$, integrating with respect to $z$ and integrating by parts, we obtain the following identity in $\R^N$
-	\begin{equation}
-	\begin{aligned}
-	\sigma \delta \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z &=  \int_{\R} \int_{\R} (x^2 - z^2) V''(z) \rho_\epl(x,z) \dd x \dd z \\
-	&= \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)],
-	\end{aligned}
-	\end{equation}
-	which is the desired result.
+	\partial_x \left( \sigma \phi^\epl \psi^\epl \partial_x R^\epl \right) + \partial_z \left( \frac1\delta(z-x) \phi^\epl \psi^\epl R^\epl \right) = 0.
+	\end{equation}
+	We now multiply the equation above by a continuous differentiable function $f \colon \R^2 \to \R^N$, $f = f(x,z)$, and integrate with respect to $x$ and $z$. Then integration by parts yields
+	\begin{equation}
+	\sigma \int_\R \int_\R \partial_x f(x,z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \frac1\delta \int_\R \int_\R \partial_z f(x,z) (x-z) \phi^\epl(x) \psi^\epl(z) R^\epl(x,z) \dd x \dd z,
+	\end{equation}
+	which implies the following identity in $\R^N$
+	\begin{equation}
+	\sigma \delta \int_\R \int_\R \partial_x f(x,z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \E^{\rho_\epl} \left[ \partial_z f(X^\epl,Z^\epl) (X^\epl-Z^\epl) \right].
+	\end{equation}
+	Finally, choosing 
+	\begin{equation}
+	f(x,z) = (x - z) V'(z) + V(z),
+	\end{equation}
+	we obtain the desired result.}
 \end{proof}
@@
 The Portmanteau theorem can be employed to conclude that the measure $\mu^\epl$ converges weakly to $\mu^0$ for $\epl \to 0$.
+\end{proof}
+
+\section{Proof of Theorem \ref{thm:mainTheorem_zeta}} \label{ap:zeta}
+
+\begin{lemma} \label{lem:zeta}
+	For $\epl,\delta>0$ sufficiently small and $t>0$ sufficiently big, there exists a standard Brownian motion $B_t$ independent of the processes $X_t$ and $Z_t$ such that
+	\begin{equation}
+	X_t^\epl - Z_t^\epl = \sqrt{2\Sigma}\delta \int_0^t k(t-s) \dd B_s + R(\epl,\delta),
+	\end{equation}
+	in law. The remainder $R(\epl,\delta)$ satisfies, for every $p > 0$ and $\iota \in (0,1/2)$, the estimate
+	\begin{equation} \label{eq:remainder_zeta}
+		\left( \E^{\rho_\epl} \left| R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta + \epl^\iota + \epl \delta^{1/2} \right),
+	\end{equation}
+	where $C$ is independent of $\epl$ and $\delta$.
+\end{lemma}
+\begin{proof} Let $t > s$, $\Phi$ solution of \eqref{eq:CellProblem} and $Y_t^\epl = X_t^\epl / \epl$. Then, an application of the Itô formula yields \cite[Formula 5.8]{PaS07}
+	\begin{equation}\label{eq:App_DiffXtXs}
+	\begin{aligned}
+	X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
+	&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r - \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)).
+	\end{aligned}
+	\end{equation}
+	Recall that we have
+	\begin{equation}
+	X_t^\epl - Z_t^\epl = \int_0^t k(t-s) (X_t^\epl - X_s^\epl) \dd s + e^{-t/\delta}X_t^\epl.
+	\end{equation}
+	Plugging \eqref{eq:App_DiffXtXs} into the equation above, we obtain
+	\begin{equation}
+	X_t^\epl - Z_t^\epl = I_1^\epl(t) + I_2^\epl(t) + I_3^\epl(t) + I_4^\epl(t),
+	\end{equation}
+	where
+	\begin{equation}
+	\begin{aligned}
+	I_1^\epl(t) &\defeq -\int_0^t k(t-s)\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r \dd s,\\
+	I_2^\epl(t) &\defeq \sqrt{2\sigma}\int_0^t k(t-s) \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r \dd s, \\
+	I_3^\epl(t) &\defeq - \epl \int_0^t k(t-s)(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)) \dd s,\\
+	I_4^\epl(t) &= e^{-t / \delta}X_t.
+	\end{aligned}
+	\end{equation}
+	Let us analyze the terms above singularly. For $I_1^\epl(t)$, one can show \cite[Proposition 5.8]{PaS07}
+	\begin{equation}
+	\int_s^t (\alpha \cdot V'(X_r^\epl)) (1 + \Phi'(Y^\epl_r)) \dd r = (t - s)(A \cdot V'(X_t^\epl)) + R_1^\epl(t-s),
+	\end{equation}
+	in law, where
+	\begin{equation}\label{eq:FirstTermPavStu}
+	\left(\E^{\phi^\epl}\abs{R_1^\epl(t-s)}^p\right)^{1/p} \leq C(\epl^2 + \epl(t-s)^{1/2}+(t-s)^{3/2}).
+	\end{equation}
+	Therefore, 
+	\begin{equation}\label{eq:Diff_I1}
+	\begin{aligned}
+	I_1^\epl(t) &= -(A \cdot V'(X_t^\epl)) \int_0^t k(t-s) (t-s)\dd s + \int_0^t k(t-s)R^\epl(t-s) \dd s\\
+	&= -\delta (A \cdot  V'(X_t^\epl)) + e^{-t/\delta}(t + \delta)(A \cdot V'(X_t^\epl)) + \widetilde R_1^\epl(t),
+	\end{aligned}
+	\end{equation}
+	where we exploited the equality
+	\begin{equation}
+	\int_0^t k(t-s) (t-s) \dd s = \delta - e^{-t/\delta}(t + \delta),
+	\end{equation}
+	and where
+	\begin{equation}
+	\widetilde R_1^\epl(t) \defeq \int_0^t k(t-s)R_1^\epl(t-s) \dd s.
+	\end{equation}
+	Now, Jensen's inequality with $\kappa(\d s)$ and the inequalities \eqref{eq:FirstTermPavStu} and \eqref{eq:FilterTminusS} yield for all integers $p \geq 1$ and a constant $C$ depending only on $p$
+	\begin{equation}
+	\begin{aligned}
+	\E^{\phi^\epl}\abs{\widetilde R_1^\epl(t)}^{2p} &= (1-e^{-t/\delta})^{2p}\E^{\phi^\epl}\abs{\int_0^t R_1^\epl(t-s) \kappa(\d s)}^{2p}\\
+	&\leq (1-e^{-t/\delta})^{2p} \int_0^t \E^{\phi^\epl} \abs{R_1^\epl(t-s)}^{2p} \kappa(\d s)\\
+	&\leq C (1-e^{-t/\delta})^{2p-1} \int_0^t k(t-s)(\epl^{4p} + \epl^{2p}(t-s)^p+(t-s)^{3p}) \dd s\\
+	&\leq C \left( \epl^{4p} + \epl^{2p} \delta^p + \delta^{3p} \right).
+	\end{aligned}
+	\end{equation}
+	Therefore, for $t$ sufficiently big, we get
+	\begin{equation}
+	\begin{aligned}
+		\left(\E^{\phi^\epl}\abs{I_1^\epl(t)}^{p}\right)^{1/p} \le& C \left( \delta + \epl^2 + \epl \delta^{1/2} + \delta^{3/2} \right) \\
+		\le& C \left( \delta + \epl^2 + \epl \delta^{1/2} \right).
+	\end{aligned}
+	\end{equation}
+	We now consider the second term. Let us remark that it holds \cite[Proposition 5.7, Section 6.2]{PaS07}
+	\begin{equation}
+	\sqrt{2\sigma} \int_s^t \left(1+\Phi'(Y_s^\epl)\right) \dd W_r = \sqrt{2\Sigma}\left( B_t - B_s\right) + R_2^\epl(t-s),
+	\end{equation}
+	in law, where $\Sigma$ is the diffusion coefficient of the homogenized equation \eqref{eq:SDE_HOM}, $B_t$ is a standard Brownian motion \corr{independent of the process $X_t$ (?)} and 
+	\begin{equation}
+	\left(\E^{\phi^\epl}\abs{R_2^\epl(t-s)}^p\right)^{1/p} \leq C\epl^\iota,
+	\end{equation}
+	for all $\iota \in (0, 1/2)$. Therefore, it holds in law
+	\begin{equation} \label{eq:I2_decomposition}
+	I_2^\epl(t) = \sqrt{2\Sigma} \int_0^t k(t-s) \left(B_t - B_s\right) \dd s + \widetilde R_2^\epl(t),
+	\end{equation}
+	where
+	\begin{equation}
+	\widetilde R_2^\epl(t) \defeq \sqrt{2\Sigma} \int_0^t k(t-s) R_2^\epl(t-s) \dd s.
+	\end{equation}
+	Applying Jensen's inequality with $\kappa(\d s)$ we obtain
+	\begin{equation}
+	\left(\E^{\phi^\epl} \abs{\widetilde R_2^\epl(t)}^p\right)^{1/p} \leq C \epl^{\iota}.
+	\end{equation}
+	Let us remark that an application of the Itô formula yields
+	\begin{equation}
+		\dd \left( k(t-s)B_s \right) = \frac1\delta k(t-s)B_s \dd s + k(t-s) \dd B_s,
+	\end{equation}
+	which implies
+	\begin{equation} \label{eq:Ito_kB}
+		\int_0^t k(t-s)B_s \dd s = B_t - \delta \int_0^t k(t-s) \dd B_s.
+	\end{equation}
+	Substituting \eqref{eq:Ito_kB} into \eqref{eq:I2_decomposition} and recalling that
+	\begin{equation}
+		\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta},
+	\end{equation}
+	we obtain
+	\begin{equation}
+		I_2^\epl(t) = \sqrt{2\Sigma} \delta \int_0^t k(t-s) \dd B_s - \sqrt{2\Sigma} e^{-t/\delta} B_t.
+	\end{equation}
+	Moreover note that
+	\begin{equation}
+			\left(\E^{\phi^\epl} \abs{\sqrt{2\Sigma} e^{-t/\delta} B_t}^p\right)^{1/p} \le C e^{-t/\delta}.
+	\end{equation}
+
+	Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
+	\begin{equation}
+	\abs{I_3^\epl(t)} \leq C \epl, 
+	\end{equation}
+	almost surely. Finally, due to \cite[Corollary 5.4]{PaS07}, we know that $X_t^\epl$ has bounded moments of all orders and therefore
+	\begin{equation}
+	\left(\E^{\phi^\epl} \abs{I_4^\epl(t)}^p\right)^{1/p} \leq C e^{-t/\delta},
+	\end{equation}
+	which concludes the proof.
+\end{proof}
+
+\begin{proof}[Proof of Theorem \ref{thm:mainTheorem_zeta}]
+	Let us introduce the notation
+	\begin{equation}
+		\mathcal A^\epl(\delta) = \frac1\delta \widetilde{\mathcal M}_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)],
+	\end{equation}
+	where
+	\begin{equation}
+		\widetilde{\mathcal M}_\epl = \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ].
+	\end{equation}
+	Then following the proof of Theorem \ref{thm:mainTheorem} we only need to show that if $\delta = \epl^\zeta$ with $\zeta \in (0,1)$ we have
+	\begin{equation}
+		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = A, \quad \text{in law}.
+	\end{equation}
+	Using Lemma \ref{lem:zeta} and geometric ergodicity (Lemma \ref{lem:ergodicity}), we have the following equality in law
+	\begin{equation}
+	\begin{aligned}
+		\mathcal A^\epl(\delta) &= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E [(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl)] \\
+		&= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E \left[ \left( \sqrt{2\Sigma}\delta \int_0^t k(t-s) \dd B_s + R(\epl,\delta) \right)^2 V''(Z_t^\epl) \right] \\
+		&\eqdef \widetilde{\mathcal M}_\epl^{-1} \lim_{t \to \infty} \left( J_1^\epl(t) + J_2^\epl(t) + J_3^\epl(t) \right),
+	\end{aligned}
+	\end{equation}
+	where
+	\begin{equation}
+	\begin{aligned}
+		J_1^\epl(t) &= 2\Sigma\delta \E^{\rho^\epl} \left[ \left( \int_0^t k(t-s) \dd B_s \right)^2 V''(Z_t^\epl) \right], \\
+		J_2^\epl(t) &= 2\sqrt{2\Sigma} \E^{\rho^\epl} \left[ \left( \int_0^t k(t-s) \dd B_s \right) R(\epl,\delta) V''(Z_t^\epl) \right], \\
+		J_3^\epl(t) &= \frac1\delta \E^{\rho^\epl} \left[ R(\epl,\delta)^2 V''(Z_t^\epl) \right].
+	\end{aligned}
+	\end{equation}
+	Let us consider the three terms separately. First, since the Brownian motion $B_s$ is independent of the process $Z_t^\epl$, applying Itô isometry we get
+	\begin{equation}
+	J_1^\epl(t) = 2\Sigma\delta \left( \int_0^t k(t-s)^2 \dd s \right) \E [V''(Z_t^\epl)] = \Sigma \E^{\rho^\epl} [V''(Z_t^\epl)],
+	\end{equation}
+	and, by Lemma \ref{lem:distanceZandX} and weak convergence of the invariant measure, we obtain
+	\begin{equation}
+	\lim_{\epl \to 0} \lim_{t \to \infty} J_1^\epl(t) = \Sigma \lim_{\epl \to 0} \E^{\rho^\epl} [V''(Z^\epl)] = \Sigma \E^{\rho^0} [V''(X)].
+	\end{equation}
+	Moreover, due to \eqref{eq:remainder_zeta}, we have the following bounds for $J_2^\epl(t)$ and $J_3^\epl(t)$
+	\begin{equation}
+	\begin{aligned}
+		\abs{J_2^\epl(t)} &\le C \left( \delta^{1/2} + \epl^\iota \delta^{-1/2} + \epl \right), \\
+		\abs{J_3^\epl(t)} &\le C \left( \delta + \epl^{2\iota} \delta^{-1} + \epl^2 \right).
+	\end{aligned}
+	\end{equation}
+	Furthermore, by Lemma \ref{lem:distanceMandTildeM} and weak convergence of the invariant measure, we have
+	\begin{equation}
+		\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] \eqdef \mathcal M_0.
+	\end{equation}
+	Therefore
+	\begin{equation}
+		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \E^{\rho^0} [V''(X)],
+	\end{equation}
+	and, finally, an integration by parts yields
+	\begin{equation}
+		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \frac1\Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ] A = A,
+	\end{equation}
+	which implies the desired result.
 \end{proof}
@@
 	\begin{equation}\label{eq:CTL_A}
-	A = \frac1\delta \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)],
+	A = \frac1\delta \mathcal M_0^{-1} \E^{\rho^0}[(X - Z)^2 V''(Z)],
 	\end{equation}
@@
 	\begin{equation}\label{eq:CTL_alpha}
-	\alpha = \mathcal M_\epl^{-1} \left(\frac1\delta \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathfrak p_\epl \right).
+	\alpha = \mathcal M_\epl^{-1} \left(\frac1\delta \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)] - \mathfrak p_\epl \right).
 	\end{equation}
@@
 	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) &= \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \\
-	&+  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
+	&+  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X - Z)^2 V''(Z)] \right) \\
 	&- \sqrt{T} I_2^\epl(T).
@@
 	\begin{equation}
-		J_2^\epl(T) = \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right).
+		J_2^\epl(T) = \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X - Z)^2 V''(Z)] \right).
 	\end{equation}
@@
 	\begin{aligned}
-	J^\epl_{2}(T) &=  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1}  - \mathcal M_0^{-1} \right)\E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] \\
-	&\quad + \frac{\sqrt{T}}\delta \mathcal M_0^{-1}\left(\E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)] - \E^{\rho^0}[(X^2 - Z^2)V''(Z)] \right) \\
+	J^\epl_{2}(T) &=  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1}  - \mathcal M_0^{-1} \right)\E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)] \\
+	&\quad + \frac{\sqrt{T}}\delta \mathcal M_0^{-1}\left(\E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)] - \E^{\rho^0}[(X - Z)^2 V''(Z)] \right) \\
 	&\eqdef J_{2,1}^\epl(T) + J_{2,2}^\epl(T).
@@
 	\end{equation}
-	Therefore, due to Theorem \ref{thm:mainTheorem}, the inequality \eqref{eq:DistATildeAHat} and since $\delta \to 0$ for $\epl \to 0$, the desired result holds.
-\end{proof}
-
-\section{Some calculations}
-
-\begin{lemma}
-	\begin{equation}
-		Z_t^\epl - X_t^\epl = \delta (A \cdot V'(X_t^\epl)) + \ldots
-	\end{equation}
-\end{lemma}
-\begin{proof} Let $t > s$, $\Phi$ solution of \eqref{eq:CellProblem} and $Y_t^\epl = X_t^\epl / \epl$. Then, an application of the Itô formula yields \cite[Formula 5.8]{PaS07}
-	\begin{equation}\label{eq:App_DiffXtXs}
-	\begin{aligned}
-		X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
-		&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r + \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)).
-	\end{aligned}
-	\end{equation}
-	Recall that we have
-	\begin{equation}
-		X_t^\epl - Z_t^\epl = \int_0^t k(t-s) (X_t - X_s) \dd s + e^{-t/\delta}X_t.
-	\end{equation}
-	Plugging \eqref{eq:App_DiffXtXs} into the equation above, we obtain
-	\begin{equation}
-		X_t^\epl - Z_t^\epl = I_1^\epl(t) + I_2^\epl(t) + I_3^\epl(t) + I_4^\epl(t),
-	\end{equation}
-	where
-	\begin{equation}
-	\begin{aligned}
-		I_1^\epl(t) &\defeq -\int_0^t k(t-s)\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r \dd s,\\
-		I_2^\epl(t) &\defeq \sqrt{2\sigma}\int_0^t k(t-s) \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r \dd s, \\
-		I_3^\epl(t) &\defeq \epl \int_0^t k(t-s)(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)) \dd s,\\
-		I_4^\epl(t) &= e^{-t / \delta}X_t.
-	\end{aligned}
-	\end{equation}
-	Let us analyze the terms above singularly. For $I_1^\epl(t)$, one can show \cite[Proposition 5.8]{PaS07}
-	\begin{equation}
-		 \int_s^t (\alpha \cdot V'(X_r^\epl)) (1 + \Phi'(Y^\epl_r)) \dd r = (t - s)(A \cdot V'(X_t^\epl)) + R_1^\epl(t-s),
-	\end{equation}
-	in law, where
-	\begin{equation}\label{eq:FirstTermPavStu}
-		\left(\E^{\phi^\epl}\abs{R_1^\epl(t-s)}^p\right)^{1/p} \leq C(\epl^2 + \epl(t-s)^{1/2}+(t-s)^{3/2}).
-	\end{equation}
-	Therefore, 
-	\begin{equation}\label{eq:Diff_I1}
-	\begin{aligned}
-		I_1^\epl(t) &= -(A \cdot V'(X_t^\epl)) \int_0^t k(t-s) (t-s)\dd s + \int_0^t k(t-s)R^\epl(t-s) \dd s\\
-		&= -\delta (A \cdot  V'(X_t^\epl)) + e^{-t/\delta}(t + \delta)(A \cdot V'(X_t^\epl)) + \widetilde R_1^\epl(t),
-	\end{aligned}
-	\end{equation}
-	where we exploited the equality
-	\begin{equation}
-		\int_0^t k(t-s) (t-s) \dd s = \delta - e^{-t/\delta}(t + \delta),
-	\end{equation}
-	and where
-	\begin{equation}
-		\widetilde R_1^\epl(t) \defeq \int_0^t k(t-s)R_1^\epl(t-s) \dd s.
-	\end{equation}
-	Now, Jensen's inequality with $\kappa(\d s)$ and the inequalities \eqref{eq:FirstTermPavStu} and \eqref{eq:FilterTminusS} yield for all integers $p \geq 1$ and a constant $C$ depending only on $p$
-	\begin{equation}
-	\begin{aligned}
-		\E\abs{\widetilde R_1^\epl(t)}^{2p} &= (1-e^{-t/\delta})^{2p}\E\abs{\int_0^t R_1^\epl(t-s) \kappa(\d s)}^{2p}\\
-		&\leq (1-e^{-t/\delta})^{2p} \int_0^t \E \abs{R_1^\epl(t-s)}^{2p} \kappa(\d s)\\
-		&\leq C (1-e^{-t/\delta})^{2p-1} \int_0^t k(t-s)(\epl^{4p} + \epl(t-s)^p+(t-s)^{3p}) \dd s\\
-		&\leq C \left( \epl^{4p} + \epl \delta^p + \delta^{3p} \right).
-	\end{aligned}
-	\end{equation}
-	We now consider the second term. Let us remark that it holds \cite[Proposition 5.7, Section 6.2]{PaS07}
-	\begin{equation}
-		\sqrt{2\sigma} \int_s^t \left(1+\Phi'(Y_s^\epl)\right) \dd W_r = \sqrt{2\Sigma}\left(\widehat W_t - \widehat W_s\right) + R_2^\epl(t-s),
-	\end{equation}
-	in law, where $\Sigma$ is the diffusion coefficient of the homogenized equation \eqref{eq:SDE_HOM}, $\widehat W_t$ is a standard Brownian motion and 
-	\begin{equation}
-		\left(\E\abs{R_2^\epl(t-s)}^p\right)^{1/p} \leq C\epl^\iota,
-	\end{equation}
-	for all $\iota \in (0, 1/2)$. Therefore, it holds in law
-	\begin{equation}
-		I_2^\epl(t) = \int_0^t k(t-s) \left(\widehat W_t - \widehat W_s\right) \dd s + \widetilde R_2^\epl(t),
-	\end{equation}
-	where
-	\begin{equation}
-		\widetilde R_2^\epl(t) \defeq \int_0^t k(t-s) R_2^\epl(t-s) \dd s.
-	\end{equation}
-	Let us now remark that applying Jensen's inequality with $\kappa(\d s)$, due to the moments of the Gaussian distribution and applying \eqref{eq:FilterTminusS}, we have for a constant $C > 0$ depending only on $p$
-	\begin{equation}
-	\begin{aligned}
-		\E\abs{\int_0^t k(t-s) \left(\widehat W_t - \widehat W_s\right) \dd s}^p &\leq (1-e^{-t/\delta})^{p-1} \int_0^t (2\Sigma)^{p/2}k(t-s)\E\abs{\widehat W_t - \widehat W_s}^p \dd s\\
-		&\leq C \int_0^t k(t - s) (t-s)^p \dd s \\
-		&\leq C \delta^p.
-	\end{aligned}
-	\end{equation}
-	Moreover, always applying Jensen's inequality with $\kappa(\d s)$ we simply obtain
-	\begin{equation}
-		\E\abs{\widetilde R_2^\epl(t)}^p \leq C \epl^{p\iota}.
-	\end{equation}
-	Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
-	\begin{equation}
-		\abs{I_3^\epl(t)} \leq C \epl, 
-	\end{equation}
-	almost surely. Finally, due to \cite[Corollary 5.4]{PaS07}, we know that $X_t^\epl$ has bounded moments of all orders and therefore
-	\begin{equation}
-		\E\abs{I_4^\epl(t)}^p \leq C e^{-pt/\delta},
-	\end{equation}
-	which concludes the proof.
+	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta \to 0$ for $\epl \to 0$, the desired result holds.
 \end{proof}

### 2020-03-20 CLT_Preliminaries/CLT.tex
update delta=eps power

--- 2020-03-10 CalNotes.tex
@@
 
-\input{ex_shared}
+\input{../ex_shared}
 
 \begin{document}
-\maketitle
-
-\textbf{Abstract.} We study the problem of drift estimation for two-scale continuous time series.
-We set ourselves in the framework of overdamped Langevin equations, for which a single-scale surrogate homogenized equation exists.
-In this setting, estimating the drift coefficient of the homogenized equation requires pre-processing of the data, often in the form of subsampling.
-We avoid subsampling by filtering the data with an appropriate kernel function and compute maximum likelihood estimators based on the filtered process.
-We show that the estimators we propose are asymptotically unbiased and demonstrate numerically the advantages of our method with respect to subsampling.
-Finally, we show how our filtering methodology can be combined with Bayesian techniques and provide a full uncertainty quantification of the inference procedure.
-
-\textbf{AMS subject classifications.} 62F15, 65C30, 62M05, 74Q10.
-
-\textbf{Keywords.} Parameter inference, diffusion process, data-driven homogenization, filtering, Bayesian inference, Langevin equation.
-
-\section{Introduction}
-
-Efficient parameter estimation for stochastic models is essential in a wide range of applications in natural and social sciences.
-In several areas, the data originate from phenomena which vary continuously in time and which are endowed with a multiscale structure.
-This is the case, for example, in molecular dynamics, oceanography and atmosphere science or in econometrics.
-Frequently, it is desirable in this areas to infer from data a simpler model which captures effectively large-scale structures, or slow variations, disregarding small-scale fluctuations or treating them as a source of noise.
-The mismatch between the data and their desired slow-scale representation is a typical instance of a problem of model misspecification, which, if ignored or mistreated, can lead to wrong solutions.
-Indeed, the data, coming from the full dynamics, are compatible with the coarse-grained model only at the time scales at which the effective dynamics is valid.
-
-In this paper we consider a simple multiscale setting arising from models of molecular dynamics, with a complete separation between a fast and a slow scale.
-In particular, we consider diffusion processes for which the confining potential has slow variations, and whose motion is perturbed by a fast-scale potential with rapid periodic and bounded oscillations.
-Given this simple class of model problems, we are interested in determining the drift coefficient of an equation of the overdamped Langevin type in which the fast-scale potential is eliminated.
-The theory of homogenization guarantees that such a single-scale equation can be uniquely determined, and our goal is therefore to obtain effective coarse-grained dynamics from data consistently with respect to the homogenization result.
-
-Several methods to take into account model misspecification in multiscale frameworks as above exist.
-For diffusion processes, the proposed approaches rely in different measures to subsampling, which has proved itself to some extent effective in many applications, but which requires nevertheless precise knowledge of how separated the two characteristic time scales are.
-Robustness of this methodology is dubious, too, as inference results tend to be extremely sensitive to the subsampling rate.
-
-In the rest of the introduction, we first give a brief overview of the existing literature on the topic of deterministic and stochastic multiscale inference problems, then introduce our novel methodology and its favourable properties and conclude with an outline of this paper.
-
-\subsection{Literature Review}
-
-For simple models in molecular dynamics, the effect of model misspecification was studied in a series of papers \cite{ABT10,ABJ13,PaS07,PPS09,PPS12,GaS17,GaS18} under the assumption of scale separation.
-In particular, for Brownian particles moving in two-scale potentials it was shown that, when fitting data from the full dynamics to the homogenized equation, the maximum likelihood estimator (MLE) is asymptotically biased \cite[Theorem 3.4]{PaS07}.
-To be more precise, in the large sample size limit the MLE converges to the coefficients of the unhomogenized equation, rather than to those of the homogenized one.
-The bias of the MLE can be eliminated by subsampling at an appropriate rate, which lies between the two characteristic time scales of the problem \cite[Theorems 3.5 and 3.6]{PaS07}.
-
-Similar techniques can be employed in econometrics, in particular for the estimation of the integrated stochastic volatility in the presence of market micro-structure noise.
-In this case, too, the data have to be subsampled at an appropriate rate \cite{AMZ05,OSP10}.
-The correct subsampling rate can be in some instances rather extreme with respect to the frequency of the data and lead to get rid of more than $99\%$ of the data.
-As the intuition suggests, this increases significantly the bias of the estimator, which is usually taken care of with additional bias corrections and variance reduction procedures.
-The need of such methodology is accentuated by data being obtained at high-frequency \cite{AiJ14,ZMA05}.
-
-The problem of extracting large-scale variations from multiscale data is studied in atmosphere and ocean science.
-In this field, too, subsampling the data is necessary to obtain an accurate coarse-grained model \cite{CoP09,YMV19}.
-
-The necessity to subsample the data can be alleviated by using appropriate martingale estimators, as was done in \cite{KPK13,KKP15}.
-This class of estimators can be applied to the case where the noise is multiplicative and also given by a deterministic chaotic system, as opposed to white noise.
-Estimators of this family have been applied to time series from paleoclimatic data and marine biology and augmented with appropriate model selection methodologies \cite{KPP15}.
-
-Inference of diffusion processes can be naturally performed under a Bayesian perspective.
-If one focuses on the drift coefficient, the form of the likelihood function guarantees, under a Gaussian prior hypothesis, that the posterior distribution is itself a Gaussian.
-The versatility of the Bayesian approach in the infinite-dimensional case \cite{Stu10, DaS16} gives the possibility to extend the problem of inferring the drift of a diffusion process to the non-parametric case \cite{PSV09, PSZ13}.
-
-The issue of model misspecification in inverse problems with a multiscale structure has been treated in the context of partial differential equations, too.
-In particular, it has been shown that it is possible to infer a coarse-grained equation from data coming from the full model and to retrieve asymptotically the correct result \cite{NPS12}.
-A series of papers \cite{AbD18, AbD19, AGZ19} focuses on retrieving the full model when the multiscale coefficient is endowed with a specific parametrized structure.
-Being these problems ill-posed, the latter is achieved via Tikhonov regularization \cite{AbD19,NPS12}, adopting a Bayesian approach \cite{AbD18, NPS12} or exploiting techniques of Kalman filtering \cite{AGZ19}.
-In \cite{AbD18,AGZ19}, the authors highlight the need of accounting explicitly for the modelling error due to homogenization and apply statistical techniques taken from \cite{CDS18,CES14}.
-
-\subsection{Our contributions}
-In this paper, we bypass the issue of subsampling by implementing an appropriate filtering methodology.
-In particular, we show that smoothing the data coming from the multiscale model with an appropriate linear time-invariant filter of the exponential family allows to retrieve the drift coefficient of the homogenized equation.
-The methodology we present is not involved computationally, easy to implement in practice and presents two main advantages:
-\begin{enumerate}
-	\item the filter's kernel depends on two parameters which can be tuned to obtain more robust results and which can be interpreted as analogous to the subsampling rate.
-Nevertheless, while the MLE is extremely sensitive with respect to the latter, our filtering methodology is robust with respect to its parameters, and can therefore be applied as a black-box tool for parameter estimation,
-	\item the entire stream of data is employed, which, in practice, enhances the quality of the filter-based MLE in terms of bias.
-Moreover, avoiding subsampling and thus discretising the data allows us to employ continuous-time theoretical tools.
-\end{enumerate}
-After having deduced unbiased estimators, we focus on how to insert the filtering methodology into a Bayesian approach.
-In particular, we analyse the effects of modifying the likelihood function if the smoothed trajectory is inserted in an appropriate manner.
-Under mild hypotheses on the filter parameters, we are able to show that the posterior distributions obtained with our methodology are asymptotically consistent with respect to the drift parameter of the homogenized equation.
-To our knowledge, this is the first instance of a successful Bayesian approach applied to multiscale diffusion processes.
-
-\subsection{Outline}
-The rest of the paper is organised as follows.
-In Section \ref{sec:Setting} we introduce the problem and lay the basis of our analysis setting the main assumptions and notation.
-In Section \ref{sec:Filter} we present our filtering methodology, with a particular focus on ergodic properties, on multiscale convergence and, naturally, on the properties of our estimators.
-In Section \ref{sec:Bayesian} we introduce the Bayesian framework and show how it can be enhanced with filtering techniques.
-Finally, in Section \ref{sec:NumExp} we demonstrate the effectiveness of our methodology via a series of numerical experiments.
-
-\section{Problem setting}\label{sec:Setting}
-
-In this section, we introduce the class of diffusion processes which we treat in this paper and the classical methodology employed for the estimation of the drift.
-Let $\epl > 0$ and let us consider the one-dimensional multiscale stochastic differential equation (SDE)
-\begin{equation}\label{eq:SDE_MS}
-	\d X_t^\epl = -\alpha \cdot V'(X_t^\epl) \dd t - \frac1\epl p'\left(\frac{X_t^\epl}\epl\right) \dd t + \sqrt{2\sigma} \dd W_t,
-\end{equation}
-where, given a positive integer $N$, we have that $\alpha \in \R^N$ and $\sigma > 0$ are the drift and diffusion coefficients respectively and $W_t$ is a standard one-dimensional Brownian motion.
-The functions $V\colon \R \to \R^N$ and $p\colon \R \to \R$ correspond to the slow-scale and the fast-scale confining potentials.
-In particular, we assume
-\begin{equation}\label{eq:Potential}
-	V(x) = \begin{pmatrix} V_1(x) & V_2(x) & \cdots & V_N(x) \end{pmatrix}^\top,
-\end{equation}
-for smooth functions $V_i\colon \R \to \R$, $i = 1, \ldots, N$.
-Moreover, we assume $p$ to be smooth and periodic of period $L$.
-Theory of homogenization \cite[Chapter 3]{BLP78} guarantees the existence of an SDE of the form
-\begin{equation}\label{eq:SDE_HOM}
-	\d X_t = - A \cdot V'(X_t) \dd t + \sqrt{2\Sigma} \dd W_t,
-\end{equation}
-where $W_t$ is the same Brownian motion as in \eqref{eq:SDE_MS}, such that $X_t^\epl \to X_t$ for $\epl\to 0$ in law as random variables in $\mathcal C^0([0, T]; \R)$.
-In particular, we have $A = K\alpha$ and $\Sigma = K \sigma$, where the coefficient \corr{$0<K<1$} is given by the formula
-\begin{equation}\label{eq:K_HOM}
-	K = \int_0^L (1 + \Phi'(y))^2 \, \mu(\d y),
-\end{equation}
-with 
-\begin{equation}
-	\mu(\d y) = \frac1Z e^{-p(y)/\sigma} \dd y, \quad\text{where}\quad Z = \int_0^L e^{-p(y)/\sigma} \dd y,
-\end{equation}
-and where the function $\Phi$ is the unique solution with zero-mean with respect to the measure $\mu$ of the elliptic partial differential equation
-\begin{equation}\label{eq:CellProblem}
-	-p'(y)\Phi'(y) + \sigma \Phi''(y) = p'(y), \quad 0 \leq y \leq L,
-\end{equation}
-endowed with periodic boundary conditions. \corr{Let us remark that in this one-dimensional setting it is possible to determine $\Phi$ explicitly, and the homogenization coefficient $K$ is given by
-\begin{equation}
-	K = \frac{L^2}{Z\widehat Z},
-\end{equation}
-where
-\begin{equation}
-	Z = \int_0^L e^{-p(y)/\sigma} \dd y, \quad \widehat Z = \int_0^L e^{p(y)/\sigma} \dd y.
-\end{equation}}
-We now briefly present the classical methodology for estimating the drift coefficient.
-Let $T > 0$ and let $X^\epl \defeq (X^\epl_t, 0\leq t \leq T)$ be a realization of the solution of \eqref{eq:SDE_MS} up to final time.
-Girsanov's change of measure formula applied to \eqref{eq:SDE_HOM} allows to write the likelihood of $X^\epl$ given a drift coefficient $A$ as
-\begin{equation}\label{eq:Likelihood}
-p(X^\epl \mid A) = \exp\left(-\frac{I(X^\epl\mid A)}{2\Sigma} \right), 
-\end{equation}
-where 
-\begin{equation}
-I(X^\epl \mid A) = \int_0^T A \cdot V'(X^\epl_t) \dd X^\epl_t + \frac12 \int_0^T \left( A \cdot V'(X^\epl_t) \right)^2 \dd t.
-\end{equation}
-Minimizing the functional $I(X^\epl \mid A)$ with respect to $A$ therefore gives the maximum likelihood estimator (MLE) of $A$, which can be formally computed in closed form as
-\begin{equation}\label{eq:MLE}
-	\widehat A^\epl(T) \defeq \arg \min_{A \in \R^N} I(X^\epl \mid A) = M^{-1}h,
-\end{equation}
-where $M\in\R^{N\times N}$ and $h\in\R^N$ are defined as
-\begin{equation}\label{eq:MandH}
-M = \frac1T \int_0^T V'(X^\epl_t) \otimes V'(X^\epl_t) \dd t, \quad h = \frac1T \int_0^T V'(X^\epl_t) \dd X^\epl_t,
-\end{equation}
-and where $\otimes$ denotes the outer product in $\R^N$.
-Let us now state the assumptions which will be employed throughout the rest of our work.
-In particular, we consider the same dissipative setting as \cite[Assumption 3.1]{PaS07}.
-\begin{assumption}\label{as:regularity} The potentials $p$ and $V$ satisfy
-	\begin{enumerate}
-		\item $p \in \mathcal C^\infty(\R) \cap L^\infty(\R)$ and is $L$-periodic for some $L > 0$,
-		\item\label{as:regularity_diss} $V_i \in \mathcal C^\infty(\R)$ for all $i=1, \ldots, N$ is polynomially bounded from above and bounded from below,  and there exist $a,b > 0$ such that
-		\begin{equation}
-		-\alpha \cdot V'(x) x \leq a - bx^2.
-		\end{equation} 
-		\item $V'$ is Lipschitz continuous, i.e. there exists a constant $C > 0$ such that
-		\begin{equation}
-			\norm{V'(x) - V'(y)}_2 \leq C\abs{x - y},
-		\end{equation} 
-		\item for all $T > 0$, the symmetric matrix $M$ is positive definite and there exists $\bar \lambda > 0$ such that $\lambda_{\min}(M) \geq \bar \lambda$.
-	\end{enumerate}
-\end{assumption}
-
-\corr{
-\begin{remark}\label{rem:regularity_diss} In the following, in particular in the proof of Lemma \ref{lem:ergodicity}, we will employ Assumption \ref{as:regularity}\ref{as:regularity_diss} for the whole drift of the SDE \eqref{eq:SDE_MS}, i.e., the function
-	\begin{equation}
-		V^\epl(x) \defeq \alpha \cdot V(x) - p\left(\frac{x}{\epl}\right).
-	\end{equation}
-	Since $p \in L^\infty$, the assumption above is sufficient for $V^\epl$ to satisfy Assumption \ref{as:regularity}\ref{as:regularity_diss} with different values for $a$ and $b$.
-In particular, if the condition holds for $\alpha \cdot V$ for a given $b > 0$, then one can choose a new value for the same coefficient which is arbitrarily close to the original one for $V^\epl$.
-\end{remark}
-}
-
-Under these assumptions, the MLE given in \eqref{eq:MLE} is indeed the unique minimizer of the likelihood function, as shown in \cite[Theorem 2.4]{PSV09}.
-
-Given the convergence of $X^\epl_t \to X_t$ in the space of continuous stochastic processes, one would expect that the MLE \eqref{eq:MLE} would be asymptotically unbiased for the drift coefficient $A$ of the homogenized equation \eqref{eq:SDE_HOM}.
-Instead, it is possible to prove that in the asymptotic limit for $T \to \infty$ and $\epl \to 0$, the MLE tends to the drift coefficient $\alpha$ of the unhomogenized equation \eqref{eq:SDE_MS}.
-We report here this result, whose proof can be found for the case $N = 1$ in \cite[Theorem 3.4]{PaS07}.
-Let us remark that the proof for $N > 1$ follows directly from the one-dimensional case.
-
-\begin{theorem}\label{thm:Bias} Let Assumption \ref{as:regularity} hold and let $X^\epl_0$ be distributed according to the invariant measure of the process $X^\epl$ solution of \eqref{eq:SDE_MS}. Then
-	\begin{equation}
-		\lim_{\epl \to 0}\lim_{T \to \infty} \widehat A^\epl(T) = \alpha, \quad \text{a.s.},
-	\end{equation}
-	where $\alpha$ is the drift coefficient of equation \eqref{eq:SDE_MS}.
-\end{theorem}
-
-As anticipated in the introduction, the main tool for obtaining unbiased estimators in the literature is subsampling the data.
-In particular, let the dimension of the parameter $N = 1$, let $\delta > 0$ and let $T = n\delta$ with $n$ a positive integer.
-Then, a subsampled estimator for $A$ is given by
-\begin{equation}
-	\widehat A^\epl_\delta(T) = - \frac{\sum_{j=0}^{n-1} V'(X^\epl_{j\delta})\left(X^\epl_{(j+1)\delta} - X^\epl_{j\delta}\right)}{\delta \sum_{j=0}^{n-1} V'(X^\epl_{j\delta})^2},
-\end{equation}
-which is a discretized version of $\widehat A^\epl(T)$.
-It is possible to show \cite[Theorem 3.5]{PaS07} that choosing $\delta = \epl^\zeta$ with $\zeta \in (0, 1)$ and if $T$ is sufficiently big, then $\widehat A^\epl_\delta(T)$ is an asymptotically unbiased estimator of $A$ with respect to $T \to \infty$ and $\epl \to 0$, in probability.
-Despite being widely employed in practice, estimators based on subsampling present some drawbacks, as discussed in the introduction.
-In the following, we will introduce and analyse a novel approach for the drift estimation.
-
-\begin{remark} Let us remark that for enhancing the clarity of the exposition, in this article we chose to focus on the case of a multi-dimensional parameter in the setting of one-dimensional diffusion processes.
-In fact, all the theory we present in the following could be generalized to the case of $d$-dimensional SDEs equivalent to \eqref{eq:SDE_MS}, which can be written as
-	\begin{equation}
-		\d X_t^\epl = - \sum_{i=1}^N \alpha_i \nabla V_i(X_t^\epl) \dd t - \frac1\epl \nabla p\left(\frac{X_t^\epl}{\epl}\right) \dd t + \sqrt{2\sigma} \dd W_t,
-	\end{equation}
-	where $W_t$ is a standard $d$-dimensional Brownian motion. The proof of all results below should be slightly modified, but we verified that all arguments still hold true in the $d$-dimensional case. 
-\end{remark}
-
-\section{The filtering approach}\label{sec:Filter}
-
-In this section, we introduce and analyse a novel filtering approach to solve the biasedness issue highlighted by Theorem \ref{thm:Bias}.
-Let $\beta, \delta > 0$ and let us consider a family of exponential kernel functions $k \colon \R^+ \to \R$ defined as
-\begin{equation}\label{eq:filter}
-k(r) = C_\beta \delta^{-1/\beta} e^{-r^\beta/\delta},
-\end{equation}
-where $C_{\beta}$ is a normalizing constant given by
-\begin{equation}
-C_\beta = \beta \, \Gamma(1/\beta)^{-1},
-\end{equation}
-and where $\Gamma(\cdot)$ is the gamma function. We consider the process $Z^\epl \defeq (Z^\epl_t, 0 \leq t \leq T)$ defined by the weighted average
-\begin{equation}\label{eq:ZDef}
-	Z^{\epl}_t \defeq \int_0^t k(t - s)X^\epl_s \dd s.
-\end{equation}
-The process $Z^\epl$ can be interpreted as a smoothed version of the original trajectory $X^\epl$.
-In fact, in the field of signal processing the kernel \eqref{eq:filter} belongs to the class of low-pass linear time-invariant filters, which cut the high frequencies in a signal to highlight its slowest components.
-In the following, only in case $\beta = 1$ a rigorous analysis is carried on.
-Nonetheless, numerical experiments show that for higher values of $\beta$ the performances of estimators computed employing the filter are more robust and qualitatively better.
-
-\begin{remark} Given a trajectory $X^\epl$, it is relatively inexpensive to compute $Z^\epl$ from a computational standpoint.
-In particular, the process $Z^\epl$ is the truncated convolution of the kernel with the process $X^\epl$.
-Hence, computational tools based on the Fast Fourier Transform (FFT) exist and allow to compute $Z^\epl$ fast component-wise.
-Moreover, the process $Z^\epl$ can be computed, in case $\beta = 1$, in a recursive manner and therefore ``online''.
-\end{remark}
-
-In the rest of this section we will focus on the properties of the process $Z^\epl$ when it is considered together with the original process $X^\epl$.
-In particular, we focus on ergodic properties and multiscale convergence.
-Finally, we present and analyse unbiased estimators obtained with the filtering process.
-
-\subsection{Ergodic properties of the filter}\label{sec:ergodic}
-
-Let us consider the filtering kernel \eqref{eq:filter} with $\beta = 1$, i.e.,
-\begin{equation}\label{eq:filter_beta1}
-	k(r) = \frac{1}{\delta} e^{-r/\delta}.
-\end{equation}
-In this case, Leibniz integral rule yields the equality
-\begin{equation}
-	\d Z^\epl_t = k(0) X^\epl_t \dd t + \int_0^t k'(t-s) X^\epl_s \dd s \dd t = \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t,
-\end{equation}
-which can be interpreted as an ordinary differential equation for $Z_t^\epl$ driven by the stochastic signal $X^\epl$.
-Considering the processes $X^\epl$ and $Z^\epl$ together, we obtain the system of two one-dimensional SDEs
-\begin{equation}
-\label{eq:systemSDE}
-\begin{aligned}
-\d X_t^\epl &= -\alpha \cdot V'(X_t^\epl) \dd t - \frac1\epl p'\left(\frac{X_t^\epl}\epl\right) \dd t+ \sqrt{2\sigma} \dd W_t, \\
-\d Z^\epl_t &= \frac{1}{\delta} \left ( X^\epl_t - Z^\epl_t \right ) \dd t.
-\end{aligned}
-\end{equation}
-The first ingredient for verifying the ergodic properties of the two-dimensional process $(X^\epl, Z^\epl)^\top \defeq ((X^\epl_t, Z^\epl_t)^\top, 0 \leq t \leq T)$ is verifying that the measure induced by the stochastic process admits a smooth density with respect to the Lebesgue measure.
-Since noise is present only on the first component, this is a consequence of the theory of hypo-ellipticity, as summarized in the following Lemma, \corr{whose proof is given in Appendix \ref{ap:Proofs}.}
-
-\begin{lemma}\label{lem:density} Let $(X^\epl, Z^\epl)^\top$ be the solution of \eqref{eq:systemSDE} and let $\mu^\epl_t$ be the measure induced by the couple at time $t$.
-Then, the measure $\mu^\epl_t$ admits a smooth density $\rho^\epl_t$ with respect to the Lebesgue measure.
-\end{lemma}
-
-Once it is established that the law of the process admits a smooth density for all times $t>0$, which satisfies a time-dependent Fokker--Planck equation, we are interested in the limiting properties of this law.
-In particular, we know that the process $X^\epl$ alone is geometrically ergodic \cite[Theorem 4.4]{MSH02}, and we wish the couple $(X^\epl, Z^\epl)^\top$ to be endowed with the same property.
-The following Lemma guarantees that the couple is indeed geometrically ergodic, \corr{and its proof is given in Appendix \ref{ap:Proofs}.}
-
-\begin{lemma}\label{lem:ergodicity} Let Assumption \ref{as:regularity} hold and let $b > 0$ be given in Assumption \ref{as:regularity}\ref{as:regularity_diss}.
-Then, if $\delta > 1/(4b)$, the process $(X^\epl, Z^\epl)^\top$ solution of \eqref{eq:systemSDE} is geometrically ergodic, i.e., there exists $C, \lambda > 0$ such that for all measurable $f\colon \R^2\to \R$ such that for some integer $q > 0$
-	\begin{equation}
-		f(x, z) \leq 1 + \norm{\begin{pmatrix} x & z \end{pmatrix}^\top}_2^q,
-	\end{equation}
-	it holds
-	\begin{equation}
-		\abs{\E f(X^\epl_t, Z^\epl_t) - \int_\R\int_\R f(x, z) \rho^\epl(x, z) \dd x \dd z} \leq C\left(1 + \norm{\begin{pmatrix} X^\epl_0 & Z^\epl_0 \end{pmatrix}^\top}_2^q \right)e^{-\lambda t},
-	\end{equation}
-	where $\E$ denotes expectation with respect to the Wiener measure and $\rho^\epl$ is the solution to the stationary Fokker--Planck equation
-	\begin{equation}
-	\label{eq:FPsystem}
-	\sigma \partial^2_{xx} \rho^\epl(x,z) +  \partial_x \left( \left( \alpha \cdot V'(x) + \frac{1}{\epl} p' \left ( \frac{x}\epl \right ) \right ) \rho^\epl(x,z) \right) + \frac{1}{\delta} \partial_z \left((z - x) \rho^\epl(x,z)\right) = 0.
-	\end{equation}
-\end{lemma}
-
-\begin{remark} The condition $\delta > 1 / (4b)$ is not very restrictive.
-Let the parameter dimension $N = 1$ and let $V(x) \propto x^{2p}$ for an integer $p > 1$.
-Then, Assumption \ref{as:regularity}\ref{as:regularity_diss} holds for an arbitrarily large $b > 0$.
-Therefore, the parameter of the filter $\delta$ can be chosen along the entire positive real axis.
-A similar argument can be employed for higher dimensions $N > 1$.
-\end{remark}
-
-\begin{example}\label{ex:OrnUhl} A closed form solution of \eqref{eq:FPsystem} can be obtained in a simple homogenized case with the dimension of the parameter $N=1$.
-Let $p(y) = 0$ and the parameters $\alpha$, $\sigma$ be replaced respectively by $A$ and $\Sigma$.
-Then, if $V(x) = x^2/2$, equation \eqref{eq:FPsystem} has the analytical solution
-\begin{equation}
-\rho^0(x,z) = \frac{1}{C_{\rho^0}} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right),
-\end{equation}
-where
-\begin{equation}
-C_{\rho^0} = \int_{\R} \int_{\R} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right) \dd x \dd z.
-\end{equation}
-This is the density of a multivariate normal distribution $\mathcal N(0, \Gamma)$, where the covariance matrix is given by
-\begin{equation}
-\Gamma = \frac{\Sigma}{A (1 + A\delta)} \begin{pmatrix} 1+A\delta & 1 \\ 1 & 1 \end{pmatrix}.
-\end{equation}
-Let us remark that this distribution can be obtained from direct computations involving Gaussian processes.
-In particular, it is known that $X \sim \mathcal{GP}(\mu_t, \mathcal C(t, s))$, where at stationarity $\mu_t = 0$ and
-\begin{equation}
-	\mathcal C(t, s) = \frac{\Sigma}{A} e^{-A|t-s|}.
-\end{equation}
-The basic properties of Gaussian processes imply that $Z$ is a Gaussian process, and that the couple $(X, Z)^\top$ is a Gaussian process, too, whose mean and covariance are computable explicitly.
-\end{example}
-
-In a general case, it is not possible to find an explicit solution to \eqref{eq:FPsystem}.
-Nevertheless, it is possible to show some relevant properties of the solution itself, which are summarized in the following Lemma, \corr{whose proof is given in Appendix \ref{ap:Proofs}.}
-
-\begin{lemma}\label{lem:FPMarginal} Under the assumptions of Lemma \ref{lem:ergodicity}, let $\rho^\epl$ be the solution of \eqref{eq:FPsystem} and let us write 
-\begin{equation}\label{eq:densityDecomposition}
-	\rho^\epl(x, z) = \phi^\epl(x)\psi^\epl(z)R^\epl(x,z),
-\end{equation}
-where $\phi^\epl$ and $\psi^\epl$ are the marginal densities of $X^\epl$ and $Z^\epl$ respectively, i.e., 
-\begin{equation}
-	\phi^\epl(x) = \int_{\R} \rho^\epl(x,z) \dd z, \quad  \psi^\epl(z) = \int_{\R} \rho^\epl(x,z) \dd x.
-\end{equation}
-Then, it holds
-\begin{equation}\label{eq:marginalX}
-	\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(-\frac{1}{\sigma} \alpha \cdot V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
-\end{equation}
-where
-\begin{equation}
-	C_{\phi^\epl} = \int_{\R} \exp\left(-\frac{1}{\sigma} \alpha \cdot V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right) \dd x.
-\end{equation}
-Moreover, it holds
-\begin{equation}
-	\sigma \delta \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)].
-\end{equation}
-\end{lemma}
-
-\subsection{Multiscale convergence}\label{sec:convMS}
-
-We now investigate the convergence of the couple $(X^\epl, Z^\epl)^\top$ with respect to the multiscale parameter $\epl \to 0$.
-In particular, it is known that the invariant measure of $X^\epl$ converges weakly to the invariant measure of $X$ solution of the homogenized equation \eqref{eq:SDE_HOM}.
-The following result, \corr{whose proof is given in Appendix \ref{ap:Proofs},} guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.
-
-\begin{lemma}\label{lem:convMeasure} Under Assumption \ref{as:regularity}, let $\mu^\epl$ be the invariant measure of the couple $(X^\epl, Z^\epl)^\top$ and let $(X_0^\epl, Z_0^\epl)^\top \sim \mu^\epl$.
-Then, the measure $\mu^\epl$ converges weakly to the measure $\mu^0(\d x, \d z) = \rho^0(x, z) \dd x \dd z$, whose density $\rho^0$ is the unique solution of the Fokker--Planck equation
-\begin{equation} \label{eq:FPsystem_homogenized}
-	\Sigma \partial^2_{xx} \rho^0(x,z) + \partial_x\left( A \cdot V'(x) \rho^0(x,z) \right) + \frac{1}{\delta}\partial_z\left((z - x) \rho^0(x,z) \right) = 0,
-\end{equation}
-where $A$ and $\Sigma$ are the coefficients of the homogenized equation \eqref{eq:SDE_HOM}.
-\end{lemma}
-
-We conclude this section presenting an analogous result to Lemma \ref{lem:FPMarginal} for the limit distribution.
-
-\begin{corollary}\label{lem:FPMarginal_Hom} Let $\rho^0$ be the solution of \eqref{eq:FPsystem_homogenized} and let us write 
-	\begin{equation}
-		\rho^0(x, z) = \phi^0(x)\psi^0(z)R^0(x,z),
-	\end{equation}
-	where $\phi^0$ and $\psi^0$ are the marginal densities, i.e., 
-	\begin{equation}
-		\phi^0(x) = \int_{\R} \rho^0(x,z) \dd z, \quad \psi^0(z) = \int_{\R} \rho^0(x,z) \dd x.
-	\end{equation}
-	Then, if $A$ and $\Sigma$ are the coefficients of the homogenized equation \eqref{eq:SDE_HOM}, it holds
-	\begin{equation}
-		\phi^0(x) = \frac{1}{C_{\phi^0}} \exp\left(- \frac1{\Sigma} A\cdot V(x)\right), \quad \text{where } \quad C_{\phi^0} = \int_{\R} \exp\left(- \frac1{\Sigma} A\cdot V(x) \right) \dd x.
-	\end{equation}
-	Moreover, it holds
-	\begin{equation}
-		\Sigma \delta \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z = \E^{\rho^0}[(X^2 - Z^2)V''(Z)].
-	\end{equation}
-\end{corollary}
-\begin{proof} The proof is directly obtained from Lemma \ref{lem:FPMarginal} replacing $p(y)=0$ and $\alpha, \sigma$ by $A, \Sigma$ respectively. 
-\end{proof}
-
-\subsection{The filtering-based estimator}\label{sec:FilterMLE}
-
-We now consider the inference problem and propose our filtering-based estimator of the drift, which is formally given by the formula
-\begin{equation}\label{eq:AHatMixed}
-	\widehat A^\epl_k(T) = - \widetilde M^{-1} \widetilde h,
-\end{equation}
-where we employ the subscript $k$ for reference to the filter's kernel in \eqref{eq:filter}, and where
-\begin{equation}\label{eq:MandHTilde}
-	\widetilde M = \frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t, \qquad \text{and} \qquad \widetilde h = \frac{1}{T} \int_0^T V'(Z^\epl_t) \dd X^\epl_t.
-\end{equation}
-Let us remark that the formula above is obtained from \eqref{eq:MLE} by replacing only one instance of $X_t^\epl$ with $Z_t^\epl$ in both $M$ and $h$.
-In particular, it is fundamental for proving unbiasedness to keep in the definition of $h$ the differential of the original process $\d X^\epl_t$.
-Let us furthermore remark that $\widehat A^\epl_k(T)$ need not be the minimizer of some filtering-based likelihood function.
-In fact, if one were to replace $Z_t^\epl$ directly in \eqref{eq:Likelihood}, the symmetric part of the matrix $\widetilde M$ would appear and $\widehat A^\epl_k(T)$ would not be the minimizer.
-Therefore, the estimator $\widehat A^\epl_k(T)$ has to be thought of as a perturbation of $\widehat A^\epl(T)$, directly at the level of estimators and after the maximization procedure.
-The only theoretical guarantee which is still needed for the well-posedness of $\widehat A^\epl_k(T)$ is for $\widetilde M$ to be invertible, which we assume to be true and which we observed to hold in practice.
-
-%\begin{lemma}\label{lem:AHatWellPosed} Under Assumption \ref{as:regularity}, the matrix $\widetilde M$ defined in \eqref{eq:MandHTilde} is invertible a.s. 
-%\end{lemma}
-%\begin{proof} 
-%\todo: \corr{Idea.
-We don't need $\widetilde M$ to be symmetric positive definite (it is not) due to the comment just above the lemma.
-Nevertheless, if the functions $V_i'(x)$ are not such that the rows of $\widetilde M$ are identical for any $(X_t, Z_t)$, then the randomness in the entries should guarantee that $\det \widetilde M \neq 0$ with probability one.
-Still missing the (probably trivial) argument why this is true.}
-%\end{proof}
-
-We are now able to present the main result of unbiasedness of the filtering-based estimator.
-\begin{theorem}\label{thm:mainTheorem} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, and let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed}.
-If $\widetilde M$ is invertible, then
-	\begin{equation}
-	\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A_k^\epl(T) = A, \quad \text{a.s.},
-	\end{equation}
-	where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.
-\end{theorem}
-
-\begin{proof} Replacing the expression of $\d X^\epl_t$ into \eqref{eq:MandHTilde}, we get for $\widetilde h$
-\begin{equation}\label{Ahat_decomposition}
-\widetilde h = -\widetilde M \alpha - \frac{1}{T} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t + \frac{\sqrt{2\sigma}}{T} \int_0^T V'(Z^\epl_t) \dd W_t.
-\end{equation}
-Therefore, we have
-\begin{equation}\label{eq:alphaDecomposition}
-\begin{aligned}
-	\widehat A^\epl_k(T) &= \alpha + \frac{1}{T} \widetilde M^{-1} \int_0^T \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t) \dd t - \frac{\sqrt{2\sigma}}{T}  \widetilde M^{-1} \int_0^T V'(Z^\epl_t) \dd W_t\\
-	&\eqdef \alpha + I_1^\epl(T) - I_2^\epl(T).
-\end{aligned}
-\end{equation}
-We study the terms $I_1^\epl(T)$ and $I_2^\epl(T)$ separately. The ergodic theorem applied to $I_1^\epl(T)$ yields
-\begin{equation}\label{limit_estimator}
-\lim_{T \to \infty} I_1^\epl(T) = \E^{\rho^\epl} [V'(Z^\epl) \otimes V'(X^\epl)]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ], \quad \text{a.s.}
-\end{equation}
-Due to Lemma \ref{lem:FPMarginal} and integrating by parts, we have
-\begin{equation}
-\begin{aligned}
-	\E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] &= \int_{\R} \int_{\R} V'(z) \, \frac1\epl p' \left ( \frac{x}\epl \right ) \frac{1}{C_{\phi^\epl}} e^{- \frac{1}{\sigma} \alpha \cdot V(x)} e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \psi^\epl(z) R^\epl(x,z) \dd x \dd z \\
-	&= -\sigma \int_{\R} \int_{\R} \frac{\d}{\d x}\left( e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \right) \frac{1}{C_{\phi^\epl}} e^{- \frac{1}{\sigma} \alpha \cdot V(x)} V'(z) \psi^\epl(z) R^\epl(x,z) \dd x \dd z \\
-	&= \sigma \int_{\R} \int_{\R} \frac{1}{C_{\phi^\epl}} e^{ - \frac{1}{\sigma} p \left ( \frac{x}\epl \right)} \partial_x \left ( e^{- \frac{1}{\sigma} \alpha \cdot V(x)} R^\epl(x,z) \right ) V'(z) \psi^\epl(z) \dd x \dd z,
-\end{aligned}
-\end{equation}
-which implies
-\begin{align}
-	\E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] &= 
-	\begin{aligned}[t]
-		&- \left(\int_{\R} \int_{\R} V'(z) \otimes V'(x) \rho^\epl(x, z) \dd x \dd z\right) \alpha \\
-		&+\sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z 
-	\end{aligned}
-	\\
-	&= -  \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]\alpha + \sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z.
-\end{align}
-Replacing the equality above into \eqref{limit_estimator}, we obtain
-\begin{equation}
-\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z, \quad \text{a.s.}
-\end{equation}
-Due to Lemma \ref{lem:FPMarginal}, we therefore have
-\begin{equation}
-	\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)], \quad \text{a.s.}	
-\end{equation}
-We now pass to the limit as $\epl$ goes to zero and
-\begin{equation} \label{limit_estimator_2}
-	\lim_{\epl \to 0} \lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X^2 - Z^2)V''(Z)], \quad \text{a.s.},
-\end{equation}
-where the function $\rho^0$ is the density of the limit invariant distribution for $\epl \to 0$, as in Lemma \ref{lem:convMeasure}. Due to Corollary \ref{lem:FPMarginal_Hom}, we have
-\begin{equation}\label{eq:final_result}
-	\frac{1}{\delta} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] = \Sigma \int_{\R} \int_{\R} V'(z) \phi^0(x) \psi^0(z) \partial_x R^0(x,z) \dd x \dd z,
-\end{equation}
-and moreover, an integration by parts yields
-\begin{equation}
-\begin{aligned}
-	\frac{1}{\delta} \E^{\rho^0}[(X^2 - Z^2)V''(Z)] &= -\Sigma \int_{\R} \int_{\R} V'(z) (\phi^0)'(x) \psi^0(z) R^0(x,z) \dd x \dd z\\
-	&= -\Sigma \int_{\R} \int_{\R} V'(z) \frac{\d}{\d x} \left ( \frac{1}{C_{\phi^0}} e^{-\frac{1}{\Sigma} A\cdot V(x)} \right ) \psi^0(z) R^0(x,z) \dd x \dd z \\
-	&= \left(\int_{\R} \int_{\R} V'(z) \otimes V'(x) \rho^0(x,z) \dd x \dd z\right)A\\
-	&=  \E^{\rho^0} [ V'(Z) \otimes V'(X) ]A.
-\end{aligned}
-\end{equation}
-We can therefore conclude that
-\begin{equation}\label{eq:Proof_I1}
-\lim_{\epl \to 0} \lim_{T \to \infty} I_1^\epl(T) = -\alpha + A, \quad \text{a.s.}
-\end{equation}
-We now consider the second term $I_2^\epl(T)$, and rewrite it as
-\begin{equation}
-	I^\epl_2(T) = \sqrt{2\sigma} I_{2,1}^\epl(T)  I_{2,2}^\epl(T),
-\end{equation}
-where
-\begin{equation}
-\begin{aligned}
-	I_{2,1}^\epl(T) &\defeq \left(\frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\left(\frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t\right),\\
-	I_{2,2}^\epl(T) &\defeq \left(\frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t\right)^{-1} \left(\frac1T \int_0^T V'(Z^\epl_t) \dd W_t\right).
-\end{aligned}
-\end{equation}
-The ergodic theorem yields
-\begin{equation}
-	\lim_{T \to \infty} I_{2,1}^\epl(T) = \E^{\rho^\epl}\left[V'(Z^\epl) \otimes V'(X^\epl)\right]^{-1}\E^{\rho^\epl}\left[V'(Z^\epl) \otimes V'(Z^\epl)\right] \eqdef R^\epl,
-\end{equation}
-where $R^\epl$ is bounded uniformly in $\epl$. Moreover, the strong law of large numbers for martingales implies
-\begin{equation}
-	\lim_{T \to \infty} I_{2,2}^\epl(T) = 0, \quad \text{a.s.},
-\end{equation}
-independently of $\epl$. Therefore
-\begin{equation}
-	\lim_{\epl \to 0}\lim_{T \to \infty} I_2^\epl(T) = 0, \quad \text{a.s.},
-\end{equation}
-which, together with \eqref{eq:Proof_I1} and \eqref{eq:alphaDecomposition}, proves the desired result.
-\end{proof}
 
@@
 }
-\section{The Bayesian setting}\label{sec:Bayesian}
-
-In this section we present a Bayesian reinterpretation of the inference procedure, which, given the structure of the problem, allows to get at a full uncertainty quantification with a low computational effort.
-
-Let us fix a Gaussian prior $\mu_0 = \mathcal N(A_0, C_0)$ on $A$, where $A_0 \in \R^N$ and $C_0 \in \R^{N\times N}$ is symmetric positive definite.
-Then, given a final time $T > 0$, the posterior distribution $\mu_{T,\epl}$ admits a density $p(A \mid X^\epl)$ with respect to the Lebesgue measure which satisfies
-\begin{equation}
-p(A \mid X^\epl) = \frac1{Z^\epl} \, p(X^\epl \mid A) \, p_0(A),
-\end{equation}
-where $Z^\epl$ is the normalization constant, $p_0$ is the density of $\mu_0$, and where the likelihood $p(X^\epl \mid A)$ is given in \eqref{eq:Likelihood}.
-The log-posterior density is therefore given by
-\begin{equation}\label{eq:Posterior}
-\log p(A \mid X^\epl) = -\log Z^\epl - \frac{T}{2\Sigma} A \cdot h - \frac{T}{4\Sigma} A \cdot M A - \frac12 (A - A_0) \cdot C_0^{-1}(A-A_0),
-\end{equation}
-where $M$ and $h$ are defined in \eqref{eq:MandH}.
-Since the log-posterior density is quadratic in $A$, the posterior is Gaussian, and it is therefore sufficient to determine its mean and covariance to fully characterize it.
-We denote by $m_{T,\epl}$ and $C_{T,\epl}$ the mean and covariance matrix, respectively.
-Completing the squares in the log-posterior density, we formally obtain
-\begin{equation}
-\begin{aligned}
-C_{T,\epl}^{-1} &= C_0^{-1} + \frac{T}{2\Sigma} M, \\
-C_{T,\epl}^{-1}m_{T,\epl} &= C_0^{-1}A_0 - \frac{T}{2\Sigma} h. 
-\end{aligned}
-\end{equation}
-Under Assumption \ref{as:regularity}, one can show that the posterior at time $T > 0$ is indeed given by $\mu_{T,\epl} = \mathcal N(m_{T,\epl}, C_{T,\epl})$.
-We are now interested in the asymptotic limit of the posterior distribution for $T \to \infty$ and for $\epl \to 0$.
-
-We can now state the main result for asymptotic convergence of the posterior distribution.
-\begin{theorem}\label{thm:BayesianBias} Under Assumption \ref{as:regularity}, the posterior measure $\mu_{T,\epl} = \mathcal N(m_{T,\epl}, C_{T,\epl})$ satisfies
-	\begin{equation}
-		\lim_{\epl \to 0}\lim_{T \to \infty} \mu_{T,\epl}(\cdot) = \delta(\cdot - \alpha), \quad \text{a.s.},
-	\end{equation}
-	weakly in the space of probability measures on $\R^N$, where $\delta$ is the Dirac measure on $\R^N$.
-\end{theorem}
-\begin{proof} Let us first consider the covariance matrix. Hua's identity yields
-	\begin{equation}
-	C_{T,\epl} = \frac{2\Sigma}{T} \left(M^{-1} - Q^{-1}\right),
-	\end{equation}
-	where 
-	\begin{equation}
-	Q = M + \frac{T}{2\Sigma} M C_0 M.
-	\end{equation}
-	Let us first remark that due to the hypothesis on $M$ and the ergodic theorem it holds for all $T > 0$
-	\begin{equation}
-		\norm{M^{-1}}_2 \leq \frac1{\bar \lambda}.
-	\end{equation}
-	We now have that for generic symmetric positive definite matrices $R$ and $S$ it holds
-	\begin{equation}
-		\norm{(R+S)^{-1}}_2 \leq \norm{S^{-1}}_2.
-	\end{equation}
-	Applying this inequality to $Q^{-1}$, we obtain
-	\begin{equation}
-		\norm{Q^{-1}}_2 \leq \frac{2\Sigma}T \norm{(MC_0M)^{-1}}_2 \leq \frac{2\Sigma}T \norm{M^{-1}}_2^2 \norm{C_0^{-1}}_2 = \frac{2\Sigma}{T\bar \lambda^2} \norm{C_0^{-1}}_2,
-	\end{equation}
-	which implies
-	\begin{equation}
-		\lim_{T \to \infty}\norm{Q^{-1}}_2 = 0,
-	\end{equation}
-	and due to the triangle inequality
-	\begin{equation}\label{eq:CovarianceShrink}
-		\lim_{T \to \infty}\norm{C_{T,\epl}}_2 = 0.
-	\end{equation}
-	We proved that in the limit for $T \to \infty$ the covariance shrinks to zero independently of $\epl$. We now consider the mean. First, we remark that the triangle inequality yields
-	\begin{equation}
-		\norm{m_{T,\epl} - \alpha}_2 \leq \norm{m_{T,\epl} - \widehat A^\epl(T)}_2 + \norm{\widehat A^\epl(T) - \alpha}_2.
-	\end{equation}
-	For the second term, Theorem \ref{thm:Bias} implies 
-	\begin{equation}
-		\lim_{\epl \to 0} \lim_{T \to \infty}\norm{\widehat A^\epl(T) - \alpha}_2 = 0, \quad \text{a.s.}
-	\end{equation}
-	Let us now consider the first term.	Replacing the expression of the maximum likelihood estimator \eqref{eq:MLE} and due to the Cauchy--Schwarz and triangle inequalities, we obtain
-	\begin{equation}
-	\begin{aligned}
-		\norm{m_{T,\epl} - \widehat A^\epl(T)}_2 &= \frac{2\Sigma}T\norm{M^{-1}C_0^{-1}A_0 - Q^{-1}\left(C_0^{-1}A_0 - \frac{T}{2\Sigma} h \right)}_2\\
-		&\leq \frac{2\Sigma}{T\bar \lambda} \norm{C_0^{-1}}_2 \left(\norm{A_0}_2 + \frac1{\bar \lambda}\norm{h}_2 + \frac{2\Sigma}{T\bar \lambda} \norm{C_0^{-1}}_2\norm{A_0}_2\right).
-	\end{aligned}
-	\end{equation}
-	Moreover, the ergodic theorem and the strong law of large numbers for martingales guarantee that $\norm{h}_2$ is bounded a.s. for $T \to \infty$. Therefore
-	\begin{equation}
-	\lim_{T\to\infty} \norm{m_{T,\epl} - \widehat A^\epl(T)}_2 = 0, \quad \text{a.s.},
-	\end{equation}
-	independently of $\epl$. Finally, 
-	\begin{equation}
-		\lim_{\epl \to 0} \lim_{T \to \infty}\norm{m_{T,\epl} - \alpha}_2 = 0, \quad \text{a.s.},
-	\end{equation}
-	which, together with \eqref{eq:CovarianceShrink}, implies the desired result. 
-\end{proof}
-
-\begin{remark} The result above has the same consequences in the Bayesian setting as Theorem \ref{thm:Bias} has for the MLE.
-In particular, it shows that the posterior distribution obtained when data is not pre-processed concentrates asymptotically on the drift coefficient of the unhomogenized equation \eqref{eq:SDE_MS}.
-Moreover, a partial result which can be deduced from the proof is that in the limit for $T \to \infty$ and for a positive value $\epl > 0$ the Bayesian and the MLE approaches are equivalent.
-In particular, we have for all $\epl > 0$
-	\begin{equation}
-	\begin{aligned}
-		&\lim_{T\to\infty} \norm{C_{T,\epl}}_2 = 0,\\
-		&\lim_{T \to\infty}\norm{m_{T,\epl} - \widehat A^\epl(T)}_2 =0,
-	\end{aligned}	
-	\end{equation} 
-	i.e., the weak limit of the posterior $\mu_{T,\epl}$ for $T\to \infty$ is the Dirac delta concentrated on the limit of $\widehat A^\epl(T)$ for $T\to \infty$. 
-\end{remark}
-
-\subsection{The filtering approach}\label{sec:BayesianFilter}
-
-In this section, we present how to correct the faulty behaviour highlighted by Theorem \ref{thm:BayesianBias} with filtering techniques.
-Employing the filter in the same way as for the MLE, we can modify the likelihood function and obtain
-\begin{equation}
-	\widehat p(X^\epl \mid A) = \exp\left(-\frac{\widehat I(X^\epl\mid A)}{2\Sigma} \right), 
-\end{equation}
-where 
-\begin{equation}
-\begin{aligned}
-	\widehat I(X^\epl \mid A) & = \int_0^T A \cdot V'(Z^\epl_t) \dd X^\epl_t + \frac12 \int_0^T \left(A \cdot V'(X^\epl_t)\right)\left(A \cdot V'(Z^\epl_t)\right) \dd t \\
-	&= \widetilde h \cdot A + \frac12 A \cdot \widetilde M A.
-\end{aligned}
-\end{equation}
-Let us remark that $\widetilde M$ is not symmetric. Nevertheless, we have that
-\begin{equation}
-	A \cdot \widetilde M A = A \cdot \widetilde M_S A,
-\end{equation}
-where $\widetilde M_S$ is the symmetric part of $\widetilde M$.
-Repeating the same reasoning as above, one would therefore obtain a modified posterior $\widehat \mu_{T, \epl} = \mathcal N(\widehat m_{T, \epl}, \widehat C_{T, \epl})$, whose covariance matrix and mean would be given by
-\begin{equation}
-\begin{aligned}
-	\widehat C_{T, \epl}^{-1} &= C_0^{-1} + \frac{T}{2\Sigma} \widetilde M_S, \\
-	\widehat C_{T,\epl}^{-1}\widehat m_{T,\epl} &= C_0^{-1}A_0 - \frac{T}{2\Sigma} \widetilde h. 
-\end{aligned}	
-\end{equation}
-There is no guarantee under Assumption \ref{as:regularity} that $\widehat C_{T, \epl}$ is positive define and therefore a covariance matrix.
-Hence, in this Bayesian setting, we consider a different modification of the likelihood where we perturb only the vector $h$, i.e.,
-\begin{equation}
-	\widetilde p(X^\epl \mid A) = \exp\left(-\frac{\widetilde I(X^\epl\mid A)}{2\Sigma} \right), 
-\end{equation}
-where 
-\begin{equation}
-\begin{aligned}
-	\widetilde I(X^\epl \mid A) & = \int_0^T A \cdot V'(Z^\epl_t) \dd X^\epl_t + \frac12 \int_0^T \left(A \cdot V'(X^\epl_t)\right)^2 \dd t \\
-	&= \widetilde h \cdot A + \frac12 A \cdot M A.
-\end{aligned}
-\end{equation}
-so that we obtain the modified posterior $\widetilde \mu_{T,\epl} = \mathcal N(\widetilde m_{T, \epl}, C_{T, \epl})$, whose parameters are given by
-\begin{equation}
-\begin{aligned}
-	C_{T, \epl}^{-1} &= C_0^{-1} + \frac{T}{2\Sigma} M, \\
-	C_{T,\epl}^{-1}\widetilde m_{T,\epl} &= C_0^{-1}A_0 - \frac{T}{2\Sigma} \widetilde h. 
-\end{aligned}	
-\end{equation}
-Let us remark that the posterior $\widetilde \mu_{T,\epl}$ has the same covariance as $\mu_{T,\epl}$ and that therefore it is indeed a valid Gaussian posterior distribution.
-Nevertheless, in order to employ the tool of convergence introduced in Theorem \ref{thm:BayesianBias}, we need to study the properties of the MLE based on the likelihood $\widetilde p(X^\epl \mid A)$, i.e., the quantity
-\begin{equation}\label{eq:AHatMixedTilde}
-	\widetilde A^\epl_k(T) = - M^{-1} \widetilde h.
-\end{equation}
-The following theorem guarantees the unbiasedness of this estimator under a condition on the parameter $\delta$ of the filter, and we refer to Appendix \ref{ap:EstimatorTilde} for its proof.
-\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold.
-Then, if $\delta$ in \eqref{eq:filter} satisfies $\delta = \delta(\epl)$ with $\delta(\epl) \to 0$ for $\epl \to 0$, it holds
-	\begin{equation}
-	\lim_{\epl \to 0} \lim_{T \to \infty} \widetilde A^\epl_k(T) = A, \quad \text{a.s.},
-	\end{equation} 
-	for $\widetilde A^\epl_k(T)$ defined in \eqref{eq:AHatMixedTilde}.
-\end{theorem}
-
-The following result gives the convergence of the modified posterior distribution $\widetilde \mu_{T, \epl}$ to the drift coefficient of the homogenized equation.
-\begin{theorem} Let the Assumptions of Theorem \ref{thm:mainTheoremTilde} hold. Then, the modified posterior measure $\widetilde\mu_{T,\epl} = \mathcal N(\widetilde m_{T,\epl}, C_{T,\epl})$ satisfies
-	\begin{equation}
-	\lim_{\epl \to 0}\lim_{T \to \infty} \widetilde \mu_{T,\epl}(\cdot) = \delta(\cdot - A), \quad \text{a.s.},
-	\end{equation}
-	weakly in the space of probability measures on $\R^N$, where $\delta$ is the Dirac measure on $\R^N$.
-\end{theorem}
-\begin{proof} The proof follows from the proof of Theorem \ref{thm:BayesianBias} and from Theorem \ref{thm:mainTheoremTilde}.
-\end{proof}
-
-\section{Numerical experiments}\label{sec:NumExp}
-
-In this section we show numerical experiments confirming our theoretical findings and showing the potentiality of the filtering approach.
-
-\subsection{Parameters of the filter}\label{sec:Num_Param}
-\begin{figure}[t]
-	\centering
-	\begin{tabular}{ccc}
-		\includegraphics[]{Figures/OUSubs_s5} & \includegraphics[]{Figures/OUFilt_s5_b1}  & \includegraphics[]{Figures/OUFilt_s5_b5} \\ % & \includegraphics[]{Figures/OUFilt_s5_b10} \\
-		\includegraphics[]{Figures/OUSubs_s7} & \includegraphics[]{Figures/OUFilt_s7_b1}  & \includegraphics[]{Figures/OUFilt_s7_b5} \\ % & \includegraphics[]{Figures/OUFilt_s7_b10} \\
-		\includegraphics[]{Figures/OUSubs_s10} & \includegraphics[]{Figures/OUFilt_s10_b1}  & \includegraphics[]{Figures/OUFilt_s10_b5} % & \includegraphics[]{Figures/OUFilt_s10_b10}
-	\end{tabular}
-	\caption{Results for the Ornstein--Uhlenbeck process.
-The axis of abscissae $\zeta$ represents the value of $\delta = \epl^\zeta$ for both subsampling and the filter.
-The three rows correspond to $\sigma = 0.5, 0.7, 1.0$ from top to bottom.}
-	\label{fig:OU}
-\end{figure}
-We consider $N = 1$ and the quadratic potential $V(x) = x^2/2$.
-In this case, the solution of the homogenized equation is an Ornstein--Uhlenbeck process.
-Moreover, we set the multiscale equation \eqref{eq:SDE_MS} with $\epl = 0.1$ and the fast potential $p(y) = \cos(y)$.
-We generate data $X^\epl$ for $0 \leq t \leq T$ and $T = 10^3$ employing the Euler--Maruyama method with time step $\Delta_t = \epl^3$.
-
-As a first experiment, we consider the effect of setting different values of the parameter $\delta$ of the filter \eqref{eq:filter} on the estimator.
-As a comparison and for similarity with the subsampling approach, we consider $\delta = \epl^{\zeta}$ and vary $\zeta \in [0, 1]$.
-We employ the same values of $\delta$ for the subsampling, too, as the theoretical results guarantee convergence only for these values.
-Moreover, we repeat the experiments fixing $\beta = 1, 5$ and for three different values of the diffusion, i.e., we choose $\sigma = 0.5, 0.7, 1$.
-We report in Figure \ref{fig:OU} the experimental results.
-Let us remark that
-\begin{enumerate}
-	\item for $\sigma = 0.5$ the results given by subsampling and by the filter with $\beta = 1$ are similar, while for higher values of $\sigma$ the filtering approach seems better than subsampling, 
-	\item in general, choosing a higher value of $\beta$ seems beneficial for the quality of the estimator,
-	\item the dependence on $\delta$ of numerical results given by the filter seems relevant only in case $\beta = 1$ and for small values of $\sigma$.
-For $\beta = 1$ and higher values of $\sigma$, the estimator is stable with respect to this parameter, as predicted in Theorem \ref{thm:mainTheorem}.
-This can be observed for a higher value of $\beta$ but we have no theoretical guarantee in this case.
-\end{enumerate}
-
-As a second experiment, we therefore test the variability of the estimator with respect to $\beta$ in \eqref{eq:filter}.
-We repeat the numerical experiment in Figure \ref{fig:OU} and we choose to consider $\delta = \epl$, which corresponds to $\zeta = 1$ and seems to be the worst-case scenario for the filter, at least for $\beta = 1$.
-We consider again $\sigma = 0.5, 0.7, 1$ and vary $\beta = 1, 2, \ldots, 10$.
-Results, given in Figure \ref{fig:OUBeta}, show empirically that the estimator is fast stable with respect to $\beta$.
-
-\begin{figure}[t]
-	\centering
-	\begin{tabular}{ccc}
-		\includegraphics[]{Figures/OUBeta_s5} & \includegraphics[]{Figures/OUBeta_s7}  & \includegraphics[]{Figures/OUBeta_s10} \\
-	\end{tabular}
-	\caption{Dependence of the estimator given by the filter for the Ornstein--Uhlenbeck process on the parameter $\beta$ in \eqref{eq:filter}.
-From left to right we consider different values of $\sigma$.}
-	\label{fig:OUBeta}
-\end{figure}
 
@@
 	\centering
-	\includegraphics[]{Figures/CLT}
+	\includegraphics[]{../Figures/CLT}
 	\caption{Central limit theorem result.
@@
 Results, depicted in Figure \ref{fig:CLT}, show that the distribution of $\Delta_A^\epl(T)$ indeed follows a zero-mean Gaussian law, \corr{whose covariance agrees with the theoretical results (?)}.
-
-\subsection{Multi-dimensional drift coefficient}
-
-\begin{figure}[t]
-	\centering
-	\begin{tabular}{ccc}
-		\includegraphics[]{Figures/KLNothing} & \includegraphics[]{Figures/KLFilt}  & \includegraphics[]{Figures/KLSubs}
-	\end{tabular}
-	\caption{Results for the four-dimensional parameter. From left to right the potential function estimated with the data itself, the filter, subsampled data.}
-	\label{fig:KLStyle}
-\end{figure}
-
-\begin{table}[t]
-	\centering
-	\begin{tabular}{cccccc}
-		\toprule
-		Coefficient & Multiscale & Homogenized & No preprocessing  & Filtering  		  & Subsampling  			 \\ 
-		& $\alpha$ & $A$   & $\widehat A^\epl$ & $\widehat A^\epl_k$ & $\widehat A^\epl_\delta$ \\
-		\midrule
-		$1$ &-1   & -0.62 & -0.92 & -0.70 & -0.59\\
-		$2$ &-0.5 & -0.31 & -0.70 & -0.27 & 0.05 \\
-		$3$ & 0.5 & 0.31  & 0.55  & 0.31  & 0.14 \\
-		$4$ & 1   & 0.62  & 1.22  & 0.57  & 0.13 \\
-		\bottomrule
-	\end{tabular}
-	\caption{Numerical results for the four-dimensional parameter.}
-	\label{tab:KLStyle}
-\end{table}
-
-Let us consider the Chebyshev polynomials of the first kind, i.e., the polynomials $T_i\colon \R \to \R$, $i=0, 1, \ldots$, defined by the recurrence relation
-\begin{equation}
-T_0(x) = 1, \quad T_1(x) = x, \quad T_{i+1}(x) = 2xT_i(x) - T_{i-1}(x).
-\end{equation}
-We consider the potential function $V(x)$ as in \eqref{eq:Potential} with
-\begin{equation}
-V_i(x) = T_i(x), \quad i =1, \ldots, 4.
-\end{equation}
-This potential function satisfies Assumption \ref{as:regularity} whenever $N$ is even and if the leading coefficient $\alpha_N$ is positive.
-We set $N = 4$ and the drift coefficient $\alpha = (-1, -1/2, 1/2, 1)$.
-With this drift coefficient, the potential function is of the bistable kind.
-Moreover, we set $\epl = 0.05$, the diffusion coefficient $\sigma = 1$, the fast potential $p(y) = \cos(y)$ and simulate a trajectory of $X^\epl$ for $0 \leq t \leq T$ with $T = 10^3$ employing the Euler--Maruyama method with time step $\Delta_t = \epl^3$.
-We estimate the drift coefficient $A \in \R^4$ with the estimators
-\begin{enumerate}
-	\item $\widehat A^\epl(T)$ based on the data $X^\epl$ itself,
-	\item $\widehat A^\epl_\delta(T)$ based on subsampled data with subsampling parameter $\delta = \epl^{2/3}$,
-	\item $\widehat A^\epl_k(T)$ based on filtered data $Z^\epl$ computed with $\beta = 1$ and $\delta = 1$.
-\end{enumerate}
-In particular, we pick this specific value of $\delta$ for the subsampling following the optimality criterion given in \cite{PaS07}.
-Results, given in Figure \ref{fig:KLStyle} and Table \ref{tab:KLStyle}, show that the filter-based estimation captures well the homogenized potential as well as the coefficient $A$.
-Moreover, it is possible to remark the negative result given by Theorem \ref{thm:Bias} holds in practice, i.e., with no pre-processing the estimator $\widehat A^\epl(T)$ tends to the drift coefficient $\alpha$ of the unhomogenized equation.
-
-\subsection{The Bayesian approach: bistable potential}
-\begin{figure}[t]
-	\centering
-	\begin{tabular}{ccc}
-		\includegraphics[]{Figures/Bayes_T100} & \includegraphics[]{Figures/Bayes_T200}  & \includegraphics[]{Figures/Bayes_T400} \\
-	\end{tabular}
-	\caption{Posterior distributions over the parameter $A = (A_1, A_2)^\top$ for the bistable potential obtained with the filtering approach.
-The figures refer to final time $T = 100, 200, 400$ from left to right, respectively.
-The MLE $\widetilde A^\epl_k(t)$ is represented with a circle, while the true value $A$ of the drift coefficient of the homogenized equation is represented with a cross.}
-	\label{fig:Bayes}
-\end{figure}
-
-In this numerical experiment we consider $N = 2$ and the bistable potential, i.e., the function $V$ defined as
-\begin{equation}
-	V(x) = \begin{pmatrix} \dfrac{x^4}{4} & -\dfrac{x^2}{2} \end{pmatrix}^\top,
-\end{equation}
-with coefficients $\alpha_1 = 1$ and $\alpha_2 = 2$.
-We then consider the multiscale equation with $\sigma = 0.7$, the fast potential $p(y) = \cos(y)$ and $\epl = 0.05$, thus simulating a trajectory $X^\epl$.
-We adopt here a Bayesian approach and compute the posterior distribution $\widetilde \mu_{T, \epl}$ obtained with the filtering approach introduced in Section \ref{sec:BayesianFilter}.
-The parameters of the filter are set to $\beta = 1$ and $\delta = \epl$ in \eqref{eq:filter}.
-Let us remark that in order to compute the posterior covariance the diffusion coefficient $\Sigma$ of the homogenized equation has to be known.
-In this case, we pre-compute the value of $\Sigma$ via the coefficient $K$ and the theory of homogenization, but let us remark that $\Sigma$ could be estimated employing the subsampling technique of \cite{PaS07}.
-We stop computations at times $T = 100, 200, 400$ in order to observe the shrinkage of the Gaussian posterior towards the MLE $\widetilde A^\epl_k(T)$ with respect to time.
-In Figure \ref{fig:Bayes}, we observe that the posterior does indeed shrink towards the MLE, which in turn gets progressively closer to the true value of the drift coefficient $A$ of the homogenized equation.
-
-\section{Conclusion}
-
-In this work we considered a novel methodology based on filtering for the estimation of the drift of multiscale diffusion processes.
-We proved results of ergodicity, convergence and, most importantly, unbiasedness of estimators drawn from our methodology.
-Moreover, we combined a Bayesian approach and our new technique to guarantee a robust uncertainty quantification of the inference procedure.
-Numerical experiments demonstrate how the filtering-based estimator requires less knowledge of the characteristic time-scales of the multiscale equation and how it can be employed as a black-box tool for parameter estimation on a range of academic examples.
-We believe this work gives way to several further developments.
-In particular, we believe it would be relevant to
-\begin{enumerate}
-	\item analyse the filtering methodology for $\beta > 1$ in \eqref{eq:filter}, which seems to give more robust results in practice,
-	\item extend the analysis to the non-parametric framework most likely by means of Bayesian regularization techniques,
-	\item consider multiscale models for which the homogenized equation presents multiplicative noise,
-	\item test the filtering methodology against real-world data,
-	\item apply similar filtering methodologies to correct faulty behaviour of non likelihood-based estimators.
-\end{enumerate}
-
-\begin{appendices}
-
-\section{Proof of Lemmas}\label{ap:Proofs}
-
-\begin{proof}[Proof of Lemma \ref{lem:density}] We have to show that the joint process solution to \eqref{eq:systemSDE} is hypo-elliptic. Denoting as $f\colon \R \to \R$ the function 
-	\begin{equation}
-	f(x) = -\alpha \cdot V'(x) - \frac1\epl p'\left(\frac{x}\epl\right),
-	\end{equation}
-	the generator of the process $(X^\epl, Z^\epl)^\top$ is given by
-	\begin{equation}
-	\mathcal L = f \partial_x + \sigma \partial_{xx}^2 + \frac1\delta (x - z)\partial_z \eqdef \mathcal X_0 + \sigma \mathcal X_1^2, 
-	\end{equation}
-	where 
-	\begin{equation}
-	\mathcal X_0 = f \partial_x + \frac1\delta (x - z)\partial_z, \quad \mathcal X_1 = \partial_x.
-	\end{equation}
-	The commutator $[\mathcal X_0, \mathcal X_1]$ applied to a test function $v$ then gives
-	\begin{equation}
-	\begin{aligned}
-	[\mathcal X_0, \mathcal X_1]v &= f \partial_x^2 v + \frac1\delta (x - z) \partial_x \partial_z v  - \partial_x\left(f\partial_x v + \frac1\delta (x - z)\partial_z v\right)\\
-	&= -\partial_x f \partial_x v - \frac1\delta \partial_z v.
-	\end{aligned}
-	\end{equation}
-	Consequently, 
-	\begin{equation}
-	\mathrm{Lie}\left(\mathcal X_1, [\mathcal X_0, \mathcal X_1]\right) = \mathrm{Lie} \left(\partial_x, -\partial_x f \partial_x - \frac1\delta\partial_z\right),
-	\end{equation}
-	which spans the tangent space of $\R^2$ at $(x, z)$, denoted $T_{x, z}\R^2$. The desired result then follows from Hörmander's theorem (see e.g. \cite[Chapter 6]{Pav14}).
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{lem:ergodicity}] Lemma \ref{lem:density} guarantees that the Fokker--Planck equation can be written directly from the system \eqref{eq:systemSDE}.
-For geometric ergodicity, let
-	\begin{equation}
-	\mathcal S(x,z) \defeq \begin{pmatrix} -\alpha \cdot V'(x) - \frac1\epl p'(\frac{x}{\epl}) \\ \frac1\delta (x - z) \end{pmatrix} \cdot \begin{pmatrix} x \\ z \end{pmatrix} =  -\left(\alpha \cdot V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)x + \frac1\delta(xz-z^2).
-	\end{equation}
-	Due to Assumption \ref{as:regularity}\ref{as:regularity_diss}, Remark \ref{rem:regularity_diss} and Young's inequality, we then have for all $\gamma > 0$
-	\begin{equation}
-	\mathcal S(x,z) \leq a + \left(\frac{1}{2\gamma\delta} - b\right)x^2 + \frac1\delta\left(\frac{\gamma}{2} - 1\right)z^2.
-	\end{equation}
-	We choose $\gamma = \gamma^* \defeq 1 - b\delta + \sqrt{1 + (1 - b\delta)^2} > 0$ so that
-	\begin{equation}
-	C(\gamma^*) \defeq -\frac{1}{2\gamma^*\delta} + b = -\frac1\delta\left(\frac{\gamma^*}{2} - 1\right),
-	\end{equation}
-	and we notice that $C(\gamma^*) > 0$ if $\delta > 1/(4b)$. In this case, we have
-	\begin{equation}
-	\mathcal S(x, z) \leq a - C(\gamma^*) \norm{\begin{pmatrix} x & z \end{pmatrix}^\top}^2,
-	\end{equation}
-	and problem \eqref{eq:systemSDE} is dissipative. The result then follows from \cite[Theorem 4.4]{MSH02}.
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{lem:FPMarginal}] Integrating equation \eqref{eq:FPsystem} with respect to $z$ we obtain the stationary Fokker--Planck equation for the process $X^\epl$, i.e.
-	\begin{equation}
-	\label{FPx}
-	\sigma (\phi^\epl)''(x) + \frac{\d}{\d x} \left( \left ( \alpha \cdot V'(x) + \frac{1}{\epl} p' \left ( \frac{x}\epl \right ) \right ) \phi^\epl(x)\right) = 0,
-	\end{equation}
-	whose solution is given by
-	\begin{equation}
-	\phi^\epl(x) = \frac{1}{C_{\phi^\epl}} \exp\left(- \frac{1}{\sigma} \alpha \cdot V(x) - \frac{1}{\sigma} p \left ( \frac{x}\epl \right )\right),
-	\end{equation}
-	and which proves \eqref{eq:marginalX}. By integrating equation \eqref{eq:FPsystem} with respect to $x$ and integrating by parts we obtain
-	\begin{equation}
-	\psi^\epl(z) + z (\psi^\epl)'(z) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x,
-	\end{equation}
-	which can be written as
-	\begin{equation}
-	\frac{\d}{\d z} (z \psi^\epl(z)) = \frac{\d}{\d z} \int_{\R} x \rho^\epl(x,z) \dd x.
-	\end{equation}
-	Now, since $\psi^\epl$ is the density of a probability distribution, this implies that 
-	\begin{equation}\label{FPz}
-	z \psi^\epl(z) = \int_{\R} x \rho^\epl(x,z) \dd x,
-	\end{equation}
-	which, replacing the decomposition \eqref{eq:densityDecomposition}, yields
-	\begin{equation} \label{eq:z_condition}
-	z = \int_{\R} x \phi^\epl(x) R^\epl(x,z) \dd x.
-	\end{equation}
-	In view of \eqref{eq:densityDecomposition} and \eqref{FPx}, equation \eqref{eq:FPsystem} can be rewritten as
-	\begin{equation}\label{eq:psiEqualityPDE}
-	\sigma \phi^\epl \psi^\epl \partial^2_{xx} R^\epl + \frac{1}{\delta} \phi^\epl \psi^\epl R^\epl + \sigma (\phi^\epl)' \psi^\epl \partial_x R^\epl + \frac{1}{\delta} (z-x) \phi^\epl ((\psi^\epl)' R + \psi^\epl \partial_z R^\epl) = 0.
-	\end{equation}
-	We now multiply the equation above by $x$ and integrate with respect to $x$. Let us consider some simplifications explicitly. First, an integration by parts yields
-	\begin{equation}\label{eq:psiEqualityPDE_1}
-	\begin{aligned}
-	\sigma \psi^\epl \int_{\R}  x \phi^\epl \partial^2_{xx} R^\epl \dd x+ \sigma \psi^\epl \int_{\R} x (\phi^\epl)' \partial_x R^\epl \dd x &= -\sigma \psi^\epl \int_{\R} \phi^\epl \partial_x R^\epl \dd x.
-	\end{aligned}
-	\end{equation}
-	Then, applying \eqref{eq:z_condition}, we have
-	\begin{equation}\label{eq:psiEqualityPDE_2}
-	\frac1\delta \psi^\epl \int_{\R} x \phi^\epl  R^\epl \dd x = \frac1\delta z \psi^\epl.
-	\end{equation}
-	Moreover, again applying \eqref{eq:z_condition}, we can compute
-	\begin{equation}\label{eq:psiEqualityPDE_3}
-	\begin{aligned}
-	\frac1\delta (\psi^\epl)' \int_\R (z-x)x \phi^\epl  R \dd x = \frac1\delta (\psi^\epl)' \left(z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x\right).
-	\end{aligned}
-	\end{equation}
-	Finally, we compute the last term always applying \eqref{eq:z_condition} obtaining
-	\begin{equation}\label{eq:psiEqualityPDE_4}
-	\frac1\delta \psi^\epl \int_\R (z-x)x \phi^\epl \partial_z R \dd x = \frac1\delta \psi^\epl\left(z - \int_{\R} x^2 \phi^\epl \partial_z R^\epl \dd x\right).
-	\end{equation}
-	Replacing the equalities \eqref{eq:psiEqualityPDE_1}, \eqref{eq:psiEqualityPDE_2}, \eqref{eq:psiEqualityPDE_3} and \eqref{eq:psiEqualityPDE_4} into \eqref{eq:psiEqualityPDE} we obtain
-	\begin{equation}
-	(\psi^\epl)' \left ( z^2 - \int_{\R} x^2 \phi^\epl R^\epl \dd x \right ) + \psi^\epl \left ( 2z - \int_{\R} x^2 \phi^\epl \partial_z R^\epl \dd x - \delta \sigma \int_{\R} \phi^\epl \partial_x R^\epl \dd x \right ) = 0.
-	\end{equation}
-	We rewrite the equality above as
-	\begin{equation} \label{eq:psiEquality}
-	\delta \sigma \psi^\epl(z) \int_{\R} \phi^\epl(x) \partial_x R^\epl(x, z) \dd x = 
-	\begin{aligned}[t] &(\psi^\epl)'(z) z^2 - (\psi^\epl)'(z) \int_{\R} x^2 \phi^\epl(x) R^\epl(x, z) \dd x \\
-	& + 2 \psi^\epl(x) z - \psi^\epl \int_{\R} x^2 \phi^\epl(x) \partial_z R^\epl(x, z) \dd x.
-	\end{aligned}
-	\end{equation}
-	Multiplying by $V'(z)$, integrating with respect to $z$ and integrating by parts, we obtain the following identity in $\R^N$
-	\begin{equation}
-	\begin{aligned}
-	\sigma \delta \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z &=  \int_{\R} \int_{\R} (x^2 - z^2) V''(z) \rho_\epl(x,z) \dd x \dd z \\
-	&= \E^{\rho^\epl}[((X^\epl)^2 - (Z^\epl)^2)V''(Z^\epl)],
-	\end{aligned}
-	\end{equation}
-	which is the desired result.
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{lem:convMeasure}] Let $(X, Z)^\top \defeq \left((X_t, Z_t)^\top, 0\leq t \leq T\right)$ be the solution of
-	\begin{equation}
-	\label{eq:systemSDEHom}
-	\begin{aligned}
-	\d X_t &= -A \cdot V'(X_t) \dd t + \sqrt{2\Sigma} \dd W_t, \\
-	\d Z_t &= \frac{1}{\delta} \left ( X_t - Z_t \right ) \dd t,
-	\end{aligned}
-	\end{equation} 
-	with $(X_0, Z_0)^\top \sim \mu^0$.
-The arguments of Section \ref{sec:ergodic} can be repeated to conclude that the invariant measure of $(X, Z)^\top$ admits a smooth density $\rho^0$ which satisfies \eqref{eq:FPsystem_homogenized}.
-Moreover, standard homogenization theory (see e.g.
-\cite[Chapter 3]{BLP78}) guarantees that $(X^\epl,Z^\epl)^\top \to (X,Z)^\top$ for $\epl \to 0$ in law as random variables with values in $\mathcal C^0([0, T]; \R^2)$.
-The Portmanteau theorem can be employed to conclude that the measure $\mu^\epl$ converges weakly to $\mu^0$ for $\epl \to 0$.
-\end{proof}
 
@@
 
-\section{Proof of Theorem \ref{thm:mainTheoremTilde}}\label{ap:EstimatorTilde}
-Let us consider the estimator defined in \eqref{eq:AHatMixedTilde}, that is
-\begin{equation}
-	\widetilde A^\epl_k(T) = -M^{-1}\widetilde h,
-\end{equation}
-where the matrix $M$ is taken from \eqref{eq:MandH} and the vector $\widetilde{h}$ is taken from \eqref{eq:MandHTilde}.
-We prove here Theorem \ref{thm:mainTheoremTilde}, i.e., the unbiasedness of this estimator, for which it is necessary to prove two technical lemmas.
-Let us start with an estimate concerning the distance between $X^\epl$ and $Z^\epl$.
-
-\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
-Then, if $\delta \leq 1$, it holds for any integer $p \geq 1$
-	\begin{equation}
-	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
-	\end{equation}
-	for a constant $C > 0$ independent of $\epl$ and $\delta$.
-\end{lemma}
-\begin{proof} Let us first remark that the filtering kernel satisfies
-	\begin{equation}\label{eq:filterIntegral}
-	\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta},
-	\end{equation}
-	which implies that the measure $\kappa_t(\d s)$ on $(0, t)$ defined as
-	\begin{equation}
-	\kappa_t(\d s) \defeq \frac{k(t-s)}{1 - e^{-t/\delta}} \dd s,
-	\end{equation}
-	is a probability measure.
-Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$.
-Let $Z_t^\epl$ be the corresponding filtered process.
-By definition of $Z^\epl_t$ and due \eqref{eq:filterIntegral} we now have
-	\begin{equation}
-	\begin{aligned}
-	X_t^\epl - Z_t^\epl &= X_t^\epl - \int_0^t k(t-s) X_s^\epl \dd s\\
-	&= \int_0^t k(t - s) \left(X_t^\epl - X_s^\epl\right) \dd s + e^{-t/\delta} X^\epl_t\\
-	&= (1 - e^{-t/\delta})\int_0^t \left(X_t^\epl - X_s^\epl\right) \kappa_t(\d s) + e^{-t/\delta} X^\epl_t.
-	\end{aligned}
-	\end{equation}
-	Therefore, Jensen's inequalities yields for a constant $C > 0$ depending only on $p$
-	\begin{equation}
-	\begin{aligned}
-	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} &\leq C (1 - e^{-t/\delta})^{2p} \int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} \kappa_t (\d s) + C e^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p}\\
-	&\leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} k(t-s) \dd s + Ce^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p},
-	\end{aligned}
-	\end{equation}
-	where we replaced the definition of $\kappa(\d s)$ and exploited the fact that $1 - e^{-t/\delta}\leq 1$ for all $t \geq 0$.
-Due to \cite[Corollary 5.4]{PaS07}, we know that $X^\epl_t$ has bounded moments of all orders with respect to its invariant measure.
-Moreover, the estimate
-	\begin{equation}
-	\E^{\phi^\epl}\abs{X_t^\epl - X_s^\epl}^{2p} \leq C\left(\epl^{2p} + (t-s)^{2p} + (t-s)^p\right),
-	\end{equation}
-	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}. Finally, it is possible to verify by induction on $r$ that for all integers $r$ it holds
-	\begin{equation}
-	\int_0^t k(t-s) (t - s)^r \dd s \leq r! \, \delta^r, 
-	\end{equation}
-	which implies that there exists a constant $C > 0$ depending only on $p$ such that
-	\begin{equation}
-	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p + e^{-2pt/\delta}\right).
-	\end{equation}
-	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
-In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$
-	\begin{equation}
-	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} + Ce^{-\lambda t},
-	\end{equation}
-	which, for $t$ sufficiently big, yields
-	\begin{equation}
-	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
-	\end{equation}
-	which is the desired result.
-\end{proof}
-
-Let us consider a couple $(X^\epl, Z^\epl)^\top$. In the following, we will adopt the notation
-\begin{equation}\label{eq:CalM}
-\mathcal M = \E^{\rho^\epl}[V'(X^\epl) \otimes V'(X^\epl)] \quad \text{and} \quad \widetilde{\mathcal M} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)],
-\end{equation}
-which due to the ergodic theorem satisfy
-\begin{equation}
-\lim_{T \to \infty} M = \mathcal M, \quad \text{and} \quad \lim_{T \to \infty} \widetilde M = \mathcal{\widetilde M},
-\end{equation}
-almost surely. In the following Lemma, we consider the difference between the two matrices $\mathcal M$ and $\widetilde{\mathcal M}$.
-
-\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Lemma \ref{lem:distanceZandX} hold. Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}$ defined in \eqref{eq:CalM} satisfy
-	\begin{equation}
-	\norm{\mathcal M - \widetilde{\mathcal M}}_2 \leq C\left(\epl + \delta^{1/2}\right),
-	\end{equation}
-	for a constant $C > 0$ independent of $\epl$ and $\delta$.
-\end{lemma}
-\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
-	\begin{equation}
-	\begin{aligned}
-	\norm{\mathcal M - \widetilde{\mathcal M}}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
-	&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
-	\end{aligned}
-	\end{equation}
-	The Lipschitz condition on $V$ together with the boundedness of the moments of $X^\epl$ and Lemma \ref{lem:distanceZandX} yield for a constant $C > 0$
-	\begin{equation}
-	\begin{aligned}
-	\norm{\mathcal M - \widetilde{\mathcal M}}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
-	\end{aligned}
-	\end{equation}
-	which is the desired result.
-\end{proof}
-
-We can finally prove the unbiasedness of the estimator $\widetilde A^\epl_k(T)$.
-
-\begin{proof}[Proof of Theorem \ref{thm:mainTheoremTilde}] We first consider the difference between the two estimators $\widetilde A^\epl_k(T)$ and $\widehat A^\epl_k(T)$.
-In particular, the ergodic theorem and an algebraic equality imply
-	\begin{equation}
-	\begin{aligned}
-	\lim_{T \to \infty} \left(\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)\right) &= \left(\mathcal M^{-1} - \widetilde{\mathcal M}^{-1}\right) \lim_{T \to \infty}\widetilde h \\
-	&= \mathcal M^{-1}\left(\mathcal M - \widetilde{\mathcal M}\right)  \widetilde{\mathcal M}^{-1} \lim_{T \to \infty} \widetilde h\\
-	&= \mathcal M^{-1}\left(\mathcal M - \widetilde{\mathcal M}\right)\lim_{T \to \infty} \widehat A^\epl_k(T),
-	\end{aligned}
-	\end{equation}
-	almost surely. Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
-	\begin{equation}\label{eq:DistATildeAHat}
-	\lim_{T \to \infty} \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 \leq C \left(\epl + \delta^{1/2} \right).
-	\end{equation}
-	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem}. Now, the triangle inequality yields
-	\begin{equation}
-	\norm{\widetilde A^\epl_k(T) - A}_2 \leq \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 + \norm{\widehat A^\epl_k(T) - A}_2.
-	\end{equation}
-	Therefore, due to Theorem \ref{thm:mainTheorem}, the inequality \eqref{eq:DistATildeAHat} and since $\delta \to 0$ for $\epl \to 0$, the desired result holds.
-\end{proof}
-
-\end{appendices}
-
-\bibliographystyle{siam}
-\bibliography{anmc}
 \end{document}

### 2020-03-20 CalNotes.tex
update delta=eps power

@@
 \end{theorem}}
-
-\subsection{Central limit theorem}
-
-\corr{Text to be added with motivation, proof in Appendix \ref{ap:CLT}.
-\begin{theorem}\label{thm:CLT} Central limit theorem statement:
-	\begin{equation}
-		\lim_{\epl \to 0}\lim_{T \to \infty} \sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \Lambda, \quad \text{in law,}
-	\end{equation}
-	where $\Lambda \sim \mathcal N(0, \Gamma)$ and
-	\begin{equation}
-		\Gamma = 2\sigma \E^{\rho^0}[V'(Z) \otimes V'(X)]^{-1}\E^{\rho^0}[V'(Z) \otimes V'(Z)]\E^{\rho^0}[V'(X) \otimes V'(Z)]^{-1}.
-	\end{equation}
-	This covariance may not be correct (see proof in the Appendix) but it is just the limit of the ``third term'' 
-\end{theorem}
-}
 
@@
 
-\subsection{Central limit theorem}
-\begin{figure}[t]
-	\centering
-	\includegraphics[]{Figures/CLT}
-	\caption{Central limit theorem result.
-The histogram represents numerical results, the solid curve a Gaussian fit to the latter and the dashed curve the theoretical estimate given in Theorem \ref{thm:CLT}.}
-	\label{fig:CLT}
-\end{figure}
-
-In this experiment we wish to confirm the validity of Theorem \ref{thm:CLT}.
-We consider the same test equation as for Section \ref{sec:Num_Param}, i.e., the quadratic potential $V(x) = x^2/2$ with fluctuating potential $p(y) = \sin(y)$, multiscale parameter $\epl = 0.05$ and diffusion coefficient $\sigma = 1$.
-The parameters of the filter are set to $\beta = 1$ and $\delta = 1$.
-We compute the estimator $\widehat A^\epl_k(T)$ with final time $T = 10^3$ on $2000$ realizations of the solution and estimate the quantity
-\begin{equation}	
-	\Delta_A^\epl(T) \defeq \sqrt{T}\left(\widehat A^\epl_k(T) - A\right),	
-\end{equation}
-where $A$ is the drift coefficient of the homogenized equation.
-Results, depicted in Figure \ref{fig:CLT}, show that the distribution of $\Delta_A^\epl(T)$ indeed follows a zero-mean Gaussian law, \corr{whose covariance agrees with the theoretical results (?)}.
-
 \subsection{Multi-dimensional drift coefficient}
@@
 
-\section{Proof of Theorem \ref{thm:mainTheorem_zeta}} \label{ap:zeta}
-
-\begin{lemma} \label{lem:zeta}
-	For $\epl,\delta>0$ sufficiently small and $t>0$ sufficiently big, there exists a standard Brownian motion $B_t$ independent of the processes $X_t$ and $Z_t$ such that
-	\begin{equation}
-	X_t^\epl - Z_t^\epl = \sqrt{2\Sigma}\delta \int_0^t k(t-s) \dd B_s + R(\epl,\delta),
-	\end{equation}
-	in law. The remainder $R(\epl,\delta)$ satisfies, for every $p > 0$ and $\iota \in (0,1/2)$, the estimate
+\section{Estimates on the filtered solution}
+
+In this section, we prove a series of results which quantify the distance between the multiscale solution $X_t^\epl$ and the filtered trajectory $Z_t^\epl$.
+First, we prove a Jensen-like inequality for the kernel of the filter.
+
+\begin{lemma}\label{lem:FilterJensen} Let $\delta > 0$ and $k(r)$ be defined as
+	\begin{equation}
+		k(r) = \frac1\delta e^{-r/\delta}.
+	\end{equation}
+	Then, for any $t > 0$, $p \geq 0$ and any function $g\in \mathcal C^0(0, t)$ it holds 
+	\begin{equation}
+		\abs{\int_0^t k(t-s) g(s) \dd s}^p \leq (1 - e^{-t/\delta})^{p-1}\int_0^t k(t-s) \abs{g(s)}^p \dd s.
+	\end{equation}
+	Moreover, if $p \geq 1$ and since $0 < (1-e^{-t/\delta}) < 1$ for all $t > 0$, it holds
+	\begin{equation}
+		\abs{\int_0^t k(t-s) g(s) \dd s}^p \leq \int_0^t k(t-s) \abs{g(s)}^p \dd s.
+	\end{equation}
+\end{lemma}
+\begin{proof} Let us first note that
+	\begin{equation}
+		\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta}.
+	\end{equation}
+	Therefore, the measure $\kappa_t(\d s)$ on $(0, t)$ defined as
+	\begin{equation}
+		\kappa_t(\d s) \defeq \frac{k(t-s)}{1 - e^{-t/\delta}} \dd s,
+	\end{equation}
+	is a probability measure. An application of Jensen's inequality therefore yields
+	\begin{equation}
+	\begin{aligned}
+		\abs{\int_0^t k(t-s) g(s) \dd s}^p &\leq (1 - e^{-t/\delta})^p \int_0^t \abs{g(s)}^p \kappa_t(\d s) \\
+		&= (1 - e^{-t/\delta})^{p-1} \int_0^t k(t-s) \abs{g(s)}^p \dd s,
+	\end{aligned}
+	\end{equation}
+	which is the desired result.
+\end{proof}
+
+The following lemma characterizes the action of the filter when it is applied to polynomials.
+\begin{lemma}\label{lem:FilterPoly} With the notation of Lemma \ref{lem:FilterJensen}, it holds for all $p \geq 0$
+	\begin{equation}
+		\int_0^t k(t-s)(t-s)^p \dd s \leq C \delta^p,
+	\end{equation}
+	where $C > 0$ is a positive constant independent of $\delta$.
+\end{lemma}
+\begin{proof} The change of variable $u = (t-s)/\delta$ yields
+	\begin{equation}
+		\int_0^t k(t-s)(t-s)^p \dd s = \delta^p \int_0^{t/\delta} u^p e^{-u} \dd u = \delta^p \gamma\left(p+1, \frac{t}{\delta}\right),
+	\end{equation}
+	where $\gamma$ is the lower incomplete Gamma function, which is bounded by the complete Gamma function $\Gamma(p+1)$ independently of the second argument.
+\end{proof}
+We can now prove a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.
+
+\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
+Then, if $\delta \leq 1$, it holds for any $p \geq 1$
+	\begin{equation}
+		\left(\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p\right)^{1/p} \leq C\left(\epl + \delta^{1/2}\right),
+	\end{equation}
+	for a constant $C > 0$ independent of $\epl$ and $\delta$.
+\end{lemma}
+\begin{proof} Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$.
+Let $Z_t^\epl$ be the corresponding filtered process.
+By definition of $Z^\epl_t$ we have
+	\begin{equation}
+	\begin{aligned}
+		X_t^\epl - Z_t^\epl &= X_t^\epl - \int_0^t k(t-s) X_s^\epl \dd s\\
+		&= \int_0^t k(t - s) \left(X_t^\epl - X_s^\epl\right) \dd s + e^{-t/\delta} X^\epl_t.
+	\end{aligned}
+	\end{equation}
+	Therefore, Lemma \ref{lem:FilterJensen} yields for a constant $C > 0$ depending only on $p$
+	\begin{equation}
+		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^p k(t-s) \dd s + Ce^{-pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^p.
+	\end{equation}
+	Moreover, the estimate
+	\begin{equation}
+		\E^{\phi^\epl}\abs{X_t^\epl - X_s^\epl}^p \leq C\left(\epl^p + (t-s)^p + (t-s)^{p/2}\right),
+	\end{equation}
+	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}.
+Finally, since the moments of $X_t^\epl$ are bounded \cite[Corollary 5.4]{PaS07} and due to Lemma \ref{lem:FilterPoly} there exists a constant $C > 0$ depending only on $p$ such that
+	\begin{equation}
+		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\left(\epl^p + \delta^{p/2} + e^{-pt/\delta}\right).
+	\end{equation}
+	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
+In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$
+	\begin{equation}
+	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + Ce^{-\lambda t},
+	\end{equation}
+	which, for $t$ sufficiently big, yields the desired result.
+\end{proof}
+
+It is relevant to study the quantities
+\begin{equation}\label{eq:CalM}
+\mathcal M_\epl \defeq \E^{\rho^\epl}[V'(X^\epl) \otimes V'(X^\epl)] \quad \text{and} \quad \widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)],
+\end{equation}
+which are by the ergodic theorem the time limit of the matrices appearing in the estimators $\widehat A^\epl(T)$ and $\widehat A^\epl_k(T)$, respectively.
+In particular, the distance between the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ can be bounded, which is summarized in the following lemma.
+
+\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Lemma \ref{lem:distanceZandX} hold.
+Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}_\epl$ defined in \eqref{eq:CalM} satisfy
+	\begin{equation}
+	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 \leq C\left(\epl + \delta^{1/2}\right),
+	\end{equation}
+	for a constant $C > 0$ independent of $\epl$ and $\delta$.
+\end{lemma}
+\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
+	\begin{equation}
+	\begin{aligned}
+	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
+	&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
+	\end{aligned}
+	\end{equation}
+	The Lipschitz condition on $V'$ together with the boundedness of the moments of $X^\epl$ and Lemma \ref{lem:distanceZandX} yield for a constant $C > 0$
+	\begin{equation}
+	\begin{aligned}
+	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
+	\end{aligned}
+	\end{equation}
+	which is the desired result.
+\end{proof}
+
+The final result presented in this section is a sharper quantification of the difference between $X^\epl_t$ and $Z^\epl_t$ than Lemma \ref{lem:distanceZandX}.
+In particular, denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
+\cite[Formula 5.8]{PaS07}
+\begin{equation}\label{eq:App_DiffXtXs}
+\begin{aligned}
+	X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
+	&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r - \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)),
+\end{aligned}
+\end{equation}
+which is obtained applying the Itô formula to $\Phi$, the solution of the cell problem \eqref{eq:CellProblem}.
+
+\begin{lemma} \label{lem:zeta} Let Assumption \ref{as:regularity} hold and $\epl,\delta>0$ be sufficiently small. Then, it holds for every $t > 0$ sufficiently big 
+	\begin{equation}
+		X_t^\epl - Z_t^\epl = \delta \beta^\epl_t + R(\epl,\delta),
+	\end{equation}
+	where the stochastic process $\beta_t^\epl$ is defined as
+	\begin{equation}\label{eq:defBeta}
+		\beta_t^\epl \defeq \sqrt{2\sigma} \int_0^t k(t-s)(1 + \Phi'(Y_s^\epl)) \dd W_s,
+	\end{equation}
+	where $\Phi$ is the solution of the cell problem \eqref{eq:CellProblem}, $W_s$ is the Brownian motion appearing in \eqref{eq:SDE_MS} and $Y_t^\epl = X_t^\epl / \epl$.
+Moreover, the remainder $R(\epl,\delta)$ satisfies for every $p > 0$ the estimate
 	\begin{equation} \label{eq:remainder_zeta}
-		\left( \E^{\rho_\epl} \left| R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta + \epl^\iota + \epl \delta^{1/2} \right),
+	\left( \E^{\rho_\epl} \left| R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta + \epl^2 + \epl \delta^{1/2} \right),
 	\end{equation}
@@
 \end{lemma}
-\begin{proof} Let $t > s$, $\Phi$ solution of \eqref{eq:CellProblem} and $Y_t^\epl = X_t^\epl / \epl$. Then, an application of the Itô formula yields \cite[Formula 5.8]{PaS07}
-	\begin{equation}\label{eq:App_DiffXtXs}
-	\begin{aligned}
-	X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
-	&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r - \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)).
-	\end{aligned}
-	\end{equation}
-	Recall that we have
+\begin{proof} Recall that by definition of $Z_t^\epl$ we have
 	\begin{equation}
@@
 	\end{equation}
-	Plugging \eqref{eq:App_DiffXtXs} into the equation above, we obtain
+	Plugging the decomposition \eqref{eq:App_DiffXtXs} into the equation above, we obtain
 	\begin{equation}
@@
 	\end{equation}
-	in law, where
+	in law, where the remainder $R_1^\epl$ satisfies 
 	\begin{equation}\label{eq:FirstTermPavStu}
@@
 	\end{equation}
-	Therefore, 
+	Therefore, it holds 
 	\begin{equation}\label{eq:Diff_I1}
@@
 	\end{equation}
-	Now, Jensen's inequality with $\kappa(\d s)$ and the inequalities \eqref{eq:FirstTermPavStu} and \eqref{eq:FilterTminusS} yield for all integers $p \geq 1$ and a constant $C$ depending only on $p$
-	\begin{equation}
-	\begin{aligned}
-	\E^{\phi^\epl}\abs{\widetilde R_1^\epl(t)}^{2p} &= (1-e^{-t/\delta})^{2p}\E^{\phi^\epl}\abs{\int_0^t R_1^\epl(t-s) \kappa(\d s)}^{2p}\\
-	&\leq (1-e^{-t/\delta})^{2p} \int_0^t \E^{\phi^\epl} \abs{R_1^\epl(t-s)}^{2p} \kappa(\d s)\\
-	&\leq C (1-e^{-t/\delta})^{2p-1} \int_0^t k(t-s)(\epl^{4p} + \epl^{2p}(t-s)^p+(t-s)^{3p}) \dd s\\
-	&\leq C \left( \epl^{4p} + \epl^{2p} \delta^p + \delta^{3p} \right).
-	\end{aligned}
-	\end{equation}
-	Therefore, for $t$ sufficiently big, we get
-	\begin{equation}
-	\begin{aligned}
-		\left(\E^{\phi^\epl}\abs{I_1^\epl(t)}^{p}\right)^{1/p} \le& C \left( \delta + \epl^2 + \epl \delta^{1/2} + \delta^{3/2} \right) \\
-		\le& C \left( \delta + \epl^2 + \epl \delta^{1/2} \right).
-	\end{aligned}
-	\end{equation}
-	We now consider the second term. Let us remark that it holds \cite[Proposition 5.7, Section 6.2]{PaS07}
-	\begin{equation}
-	\sqrt{2\sigma} \int_s^t \left(1+\Phi'(Y_s^\epl)\right) \dd W_r = \sqrt{2\Sigma}\left( B_t - B_s\right) + R_2^\epl(t-s),
-	\end{equation}
-	in law, where $\Sigma$ is the diffusion coefficient of the homogenized equation \eqref{eq:SDE_HOM}, $B_t$ is a standard Brownian motion \corr{independent of the process $X_t$ (?)} and 
-	\begin{equation}
-	\left(\E^{\phi^\epl}\abs{R_2^\epl(t-s)}^p\right)^{1/p} \leq C\epl^\iota,
-	\end{equation}
-	for all $\iota \in (0, 1/2)$. Therefore, it holds in law
-	\begin{equation} \label{eq:I2_decomposition}
-	I_2^\epl(t) = \sqrt{2\Sigma} \int_0^t k(t-s) \left(B_t - B_s\right) \dd s + \widetilde R_2^\epl(t),
-	\end{equation}
-	where
-	\begin{equation}
-	\widetilde R_2^\epl(t) \defeq \sqrt{2\Sigma} \int_0^t k(t-s) R_2^\epl(t-s) \dd s.
-	\end{equation}
-	Applying Jensen's inequality with $\kappa(\d s)$ we obtain
-	\begin{equation}
-	\left(\E^{\phi^\epl} \abs{\widetilde R_2^\epl(t)}^p\right)^{1/p} \leq C \epl^{\iota}.
-	\end{equation}
-	Let us remark that an application of the Itô formula yields
-	\begin{equation}
-		\dd \left( k(t-s)B_s \right) = \frac1\delta k(t-s)B_s \dd s + k(t-s) \dd B_s,
-	\end{equation}
-	which implies
-	\begin{equation} \label{eq:Ito_kB}
-		\int_0^t k(t-s)B_s \dd s = B_t - \delta \int_0^t k(t-s) \dd B_s.
-	\end{equation}
-	Substituting \eqref{eq:Ito_kB} into \eqref{eq:I2_decomposition} and recalling that
-	\begin{equation}
-		\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta},
-	\end{equation}
-	we obtain
-	\begin{equation}
-		I_2^\epl(t) = \sqrt{2\Sigma} \delta \int_0^t k(t-s) \dd B_s - \sqrt{2\Sigma} e^{-t/\delta} B_t.
-	\end{equation}
-	Moreover note that
-	\begin{equation}
-			\left(\E^{\phi^\epl} \abs{\sqrt{2\Sigma} e^{-t/\delta} B_t}^p\right)^{1/p} \le C e^{-t/\delta}.
-	\end{equation}
-
+	Now, Lemma \ref{lem:FilterJensen}, the inequality \eqref{eq:FirstTermPavStu} and Lemma \ref{lem:FilterPoly} yield for all $p \geq 1$
+	\begin{equation}
+	\begin{aligned}
+		\E^{\phi^\epl}\abs{\widetilde R_1^\epl(t)}^p &\leq C \int_0^t k(t-s)\E^{\phi^\epl} \abs{R_1^\epl(t-s)}^p \dd s\\
+		&\leq C \int_0^t k(t-s)(\epl^{2p} + \epl^p(t-s)^{p/2}+(t-s)^{3p/2}) \dd s\\
+		&\leq C \left( \epl^{2p} + \epl^p \delta^{p/2} + \delta^{3p/2} \right),
+	\end{aligned}
+	\end{equation}
+	where $C$ is a positive constant independent of $\epl$ and $\delta$. Therefore, for $t$ sufficiently big and $\delta$ sufficiently small, we get
+	\begin{equation}
+		\left(\E^{\phi^\epl}\abs{I_1^\epl(t)}^{p}\right)^{1/p} \leq C \left( \delta + \epl^2 + \epl \delta^{1/2} \right).
+	\end{equation}
+	We now consider the second term. Let us introduce the notation  
+	\begin{equation}
+		Q_t \defeq \int_0^t \left(1 + \Phi'(Y_r^\epl)\right) \dd W_r,
+	\end{equation}
+	and therefore rewrite
+	\begin{equation}
+		I_2^\epl(t) = \sqrt{2\sigma} Q_t \int_0^t k(t-s)(Q_t - Q_s) \dd s.
+	\end{equation}
+	An application of the Itô formula to $u(s, Q_s)$ where $u(s, x) = k(t-s)x$ yields
+	\begin{equation}
+	\begin{aligned}
+		I_2^\epl(t) &= \sqrt{2\sigma} \left(Q_t\int_0^t k(t-s) \dd s - Q_t + \delta \int_0^t k(t-s)\left(1 + \Phi'(Y_s^\epl)\right) \dd W_s\right)\\
+		  			&= \delta \beta_t^\epl - \sqrt{2\sigma} e^{-t/\delta} Q_t \eqdef \delta \beta_t^\epl - R_2^\epl(t).
+	\end{aligned}
+	\end{equation}
+	where $\beta_t^\epl$ is defined in \eqref{eq:defBeta}. For the remainder $R_2^\epl(t)$, let us remark that for all $p \geq 1$ it holds
+	\begin{equation}
+	\begin{aligned}
+		\left(\E\abs{Q_t}^p\right)^2 \leq \E\abs{Q_t}^{2p} \leq Ct^{p-1}\int_0^t \E \abs{1 + \Phi'(Y_r^\epl)}^{2p} \dd r \leq C t
+	\end{aligned}
+	\end{equation}
+	where we applied Jensen's inequality, an estimate for the moments of stochastic integrals \cite[Formula (3.25), p. 163]{KaS91} and the boundedness of $\Phi$. Therefore, for $t$ large enough, we have
+	\begin{equation}
+		\E\abs{R_2^\epl(t)}^p \leq C \sqrt{t}e^{-pt/\delta}.
+	\end{equation}
 	Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
@@
 \end{proof}
+
+\corr{
+\begin{remark} Let us remark that one can show for all $p \geq 1$ and a constant $C > 0$ independent of $\delta$
+	\begin{equation}
+		\left(\E\abs{\beta_t^\epl}^p \right)^{1/p} \leq C \delta^{-1/2}.
+	\end{equation}
+	Therefore, the estimate presented in Lemma \ref{lem:zeta} is consistent with the rough estimate of Lemma \ref{lem:distanceZandX}, and the term highlighted in the statement of Lemma \ref{lem:zeta} is indeed the dominating term in terms of powers of $\delta$.
+\end{remark}
+}
+
+\section{Proof of Theorem \ref{thm:mainTheorem_zeta}} \label{ap:zeta}
 
@@
 	\begin{aligned}
-		J_1^\epl(t) &= 2\Sigma\delta \E^{\rho^\epl} \left[ \left( \int_0^t k(t-s) \dd B_s \right)^2 V''(Z_t^\epl) \right], \\
-		J_2^\epl(t) &= 2\sqrt{2\Sigma} \E^{\rho^\epl} \left[ \left( \int_0^t k(t-s) \dd B_s \right) R(\epl,\delta) V''(Z_t^\epl) \right], \\
-		J_3^\epl(t) &= \frac1\delta \E^{\rho^\epl} \left[ R(\epl,\delta)^2 V''(Z_t^\epl) \right].
+		J_1^\epl(t) &= 2\Sigma\delta \E \left[ \left( \int_0^t k(t-s) \dd B_s \right)^2 V''(Z_t^\epl) \right], \\
+		J_2^\epl(t) &= 2\sqrt{2\Sigma} \E \left[ \left( \int_0^t k(t-s) \dd B_s \right) R(\epl,\delta) V''(Z_t^\epl) \right], \\
+		J_3^\epl(t) &= \frac1\delta \E\left[ R(\epl,\delta)^2 V''(Z_t^\epl) \right].
 	\end{aligned}
@@
 	\begin{equation}
-	J_1^\epl(t) = 2\Sigma\delta \left( \int_0^t k(t-s)^2 \dd s \right) \E [V''(Z_t^\epl)] = \Sigma \E^{\rho^\epl} [V''(Z_t^\epl)],
+	J_1^\epl(t) = 2\Sigma\delta \left( \int_0^t k(t-s)^2 \dd s \right) \E [V''(Z_t^\epl)] = \Sigma \E [V''(Z_t^\epl)],
 	\end{equation}
@@
 
-\section{Proof of Theorem \ref{thm:CLT}}\label{ap:CLT}
-
-Let us first introduce a technical Lemma.
-\begin{lemma}\label{lem:CLT} Let $\mathcal L_\epl$ be the generator of the couple $(X^\epl, Z^\epl)^\top$, i.e.,
-	\begin{equation}
-		\mathcal L_\epl = -\left(\alpha \cdot V'(x) + \frac1\epl p'\left(\frac{x}{\epl}\right)\right)\partial_x + \frac1\delta (x - z) \partial_z  + \sigma \partial^2_{xx}.
-	\end{equation} 
-	Moreover, let $\rho^\epl$ be the density of the invariant measure of $(X^\epl, Z^\epl)^\top$ and $u^\epl\colon \R^2 \to \R^N$ be the solution of 
-	\begin{equation}\label{eq:CLT_Poisson}
-		-\mathcal L_\epl u^\epl = \chi^\epl -  \E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)],
-	\end{equation}
-	satisfying $\E^{\rho^\epl}[u^\epl(X^\epl, Z^\epl)] = 0$ for $\chi^\epl \colon \R^2 \to \R^N$. Then, it holds
-	\begin{equation}\label{eq:CLT_PoissonIto}
-		\frac{1}{T} \int_0^T  \chi^\epl(X_t^\epl, Z_t^\epl) \dd t = \E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)] - \frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T},
-	\end{equation}
-	where
-	\begin{equation}\label{eq:CLT_PoissonRemainders}
-		R^\epl(T) \defeq u^\epl(X^\epl_T, Z^\epl_T) - u^\epl(X^\epl_0, Z^\epl_0), \quad S^\epl(T) \defeq \int_0^T \partial_x u^\epl(X_t^\epl, Z_t^\epl) \dd W_t.
-	\end{equation}
-	Moreover, it holds
-	\begin{equation}\label{eq:CLT_Equiv}
-		2\sigma \E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)] = \E^{\rho^\epl}
-		\begin{aligned}[t]
-		[&\chi^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl) \\
-		&+ u^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)].
-		\end{aligned}
-	\end{equation}	
-\end{lemma}
-\begin{proof} The proof of \eqref{eq:CLT_PoissonIto} and \eqref{eq:CLT_PoissonRemainders} is an application of the Itô formula (see e.g.
-\cite[Remark 6.17]{PaS08}).
-For \eqref{eq:CLT_Equiv}, it is possible to show that since $\mathcal L_\epl^*\rho^\epl = 0$ it holds
-	\begin{equation}
-		\mathcal L_\epl^* (u^\epl \rho^\epl) = 2 \sigma \rho^\epl \partial_{xx}^2 u^\epl - \rho^\epl \mathcal L_\epl u^\epl + 2 \sigma \partial_x u^\epl \partial_x \rho^\epl.
-	\end{equation}
-	Therefore, an integration by parts yields 
-	\begin{equation}
-	\begin{aligned}
-		\E^{\rho^\epl}[\mathcal L_\epl u^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl)] &= 	\int_{\R}\int_{\R} u^\epl \otimes \mathcal L_\epl^*\left(u^\epl \rho^\epl\right) \dd x \dd z \\
-		&= -\int_{\R}\int_{\R}u^\epl \otimes \mathcal L_\epl u^\epl \rho^\epl \dd x \dd z- 2\sigma \int_{\R}\int_{\R} \partial_x u^\epl \otimes \partial_x u^\epl \rho^\epl \dd x \dd z\\
-		&= 
-		\begin{aligned}[t]
-		&-\E^{\rho^\epl}[u^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl u^\epl(X^\epl, Z^\epl)] \\
-		&- 2\sigma \E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)].
-		\end{aligned}
-	\end{aligned}
-	\end{equation}
-	Finally, since $\E^{\rho^\epl}[u(X^\epl, Z^\epl)] = 0$ 
-	\begin{equation}
-	\begin{aligned}
-		2\sigma \E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)] &= -\E^{\rho^\epl}
-		\begin{aligned}[t]
-		[&\mathcal L_\epl u^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl) \\
-		& + u^\epl(X^\epl, Z^\epl) \otimes \mathcal L_\epl u^\epl(X^\epl, Z^\epl)]
-		\end{aligned}
-		\\
-		&= \E^{\rho^\epl}
-		\begin{aligned}[t]
-		[&\chi^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl) \\
-		&+ u^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl)],
-		\end{aligned}
-	\end{aligned}
-	\end{equation}
-	which is the desired result.
-\end{proof}
-
-\begin{lemma} \label{lem:CLT_hom}
-	Let $u^\epl$ be the solution of \eqref{eq:CLT_Poisson} with 
-	\begin{equation}
-		\chi^\epl(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z) - V'(z) \otimes V'(x) \mathcal M_\epl^{-1} \mathfrak p_\epl,
-	\end{equation}
-	where
-	\begin{equation}
-		\mathcal M_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ], \quad \mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ].
-	\end{equation}
-	Then, $u^\epl \to 0$ \corr{in which sense?} for $\epl \to 0$.
-\end{lemma}
-\begin{proof} We here present a formal proof based on asymptotic expansion with respect to $\epl$. Let us first remark that by definition
-	\begin{equation}
-		\E^{\rho^\epl}[\chi^\epl(X^\epl, Z^\epl)] = 0,
-	\end{equation}
-	and therefore problem \eqref{eq:CLT_Poisson} reads
-	\begin{equation}
-		-\mathcal L^\epl u^\epl = \chi^\epl.
-	\end{equation}
-	Let us now denote $y = x/\epl$ and write
-	\begin{equation}
-		u^\epl(x, z) = u_0(x, y, z) + \epl u_1(x, y, z) + \epl^2 u_2(x, y, z) + \ldots,
-	\end{equation}
-	which implies that
-	\begin{equation}
-	\begin{aligned}
-		\partial_x u^\epl &= \partial_x(u_0(x, y, z) + \epl u_1(x, y, z) + \epl^2 u_2(x, y, z) + \ldots) \\
-		&\quad+ \frac1\epl\partial_y(u_0(x, y, z) + \epl u_1(x, y, z) + \epl^2 u_2(x, y, z) + \ldots).
-	\end{aligned}
-	\end{equation}
-	Let us first remark that from the proof of Theorem \ref{thm:mainTheorem} we have that
-	\begin{equation}
-		\lim_{\epl \to 0} \mathcal M_\epl^{-1}\mathfrak p_\epl = A - \alpha.
-	\end{equation} 	
-	Replacing $u^\epl$ in \eqref{eq:CLT_Poisson} and grouping the terms of order $\epl^0$, $\epl^{-1}$ and $\epl^{-2}$ we get the system
-	\begin{align}
-		L_0 u_0 &= 0, \label{eq:CLT_AsExp1}\\
-		L_1 u_0 + L_0 u_1 &= - p'(y) V'(z), \label{eq:CLT_AsExp2}\\
-		L_0 u_2 + L_1 u_1 + L_2 u_0 &= \left(V'(z) \otimes V'(x)\right) (A - \alpha),\label{eq:CLT_AsExp3}
-	\end{align}
-	where 
-	\begin{equation}
-	\begin{aligned}
-		L_0 &= -p'(y) \partial_y + \sigma \partial^2_{yy},\\
-		L_1 &= -p'(y) \partial_x - \alpha \cdot V'(x) \partial_y + 2 \sigma \partial^2_{xy}, \\
-		L_2 &= 	-\alpha \cdot V'(x) \partial_x - \frac1{\delta}(z - x)	\partial_z + \sigma \partial^2_{xx}.
-	\end{aligned}
-	\end{equation}
-	Let us first remark that equation \eqref{eq:CLT_AsExp1} is satisfied for $u_0 = u_0(x, z)$ independent of $y$.
-In particular, the kernel of $L_0$ is made of constants and the kernel of $L_0^*$ is one-dimensional and $\mathrm{Ker}(L_0^*) = \mathrm{Span}\{\rho\}$ where
-	\begin{equation}\label{eq:CLT_Invariant}
-		\rho(y) = \frac1Z e^{-p(y)/\sigma}, \quad\text{where}\quad Z = \int_0^L e^{-p(y)/\sigma} \dd y,
-	\end{equation} 
-	where $L$ is the period of $p$. Since $u_0$ is independent of $y$ equation \eqref{eq:CLT_AsExp2} reduces to 
-	\begin{equation}
-		L_0 u_1 = p'(y)\left(\partial_x u_0 -V'(z)\right).
-	\end{equation}
-	Let us remark that the general solution $u_1$ can be written as
-	\begin{equation}
-		u_1(x,y,z) = \Phi(y)\left(\partial_x u_0(x, z) - V'(z)\right),
-	\end{equation}
-	where $\Phi \colon \R \to \R$ satisfies
-	\begin{equation}
-		-L_0 \Phi = -p'(y).
-	\end{equation} 
-	Let us remark that this cell problem is the same as \eqref{eq:CellProblem}. We consider now equation \eqref{eq:CLT_AsExp3} and remark that we can rewrite it as
-	\begin{equation}
-	\begin{aligned}
-		L_0 u_2 &= (V'(z) \otimes V'(x))(A - \alpha) - \left(2\Phi'(y) - \frac1\sigma p'(y) \Phi(y) + 1\right) \sigma \partial^2_{xx}u_0 \\
-		&\quad +\left(\Phi'(y) + 1\right) \left( \alpha \cdot V'(x) \right) \partial_x u_0 - \left(V'(z) \otimes V'(x) \right)\alpha \Phi'(y) + \frac1\delta(z-x) \partial_z u_0.
-	\end{aligned}
-	\end{equation}
-	By the Fredholm alternative, in order for \eqref{eq:CLT_AsExp3} to have a solution we need the right hand side to have zero-mean with respect to $\rho$ in \eqref{eq:CLT_Invariant}.
-Therefore, recalling that the homogenization coefficient $K$ in \eqref{eq:K_HOM} is given by
-	\begin{equation}
-		K = \int_0^L (1 + \Phi'(y))^2 \rho(y) \dd y
-	\end{equation}
-	and remarking that integrations by part allow to rewrite $K$ as
-	\begin{equation}
-		K = \int_0^L (1 + \Phi'(y)) \rho(y) \dd y, \quad  K = \int_0^L \left(2\Phi'(y) - \frac1\sigma p'(y) \Phi(y) + 1\right) \rho(y) \dd y,
-	\end{equation}
-	we get
-	\begin{equation}
-		0 = (V'(z) \otimes V'(x))(A - \alpha - (K - 1)\alpha) - K \sigma \partial^2_{xx}u_0 + \left(K \alpha \cdot V'(x)\right) \partial_x u_0  + \frac1\delta(z-x) \partial_z u_0.
-	\end{equation}
-	Moreover, since $A = K\alpha$ and $\Sigma = K\sigma$, it implies
-	\begin{equation}
-		0 = -\Sigma \partial^2_{xx}u_0 + \left(A \cdot V'(x)\right) \partial_x u_0  + \frac1\delta(z-x) \partial_z u_0,
-	\end{equation}
-	which can be written as
-	\begin{equation}\label{eq:CLT_Poisson_hom}
-		- \mathcal L_0 u_0 = 0,
-	\end{equation}
-	where $\mathcal L_0$ is the generator of the couple $(X^0,Z^0)^\top$. Finally, the unique solution of \eqref{eq:CLT_Poisson_hom} satisfying
-	\begin{equation}
-		\E^{\rho^0}[u_0(X,Z)] = 0,
-	\end{equation}
-	is given by
-	\begin{equation}
-		u_0(x,z) = 0.
-	\end{equation}
-\end{proof}
-
-We can now proceed with the main proof.
-\begin{proof}[Proof of Theorem \ref{thm:CLT}] Let us introduce the notation
-	\begin{equation}\label{eq:CLT_DefMEps}
-	\mathcal M_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ], \quad \mathcal M_0 \defeq \E^{\rho^0} [ V'(Z) \otimes V'(X) ],
-	\end{equation}
-	and the notation
-	\begin{equation}
-	\mathfrak p_\epl \defeq \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ]
-	\end{equation}
-	and let us remark that from the proof of Theorem \ref{thm:mainTheorem} one can deduce the equalities
-	\begin{equation}\label{eq:CTL_A}
-	A = \frac1\delta \mathcal M_0^{-1} \E^{\rho^0}[(X - Z)^2 V''(Z)],
-	\end{equation}
-	and
-	\begin{equation}\label{eq:CTL_alpha}
-	\alpha = \mathcal M_\epl^{-1} \left(\frac1\delta \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)] - \mathfrak p_\epl \right).
-	\end{equation}
-	Let us furthermore remark that the decomposition \eqref{eq:alphaDecomposition} yields
-	\begin{equation}
-	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) = \sqrt{T} \left(\alpha - A + I_1^\epl - I_2^\epl\right).
-	\end{equation}
-	Replacing the expression for $A$ and $\alpha$ given in \eqref{eq:CTL_A} and \eqref{eq:CTL_alpha}, we get
-	\begin{equation}
-	\begin{aligned}
-	\sqrt{T}\left(\widehat A^\epl_k(T) - A\right) &= \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \\
-	&+  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X - Z)^2 V''(Z)] \right) \\
-	&- \sqrt{T} I_2^\epl(T).
-	\end{aligned}
-	\end{equation}
-	\corr{Third term is OK:} We rewrite the term involving $I_2^\epl(T)$ as
-	\begin{equation}
-	\sqrt{T} I_2^\epl(T) = \frac{\sqrt{2\sigma}}{\sqrt{T}} \widetilde M^{-1} Q^\epl(T),
-	\end{equation}
-	where, since $Z_t^\epl$ is adapted with respect to the natural filtration $\mathcal F_t$ of the Wiener process $W \defeq \left(W_t, t \geq 0\right)$, the quantity
-	\begin{equation}
-	Q^\epl(T) \defeq \int_0^T V'(Z^\epl_t) \dd W_t,
-	\end{equation}
-	is a martingale whose quadratic variation is given by
-	\begin{equation}
-	\langle Q^\epl \rangle_T = \int_0^T V'(Z^\epl_t) \otimes V'(Z^\epl_t) \dd t. 
-	\end{equation}
-	Since the ergodic theorem guarantees that 
-	\begin{equation}
-	\lim_{T\to\infty}\frac{\langle Q^\epl \rangle_T}{T} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)], \quad \text{in } L^1(\mu^\epl),
-	\end{equation}
-	the martingale central limit theorem gives 
-	\begin{equation}
-	\lim_{T\to\infty}\frac{1}{\sqrt{T}} Q^\epl(T) = \Xi^\epl, \quad \text{in law},
-	\end{equation}
-	where $\Xi^\epl \sim \mathcal N(0, \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)])$.
-	Now, by the ergodic theorem 
-	\begin{equation}
-	\lim_{T \to \infty} \widetilde M^{-1} = \mathcal M_\epl^{-1}, \quad \text{a.s.}
-	\end{equation}
-	Therefore, we have by Slutsky's theorem that
-	\begin{equation}
-	\lim_{T \to \infty} \sqrt{T} I_2^\epl(T) = \Lambda^\epl \sim \mathcal N\left(0, \Gamma^\epl\right), \quad \text{in law}.
-	\end{equation}
-	where the covariance matrix $\Gamma^\epl$ is given by
-	\begin{equation}
-	\Gamma^\epl = 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[V'(Z^\epl) \otimes V'(Z^\epl)]\mathcal M_\epl^{-\top}.
-	\end{equation}
-	Finally, we denote by $\Lambda$ the limit for $\epl \to 0$ of the sequence of Gaussian random variables $\Lambda^\epl$.
-
-	\corr{Idea for the first term:} Let us introduce the notation
-	\begin{equation}
-	J_1^\epl(T) \defeq \sqrt{T}\left( I_1^\epl(T) - \mathcal M_\epl^{-1} \mathfrak p_\epl\right),
-	\end{equation}
-	and let us remark that we can rewrite
-	\begin{equation} \label{eq:decomposition_first_term}
-	\begin{aligned}
-	J_1^\epl(T) = \sqrt{T} &\left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1}\\
-		&\quad \times \left(\frac1T \int_0^T \left( \frac{1}{\epl} p' \left ( \frac{X^\epl_t}{\epl} \right ) V'(Z^\epl_t)	- V'(Z^\epl_t) \otimes V'(X^\epl_t) \mathcal M_\epl^{-1} \mathfrak p_\epl \right) \dd t	 \right).
-	\end{aligned}
-	\end{equation}
-	Let us denote by $u^\epl$ the solution of \eqref{eq:CLT_Poisson} with right hand side
-	\begin{equation}
-	\chi^\epl(x, z) = \frac 1 \epl p' \left ( \frac x \epl \right ) V'(z) - V'(z) \otimes V'(x) \mathcal M_\epl^{-1} \mathfrak p_\epl,
-	\end{equation}
-	and note that $\E^{\rho^\epl}[\chi^\epl(X^\epl,Z^\epl)] = 0$. Then, by Lemma \ref{lem:CLT}, we have
-	\begin{equation}
-	J_1^\epl(T)= \sqrt{T} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \left( -\frac{R^\epl(T)}{T} + \sqrt{2\sigma}\frac{S^\epl(T)}{T} \right),
-	\end{equation}
-	where $R^\epl(T)$ and $S^\epl(T)$ are defined in \eqref{eq:CLT_PoissonRemainders}. Since \corr{$R^\epl(T)$ is bounded independently of $\epl$ (is it clear?)}, we first get by the ergodic theorem
-	\begin{equation}
-	\lim_{T \to \infty} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{R^\epl(T)}{\sqrt{T}} = 0, \quad \text{a.s.}
-	\end{equation}
-	Repeating the same reasoning as for $Q^\epl(T)$ and employing the ergodic theorem and the Slutsky's theorem, we get 
-	\begin{equation}
-	\lim_{T \to \infty} J_1^\epl(T) = \lim_{T \to \infty} \sqrt{2\sigma} \left(\frac1T \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t\right)^{-1} \frac{S^\epl(T)}{\sqrt{T}} = \Lambda_1^\epl \sim \mathcal N(0, \Gamma_1^\epl),
-	\end{equation}
-	where the covariance is given by due to \eqref{eq:CLT_Equiv}
-	\begin{equation}
-	\begin{aligned}
-	\Gamma_1^\epl &= 2\sigma \mathcal M_\epl^{-1}\E^{\rho^\epl}[\partial_x u^\epl(X^\epl, Z^\epl) \otimes \partial_x u^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top} \\
-	&= \mathcal M_\epl^{-1}\E^{\rho^\epl}[u^\epl(X^\epl, Z^\epl) \otimes \chi^\epl(X^\epl, Z^\epl) + \chi^\epl(X^\epl, Z^\epl) \otimes u^\epl(X^\epl, Z^\epl)]\mathcal M_\epl^{-\top}.
-	\end{aligned}
-	\end{equation}
-	\corr{For the covariance $\Gamma_1^\epl$ we don't know how it behaves in the limit $\epl \to 0$.
-It would be nice if it was vanishing since it involves the solution $u^\epl$, which goes to zero (in some sense) due to Lemma \ref{lem:CLT_hom}.}
-
-	\corr{Idea for the second term:} Let us now introduce the notation
-	\begin{equation}
-		J_2^\epl(T) = \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)] - \mathcal M_0^{-1} \E^{\rho^0}[(X - Z)^2 V''(Z)] \right).
-	\end{equation}
-	We have the decomposition
-	\begin{equation}
-	\begin{aligned}
-	J^\epl_{2}(T) &=  \frac{\sqrt{T}}\delta \left( \mathcal M_\epl^{-1}  - \mathcal M_0^{-1} \right)\E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)] \\
-	&\quad + \frac{\sqrt{T}}\delta \mathcal M_0^{-1}\left(\E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)] - \E^{\rho^0}[(X - Z)^2 V''(Z)] \right) \\
-	&\eqdef J_{2,1}^\epl(T) + J_{2,2}^\epl(T).
-	\end{aligned}
-	\end{equation}
-	\corr{In order to send the terms above to zero, we need the convergence rate of $\mu^\epl$ to $\mu^0$ w.r.t.
-$\epl$ (by fixing $T = \epl^{-\gamma}$ with an appropriate $\gamma$).
-Some arguments in this sense seem to appear in [\textit{Periodic Homogenization for Hypoelliptic Diffusions} -- M.
-Hairer and G.A.
-Pavliotis 2004] but it is not clear to us whether it applies to this case too.}
-\end{proof}
-
 \section{Proof of Theorem \ref{thm:mainTheoremTilde}}\label{ap:EstimatorTilde}
@@
 where the matrix $M$ is taken from \eqref{eq:MandH} and the vector $\widetilde{h}$ is taken from \eqref{eq:MandHTilde}.
-We prove here Theorem \ref{thm:mainTheoremTilde}, i.e., the unbiasedness of this estimator, for which it is necessary to prove two technical lemmas.
-Let us start with an estimate concerning the distance between $X^\epl$ and $Z^\epl$.
-
-\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
-Then, if $\delta \leq 1$, it holds for any integer $p \geq 1$
-	\begin{equation}
-	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
-	\end{equation}
-	for a constant $C > 0$ independent of $\epl$ and $\delta$.
-\end{lemma}
-\begin{proof} Let us first remark that the filtering kernel satisfies
-	\begin{equation}\label{eq:filterIntegral}
-	\int_0^t k(t-s) \dd s = 1 - e^{-t/\delta},
-	\end{equation}
-	which implies that the measure $\kappa_t(\d s)$ on $(0, t)$ defined as
-	\begin{equation}
-	\kappa_t(\d s) \defeq \frac{k(t-s)}{1 - e^{-t/\delta}} \dd s,
-	\end{equation}
-	is a probability measure.
-Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$.
-Let $Z_t^\epl$ be the corresponding filtered process.
-By definition of $Z^\epl_t$ and due \eqref{eq:filterIntegral} we now have
-	\begin{equation}
-	\begin{aligned}
-	X_t^\epl - Z_t^\epl &= X_t^\epl - \int_0^t k(t-s) X_s^\epl \dd s\\
-	&= \int_0^t k(t - s) \left(X_t^\epl - X_s^\epl\right) \dd s + e^{-t/\delta} X^\epl_t\\
-	&= (1 - e^{-t/\delta})\int_0^t \left(X_t^\epl - X_s^\epl\right) \kappa_t(\d s) + e^{-t/\delta} X^\epl_t.
-	\end{aligned}
-	\end{equation}
-	Therefore, Jensen's inequalities yields for a constant $C > 0$ depending only on $p$
-	\begin{equation}
-	\begin{aligned}
-	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} &\leq C (1 - e^{-t/\delta})^{2p} \int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} \kappa_t (\d s) + C e^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p}\\
-	&\leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^{2p} k(t-s) \dd s + Ce^{-2pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^{2p},
-	\end{aligned}
-	\end{equation}
-	where we replaced the definition of $\kappa(\d s)$ and exploited the fact that $1 - e^{-t/\delta}\leq 1$ for all $t \geq 0$.
-Due to \cite[Corollary 5.4]{PaS07}, we know that $X^\epl_t$ has bounded moments of all orders with respect to its invariant measure.
-Moreover, the estimate
-	\begin{equation}
-	\E^{\phi^\epl}\abs{X_t^\epl - X_s^\epl}^{2p} \leq C\left(\epl^{2p} + (t-s)^{2p} + (t-s)^p\right),
-	\end{equation}
-	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}. Finally, it is possible to verify by induction on $r$ that for all integers $r$ it holds
-	\begin{equation}\label{eq:FilterTminusS}
-	\int_0^t k(t-s) (t - s)^r \dd s \leq r! \, \delta^r, 
-	\end{equation}
-	which implies that there exists a constant $C > 0$ depending only on $p$ such that
-	\begin{equation}
-	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p + e^{-2pt/\delta}\right).
-	\end{equation}
-	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
-In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$
-	\begin{equation}
-	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^{2p} + Ce^{-\lambda t},
-	\end{equation}
-	which, for $t$ sufficiently big, yields
-	\begin{equation}
-	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^{2p} \leq C\left(\epl^{2p} + \delta^p\right),
-	\end{equation}
-	which is the desired result.
-\end{proof}
-
-Let us consider a couple $(X^\epl, Z^\epl)^\top$. In the following, we will adopt the notation
-\begin{equation}\label{eq:CalM}
-\mathcal M = \E^{\rho^\epl}[V'(X^\epl) \otimes V'(X^\epl)] \quad \text{and} \quad \widetilde{\mathcal M} = \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)],
-\end{equation}
-which due to the ergodic theorem satisfy
-\begin{equation}
-\lim_{T \to \infty} M = \mathcal M, \quad \text{and} \quad \lim_{T \to \infty} \widetilde M = \mathcal{\widetilde M},
-\end{equation}
-almost surely. In the following Lemma, we consider the difference between the two matrices $\mathcal M$ and $\widetilde{\mathcal M}$.
-
-\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Lemma \ref{lem:distanceZandX} hold. Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}$ defined in \eqref{eq:CalM} satisfy
-	\begin{equation}
-	\norm{\mathcal M - \widetilde{\mathcal M}}_2 \leq C\left(\epl + \delta^{1/2}\right),
-	\end{equation}
-	for a constant $C > 0$ independent of $\epl$ and $\delta$.
-\end{lemma}
-\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
-	\begin{equation}
-	\begin{aligned}
-	\norm{\mathcal M - \widetilde{\mathcal M}}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
-	&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
-	\end{aligned}
-	\end{equation}
-	The Lipschitz condition on $V$ together with the boundedness of the moments of $X^\epl$ and Lemma \ref{lem:distanceZandX} yield for a constant $C > 0$
-	\begin{equation}
-	\begin{aligned}
-	\norm{\mathcal M - \widetilde{\mathcal M}}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
-	\end{aligned}
-	\end{equation}
-	which is the desired result.
-\end{proof}
+We prove here Theorem \ref{thm:mainTheoremTilde}, i.e., the unbiasedness of this estimator.
+Let us consider a couple $(X^\epl, Z^\epl)^\top$.
 
@@
 	\begin{aligned}
-	\lim_{T \to \infty} \left(\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)\right) &= \left(\mathcal M^{-1} - \widetilde{\mathcal M}^{-1}\right) \lim_{T \to \infty}\widetilde h \\
-	&= \mathcal M^{-1}\left(\mathcal M - \widetilde{\mathcal M}\right)  \widetilde{\mathcal M}^{-1} \lim_{T \to \infty} \widetilde h\\
-	&= \mathcal M^{-1}\left(\mathcal M - \widetilde{\mathcal M}\right)\lim_{T \to \infty} \widehat A^\epl_k(T),
-	\end{aligned}
-	\end{equation}
-	almost surely. Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
+	\lim_{T \to \infty} \left(\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)\right) &= \left(\mathcal M_\epl^{-1} - \widetilde{\mathcal M}_\epl^{-1}\right) \lim_{T \to \infty}\widetilde h \\
+	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)  \widetilde{\mathcal M}_\epl^{-1} \lim_{T \to \infty} \widetilde h\\
+	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)\lim_{T \to \infty} \widehat A^\epl_k(T),
+	\end{aligned}
+	\end{equation}
+	almost surely.
+Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M_\epl^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
 	\begin{equation}\label{eq:DistATildeAHat}

### 2020-03-22 CalNotes.tex
Two typos
update delta=epsilon^zeta

@@
 \corr{ CASE $\delta = \epl^\zeta$ (PROOF IN APPENDIX \ref{ap:zeta}).
-\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and let $\delta = \epl^\zeta$ with $\zeta \in (0,1)$.
+\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and let $\delta = \epl^\zeta$ with $\zeta \in (0,2)$.
 If $\widetilde M$ is invertible, then
@@
 	\end{equation}
-	Then, for any $t > 0$, $p \geq 0$ and any function $g\in \mathcal C^0(0, t)$ it holds 
+	Then, for any $t > 0$, $p \geq 0$ and any function $g\in \mathcal C^0([0, t])$ it holds 
 	\begin{equation}
@@
 	\end{equation}
-	Therefore, the measure $\kappa_t(\d s)$ on $(0, t)$ defined as
+	Therefore, the measure $\kappa_t(\d s)$ on $[0, t]$ defined as
 	\begin{equation}
@@
 \end{proof}
-We can now prove a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.
 
@@
 
-It is relevant to study the quantities
-\begin{equation}\label{eq:CalM}
-\mathcal M_\epl \defeq \E^{\rho^\epl}[V'(X^\epl) \otimes V'(X^\epl)] \quad \text{and} \quad \widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)],
-\end{equation}
-which are by the ergodic theorem the time limit of the matrices appearing in the estimators $\widehat A^\epl(T)$ and $\widehat A^\epl_k(T)$, respectively.
-In particular, the distance between the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ can be bounded, which is summarized in the following lemma.
-
-\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Lemma \ref{lem:distanceZandX} hold.
-Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}_\epl$ defined in \eqref{eq:CalM} satisfy
-	\begin{equation}
-	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 \leq C\left(\epl + \delta^{1/2}\right),
-	\end{equation}
-	for a constant $C > 0$ independent of $\epl$ and $\delta$.
-\end{lemma}
-\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
-	\begin{equation}
-	\begin{aligned}
-	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
-	&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
-	\end{aligned}
-	\end{equation}
-	The Lipschitz condition on $V'$ together with the boundedness of the moments of $X^\epl$ and Lemma \ref{lem:distanceZandX} yield for a constant $C > 0$
-	\begin{equation}
-	\begin{aligned}
-	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
-	\end{aligned}
-	\end{equation}
-	which is the desired result.
-\end{proof}
-
-The final result presented in this section is a sharper quantification of the difference between $X^\epl_t$ and $Z^\epl_t$ than Lemma \ref{lem:distanceZandX}.
-In particular, denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
+The following result is a quantification of the difference between $X^\epl_t$ and $Z^\epl_t$. In particular, denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
 \cite[Formula 5.8]{PaS07}
@@
 	where $\Phi$ is the solution of the cell problem \eqref{eq:CellProblem}, $W_s$ is the Brownian motion appearing in \eqref{eq:SDE_MS} and $Y_t^\epl = X_t^\epl / \epl$.
-Moreover, the remainder $R(\epl,\delta)$ satisfies for every $p > 0$ the estimate
+Moreover, $\beta_t^\epl$ and the remainder $R(\epl,\delta)$ satisfy for every $p > 0$ the estimates
+	\begin{equation} \label{eq:beta}
+	\left( \E^{\phi^\epl} \abs{\beta_t^\epl}^p \right)^{1/p} \leq C \delta^{-1},
+	\end{equation}
+	and
 	\begin{equation} \label{eq:remainder_zeta}
-	\left( \E^{\rho_\epl} \left| R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta + \epl^2 + \epl \delta^{1/2} \right),
-	\end{equation}
-	where $C$ is independent of $\epl$ and $\delta$.
+	\left( \E^{\phi^\epl} \left| R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta + \epl \right),
+	\end{equation}
+	where $C$ is independent of $\epl$ and $\delta$ and $\phi^\epl$ is the density of the invariant measure of $X^\epl$.
 \end{lemma}
@@
 	\end{equation}
-	in law, where the remainder $R_1^\epl$ satisfies 
+	where the remainder $R_1^\epl$ satisfies 
 	\begin{equation}\label{eq:FirstTermPavStu}
@@
 	\begin{aligned}
-	I_1^\epl(t) &= -(A \cdot V'(X_t^\epl)) \int_0^t k(t-s) (t-s)\dd s + \int_0^t k(t-s)R^\epl(t-s) \dd s\\
+	I_1^\epl(t) &= -(A \cdot V'(X_t^\epl)) \int_0^t k(t-s) (t-s)\dd s + \int_0^t k(t-s)R_1^\epl(t-s) \dd s\\
 	&= -\delta (A \cdot  V'(X_t^\epl)) + e^{-t/\delta}(t + \delta)(A \cdot V'(X_t^\epl)) + \widetilde R_1^\epl(t),
@@
 	\begin{equation}
-		Q_t \defeq \int_0^t \left(1 + \Phi'(Y_r^\epl)\right) \dd W_r,
+		Q_t^\epl \defeq \int_0^t \left(1 + \Phi'(Y_r^\epl)\right) \dd W_r,
 	\end{equation}
@@
 	\begin{equation}
-		I_2^\epl(t) = \sqrt{2\sigma} Q_t \int_0^t k(t-s)(Q_t - Q_s) \dd s.
-	\end{equation}
-	An application of the Itô formula to $u(s, Q_s)$ where $u(s, x) = k(t-s)x$ yields
-	\begin{equation}
-	\begin{aligned}
-		I_2^\epl(t) &= \sqrt{2\sigma} \left(Q_t\int_0^t k(t-s) \dd s - Q_t + \delta \int_0^t k(t-s)\left(1 + \Phi'(Y_s^\epl)\right) \dd W_s\right)\\
-		  			&= \delta \beta_t^\epl - \sqrt{2\sigma} e^{-t/\delta} Q_t \eqdef \delta \beta_t^\epl - R_2^\epl(t).
+		I_2^\epl(t) = \sqrt{2\sigma} \int_0^t k(t-s)(Q_t^\epl - Q_s^\epl) \dd s.
+	\end{equation}
+	An application of the Itô formula to $u(s, Q_s^\epl)$ where $u(s, x) = k(t-s)x$ yields
+	\begin{equation}
+	\begin{aligned}
+		I_2^\epl(t) &= \sqrt{2\sigma} \left(Q_t^\epl\int_0^t k(t-s) \dd s - Q_t^\epl + \delta \int_0^t k(t-s)\left(1 + \Phi'(Y_s^\epl)\right) \dd W_s\right)\\
+		  			&= \delta \beta_t^\epl - \sqrt{2\sigma} e^{-t/\delta} Q_t^\epl \eqdef \delta \beta_t^\epl - R_2^\epl(t).
 	\end{aligned}
@@
 	\begin{aligned}
-		\left(\E\abs{Q_t}^p\right)^2 \leq \E\abs{Q_t}^{2p} \leq Ct^{p-1}\int_0^t \E \abs{1 + \Phi'(Y_r^\epl)}^{2p} \dd r \leq C t
+		\left(\E\abs{Q_t^\epl}^p\right)^2 \leq \E\abs{Q_t^\epl}^{2p} \leq Ct^{p-1}\int_0^t \E \abs{1 + \Phi'(Y_r^\epl)}^{2p} \dd r \leq C t^p
 	\end{aligned}
@@
 	\begin{equation}
-		\E\abs{R_2^\epl(t)}^p \leq C \sqrt{t}e^{-pt/\delta}.
-	\end{equation}
+		\left( \E^{\phi^\epl}\abs{R_2^\epl(t)}^p \right)^{1/p} \leq C \sqrt{t} e^{-t/\delta}.
+	\end{equation}
+	Moreover, applying the Itô isometry and due to the boundedness of $\Phi'$, we get
+	\begin{equation}
+	\E^{\phi^\epl} \abs{\beta_t^\epl}^2 \le C \int_0^t k^2(t-s) \dd s \leq C \delta^{-1},
+	\end{equation}
+	which proves \eqref{eq:beta}.
 	Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
@@
 
-\corr{
-\begin{remark} Let us remark that one can show for all $p \geq 1$ and a constant $C > 0$ independent of $\delta$
-	\begin{equation}
-		\left(\E\abs{\beta_t^\epl}^p \right)^{1/p} \leq C \delta^{-1/2}.
-	\end{equation}
-	Therefore, the estimate presented in Lemma \ref{lem:zeta} is consistent with the rough estimate of Lemma \ref{lem:distanceZandX}, and the term highlighted in the statement of Lemma \ref{lem:zeta} is indeed the dominating term in terms of powers of $\delta$.
-\end{remark}
-}
+Corollary \ref{cor:distanceZandX} is a direct consequence of Lemma \ref{lem:zeta} and provides a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.
+
+\begin{corollary} \label{cor:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
+Then, if $\delta \leq 1$, it holds for any $p \geq 1$
+	\begin{equation}
+	\left(\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p\right)^{1/p} \leq C\left(\epl + \delta^{1/2}\right),
+	\end{equation}
+	for a constant $C > 0$ independent of $\epl$ and $\delta$.
+\end{corollary}
+\begin{proof}
+	Let $p \geq 1$, then due to Lemma \ref{lem:zeta} there exists a constant $C > 0$ depending only on $p$ such that
+	\begin{equation}
+	\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\left(\epl^p + \delta^{p/2}\right).
+	\end{equation}
+	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
+In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$
+	\begin{equation}
+	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + Ce^{-\lambda t},
+	\end{equation}
+	which, for $t$ sufficiently big, yields the desired result.
+\end{proof}
+
+It is relevant to study the quantities
+\begin{equation}\label{eq:CalM}
+\mathcal M_\epl \defeq \E^{\rho^\epl}[V'(X^\epl) \otimes V'(X^\epl)] \quad \text{and} \quad \widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)],
+\end{equation}
+which are by the ergodic theorem the time limit of the matrices appearing in the estimators $\widehat A^\epl(T)$ and $\widehat A^\epl_k(T)$, respectively.
+In particular, the distance between the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ can be bounded, which is summarized in the following lemma.
+
+\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Lemma \ref{lem:distanceZandX} hold.
+Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}_\epl$ defined in \eqref{eq:CalM} satisfy
+	\begin{equation}
+	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 \leq C\left(\epl + \delta^{1/2}\right),
+	\end{equation}
+	for a constant $C > 0$ independent of $\epl$ and $\delta$.
+\end{lemma}
+\begin{proof} Applying Jensen's and Cauchy--Schwarz inequalities we have
+	\begin{equation}
+	\begin{aligned}
+	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq \E^{\rho^\epl} \norm{\left(V'(Z^\epl) - V'(X^\epl)\right) \otimes V'(X^\epl)}_2 \\
+	&\leq \left(\E^{\rho^\epl}\norm{V'(Z^\epl) - V'(X^\epl)}_2^2\right)^{1/2} \left(\E^{\rho^\epl} \norm{V'(X^\epl)}_2^{2}\right)^{1/2}.
+	\end{aligned}
+	\end{equation}
+	The Lipschitz condition on $V'$ together with the boundedness of the moments of $X^\epl$ and Corollary \ref{cor:distanceZandX} yield for a constant $C > 0$
+	\begin{equation}
+	\begin{aligned}
+	\norm{\mathcal M_\epl - \widetilde{\mathcal M}_\epl}_2 &\leq C\left(\E^{\rho^\epl}\abs{Z^\epl - X^\epl}^{2}\right)^{1/2} \leq C \left(\epl + \delta^{1/2} \right),
+	\end{aligned}
+	\end{equation}
+	which is the desired result.
+\end{proof}
 
 \section{Proof of Theorem \ref{thm:mainTheorem_zeta}} \label{ap:zeta}
+
+\begin{lemma} \label{lem:quartet}
+	Let $\eta^\epl$ be the invariant measure of the quartet $(X^\epl, Y^\epl, Z^\epl, \beta^\epl)$. Then it holds
+	\begin{equation}
+	\delta \E^{\eta^\epl} \left[ (\beta^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
+	\end{equation}
+	where the remainder $\widetilde R(\epl,\delta)$ satisfies
+	\begin{equation} \label{eq:quartet_remainder}
+	\left( \E^{\eta^\epl} \left| \widetilde R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta^{3/2} + \delta \epl \right).
+	\end{equation}
+\end{lemma}
+\begin{proof}
+
+\end{proof}
+
+\begin{lemma} \label{lem:quartet_convergence}
+	It holds
+	\begin{equation}
+	\lim_{\epl \to 0} \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] = \Sigma \E^{\phi^0} [V''(X)].
+	\end{equation}
+\end{lemma}
+\begin{proof}
+
+\end{proof}
 
@@
 	\end{equation}
-	Then following the proof of Theorem \ref{thm:mainTheorem} we only need to show that if $\delta = \epl^\zeta$ with $\zeta \in (0,1)$ we have
+	Then following the proof of Theorem \ref{thm:mainTheorem} we only need to show that if $\delta = \epl^\zeta$ with \corr{$\zeta \in (0,2)$} we have
 	\begin{equation}
@@
 	\end{equation}
-	Using Lemma \ref{lem:zeta} and geometric ergodicity (Lemma \ref{lem:ergodicity}), we have the following equality in law
+	Using Lemma \ref{lem:zeta} and geometric ergodicity (Lemma \ref{lem:ergodicity}), we have the following equality
 	\begin{equation}
@@
 		\mathcal A^\epl(\delta) &= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E [(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl)] \\
-		&= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E \left[ \left( \sqrt{2\Sigma}\delta \int_0^t k(t-s) \dd B_s + R(\epl,\delta) \right)^2 V''(Z_t^\epl) \right] \\
+		&= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E \left[ \left( \delta \beta_t^\epl + R(\epl,\delta) \right)^2 V''(Z_t^\epl) \right] \\
 		&\eqdef \widetilde{\mathcal M}_\epl^{-1} \lim_{t \to \infty} \left( J_1^\epl(t) + J_2^\epl(t) + J_3^\epl(t) \right),
@@
 	\end{equation}
-	where
-	\begin{equation}
-	\begin{aligned}
-		J_1^\epl(t) &= 2\Sigma\delta \E \left[ \left( \int_0^t k(t-s) \dd B_s \right)^2 V''(Z_t^\epl) \right], \\
-		J_2^\epl(t) &= 2\sqrt{2\Sigma} \E \left[ \left( \int_0^t k(t-s) \dd B_s \right) R(\epl,\delta) V''(Z_t^\epl) \right], \\
+	where and $\E$ denotes the expectation with respect to the Wiener measure and
+	\begin{equation}
+	\begin{aligned}
+		J_1^\epl(t) &= \delta \E \left[ (\beta_t^\epl)^2 V''(Z_t^\epl) \right], \\
+		J_2^\epl(t) &= 2 \E \left[ \beta_t^\epl R(\epl,\delta) V''(Z_t^\epl) \right], \\
 		J_3^\epl(t) &= \frac1\delta \E\left[ R(\epl,\delta)^2 V''(Z_t^\epl) \right].
@@
 	\end{equation}
-	Let us consider the three terms separately. First, since the Brownian motion $B_s$ is independent of the process $Z_t^\epl$, applying Itô isometry we get
-	\begin{equation}
-	J_1^\epl(t) = 2\Sigma\delta \left( \int_0^t k(t-s)^2 \dd s \right) \E [V''(Z_t^\epl)] = \Sigma \E [V''(Z_t^\epl)],
-	\end{equation}
-	and, by Lemma \ref{lem:distanceZandX} and weak convergence of the invariant measure, we obtain
-	\begin{equation}
-	\lim_{\epl \to 0} \lim_{t \to \infty} J_1^\epl(t) = \Sigma \lim_{\epl \to 0} \E^{\rho^\epl} [V''(Z^\epl)] = \Sigma \E^{\rho^0} [V''(X)].
-	\end{equation}
-	Moreover, due to \eqref{eq:remainder_zeta}, we have the following bounds for $J_2^\epl(t)$ and $J_3^\epl(t)$
-	\begin{equation}
-	\begin{aligned}
-		\abs{J_2^\epl(t)} &\le C \left( \delta^{1/2} + \epl^\iota \delta^{-1/2} + \epl \right), \\
-		\abs{J_3^\epl(t)} &\le C \left( \delta + \epl^{2\iota} \delta^{-1} + \epl^2 \right).
+	Let us consider the three terms separately. First, by geometric ergodicity and applying Lemma \ref{lem:quartet}, we get
+	\begin{equation}
+	\lim_{t \to \infty} J_1^\epl(t) = \delta \E^{\eta^\epl} \left[ (\beta^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
+	\end{equation}
+	and, by Lemma \ref{lem:quartet_convergence} and due to \eqref{eq:quartet_remainder}, we obtain
+	\begin{equation}
+	\lim_{\epl \to 0} \lim_{t \to \infty} J_1^\epl(t) = \Sigma \E^{\rho^0} [V''(X)].
+	\end{equation}
+	Moreover, due to \eqref{eq:beta} and \eqref{eq:remainder_zeta}, we have the following bounds for $J_2^\epl(t)$ and $J_3^\epl(t)$
+	\begin{equation}
+	\begin{aligned}
+		\abs{J_2^\epl(t)} &\le C \left( \delta^{1/2} + \epl \delta^{-1/2} \right), \\
+		\abs{J_3^\epl(t)} &\le C \left( \delta + \epl^2 \delta^{-1} \right).
 	\end{aligned}
@@
 	\end{equation}
-	almost surely.
+	almost surely, where $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ are defined in \eqref{eq:CalM}.
 Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M_\epl^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$

### 2020-03-24 CalNotes.tex
Finished Appendix B

@@
 	\end{equation}
-	Then, for any $t > 0$, $p \geq 0$ and any function $g\in \mathcal C^0([0, t])$ it holds 
-	\begin{equation}
-		\abs{\int_0^t k(t-s) g(s) \dd s}^p \leq (1 - e^{-t/\delta})^{p-1}\int_0^t k(t-s) \abs{g(s)}^p \dd s.
-	\end{equation}
-	Moreover, if $p \geq 1$ and since $0 < (1-e^{-t/\delta}) < 1$ for all $t > 0$, it holds
+	Then, for any $t > 0$, $p \geq 1$ and any function $g\in \mathcal C^0([0, t])$ it holds 
 		\begin{equation}
@@
 		\end{equation}
+%	\begin{equation}
+%		\abs{\int_0^t k(t-s) g(s) \dd s}^p \leq (1 - e^{-t/\delta})^{p-1}\int_0^t k(t-s) \abs{g(s)}^p \dd s.
+%	\end{equation}
+%	Moreover, if $p \geq 1$ and since $0 < (1-e^{-t/\delta}) < 1$ for all $t > 0$, it holds
+%	\begin{equation}
+%		\abs{\int_0^t k(t-s) g(s) \dd s}^p \leq \int_0^t k(t-s) \abs{g(s)}^p \dd s.
+%	\end{equation}
 \end{lemma}
@@
 		\abs{\int_0^t k(t-s) g(s) \dd s}^p &\leq (1 - e^{-t/\delta})^p \int_0^t \abs{g(s)}^p \kappa_t(\d s) \\
-		&= (1 - e^{-t/\delta})^{p-1} \int_0^t k(t-s) \abs{g(s)}^p \dd s,
-	\end{aligned}
-	\end{equation}
-	which is the desired result.
+		&= (1 - e^{-t/\delta})^{p-1} \int_0^t k(t-s) \abs{g(s)}^p \dd s.
+	\end{aligned}
+	\end{equation}
+	Finally since $0 < (1 - e^{-t/\delta})< 1$ and $p \geq 1$, this yields the desired result.
 \end{proof}
@@
 
-\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
+%\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
 Then, if $\delta \leq 1$, it holds for any $p \geq 1$
-	\begin{equation}
-		\left(\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p\right)^{1/p} \leq C\left(\epl + \delta^{1/2}\right),
-	\end{equation}
-	for a constant $C > 0$ independent of $\epl$ and $\delta$.
-\end{lemma}
-\begin{proof} Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$.
+%	\begin{equation}
+%		\left(\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p\right)^{1/p} \leq C\left(\epl + \delta^{1/2}\right),
+%	\end{equation}
+%	for a constant $C > 0$ independent of $\epl$ and $\delta$.
+%\end{lemma}
+%\begin{proof} Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$.
 Let $Z_t^\epl$ be the corresponding filtered process.
 By definition of $Z^\epl_t$ we have
-	\begin{equation}
-	\begin{aligned}
-		X_t^\epl - Z_t^\epl &= X_t^\epl - \int_0^t k(t-s) X_s^\epl \dd s\\
-		&= \int_0^t k(t - s) \left(X_t^\epl - X_s^\epl\right) \dd s + e^{-t/\delta} X^\epl_t.
-	\end{aligned}
-	\end{equation}
-	Therefore, Lemma \ref{lem:FilterJensen} yields for a constant $C > 0$ depending only on $p$
-	\begin{equation}
-		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^p k(t-s) \dd s + Ce^{-pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^p.
-	\end{equation}
-	Moreover, the estimate
-	\begin{equation}
-		\E^{\phi^\epl}\abs{X_t^\epl - X_s^\epl}^p \leq C\left(\epl^p + (t-s)^p + (t-s)^{p/2}\right),
-	\end{equation}
-	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}.
+%	\begin{equation}
+%	\begin{aligned}
+%		X_t^\epl - Z_t^\epl &= X_t^\epl - \int_0^t k(t-s) X_s^\epl \dd s\\
+%		&= \int_0^t k(t - s) \left(X_t^\epl - X_s^\epl\right) \dd s + e^{-t/\delta} X^\epl_t.
+%	\end{aligned}
+%	\end{equation}
+%	Therefore, Lemma \ref{lem:FilterJensen} yields for a constant $C > 0$ depending only on $p$
+%	\begin{equation}
+%		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^p k(t-s) \dd s + Ce^{-pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^p.
+%	\end{equation}
+%	Moreover, the estimate
+%	\begin{equation}
+%		\E^{\phi^\epl}\abs{X_t^\epl - X_s^\epl}^p \leq C\left(\epl^p + (t-s)^p + (t-s)^{p/2}\right),
+%	\end{equation}
+%	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}.
 Finally, since the moments of $X_t^\epl$ are bounded \cite[Corollary 5.4]{PaS07} and due to Lemma \ref{lem:FilterPoly} there exists a constant $C > 0$ depending only on $p$ such that
-	\begin{equation}
-		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\left(\epl^p + \delta^{p/2} + e^{-pt/\delta}\right).
-	\end{equation}
-	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
+%	\begin{equation}
+%		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\left(\epl^p + \delta^{p/2} + e^{-pt/\delta}\right).
+%	\end{equation}
+%	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
 In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$
-	\begin{equation}
-	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + Ce^{-\lambda t},
-	\end{equation}
-	which, for $t$ sufficiently big, yields the desired result.
-\end{proof}
+%	\begin{equation}
+%	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + Ce^{-\lambda t},
+%	\end{equation}
+%	which, for $t$ sufficiently big, yields the desired result.
+%\end{proof}
 
@@
 	where $\Phi$ is the solution of the cell problem \eqref{eq:CellProblem}, $W_s$ is the Brownian motion appearing in \eqref{eq:SDE_MS} and $Y_t^\epl = X_t^\epl / \epl$.
-Moreover, $\beta_t^\epl$ and the remainder $R(\epl,\delta)$ satisfy for every $p > 0$ the estimates
+Moreover, $\beta_t^\epl$ and the remainder $R(\epl,\delta)$ satisfy for every $p \geq 1$ the estimates
 	\begin{equation} \label{eq:beta}
-	\left( \E^{\phi^\epl} \abs{\beta_t^\epl}^p \right)^{1/p} \leq C \delta^{-1},
+	\left( \E^{\phi^\epl} \abs{\beta_t^\epl}^p \right)^{1/p} \leq C \delta^{-1/2},
 	\end{equation}
@@
 	An application of the Itô formula to $u(s, Q_s^\epl)$ where $u(s, x) = k(t-s)x$ yields
-	\begin{equation}
+	\begin{equation}\label{eq:rewriteI2}
 	\begin{aligned}
@@
 	where $\beta_t^\epl$ is defined in \eqref{eq:defBeta}. For the remainder $R_2^\epl(t)$, let us remark that for all $p \geq 1$ it holds
-	\begin{equation}
+	\begin{equation}\label{eq:BoundQ}
 	\begin{aligned}
@@
 	\end{equation}
-	where we applied Jensen's inequality, an estimate for the moments of stochastic integrals \cite[Formula (3.25), p. 163]{KaS91} and the boundedness of $\Phi$. Therefore, for $t$ large enough, we have
-	\begin{equation}
+	where we applied Jensen's inequality, an estimate for the moments of stochastic integrals \cite[Formula (3.25), p. 163]{KaS91} and the boundedness of $\Phi$. Therefore we have
+	\begin{equation}\label{eq:boundR2}
 		\left( \E^{\phi^\epl}\abs{R_2^\epl(t)}^p \right)^{1/p} \leq C \sqrt{t} e^{-t/\delta}.
 	\end{equation}
-	Moreover, applying the Itô isometry and due to the boundedness of $\Phi'$, we get
-	\begin{equation}
-	\E^{\phi^\epl} \abs{\beta_t^\epl}^2 \le C \int_0^t k^2(t-s) \dd s \leq C \delta^{-1},
-	\end{equation}
-	which proves \eqref{eq:beta}.
-	Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
+	In order to obtain the bound \eqref{eq:beta} on $\beta_t^\epl$, let us remark that from \eqref{eq:rewriteI2} it holds for a constant $C > 0$ depending only on $p$ 
+	\begin{equation}
+		\left(\E\abs{\beta_t^\epl}^p\right)^{1/p}\leq C \delta^{-1}\left(\E\abs{I_2^\epl(t)}^p\right)^{1/p} + C \delta^{-1} \left(\E\abs{R_2^\epl(t)}^p\right)^{1/p}.
+	\end{equation}
+	The second term is bounded exponentially fast with respect to $t$ and $\delta$ due to \eqref{eq:boundR2}.
+For the first term, applying Lemma \ref{lem:FilterJensen}, the inequality \cite[Formula (3.25), p.
+163]{KaS91} and Lemma \ref{lem:FilterPoly} we obtain for a constant $C > 0$ independent of $\delta$ and $t$
+	\begin{equation}
+	\begin{aligned}
+		\E\abs{I_2^\epl(t)}^p &\leq C \int_0^t k(t-s) \E\abs{Q_t - Q_s}^p \dd s \\
+		&\leq C\int_0^t k(t-s)(t-s)^{p/2} \dd s \leq C\delta^{p/2}.
+	\end{aligned}
+	\end{equation} 
+	Therefore, it holds
+	\begin{equation}
+		\left(\E\abs{\beta_t^\epl}^p\right)^{1/p}\leq C \delta^{-1/2},
+	\end{equation}
+	which proves the bound \eqref{eq:beta}.	Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
 	\begin{equation}
@@
 
-\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Lemma \ref{lem:distanceZandX} hold.
+\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Corollary \ref{cor:distanceZandX} hold.
 Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}_\epl$ defined in \eqref{eq:CalM} satisfy

### 2020-03-24 CalNotes.tex
update delta=epsilon^zeta

@@
 	\begin{equation} \label{eq:quartet_remainder}
-	\left( \E^{\eta^\epl} \left| \widetilde R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta^{3/2} + \delta \epl \right).
+	\left| \widetilde R(\epl,\delta) \right| \le C \left( \delta^{1/2} + \epl \right).
 	\end{equation}
@@
 \begin{proof}
-
+	Let us consider the following system of stochastic differential equations for the processes $X_t^\epl, Z_t^\epl, \beta_t^\epl, Y_t^\epl$
+	\begin{equation}
+	\label{eq:systemSDEquartet}
+	\begin{aligned}
+	\d X_t^\epl &= -\alpha \cdot V'(X_t^\epl) \dd t - \frac1\epl p'(Y_t^\epl) \dd t+ \sqrt{2\sigma} \dd W_t, \\
+	\d Z_t^\epl &= \frac1\delta \left ( X^\epl_t - Z^\epl_t \right ) \dd t, \\
+	\d \beta_t^\epl &= - \frac1\delta \beta_t^\epl \dd t + \frac{\sqrt{2\sigma}}{\delta}(1+\Phi'(Y_t^\epl)) \dd W_t, \\
+	\d Y_t^\epl &= -\frac1\epl \alpha \cdot V'(X_t^\epl) \dd t - \frac{1}{\epl^2} p'(Y_t^\epl) \dd t+ \frac{\sqrt{2\sigma}}{\epl} \dd W_t,
+	\end{aligned}
+	\end{equation}
+	whose generator $\widetilde{\mathcal L}^\epl$ is given by
+	\begin{equation}
+	\begin{aligned}
+	\widetilde{\mathcal L}^\epl =& -\left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \partial_x + \frac1\delta (x-z) \partial_z - \frac1\delta b \partial_b - \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \partial_y \\
+	& + \sigma \left( \partial_{xx}^2 + \frac2\epl \partial_{xy}^2 + \frac{1}{\epl^2} \partial_{yy}^2 + \frac{2(1+\Phi'(y))}{\delta} \partial_{xb}^2 + \frac{2(1+\Phi'(y))}{\epl \delta} \partial_{yb}^2 + \frac{(1+\Phi'(y))^2}{\delta^2} \partial_{bb}^2 \right).
+	\end{aligned}
+	\end{equation}
+	Let us denote by $\eta^\epl \colon \R^3 \times [0,L] \to \R$, $\eta^\epl = \eta^\epl(x,z,b,y)$, the invariant measure of the quartet $(X_t^\epl, Z_t^\epl, \beta_t^\epl, Y_t^\epl)$.
+Then $\eta^\epl$ solves the stationary Fokker-Planck equation
+	\begin{equation} \label{eq:FPSDEquartet}
+	\begin{aligned}
+	\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \eta^\epl \right) - \partial_z \left( \frac1\delta (x-z) \eta^\epl \right) & \\
+	+ \partial_b \left( \frac1\delta b \eta^\epl \right) + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \eta^\epl \right) & \\
+	+ \sigma \left( \partial_{xx}^2 \eta^\epl + \partial_{xy}^2 \left( \frac2\epl \eta^\epl \right) + \partial_{yy}^2 \left( \frac{1}{\epl^2} \eta^\epl \right) \right) & \\
+	+ \sigma \left( \partial_{xb}^2 \left( \frac{2(1+\Phi'(y))}{\delta} \eta^\epl \right) + \partial_{yb}^2 \left( \frac{2(1+\Phi'(y))}{\epl \delta} \eta^\epl \right) + \partial_{bb}^2 \left( \frac{(1+\Phi'(y))^2}{\delta^2} \eta^\epl \right) \right) & = 0.
+	\end{aligned}
+	\end{equation}
+	We now multiply the equation above by a continuous differentiable function $f \colon \R^2 \to \R^N$, $f = f(z,b)$, and integrate with respect to $x$, $z$, $b$ and $y$.
+Then integration by parts yields
+	\begin{equation}
+	\frac1\delta \int_{\R^3 \times [0,L]} \partial_z f(z,b) (x-z) \eta^\epl - \frac1\delta \int_{\R^3 \times [0,L]} \partial_b f(z,b) b \eta^\epl + \frac{\sigma}{\delta^2} \int_{\R^3 \times [0,L]} \partial_{bb}^2 f(z,b) (1+\Phi'(y))^2 \eta^\epl,
+	\end{equation}
+	which implies the following identity in $\R^N$
+	\begin{equation}
+	\delta \E^{\eta^\epl}\left[ \partial_b f(Z^\epl, \beta^\epl) \beta^\epl \right] = \sigma \E^{\eta^\epl} \left[ \partial_{bb}^2 f(Z^\epl, \beta^\epl) (1+\Phi'(Y^\epl)) \right] + \delta \E^{\eta^\epl} \left[ \partial_z f(Z^\epl, \beta^\epl) (X^\epl-Z^\epl) \right].
+	\end{equation}
+	Choosing
+	\begin{equation}
+	f(z,b) = \frac12 b^2 V''(z)
+	\end{equation}
+	we obtain
+	\begin{equation}
+	\begin{aligned}
+	\delta \E^{\eta^\epl}\left[ (\beta^\epl)^2 V''(Z^\epl) \right] &= \sigma \E^{\eta^\epl} \left[ V''(Z^\epl) (1+\Phi'(Y^\epl)) \right] + \frac\delta2 \E^{\eta^\epl} \left[ (\beta^\epl)^2 V'''(Z^\epl) (X^\epl-Z^\epl) \right] \\
+	&\eqdef \sigma \E^{\eta^\epl} \left[ V''(Z^\epl) (1+\Phi'(Y^\epl)) \right] + \widetilde R(\epl,\delta).
+	\end{aligned}
+	\end{equation}
+	We now consider the remainder and, applying Hölder's inequality, Lemma \ref{lem:distanceZandX}, Lemma \corr{boundedness of moments of $Z^\epl$} and \eqref{eq:estimate_beta}, we get for $p,q,r$ such that $1/p+1/q+1/r=1$
+	\begin{equation}
+	\left| \widetilde R(\epl,\delta) \right| \le C \delta \left( \E^{\eta^\epl} |\beta^\epl|^{2p} \right)^{1/p} \left( \E^{\eta^\epl} |V''(Z^\epl)|^q \right)^{1/q} \left( \E^{\eta^\epl} |X^\epl - Z^\epl|^r \right)^{1/r} \le C (\delta^{1/2} + \epl),
+	\end{equation}
+	which completes the proof.
 \end{proof}
@@
 \begin{lemma} \label{lem:quartet_convergence}
-	It holds
+	Let $\delta = \epl^\zeta$ with \corr{$\zeta \in (0,2)$}, then it holds
 	\begin{equation}
@@
 \begin{proof}
-
+	Let us introduce the notation 
+	\begin{equation}
+	\Delta(\epl) = \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right|,
+	\end{equation}
+	and note that the aim is to show that $\lim_{\epl \to 0} \Delta(\epl) = 0$. By the triangle inequality we get
+	\begin{equation}
+	\begin{aligned}
+	\Delta(\epl) \le& \left| \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] - \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] \right| \\
+	&+ \left| \sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] - \Sigma \E^{\phi^0} [V''(X)] \right| \\
+	\eqdef& \Delta_1(\epl) + \Delta_2(\epl).
+	\end{aligned}
+	\end{equation}
+	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularity} and Lemma \ref{lem:distanceZandX} we have
+	\begin{equation}
+	\Delta_1(\epl) \le C \E^{\eta^\epl} \abs{X^\epl - Z^\epl} \le C (\delta^{1/2} + \epl) = C (\epl^\zeta + \epl),
+	\end{equation}
+	which implies
+	\begin{equation}
+	\lim_{\epl \to 0} \Delta_1(\epl) = 0.
+	\end{equation}
+	We now consider $\Delta_2(\epl)$.
+Integrating equation \ref{eq:FPSDEquartet} with respect to $z$ and $b$ we obtain the Fokker-Planck equation for the stationary marginal distribution $\lambda \colon \R \times [0,L]$, $\lambda = \lambda(x,y)$, of the couple $(X^\epl,Y^\epl)$
+	\begin{equation}
+	\begin{aligned}
+	\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \lambda \right) + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \lambda \right) & \\
+	+ \sigma \left( \partial_{xx}^2 \lambda + \partial_{xy}^2 \left( \frac2\epl \lambda \right) + \partial_{yy}^2 \left( \frac{1}{\epl^2} \lambda \right) \right) &= 0,
+	\end{aligned}
+	\end{equation}
+	whose solution is given by
+	\begin{equation}
+	\lambda(x,y) = \frac{1}{C_\lambda} \exp \left\{ - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right\},
+	\end{equation}
+	where
+	\begin{equation}
+	\begin{aligned}
+	C_{\lambda} &= \int_\R \int_0^L \exp \left\{ - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right\} \dd x \dd y \\
+	&= \left( \int_\R \exp \left\{ - \frac\alpha\sigma V(x) \right\} \dd x \right) \left( \int_0^L \exp \left\{ - \frac1\sigma p(y) \right\} \dd y \right) \\
+	&\eqdef C_{\lambda_x} C_{\lambda_y}.
+	\end{aligned}
+	\end{equation}
+	Therefore, by equations \eqref{eq:SDE_HOM}, \eqref{eq:K_HOM} and \eqref{eq:phi0} we have
+	\begin{equation}
+	\begin{aligned}
+	\sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) (1 + \Phi'(y))^2 \frac{1}{C_\lambda} \exp \left\{ - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right\} \dd x \dd y \\
+	&= \sigma \left( \int_\R V''(x) \frac{1}{C_{\lambda_x}} \exp \left\{ - \frac\alpha\sigma V(x) \right\} \dd x \right) \\
+	&\qquad \qquad \times \left( \int_0^L (1+\Phi'(y))^2 \frac{1}{C_{\lambda_y}} \exp \left\{ - \frac1\sigma p(y) \right\} \dd y \right) \\
+	&= \sigma K \E^{\phi^0}[V''(X)] = \Sigma \E^{\phi^0}[V''(X)],
+	\end{aligned}
+	\end{equation}
+	which shows that $\Delta_2(\epl) = 0$ and completes the proof.
 \end{proof}

### 2020-03-24 CalNotes.tex
Z has bounded moments

@@
 	Then, if $A$ and $\Sigma$ are the coefficients of the homogenized equation \eqref{eq:SDE_HOM}, it holds
-	\begin{equation}
+	\begin{equation} \label{eq:phi0}
 		\phi^0(x) = \frac{1}{C_{\phi^0}} \exp\left(- \frac1{\Sigma} A\cdot V(x)\right), \quad \text{where } \quad C_{\phi^0} = \int_{\R} \exp\left(- \frac1{\Sigma} A\cdot V(x) \right) \dd x.
@@
 	where $\gamma$ is the lower incomplete Gamma function, which is bounded by the complete Gamma function $\Gamma(p+1)$ independently of the second argument.
+\end{proof}
+
+The following lemma shows that $Z^\epl$ has bounded moments of all orders.
+\begin{lemma} \label{lem:bounded_momentZ}
+	Under Assumption \ref{as:regularity}, let $Z^\epl$ be distributed as the invariant measure $\mu^\epl$ of the couple $(X^\epl, Z^\epl)^\top$.
+Then for any $p \geq 1$ there exists a constant $C > 0$ uniform in $\epl$ such that
+	\begin{equation}
+	\E^{\rho^\epl}|Z^\epl|^p \le C.
+	\end{equation}
+\end{lemma}
+\begin{proof} Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$.
+Let $Z_t^\epl$ be the corresponding filtered process.
+By definition of $Z^\epl_t$ and applying Lemma \ref{lem:FilterJensen} we have
+\begin{equation}
+\begin{aligned}
+	\E^{\phi^\epl} |Z_t^\epl|^p &= \E^{\phi^\epl} \left| \int_0^t k(t-s) X_s^\epl \dd s \right|^p \\
+	&\leq \int_0^t k(t - s) \E^{\phi^\epl} |X_s^\epl|^p \dd s,
+\end{aligned}
+\end{equation}
+which, together with the definition of $k$ and the fact that $X_s^\epl$ has bounded moments of all orders \cite[Corollary 5.4]{PaS07}, implies
+\begin{equation}
+\E^{\phi^\epl}|Z_t^\epl|^p \le C.
+\end{equation}
+In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $\widetilde C$ depending on the initial condition and $p$  
+\begin{equation}
+\E^{\rho^\epl} \abs{Z^\epl}^p \leq \E^{\phi^\epl}\abs{Z_t^\epl}^p + \widetilde C e^{-\lambda t},
+\end{equation}
+which, for $t$ sufficiently big, yields the desired result.
 \end{proof}
@@
 Moreover, $\beta_t^\epl$ and the remainder $R(\epl,\delta)$ satisfy for every $p \geq 1$ the estimates
-	\begin{equation} \label{eq:beta}
+	\begin{equation} \label{eq:estimate_beta}
 	\left( \E^{\phi^\epl} \abs{\beta_t^\epl}^p \right)^{1/p} \leq C \delta^{-1/2},
@@
 	\end{equation}
-	In order to obtain the bound \eqref{eq:beta} on $\beta_t^\epl$, let us remark that from \eqref{eq:rewriteI2} it holds for a constant $C > 0$ depending only on $p$ 
+	In order to obtain the bound \eqref{eq:estimate_beta} on $\beta_t^\epl$, let us remark that from \eqref{eq:rewriteI2} it holds for a constant $C > 0$ depending only on $p$ 
 	\begin{equation}
@@
 	\end{equation}
-	which proves the bound \eqref{eq:beta}.	Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
+	which proves the bound \eqref{eq:estimate_beta}. Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
 	\begin{equation}
@@
 	\end{equation}
-	We now consider the remainder and, applying Hölder's inequality, Lemma \ref{lem:distanceZandX}, Lemma \corr{boundedness of moments of $Z^\epl$} and \eqref{eq:estimate_beta}, we get for $p,q,r$ such that $1/p+1/q+1/r=1$
-	\begin{equation}
-	\left| \widetilde R(\epl,\delta) \right| \le C \delta \left( \E^{\eta^\epl} |\beta^\epl|^{2p} \right)^{1/p} \left( \E^{\eta^\epl} |V''(Z^\epl)|^q \right)^{1/q} \left( \E^{\eta^\epl} |X^\epl - Z^\epl|^r \right)^{1/r} \le C (\delta^{1/2} + \epl),
+	We now consider the remainder and, applying Hölder's inequality, Lemma \ref{cor:distanceZandX}, Lemma \ref{lem:bounded_momentZ} and \eqref{eq:estimate_beta}, we get for $p,q,r$ such that $1/p+1/q+1/r=1$
+	\begin{equation}
+	\left| \widetilde R(\epl,\delta) \right| \le C \delta \left( \E^{\eta^\epl} |\beta^\epl|^{2p} \right)^{1/p} \left( \E^{\eta^\epl} |V'''(Z^\epl)|^q \right)^{1/q} \left( \E^{\eta^\epl} |X^\epl - Z^\epl|^r \right)^{1/r} \le C (\delta^{1/2} + \epl),
 	\end{equation}
@@
 \begin{lemma} \label{lem:quartet_convergence}
-	Let $\delta = \epl^\zeta$ with \corr{$\zeta \in (0,2)$}, then it holds
+	Let $\delta = \epl^\zeta$ with $\zeta > 0$, then it holds
 	\begin{equation}
@@
 	\end{equation}
-	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularity} and Lemma \ref{lem:distanceZandX} we have
-	\begin{equation}
-	\Delta_1(\epl) \le C \E^{\eta^\epl} \abs{X^\epl - Z^\epl} \le C (\delta^{1/2} + \epl) = C (\epl^\zeta + \epl),
+	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularity} and Lemma \ref{cor:distanceZandX} we have
+	\begin{equation}
+	\Delta_1(\epl) \le C \E^{\eta^\epl} \abs{X^\epl - Z^\epl} \le C (\delta^{1/2} + \epl) = C (\epl^{\zeta/2} + \epl),
 	\end{equation}
@@
 	We now consider $\Delta_2(\epl)$.
-Integrating equation \ref{eq:FPSDEquartet} with respect to $z$ and $b$ we obtain the Fokker-Planck equation for the stationary marginal distribution $\lambda \colon \R \times [0,L]$, $\lambda = \lambda(x,y)$, of the couple $(X^\epl,Y^\epl)$
+Integrating equation \eqref{eq:FPSDEquartet} with respect to $z$ and $b$ we obtain the Fokker-Planck equation for the stationary marginal distribution $\lambda \colon \R \times [0,L]$, $\lambda = \lambda(x,y)$, of the couple $(X^\epl,Y^\epl)$
 	\begin{equation}
@@
 	\end{equation}
-	Moreover, due to \eqref{eq:beta} and \eqref{eq:remainder_zeta}, we have the following bounds for $J_2^\epl(t)$ and $J_3^\epl(t)$
+	Moreover, due to \eqref{eq:estimate_beta} and \eqref{eq:remainder_zeta}, we have the following bounds for $J_2^\epl(t)$ and $J_3^\epl(t)$
 	\begin{equation}

### 2020-03-25 CalNotes.tex
Partial update in restructuring the paper

@@
 
-In the rest of this section we will focus on the properties of the process $Z^\epl$ when it is considered together with the original process $X^\epl$.
-In particular, we focus on ergodic properties and multiscale convergence.
-Finally, we present and analyse unbiased estimators obtained with the filtering process.
-
-\subsection{Ergodic properties of the filter}\label{sec:ergodic}
+\begin{figure}[t]
+	\centering
+	\begin{tabular}{c}
+		\includegraphics[]{Figures/TrajD1} \\
+		\includegraphics[]{Figures/TrajD5} \\
+		\includegraphics[]{Figures/TrajD10}
+	\end{tabular}
+	\caption{\corr{Filtering a trajectory $X^\epl$ obtained with $V(x) = x^2 / 2$, $p(y) = \cos(y)$, $\alpha = 1$, $\sigma = 0.5$ and $\epl = 0.1$.
+The filtering width is $\delta = \{1, \sqrt{\epl}, \epl\}$ from top to bottom, respectively.}}
+	\label{fig:filter}
+\end{figure}
+
+\corr{Given a trajectory $X^\epl$ and the filtered data $Z^\epl$, the estimator of the drift coefficient we propose is given by
+\begin{equation}\label{eq:AHatMixed}
+	\widehat A^\epl_k(T) = - \widetilde M^{-1} \widetilde h,
+\end{equation}
+where we employ the subscript $k$ for reference to the filter's kernel in \eqref{eq:filter}, and where
+\begin{equation}\label{eq:MandHTilde}
+\widetilde M = \frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t, \qquad \text{and} \qquad \widetilde h = \frac{1}{T} \int_0^T V'(Z^\epl_t) \dd X^\epl_t.
+\end{equation}
+Let us remark that the formula above is obtained from \eqref{eq:MLE} by replacing only one instance of $X_t^\epl$ with $Z_t^\epl$ in both $M$ and $h$.
+In particular, it is fundamental for proving unbiasedness to keep in the definition of $h$ the differential of the original process $\d X^\epl_t$.
+Let us furthermore remark that $\widehat A^\epl_k(T)$ need not be the minimizer of some filtering-based likelihood function.
+In fact, if one were to replace $Z_t^\epl$ directly in \eqref{eq:Likelihood}, the symmetric part of the matrix $\widetilde M$ would appear and $\widehat A^\epl_k(T)$ would not be the minimizer.
+Therefore, the estimator $\widehat A^\epl_k(T)$ has to be thought of as a perturbation of $\widehat A^\epl(T)$, directly at the level of estimators and after the maximization procedure.
+The only theoretical guarantee which is still needed for the well-posedness of $\widehat A^\epl_k(T)$ is for $\widetilde M$ to be invertible, which we assume to be true and which we observed to hold in practice.
+
+Let us from now on consider $\beta = 1$.
+For this value of $\beta$, the parameter $\delta$ appearing in \eqref{eq:filter} regulates the width of the filtering window.
+In practice, larger values of $\delta$ will lead to trajectories which are smoother and for which fast-scale oscillations are practically canceled.
+Let us remark that the filtering width resembles the subsampling step employed for the estimator $\widehat A^\epl_\delta$ introduced and analyzed in \cite{PaS07}.
+For subsampling, the choice guaranteeing asymptotically unbiased results is $\delta = \epl^\zeta$ with $\zeta \in (0, 1)$, and a similar analysis is due for our filtering technique.
+For visualization purposes, we depict in Figure \ref{fig:filter} the filtered trajectory $Z^\epl$ for three different values of $\delta$, namely $\delta = \{1, \sqrt{\epl}, \epl\}$.
+With $\delta = 1$, all oscillations at the fast scale are canceled and the filtered trajectory $Z^\epl$ presents only slow-scale variations are present in $Z^\epl$.
+Reducing the value of $\delta$, fast-scale oscillations are progressively taken into account.
+
+In the following, we first focus on the ergodic properties of the process $Z^\epl$ when it is coupled with the process $X^\epl$.
+This analysis is practically independent of the choice of $\delta$, and is therefore presented on its own.
+Then, we focus on two different cases which depend on the choice of the width $\delta$ of the filter.
+First, we consider $\delta$ to be of the magnitude of the slow-scale variations, i.e., $\delta \propto \epl^0$.
+In this case, an analysis based on multiscale convergence is presented.
+We then move on to the case $\delta \propto \epl^\zeta$, and show how to choose the exponent $\zeta$ in order to obtain unbiased estimators.
+For this second case, we widely employ techniques and estimates which come from \cite{PaS07}.
+}
+
+\subsection{Ergodic properties}\label{sec:ergodic}
 
@@
 The first ingredient for verifying the ergodic properties of the two-dimensional process $(X^\epl, Z^\epl)^\top \defeq ((X^\epl_t, Z^\epl_t)^\top, 0 \leq t \leq T)$ is verifying that the measure induced by the stochastic process admits a smooth density with respect to the Lebesgue measure.
-Since noise is present only on the first component, this is a consequence of the theory of hypo-ellipticity, as summarized in the following Lemma, \corr{whose proof is given in Appendix \ref{ap:Proofs}.}
+Since noise is present only on the first component, this is a consequence of the theory of hypo-ellipticity, as summarized in the following Lemma, whose proof is given in Appendix \ref{ap:Proofs}.
 
@@
 In particular, we know that the process $X^\epl$ alone is geometrically ergodic \cite[Theorem 4.4]{MSH02}, and we wish the couple $(X^\epl, Z^\epl)^\top$ to be endowed with the same property.
-The following Lemma guarantees that the couple is indeed geometrically ergodic, \corr{and its proof is given in Appendix \ref{ap:Proofs}.}
+The following Lemma guarantees that the couple is indeed geometrically ergodic, and its proof is given in Appendix \ref{ap:Proofs}.
 
@@
 In a general case, it is not possible to find an explicit solution to \eqref{eq:FPsystem}.
-Nevertheless, it is possible to show some relevant properties of the solution itself, which are summarized in the following Lemma, \corr{whose proof is given in Appendix \ref{ap:Proofs}.}
+Nevertheless, it is possible to show some relevant properties of the solution itself, which are summarized in the following Lemma, whose proof is given in Appendix \ref{ap:Proofs}.
 
@@
 
-\subsection{Multiscale convergence}\label{sec:convMS}
-
-We now investigate the convergence of the couple $(X^\epl, Z^\epl)^\top$ with respect to the multiscale parameter $\epl \to 0$.
-In particular, it is known that the invariant measure of $X^\epl$ converges weakly to the invariant measure of $X$ solution of the homogenized equation \eqref{eq:SDE_HOM}.
-The following result, \corr{whose proof is given in Appendix \ref{ap:Proofs},} guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.
+\subsection{Filtering at the slow scale}\label{sec:Slow}
+
+\corr{In this section, we analyze the behavior of the filtering-based estimator $\widehat A^\epl_k(T)$ given in \eqref{eq:AHatMixed} when the filtering width $\delta$ is independent of $\epl$.
+In particular, we suppose there exist positive constants $C_1$ and $C_2$ independent of $\epl$ and $\delta$ such that $C_1 \epl^0 \leq \delta \leq C_2 \epl^0$.
+In the following, we will write more compactly that $\delta = \mathcal O(\epl^0)$.
+The analysis in this case is based on the convergence of the couple $(X^\epl, Z^\epl)^\top$ with respect to the multiscale parameter $\epl \to 0$.} In particular, it is known that the invariant measure of $X^\epl$ converges weakly to the invariant measure of $X$ solution of the homogenized equation \eqref{eq:SDE_HOM}.
+The following result, whose proof is given in Appendix \ref{ap:Proofs}, guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.
 
 \begin{lemma}\label{lem:convMeasure} Under Assumption \ref{as:regularity}, let $\mu^\epl$ be the invariant measure of the couple $(X^\epl, Z^\epl)^\top$ and let $(X_0^\epl, Z_0^\epl)^\top \sim \mu^\epl$.
-Then, the measure $\mu^\epl$ converges weakly to the measure $\mu^0(\d x, \d z) = \rho^0(x, z) \dd x \dd z$, whose density $\rho^0$ is the unique solution of the Fokker--Planck equation
+\corr{If $\delta = \mathcal O(\epl^0)$,} then the measure $\mu^\epl$ converges weakly to the measure $\mu^0(\d x, \d z) = \rho^0(x, z) \dd x \dd z$, whose density $\rho^0$ is the unique solution of the Fokker--Planck equation
 \begin{equation} \label{eq:FPsystem_homogenized}
@@
 \end{lemma}
+
+\begin{proof} Let $(X, Z)^\top \defeq \left((X_t, Z_t)^\top, 0\leq t \leq T\right)$ be the solution of
+	\begin{equation}
+	\label{eq:systemSDEHom}
+	\begin{aligned}
+	\d X_t &= -A \cdot V'(X_t) \dd t + \sqrt{2\Sigma} \dd W_t, \\
+	\d Z_t &= \frac{1}{\delta} \left ( X_t - Z_t \right ) \dd t,
+	\end{aligned}
+	\end{equation} 
+	with $(X_0, Z_0)^\top \sim \mu^0$.
+The arguments of Section \ref{sec:ergodic} can be repeated to conclude that the invariant measure of $(X, Z)^\top$ admits a smooth density $\rho^0$ which satisfies \eqref{eq:FPsystem_homogenized}.
+Moreover, standard homogenization theory (see e.g.
+\cite[Chapter 3]{BLP78}) guarantees that $(X^\epl,Z^\epl)^\top \to (X,Z)^\top$ for $\epl \to 0$ in law as random variables with values in $\mathcal C^0([0, T]; \R^2)$.
+The Portmanteau theorem can be employed to conclude that the measure $\mu^\epl$ converges weakly to $\mu^0$ for $\epl \to 0$.
+\end{proof}
 
@@
 
-\subsection{The filtering-based estimator}\label{sec:FilterMLE}
-
-We now consider the inference problem and propose our filtering-based estimator of the drift, which is formally given by the formula
-\begin{equation}\label{eq:AHatMixed}
-	\widehat A^\epl_k(T) = - \widetilde M^{-1} \widetilde h,
-\end{equation}
-where we employ the subscript $k$ for reference to the filter's kernel in \eqref{eq:filter}, and where
-\begin{equation}\label{eq:MandHTilde}
-	\widetilde M = \frac{1}{T} \int_0^T V'(Z^\epl_t) \otimes V'(X^\epl_t) \dd t, \qquad \text{and} \qquad \widetilde h = \frac{1}{T} \int_0^T V'(Z^\epl_t) \dd X^\epl_t.
-\end{equation}
-Let us remark that the formula above is obtained from \eqref{eq:MLE} by replacing only one instance of $X_t^\epl$ with $Z_t^\epl$ in both $M$ and $h$.
-In particular, it is fundamental for proving unbiasedness to keep in the definition of $h$ the differential of the original process $\d X^\epl_t$.
-Let us furthermore remark that $\widehat A^\epl_k(T)$ need not be the minimizer of some filtering-based likelihood function.
-In fact, if one were to replace $Z_t^\epl$ directly in \eqref{eq:Likelihood}, the symmetric part of the matrix $\widetilde M$ would appear and $\widehat A^\epl_k(T)$ would not be the minimizer.
-Therefore, the estimator $\widehat A^\epl_k(T)$ has to be thought of as a perturbation of $\widehat A^\epl(T)$, directly at the level of estimators and after the maximization procedure.
-The only theoretical guarantee which is still needed for the well-posedness of $\widehat A^\epl_k(T)$ is for $\widetilde M$ to be invertible, which we assume to be true and which we observed to hold in practice.
-
-%\begin{lemma}\label{lem:AHatWellPosed} Under Assumption \ref{as:regularity}, the matrix $\widetilde M$ defined in \eqref{eq:MandHTilde} is invertible a.s. 
-%\end{lemma}
-%\begin{proof} 
-%\todo: \corr{Idea.
-We don't need $\widetilde M$ to be symmetric positive definite (it is not) due to the comment just above the lemma.
-Nevertheless, if the functions $V_i'(x)$ are not such that the rows of $\widetilde M$ are identical for any $(X_t, Z_t)$, then the randomness in the entries should guarantee that $\det \widetilde M \neq 0$ with probability one.
-Still missing the (probably trivial) argument why this is true.}
-%\end{proof}
-
-We are now able to present the main result of unbiasedness of the filtering-based estimator.
-\begin{theorem}\label{thm:mainTheorem} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, and let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed}.
+\corr{We can now prove the main result, namely the convergence of the filtering-based estimator to the drift coefficient of the homogenized equation.}
+
+\begin{theorem}\label{thm:mainTheorem} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, and let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} \corr{with $\delta = \mathcal O(\epl^0)$}.
 If $\widetilde M$ is invertible, then
@@
 \begin{equation}\label{limit_estimator}
-\lim_{T \to \infty} I_1^\epl(T) = \E^{\rho^\epl} [V'(Z^\epl) \otimes V'(X^\epl)]^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ], \quad \text{a.s.}
+\lim_{T \to \infty} I_1^\epl(T) = \widetilde {\mathcal M}_\epl^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ], \quad \text{a.s.},
+\end{equation}
+where 
+\begin{equation}
+\widetilde {\mathcal M}_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ].
 \end{equation}
@@
 	\\
-	&= -  \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]\alpha + \sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z.
+	&= - \widetilde {\mathcal M}_\epl\alpha + \sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z.
 \end{align}
@@
 \begin{equation}
-\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z, \quad \text{a.s.}
+\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \widetilde {\mathcal M}_\epl^{-1} \sigma \int_{\R} \int_{\R} V'(z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z, \quad \text{a.s.}
 \end{equation}
@@
 \begin{equation} \label{eq:for_zeta}
-	\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ]^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)], \quad \text{a.s.}	
-\end{equation}
-We now pass to the limit as $\epl$ goes to zero and
-\begin{equation} \label{limit_estimator_2}
-	\lim_{\epl \to 0} \lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \E^{\rho^0} [ V'(Z) \otimes V'(X) ]^{-1} \E^{\rho^0}[(X - Z)^2 V''(Z)], \quad \text{a.s.},
-\end{equation}
-where the function $\rho^0$ is the density of the limit invariant distribution for $\epl \to 0$, as in Lemma \ref{lem:convMeasure}. Due to Corollary \ref{lem:FPMarginal_Hom}, we have
+	\lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \widetilde {\mathcal M}_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)], \quad \text{a.s.}	
+\end{equation}
+\corr{Since $\delta = \mathcal O(\epl^0)$ we can now safely} pass to the limit as $\epl$ goes to zero and
+\begin{equation} \label{eq:limit_estimator_2}
+	\lim_{\epl \to 0} \lim_{T \to \infty} I_1^\epl(T) = -\alpha + \frac1\delta \widetilde {\mathcal M}_0^{-1} \E^{\rho^0}[(X - Z)^2 V''(Z)], \quad \text{a.s.},
+\end{equation}
+where the function $\rho^0$ is the density of the limit invariant distribution for $\epl \to 0$, as in Lemma \ref{lem:convMeasure}, and where
+\begin{equation}
+	\widetilde {\mathcal M}_0 \defeq \E^{\rho^0} [ V'(Z) \otimes V'(X) ].
+\end{equation}
+Due to Corollary \ref{lem:FPMarginal_Hom}, we have
 \begin{equation}\label{eq:final_result}
@@
 	&= \left(\int_{\R} \int_{\R} V'(z) \otimes V'(x) \rho^0(x,z) \dd x \dd z\right)A\\
-	&=  \E^{\rho^0} [ V'(Z) \otimes V'(X) ]A.
+	&=  \widetilde {\mathcal M}_0 A.
 \end{aligned}
@@
 \begin{equation}
-	\lim_{T \to \infty} I_{2,1}^\epl(T) = \E^{\rho^\epl}\left[V'(Z^\epl) \otimes V'(X^\epl)\right]^{-1}\E^{\rho^\epl}\left[V'(Z^\epl) \otimes V'(Z^\epl)\right] \eqdef R^\epl,
+	\lim_{T \to \infty} I_{2,1}^\epl(T) = \widetilde {\mathcal M}_\epl^{-1}\E^{\rho^\epl}\left[V'(Z^\epl) \otimes V'(Z^\epl)\right] \eqdef R^\epl,
 \end{equation}
@@
 \end{proof}
-
-\corr{ CASE $\delta = \epl^\zeta$ (PROOF IN APPENDIX \ref{ap:zeta}).
+\corr{
+\begin{remark}\label{rem:deltaPower} Let us remark that the condition $\delta = \mathcal O(\epl^0)$ is necessary to pass from \eqref{eq:for_zeta} to \eqref{eq:limit_estimator_2} but is not needed before \eqref{eq:for_zeta}.
+Moreover, the term $I_2^\epl(t)$ in the proof vanishes a.s.
+independently of $\epl$.
+Therefore, in the analysis of the case $\delta = \mathcal O(\epl^\zeta)$ it will be sufficient for unbiasedness to show that
+	\begin{equation}
+		\lim_{\epl\to 0}\frac1\delta \widetilde {\mathcal M}_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)] = A,
+	\end{equation}
+	which is a non-trivial limit since $\delta \to 0$ for $\epl \to 0$.
+\end{remark}
+}
+
+\subsection{Filtering at faster scales}\label{sec:Fast}
+
+\corr{Remark for Assyr, Greg, Andrew: This section is all new, therefore it's ``red''. For easing the reading process, we write it here in black.}
+
+We now consider the case of the filtering width $\delta = \mathcal O(\epl^\zeta)$, where $\zeta > 0$ will be specified in the following.
+In this case, the filtered process resembles more the original process $X^\epl$, as can be noted in Figure \ref{fig:filter}.
+Moreover, the techniques employed for proving Theorem \ref{thm:mainTheorem} can only be partly exploited, as highlighted by Remark \ref{rem:deltaPower}.
+In fact, in order to prove unbiasedness it is necessary to characterize precisely the difference between the processes $Z^\epl$ and $X^\epl$.
+A first characterization is given by the following Proposition, whose proof ought to be found in Appendix \ref{ap:ProofDistance}.
+
+\begin{proposition} \label{prop:zeta} Let Assumption \ref{as:regularity} hold and $\epl,\delta>0$ be sufficiently small. Then, it holds for every $t > 0$ sufficiently big 
+	\begin{equation}
+	X_t^\epl - Z_t^\epl = \delta \beta^\epl_t + R(\epl,\delta),
+	\end{equation}
+	where the stochastic process $\beta_t^\epl$ is defined as
+	\begin{equation}\label{eq:defBeta}
+	\beta_t^\epl \defeq \sqrt{2\sigma} \int_0^t k(t-s)(1 + \Phi'(Y_s^\epl)) \dd W_s,
+	\end{equation}
+	where $\Phi$ is the solution of the cell problem \eqref{eq:CellProblem}, $W_s$ is the Brownian motion appearing in \eqref{eq:SDE_MS} and $Y_t^\epl = X_t^\epl / \epl$.
+Moreover, $\beta_t^\epl$ and the remainder $R(\epl,\delta)$ satisfy for every $p \geq 1$ the estimates
+	\begin{equation} \label{eq:estimate_beta}
+	\left( \E^{\phi^\epl} \abs{\beta_t^\epl}^p \right)^{1/p} \leq C \delta^{-1/2},
+	\end{equation}
+	and
+	\begin{equation} \label{eq:remainder_zeta}
+	\left( \E^{\phi^\epl} \left| R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta + \epl \right),
+	\end{equation}
+	where $C$ is independent of $\epl$ and $\delta$ and $\phi^\epl$ is the density of the invariant measure of $X^\epl$.
+\end{proposition}
+
+It is clear from the Proposition above that understanding the properties of the process $\beta_t^\epl$ is key to understanding the behavior of the difference between $X^\epl$ and $Z^\epl$.
+In particular, it is relevant to study the asymptotic properties of $\beta_t^\epl$ for long times
+
+\begin{lemma} \label{lem:quartet}
+	Let $\eta^\epl$ be the invariant measure of the quartet $(X^\epl, Y^\epl, Z^\epl, \beta^\epl)$. Then it holds
+	\begin{equation}
+	\delta \E^{\eta^\epl} \left[ (\beta^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
+	\end{equation}
+	where the remainder $\widetilde R(\epl,\delta)$ satisfies
+	\begin{equation} \label{eq:quartet_remainder}
+	\left| \widetilde R(\epl,\delta) \right| \le C \left( \delta^{1/2} + \epl \right).
+	\end{equation}
+\end{lemma}
+
+\begin{lemma} \label{lem:quartet_convergence}
+	Let $\delta = \epl^\zeta$ with $\zeta > 0$, then it holds
+	\begin{equation}
+	\lim_{\epl \to 0} \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] = \Sigma \E^{\phi^0} [V''(X)].
+	\end{equation}
+\end{lemma}
+
 \begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and let $\delta = \epl^\zeta$ with $\zeta \in (0,2)$.
@@
 		where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.
-\end{theorem}}
+\end{theorem}
+\begin{proof}
+	Let us introduce the notation
+	\begin{equation}
+	\mathcal A^\epl(\delta) = \frac1\delta \widetilde{\mathcal M}_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)],
+	\end{equation}
+	where
+	\begin{equation}
+	\widetilde{\mathcal M}_\epl = \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ].
+	\end{equation}
+	Then following the proof of Theorem \ref{thm:mainTheorem} we only need to show that if $\delta = \epl^\zeta$ with \corr{$\zeta \in (0,2)$} we have
+	\begin{equation}
+	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = A, \quad \text{in law}.
+	\end{equation}
+	Using Lemma \ref{prop:zeta} and geometric ergodicity (Lemma \ref{lem:ergodicity}), we have the following equality
+	\begin{equation}
+	\begin{aligned}
+	\mathcal A^\epl(\delta) &= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E [(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl)] \\
+	&= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E \left[ \left( \delta \beta_t^\epl + R(\epl,\delta) \right)^2 V''(Z_t^\epl) \right] \\
+	&\eqdef \widetilde{\mathcal M}_\epl^{-1} \lim_{t \to \infty} \left( J_1^\epl(t) + J_2^\epl(t) + J_3^\epl(t) \right),
+	\end{aligned}
+	\end{equation}
+	where and $\E$ denotes the expectation with respect to the Wiener measure and
+	\begin{equation}
+	\begin{aligned}
+	J_1^\epl(t) &= \delta \E \left[ (\beta_t^\epl)^2 V''(Z_t^\epl) \right], \\
+	J_2^\epl(t) &= 2 \E \left[ \beta_t^\epl R(\epl,\delta) V''(Z_t^\epl) \right], \\
+	J_3^\epl(t) &= \frac1\delta \E\left[ R(\epl,\delta)^2 V''(Z_t^\epl) \right].
+	\end{aligned}
+	\end{equation}
+	Let us consider the three terms separately. First, by geometric ergodicity and applying Lemma \ref{lem:quartet}, we get
+	\begin{equation}
+	\lim_{t \to \infty} J_1^\epl(t) = \delta \E^{\eta^\epl} \left[ (\beta^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
+	\end{equation}
+	and, by Lemma \ref{lem:quartet_convergence} and due to \eqref{eq:quartet_remainder}, we obtain
+	\begin{equation}
+	\lim_{\epl \to 0} \lim_{t \to \infty} J_1^\epl(t) = \Sigma \E^{\rho^0} [V''(X)].
+	\end{equation}
+	Moreover, due to \eqref{eq:estimate_beta} and \eqref{eq:remainder_zeta}, we have the following bounds for $J_2^\epl(t)$ and $J_3^\epl(t)$
+	\begin{equation}
+	\begin{aligned}
+	\abs{J_2^\epl(t)} &\le C \left( \delta^{1/2} + \epl \delta^{-1/2} \right), \\
+	\abs{J_3^\epl(t)} &\le C \left( \delta + \epl^2 \delta^{-1} \right).
+	\end{aligned}
+	\end{equation}
+	Furthermore, by Lemma \ref{lem:distanceMandTildeM} and weak convergence of the invariant measure, we have
+	\begin{equation}
+	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] \eqdef \mathcal M_0.
+	\end{equation}
+	Therefore
+	\begin{equation}
+	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \E^{\rho^0} [V''(X)],
+	\end{equation}
+	and, finally, an integration by parts yields
+	\begin{equation}
+	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \frac1\Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ] A = A,
+	\end{equation}
+	which implies the desired result.
+\end{proof}
 
@@
 \end{equation}
-Under Assumption \ref{as:regularity}, one can show that the posterior at time $T > 0$ is indeed given by $\mu_{T,\epl} = \mathcal N(m_{T,\epl}, C_{T,\epl})$.
-We are now interested in the asymptotic limit of the posterior distribution for $T \to \infty$ and for $\epl \to 0$.
-
-We can now state the main result for asymptotic convergence of the posterior distribution.
-\begin{theorem}\label{thm:BayesianBias} Under Assumption \ref{as:regularity}, the posterior measure $\mu_{T,\epl} = \mathcal N(m_{T,\epl}, C_{T,\epl})$ satisfies
-	\begin{equation}
-		\lim_{\epl \to 0}\lim_{T \to \infty} \mu_{T,\epl}(\cdot) = \delta(\cdot - \alpha), \quad \text{a.s.},
-	\end{equation}
-	weakly in the space of probability measures on $\R^N$, where $\delta$ is the Dirac measure on $\R^N$.
+Under Assumption \ref{as:regularity}, one can show that the posterior at time $T > 0$ is indeed given by $\mu_{T,\epl}(\cdotp\mid X^\epl) = \mathcal N(m_{T,\epl}, C_{T,\epl})$.
+\corr{In the following theorem, we show that the posterior distribution obtained with no pre-processing of the data contracts asymptotically to the drift coefficient of the unhomogenized equation.
+We characterize the contraction by verifying that the posterior measure concentrates in arbitrarily small balls.
+Let us finally remark that the measure $\mu_{T, \epl}$ is a random measure, and therefore contraction has to be considered averaged with respect to the Wiener measure.
+The choice of the contraction measure and some parts of the proof are taken from \cite[Theorem 5.2]{PSZ13}.
+
+\begin{theorem}\label{thm:BayesianBias} Under Assumption \ref{as:regularity}, the posterior measure $\mu_{T,\epl}(\cdotp\mid X^\epl) = \mathcal N(m_{T,\epl}, C_{T,\epl})$ satisfies for all $c > 0$
+	\begin{equation}
+		\lim_{\epl \to 0}\lim_{T \to \infty} \E \left[\mu_{T,\epl}\left(\{a\colon \norm{a-\alpha}_2\geq c\}\mid X^\epl\right)\right] = 0,
+	\end{equation}
+	where $\E$ denotes expectation with respect to the Wiener measure and $\alpha$ is the drift coefficient of the unhomogenized equation \eqref{eq:SDE_MS}.
 \end{theorem}
-\begin{proof} Let us first consider the covariance matrix. Hua's identity yields
+}
+\begin{proof} \corr{The proof of \cite[Theorem 5.2]{PSZ13} guarantees that if the trace of $C_{T,\epl}$ tends to zero and if the mean $m_{T,\epl}$ tends to $\alpha$, then the desired result holds.
+Indeed, the triangle inequality yields
+	\begin{equation}
+	\begin{aligned}
+		\E \left[\mu_{T,\epl}\left(\{a\colon \norm{a-\alpha}_2\geq c\}\mid X^\epl\right)\right] &\leq \E \left[\mu_{T,\epl}\left(\left\{a\colon \norm{a-m_{T,\epl}}_2\geq \frac{c}{2}\right\}\mid X^\epl\right)\right]\\
+		&\quad + \mathbb P\left(\norm{m_{T,\epl} - \alpha}_2 \geq \frac{c}{2}\right).
+	\end{aligned}
+	\end{equation}
+	If the mean converges in probability, then the second term vanishes. For the first term, Markov's inequality yields
+	\begin{equation}
+		\mu_{T,\epl}\left(\left\{a\colon \norm{a-m_{T,\epl}}_2\geq \frac{c}{2}\right\}\mid X^\epl\right) \leq \frac{4}{c^2}\int_{\R^N} \norm{a-m_{T,\epl}}_2^2 \, \mu_{T,\epl}(\d a\mid X^\epl),
+	\end{equation}
+	and a change of variable simply gives
+	\begin{equation}
+		\int_{\R^N} \norm{a-m_{T,\epl}}_2^2 \, \mu_{T,\epl}(\d a\mid X^\epl) = \trace(C_{T\epl}).
+	\end{equation}
+	This proves that we just to have to verify that the covariance matrix vanishes and that the mean tends to the coefficient $\alpha$.} Let us first consider the covariance matrix.
+An algebraic identity yields
 	\begin{equation}
@@
 
-\section{Proof of Lemmas}\label{ap:Proofs}
+\section{Proofs of Sections \ref{sec:ergodic}}\label{ap:Proofs}
 
@@
 	\end{equation}
-	and which proves \eqref{eq:marginalX}. \corr{In view of \eqref{eq:densityDecomposition} and \eqref{FPx}, equation \eqref{eq:FPsystem} can be rewritten as
+	and which proves \eqref{eq:marginalX}. In view of \eqref{eq:densityDecomposition} and \eqref{FPx}, equation \eqref{eq:FPsystem} can be rewritten as
 	\begin{equation}\label{eq:psiEqualityPDE}
@@
 	\end{equation}
-	We now multiply the equation above by a continuous differentiable function $f \colon \R^2 \to \R^N$, $f = f(x,z)$, and integrate with respect to $x$ and $z$. Then integration by parts yields
+	We now multiply the equation above by a continuous differentiable function $f \colon \R^2 \to \R^N$, $f = f(x,z)$, and integrate with respect to $x$ and $z$. Then an integration by parts yields
 	\begin{equation}
@@
 	\end{equation}
-	we obtain the desired result.}
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{lem:convMeasure}] Let $(X, Z)^\top \defeq \left((X_t, Z_t)^\top, 0\leq t \leq T\right)$ be the solution of
-	\begin{equation}
-	\label{eq:systemSDEHom}
-	\begin{aligned}
-	\d X_t &= -A \cdot V'(X_t) \dd t + \sqrt{2\Sigma} \dd W_t, \\
-	\d Z_t &= \frac{1}{\delta} \left ( X_t - Z_t \right ) \dd t,
-	\end{aligned}
-	\end{equation} 
-	with $(X_0, Z_0)^\top \sim \mu^0$.
-The arguments of Section \ref{sec:ergodic} can be repeated to conclude that the invariant measure of $(X, Z)^\top$ admits a smooth density $\rho^0$ which satisfies \eqref{eq:FPsystem_homogenized}.
-Moreover, standard homogenization theory (see e.g.
-\cite[Chapter 3]{BLP78}) guarantees that $(X^\epl,Z^\epl)^\top \to (X,Z)^\top$ for $\epl \to 0$ in law as random variables with values in $\mathcal C^0([0, T]; \R^2)$.
-The Portmanteau theorem can be employed to conclude that the measure $\mu^\epl$ converges weakly to $\mu^0$ for $\epl \to 0$.
-\end{proof}
-
-\section{Estimates on the filtered solution}
-
-In this section, we prove a series of results which quantify the distance between the multiscale solution $X_t^\epl$ and the filtered trajectory $Z_t^\epl$.
+	we obtain the desired result.
+\end{proof}
+
+\section{Proof of Proposition \ref{prop:zeta}}\label{ap:ProofDistance}
+
+\subsection{Preliminary estimates}
+In order to prove the characterization provided by Proposition \ref{prop:zeta}, we need to prove two additional results on the filter.
 First, we prove a Jensen-like inequality for the kernel of the filter.
@@
 
+We can now prove Lemma \ref{prop:zeta}. Denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
+\cite[Formula 5.8]{PaS07}
+\begin{equation}\label{eq:App_DiffXtXs}
+\begin{aligned}
+	X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
+	&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r - \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)),
+\end{aligned}
+\end{equation}
+which is obtained applying the Itô formula to $\Phi$, the solution of the cell problem \eqref{eq:CellProblem}.
+
+\subsection{Proof of Proposition \ref{prop:zeta}}
+
+Recall that by definition of $Z_t^\epl$ we have
+	\begin{equation}
+	X_t^\epl - Z_t^\epl = \int_0^t k(t-s) (X_t^\epl - X_s^\epl) \dd s + e^{-t/\delta}X_t^\epl.
+	\end{equation}
+	Plugging the decomposition \eqref{eq:App_DiffXtXs} into the equation above, we obtain
+	\begin{equation}
+	X_t^\epl - Z_t^\epl = I_1^\epl(t) + I_2^\epl(t) + I_3^\epl(t) + I_4^\epl(t),
+	\end{equation}
+	where
+	\begin{equation}
+	\begin{aligned}
+	I_1^\epl(t) &\defeq -\int_0^t k(t-s)\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r \dd s,\\
+	I_2^\epl(t) &\defeq \sqrt{2\sigma}\int_0^t k(t-s) \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r \dd s, \\
+	I_3^\epl(t) &\defeq - \epl \int_0^t k(t-s)(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)) \dd s,\\
+	I_4^\epl(t) &= e^{-t / \delta}X_t.
+	\end{aligned}
+	\end{equation}
+	Let us analyze the terms above singularly. For $I_1^\epl(t)$, one can show \cite[Proposition 5.8]{PaS07}
+	\begin{equation}
+	\int_s^t (\alpha \cdot V'(X_r^\epl)) (1 + \Phi'(Y^\epl_r)) \dd r = (t - s)(A \cdot V'(X_t^\epl)) + R_1^\epl(t-s),
+	\end{equation}
+	where the remainder $R_1^\epl$ satisfies 
+	\begin{equation}\label{eq:FirstTermPavStu}
+	\left(\E^{\phi^\epl}\abs{R_1^\epl(t-s)}^p\right)^{1/p} \leq C(\epl^2 + \epl(t-s)^{1/2}+(t-s)^{3/2}).
+	\end{equation}
+	Therefore, it holds 
+	\begin{equation}\label{eq:Diff_I1}
+	\begin{aligned}
+	I_1^\epl(t) &= -(A \cdot V'(X_t^\epl)) \int_0^t k(t-s) (t-s)\dd s + \int_0^t k(t-s)R_1^\epl(t-s) \dd s\\
+	&= -\delta (A \cdot  V'(X_t^\epl)) + e^{-t/\delta}(t + \delta)(A \cdot V'(X_t^\epl)) + \widetilde R_1^\epl(t),
+	\end{aligned}
+	\end{equation}
+	where we exploited the equality
+	\begin{equation}
+	\int_0^t k(t-s) (t-s) \dd s = \delta - e^{-t/\delta}(t + \delta),
+	\end{equation}
+	and where
+	\begin{equation}
+	\widetilde R_1^\epl(t) \defeq \int_0^t k(t-s)R_1^\epl(t-s) \dd s.
+	\end{equation}
+	Now, Lemma \ref{lem:FilterJensen}, the inequality \eqref{eq:FirstTermPavStu} and Lemma \ref{lem:FilterPoly} yield for all $p \geq 1$
+	\begin{equation}
+	\begin{aligned}
+		\E^{\phi^\epl}\abs{\widetilde R_1^\epl(t)}^p &\leq C \int_0^t k(t-s)\E^{\phi^\epl} \abs{R_1^\epl(t-s)}^p \dd s\\
+		&\leq C \int_0^t k(t-s)(\epl^{2p} + \epl^p(t-s)^{p/2}+(t-s)^{3p/2}) \dd s\\
+		&\leq C \left( \epl^{2p} + \epl^p \delta^{p/2} + \delta^{3p/2} \right),
+	\end{aligned}
+	\end{equation}
+	where $C$ is a positive constant independent of $\epl$ and $\delta$. Therefore, for $t$ sufficiently big and $\delta$ sufficiently small, we get
+	\begin{equation}
+		\left(\E^{\phi^\epl}\abs{I_1^\epl(t)}^{p}\right)^{1/p} \leq C \left( \delta + \epl^2 + \epl \delta^{1/2} \right).
+	\end{equation}
+	We now consider the second term. Let us introduce the notation  
+	\begin{equation}
+		Q_t^\epl \defeq \int_0^t \left(1 + \Phi'(Y_r^\epl)\right) \dd W_r,
+	\end{equation}
+	and therefore rewrite
+	\begin{equation}
+		I_2^\epl(t) = \sqrt{2\sigma} \int_0^t k(t-s)(Q_t^\epl - Q_s^\epl) \dd s.
+	\end{equation}
+	An application of the Itô formula to $u(s, Q_s^\epl)$ where $u(s, x) = k(t-s)x$ yields
+	\begin{equation}\label{eq:rewriteI2}
+	\begin{aligned}
+		I_2^\epl(t) &= \sqrt{2\sigma} \left(Q_t^\epl\int_0^t k(t-s) \dd s - Q_t^\epl + \delta \int_0^t k(t-s)\left(1 + \Phi'(Y_s^\epl)\right) \dd W_s\right)\\
+		  			&= \delta \beta_t^\epl - \sqrt{2\sigma} e^{-t/\delta} Q_t^\epl \eqdef \delta \beta_t^\epl - R_2^\epl(t).
+	\end{aligned}
+	\end{equation}
+	where $\beta_t^\epl$ is defined in \eqref{eq:defBeta}. For the remainder $R_2^\epl(t)$, let us remark that for all $p \geq 1$ it holds
+	\begin{equation}\label{eq:BoundQ}
+	\begin{aligned}
+		\left(\E\abs{Q_t^\epl}^p\right)^2 \leq \E\abs{Q_t^\epl}^{2p} \leq Ct^{p-1}\int_0^t \E \abs{1 + \Phi'(Y_r^\epl)}^{2p} \dd r \leq C t^p
+	\end{aligned}
+	\end{equation}
+	where we applied Jensen's inequality, an estimate for the moments of stochastic integrals \cite[Formula (3.25), p. 163]{KaS91} and the boundedness of $\Phi$. Therefore we have
+	\begin{equation}\label{eq:boundR2}
+		\left( \E^{\phi^\epl}\abs{R_2^\epl(t)}^p \right)^{1/p} \leq C \sqrt{t} e^{-t/\delta}.
+	\end{equation}
+	In order to obtain the bound \eqref{eq:estimate_beta} on $\beta_t^\epl$, let us remark that from \eqref{eq:rewriteI2} it holds for a constant $C > 0$ depending only on $p$ 
+	\begin{equation}
+		\left(\E\abs{\beta_t^\epl}^p\right)^{1/p}\leq C \delta^{-1}\left(\E\abs{I_2^\epl(t)}^p\right)^{1/p} + C \delta^{-1} \left(\E\abs{R_2^\epl(t)}^p\right)^{1/p}.
+	\end{equation}
+	The second term is bounded exponentially fast with respect to $t$ and $\delta$ due to \eqref{eq:boundR2}.
+For the first term, applying Lemma \ref{lem:FilterJensen}, the inequality \cite[Formula (3.25), p.
+163]{KaS91} and Lemma \ref{lem:FilterPoly} we obtain for a constant $C > 0$ independent of $\delta$ and $t$
+	\begin{equation}
+	\begin{aligned}
+		\E\abs{I_2^\epl(t)}^p &\leq C \int_0^t k(t-s) \E\abs{Q_t - Q_s}^p \dd s \\
+		&\leq C\int_0^t k(t-s)(t-s)^{p/2} \dd s \leq C\delta^{p/2}.
+	\end{aligned}
+	\end{equation} 
+	Therefore, it holds
+	\begin{equation}
+		\left(\E\abs{\beta_t^\epl}^p\right)^{1/p}\leq C \delta^{-1/2},
+	\end{equation}
+	which proves the bound \eqref{eq:estimate_beta}. Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
+	\begin{equation}
+	\abs{I_3^\epl(t)} \leq C \epl, 
+	\end{equation}
+	almost surely. Finally, due to \cite[Corollary 5.4]{PaS07}, we know that $X_t^\epl$ has bounded moments of all orders and therefore
+	\begin{equation}
+	\left(\E^{\phi^\epl} \abs{I_4^\epl(t)}^p\right)^{1/p} \leq C e^{-t/\delta},
+	\end{equation}
+	which concludes the proof. \qed
+
+\section{Proofs of Section \ref{sec:Fast}} \label{ap:zeta}
+
+\subsection{Preliminary estimates}
+
 The following lemma shows that $Z^\epl$ has bounded moments of all orders.
@@
 
-%\begin{lemma}\label{lem:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
-Then, if $\delta \leq 1$, it holds for any $p \geq 1$
-%	\begin{equation}
-%		\left(\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p\right)^{1/p} \leq C\left(\epl + \delta^{1/2}\right),
-%	\end{equation}
-%	for a constant $C > 0$ independent of $\epl$ and $\delta$.
-%\end{lemma}
-%\begin{proof} Let $X_t^\epl$ be at stationarity with respect to its invariant measure, which we recall having density denoted as $\phi^\epl$.
-Let $Z_t^\epl$ be the corresponding filtered process.
-By definition of $Z^\epl_t$ we have
-%	\begin{equation}
-%	\begin{aligned}
-%		X_t^\epl - Z_t^\epl &= X_t^\epl - \int_0^t k(t-s) X_s^\epl \dd s\\
-%		&= \int_0^t k(t - s) \left(X_t^\epl - X_s^\epl\right) \dd s + e^{-t/\delta} X^\epl_t.
-%	\end{aligned}
-%	\end{equation}
-%	Therefore, Lemma \ref{lem:FilterJensen} yields for a constant $C > 0$ depending only on $p$
-%	\begin{equation}
-%		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\int_0^t \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^p k(t-s) \dd s + Ce^{-pt/\delta} \E^{\phi^\epl} \abs{X^\epl_t}^p.
-%	\end{equation}
-%	Moreover, the estimate
-%	\begin{equation}
-%		\E^{\phi^\epl}\abs{X_t^\epl - X_s^\epl}^p \leq C\left(\epl^p + (t-s)^p + (t-s)^{p/2}\right),
-%	\end{equation}
-%	holds for all $t > s$ due to \cite[Lemma 6.1]{PaS07}.
-Finally, since the moments of $X_t^\epl$ are bounded \cite[Corollary 5.4]{PaS07} and due to Lemma \ref{lem:FilterPoly} there exists a constant $C > 0$ depending only on $p$ such that
-%	\begin{equation}
-%		\E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p \leq C\left(\epl^p + \delta^{p/2} + e^{-pt/\delta}\right).
-%	\end{equation}
-%	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
-In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$
-%	\begin{equation}
-%	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + Ce^{-\lambda t},
-%	\end{equation}
-%	which, for $t$ sufficiently big, yields the desired result.
-%\end{proof}
-
-The following result is a quantification of the difference between $X^\epl_t$ and $Z^\epl_t$. In particular, denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
-\cite[Formula 5.8]{PaS07}
-\begin{equation}\label{eq:App_DiffXtXs}
-\begin{aligned}
-	X_t^\epl - X_s^\epl &= -\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r\\
-	&\quad +\sqrt{2\sigma} \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r - \epl(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)),
-\end{aligned}
-\end{equation}
-which is obtained applying the Itô formula to $\Phi$, the solution of the cell problem \eqref{eq:CellProblem}.
-
-\begin{lemma} \label{lem:zeta} Let Assumption \ref{as:regularity} hold and $\epl,\delta>0$ be sufficiently small. Then, it holds for every $t > 0$ sufficiently big 
-	\begin{equation}
-		X_t^\epl - Z_t^\epl = \delta \beta^\epl_t + R(\epl,\delta),
-	\end{equation}
-	where the stochastic process $\beta_t^\epl$ is defined as
-	\begin{equation}\label{eq:defBeta}
-		\beta_t^\epl \defeq \sqrt{2\sigma} \int_0^t k(t-s)(1 + \Phi'(Y_s^\epl)) \dd W_s,
-	\end{equation}
-	where $\Phi$ is the solution of the cell problem \eqref{eq:CellProblem}, $W_s$ is the Brownian motion appearing in \eqref{eq:SDE_MS} and $Y_t^\epl = X_t^\epl / \epl$.
-Moreover, $\beta_t^\epl$ and the remainder $R(\epl,\delta)$ satisfy for every $p \geq 1$ the estimates
-	\begin{equation} \label{eq:estimate_beta}
-	\left( \E^{\phi^\epl} \abs{\beta_t^\epl}^p \right)^{1/p} \leq C \delta^{-1/2},
-	\end{equation}
-	and
-	\begin{equation} \label{eq:remainder_zeta}
-	\left( \E^{\phi^\epl} \left| R(\epl,\delta) \right|^p \right)^{1/p} \le C \left( \delta + \epl \right),
-	\end{equation}
-	where $C$ is independent of $\epl$ and $\delta$ and $\phi^\epl$ is the density of the invariant measure of $X^\epl$.
-\end{lemma}
-\begin{proof} Recall that by definition of $Z_t^\epl$ we have
-	\begin{equation}
-	X_t^\epl - Z_t^\epl = \int_0^t k(t-s) (X_t^\epl - X_s^\epl) \dd s + e^{-t/\delta}X_t^\epl.
-	\end{equation}
-	Plugging the decomposition \eqref{eq:App_DiffXtXs} into the equation above, we obtain
-	\begin{equation}
-	X_t^\epl - Z_t^\epl = I_1^\epl(t) + I_2^\epl(t) + I_3^\epl(t) + I_4^\epl(t),
-	\end{equation}
-	where
-	\begin{equation}
-	\begin{aligned}
-	I_1^\epl(t) &\defeq -\int_0^t k(t-s)\int_s^t (\alpha \cdot V'(X_r^\epl))(1 + \Phi'(Y^\epl_r)) \dd r \dd s,\\
-	I_2^\epl(t) &\defeq \sqrt{2\sigma}\int_0^t k(t-s) \int_s^t (1 + \Phi'(Y_r^\epl)) \dd W_r \dd s, \\
-	I_3^\epl(t) &\defeq - \epl \int_0^t k(t-s)(\Phi(Y^\epl_t)-\Phi(Y^\epl_s)) \dd s,\\
-	I_4^\epl(t) &= e^{-t / \delta}X_t.
-	\end{aligned}
-	\end{equation}
-	Let us analyze the terms above singularly. For $I_1^\epl(t)$, one can show \cite[Proposition 5.8]{PaS07}
-	\begin{equation}
-	\int_s^t (\alpha \cdot V'(X_r^\epl)) (1 + \Phi'(Y^\epl_r)) \dd r = (t - s)(A \cdot V'(X_t^\epl)) + R_1^\epl(t-s),
-	\end{equation}
-	where the remainder $R_1^\epl$ satisfies 
-	\begin{equation}\label{eq:FirstTermPavStu}
-	\left(\E^{\phi^\epl}\abs{R_1^\epl(t-s)}^p\right)^{1/p} \leq C(\epl^2 + \epl(t-s)^{1/2}+(t-s)^{3/2}).
-	\end{equation}
-	Therefore, it holds 
-	\begin{equation}\label{eq:Diff_I1}
-	\begin{aligned}
-	I_1^\epl(t) &= -(A \cdot V'(X_t^\epl)) \int_0^t k(t-s) (t-s)\dd s + \int_0^t k(t-s)R_1^\epl(t-s) \dd s\\
-	&= -\delta (A \cdot  V'(X_t^\epl)) + e^{-t/\delta}(t + \delta)(A \cdot V'(X_t^\epl)) + \widetilde R_1^\epl(t),
-	\end{aligned}
-	\end{equation}
-	where we exploited the equality
-	\begin{equation}
-	\int_0^t k(t-s) (t-s) \dd s = \delta - e^{-t/\delta}(t + \delta),
-	\end{equation}
-	and where
-	\begin{equation}
-	\widetilde R_1^\epl(t) \defeq \int_0^t k(t-s)R_1^\epl(t-s) \dd s.
-	\end{equation}
-	Now, Lemma \ref{lem:FilterJensen}, the inequality \eqref{eq:FirstTermPavStu} and Lemma \ref{lem:FilterPoly} yield for all $p \geq 1$
-	\begin{equation}
-	\begin{aligned}
-		\E^{\phi^\epl}\abs{\widetilde R_1^\epl(t)}^p &\leq C \int_0^t k(t-s)\E^{\phi^\epl} \abs{R_1^\epl(t-s)}^p \dd s\\
-		&\leq C \int_0^t k(t-s)(\epl^{2p} + \epl^p(t-s)^{p/2}+(t-s)^{3p/2}) \dd s\\
-		&\leq C \left( \epl^{2p} + \epl^p \delta^{p/2} + \delta^{3p/2} \right),
-	\end{aligned}
-	\end{equation}
-	where $C$ is a positive constant independent of $\epl$ and $\delta$. Therefore, for $t$ sufficiently big and $\delta$ sufficiently small, we get
-	\begin{equation}
-		\left(\E^{\phi^\epl}\abs{I_1^\epl(t)}^{p}\right)^{1/p} \leq C \left( \delta + \epl^2 + \epl \delta^{1/2} \right).
-	\end{equation}
-	We now consider the second term. Let us introduce the notation  
-	\begin{equation}
-		Q_t^\epl \defeq \int_0^t \left(1 + \Phi'(Y_r^\epl)\right) \dd W_r,
-	\end{equation}
-	and therefore rewrite
-	\begin{equation}
-		I_2^\epl(t) = \sqrt{2\sigma} \int_0^t k(t-s)(Q_t^\epl - Q_s^\epl) \dd s.
-	\end{equation}
-	An application of the Itô formula to $u(s, Q_s^\epl)$ where $u(s, x) = k(t-s)x$ yields
-	\begin{equation}\label{eq:rewriteI2}
-	\begin{aligned}
-		I_2^\epl(t) &= \sqrt{2\sigma} \left(Q_t^\epl\int_0^t k(t-s) \dd s - Q_t^\epl + \delta \int_0^t k(t-s)\left(1 + \Phi'(Y_s^\epl)\right) \dd W_s\right)\\
-		  			&= \delta \beta_t^\epl - \sqrt{2\sigma} e^{-t/\delta} Q_t^\epl \eqdef \delta \beta_t^\epl - R_2^\epl(t).
-	\end{aligned}
-	\end{equation}
-	where $\beta_t^\epl$ is defined in \eqref{eq:defBeta}. For the remainder $R_2^\epl(t)$, let us remark that for all $p \geq 1$ it holds
-	\begin{equation}\label{eq:BoundQ}
-	\begin{aligned}
-		\left(\E\abs{Q_t^\epl}^p\right)^2 \leq \E\abs{Q_t^\epl}^{2p} \leq Ct^{p-1}\int_0^t \E \abs{1 + \Phi'(Y_r^\epl)}^{2p} \dd r \leq C t^p
-	\end{aligned}
-	\end{equation}
-	where we applied Jensen's inequality, an estimate for the moments of stochastic integrals \cite[Formula (3.25), p. 163]{KaS91} and the boundedness of $\Phi$. Therefore we have
-	\begin{equation}\label{eq:boundR2}
-		\left( \E^{\phi^\epl}\abs{R_2^\epl(t)}^p \right)^{1/p} \leq C \sqrt{t} e^{-t/\delta}.
-	\end{equation}
-	In order to obtain the bound \eqref{eq:estimate_beta} on $\beta_t^\epl$, let us remark that from \eqref{eq:rewriteI2} it holds for a constant $C > 0$ depending only on $p$ 
-	\begin{equation}
-		\left(\E\abs{\beta_t^\epl}^p\right)^{1/p}\leq C \delta^{-1}\left(\E\abs{I_2^\epl(t)}^p\right)^{1/p} + C \delta^{-1} \left(\E\abs{R_2^\epl(t)}^p\right)^{1/p}.
-	\end{equation}
-	The second term is bounded exponentially fast with respect to $t$ and $\delta$ due to \eqref{eq:boundR2}.
-For the first term, applying Lemma \ref{lem:FilterJensen}, the inequality \cite[Formula (3.25), p.
-163]{KaS91} and Lemma \ref{lem:FilterPoly} we obtain for a constant $C > 0$ independent of $\delta$ and $t$
-	\begin{equation}
-	\begin{aligned}
-		\E\abs{I_2^\epl(t)}^p &\leq C \int_0^t k(t-s) \E\abs{Q_t - Q_s}^p \dd s \\
-		&\leq C\int_0^t k(t-s)(t-s)^{p/2} \dd s \leq C\delta^{p/2}.
-	\end{aligned}
-	\end{equation} 
-	Therefore, it holds
-	\begin{equation}
-		\left(\E\abs{\beta_t^\epl}^p\right)^{1/p}\leq C \delta^{-1/2},
-	\end{equation}
-	which proves the bound \eqref{eq:estimate_beta}. Let us now consider $I_3^\epl(t)$. Since $\Phi$ is bounded, we simply have
-	\begin{equation}
-	\abs{I_3^\epl(t)} \leq C \epl, 
-	\end{equation}
-	almost surely. Finally, due to \cite[Corollary 5.4]{PaS07}, we know that $X_t^\epl$ has bounded moments of all orders and therefore
-	\begin{equation}
-	\left(\E^{\phi^\epl} \abs{I_4^\epl(t)}^p\right)^{1/p} \leq C e^{-t/\delta},
-	\end{equation}
-	which concludes the proof.
-\end{proof}
-
-Corollary \ref{cor:distanceZandX} is a direct consequence of Lemma \ref{lem:zeta} and provides a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.
+Corollary \ref{cor:distanceZandX} is a direct consequence of Lemma \ref{prop:zeta} and provides a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.
 
@@
 \begin{proof}
-	Let $p \geq 1$, then due to Lemma \ref{lem:zeta} there exists a constant $C > 0$ depending only on $p$ such that
+	Let $p \geq 1$, then due to Lemma \ref{prop:zeta} there exists a constant $C > 0$ depending only on $p$ such that
 	\begin{equation}
@@
 
-\section{Proof of Theorem \ref{thm:mainTheorem_zeta}} \label{ap:zeta}
-
-\begin{lemma} \label{lem:quartet}
-	Let $\eta^\epl$ be the invariant measure of the quartet $(X^\epl, Y^\epl, Z^\epl, \beta^\epl)$. Then it holds
-	\begin{equation}
-	\delta \E^{\eta^\epl} \left[ (\beta^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
-	\end{equation}
-	where the remainder $\widetilde R(\epl,\delta)$ satisfies
-	\begin{equation} \label{eq:quartet_remainder}
-	\left| \widetilde R(\epl,\delta) \right| \le C \left( \delta^{1/2} + \epl \right).
-	\end{equation}
-\end{lemma}
-\begin{proof}
+\subsection{Proof of Lemmas \ref{lem:quartet} and \ref{lem:quartet_convergence}}
+
+\begin{proof}[Proof of Lemma \ref{lem:quartet}]
 	Let us consider the following system of stochastic differential equations for the processes $X_t^\epl, Z_t^\epl, \beta_t^\epl, Y_t^\epl$
@@
 
-\begin{lemma} \label{lem:quartet_convergence}
-	Let $\delta = \epl^\zeta$ with $\zeta > 0$, then it holds
-	\begin{equation}
-	\lim_{\epl \to 0} \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] = \Sigma \E^{\phi^0} [V''(X)].
-	\end{equation}
-\end{lemma}
-\begin{proof}
+\begin{proof}[Proof of Lemma \ref{lem:quartet_convergence}]
 	Let us introduce the notation 
@@
 
-\begin{proof}[Proof of Theorem \ref{thm:mainTheorem_zeta}]
-	Let us introduce the notation
-	\begin{equation}
-		\mathcal A^\epl(\delta) = \frac1\delta \widetilde{\mathcal M}_\epl^{-1} \E^{\rho^\epl}[(X^\epl - Z^\epl)^2 V''(Z^\epl)],
-	\end{equation}
-	where
-	\begin{equation}
-		\widetilde{\mathcal M}_\epl = \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ].
-	\end{equation}
-	Then following the proof of Theorem \ref{thm:mainTheorem} we only need to show that if $\delta = \epl^\zeta$ with \corr{$\zeta \in (0,2)$} we have
-	\begin{equation}
-		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = A, \quad \text{in law}.
-	\end{equation}
-	Using Lemma \ref{lem:zeta} and geometric ergodicity (Lemma \ref{lem:ergodicity}), we have the following equality
-	\begin{equation}
-	\begin{aligned}
-		\mathcal A^\epl(\delta) &= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E [(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl)] \\
-		&= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E \left[ \left( \delta \beta_t^\epl + R(\epl,\delta) \right)^2 V''(Z_t^\epl) \right] \\
-		&\eqdef \widetilde{\mathcal M}_\epl^{-1} \lim_{t \to \infty} \left( J_1^\epl(t) + J_2^\epl(t) + J_3^\epl(t) \right),
-	\end{aligned}
-	\end{equation}
-	where and $\E$ denotes the expectation with respect to the Wiener measure and
-	\begin{equation}
-	\begin{aligned}
-		J_1^\epl(t) &= \delta \E \left[ (\beta_t^\epl)^2 V''(Z_t^\epl) \right], \\
-		J_2^\epl(t) &= 2 \E \left[ \beta_t^\epl R(\epl,\delta) V''(Z_t^\epl) \right], \\
-		J_3^\epl(t) &= \frac1\delta \E\left[ R(\epl,\delta)^2 V''(Z_t^\epl) \right].
-	\end{aligned}
-	\end{equation}
-	Let us consider the three terms separately. First, by geometric ergodicity and applying Lemma \ref{lem:quartet}, we get
-	\begin{equation}
-	\lim_{t \to \infty} J_1^\epl(t) = \delta \E^{\eta^\epl} \left[ (\beta^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
-	\end{equation}
-	and, by Lemma \ref{lem:quartet_convergence} and due to \eqref{eq:quartet_remainder}, we obtain
-	\begin{equation}
-	\lim_{\epl \to 0} \lim_{t \to \infty} J_1^\epl(t) = \Sigma \E^{\rho^0} [V''(X)].
-	\end{equation}
-	Moreover, due to \eqref{eq:estimate_beta} and \eqref{eq:remainder_zeta}, we have the following bounds for $J_2^\epl(t)$ and $J_3^\epl(t)$
-	\begin{equation}
-	\begin{aligned}
-		\abs{J_2^\epl(t)} &\le C \left( \delta^{1/2} + \epl \delta^{-1/2} \right), \\
-		\abs{J_3^\epl(t)} &\le C \left( \delta + \epl^2 \delta^{-1} \right).
-	\end{aligned}
-	\end{equation}
-	Furthermore, by Lemma \ref{lem:distanceMandTildeM} and weak convergence of the invariant measure, we have
-	\begin{equation}
-		\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] \eqdef \mathcal M_0.
-	\end{equation}
-	Therefore
-	\begin{equation}
-		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \E^{\rho^0} [V''(X)],
-	\end{equation}
-	and, finally, an integration by parts yields
-	\begin{equation}
-		\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \frac1\Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ] A = A,
-	\end{equation}
-	which implies the desired result.
-\end{proof}
-
 \section{Proof of Theorem \ref{thm:mainTheoremTilde}}\label{ap:EstimatorTilde}

### 2020-03-26 CalNotes.tex
Restructuring done. Double-check to do

@@
 The first ingredient for verifying the ergodic properties of the two-dimensional process $(X^\epl, Z^\epl)^\top \defeq ((X^\epl_t, Z^\epl_t)^\top, 0 \leq t \leq T)$ is verifying that the measure induced by the stochastic process admits a smooth density with respect to the Lebesgue measure.
-Since noise is present only on the first component, this is a consequence of the theory of hypo-ellipticity, as summarized in the following Lemma, whose proof is given in Appendix \ref{ap:Proofs}.
+Since noise is present only on the first component, this is a consequence of the theory of hypo-ellipticity, as summarized in the following Lemma, whose proof is given in Appendix \ref{ap:ProofsErgodic}.
 
@@
 In particular, we know that the process $X^\epl$ alone is geometrically ergodic \cite[Theorem 4.4]{MSH02}, and we wish the couple $(X^\epl, Z^\epl)^\top$ to be endowed with the same property.
-The following Lemma guarantees that the couple is indeed geometrically ergodic, and its proof is given in Appendix \ref{ap:Proofs}.
+The following Lemma guarantees that the couple is indeed geometrically ergodic, and its proof is given in Appendix \ref{ap:ProofsErgodic}.
 
@@
 In a general case, it is not possible to find an explicit solution to \eqref{eq:FPsystem}.
-Nevertheless, it is possible to show some relevant properties of the solution itself, which are summarized in the following Lemma, whose proof is given in Appendix \ref{ap:Proofs}.
+Nevertheless, it is possible to show some relevant properties of the solution itself, which are summarized in the following Lemma, whose proof is given in Appendix \ref{ap:ProofsErgodic}.
 
@@
 The analysis in this case is based on the convergence of the couple $(X^\epl, Z^\epl)^\top$ with respect to the multiscale parameter $\epl \to 0$.} In particular, it is known that the invariant measure of $X^\epl$ converges weakly to the invariant measure of $X$ solution of the homogenized equation \eqref{eq:SDE_HOM}.
-The following result, whose proof is given in Appendix \ref{ap:Proofs}, guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.
+The following result, whose proof is given in Appendix \ref{ap:ProofsErgodic}, guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.
 
@@
 
-\corr{We can now prove the main result, namely the convergence of the filtering-based estimator to the drift coefficient of the homogenized equation.}
+\corr{Let us introduce a notation which will be used throughout the rest of the paper. We denote
+\begin{equation}
+	\widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl)\otimes V'(X^\epl)], \quad \widetilde{\mathcal M}_0 \defeq \E^{\rho^0}[V'(Z)\otimes V'(X)],
+\end{equation}
+\i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to Lemma \ref{lem:convMeasure}.
+We can now introduce the main result, namely the convergence of the filtering-based estimator to the drift coefficient of the homogenized equation.}
 
@@
 \end{equation}
-We study the terms $I_1^\epl(T)$ and $I_2^\epl(T)$ separately. The ergodic theorem applied to $I_1^\epl(T)$ yields
+We study the terms $I_1^\epl(T)$ and $I_2^\epl(T)$ separately. First, the ergodic theorem applied to $I_1^\epl(T)$ yields
 \begin{equation}\label{limit_estimator}
-\lim_{T \to \infty} I_1^\epl(T) = \widetilde {\mathcal M}_\epl^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ], \quad \text{a.s.},
-\end{equation}
-where 
-\begin{equation}
-\widetilde {\mathcal M}_\epl \defeq \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ].
+\lim_{T \to \infty} I_1^\epl(T) = \widetilde {\mathcal M}_\epl^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ], \quad \text{a.s.}
 \end{equation}
@@
 \end{equation}
-where the function $\rho^0$ is the density of the limit invariant distribution for $\epl \to 0$, as in Lemma \ref{lem:convMeasure}, and where
-\begin{equation}
-	\widetilde {\mathcal M}_0 \defeq \E^{\rho^0} [ V'(Z) \otimes V'(X) ].
-\end{equation}
-Due to Corollary \ref{lem:FPMarginal_Hom}, we have
+where the function $\rho^0$ is the density of the limit invariant distribution for $\epl \to 0$, as in Lemma \ref{lem:convMeasure}. Due to Corollary \ref{lem:FPMarginal_Hom}, we have
 \begin{equation}\label{eq:final_result}
@@
 	\begin{equation}
-	X_t^\epl - Z_t^\epl = \delta \beta^\epl_t + R(\epl,\delta),
-	\end{equation}
-	where the stochastic process $\beta_t^\epl$ is defined as
+	X_t^\epl - Z_t^\epl = \delta B^\epl_t + R(\epl,\delta),
+	\end{equation}
+	where the stochastic process $B_t^\epl$ is defined as
 	\begin{equation}\label{eq:defBeta}
-	\beta_t^\epl \defeq \sqrt{2\sigma} \int_0^t k(t-s)(1 + \Phi'(Y_s^\epl)) \dd W_s,
+	B_t^\epl \defeq \sqrt{2\sigma} \int_0^t k(t-s)(1 + \Phi'(Y_s^\epl)) \dd W_s,
 	\end{equation}
 	where $\Phi$ is the solution of the cell problem \eqref{eq:CellProblem}, $W_s$ is the Brownian motion appearing in \eqref{eq:SDE_MS} and $Y_t^\epl = X_t^\epl / \epl$.
-Moreover, $\beta_t^\epl$ and the remainder $R(\epl,\delta)$ satisfy for every $p \geq 1$ the estimates
+Moreover, $B_t^\epl$ and the remainder $R(\epl,\delta)$ satisfy for every $p \geq 1$ the estimates
 	\begin{equation} \label{eq:estimate_beta}
-	\left( \E^{\phi^\epl} \abs{\beta_t^\epl}^p \right)^{1/p} \leq C \delta^{-1/2},
+	\left( \E^{\phi^\epl} \abs{B_t^\epl}^p \right)^{1/p} \leq C \delta^{-1/2},
 	\end{equation}
@@
 
-It is clear from the Proposition above that understanding the properties of the process $\beta_t^\epl$ is key to understanding the behavior of the difference between $X^\epl$ and $Z^\epl$.
-In particular, it is relevant to study the asymptotic properties of $\beta_t^\epl$ for long times
-
-\begin{lemma} \label{lem:quartet}
-	Let $\eta^\epl$ be the invariant measure of the quartet $(X^\epl, Y^\epl, Z^\epl, \beta^\epl)$. Then it holds
-	\begin{equation}
-	\delta \E^{\eta^\epl} \left[ (\beta^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
+It is clear from the Proposition above that understanding the properties of the process $B_t^\epl$ is key to understanding the behavior of the difference between $X^\epl$ and $Z^\epl$.
+In particular, we can write the dynamics of $B_t^\epl$ with an application of the Itô formula and due to the properties of the kernel $k(t)$ as
+\begin{equation}
+	\d B_t^\epl = - \frac1\delta B_t^\epl \dd t + \frac{\sqrt{2\sigma}}{\delta}(1+\Phi'(Y_t^\epl)) \dd W_t.
+\end{equation}
+This equation can be coupled with the dynamics of the processes $X_t^\epl$, $Y_t^\epl$ and $Z_t^\epl$, thus describing the evolution of the quadruple $(X^\epl, Y^\epl, Z^\epl, B^\epl)$ together.
+In particular, it is possible to show that the results of Section \ref{sec:ergodic} hold for the quadruple, and the properties of the invariant measure of the quadruple can be exploited to prove the unbiasedness of the estimator in the case $\delta = \mathcal O(\epl^\zeta)$ in the same way as in the case $\delta = \mathcal O(\epl^0)$.
+In this context, a further assumption on the potential $V$ is necessary.
+\begin{assumption}\label{as:regularityZeta} The derivatives $V'$, $V''$ and $V'''$ of the potential $V \colon \R \to \R^N$ are polynomially bounded from above and bounded from below, and the second derivative is Lipschitz, i.e., there exists a constant $L > 0$ such that
+	\begin{equation}
+		\norm{V''(x)-V''(y)} \leq L \abs{x - y},
+	\end{equation}
+	for all $x, y \in \R$.
+\end{assumption}
+
+ In particular, in light of Remark \ref{rem:deltaPower}, it is fundamental to understand the behavior of the quantity
+\begin{equation}
+	(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl),
+\end{equation}
+and of its limit for $t\to \infty$ and for $\epl \to 0$. Let us remark that due to Proposition \ref{prop:zeta} we have
+\begin{equation}
+	(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl) \approx \delta^2 (B_t^\epl)^2 V''(Z_t^\epl),
+\end{equation}
+and therefore studying the right hand side of the approximate equality above is the goal of the upcoming discussion.
+The following result, whose proof is in Appendix \ref{ap:ProofsDeltaZeta}, gives a first characterization.
+
+\begin{lemma} \label{lem:quadruple} Under Assumptions \ref{as:regularity} and \ref{as:regularityZeta}, let $\eta^\epl$ be the invariant measure of the quadruple $(X^\epl, Y^\epl, Z^\epl, B^\epl)$.
+Then it holds
+	\begin{equation}
+	\delta \E^{\eta^\epl} \left[ (B^\epl)^2 V''(Z^\epl)  \right] = \sigma \E^{\eta^\epl} [(1 + \Phi'(Y^\epl))^2V''(Z^\epl) ] + \widetilde R(\epl,\delta),
 	\end{equation}
 	where the remainder $\widetilde R(\epl,\delta)$ satisfies
-	\begin{equation} \label{eq:quartet_remainder}
+	\begin{equation} \label{eq:quadruple_remainder}
 	\left| \widetilde R(\epl,\delta) \right| \le C \left( \delta^{1/2} + \epl \right).
@@
 
-\begin{lemma} \label{lem:quartet_convergence}
-	Let $\delta = \epl^\zeta$ with $\zeta > 0$, then it holds
-	\begin{equation}
-	\lim_{\epl \to 0} \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] = \Sigma \E^{\phi^0} [V''(X)].
-	\end{equation}
+Let us remark that the quantity appearing above hints towards the theory of homogenization. In fact, we recall that the homogenization coefficient $K$ is given by
+\begin{equation}
+	K = \int_0^L \left(1 + \Phi'(y)\right)^2 \mu(\d y),
+\end{equation}
+where $\mu$ is the marginal measure of the process $Y^\epl$ when coupled with $X^\epl$.
+Therefore, the next step is considering the homogenization limit, i.e., the limit of vanishing $\epl$, which is considered in the following Lemma, whose proof is given in Appendix \ref{ap:ProofsDeltaZeta}.
+
+\begin{lemma} \label{lem:quadruple_convergence} Let the assumptions of Lemma \ref{lem:quadruple} hold, and let $\delta = \epl^\zeta$ with $\zeta > 0$. Then, it holds
+	\begin{equation}
+	\lim_{\epl \to 0} \sigma \E^{\eta^\epl} [(1 + \Phi'(Y^\epl))^2V''(Z^\epl) ] = \Sigma \E^{\phi^0} [V''(X)],
+	\end{equation}
+	where $\Sigma$ is the diffusion coefficient of the homogenized equation \ref{eq:SDE_HOM}.
 \end{lemma}
 
-\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and let $\delta = \epl^\zeta$ with $\zeta \in (0,2)$.
+Provided with the results presented above, we can prove the following Theorem, stating that the estimator $\widehat A^\epl_k(T)$ is asimptotically unbiased even in the case of the filtering width $\delta$ vanishing with respect to the multiscale parameter $\epl$.
+
+\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:quadruple} hold.
+Let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and $\delta = \epl^\zeta$ with $\zeta \in (0,2)$.
 If $\widetilde M$ is invertible, then
 		\begin{equation}
-		\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A_k^\epl(T) = A, \quad \text{in law},
+		\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A_k^\epl(T) = A, \quad \text{in probability},
 		\end{equation}
@@
 	\mathcal A^\epl(\delta) &= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E [(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl)] \\
-	&= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E \left[ \left( \delta \beta_t^\epl + R(\epl,\delta) \right)^2 V''(Z_t^\epl) \right] \\
+	&= \widetilde{\mathcal M}_\epl^{-1} \frac1\delta \lim_{t \to \infty} \E \left[ \left( \delta B_t^\epl + R(\epl,\delta) \right)^2 V''(Z_t^\epl) \right] \\
 	&\eqdef \widetilde{\mathcal M}_\epl^{-1} \lim_{t \to \infty} \left( J_1^\epl(t) + J_2^\epl(t) + J_3^\epl(t) \right),
@@
 	\begin{aligned}
-	J_1^\epl(t) &= \delta \E \left[ (\beta_t^\epl)^2 V''(Z_t^\epl) \right], \\
-	J_2^\epl(t) &= 2 \E \left[ \beta_t^\epl R(\epl,\delta) V''(Z_t^\epl) \right], \\
+	J_1^\epl(t) &= \delta \E \left[ (B_t^\epl)^2 V''(Z_t^\epl) \right], \\
+	J_2^\epl(t) &= 2 \E \left[ B_t^\epl R(\epl,\delta) V''(Z_t^\epl) \right], \\
 	J_3^\epl(t) &= \frac1\delta \E\left[ R(\epl,\delta)^2 V''(Z_t^\epl) \right].
@@
 	\end{equation}
-	Let us consider the three terms separately. First, by geometric ergodicity and applying Lemma \ref{lem:quartet}, we get
-	\begin{equation}
-	\lim_{t \to \infty} J_1^\epl(t) = \delta \E^{\eta^\epl} \left[ (\beta^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
-	\end{equation}
-	and, by Lemma \ref{lem:quartet_convergence} and due to \eqref{eq:quartet_remainder}, we obtain
+	Let us consider the three terms separately. First, by geometric ergodicity and applying Lemma \ref{lem:quadruple}, we get
+	\begin{equation}
+	\lim_{t \to \infty} J_1^\epl(t) = \delta \E^{\eta^\epl} \left[ (B^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
+	\end{equation}
+	and, by Lemma \ref{lem:quadruple_convergence} and due to \eqref{eq:quadruple_remainder}, we obtain
 	\begin{equation}
@@
 	\begin{equation}
-	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] \eqdef \mathcal M_0.
+	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] = \mathcal M_0.
 	\end{equation}
@@
 	\begin{equation}
-	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \E^{\rho^0} [V''(X)],
+	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \mathcal M_0^{-1} \E^{\rho^0} [V''(X)],
 	\end{equation}
@@
 	\begin{equation}
-	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ]^{-1} \frac1\Sigma \E^{\rho^0} [V'(X) \otimes V'(X) ] A = A,
+	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \mathcal M_0^{-1} \frac1\Sigma \mathcal M_0 A = A,
 	\end{equation}
@@
 The following theorem guarantees the unbiasedness of this estimator under a condition on the parameter $\delta$ of the filter, and we refer to Appendix \ref{ap:EstimatorTilde} for its proof.
-\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold.
-Then, if $\delta$ in \eqref{eq:filter} satisfies $\delta = \delta(\epl)$ with $\delta(\epl) \to 0$ for $\epl \to 0$, it holds
-	\begin{equation}
-	\lim_{\epl \to 0} \lim_{T \to \infty} \widetilde A^\epl_k(T) = A, \quad \corr{\text{in law}},
+\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold. Then, if \corr{$\delta = \epl^\zeta$, with $\zeta \in (0, 2)$}, it holds
+	\begin{equation}
+	\lim_{\epl \to 0} \lim_{T \to \infty} \widetilde A^\epl_k(T) = A, \quad \text{in probability},
 	\end{equation} 
@@
 
-The following result gives the convergence of the modified posterior distribution $\widetilde \mu_{T, \epl}$ to the drift coefficient of the homogenized equation.
-\begin{theorem} Let the Assumptions of Theorem \ref{thm:mainTheoremTilde} hold. Then, the modified posterior measure $\widetilde\mu_{T,\epl} = \mathcal N(\widetilde m_{T,\epl}, C_{T,\epl})$ satisfies
-	\begin{equation}
-	\lim_{\epl \to 0}\lim_{T \to \infty} \widetilde \mu_{T,\epl}(\cdot) = \delta(\cdot - A), \quad \corr{\text{in law}},
-	\end{equation}
-	weakly in the space of probability measures on $\R^N$, where $\delta$ is the Dirac measure on $\R^N$.
-\end{theorem}
+\corr{In light of the proof of Theorem \ref{thm:BayesianBias}, the result above guarantees that the mean of the posterior distribution $\widetilde \mu_{T, \epl}$ converges to the drift coefficient of the homogenized equation.
+Being the covariance matrix the same for $\mu_{T, \epl}$ and $\widetilde \mu_{T, \epl}$, it is possible to prove a positive convergence result for $\widetilde \mu_{T, \epl}$, which is given by the following Theorem.
+\begin{theorem} Let the Assumptions of Theorem \ref{thm:mainTheoremTilde} hold.
+Then, the modified posterior measure $\widetilde\mu_{T,\epl}(\cdotp\mid X^\epl) = \mathcal N(\widetilde m_{T,\epl}, C_{T,\epl})$ satisfies
+	\begin{equation}
+		\lim_{\epl \to 0}\lim_{T \to \infty} \E \left[\mu_{T,\epl}\left(\{a\colon \norm{a-A}_2\geq c\}\mid X^\epl\right)\right] = 0,
+	\end{equation}
+	where $\E$ denotes expectation with respect to the Wiener measure and $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_HOM}.
+\end{theorem}}
 \begin{proof} The proof follows from the proof of Theorem \ref{thm:BayesianBias} and from Theorem \ref{thm:mainTheoremTilde}.
@@
 
-\section{Proofs of Sections \ref{sec:ergodic}}\label{ap:Proofs}
+\section{Proofs of Sections \ref{sec:ergodic}}\label{ap:ProofsErgodic}
 
@@
 		I_2^\epl(t) &= \sqrt{2\sigma} \left(Q_t^\epl\int_0^t k(t-s) \dd s - Q_t^\epl + \delta \int_0^t k(t-s)\left(1 + \Phi'(Y_s^\epl)\right) \dd W_s\right)\\
-		  			&= \delta \beta_t^\epl - \sqrt{2\sigma} e^{-t/\delta} Q_t^\epl \eqdef \delta \beta_t^\epl - R_2^\epl(t).
-	\end{aligned}
-	\end{equation}
-	where $\beta_t^\epl$ is defined in \eqref{eq:defBeta}. For the remainder $R_2^\epl(t)$, let us remark that for all $p \geq 1$ it holds
+		  			&= \delta B_t^\epl - \sqrt{2\sigma} e^{-t/\delta} Q_t^\epl \eqdef \delta B_t^\epl - R_2^\epl(t).
+	\end{aligned}
+	\end{equation}
+	where $B_t^\epl$ is defined in \eqref{eq:defBeta}. For the remainder $R_2^\epl(t)$, let us remark that for all $p \geq 1$ it holds
 	\begin{equation}\label{eq:BoundQ}
@@
 	\end{equation}
-	In order to obtain the bound \eqref{eq:estimate_beta} on $\beta_t^\epl$, let us remark that from \eqref{eq:rewriteI2} it holds for a constant $C > 0$ depending only on $p$ 
-	\begin{equation}
-		\left(\E\abs{\beta_t^\epl}^p\right)^{1/p}\leq C \delta^{-1}\left(\E\abs{I_2^\epl(t)}^p\right)^{1/p} + C \delta^{-1} \left(\E\abs{R_2^\epl(t)}^p\right)^{1/p}.
+	In order to obtain the bound \eqref{eq:estimate_beta} on $B_t^\epl$, let us remark that from \eqref{eq:rewriteI2} it holds for a constant $C > 0$ depending only on $p$ 
+	\begin{equation}
+		\left(\E\abs{B_t^\epl}^p\right)^{1/p}\leq C \delta^{-1}\left(\E\abs{I_2^\epl(t)}^p\right)^{1/p} + C \delta^{-1} \left(\E\abs{R_2^\epl(t)}^p\right)^{1/p}.
 	\end{equation}
@@
 	\begin{equation}
-		\left(\E\abs{\beta_t^\epl}^p\right)^{1/p}\leq C \delta^{-1/2},
+		\left(\E\abs{B_t^\epl}^p\right)^{1/p}\leq C \delta^{-1/2},
 	\end{equation}
@@
 
-\section{Proofs of Section \ref{sec:Fast}} \label{ap:zeta}
+\section{Proofs of Section \ref{sec:Fast}} \label{ap:ProofsDeltaZeta}
 
@@
 \begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Corollary \ref{cor:distanceZandX} hold.
-Then the matrices $\mathcal M$ and $\widetilde{\mathcal M}_\epl$ defined in \eqref{eq:CalM} satisfy
+Then the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ defined in \eqref{eq:CalM} satisfy
 	\begin{equation}
@@
 
-\subsection{Proof of Lemmas \ref{lem:quartet} and \ref{lem:quartet_convergence}}
-
-\begin{proof}[Proof of Lemma \ref{lem:quartet}]
-	Let us consider the following system of stochastic differential equations for the processes $X_t^\epl, Z_t^\epl, \beta_t^\epl, Y_t^\epl$
-	\begin{equation}
-	\label{eq:systemSDEquartet}
+\subsection{Proof of Lemma \ref{lem:quadruple}}
+
+	Let us consider the following system of stochastic differential equations for the processes $X_t^\epl, Z_t^\epl, B_t^\epl, Y_t^\epl$
+	\begin{equation}
+	\label{eq:systemSDEquadruple}
 	\begin{aligned}
@@
 	\d Z_t^\epl &= \frac1\delta \left ( X^\epl_t - Z^\epl_t \right ) \dd t, \\
-	\d \beta_t^\epl &= - \frac1\delta \beta_t^\epl \dd t + \frac{\sqrt{2\sigma}}{\delta}(1+\Phi'(Y_t^\epl)) \dd W_t, \\
+	\d B_t^\epl &= - \frac1\delta B_t^\epl \dd t + \frac{\sqrt{2\sigma}}{\delta}(1+\Phi'(Y_t^\epl)) \dd W_t, \\
 	\d Y_t^\epl &= -\frac1\epl \alpha \cdot V'(X_t^\epl) \dd t - \frac{1}{\epl^2} p'(Y_t^\epl) \dd t+ \frac{\sqrt{2\sigma}}{\epl} \dd W_t,
@@
 	\end{equation}
-	whose generator $\widetilde{\mathcal L}^\epl$ is given by
-	\begin{equation}
-	\begin{aligned}
-	\widetilde{\mathcal L}^\epl =& -\left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \partial_x + \frac1\delta (x-z) \partial_z - \frac1\delta b \partial_b - \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \partial_y \\
+	whose generator $\widetilde{\mathcal L}_\epl$ is given by
+	\begin{equation}
+	\begin{aligned}
+	\widetilde{\mathcal L}_\epl =& -\left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \partial_x + \frac1\delta (x-z) \partial_z - \frac1\delta b \partial_b - \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \partial_y \\
 	& + \sigma \left( \partial_{xx}^2 + \frac2\epl \partial_{xy}^2 + \frac{1}{\epl^2} \partial_{yy}^2 + \frac{2(1+\Phi'(y))}{\delta} \partial_{xb}^2 + \frac{2(1+\Phi'(y))}{\epl \delta} \partial_{yb}^2 + \frac{(1+\Phi'(y))^2}{\delta^2} \partial_{bb}^2 \right).
@@
 	\end{equation}
-	Let us denote by $\eta^\epl \colon \R^3 \times [0,L] \to \R$, $\eta^\epl = \eta^\epl(x,z,b,y)$, the invariant measure of the quartet $(X_t^\epl, Z_t^\epl, \beta_t^\epl, Y_t^\epl)$.
-Then $\eta^\epl$ solves the stationary Fokker-Planck equation
-	\begin{equation} \label{eq:FPSDEquartet}
-	\begin{aligned}
-	\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \eta^\epl \right) - \partial_z \left( \frac1\delta (x-z) \eta^\epl \right) & \\
-	+ \partial_b \left( \frac1\delta b \eta^\epl \right) + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \eta^\epl \right) & \\
-	+ \sigma \left( \partial_{xx}^2 \eta^\epl + \partial_{xy}^2 \left( \frac2\epl \eta^\epl \right) + \partial_{yy}^2 \left( \frac{1}{\epl^2} \eta^\epl \right) \right) & \\
-	+ \sigma \left( \partial_{xb}^2 \left( \frac{2(1+\Phi'(y))}{\delta} \eta^\epl \right) + \partial_{yb}^2 \left( \frac{2(1+\Phi'(y))}{\epl \delta} \eta^\epl \right) + \partial_{bb}^2 \left( \frac{(1+\Phi'(y))^2}{\delta^2} \eta^\epl \right) \right) & = 0.
+	Let us denote by $\eta^\epl \colon \R^3 \times [0,L] \to \R$, $\eta^\epl = \eta^\epl(x,z,b,y)$, the invariant measure of the quadruple $(X_t^\epl, Z_t^\epl, B_t^\epl, Y_t^\epl)$.
+Then $\eta^\epl$ solves the stationary Fokker-Planck equation $\widetilde{\mathcal L}_\epl^* \eta^\epl = 0$, i.e., explicitly
+	\begin{equation} \label{eq:FPSDEquadruple}
+	\begin{aligned}
+	&\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \eta^\epl \right) - \frac1\delta\partial_z \left( (x-z) \eta^\epl \right) \\
+	&\quad + \frac1\delta \partial_b \eta^\epl  + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \eta^\epl \right) + \sigma \left( \partial_{xx}^2 \eta^\epl + \frac2\epl \partial_{xy}^2 \eta^\epl + \frac1{\epl^2} \partial_{yy}^2 \eta^\epl \right) \\
+	&\quad + \sigma \left( \frac2\delta \partial_{xb}^2 \left( (1+\Phi'(y)) \eta^\epl \right) + \frac2{\epl\delta}\partial_{yb}^2 \left( (1+\Phi'(y))\eta^\epl \right) + \frac1{\delta^2}\partial_{bb}^2 \left( (1+\Phi'(y))^2 \eta^\epl \right) \right) = 0.
 	\end{aligned}
@@
 	We now multiply the equation above by a continuous differentiable function $f \colon \R^2 \to \R^N$, $f = f(z,b)$, and integrate with respect to $x$, $z$, $b$ and $y$.
-Then integration by parts yields
+Then an integration by parts yields
 	\begin{equation}
@@
 	\begin{equation}
-	\delta \E^{\eta^\epl}\left[ \partial_b f(Z^\epl, \beta^\epl) \beta^\epl \right] = \sigma \E^{\eta^\epl} \left[ \partial_{bb}^2 f(Z^\epl, \beta^\epl) (1+\Phi'(Y^\epl)) \right] + \delta \E^{\eta^\epl} \left[ \partial_z f(Z^\epl, \beta^\epl) (X^\epl-Z^\epl) \right].
+	\delta \E^{\eta^\epl}\left[ \partial_b f(Z^\epl, B^\epl) B^\epl \right] = \sigma \E^{\eta^\epl} \left[ \partial_{bb}^2 f(Z^\epl, B^\epl) (1+\Phi'(Y^\epl)) \right] + \delta \E^{\eta^\epl} \left[ \partial_z f(Z^\epl, B^\epl) (X^\epl-Z^\epl) \right].
 	\end{equation}
@@
 	\begin{aligned}
-	\delta \E^{\eta^\epl}\left[ (\beta^\epl)^2 V''(Z^\epl) \right] &= \sigma \E^{\eta^\epl} \left[ V''(Z^\epl) (1+\Phi'(Y^\epl)) \right] + \frac\delta2 \E^{\eta^\epl} \left[ (\beta^\epl)^2 V'''(Z^\epl) (X^\epl-Z^\epl) \right] \\
+	\delta \E^{\eta^\epl}\left[ (B^\epl)^2 V''(Z^\epl) \right] &= \sigma \E^{\eta^\epl} \left[ V''(Z^\epl) (1+\Phi'(Y^\epl)) \right] + \frac\delta2 \E^{\eta^\epl} \left[ (B^\epl)^2 V'''(Z^\epl) (X^\epl-Z^\epl) \right] \\
 	&\eqdef \sigma \E^{\eta^\epl} \left[ V''(Z^\epl) (1+\Phi'(Y^\epl)) \right] + \widetilde R(\epl,\delta).
@@
 	\end{equation}
-	We now consider the remainder and, applying Hölder's inequality, Lemma \ref{cor:distanceZandX}, Lemma \ref{lem:bounded_momentZ} and \eqref{eq:estimate_beta}, we get for $p,q,r$ such that $1/p+1/q+1/r=1$
-	\begin{equation}
-	\left| \widetilde R(\epl,\delta) \right| \le C \delta \left( \E^{\eta^\epl} |\beta^\epl|^{2p} \right)^{1/p} \left( \E^{\eta^\epl} |V'''(Z^\epl)|^q \right)^{1/q} \left( \E^{\eta^\epl} |X^\epl - Z^\epl|^r \right)^{1/r} \le C (\delta^{1/2} + \epl),
-	\end{equation}
-	which completes the proof.
-\end{proof}
-
-\begin{proof}[Proof of Lemma \ref{lem:quartet_convergence}]
+	We now consider the remainder and, applying Hölder's inequality, Corollary \ref{cor:distanceZandX}, Lemma \ref{lem:bounded_momentZ} and \eqref{eq:estimate_beta}, we get for $p,q,r$ such that $1/p+1/q+1/r=1$
+	\begin{equation}
+	\left| \widetilde R(\epl,\delta) \right| \le C \delta \left( \E^{\eta^\epl} |B^\epl|^{2p} \right)^{1/p} \left( \E^{\eta^\epl} |V'''(Z^\epl)|^q \right)^{1/q} \left( \E^{\eta^\epl} |X^\epl - Z^\epl|^r \right)^{1/r} \le C (\delta^{1/2} + \epl),
+	\end{equation}
+	which completes the proof. \qed
+
+\subsection{Proof of Lemma \ref{lem:quadruple_convergence}}
+
 	Let us introduce the notation 
@@
 	We now consider $\Delta_2(\epl)$.
-Integrating equation \eqref{eq:FPSDEquartet} with respect to $z$ and $b$ we obtain the Fokker-Planck equation for the stationary marginal distribution $\lambda \colon \R \times [0,L]$, $\lambda = \lambda(x,y)$, of the couple $(X^\epl,Y^\epl)$
+Integrating equation \eqref{eq:FPSDEquadruple} with respect to $z$ and $b$ we obtain the Fokker-Planck equation for the stationary marginal distribution $\lambda \colon \R \times [0,L]$, $\lambda = \lambda(x,y)$, of the couple $(X^\epl,Y^\epl)$
 	\begin{equation}
@@
 	\end{equation}
-	which shows that $\Delta_2(\epl) = 0$ and completes the proof.
-\end{proof}
+	which shows that $\Delta_2(\epl) = 0$ and completes the proof. \qed
 
@@
 	\end{equation}
-	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta \to 0$ for $\epl \to 0$, the desired result holds.
+	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta = \mathcal O(\epl^\zeta)$, the desired result holds.
 \end{proof}

### 2020-03-26 CalNotes.tex
Theorem 3.15 proof rewritten

@@
 \corr{Let us introduce a notation which will be used throughout the rest of the paper. We denote
-\begin{equation}
+\begin{equation}\label{eq:DefMTilde}
 	\widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl)\otimes V'(X^\epl)], \quad \widetilde{\mathcal M}_0 \defeq \E^{\rho^0}[V'(Z)\otimes V'(X)],
@@
 
- In particular, in light of Remark \ref{rem:deltaPower}, it is fundamental to understand the behavior of the quantity
+In light of Remark \ref{rem:deltaPower}, it is fundamental to understand the behavior of the quantity
 \begin{equation}
@@
 	\end{equation}
-	where
-	\begin{equation}
-	\widetilde{\mathcal M}_\epl = \E^{\rho^\epl} [ V'(Z^\epl) \otimes V'(X^\epl) ].
-	\end{equation}
-	Then following the proof of Theorem \ref{thm:mainTheorem} we only need to show that if $\delta = \epl^\zeta$ with \corr{$\zeta \in (0,2)$} we have
+	where $\widetilde{\mathcal M}_\epl$ is defined in \eqref{eq:DefMTilde}.	Then following the proof of Theorem \ref{thm:mainTheorem} and in light of Remark \ref{rem:deltaPower}, we only need to show that if $\delta = \epl^\zeta$ with $\zeta \in (0,2)$ we have
 	\begin{equation}
@@
 	\end{equation}
-	where and $\E$ denotes the expectation with respect to the Wiener measure and
+	where $R(\epl, \delta)$ is given in Proposition \ref{prop:zeta}, $\E$ denotes the expectation with respect to the Wiener measure and
 	\begin{equation}
@@
 	\end{equation}
-	Let us consider the three terms separately. First, by geometric ergodicity and applying Lemma \ref{lem:quadruple}, we get
-	\begin{equation}
-	\lim_{t \to \infty} J_1^\epl(t) = \delta \E^{\eta^\epl} \left[ (B^\epl)^2 V''(Z^\epl) \right] = \sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta),
-	\end{equation}
-	and, by Lemma \ref{lem:quadruple_convergence} and due to \eqref{eq:quadruple_remainder}, we obtain
-	\begin{equation}
-	\lim_{\epl \to 0} \lim_{t \to \infty} J_1^\epl(t) = \Sigma \E^{\rho^0} [V''(X)].
-	\end{equation}
-	Moreover, due to \eqref{eq:estimate_beta} and \eqref{eq:remainder_zeta}, we have the following bounds for $J_2^\epl(t)$ and $J_3^\epl(t)$
-	\begin{equation}
-	\begin{aligned}
-	\abs{J_2^\epl(t)} &\le C \left( \delta^{1/2} + \epl \delta^{-1/2} \right), \\
-	\abs{J_3^\epl(t)} &\le C \left( \delta + \epl^2 \delta^{-1} \right).
-	\end{aligned}
-	\end{equation}
-	Furthermore, by Lemma \ref{lem:distanceMandTildeM} and weak convergence of the invariant measure, we have
-	\begin{equation}
-	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] = \mathcal M_0.
+	Let us consider the three terms separately. First, by geometric ergodicity and applying Lemma \ref{lem:quadruple} and Lemma \ref{lem:quadruple_convergence} we get
+	\begin{equation}
+	\begin{aligned}
+	\lim_{\epl \to 0} \lim_{t \to \infty} J_1^\epl(t) &= \lim_{\epl \to 0}\delta \E^{\eta^\epl} \left[ (B^\epl)^2 V''(Z^\epl) \right] \\
+	&= \lim_{\epl \to 0} \left(\sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta)\right)\\
+	&= \Sigma \E^{\rho^0} [V''(X)].
+	\end{aligned}
+	\end{equation}
+	Let us now consider $J_2^\epl(t)$. Considering Hölder conjugates $p,q,r$ the Hölder inequality yields
+	\begin{equation}
+		\abs{J_2^\epl(t)} \leq \E[(B_t^\epl)^p]^{1/p}\E[R(\epl,\delta)^q]^{1/q}\E[V''(Z^\epl)^r]^{1/r}.
+	\end{equation}
+	Now, we can bound the first two terms with \eqref{eq:estimate_beta} and \eqref{eq:remainder_zeta}, respectively.
+The third term is bounded due to Assumption \ref{as:regularityZeta} and Lemma \ref{lem:bounded_momentZ}.
+Hence, we have
+	\begin{equation}
+		\abs{J_2^\epl(t)} \le C \left( \delta^{1/2} + \epl \delta^{-1/2} \right).
+	\end{equation}
+	We consider now $J_3^\epl(t)$. The Hölder inequality yields for conjugates $p$ and $q$
+	\begin{equation}
+		\abs{J_3^\epl(t)} \le \E[R(\epl, \delta)^{2p}]^{1/p} \E[V''(Z_t^\epl)^q]^{1/q},
+	\end{equation}
+	which, reasoning as above, yields
+	\begin{equation}
+		\abs{J_3^\epl(t)} \le C \left( \delta + \epl^2 \delta^{-1} \right).
+	\end{equation}
+	Therefore, since $\delta = \mathcal O(\epl^\zeta)$ for $\zeta \in (0, 2)$, and due to geometric ergodicity the terms $J_2^\epl(t)$ and $J_3^\epl(t)$ vanish in the limit for $t \to \infty$ and $\epl \to 0$.
+Furthermore, by Lemma \ref{lem:distanceMandTildeM} and by weak convergence of the invariant measure $\mu^\epl$ to $\mu^0$, we have
+	\begin{equation}
+	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] \eqdef \mathcal M_0.
 	\end{equation}

### 2020-03-26 CalNotes.tex
Final GIACOMO

@@
 \corr{Let us introduce a notation which will be used throughout the rest of the paper. We denote
-\begin{equation}\label{eq:DefMTilde}
+\begin{equation}\label{eq:DefCalMTilde}
 	\widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl)\otimes V'(X^\epl)], \quad \widetilde{\mathcal M}_0 \defeq \E^{\rho^0}[V'(Z)\otimes V'(X)],
@@
 \i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to Lemma \ref{lem:convMeasure}.
-We can now introduce the main result, namely the convergence of the filtering-based estimator to the drift coefficient of the homogenized equation.}
+For completeness, we introduce here the symmetric matrices $\mathcal M_\epl$ and $\mathcal M_0$ which are defined as
+\begin{equation}\label{eq:DefCalM}
+	\mathcal M_\epl \defeq \E^{\rho^\epl}[V'(X^\epl)\otimes V'(X^\epl)], \quad \mathcal M_0 \defeq \E^{\rho^0}[V'(X)\otimes V'(X)],
+\end{equation}
+and which will be employed in the following. We can now introduce the main result, namely the convergence of the filtering-based estimator to the drift coefficient of the homogenized equation.}
 
@@
 \begin{equation}
-	(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl),
+	\frac1\delta (X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl),
 \end{equation}
@@
 \begin{equation}
-	(X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl) \approx \delta^2 (B_t^\epl)^2 V''(Z_t^\epl),
+	\frac1\delta (X_t^\epl - Z_t^\epl)^2 V''(Z_t^\epl) \approx \delta (B_t^\epl)^2 V''(Z_t^\epl),
 \end{equation}
@@
 where $\mu$ is the marginal measure of the process $Y^\epl$ when coupled with $X^\epl$.
-Therefore, the next step is considering the homogenization limit, i.e., the limit of vanishing $\epl$, which is considered in the following Lemma, whose proof is given in Appendix \ref{ap:ProofsDeltaZeta}.
+Therefore, the next step is the homogenization limit, i.e., the limit of vanishing $\epl$, which is considered in the following Lemma, and whose proof is given in Appendix \ref{ap:ProofsDeltaZeta}.
 
@@
 
-\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:quadruple} hold.
+\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:quadruple_convergence} hold.
 Let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and $\delta = \epl^\zeta$ with $\zeta \in (0,2)$.
@@
 	\end{equation}
-	where $\widetilde{\mathcal M}_\epl$ is defined in \eqref{eq:DefMTilde}.	Then following the proof of Theorem \ref{thm:mainTheorem} and in light of Remark \ref{rem:deltaPower}, we only need to show that if $\delta = \epl^\zeta$ with $\zeta \in (0,2)$ we have
-	\begin{equation}
-	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = A, \quad \text{in law}.
+	where $\widetilde{\mathcal M}_\epl$ is defined in \eqref{eq:DefCalMTilde}.	Then following the proof of Theorem \ref{thm:mainTheorem} and in light of Remark \ref{rem:deltaPower}, we only need to show that if $\delta = \epl^\zeta$ with $\zeta \in (0,2)$ we have
+	\begin{equation}
+	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = A, \quad \text{in probability}.
 	\end{equation}
@@
 	&= \lim_{\epl \to 0} \left(\sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] + \widetilde R(\epl,\delta)\right)\\
-	&= \Sigma \E^{\rho^0} [V''(X)].
+	&= \Sigma \E^{\phi^0} [V''(X)].
 	\end{aligned}
@@
 	\begin{equation}
-	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl^{-1} = \E^{\rho^0} [V'(X) \otimes V'(X) ] \eqdef \mathcal M_0.
-	\end{equation}
-	Therefore
-	\begin{equation}
-	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \mathcal M_0^{-1} \E^{\rho^0} [V''(X)],
+	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl = \mathcal M_0,
+	\end{equation}
+	where $\mathcal M_0$ is defined in \eqref{eq:DefCalM}. Therefore
+	\begin{equation}
+	\lim_{\epl \to 0} \mathcal A^\epl(\delta) = \Sigma \mathcal M_0^{-1} \E^{\phi^0} [V''(X)],
 	\end{equation}
@@
 \end{equation}
-The following theorem guarantees the unbiasedness of this estimator under a condition on the parameter $\delta$ of the filter, and we refer to Appendix \ref{ap:EstimatorTilde} for its proof.
+The following theorem guarantees the unbiasedness of this estimator under a condition on the parameter $\delta$ of the filter.
 \begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold. Then, if \corr{$\delta = \epl^\zeta$, with $\zeta \in (0, 2)$}, it holds
@@
 \end{theorem}
-
-\corr{In light of the proof of Theorem \ref{thm:BayesianBias}, the result above guarantees that the mean of the posterior distribution $\widetilde \mu_{T, \epl}$ converges to the drift coefficient of the homogenized equation.
+\begin{proof} We first consider the difference between the two estimators $\widetilde A^\epl_k(T)$ and $\widehat A^\epl_k(T)$. In particular, the ergodic theorem and an algebraic equality imply
+	\begin{equation}
+	\begin{aligned}
+	\lim_{T \to \infty} \left(\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)\right) &= \left(\mathcal M_\epl^{-1} - \widetilde{\mathcal M}_\epl^{-1}\right) \lim_{T \to \infty}\widetilde h \\
+	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)  \widetilde{\mathcal M}_\epl^{-1} \lim_{T \to \infty} \widetilde h\\
+	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)\lim_{T \to \infty} \widehat A^\epl_k(T),
+	\end{aligned}
+	\end{equation}
+	almost surely, where $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ are defined in \eqref{eq:DefCalM} and \eqref{eq:DefCalMTilde}, respectively.
+Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M_\epl^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
+	\begin{equation}\label{eq:DistATildeAHat}
+	\lim_{T \to \infty} \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 \leq C \left(\epl + \delta^{1/2} \right).
+	\end{equation}
+	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem}. Now, the triangle inequality yields
+	\begin{equation}
+	\norm{\widetilde A^\epl_k(T) - A}_2 \leq \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 + \norm{\widehat A^\epl_k(T) - A}_2.
+	\end{equation}
+	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta = \mathcal O(\epl^\zeta)$, the desired result holds.
+\end{proof}
+\corr{
+In light of the proof of Theorem \ref{thm:BayesianBias}, the result above guarantees that the mean of the posterior distribution $\widetilde \mu_{T, \epl}$ converges to the drift coefficient of the homogenized equation.
 Being the covariance matrix the same for $\mu_{T, \epl}$ and $\widetilde \mu_{T, \epl}$, it is possible to prove a positive convergence result for $\widetilde \mu_{T, \epl}$, which is given by the following Theorem.
@@
 
-It is relevant to study the quantities
-\begin{equation}\label{eq:CalM}
-\mathcal M_\epl \defeq \E^{\rho^\epl}[V'(X^\epl) \otimes V'(X^\epl)] \quad \text{and} \quad \widetilde{\mathcal M}_\epl \defeq \E^{\rho^\epl}[V'(Z^\epl) \otimes V'(X^\epl)],
-\end{equation}
-which are by the ergodic theorem the time limit of the matrices appearing in the estimators $\widehat A^\epl(T)$ and $\widehat A^\epl_k(T)$, respectively.
-In particular, the distance between the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ can be bounded, which is summarized in the following lemma.
-
-\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Corollary \ref{cor:distanceZandX} hold.
-Then the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ defined in \eqref{eq:CalM} satisfy
+Let us conclude with a last preliminary estimate concerning the matrices $\widetilde{\mathcal M}_\epl$ and $\mathcal M_\epl$ defined in \eqref{eq:DefCalMTilde} and \eqref{eq:DefCalM}, respectively.
+
+\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Corollary \ref{cor:distanceZandX} hold. Then the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ satisfy
 	\begin{equation}
@@
 	\begin{aligned}
-	&\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \eta^\epl \right) - \frac1\delta\partial_z \left( (x-z) \eta^\epl \right) \\
-	&\quad + \frac1\delta \partial_b \eta^\epl  + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \eta^\epl \right) + \sigma \left( \partial_{xx}^2 \eta^\epl + \frac2\epl \partial_{xy}^2 \eta^\epl + \frac1{\epl^2} \partial_{yy}^2 \eta^\epl \right) \\
+	&\partial_x \left( \left( \alpha \cdot V'(x) + \frac1\epl p'(y) \right) \eta^\epl \right) + \frac1\delta\partial_z \left( (z-x) \eta^\epl \right) \\
+	&\quad + \frac1\delta \partial_b (b\eta^\epl)  + \partial_y \left( \left( \frac1\epl \alpha \cdot V'(x) + \frac{1}{\epl^2} p'(y) \right) \eta^\epl \right) + \sigma \left( \partial_{xx}^2 \eta^\epl + \frac2\epl \partial_{xy}^2 \eta^\epl + \frac1{\epl^2} \partial_{yy}^2 \eta^\epl \right) \\
 	&\quad + \sigma \left( \frac2\delta \partial_{xb}^2 \left( (1+\Phi'(y)) \eta^\epl \right) + \frac2{\epl\delta}\partial_{yb}^2 \left( (1+\Phi'(y))\eta^\epl \right) + \frac1{\delta^2}\partial_{bb}^2 \left( (1+\Phi'(y))^2 \eta^\epl \right) \right) = 0.
@@
 	\begin{equation}
-	\lambda(x,y) = \frac{1}{C_\lambda} \exp \left\{ - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right\},
+	\lambda(x,y) = \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right),
 	\end{equation}
@@
 	\begin{aligned}
-	C_{\lambda} &= \int_\R \int_0^L \exp \left\{ - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right\} \dd x \dd y \\
-	&= \left( \int_\R \exp \left\{ - \frac\alpha\sigma V(x) \right\} \dd x \right) \left( \int_0^L \exp \left\{ - \frac1\sigma p(y) \right\} \dd y \right) \\
+	C_{\lambda} &= \int_\R \int_0^L \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
+	&= \left( \int_\R \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \left( \int_0^L \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
 	&\eqdef C_{\lambda_x} C_{\lambda_y}.
@@
 	\begin{aligned}
-	\sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) (1 + \Phi'(y))^2 \frac{1}{C_\lambda} \exp \left\{ - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right\} \dd x \dd y \\
-	&= \sigma \left( \int_\R V''(x) \frac{1}{C_{\lambda_x}} \exp \left\{ - \frac\alpha\sigma V(x) \right\} \dd x \right) \\
-	&\qquad \qquad \times \left( \int_0^L (1+\Phi'(y))^2 \frac{1}{C_{\lambda_y}} \exp \left\{ - \frac1\sigma p(y) \right\} \dd y \right) \\
+	\sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) (1 + \Phi'(y))^2 \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
+	&= \sigma \left( \int_\R V''(x) \frac{1}{C_{\lambda_x}} \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \\
+	&\qquad \qquad \times \left( \int_0^L (1+\Phi'(y))^2 \frac{1}{C_{\lambda_y}} \exp \left( - \frac1\sigma p(y) \right) \dd y \right) \\
 	&= \sigma K \E^{\phi^0}[V''(X)] = \Sigma \E^{\phi^0}[V''(X)],
@@
 	which shows that $\Delta_2(\epl) = 0$ and completes the proof. \qed 
-
-\section{Proof of Theorem \ref{thm:mainTheoremTilde}}\label{ap:EstimatorTilde}
-Let us consider the estimator defined in \eqref{eq:AHatMixedTilde}, that is
-\begin{equation}
-	\widetilde A^\epl_k(T) = -M^{-1}\widetilde h,
-\end{equation}
-where the matrix $M$ is taken from \eqref{eq:MandH} and the vector $\widetilde{h}$ is taken from \eqref{eq:MandHTilde}.
-We prove here Theorem \ref{thm:mainTheoremTilde}, i.e., the unbiasedness of this estimator.
-Let us consider a couple $(X^\epl, Z^\epl)^\top$.
-
-We can finally prove the unbiasedness of the estimator $\widetilde A^\epl_k(T)$.
-
-\begin{proof}[Proof of Theorem \ref{thm:mainTheoremTilde}] We first consider the difference between the two estimators $\widetilde A^\epl_k(T)$ and $\widehat A^\epl_k(T)$.
-In particular, the ergodic theorem and an algebraic equality imply
-	\begin{equation}
-	\begin{aligned}
-	\lim_{T \to \infty} \left(\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)\right) &= \left(\mathcal M_\epl^{-1} - \widetilde{\mathcal M}_\epl^{-1}\right) \lim_{T \to \infty}\widetilde h \\
-	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)  \widetilde{\mathcal M}_\epl^{-1} \lim_{T \to \infty} \widetilde h\\
-	&= \mathcal M_\epl^{-1}\left(\mathcal M_\epl - \widetilde{\mathcal M}_\epl\right)\lim_{T \to \infty} \widehat A^\epl_k(T),
-	\end{aligned}
-	\end{equation}
-	almost surely, where $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ are defined in \eqref{eq:CalM}.
-Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M_\epl^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
-	\begin{equation}\label{eq:DistATildeAHat}
-	\lim_{T \to \infty} \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 \leq C \left(\epl + \delta^{1/2} \right).
-	\end{equation}
-	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem}. Now, the triangle inequality yields
-	\begin{equation}
-	\norm{\widetilde A^\epl_k(T) - A}_2 \leq \norm{\widetilde A^\epl_k(T) - \widehat A^\epl_k(T)}_2 + \norm{\widehat A^\epl_k(T) - A}_2.
-	\end{equation}
-	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta = \mathcal O(\epl^\zeta)$, the desired result holds.
-\end{proof}
-
 \end{appendices}

### 2020-03-26 CalNotes.tex
some modifications

@@
 \begin{equation}\label{eq:MLE}
-	\widehat A^\epl(T) \defeq \arg \min_{A \in \R^N} I(X^\epl \mid A) = M^{-1}h,
+	\widehat A^\epl(T) \defeq \arg \min_{A \in \R^N} I(X^\epl \mid A) = - M^{-1}h,
 \end{equation}
@@
 	\begin{equation}
-		V^\epl(x) \defeq \alpha \cdot V(x) - p\left(\frac{x}{\epl}\right).
+		V^\epl(x) \defeq \alpha \cdot V(x) + p\left(\frac{x}{\epl}\right).
 	\end{equation}
@@
 	\caption{\corr{Filtering a trajectory $X^\epl$ obtained with $V(x) = x^2 / 2$, $p(y) = \cos(y)$, $\alpha = 1$, $\sigma = 0.5$ and $\epl = 0.1$.
-The filtering width is $\delta = \{1, \sqrt{\epl}, \epl\}$ from top to bottom, respectively.}}
+The filtering width is $\delta = \{1, \sqrt{\epl}, \epl\}$ from top to bottom, respectively, and $\beta = 1$.}}
 	\label{fig:filter}
@@
 For visualization purposes, we depict in Figure \ref{fig:filter} the filtered trajectory $Z^\epl$ for three different values of $\delta$, namely $\delta = \{1, \sqrt{\epl}, \epl\}$.
-With $\delta = 1$, all oscillations at the fast scale are canceled and the filtered trajectory $Z^\epl$ presents only slow-scale variations are present in $Z^\epl$.
+With $\delta = 1$, all oscillations at the fast scale are canceled and the filtered trajectory $Z^\epl$ presents only slow-scale variations.
 Reducing the value of $\delta$, fast-scale oscillations are progressively taken into account.
@@
 
-\begin{example}\label{ex:OrnUhl} A closed form solution of \eqref{eq:FPsystem} can be obtained in a simple homogenized case with the dimension of the parameter $N=1$.
-Let $p(y) = 0$ and the parameters $\alpha$, $\sigma$ be replaced respectively by $A$ and $\Sigma$.
-Then, if $V(x) = x^2/2$, equation \eqref{eq:FPsystem} has the analytical solution
-\begin{equation}
-\rho^0(x,z) = \frac{1}{C_{\rho^0}} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right),
-\end{equation}
-where
-\begin{equation}
-C_{\rho^0} = \int_{\R} \int_{\R} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right) \dd x \dd z.
-\end{equation}
-This is the density of a multivariate normal distribution $\mathcal N(0, \Gamma)$, where the covariance matrix is given by
-\begin{equation}
-\Gamma = \frac{\Sigma}{A (1 + A\delta)} \begin{pmatrix} 1+A\delta & 1 \\ 1 & 1 \end{pmatrix}.
-\end{equation}
-Let us remark that this distribution can be obtained from direct computations involving Gaussian processes.
-In particular, it is known that $X \sim \mathcal{GP}(\mu_t, \mathcal C(t, s))$, where at stationarity $\mu_t = 0$ and
-\begin{equation}
-	\mathcal C(t, s) = \frac{\Sigma}{A} e^{-A|t-s|}.
-\end{equation}
-The basic properties of Gaussian processes imply that $Z$ is a Gaussian process, and that the couple $(X, Z)^\top$ is a Gaussian process, too, whose mean and covariance are computable explicitly.
-\end{example}
-
 In a general case, it is not possible to find an explicit solution to \eqref{eq:FPsystem}.
@@
 The analysis in this case is based on the convergence of the couple $(X^\epl, Z^\epl)^\top$ with respect to the multiscale parameter $\epl \to 0$.} In particular, it is known that the invariant measure of $X^\epl$ converges weakly to the invariant measure of $X$ solution of the homogenized equation \eqref{eq:SDE_HOM}.
-The following result, whose proof is given in Appendix \ref{ap:ProofsErgodic}, guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.
+The following result guarantees the same kind of convergence for the couple $(X^\epl, Z^\epl)^\top$.
 
@@
 
-We conclude this section presenting an analogous result to Lemma \ref{lem:FPMarginal} for the limit distribution.
+\begin{example}\label{ex:OrnUhl} A closed form solution of \eqref{eq:FPsystem_homogenized} can be obtained in the simple case with the dimension of the parameter $N=1$ and $V(x) = x^2/2$.
+The analytical solution is given by
+	\begin{equation}
+	\rho^0(x,z) = \frac{1}{C_{\rho^0}} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right),
+	\end{equation}
+	where
+	\begin{equation}
+	C_{\rho^0} = \int_{\R} \int_{\R} \exp\left(-\frac{A}{\Sigma} \frac{x^2}{2} - \frac{1}{\delta \Sigma} \frac{(x - (1+A \delta)z)^2}{2}\right) \dd x \dd z.
+	\end{equation}
+	This is the density of a multivariate normal distribution $\mathcal N(0, \Gamma)$, where the covariance matrix is given by
+	\begin{equation}
+	\Gamma = \frac{\Sigma}{A (1 + A\delta)} \begin{pmatrix} 1+A\delta & 1 \\ 1 & 1 \end{pmatrix}.
+	\end{equation}
+	Let us remark that this distribution can be obtained from direct computations involving Gaussian processes.
+In particular, it is known that $X \sim \mathcal{GP}(\mu_t, \mathcal C(t, s))$, where at stationarity $\mu_t = 0$ and
+	\begin{equation}
+	\mathcal C(t, s) = \frac{\Sigma}{A} e^{-A|t-s|}.
+	\end{equation}
+	The basic properties of Gaussian processes imply that $Z$ is a Gaussian process, and that the couple $(X, Z)^\top$ is a Gaussian process, too, whose mean and covariance are computable explicitly.
+\end{example}
+
+We now present an analogous result to Lemma \ref{lem:FPMarginal} for the limit distribution.
 
@@
 \end{equation}
-\i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to Lemma \ref{lem:convMeasure}.
+i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to Lemma \ref{lem:convMeasure}.
 For completeness, we introduce here the symmetric matrices $\mathcal M_\epl$ and $\mathcal M_0$ which are defined as
@@
 	\end{equation}
-	where $\Sigma$ is the diffusion coefficient of the homogenized equation \ref{eq:SDE_HOM}.
+	where $\Sigma$ is the diffusion coefficient of the homogenized equation \eqref{eq:SDE_HOM}.
 \end{lemma}
@@
 		\end{equation}
-		where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_MS}.
+		where $A$ is the drift coefficient of the homogenized equation \eqref{eq:SDE_HOM}.
 \end{theorem}
@@
 	\end{equation}
-	Therefore, since $\delta = \mathcal O(\epl^\zeta)$ for $\zeta \in (0, 2)$, and due to geometric ergodicity the terms $J_2^\epl(t)$ and $J_3^\epl(t)$ vanish in the limit for $t \to \infty$ and $\epl \to 0$.
+	Therefore, since $\delta = \mathcal O(\epl^\zeta)$ for $\zeta \in (0, 2)$, the terms $J_2^\epl(t)$ and $J_3^\epl(t)$ vanish in the limit for $t \to \infty$ and $\epl \to 0$.
 Furthermore, by Lemma \ref{lem:distanceMandTildeM} and by weak convergence of the invariant measure $\mu^\epl$ to $\mu^0$, we have
@@
 \end{equation}
-There is no guarantee under Assumption \ref{as:regularity} that $\widehat C_{T, \epl}$ is positive define and therefore a covariance matrix.
+There is no guarantee under Assumption \ref{as:regularity} that $\widehat C_{T, \epl}$ is positive definite and therefore a covariance matrix.
 Hence, in this Bayesian setting, we consider a different modification of the likelihood where we perturb only the vector $h$, i.e.,
@@
 The following theorem guarantees the unbiasedness of this estimator under a condition on the parameter $\delta$ of the filter.
-\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem} hold. Then, if \corr{$\delta = \epl^\zeta$, with $\zeta \in (0, 2)$}, it holds
+\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem_zeta} hold. Then, if \corr{$\delta = \epl^\zeta$, with $\zeta \in (0, 2)$}, it holds
 	\begin{equation}
@@
 	\end{equation}
-	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem}. Now, the triangle inequality yields
+	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem_zeta}. Now, the triangle inequality yields
 	\begin{equation}
@@
 	\end{equation}
-	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta = \mathcal O(\epl^\zeta)$, the desired result holds.
+	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta = \epl^\zeta$, the desired result holds.
 \end{proof}
@@
 
-The following lemma characterizes the action of the filter when it is applied to polynomials.
+The following lemma characterizes the action of the filter when it is applied to polynomials in $(t-s)$.
 \begin{lemma}\label{lem:FilterPoly} With the notation of Lemma \ref{lem:FilterJensen}, it holds for all $p \geq 0$
@@
 
-We can now prove Lemma \ref{prop:zeta}. Denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
+We can now prove Proposition \ref{prop:zeta}. Denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
 \cite[Formula 5.8]{PaS07}
@@
 
-Corollary \ref{cor:distanceZandX} is a direct consequence of Lemma \ref{prop:zeta} and provides a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.
+Corollary \ref{cor:distanceZandX} is a direct consequence of Proposition \ref{prop:zeta} and provides a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.
 
@@
 \begin{proof}
-	Let $p \geq 1$, then due to Lemma \ref{prop:zeta} there exists a constant $C > 0$ depending only on $p$ such that
+	Let $p \geq 1$, then due to Proposition \ref{prop:zeta} there exists a constant $C > 0$ depending only on $p$ such that
 	\begin{equation}
@@
 	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
-In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $C$ depending on the initial condition and $p$
-	\begin{equation}
-	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + Ce^{-\lambda t},
+In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $\widetilde C$ depending on the initial condition and $p$
+	\begin{equation}
+	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + \widetilde Ce^{-\lambda t},
 	\end{equation}
@@
 	\begin{equation}
-	f(z,b) = \frac12 b^2 V''(z)
+	f(z,b) = \frac12 b^2 V''(z),
 	\end{equation}
@@
 	\end{equation}
-	We now consider the remainder and, applying Hölder's inequality, Corollary \ref{cor:distanceZandX}, Lemma \ref{lem:bounded_momentZ} and \eqref{eq:estimate_beta}, we get for $p,q,r$ such that $1/p+1/q+1/r=1$
+	We now consider the remainder and, applying Hölder's inequality, Corollary \ref{cor:distanceZandX}, Lemma \ref{lem:bounded_momentZ}, Assumption \ref{as:regularityZeta} and \eqref{eq:estimate_beta}, we get for $p,q,r$ such that $1/p+1/q+1/r=1$
 	\begin{equation}
@@
 	\end{equation}
-	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularity} and Lemma \ref{cor:distanceZandX} we have
+	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularityZeta} and Lemma \ref{cor:distanceZandX} we have
 	\begin{equation}
@@
 	\end{equation}
-	Therefore, by equations \eqref{eq:SDE_HOM}, \eqref{eq:K_HOM} and \eqref{eq:phi0} we have
+	Therefore, since $\Sigma = K\sigma$ and by equations \eqref{eq:K_HOM} and \eqref{eq:phi0} we have
 	\begin{equation}

### 2020-03-26 PaperSDE.tex
Added a structure file and changed the name of the pdf file to PaperSDE

--- 2020-03-26 CalNotes.tex
@@
 
-\begin{example}\label{ex:OrnUhl} A closed form solution of \eqref{eq:FPsystem_homogenized} can be obtained in the simple case with the dimension of the parameter $N=1$ and $V(x) = x^2/2$.
-The analytical solution is given by
+\begin{example}\label{ex:OrnUhl} A closed form solution of \eqref{eq:FPsystem_homogenized} can be obtained in a simple case.
+Let the dimension of the parameter $N=1$ and let $V(x) = x^2/2$.
+Then, the analytical solution is given by
 	\begin{equation}
@@
 
-We can now prove Proposition \ref{prop:zeta}. Denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
+\subsection{Proof of Proposition \ref{prop:zeta}}
+Denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
 \cite[Formula 5.8]{PaS07}
@@
 \end{equation}
-which is obtained applying the Itô formula to $\Phi$, the solution of the cell problem \eqref{eq:CellProblem}.
-
-\subsection{Proof of Proposition \ref{prop:zeta}}
-
-Recall that by definition of $Z_t^\epl$ we have
+which is obtained applying the Itô formula to $\Phi$, the solution of the cell problem \eqref{eq:CellProblem}. Recall that by definition of $Z_t^\epl$ we have
 	\begin{equation}

### 2020-03-31 PaperSDE.tex
small corrections
Modifications after discussion with AA -- waiting for new data

@@
 In particular, we show that smoothing the data coming from the multiscale model with an appropriate linear time-invariant filter of the exponential family allows to retrieve the drift coefficient of the homogenized equation.
-The methodology we present is not involved computationally, easy to implement in practice and presents two main advantages:
+\corr{The methodology we present is not involved computationally, easy to implement in practice and robust.
+In particular, we show theoretically and demonstrate via numerical experiments that
 \begin{enumerate}
-	\item the filter's kernel depends on two parameters which can be tuned to obtain more robust results and which can be interpreted as analogous to the subsampling rate.
-Nevertheless, while the MLE is extremely sensitive with respect to the latter, our filtering methodology is robust with respect to its parameters, and can therefore be applied as a black-box tool for parameter estimation,
+	\item the smoothing width of the filter can be alternatively tuned to be proportional to the speed of the slow process or to smaller scales and provide in both cases unbiased results for maximum likelihood parameter estimation.
+Sharp estimates on the minimal width with respect to the multiscale parameter are provided.
+	\item estimations based on our technique are robust in practice with respect to the parameter of the filter.
+This is not the case for subsampling, which is strongly influenced by the subsampling frequency.
 	\item the entire stream of data is employed, which, in practice, enhances the quality of the filter-based MLE in terms of bias.
 Moreover, avoiding subsampling and thus discretising the data allows us to employ continuous-time theoretical tools.
+	\item it is possible to insert the filtering methodology into a continuous-time Bayesian framework by a careful modification of the likelihood function.
+Under mild hypotheses on the filter parameters, we are able to show that the posterior distributions obtained with our methodology are asymptotically consistent with respect to the drift parameter of the homogenized equation.
 \end{enumerate} 
-After having deduced unbiased estimators, we focus on how to insert the filtering methodology into a Bayesian approach.
-In particular, we analyse the effects of modifying the likelihood function if the smoothed trajectory is inserted in an appropriate manner.
-Under mild hypotheses on the filter parameters, we are able to show that the posterior distributions obtained with our methodology are asymptotically consistent with respect to the drift parameter of the homogenized equation.
-To our knowledge, this is the first instance of a successful Bayesian approach applied to multiscale diffusion processes.
+}
 
@@
 	\centering
-	\begin{tabular}{c}
-		\includegraphics[]{Figures/TrajD1} \\
-		\includegraphics[]{Figures/TrajD5} \\
-		\includegraphics[]{Figures/TrajD10}
+	\begin{tabular}{cc}
+		\includegraphics[]{Figures/TrajD1} & \includegraphics[]{Figures/TrajD1Z}\\
+		\includegraphics[]{Figures/TrajD5} & \includegraphics[]{Figures/TrajD5Z} \\
+		\includegraphics[]{Figures/TrajD10}& \includegraphics[]{Figures/TrajD10Z}
 	\end{tabular}
@@
 
-\subsection{Filtering at the slow scale}\label{sec:Slow}
+\subsection{Filtering at the homogenized regime}\label{sec:Slow}
 
@@
 
-\subsection{Filtering at faster scales}\label{sec:Fast}
+\subsection{Filtering at the multiscale regime}\label{sec:Fast}
 
@@
 	\begin{equation}
-		\lim_{\epl \to 0}\lim_{T \to \infty} \E \left[\mu_{T,\epl}\left(\{a\colon \norm{a-A}_2\geq c\}\mid X^\epl\right)\right] = 0,
+		\lim_{\epl \to 0}\lim_{T \to \infty} \E \left[\widetilde \mu_{T,\epl}\left(\{a\colon \norm{a-A}_2\geq c\}\mid X^\epl\right)\right] = 0,
 	\end{equation}
@@
 \subsection{Parameters of the filter}\label{sec:Num_Param}
+
+For the first preliminary experiments, we consider $N = 1$ and the quadratic potential $V(x) = x^2/2$.
+In this case, the solution of the homogenized equation is an Ornstein--Uhlenbeck process.
+Moreover, we set the the fast potential in the multiscale equation \eqref{eq:SDE_MS} as $p(y) = \cos(y)$.
+In all experiments, data is generated employing the Euler--Maruyama method with a fine time step.
+
+\subsubsection{Verification of theoretical results}\label{sec:Num_Param1}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[]{Figures/Transition}
+	\caption{Results for Section \ref{sec:Num_Param1}.
+Horizontal lines represent $\alpha$ and $A$, the drift coefficients of the unhomogenized and homogenized equations.
+The gray vertical line represents the lower bound for the validity of Theorem \ref{thm:mainTheorem_zeta}.
+The curved lines (dashed, dotted and dash-dotted) represents the values of $\widehat A_k^\epl(T)$ for $\epl = \{0.1, 0.05, 0.025\}$, respectively.
+Remark that the $\delta$-axis is in logarithmic scale.}
+	\label{fig:TheoremVerification}
+\end{figure}
+
+We first demonstrate numerically the validity of Theorems \ref{thm:mainTheorem} and \ref{thm:mainTheorem_zeta}, i.e., the unbiasedness of $\widehat A^\epl_k(T)$ for $\delta = \epl^\zeta$ with $\zeta \in [0, 2)$.
+Let us recall that for $\zeta = 0$ the analysis and the theoretical result are fundamentally different than for $\zeta \in (0, 2)$.
+We consider $\epl \in \{0.1, 0.05, 0.025\}$, the diffusion coefficient $\sigma = 1$ and generate data $X^\epl_t$ for $0 \leq t \leq T$ with $T = 10^3$.
+Then we filter the data by choosing $\delta = \epl^\zeta$, and $\zeta = 0, 0.1, 0.2,\ldots, 3$, and compute $\widehat A^\epl_k(T)$.
+Results are displayed in Figure \ref{fig:TheoremVerification}, and show that for $\zeta > 2$, i.e., $\delta = o(\epl^2)$, the estimator tends to the drift coefficient $\alpha$ of the unhomogenized equation.
+Conversely, as predicted by the theory, for $\zeta \in [0, 2)$ the estimator tends to $A$, the drift coefficient of the homogenized equation.
+Therefore, the point $\delta = \epl^2$ acts asymptotically as a switch between two completely different regimes.
+The transition between these two regimes is theoretically sharp in the limit for $\epl \to 0$.
+In finite computations the passage between $A$ and $\alpha$ is smoother, and suggests to take, if possible, $\delta = \epl^0$.
+In the Bayesian case one has to fix $\zeta > 0$, and results indicate that possibly $\zeta$ should be close to $0$.
+In particular, all values of $\zeta \in [0, 1]$ seem to output similarly good results.
+
+\subsubsection{Comparison with subsampling}\label{sec:Num_Param2}
+
 \begin{figure}[t]
@@
 	\end{tabular}
-	\caption{Results for the Ornstein--Uhlenbeck process.
-The axis of abscissae $\zeta$ represents the value of $\delta = \epl^\zeta$ for both subsampling and the filter.
+	\caption{Results for Section \ref{sec:Num_Param2}.
+The case of $\delta = \epl^0$ is highlighted as a solid dot for the filtering technique, as the analysis and theoretical result is different in this case.
 The three rows correspond to $\sigma = 0.5, 0.7, 1.0$ from top to bottom.}
@@
 \end{figure}
-We consider $N = 1$ and the quadratic potential $V(x) = x^2/2$.
-In this case, the solution of the homogenized equation is an Ornstein--Uhlenbeck process.
-Moreover, we set the multiscale equation \eqref{eq:SDE_MS} with $\epl = 0.1$ and the fast potential $p(y) = \cos(y)$.
-We generate data $X^\epl$ for $0 \leq t \leq T$ and $T = 10^3$ employing the Euler--Maruyama method with time step $\Delta_t = \epl^3$.
-
-As a first experiment, we consider the effect of setting different values of the parameter $\delta$ of the filter \eqref{eq:filter} on the estimator.
-As a comparison and for similarity with the subsampling approach, we consider $\delta = \epl^{\zeta}$ and vary $\zeta \in [0, 1]$.
-We employ the same values of $\delta$ for the subsampling, too, as the theoretical results guarantee convergence only for these values.
-Moreover, we repeat the experiments fixing $\beta = 1, 5$ and for three different values of the diffusion, i.e., we choose $\sigma = 0.5, 0.7, 1$.
+
+We now compare the results given by the filtering technique with the results given by subsampling the data, i.e., the difference between the estimators $\widehat A^\epl_k(T)$ and $\widehat A^\epl_\delta(T)$.
+We fix the diffusion coefficient $\sigma = 0.5$, the multiscale parameter $\epl = 0.1$ and generate data for $0 \leq t \leq T$ with $T = 10^3$.
+We choose $\delta = \epl^{\zeta}$ and vary $\zeta \in [0, 1]$, where $\delta$ is the filtering and the subsampling width, respectively.
+Moreover, for the filtering method we consider both $\beta = 1$ and $\beta = 5$.
 We report in Figure \ref{fig:OU} the experimental results.
@@
 	\item the dependence on $\delta$ of numerical results given by the filter seems relevant only in case $\beta = 1$ and for small values of $\sigma$.
-For $\beta = 1$ and higher values of $\sigma$, the estimator is stable with respect to this parameter, as predicted in Theorem \ref{thm:mainTheorem}.
+For $\beta = 1$ and higher values of $\sigma$, the estimator is stable with respect to this parameter.
 This can be observed for a higher value of $\beta$ but we have no theoretical guarantee in this case.
@@
 
-As a second experiment, we therefore test the variability of the estimator with respect to $\beta$ in \eqref{eq:filter}.
-We repeat the numerical experiment in Figure \ref{fig:OU} and we choose to consider $\delta = \epl$, which corresponds to $\zeta = 1$ and seems to be the worst-case scenario for the filter, at least for $\beta = 1$.
+\subsubsection{The influence of $\beta$}\label{sec:Num_Param3}
+We finally test the variability of the estimator with respect to $\beta$ in \eqref{eq:filter}.
+We consider $\delta = \epl$, which corresponds to $\zeta = 1$ and seems to be the worst-case scenario for the filter, at least for $\beta = 1$.
 We consider again $\sigma = 0.5, 0.7, 1$ and vary $\beta = 1, 2, \ldots, 10$.
-Results, given in Figure \ref{fig:OUBeta}, show empirically that the estimator is fast stable with respect to $\beta$.
+Results, given in Figure \ref{fig:OUBeta}, show empirically that the estimator stabilizes fast with respect to $\beta$.
+Nevertheless, there is no theoretical guarantee supporting this empirical observation.
 
@@
 	\end{tabular}
-	\caption{Dependence of the estimator given by the filter for the Ornstein--Uhlenbeck process on the parameter $\beta$ in \eqref{eq:filter}.
+	\caption{Results for Section \ref{sec:Num_Param3}.
+The result for $\beta=1$, for which there are theoretical guarantees given by Theorem \ref{thm:mainTheorem_zeta}, is highlighted as a solid dot.
 From left to right we consider different values of $\sigma$.}
@@
 
-\subsection{Multi-dimensional drift coefficient}
+\subsection{Multi-dimensional drift coefficient}\label{sec:Num_Multi}
 
@@
 	\end{tabular}
-	\caption{Results for the four-dimensional parameter. From left to right the potential function estimated with the data itself, the filter, subsampled data.}
-	\label{fig:KLStyle}
-\end{figure}
-
-\begin{table}[t]
-	\centering
+
 	\begin{tabular}{cccccc}
@@
 	\end{tabular}
-	\caption{Numerical results for the four-dimensional parameter.}
-	\label{tab:KLStyle}
-\end{table}
+	\caption{Results for Section \ref{sec:Num_Multi}.
+In the figure, from left to right the potential function estimated with the data itself, the filter, subsampled data.
+In the table, numerical results for the single components of the true and estimated drift coefficients.}
+	\label{fig:KLStyle}
+\end{figure}
 
@@
 In particular, we pick this specific value of $\delta$ for the subsampling following the optimality criterion given in \cite{PaS07}.
-Results, given in Figure \ref{fig:KLStyle} and Table \ref{tab:KLStyle}, show that the filter-based estimation captures well the homogenized potential as well as the coefficient $A$.
+Results, given in Figure \ref{fig:KLStyle}, show that the filter-based estimation captures well the homogenized potential as well as the coefficient $A$.
 Moreover, it is possible to remark the negative result given by Theorem \ref{thm:Bias} holds in practice, i.e., with no pre-processing the estimator $\widehat A^\epl(T)$ tends to the drift coefficient $\alpha$ of the unhomogenized equation.
 
-\subsection{The Bayesian approach: bistable potential}
+\subsection{The Bayesian approach: bistable potential} \label{sec:Num_Bayes}
 \begin{figure}[t]
@@
 	\end{tabular}
-	\caption{Posterior distributions over the parameter $A = (A_1, A_2)^\top$ for the bistable potential obtained with the filtering approach.
+	\caption{Results for Section \ref{sec:Num_Bayes}.
+Posterior distributions over the parameter $A = (A_1, A_2)^\top$ for the bistable potential obtained with the filtering approach.
 The figures refer to final time $T = 100, 200, 400$ from left to right, respectively.
@@
 	\begin{aligned}
-	\sigma \E^{\eta^\epl} [V''(Z^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) (1 + \Phi'(y))^2 \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
+	\sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) (1 + \Phi'(y))^2 \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
 	&= \sigma \left( \int_\R V''(x) \frac{1}{C_{\lambda_x}} \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \\

### 2020-03-31 PaperSDE.tex
proof delta=eps^zeta with zeta>2

@@
 	\end{equation}
-	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ be its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
+	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ being its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
 In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $\widetilde C$ depending on the initial condition and $p$
@@
 	which shows that $\Delta_2(\epl) = 0$ and completes the proof. \qed
+
+\section{The end ?}
+
+\begin{theorem}\label{thm:mainTheorem_zetaAlpha} Let the assumptions of Lemma \ref{lem:ergodicity} and Assmuption \ref{as:regularityZeta} hold.
+Let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and $\delta = \epl^\zeta$ with $\zeta > 2$.
+If $\widetilde M$ is invertible, then
+	\begin{equation}
+	\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A_k^\epl(T) = \alpha, \quad \text{in probability},
+	\end{equation}
+	where $\alpha$ is the drift coefficient of the multiscale equation \ref{eq:SDE_MS}.
+\end{theorem}
+\begin{proof}
+	First, let us remark that by equation \ref{eq:SDE_MS} we have for all $0 \le s < t$
+	\begin{equation}
+		X_t^\epl - X_s^\epl = -\alpha \int_s^t V'(X_r^\epl) \dd r - \frac1\epl \int_s^t p' \left( \frac{X_r^\epl}{\epl} \right) \dd r + \sqrt{2\sigma}(W_t - W_s),
+	\end{equation}
+	and applying Jensen's inequality and due to the assumptions on $p$ and the fact that $X_t^\epl$ has bounded moments of all orders (see \cite[Corollary 5.4]{PaS07}), it holds for any $p \ge 1$
+	\begin{equation} \label{eq:Xt_Xs}
+		\E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^p \le C \left( (t-s)^p + (t-s)^p\epl^{-p} + (t-s)^{p/2} \right),
+	\end{equation}
+	where $\phi^\epl$ is the invariant measure of $X^\epl$ and $C>0$ is a constant independent of $s$, $t$ and $\epl$. By definition of $Z_t^\epl$ we have
+	\begin{equation}
+		X_t^\epl - Z_t^\epl = \int_0^t k(t-s) (X_t^\epl - X_s^\epl) \dd s + e^{-t/\delta}X_t^\epl,
+	\end{equation}
+	therefore, by \eqref{eq:Xt_Xs} and Lemmas \ref{lem:FilterJensen} and \ref{lem:FilterPoly}, we deduce
+	\begin{equation}
+	\begin{aligned}
+		\E^{\phi^\epl} \abs{X_t^\epl - Z_t^\epl}^p &\le C \left( \int_0^t k(t-s) \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^p \dd s + e^{-pt/\delta}  \E^{\phi^\epl} \abs{X_t^\epl}^p \right) \\
+		&\le C \left( \delta^p + \delta^p\epl^{-p} + \delta^{p/2} + e^{-pt/\delta} \right).
+	\end{aligned}
+	\end{equation}
+	Let us recall that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ being its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
+Moreover, due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $\widetilde C$ depending on the initial condition and $p$
+	\begin{equation}
+		\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + \widetilde Ce^{-\lambda t},
+	\end{equation}
+	which, for $t$ sufficiently big, yields
+	\begin{equation} \label{eq:Xt_Zt}
+		\left( \E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \right)^{1/p} \le C \left( \delta + \delta \epl^{-1} + \delta^{1/2} \right).
+	\end{equation}
+	Let us now consider decomposition \eqref{eq:alphaDecomposition}
+	\begin{equation}
+	\widehat A_k^\epl(T) = \alpha + I_1^\epl(T) - I_2^\epl(T),
+	\end{equation}
+	where 
+	\begin{equation}
+	\lim_{T \to \infty} I_1^\epl(T) = \widetilde {\mathcal M}_\epl^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ], \quad \text{a.s.}
+	\end{equation}
+	and
+	\begin{equation}
+	\lim_{T \to \infty} I_2^\epl(T) = 0, \quad \text{a.s.}
+	\end{equation}
+	Then, by assumptions on $V$ we can write
+	\begin{equation}
+	V'(Z^\epl) = V'(X^\epl) + V''(\widetilde X^\epl) (Z^\epl - X^\epl),
+	\end{equation}
+	where $\widetilde X^\epl$ is a random variable which assumes values between $X^\epl$ and $Z^\epl$. Therefore we have
+	\begin{equation}
+	\begin{aligned}
+	\E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] &= \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(X^\epl) \right ] + \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V''(\widetilde X^\epl) (Z^\epl - X^\epl) \right ] \\
+	&\eqdef J_1^\epl + J_2^\epl,
+	\end{aligned}
+	\end{equation}
+	and in order to conclude we need to show that $J_1^\epl$ and $J_2^\epl$ vanish as $\epl$ goes to zero. Integrating by parts we have
+	\begin{equation}
+	\begin{aligned}
+	J_1^\epl &= \int_\R \frac{1}{\epl} p' \left( \frac{x}{\epl} \right) V'(x) \frac{1}{C_{\rho^\epl}} \exp \left( -\frac\alpha\sigma V'(x) - \frac1\sigma p\left(\frac{x}{\epl}\right) \right) \dd x \\
+	&= \int_\R \left ( \sigma V''(x) -  \left(V'(x) \otimes V'(x)\right) \alpha \right) \frac{1}{C_{\rho^\epl}} \exp \left( -\frac\alpha\sigma V'(x) - \frac1\sigma p\left(\frac{x}{\epl}\right) \right) \dd x \\
+	&= \sigma \E^{\rho^\epl} \left[ V''(X^\epl) \right] - \E^{\rho^\epl} \left[ V'(X^\epl) \otimes V'(X^\epl) \right] \alpha,
+	\end{aligned}
+	\end{equation}
+	and passing to the limit as $\epl \to 0$ and integrating again by parts we obtain
+	\begin{equation} \label{eq:limJ1_0}
+	\lim_{\epl\to 0} J_1^\epl = \sigma \E^{\rho^0} \left[ V''(X) \right] - \E^{\rho^0} \left[ V'(X) \otimes V'(X) \right] \alpha = 0.
+	\end{equation}
+	We now consider $J_2^\epl$ and applying Hölder's inequality with conjugate exponents $p$ and $q$ and due to the assumptions on $p$ and $V$ we get
+	\begin{equation}
+	\abs{J_2^\epl} \le C \epl^{-1} \left( \E^{\rho^\epl} \abs{\widetilde X^\epl}^q \right)^{1/q} \left( \E^{\rho^\epl} \abs{Z^\epl - X^\epl}^p \right)^{1/p}.
+	\end{equation}
+	Since $\widetilde X^\epl$ assumes values between $X^\epl$ and $Z^\epl$, which both have bounded moments of all order respectively by \cite[Corollary 5.4]{PaS07} and Lemma \ref{lem:bounded_momentZ}, and due to \eqref{eq:Xt_Zt} we have
+	\begin{equation} \label{eq:limJ2_0}
+	\abs{J_2^\epl} \le C \left( \delta \epl^{-1} + \delta \epl^{-2} + \delta^{1/2} \epl^{-1} \right).
+	\end{equation}
+	 Moreover, by Lemma \ref{lem:distanceMandTildeM} and by weak convergence of the invariant measure $\mu^\epl$ to $\mu^0$, we have
+	\begin{equation}
+	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl = \mathcal M_0,
+	\end{equation}
+	which, together with \eqref{eq:limJ1_0}, \eqref{eq:limJ2_0} and the fact that $\delta = \epl^\zeta$ with $\zeta > 2$, implies the desired result.
+\end{proof}
+
 \end{appendices}

### 2020-04-01 PaperSDE.tex
Added negative result for zeta > 2

--- 2020-03-31 PaperSDE.tex
@@
 
+\corr{
+We conclude this section with a negative convergence result, i.e., that if $\delta = \epl^\zeta$ with $\zeta > 2$, the filtering estimator converges to the coefficient $\alpha$ of the unhomogenized equation.
+This result is relevant for two reasons.
+First, it shows the sharpness of the bound on $\zeta$ in the assumptions of Theorem \ref{thm:mainTheorem_zeta}.
+Second, it shows an interesting switch with boundary $\zeta=2$ between two completely different regimes, which happens arbitrarily fast in the limit $\epl \to 0$.
+\begin{theorem}\label{thm:mainTheorem_zetaAlpha} Let the assumptions of Lemma \ref{lem:ergodicity} and Assmuption \ref{as:regularityZeta} hold.
+Let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and $\delta = \epl^\zeta$ with $\zeta > 2$.
+If $\widetilde M$ is invertible, then
+	\begin{equation}
+	\lim_{\epl \to 0} \lim_{T \to \infty} \widehat A_k^\epl(T) = \alpha, \quad \text{in probability},
+	\end{equation}
+	where $\alpha$ is the drift coefficient of the multiscale equation \eqref{eq:SDE_MS}.
+\end{theorem}
+The proof is given in Appendix \ref{ap:ProofsDeltaZeta}.
+}
+
 \section{The Bayesian setting}\label{sec:Bayesian}
@@
 The curved lines (dashed, dotted and dash-dotted) represents the values of $\widehat A_k^\epl(T)$ for $\epl = \{0.1, 0.05, 0.025\}$, respectively.
-Remark that the $\delta$-axis is in logarithmic scale.}
+Remark that the $\delta$-axis is in logarithmic scale and is normalized with respect to $\epl$.}
 	\label{fig:TheoremVerification}
@@
 
+\corr{
+The result above can be in some sense rather counter-intuitive.
+Indeed, for a fixed $\epl > 0$ and for $\delta \to 0$ independently of $\epl$, one expects the filtered trajectory $Z^\epl$ to approach $X^\epl$.
+This is provided by the following Lemma.
+\begin{lemma}\label{lem:distanceZandX2} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
+Then, if $\delta \leq 1$, it holds for any $p \geq 1$
+	\begin{equation}
+	\left(\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p\right)^{1/p} \leq C\left(\delta\epl^{-1} + \delta^{1/2}\right),
+	\end{equation}
+	for a constant $C > 0$ independent of $\epl$ and $\delta$.	
+\end{lemma}
+\begin{proof}
+	By equation \eqref{eq:SDE_MS} we have for all $0 \le s < t$
+	\begin{equation}
+	X_t^\epl - X_s^\epl = -\alpha \int_s^t V'(X_r^\epl) \dd r - \frac1\epl \int_s^t p' \left( \frac{X_r^\epl}{\epl} \right) \dd r + \sqrt{2\sigma}(W_t - W_s).
+	\end{equation}
+	Therefore, by Assumption \ref{as:regularity} and since $X_t^\epl$ has bounded moments of all orders at stationarity \cite[Corollary 5.4]{PaS07}, it holds for any $p \ge 1$ and a constant $C > 0$
+	\begin{equation} \label{eq:Xt_Xs}
+	\E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^p \le C \left( (t-s)^p + (t-s)^p\epl^{-p} + (t-s)^{p/2} \right),
+	\end{equation}
+	where $\phi^\epl$ is the invariant measure of $X^\epl$. By definition of $Z_t^\epl$ we have
+	\begin{equation}
+	X_t^\epl - Z_t^\epl = \int_0^t k(t-s) (X_t^\epl - X_s^\epl) \dd s + e^{-t/\delta}X_t^\epl,
+	\end{equation}
+	which, applying Lemma \ref{lem:FilterJensen}, the inequality \eqref{eq:Xt_Xs} and Lemma \ref{lem:FilterPoly}, implies
+	\begin{equation}
+	\begin{aligned}
+	\E^{\phi^\epl} \abs{X_t^\epl - Z_t^\epl}^p &\le C \left( \int_0^t k(t-s) \E^{\phi^\epl} \abs{X_t^\epl - X_s^\epl}^p \dd s + e^{-pt/\delta}  \E^{\phi^\epl} \abs{X_t^\epl}^p \right) \\
+	&\le C \left( \delta^p + \delta^p\epl^{-p} + \delta^{p/2} + e^{-pt/\delta} \right).
+	\end{aligned}
+	\end{equation}
+	Geometric ergodicity (Lemma \ref{lem:ergodicity}) then implies for $\rho^\epl$ the measure of the couple $(X^\epl, Z^\epl)^\top$ and a constant $C > 0$
+	\begin{equation}
+	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + Ce^{-\lambda t},
+	\end{equation}
+	which, for $t$ sufficiently big and since $\delta \leq 1$ yields the desired result.
+\end{proof}
+}
 Let us conclude with a last preliminary estimate concerning the matrices $\widetilde{\mathcal M}_\epl$ and $\mathcal M_\epl$ defined in \eqref{eq:DefCalMTilde} and \eqref{eq:DefCalM}, respectively.
@@
 	which shows that $\Delta_2(\epl) = 0$ and completes the proof. \qed
+
+\subsection{Proof of Theorem \ref{thm:mainTheorem_zetaAlpha}}
+
+\begin{proof}
+	Let us consider the decomposition \eqref{eq:alphaDecomposition}, i.e.,
+	\begin{equation}
+	\widehat A_k^\epl(T) = \alpha + I_1^\epl(T) - I_2^\epl(T),
+	\end{equation}
+	where $I_1^\epl(T)$ is defined as
+	\begin{equation}
+		\lim_{T \to \infty} I_1^\epl(T) = \widetilde {\mathcal M}_\epl^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ], \quad \text{a.s.}
+	\end{equation}
+	and, by the proof of Theorem \ref{thm:mainTheorem} we have independently of $\epl$
+	\begin{equation}
+		\lim_{T \to \infty} I_2^\epl(T) = 0, \quad \text{a.s.}
+	\end{equation}
+	A Taylor expansion of the first order of $V'$ yields
+	\begin{equation}
+	V'(Z^\epl) = V'(X^\epl) + V''(\widetilde X^\epl) (Z^\epl - X^\epl),
+	\end{equation}
+	where $\widetilde X^\epl$ is a random variable which assumes values between $X^\epl$ and $Z^\epl$. We can therefore write
+	\begin{equation}
+	\begin{aligned}
+	\E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] &= \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(X^\epl) \right ] + \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V''(\widetilde X^\epl) (Z^\epl - X^\epl) \right ] \\
+	&\eqdef J_1^\epl + J_2^\epl.
+	\end{aligned}
+	\end{equation}
+	We now consider the two terms separately and show they vanish for $\epl \to 0$. Integrating by parts in $J_1^\epl$ we obtain
+	\begin{equation}
+	\begin{aligned}
+	J_1^\epl &= \int_\R \frac{1}{\epl} p' \left( \frac{x}{\epl} \right) V(x) \frac{1}{C_{\rho^\epl}} \exp \left( -\frac\alpha\sigma V(x) - \frac1\sigma p\left(\frac{x}{\epl}\right) \right) \dd x \\
+	&= \int_\R \left ( \sigma V''(x) -  \left(V'(x) \otimes V'(x)\right) \alpha \right) \frac{1}{C_{\rho^\epl}} \exp \left( -\frac\alpha\sigma V(x) - \frac1\sigma p\left(\frac{x}{\epl}\right) \right) \dd x \\
+	&= \sigma \E^{\rho^\epl} \left[ V''(X^\epl) \right] - \E^{\rho^\epl} \left[ V'(X^\epl) \otimes V'(X^\epl) \right] \alpha.
+	\end{aligned}
+	\end{equation}
+	We then pass to the limit as $\epl \to 0$ and integrate by parts again to obtain
+	\begin{equation} \label{eq:limJ1_0}
+	\lim_{\epl\to 0} J_1^\epl = \sigma \E^{\rho^0} \left[ V''(X) \right] - \E^{\rho^0} \left[ V'(X) \otimes V'(X) \right] \alpha = 0.
+	\end{equation}
+	We now turn to $J_2^\epl$. The Hölder's inequality with conjugate exponents $p$ and $q$ and the assumptions on $p$ and $V$ yield
+	\begin{equation}
+	\abs{J_2^\epl} \le C \epl^{-1} \left( \E^{\rho^\epl} \abs{\widetilde X^\epl}^q \right)^{1/q} \left( \E^{\rho^\epl} \abs{Z^\epl - X^\epl}^p \right)^{1/p}.
+	\end{equation}
+	Since $\widetilde X^\epl$ assumes values between $X^\epl$ and $Z^\epl$, it has bounded moments by \cite[Corollary 5.4]{PaS07} and Lemma \ref{lem:bounded_momentZ}.
+Hence, applying Lemma \ref{lem:distanceZandX2} we have
+	\begin{equation} 
+	\abs{J_2^\epl} \le C \left( \delta \epl^{-2} + \delta^{1/2} \epl^{-1} \right),
+	\end{equation}
+	which, since $\delta = \epl^\zeta$ with $\zeta > 2$, implies
+	\begin{equation}\label{eq:limJ2_0}
+		\lim_{\epl \to 0} \abs{J_2^\epl} = 0.
+	\end{equation}
+	Finally, Lemma \ref{lem:distanceMandTildeM} and the weak convergence of the invariant measure $\phi^\epl$ to $\phi^0$ imply
+	\begin{equation}
+	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl = \mathcal M_0,
+	\end{equation}
+	which, together with \eqref{eq:limJ1_0}, \eqref{eq:limJ2_0} implies that $J_1^\epl \to 0$ for $\epl \to 0$, which implies the desired result.
+\end{proof}
+
 \end{appendices}

### 2020-04-01 PaperSDE.tex
Minor fix
Minor Fix

@@
 
-We first demonstrate numerically the validity of Theorems \ref{thm:mainTheorem} and \ref{thm:mainTheorem_zeta}, i.e., the unbiasedness of $\widehat A^\epl_k(T)$ for $\delta = \epl^\zeta$ with $\zeta \in [0, 2)$.
+We first demonstrate numerically the validity of Theorem \ref{thm:mainTheorem}, Theorem \ref{thm:mainTheorem_zeta} and Theorem \ref{thm:mainTheorem_zetaAlpha}, i.e., the unbiasedness of $\widehat A^\epl_k(T)$ for $\delta = \epl^\zeta$ with $\zeta \in [0, 2)$.
 Let us recall that for $\zeta = 0$ the analysis and the theoretical result are fundamentally different than for $\zeta \in (0, 2)$.
@@
 \subsection{Proof of Theorem \ref{thm:mainTheorem_zetaAlpha}}
-
-\begin{proof}
 	Let us consider the decomposition \eqref{eq:alphaDecomposition}, i.e.,
@@
 	\end{equation}
-	which, together with \eqref{eq:limJ1_0}, \eqref{eq:limJ2_0} implies that $J_1^\epl \to 0$ for $\epl \to 0$, which implies the desired result.
-\end{proof}
+	which, together with \eqref{eq:limJ1_0}, \eqref{eq:limJ2_0} implies that $J_1^\epl \to 0$ for $\epl \to 0$, which implies the desired result. \qed
 

### 2020-04-01 PaperSDE.tex
Minor fix

@@
 	\end{equation}
-	which, together with \eqref{eq:limJ1_0}, \eqref{eq:limJ2_0} implies that $J_1^\epl \to 0$ for $\epl \to 0$, which implies the desired result. \qed
+	which, together with \eqref{eq:limJ1_0}, \eqref{eq:limJ2_0} implies that $I_1^\epl(T) \to 0$ for $\epl \to 0$, which implies the desired result. \qed
 

### 2020-04-01 PaperSDE.tex
C tilde

--- 2020-04-01 PaperSDE.tex
@@
 	\end{equation}
-	which, together with the definition of $k$ and the fact that $X_s^\epl$ has bounded moments of all orders \cite[Corollary 5.4]{PaS07}, implies
+	which, together with the definition of $k$ and the fact that $X_s^\epl$ has bounded moments of all orders \cite[Corollary 5.4]{PaS07}, implies for a constant $C>0$
 	\begin{equation}
@@
 	\end{equation}
-	In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $\widetilde C$ depending on the initial condition and $p$  
-	\begin{equation}
-	\E^{\rho^\epl} \abs{Z^\epl}^p \leq \E^{\phi^\epl}\abs{Z_t^\epl}^p + \widetilde C e^{-\lambda t},
+	In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$
+	\begin{equation}
+	\E^{\rho^\epl} \abs{Z^\epl}^p \leq \E^{\phi^\epl}\abs{Z_t^\epl}^p + C e^{-\lambda t},
 	\end{equation}
@@
 	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ being its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
-In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$ and for a constant $\widetilde C$ depending on the initial condition and $p$
-	\begin{equation}
-	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + \widetilde Ce^{-\lambda t},
+In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$
+	\begin{equation}
+	\E^{\rho^\epl} \abs{X^\epl - Z^\epl}^p \leq \E^{\phi^\epl}\abs{X_t^\epl - Z_t^\epl}^p + Ce^{-\lambda t},
 	\end{equation}
@@
 	\end{equation}
-	Geometric ergodicity (Lemma \ref{lem:ergodicity}) then implies for $\rho^\epl$ the measure of the couple $(X^\epl, Z^\epl)^\top$ and a constant $C > 0$
+	Geometric ergodicity (Lemma \ref{lem:ergodicity}) then implies for $\rho^\epl$ the measure of the couple $(X^\epl, Z^\epl)^\top$
 	\begin{equation}
@@
 	\end{equation}
-	which, together with \eqref{eq:limJ1_0}, \eqref{eq:limJ2_0} implies that $J_1^\epl \to 0$ for $\epl \to 0$, which implies the desired result. \qed
+	which, together with \eqref{eq:limJ1_0}, \eqref{eq:limJ2_0} implies that $I_1^\epl(T) \to 0$ for $T \to \infty$ and $\epl \to 0$, which implies the desired result. \qed
 

### 2020-04-01 PaperSDE.tex
SIAM Template

@@
 In particular, it has been shown that it is possible to infer a coarse-grained equation from data coming from the full model and to retrieve asymptotically the correct result \cite{NPS12}.
-A series of papers \cite{AbD18, AbD19, AGZ19} focuses on retrieving the full model when the multiscale coefficient is endowed with a specific parametrized structure.
-Being these problems ill-posed, the latter is achieved via Tikhonov regularization \cite{AbD19,NPS12}, adopting a Bayesian approach \cite{AbD18, NPS12} or exploiting techniques of Kalman filtering \cite{AGZ19}.
-In \cite{AbD18,AGZ19}, the authors highlight the need of accounting explicitly for the modelling error due to homogenization and apply statistical techniques taken from \cite{CDS18,CES14}.
+A series of papers \cite{AbD20, AbD19, AGZ19} focuses on retrieving the full model when the multiscale coefficient is endowed with a specific parametrized structure.
+Being these problems ill-posed, the latter is achieved via Tikhonov regularization \cite{AbD19,NPS12}, adopting a Bayesian approach \cite{AbD20, NPS12} or exploiting techniques of Kalman filtering \cite{AGZ19}.
+In \cite{AbD20,AGZ19}, the authors highlight the need of accounting explicitly for the modelling error due to homogenization and apply statistical techniques taken from \cite{CDS18,CES14}.
 

### 2020-04-01 SIAM_TEMPLATE/PaperSDE.tex
Fix

--- 2020-04-01 PaperSDE.tex
@@
-\documentclass[10pt]{article}
+\documentclass[review,onefignum,onetabnum]{siamonline190516}
 
@@
 \begin{document}
+
 \maketitle
 
-\textbf{Abstract.} We study the problem of drift estimation for two-scale continuous time series.
+\begin{abstract} We study the problem of drift estimation for two-scale continuous time series.
 We set ourselves in the framework of overdamped Langevin equations, for which a single-scale surrogate homogenized equation exists.
@@
 Finally, we show how our filtering methodology can be combined with Bayesian techniques and provide a full uncertainty quantification of the inference procedure.
-
-\textbf{AMS subject classifications.} 62F15, 65C30, 62M05, 74Q10.
-
-\textbf{Keywords.} Parameter inference, diffusion process, data-driven homogenization, filtering, Bayesian inference, Langevin equation.
+\end{abstract}
+
+\begin{keywords} Parameter inference, diffusion process, data-driven homogenization, filtering, Bayesian inference, Langevin equation. 
+\end{keywords}
+\begin{AMS} 62F15, 65C30, 62M05, 74Q10. \end{AMS}
 
@@
 
-\subsubsection{The influence of $\beta$}\label{sec:Num_Param3}
+\subsubsection{The second parameter of the filter}\label{sec:Num_Param3}
 We finally test the variability of the estimator with respect to $\beta$ in \eqref{eq:filter}.
@@
 	\begin{equation}
-	\sigma \int_\R \int_\R \partial_x f(x,z) \phi^\epl(x) \psi^\epl(z) \partial_x R^\epl(x,z) \dd x \dd z = \frac1\delta \int_\R \int_\R \partial_z f(x,z) (x-z) \phi^\epl(x) \psi^\epl(z) R^\epl(x,z) \dd x \dd z,
+	\begin{aligned}
+	\sigma \int_\R \int_\R \partial_x f(x,z) \phi^\epl(x) \psi^\epl(z) &\partial_x R^\epl(x,z) \dd x \dd z = \\
+	&\frac1\delta \int_\R \int_\R \partial_z f(x,z) (x-z) \phi^\epl(x) \psi^\epl(z) R^\epl(x,z) \dd x \dd z,
+	\end{aligned}
 	\end{equation}
@@
 	\begin{aligned}
-	\sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) (1 + \Phi'(y))^2 \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y \\
+	\sigma \E^{\eta^\epl} [V''(X^\epl) (1 + \Phi'(Y^\epl))^2] &= \sigma \int_\R \int_0^L V''(x) 
+	\begin{aligned}[t]
+	&(1 + \Phi'(y))^2\\
+	&\times \frac{1}{C_\lambda} \exp \left( - \frac\alpha\sigma V(x) - \frac1\sigma p(y) \right) \dd x \dd y 
+	\end{aligned}
+	\\
 	&= \sigma \left( \int_\R V''(x) \frac{1}{C_{\lambda_x}} \exp \left( - \frac\alpha\sigma V(x) \right) \dd x \right) \\
@@
 
-\bibliographystyle{siam}
+\bibliographystyle{siamplain}
 \bibliography{anmc}

### 2020-04-01 SIAM_TEMPLATE/PaperSDE.tex
Cref for SIAM template

@@
 \corr{
-\begin{remark}\label{rem:regularity_diss} In the following, in particular in the proof of Lemma \ref{lem:ergodicity}, we will employ Assumption \ref{as:regularity}\ref{as:regularity_diss} for the whole drift of the SDE \eqref{eq:SDE_MS}, i.e., the function
+\begin{remark}\label{rem:regularity_diss} In the following, in particular in the proof of \cref{lem:ergodicity}, we will employ \cref{as:regularity}\ref{as:regularity_diss} for the whole drift of the SDE \eqref{eq:SDE_MS}, i.e., the function
 	\begin{equation}
@@
 	\end{equation}
-	Since $p \in L^\infty$, the assumption above is sufficient for $V^\epl$ to satisfy Assumption \ref{as:regularity}\ref{as:regularity_diss} with different values for $a$ and $b$.
+	Since $p \in L^\infty$, the assumption above is sufficient for $V^\epl$ to satisfy \cref{as:regularity}\ref{as:regularity_diss} with different values for $a$ and $b$.
 In particular, if the condition holds for $\alpha \cdot V$ for a given $b > 0$, then one can choose a new value for the same coefficient which is arbitrarily close to the original one for $V^\epl$.
@@
 
-\begin{theorem}\label{thm:Bias} Let Assumption \ref{as:regularity} hold and let $X^\epl_0$ be distributed according to the invariant measure of the process $X^\epl$ solution of \eqref{eq:SDE_MS}. Then
+\begin{theorem}\label{thm:Bias} Let \cref{as:regularity} hold and let $X^\epl_0$ be distributed according to the invariant measure of the process $X^\epl$ solution of \eqref{eq:SDE_MS}. Then
 	\begin{equation}
@@
 
-In this section, we introduce and analyse a novel filtering approach to solve the biasedness issue highlighted by Theorem \ref{thm:Bias}.
+In this section, we introduce and analyse a novel filtering approach to solve the biasedness issue highlighted by \cref{thm:Bias}.
 Let $\beta, \delta > 0$ and let us consider a family of exponential kernel functions $k \colon \R^+ \to \R$ defined as
@@
 For subsampling, the choice guaranteeing asymptotically unbiased results is $\delta = \epl^\zeta$ with $\zeta \in (0, 1)$, and a similar analysis is due for our filtering technique.
-For visualization purposes, we depict in Figure \ref{fig:filter} the filtered trajectory $Z^\epl$ for three different values of $\delta$, namely $\delta = \{1, \sqrt{\epl}, \epl\}$.
+For visualization purposes, we depict in \cref{fig:filter} the filtered trajectory $Z^\epl$ for three different values of $\delta$, namely $\delta = \{1, \sqrt{\epl}, \epl\}$.
 With $\delta = 1$, all oscillations at the fast scale are canceled and the filtered trajectory $Z^\epl$ presents only slow-scale variations.
@@
 
-\begin{lemma}\label{lem:ergodicity} Let Assumption \ref{as:regularity} hold and let $b > 0$ be given in Assumption \ref{as:regularity}\ref{as:regularity_diss}.
+\begin{lemma}\label{lem:ergodicity} Let \cref{as:regularity} hold and let $b > 0$ be given in \cref{as:regularity}\ref{as:regularity_diss}.
 Then, if $\delta > 1/(4b)$, the process $(X^\epl, Z^\epl)^\top$ solution of \eqref{eq:systemSDE} is geometrically ergodic, i.e., there exists $C, \lambda > 0$ such that for all measurable $f\colon \R^2\to \R$ such that for some integer $q > 0$
@@
 Let the parameter dimension $N = 1$ and let $V(x) \propto x^{2p}$ for an integer $p > 1$.
-Then, Assumption \ref{as:regularity}\ref{as:regularity_diss} holds for an arbitrarily large $b > 0$.
+Then, \cref{as:regularity}\ref{as:regularity_diss} holds for an arbitrarily large $b > 0$.
 Therefore, the parameter of the filter $\delta$ can be chosen along the entire positive real axis.
@@
 
-\begin{lemma}\label{lem:FPMarginal} Under the assumptions of Lemma \ref{lem:ergodicity}, let $\rho^\epl$ be the solution of \eqref{eq:FPsystem} and let us write 
+\begin{lemma}\label{lem:FPMarginal} Under the assumptions of \cref{lem:ergodicity}, let $\rho^\epl$ be the solution of \eqref{eq:FPsystem} and let us write 
 \begin{equation}\label{eq:densityDecomposition}
@@
 
-\begin{lemma}\label{lem:convMeasure} Under Assumption \ref{as:regularity}, let $\mu^\epl$ be the invariant measure of the couple $(X^\epl, Z^\epl)^\top$ and let $(X_0^\epl, Z_0^\epl)^\top \sim \mu^\epl$.
+\begin{lemma}\label{lem:convMeasure} Under \cref{as:regularity}, let $\mu^\epl$ be the invariant measure of the couple $(X^\epl, Z^\epl)^\top$ and let $(X_0^\epl, Z_0^\epl)^\top \sim \mu^\epl$.
 \corr{If $\delta = \mathcal O(\epl^0)$,} then the measure $\mu^\epl$ converges weakly to the measure $\mu^0(\d x, \d z) = \rho^0(x, z) \dd x \dd z$, whose density $\rho^0$ is the unique solution of the Fokker--Planck equation
@@
 
-We now present an analogous result to Lemma \ref{lem:FPMarginal} for the limit distribution.
-
-\begin{corollary}\label{lem:FPMarginal_Hom} Let $\rho^0$ be the solution of \eqref{eq:FPsystem_homogenized} and let us write 
+We now present an analogous result to \cref{lem:FPMarginal} for the limit distribution.
+
+\begin{corollary}\label{cor:FPMarginal_Hom} Let $\rho^0$ be the solution of \eqref{eq:FPsystem_homogenized} and let us write 
 	\begin{equation}
@@
 \end{corollary}
-\begin{proof} The proof is directly obtained from Lemma \ref{lem:FPMarginal} replacing $p(y)=0$ and $\alpha, \sigma$ by $A, \Sigma$ respectively. 
+\begin{proof} The proof is directly obtained from \cref{lem:FPMarginal} replacing $p(y)=0$ and $\alpha, \sigma$ by $A, \Sigma$ respectively. 
 \end{proof}
@@
 \end{equation}
-i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to Lemma \ref{lem:convMeasure}.
+i.e., $\widetilde{\mathcal M}_\epl$ is the limit for $T \to \infty$ of the matrix $\widetilde M$ by the ergodic theorem, and $\widetilde{\mathcal M}_0$ is the limit for $\epl \to 0$ of the matrix $\widetilde{\mathcal M}_\epl$ due to \cref{lem:convMeasure}.
 For completeness, we introduce here the symmetric matrices $\mathcal M_\epl$ and $\mathcal M_0$ which are defined as
@@
 
-\begin{theorem}\label{thm:mainTheorem} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:convMeasure} hold, and let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} \corr{with $\delta = \mathcal O(\epl^0)$}.
+\begin{theorem}\label{thm:mainTheorem} Let the assumptions of \cref{lem:ergodicity} and \cref{lem:convMeasure} hold, and let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} \corr{with $\delta = \mathcal O(\epl^0)$}.
 If $\widetilde M$ is invertible, then
@@
 \end{equation}
-Due to Lemma \ref{lem:FPMarginal} and integrating by parts, we have
+Due to \cref{lem:FPMarginal} and integrating by parts, we have
 \begin{equation}
@@
 \end{equation}
-Due to Lemma \ref{lem:FPMarginal}, we therefore have
+Due to \cref{lem:FPMarginal}, we therefore have
 \begin{equation} \label{eq:for_zeta}
@@
 \end{equation}
-where the function $\rho^0$ is the density of the limit invariant distribution for $\epl \to 0$, as in Lemma \ref{lem:convMeasure}. Due to Corollary \ref{lem:FPMarginal_Hom}, we have
+where the function $\rho^0$ is the density of the limit invariant distribution for $\epl \to 0$, as in \cref{lem:convMeasure}. Due to \cref{cor:FPMarginal_Hom}, we have
 \begin{equation}\label{eq:final_result}
@@
 We now consider the case of the filtering width $\delta = \mathcal O(\epl^\zeta)$, where $\zeta > 0$ will be specified in the following.
-In this case, the filtered process resembles more the original process $X^\epl$, as can be noted in Figure \ref{fig:filter}.
-Moreover, the techniques employed for proving Theorem \ref{thm:mainTheorem} can only be partly exploited, as highlighted by Remark \ref{rem:deltaPower}.
+In this case, the filtered process resembles more the original process $X^\epl$, as can be noted in \cref{fig:filter}.
+Moreover, the techniques employed for proving \cref{thm:mainTheorem} can only be partly exploited, as highlighted by \cref{rem:deltaPower}.
 In fact, in order to prove unbiasedness it is necessary to characterize precisely the difference between the processes $Z^\epl$ and $X^\epl$.
@@
 
-\begin{proposition} \label{prop:zeta} Let Assumption \ref{as:regularity} hold and $\epl,\delta>0$ be sufficiently small. Then, it holds for every $t > 0$ sufficiently big 
+\begin{proposition} \label{prop:zeta} Let \cref{as:regularity} hold and $\epl,\delta>0$ be sufficiently small. Then, it holds for every $t > 0$ sufficiently big 
 	\begin{equation}
@@
 This equation can be coupled with the dynamics of the processes $X_t^\epl$, $Y_t^\epl$ and $Z_t^\epl$, thus describing the evolution of the quadruple $(X^\epl, Y^\epl, Z^\epl, B^\epl)$ together.
-In particular, it is possible to show that the results of Section \ref{sec:ergodic} hold for the quadruple, and the properties of the invariant measure of the quadruple can be exploited to prove the unbiasedness of the estimator in the case $\delta = \mathcal O(\epl^\zeta)$ in the same way as in the case $\delta = \mathcal O(\epl^0)$.
+In particular, it is possible to show that the results of \cref{sec:ergodic} hold for the quadruple, and the properties of the invariant measure of the quadruple can be exploited to prove the unbiasedness of the estimator in the case $\delta = \mathcal O(\epl^\zeta)$ in the same way as in the case $\delta = \mathcal O(\epl^0)$.
 In this context, a further assumption on the potential $V$ is necessary.
@@
 
-In light of Remark \ref{rem:deltaPower}, it is fundamental to understand the behavior of the quantity
+In light of \cref{rem:deltaPower}, it is fundamental to understand the behavior of the quantity
 \begin{equation}
@@
 \end{equation}
-and of its limit for $t\to \infty$ and for $\epl \to 0$. Let us remark that due to Proposition \ref{prop:zeta} we have
+and of its limit for $t\to \infty$ and for $\epl \to 0$. Let us remark that due to \cref{prop:zeta} we have
 \begin{equation}
@@
 
-\begin{lemma} \label{lem:quadruple} Under Assumptions \ref{as:regularity} and \ref{as:regularityZeta}, let $\eta^\epl$ be the invariant measure of the quadruple $(X^\epl, Y^\epl, Z^\epl, B^\epl)$.
-Then it holds
+\begin{lemma} \label{lem:quadruple} Under \cref{as:regularity} and \cref{as:regularityZeta}, let $\eta^\epl$ be the invariant measure of the quadruple $(X^\epl, Y^\epl, Z^\epl, B^\epl)$. Then it holds
 	\begin{equation}
@@
 
-\begin{lemma} \label{lem:quadruple_convergence} Let the assumptions of Lemma \ref{lem:quadruple} hold, and let $\delta = \epl^\zeta$ with $\zeta > 0$. Then, it holds
+\begin{lemma} \label{lem:quadruple_convergence} Let the assumptions of \cref{lem:quadruple} hold, and let $\delta = \epl^\zeta$ with $\zeta > 0$. Then, it holds
 	\begin{equation}
@@
 
-\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of Lemma \ref{lem:ergodicity} and Lemma \ref{lem:quadruple_convergence} hold.
+\begin{theorem}\label{thm:mainTheorem_zeta} Let the assumptions of \cref{lem:ergodicity} and \cref{lem:quadruple_convergence} hold.
 Let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and $\delta = \epl^\zeta$ with $\zeta \in (0,2)$.
@@
 	\end{equation}
-	where $\widetilde{\mathcal M}_\epl$ is defined in \eqref{eq:DefCalMTilde}.	Then following the proof of Theorem \ref{thm:mainTheorem} and in light of Remark \ref{rem:deltaPower}, we only need to show that if $\delta = \epl^\zeta$ with $\zeta \in (0,2)$ we have
+	where $\widetilde{\mathcal M}_\epl$ is defined in \eqref{eq:DefCalMTilde}.	Then following the proof of \cref{thm:mainTheorem} and in light of \cref{rem:deltaPower}, we only need to show that if $\delta = \epl^\zeta$ with $\zeta \in (0,2)$ we have
 	\begin{equation}
@@
 	\end{equation}
-	Using Lemma \ref{prop:zeta} and geometric ergodicity (Lemma \ref{lem:ergodicity}), we have the following equality
+	Using \cref{prop:zeta} and geometric ergodicity (\cref{lem:ergodicity}), we have the following equality
 	\begin{equation}
@@
 	\end{equation}
-	where $R(\epl, \delta)$ is given in Proposition \ref{prop:zeta}, $\E$ denotes the expectation with respect to the Wiener measure and
+	where $R(\epl, \delta)$ is given in \cref{prop:zeta}, $\E$ denotes the expectation with respect to the Wiener measure and
 	\begin{equation}
@@
 	\end{equation}
-	Let us consider the three terms separately. First, by geometric ergodicity and applying Lemma \ref{lem:quadruple} and Lemma \ref{lem:quadruple_convergence} we get
+	Let us consider the three terms separately. First, by geometric ergodicity and applying \cref{lem:quadruple} and \cref{lem:quadruple_convergence} we get
 	\begin{equation}
@@
 	Now, we can bound the first two terms with \eqref{eq:estimate_beta} and \eqref{eq:remainder_zeta}, respectively.
-The third term is bounded due to Assumption \ref{as:regularityZeta} and Lemma \ref{lem:bounded_momentZ}.
+The third term is bounded due to \cref{as:regularityZeta} and \cref{lem:bounded_momentZ}.
 Hence, we have
@@
 	Therefore, since $\delta = \mathcal O(\epl^\zeta)$ for $\zeta \in (0, 2)$, the terms $J_2^\epl(t)$ and $J_3^\epl(t)$ vanish in the limit for $t \to \infty$ and $\epl \to 0$.
-Furthermore, by Lemma \ref{lem:distanceMandTildeM} and by weak convergence of the invariant measure $\mu^\epl$ to $\mu^0$, we have
+Furthermore, by \cref{lem:distanceMandTildeM} and by weak convergence of the invariant measure $\mu^\epl$ to $\mu^0$, we have
 	\begin{equation}
@@
 This result is relevant for two reasons.
-First, it shows the sharpness of the bound on $\zeta$ in the assumptions of Theorem \ref{thm:mainTheorem_zeta}.
+First, it shows the sharpness of the bound on $\zeta$ in the assumptions of \cref{thm:mainTheorem_zeta}.
 Second, it shows an interesting switch with boundary $\zeta=2$ between two completely different regimes, which happens arbitrarily fast in the limit $\epl \to 0$.
-\begin{theorem}\label{thm:mainTheorem_zetaAlpha} Let the assumptions of Lemma \ref{lem:ergodicity} and Assmuption \ref{as:regularityZeta} hold.
+\begin{theorem}\label{thm:mainTheorem_zetaAlpha} Let the assumptions of \cref{lem:ergodicity} and \cref{as:regularityZeta} hold.
 Let $\widehat A^\epl_k(T)$ be defined in \eqref{eq:AHatMixed} and $\delta = \epl^\zeta$ with $\zeta > 2$.
@@
 \end{equation}
-Under Assumption \ref{as:regularity}, one can show that the posterior at time $T > 0$ is indeed given by $\mu_{T,\epl}(\cdotp\mid X^\epl) = \mathcal N(m_{T,\epl}, C_{T,\epl})$.
+Under \cref{as:regularity}, one can show that the posterior at time $T > 0$ is indeed given by $\mu_{T,\epl}(\cdotp\mid X^\epl) = \mathcal N(m_{T,\epl}, C_{T,\epl})$.
 \corr{In the following theorem, we show that the posterior distribution obtained with no pre-processing of the data contracts asymptotically to the drift coefficient of the unhomogenized equation.
@@
 
-\begin{theorem}\label{thm:BayesianBias} Under Assumption \ref{as:regularity}, the posterior measure $\mu_{T,\epl}(\cdotp\mid X^\epl) = \mathcal N(m_{T,\epl}, C_{T,\epl})$ satisfies for all $c > 0$
+\begin{theorem}\label{thm:BayesianBias} Under \cref{as:regularity}, the posterior measure $\mu_{T,\epl}(\cdotp\mid X^\epl) = \mathcal N(m_{T,\epl}, C_{T,\epl})$ satisfies for all $c > 0$
 	\begin{equation}
@@
 	\end{equation}
-	For the second term, Theorem \ref{thm:Bias} implies 
+	For the second term, \cref{thm:Bias} implies 
 	\begin{equation}
@@
 
-\begin{remark} The result above has the same consequences in the Bayesian setting as Theorem \ref{thm:Bias} has for the MLE.
+\begin{remark} The result above has the same consequences in the Bayesian setting as \cref{thm:Bias} has for the MLE.
 In particular, it shows that the posterior distribution obtained when data is not pre-processed concentrates asymptotically on the drift coefficient of the unhomogenized equation \eqref{eq:SDE_MS}.
@@
 
-In this section, we present how to correct the faulty behaviour highlighted by Theorem \ref{thm:BayesianBias} with filtering techniques.
+In this section, we present how to correct the faulty behaviour highlighted by \cref{thm:BayesianBias} with filtering techniques.
 Employing the filter in the same way as for the MLE, we can modify the likelihood function and obtain
@@
 \end{equation}
-There is no guarantee under Assumption \ref{as:regularity} that $\widehat C_{T, \epl}$ is positive definite and therefore a covariance matrix.
+There is no guarantee under \cref{as:regularity} that $\widehat C_{T, \epl}$ is positive definite and therefore a covariance matrix.
 Hence, in this Bayesian setting, we consider a different modification of the likelihood where we perturb only the vector $h$, i.e.,
@@
 Let us remark that the posterior $\widetilde \mu_{T,\epl}$ has the same covariance as $\mu_{T,\epl}$ and that therefore it is indeed a valid Gaussian posterior distribution.
-Nevertheless, in order to employ the tool of convergence introduced in Theorem \ref{thm:BayesianBias}, we need to study the properties of the MLE based on the likelihood $\widetilde p(X^\epl \mid A)$, i.e., the quantity
+Nevertheless, in order to employ the tool of convergence introduced in \cref{thm:BayesianBias}, we need to study the properties of the MLE based on the likelihood $\widetilde p(X^\epl \mid A)$, i.e., the quantity
 \begin{equation}\label{eq:AHatMixedTilde}
@@
 The following theorem guarantees the unbiasedness of this estimator under a condition on the parameter $\delta$ of the filter.
-\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of Theorem \ref{thm:mainTheorem_zeta} hold. Then, if \corr{$\delta = \epl^\zeta$, with $\zeta \in (0, 2)$}, it holds
+\begin{theorem}\label{thm:mainTheoremTilde} Let the assumptions of \cref{thm:mainTheorem_zeta} hold. Then, if \corr{$\delta = \epl^\zeta$, with $\zeta \in (0, 2)$}, it holds
 	\begin{equation}
@@
 	almost surely, where $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ are defined in \eqref{eq:DefCalM} and \eqref{eq:DefCalMTilde}, respectively.
-Therefore, due to Assumption \ref{as:regularity} which allows controlling the norm of $\mathcal M_\epl^{-1}$ and due to Lemma \ref{lem:distanceMandTildeM} we have for a constant $C > 0$
+Therefore, due to \cref{as:regularity} which allows controlling the norm of $\mathcal M_\epl^{-1}$ and due to \cref{lem:distanceMandTildeM} we have for a constant $C > 0$
 	\begin{equation}\label{eq:DistATildeAHat}
@@
 	\end{equation}
-	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to Theorem \ref{thm:mainTheorem_zeta}. Now, the triangle inequality yields
+	Let us remark that $\widehat A^\epl_k(T)$ has a bounded norm for $\epl$ sufficiently small due to \cref{thm:mainTheorem_zeta}. Now, the triangle inequality yields
 	\begin{equation}
@@
 	\end{equation}
-	Therefore, due to Theorem \ref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta = \epl^\zeta$, the desired result holds.
+	Therefore, due to \cref{thm:mainTheorem_zeta}, the inequality \eqref{eq:DistATildeAHat} and since $\delta = \epl^\zeta$, the desired result holds.
 \end{proof}
 \corr{
-In light of the proof of Theorem \ref{thm:BayesianBias}, the result above guarantees that the mean of the posterior distribution $\widetilde \mu_{T, \epl}$ converges to the drift coefficient of the homogenized equation.
+In light of the proof of \cref{thm:BayesianBias}, the result above guarantees that the mean of the posterior distribution $\widetilde \mu_{T, \epl}$ converges to the drift coefficient of the homogenized equation.
 Being the covariance matrix the same for $\mu_{T, \epl}$ and $\widetilde \mu_{T, \epl}$, it is possible to prove a positive convergence result for $\widetilde \mu_{T, \epl}$, which is given by the following Theorem.
-\begin{theorem} Let the Assumptions of Theorem \ref{thm:mainTheoremTilde} hold.
+\begin{theorem} Let the Assumptions of \cref{thm:mainTheoremTilde} hold.
 Then, the modified posterior measure $\widetilde\mu_{T,\epl}(\cdotp\mid X^\epl) = \mathcal N(\widetilde m_{T,\epl}, C_{T,\epl})$ satisfies
@@
 \end{theorem}}
-\begin{proof} The proof follows from the proof of Theorem \ref{thm:BayesianBias} and from Theorem \ref{thm:mainTheoremTilde}.
+\begin{proof} The proof follows from the proof of \cref{thm:BayesianBias} and from \cref{thm:mainTheoremTilde}.
 \end{proof}
@@
 	\includegraphics[]{Figures/Transition}
-	\caption{Results for Section \ref{sec:Num_Param1}.
+	\caption{Results for \cref{sec:Num_Param1}.
 Horizontal lines represent $\alpha$ and $A$, the drift coefficients of the unhomogenized and homogenized equations.
-The gray vertical line represents the lower bound for the validity of Theorem \ref{thm:mainTheorem_zeta}.
+The gray vertical line represents the lower bound for the validity of \cref{thm:mainTheorem_zeta}.
 The curved lines (dashed, dotted and dash-dotted) represents the values of $\widehat A_k^\epl(T)$ for $\epl = \{0.1, 0.05, 0.025\}$, respectively.
@@
 
-We first demonstrate numerically the validity of Theorem \ref{thm:mainTheorem}, Theorem \ref{thm:mainTheorem_zeta} and Theorem \ref{thm:mainTheorem_zetaAlpha}, i.e., the unbiasedness of $\widehat A^\epl_k(T)$ for $\delta = \epl^\zeta$ with $\zeta \in [0, 2)$.
+We first demonstrate numerically the validity of \cref{thm:mainTheorem}, \cref{thm:mainTheorem_zeta} and \cref{thm:mainTheorem_zetaAlpha}, i.e., the unbiasedness of $\widehat A^\epl_k(T)$ for $\delta = \epl^\zeta$ with $\zeta \in [0, 2)$.
 Let us recall that for $\zeta = 0$ the analysis and the theoretical result are fundamentally different than for $\zeta \in (0, 2)$.
@@
 Then we filter the data by choosing $\delta = \epl^\zeta$, and $\zeta = 0, 0.1, 0.2,\ldots, 3$, and compute $\widehat A^\epl_k(T)$.
-Results are displayed in Figure \ref{fig:TheoremVerification}, and show that for $\zeta > 2$, i.e., $\delta = o(\epl^2)$, the estimator tends to the drift coefficient $\alpha$ of the unhomogenized equation.
+Results are displayed in \cref{fig:TheoremVerification}, and show that for $\zeta > 2$, i.e., $\delta = o(\epl^2)$, the estimator tends to the drift coefficient $\alpha$ of the unhomogenized equation.
 Conversely, as predicted by the theory, for $\zeta \in [0, 2)$ the estimator tends to $A$, the drift coefficient of the homogenized equation.
@@
 	\end{tabular}
-	\caption{Results for Section \ref{sec:Num_Param2}.
+	\caption{Results for \cref{sec:Num_Param2}.
 The case of $\delta = \epl^0$ is highlighted as a solid dot for the filtering technique, as the analysis and theoretical result is different in this case.
@@
 Moreover, for the filtering method we consider both $\beta = 1$ and $\beta = 5$.
-We report in Figure \ref{fig:OU} the experimental results.
+We report in \cref{fig:OU} the experimental results.
 Let us remark that
@@
 We consider again $\sigma = 0.5, 0.7, 1$ and vary $\beta = 1, 2, \ldots, 10$.
-Results, given in Figure \ref{fig:OUBeta}, show empirically that the estimator stabilizes fast with respect to $\beta$.
+Results, given in \cref{fig:OUBeta}, show empirically that the estimator stabilizes fast with respect to $\beta$.
 Nevertheless, there is no theoretical guarantee supporting this empirical observation.
@@
 	\end{tabular}
-	\caption{Results for Section \ref{sec:Num_Param3}.
-The result for $\beta=1$, for which there are theoretical guarantees given by Theorem \ref{thm:mainTheorem_zeta}, is highlighted as a solid dot.
+	\caption{Results for \cref{sec:Num_Param3}.
+The result for $\beta=1$, for which there are theoretical guarantees given by \cref{thm:mainTheorem_zeta}, is highlighted as a solid dot.
 From left to right we consider different values of $\sigma$.}
@@
 	\end{tabular}
-	\caption{Results for Section \ref{sec:Num_Multi}.
+	\caption{Results for \cref{sec:Num_Multi}.
 In the figure, from left to right the potential function estimated with the data itself, the filter, subsampled data.
@@
 \end{equation}
-This potential function satisfies Assumption \ref{as:regularity} whenever $N$ is even and if the leading coefficient $\alpha_N$ is positive.
+This potential function satisfies \cref{as:regularity} whenever $N$ is even and if the leading coefficient $\alpha_N$ is positive.
 We set $N = 4$ and the drift coefficient $\alpha = (-1, -1/2, 1/2, 1)$.
@@
 In particular, we pick this specific value of $\delta$ for the subsampling following the optimality criterion given in \cite{PaS07}.
-Results, given in Figure \ref{fig:KLStyle}, show that the filter-based estimation captures well the homogenized potential as well as the coefficient $A$.
-Moreover, it is possible to remark the negative result given by Theorem \ref{thm:Bias} holds in practice, i.e., with no pre-processing the estimator $\widehat A^\epl(T)$ tends to the drift coefficient $\alpha$ of the unhomogenized equation.
+Results, given in \cref{fig:KLStyle}, show that the filter-based estimation captures well the homogenized potential as well as the coefficient $A$.
+Moreover, it is possible to remark the negative result given by \cref{thm:Bias} holds in practice, i.e., with no pre-processing the estimator $\widehat A^\epl(T)$ tends to the drift coefficient $\alpha$ of the unhomogenized equation.
 
@@
 	\end{tabular}
-	\caption{Results for Section \ref{sec:Num_Bayes}.
+	\caption{Results for \cref{sec:Num_Bayes}.
 Posterior distributions over the parameter $A = (A_1, A_2)^\top$ for the bistable potential obtained with the filtering approach.
@@
 We then consider the multiscale equation with $\sigma = 0.7$, the fast potential $p(y) = \cos(y)$ and $\epl = 0.05$, thus simulating a trajectory $X^\epl$.
-We adopt here a Bayesian approach and compute the posterior distribution $\widetilde \mu_{T, \epl}$ obtained with the filtering approach introduced in Section \ref{sec:BayesianFilter}.
+We adopt here a Bayesian approach and compute the posterior distribution $\widetilde \mu_{T, \epl}$ obtained with the filtering approach introduced in \cref{sec:BayesianFilter}.
 The parameters of the filter are set to $\beta = 1$ and $\delta = \epl$ in \eqref{eq:filter}.
@@
 We stop computations at times $T = 100, 200, 400$ in order to observe the shrinkage of the Gaussian posterior towards the MLE $\widetilde A^\epl_k(T)$ with respect to time.
-In Figure \ref{fig:Bayes}, we observe that the posterior does indeed shrink towards the MLE, which in turn gets progressively closer to the true value of the drift coefficient $A$ of the homogenized equation.
+In \cref{fig:Bayes}, we observe that the posterior does indeed shrink towards the MLE, which in turn gets progressively closer to the true value of the drift coefficient $A$ of the homogenized equation.
 
@@
 
-\begin{proof}[Proof of Lemma \ref{lem:density}] We have to show that the joint process solution to \eqref{eq:systemSDE} is hypo-elliptic. Denoting as $f\colon \R \to \R$ the function 
+\begin{proof}[Proof of \cref{lem:density}] We have to show that the joint process solution to \eqref{eq:systemSDE} is hypo-elliptic. Denoting as $f\colon \R \to \R$ the function 
 	\begin{equation}
@@
 
-\begin{proof}[Proof of Lemma \ref{lem:ergodicity}] Lemma \ref{lem:density} guarantees that the Fokker--Planck equation can be written directly from the system \eqref{eq:systemSDE}.
+\begin{proof}[Proof of \cref{lem:ergodicity}] \cref{lem:density} guarantees that the Fokker--Planck equation can be written directly from the system \eqref{eq:systemSDE}.
 For geometric ergodicity, let
@@
 	\end{equation}
-	Due to Assumption \ref{as:regularity}\ref{as:regularity_diss}, Remark \ref{rem:regularity_diss} and Young's inequality, we then have for all $\gamma > 0$
+	Due to \cref{as:regularity}\ref{as:regularity_diss}, \cref{rem:regularity_diss} and Young's inequality, we then have for all $\gamma > 0$
 	\begin{equation}
@@
 
-\begin{proof}[Proof of Lemma \ref{lem:FPMarginal}] Integrating equation \eqref{eq:FPsystem} with respect to $z$ we obtain the stationary Fokker--Planck equation for the process $X^\epl$, i.e.
+\begin{proof}[Proof of \cref{lem:FPMarginal}] Integrating equation \eqref{eq:FPsystem} with respect to $z$ we obtain the stationary Fokker--Planck equation for the process $X^\epl$, i.e.
 	\begin{equation}
@@
 
-\section{Proof of Proposition \ref{prop:zeta}}\label{ap:ProofDistance}
+\section{Proof of \cref{prop:zeta}}\label{ap:ProofDistance}
 
 \subsection{Preliminary estimates}
-In order to prove the characterization provided by Proposition \ref{prop:zeta}, we need to prove two additional results on the filter.
-First, we prove a Jensen-like inequality for the kernel of the filter.
+In order to prove the characterization provided by \cref{prop:zeta}, we need to prove two additional results on the filter. First, we prove a Jensen-like inequality for the kernel of the filter.
 
@@
 The following lemma characterizes the action of the filter when it is applied to polynomials in $(t-s)$.
-\begin{lemma}\label{lem:FilterPoly} With the notation of Lemma \ref{lem:FilterJensen}, it holds for all $p \geq 0$
+\begin{lemma}\label{lem:FilterPoly} With the notation of \cref{lem:FilterJensen}, it holds for all $p \geq 0$
 	\begin{equation}
@@
 
-\subsection{Proof of Proposition \ref{prop:zeta}}
+\subsection{Proof of \cref{prop:zeta}}
 Denoting $Y_t^\epl \defeq X_t^\epl/\epl$, we will make use of the decomposition
@@
 	\end{equation}
-	Now, Lemma \ref{lem:FilterJensen}, the inequality \eqref{eq:FirstTermPavStu} and Lemma \ref{lem:FilterPoly} yield for all $p \geq 1$
+	Now, \cref{lem:FilterJensen}, the inequality \eqref{eq:FirstTermPavStu} and \cref{lem:FilterPoly} yield for all $p \geq 1$
 	\begin{equation}
@@
 	The second term is bounded exponentially fast with respect to $t$ and $\delta$ due to \eqref{eq:boundR2}.
-For the first term, applying Lemma \ref{lem:FilterJensen}, the inequality \cite[Formula (3.25), p.
-163]{KaS91} and Lemma \ref{lem:FilterPoly} we obtain for a constant $C > 0$ independent of $\delta$ and $t$
+For the first term, applying \cref{lem:FilterJensen}, the inequality \cite[Formula (3.25), p.
+163]{KaS91} and \cref{lem:FilterPoly} we obtain for a constant $C > 0$ independent of $\delta$ and $t$
 	\begin{equation}
@@
 
-\section{Proofs of Section \ref{sec:Fast}} \label{ap:ProofsDeltaZeta}
+\section{Proofs of \cref{sec:Fast}} \label{ap:ProofsDeltaZeta}
 
@@
 \begin{lemma} \label{lem:bounded_momentZ}
-	Under Assumption \ref{as:regularity}, let $Z^\epl$ be distributed as the invariant measure $\mu^\epl$ of the couple $(X^\epl, Z^\epl)^\top$.
+	Under \cref{as:regularity}, let $Z^\epl$ be distributed as the invariant measure $\mu^\epl$ of the couple $(X^\epl, Z^\epl)^\top$.
 Then for any $p \geq 1$ there exists a constant $C > 0$ uniform in $\epl$ such that
@@
 Let $Z_t^\epl$ be the corresponding filtered process.
-By definition of $Z^\epl_t$ and applying Lemma \ref{lem:FilterJensen} we have
+By definition of $Z^\epl_t$ and applying \cref{lem:FilterJensen} we have
 	\begin{equation}
@@
 	\end{equation}
-	In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$
+	In order to conclude, we remark that due to \cref{lem:ergodicity} we have for all $t \geq 0$
 	\begin{equation}
@@
 
-Corollary \ref{cor:distanceZandX} is a direct consequence of Proposition \ref{prop:zeta} and provides a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.
-
-\begin{corollary} \label{cor:distanceZandX} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
+\cref{cor:distanceZandX} is a direct consequence of \cref{prop:zeta} and provides a rough estimate of the difference between the trajectories $X_t^\epl$ and $Z_t^\epl$ when they are at stationarity.
+
+\begin{corollary} \label{cor:distanceZandX} Under \cref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
 Then, if $\delta \leq 1$, it holds for any $p \geq 1$
@@
 \begin{proof}
-	Let $p \geq 1$, then due to Proposition \ref{prop:zeta} there exists a constant $C > 0$ depending only on $p$ such that
+	Let $p \geq 1$, then due to \cref{prop:zeta} there exists a constant $C > 0$ depending only on $p$ such that
 	\begin{equation}
@@
 	Let us now remark that this result holds for $X_t^\epl$ being at stationarity and for $Z_t^\epl$ being its filtered process, and not for a couple $(X^\epl, Z^\epl)^\top \sim \mu^\epl$.
-In order to conclude, we remark that due to Lemma \ref{lem:ergodicity} we have for all $t \geq 0$
+In order to conclude, we remark that due to \cref{lem:ergodicity} we have for all $t \geq 0$
 	\begin{equation}
@@
 This is provided by the following Lemma.
-\begin{lemma}\label{lem:distanceZandX2} Under Assumption \ref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
+\begin{lemma}\label{lem:distanceZandX2} Under \cref{as:regularity}, let the couple $(X^\epl, Z^\epl)^\top$ be distributed as its invariant measure $\mu^\epl$.
 Then, if $\delta \leq 1$, it holds for any $p \geq 1$
@@
 	\end{equation}
-	Therefore, by Assumption \ref{as:regularity} and since $X_t^\epl$ has bounded moments of all orders at stationarity \cite[Corollary 5.4]{PaS07}, it holds for any $p \ge 1$ and a constant $C > 0$
+	Therefore, by \cref{as:regularity} and since $X_t^\epl$ has bounded moments of all orders at stationarity \cite[Corollary 5.4]{PaS07}, it holds for any $p \ge 1$ and a constant $C > 0$
 	\begin{equation} \label{eq:Xt_Xs}
@@
 	\end{equation}
-	which, applying Lemma \ref{lem:FilterJensen}, the inequality \eqref{eq:Xt_Xs} and Lemma \ref{lem:FilterPoly}, implies
+	which, applying \cref{lem:FilterJensen}, the inequality \eqref{eq:Xt_Xs} and \cref{lem:FilterPoly}, implies
 	\begin{equation}
@@
 	\end{equation}
-	Geometric ergodicity (Lemma \ref{lem:ergodicity}) then implies for $\rho^\epl$ the measure of the couple $(X^\epl, Z^\epl)^\top$
+	Geometric ergodicity (\cref{lem:ergodicity}) then implies for $\rho^\epl$ the measure of the couple $(X^\epl, Z^\epl)^\top$
 	\begin{equation}
@@
 
-\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of Corollary \ref{cor:distanceZandX} hold. Then the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ satisfy
+\begin{lemma}\label{lem:distanceMandTildeM} Let the assumptions of \cref{cor:distanceZandX} hold. Then the matrices $\mathcal M_\epl$ and $\widetilde{\mathcal M}_\epl$ satisfy
 	\begin{equation}
@@
 	\end{equation}
-	The Lipschitz condition on $V'$ together with the boundedness of the moments of $X^\epl$ and Corollary \ref{cor:distanceZandX} yield for a constant $C > 0$
+	The Lipschitz condition on $V'$ together with the boundedness of the moments of $X^\epl$ and \cref{cor:distanceZandX} yield for a constant $C > 0$
 	\begin{equation}
@@
 
-\subsection{Proof of Lemma \ref{lem:quadruple}}
+\subsection{Proof of \cref{lem:quadruple}}
 
@@
 	\end{equation}
-	We now consider the remainder and, applying Hölder's inequality, Corollary \ref{cor:distanceZandX}, Lemma \ref{lem:bounded_momentZ}, Assumption \ref{as:regularityZeta} and \eqref{eq:estimate_beta}, we get for $p,q,r$ such that $1/p+1/q+1/r=1$
+	We now consider the remainder and, applying Hölder's inequality, \cref{cor:distanceZandX}, \cref{lem:bounded_momentZ}, \cref{as:regularityZeta} and \eqref{eq:estimate_beta}, we get for $p,q,r$ such that $1/p+1/q+1/r=1$
 	\begin{equation}
@@
 
-\subsection{Proof of Lemma \ref{lem:quadruple_convergence}}
+\subsection{Proof of \cref{lem:quadruple_convergence}}
 
@@
 	\end{equation}
-	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, Assumption \ref{as:regularityZeta} and Lemma \ref{cor:distanceZandX} we have
+	We first study $\Delta_1(\epl)$ and due to the boundedness of $\Phi'$, \cref{as:regularityZeta} and \cref{cor:distanceZandX} we have
 	\begin{equation}
@@
 
-\subsection{Proof of Theorem \ref{thm:mainTheorem_zetaAlpha}}
+\subsection{Proof of \cref{thm:mainTheorem_zetaAlpha}}
 	Let us consider the decomposition \eqref{eq:alphaDecomposition}, i.e.,
@@
 	\end{equation}
-	and, by the proof of Theorem \ref{thm:mainTheorem} we have independently of $\epl$
+	and, by the proof of \cref{thm:mainTheorem} we have independently of $\epl$
 	\begin{equation}
@@
 	\end{equation}
-	Since $\widetilde X^\epl$ assumes values between $X^\epl$ and $Z^\epl$, it has bounded moments by \cite[Corollary 5.4]{PaS07} and Lemma \ref{lem:bounded_momentZ}.
-Hence, applying Lemma \ref{lem:distanceZandX2} we have
+	Since $\widetilde X^\epl$ assumes values between $X^\epl$ and $Z^\epl$, it has bounded moments by \cite[Corollary 5.4]{PaS07} and \cref{lem:bounded_momentZ}.
+Hence, applying \cref{lem:distanceZandX2} we have
 	\begin{equation} 
@@
 	\end{equation}
-	Finally, Lemma \ref{lem:distanceMandTildeM} and the weak convergence of the invariant measure $\phi^\epl$ to $\phi^0$ imply
+	Finally, \cref{lem:distanceMandTildeM} and the weak convergence of the invariant measure $\phi^\epl$ to $\phi^0$ imply
 	\begin{equation}

### 2020-04-01 SIAM_TEMPLATE/PaperSDE.tex
Minor Fix

@@
 This equation can be coupled with the dynamics of the processes $X_t^\epl$, $Y_t^\epl$ and $Z_t^\epl$, thus describing the evolution of the quadruple $(X^\epl, Y^\epl, Z^\epl, B^\epl)$ together.
-In particular, it is possible to show that the results of \cref{sec:ergodic} hold for the quadruple, and the properties of the invariant measure of the quadruple can be exploited to prove the unbiasedness of the estimator in the case $\delta = \mathcal O(\epl^\zeta)$ in the same way as in the case $\delta = \mathcal O(\epl^0)$.
+In particular, it is possible to show that the results of Section \ref{sec:ergodic} hold for the quadruple, and the properties of the invariant measure of the quadruple can be exploited to prove the unbiasedness of the estimator in the case $\delta = \mathcal O(\epl^\zeta)$ in the same way as in the case $\delta = \mathcal O(\epl^0)$.
 In this context, a further assumption on the potential $V$ is necessary.
@@
 	\includegraphics[]{Figures/Transition}
-	\caption{Results for \cref{sec:Num_Param1}.
+	\caption{Results for Section \ref{sec:Num_Param1}.
 Horizontal lines represent $\alpha$ and $A$, the drift coefficients of the unhomogenized and homogenized equations.
@@
 	\end{tabular}
-	\caption{Results for \cref{sec:Num_Param2}.
+	\caption{Results for Section \ref{sec:Num_Param2}.
 The case of $\delta = \epl^0$ is highlighted as a solid dot for the filtering technique, as the analysis and theoretical result is different in this case.
@@
 	\end{tabular}
-	\caption{Results for \cref{sec:Num_Param3}.
+	\caption{Results for Section \ref{sec:Num_Param3}.
 The result for $\beta=1$, for which there are theoretical guarantees given by \cref{thm:mainTheorem_zeta}, is highlighted as a solid dot.
@@
 	\end{tabular}
-	\caption{Results for \cref{sec:Num_Multi}.
+	\caption{Results for Section \ref{sec:Num_Multi}.
 In the figure, from left to right the potential function estimated with the data itself, the filter, subsampled data.
@@
 	\end{tabular}
-	\caption{Results for \cref{sec:Num_Bayes}.
+	\caption{Results for Section \ref{sec:Num_Bayes}.
 Posterior distributions over the parameter $A = (A_1, A_2)^\top$ for the bistable potential obtained with the filtering approach.
@@
 We then consider the multiscale equation with $\sigma = 0.7$, the fast potential $p(y) = \cos(y)$ and $\epl = 0.05$, thus simulating a trajectory $X^\epl$.
-We adopt here a Bayesian approach and compute the posterior distribution $\widetilde \mu_{T, \epl}$ obtained with the filtering approach introduced in \cref{sec:BayesianFilter}.
+We adopt here a Bayesian approach and compute the posterior distribution $\widetilde \mu_{T, \epl}$ obtained with the filtering approach introduced in Section \ref{sec:BayesianFilter}.
 The parameters of the filter are set to $\beta = 1$ and $\delta = \epl$ in \eqref{eq:filter}.
@@
 
-\section{Proofs of \cref{sec:Fast}} \label{ap:ProofsDeltaZeta}
+\section{Proofs of Section \ref{sec:Fast}} \label{ap:ProofsDeltaZeta}
 
